### 2021-05-20 manuscript/Chapter3-manuscript.Rmd
draft of the introduction

---
title: "How hunting experience, habitat structure, and prey predictability jointly shape individual specialisation in predator foraging mode in an online videogame"
author: "Maxime Fraser Franco^1^, Francesca Santostefano^1^, Clint D. Kelly^1^, Pierre-Olivier Montiglio^1^"
output: 
  word_document:
    reference_docx: Chapter3-styles.docx
bibliography: references.bib
csl: american-naturalist.csl
---
###### Groupe de Recherche en Écologie Comportementale et Animale (GRECA), Département des Sciences Biologiques, Université du Québec à Montréal, Montréal, QC, Canada

###### ^1^Correspondence: Pavillon des Sciences Biologiques (SB) SB-1805, 141 Avenue du Président-Kennedy, Montréal (Québec), Canada, H2X 1Y4

###### ^1^Corresponding author: maxime(dot)fraser(dot)franco(at)hotmail.com

\newpage
# Abstract {.unnumbered}
This is my abstract paragraph

Keywords: individual variation, hunting success, plasticity, learning, prey predictability, online videogames

\newpage
# Introduction {.unnumbered}

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [sources]. Recently, ecologists have began to hypothesise that there may be a functional relationship linking individual foraging specialisation to specialisation in resource consumption (i.e. niche specialisation) [sources: Toscano et al. 2016, etc]. One of the postulates of this hypothesis is that predators need to develop specific foraging tactics that are fine tuned to specific prey attributes [sources: Phillips, Woo, etc.]. For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter [sources : Woo, Estes, tinker, etc]. However, it remains largely unclear how extrinsinc and intrinsinct factors interact to shape these individual-level processes. Therefore, we still have limited knowledge on the ecological consequences of individual foraging and diet specialisation. An important question that remains unanswered is how generalist and specialist individuals can coexist within predator populations. If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate these two individual components with their associate causes and consequences.

Several studies have shown that generalist and specialist individuals often don't differ in fitness related measures [sources: à partir de Woo]. An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on the time scale [sources : Woo, Phillips, Ceia, etc]. The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns. The rationale behind this prediction is that individuals should have higher prey delivery rates when they repeatedly employ the same foraging technique as it is easier to assess prey predictability over shorter time-scales. In contrast, individual generalists should be advantaged over longer time scales as resource parameters are expected to fluctuate.

Hunting experience and age have been proposed as major potential drivers of the relationship between foraging specialisation and resource use [sources]. Learning how to hunt is crucial for young predators to reach adulthood and survive.

(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)

A second important driver of individual differences in predator hunting behaviour is related to habitat specific features [sources]. Predators are expected to adjust their foraging strategies to their habitat as they offer different structures which can aid/impair (ex. perches, vegetation density) vision or the ability to hide, which may facilitate the use of a specific hunting mode (ambush vs cursorial). For instance, predators often shift from a cursorial hunting mode in open and homogeneous landscapes, to an ambush hunting mode in closed and heterogeneous landscapes [sources].

Several studies have shown that individual specialists can outperform

- Paragraphe 1 (effet de la taille, du sexe, et importance du foraging mode)

- Paragraphe 2 (importance des proies (woo et al.) et de l'habitat)

- Paragraphe 3 (importance de l'expérience et comment c'est un rôle probable mais encore inexploré) (sources Weimerskirch, 2005, 2007)

- Paragraphe 4 (système qu'on utilise) (jeux vidéo : paragraphe le + court possible)

- Paragraphe 5 (objectifs et hypotèses)

### 2021-05-20 manuscript/Chapter3-manuscript.Rmd
updated intro

@@
 One of the postulates of this hypothesis is that predators need to develop specific foraging tactics that are fine tuned to specific prey attributes [sources: Phillips, Woo, etc.].
-For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter [sources : Woo, Estes, tinker, etc].
+For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc].
 However, it remains largely unclear how extrinsinc and intrinsinct factors interact to shape these individual-level processes.
@@
 An important question that remains unanswered is how generalist and specialist individuals can coexist within predator populations.
-If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate these two individual components with their associate causes and consequences.
+If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate the causes and consequences of these two individual components.
 
-Several studies have shown that generalist and specialist individuals often don't differ in fitness related measures [sources: à partir de Woo].
-An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on the time scale [sources : Woo, Phillips, Ceia, etc].
+Several studies have often shown that generalist and specialist individuals don't differ in fitness related measures [sources: à partir de Woo].
+An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc].
 The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns.
@@
 
+(learning optimises return rates or foraging success)
 (par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)

### 2021-05-20 manuscript/Chapter3-manuscript.Rmd
notes intro
updated intro

@@
 
-Several studies have often shown that generalist and specialist individuals don't differ in fitness related measures [sources: à partir de Woo].
+A number of long-term studies have observed similar fitness related measures generalist and specialist individuals [sources: à partir de Woo].
 An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc].
@@
 
-A second important driver of individual differences in predator hunting behaviour is related to habitat specific features [sources].
-Predators are expected to adjust their foraging strategies to their habitat as they offer different structures which can aid/impair (ex.
-perches, vegetation density) vision or the ability to hide, which may facilitate the use of a specific hunting mode (ambush vs cursorial).
-For instance, predators often shift from a cursorial hunting mode in open and homogeneous landscapes, to an ambush hunting mode in closed and heterogeneous landscapes [sources].
+A second important driver of individual differences in predator hunting behaviour is related to habitat-specific features [sources, Kobler, parler de la ideal free distribution?].
+Predators are expected to adjust their foraging mode (ambush vs cursorial) to habitat structures that aid/impair (ex.
+perches, vegetation density) their vision, ability to hide, or energetic/time requirements.
+For instance, predators who ambush in closed and heterogeneous landscapes often switch to cursorial hunters in open and homogeneous landscapes [sources].
+(Donner exemple des orcs)
 

### 2021-05-20 tests/test.R
added .csl files created test script

@@ -1,0 +1,2 @@
+library(rmarkdown)
+rmarkdown::render("./manuscript/Chapter3-manuscript.Rmd")

### 2021-05-20 manuscript/Chapter3-manuscript.Rmd
update manuscript

@@
 niche specialisation) [sources: Toscano et al.
-2016, etc].
+2016, etc, michalko et gibbons, Kerr, Tinker, Bowen].
 One of the postulates of this hypothesis is that predators need to develop specific foraging tactics that are fine tuned to specific prey attributes [sources: Phillips, Woo, etc.].
@@
 
-A number of long-term studies have observed similar fitness related measures generalist and specialist individuals [sources: à partir de Woo].
-An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc].
+A number of long-term studies have observed similar fitness related measures among generalist and specialist individuals [sources: à partir de Woo].
+An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc, Courbin, Chang].
 The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns.

### 2021-07-08 manuscript/Chapter3-manuscript.Rmd
update manuscript
analysis plan and updated introduction

@@
 ---
-title: "How hunting experience, habitat structure, and prey predictability jointly shape individual specialisation in predator foraging mode in an online videogame"
-author: "Maxime Fraser Franco^1^, Francesca Santostefano^1^, Clint D. Kelly^1^, Pierre-Olivier Montiglio^1^"
+title: "How hunting experience and prey predictability jointly shape individual foraging and diet specialisation of a predator within an online multiplayer videogame"
 output: 
@@
 ---
-###### Groupe de Recherche en Écologie Comportementale et Animale (GRECA), Département des Sciences Biologiques, Université du Québec à Montréal, Montréal, QC, Canada
-
-###### ^1^Correspondence: Pavillon des Sciences Biologiques (SB) SB-1805, 141 Avenue du Président-Kennedy, Montréal (Québec), Canada, H2X 1Y4
-
-###### ^1^Corresponding author: maxime(dot)fraser(dot)franco(at)hotmail.com
 
@@
 # Abstract {.unnumbered}
-This is my abstract paragraph
+Key points in this study:
+
+- How experience shapes individual specialisation
+  - H1: experience increases the range of behaviors and plasticity by reducing costs to swithing
+  - H2: optimizing/refinement process - specialize with time - increase success)
+
+- Prey predictability shapes individual foraging specialization
+  - H1: prey predictability is positively correlated to behavioral predictability
+
+- Specialist hunters will fare better on short timescales, when prey predictability is higher
+- Generalist hunters will fare better on longer timescales, as they follow prey fluctuations
+- Both types of hunters will thus achieve similar hunting success over the sampling period
 
@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [sources].
-Recently, ecologists have began to hypothesise that there may be a functional relationship linking individual foraging specialisation to specialisation in resource consumption (i.e.
-niche specialisation) [sources: Toscano et al.
+A potential consequence of among-individual differences in foraging behavior is that they can lead to individual differences in the type of prey captured (i.e.
+individual niche specialization) [Woo et al., 2008, sources].
+There may thus exist a functional relationship linking individual foraging specialisation to specialisation in resource consumption [sources: Toscano et al.
 2016, etc, michalko et gibbons, Kerr, Tinker, Bowen].
-One of the postulates of this hypothesis is that predators need to develop specific foraging tactics that are fine tuned to specific prey attributes [sources: Phillips, Woo, etc.].
+This would imply that predators need to develop foraging tactics that are fine tuned to specific prey attributes or prey types [sources: Phillips, Woo, etc.].
 For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc].
-However, it remains largely unclear how extrinsinc and intrinsinct factors interact to shape these individual-level processes.
-Therefore, we still have limited knowledge on the ecological consequences of individual foraging and diet specialisation.
-An important question that remains unanswered is how generalist and specialist individuals can coexist within predator populations.
+However, it remains largely unclear how extrinsinc and intrinsinct factors interact to shape these individual differences.
+Therefore, we still have limited knowledge on how individual foraging specialisation arises, and its ecological and community consequences.
+
+(travailler ceci) An important question that remains unanswered is how can generalist and specialist individuals coexist within predator populations.
 If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate the causes and consequences of these two individual components.
 
-A number of long-term studies have observed similar fitness related measures among generalist and specialist individuals [sources: à partir de Woo].
+A number of long-term studies observed that generalist and specialist individuals can achieve similar fitness [sources: à partir de Woo].
 An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc, Courbin, Chang].
 The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns.
-The rationale behind this prediction is that individuals should have higher prey delivery rates when they repeatedly employ the same foraging technique as it is easier to assess prey predictability over shorter time-scales.
-In contrast, individual generalists should be advantaged over longer time scales as resource parameters are expected to fluctuate.
+The rationale is that individuals should have higher prey delivery rates when they repeatedly employ the same foraging technique, as it is easier to assess prey predictability over shorter time-scales.
+In contrast, individual generalists should be advantaged over longer time scales, as resource parameters are expected to fluctuate.
+[revoir ceia et ramos pour les sources]
 
-Hunting experience and age have been proposed as major potential drivers of the relationship between foraging specialisation and resource use [sources].
+Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources].
 Learning how to hunt is crucial for young predators to reach adulthood and survive.
@@
 (learning optimises return rates or foraging success)
+(apprentissage, search images, prior information)
 (par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
 (parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)
-
-A second important driver of individual differences in predator hunting behaviour is related to habitat-specific features [sources, Kobler, parler de la ideal free distribution?].
-Predators are expected to adjust their foraging mode (ambush vs cursorial) to habitat structures that aid/impair (ex.
-perches, vegetation density) their vision, ability to hide, or energetic/time requirements.
-For instance, predators who ambush in closed and heterogeneous landscapes often switch to cursorial hunters in open and homogeneous landscapes [sources].
-(Donner exemple des orcs)
 

### 2022-05-18 manuscript/Chapter3-manuscript.Rmd
updated the plan
wrote last paragraph of intro

@@
 ---
-title: "How hunting experience and prey predictability jointly shape individual foraging and diet specialisation of a predator within an online multiplayer videogame"
+title: "Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame"
 output: 
@@
 
-Keywords: individual variation, hunting success, plasticity, learning, prey predictability, online videogames
+Keywords: foraging behaviour, individual specialization, experience, learning, prey predictability, online videogames
 
@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [sources].
+*Ideas* : 
+- * usually measured at the population level*
+- * we now have metrics that enable the quantification of individual specialization*
+
 A potential consequence of among-individual differences in foraging behavior is that they can lead to individual differences in the type of prey captured (i.e.
@@
 This would imply that predators need to develop foraging tactics that are fine tuned to specific prey attributes or prey types [sources: Phillips, Woo, etc.].
+*ICI GARDER LES IDÉES MAIS METTRE L'ACCENT SUR LE FAIT QUE C'EST LES PROIES DISPONIBLES AU LIEU DES PROIES MANGÉES*
+
 For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc].
@@
 If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate the causes and consequences of these two individual components.
+
+Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources].
+Learning how to hunt is crucial for young predators to reach adulthood and survive.
+(check Urszan et al)
 
@@
 
-Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources].
-Learning how to hunt is crucial for young predators to reach adulthood and survive.
-
 (learning optimises return rates or foraging success)
@@
 
-- Paragraphe 1 (effet de la taille, du sexe, et importance du foraging mode)
+- Paragraphe 1 : Importance of among-individual variation in foraging behaviour
 
-- Paragraphe 2 (importance des proies (woo et al.) et de l'habitat)
+- Paragraphe 2 : Factors shaping individual variation in foraging behaviour - the role of experience
+  (sources Weimerskirch, 2005, 2007) (explain mechanisms). Explain how it may unravel why foraging specialists are often thought to be more succesful.
 
-- Paragraphe 3 (importance de l'expérience et comment c'est un rôle probable mais encore inexploré) (sources Weimerskirch, 2005, 2007)
+- Paragraphe 3: (Linking prey variability to experience (woo et al.)) how trophic interactions are probably the main driver of learning and experience
 
@@
 - Paragraphe 5 (objectifs et hypotèses)
+
+*Idéé* :
+- Est-ce que ça se pourrait que les proies déterminent si les prédateurs se spécialize avec l'expérience ou plutôt deviennent flexible?
+Dans ce cas, j'utiliserais pas la covariance mais le comportement des proies en effet fixe sur la variance?
+ou il faudrait que je change les covariances?
+
+# Dernier paragraphe intro (Thèsez-vous)
+Here, we collected individual behavioural data from players in *Dead by Daylight* to investigate how hunting experience and the behavioural variation in prey encountered shaped predator foraging specialization.
+This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial.
+First, we hypothesize that individual hunting behaviour will change with hunting experience.
+If experience reduces the costs of switching tactics, then predators should become more flexible through time.
+Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time.
+Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator foraging behaviour.
+Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable.
+Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal.
+Specialist hunters should fare better when prey variability is lower, while flexible hunters will fare better when prey variability is higher.

### 2022-05-18 manuscript/Chapter3-manuscript.Rmd
update manuscript. delete workspace

@@
 # Abstract {.unnumbered}
-Key points in this study:
-
-- How experience shapes individual specialisation
-  - H1: experience increases the range of behaviors and plasticity by reducing costs to swithing
-  - H2: optimizing/refinement process - specialize with time - increase success)
-
-- Prey predictability shapes individual foraging specialization
-  - H1: prey predictability is positively correlated to behavioral predictability
-
-- Specialist hunters will fare better on short timescales, when prey predictability is higher
-- Generalist hunters will fare better on longer timescales, as they follow prey fluctuations
-- Both types of hunters will thus achieve similar hunting success over the sampling period
 
@@
 
-Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [sources].
+Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015].
+Studies report for many predator species that populations are often comprised of an assemblage of individuals specialising in different foraging strategies or resources [].
+
 *Ideas* : 
 - * usually measured at the population level*
+- *effets de l'âge, blablabla*
 - * we now have metrics that enable the quantification of individual specialization*
@@
 (check Urszan et al)
+(learning optimises return rates or foraging success)
+(apprentissage, search images, prior information)
+(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
+(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)
 
@@
 [revoir ceia et ramos pour les sources]
-
-(learning optimises return rates or foraging success)
-(apprentissage, search images, prior information)
-(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
-(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)
 

### 2022-05-18 manuscript/Chapter3-manuscript.Rmd
update renv. first par manuscript. update refs

@@
 
-Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015].
-Studies report for many predator species that populations are often comprised of an assemblage of individuals specialising in different foraging strategies or resources [].
+Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015, @Michalko.Pekar2016].
+Indeed, predator populations are often comprised of an assemblage of individuals that specialize in different foraging strategies or resources [@ceiaIndividualSpecializationForaging2015, @phillipsCausesConsequencesIndividual2017].
+Sexual and age related differences are common proximate factors underlying such among-individual variation, while environmental heterogeneity is known as a prevailing external factor [].
+
+*les drivers connus (age, sex, etc.), mais quand on contrôle on voit que la spécxialisation est toujours là!!* *(finir en mettant l'accent sur le fait que les interactions modulent aussi, mais qu'on sait très peu comment ça interagit avec les facteurs proximaux)*
 

### 2022-05-18 manuscript/Chapter3-manuscript.Rmd
almost done par.1

@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015, @Michalko.Pekar2016].
-Indeed, predator populations are often comprised of an assemblage of individuals that specialize in different foraging strategies or resources [@ceiaIndividualSpecializationForaging2015, @phillipsCausesConsequencesIndividual2017].
-Sexual and age related differences are common proximate factors underlying such among-individual variation, while environmental heterogeneity is known as a prevailing external factor [].
+Indeed, predator populations are often composed of an assemblage of individuals that specialize in different foraging strategies or resources [@estesIndividualVariationPrey2003, tinkerFoodLimitationLeads2008, kernaleguenDeterminantsIndividualForaging2015, @phillipsCausesConsequencesIndividual2017].
+It is now well established that such individual specialization cannot be attributed exclusively to sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003, bolnickEcologyIndividualsIncidence2003, Woo.etal2008, bolnickWhyIntraspecificTrait2011].
+Indeed, a growing body of evidence suggests that ecological interactions may act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011, @toscanoPersonalityForagingBehavior2016].
+For instance, competition, cooperation, and predation, are all expected to shape the foraging preferences of interacting individuals [].
+Yet, we have very limited knowledge on how intrinsic factors and ecological interactions reciprocally affect foraging specialization, and the underlying consequences of such among-individual differences for natural populations.
+*phillips 2017*
 
-*les drivers connus (age, sex, etc.), mais quand on contrôle on voit que la spécxialisation est toujours là!!* *(finir en mettant l'accent sur le fait que les interactions modulent aussi, mais qu'on sait très peu comment ça interagit avec les facteurs proximaux)*
+*on connait peu sur l'interaction entre facteurs internes et externes, et encore moins les consequences de ces interactions (fitness, etc)*
+
+sexual, morphological, or age-related differences, while environmental heterogeneity is a prevailing external factor [@Weimerskirch2007, @ceiaIndividualSpecializationForaging2015, @phillipsCausesConsequencesIndividual2017, @Patrick.etal2021].
+
+*les drivers connus (age, sex, etc.), mais quand on contrôle on voit que la spécialisation est toujours là!!
+(bolnick, araujo, woo)* *(finir en mettant l'accent sur le fait que les interactions modulent aussi, mais qu'on sait très peu comment ça interagit avec les facteurs proximaux)*
 
 *Ideas* : 
-- * usually measured at the population level*
-- *effets de l'âge, blablabla*
-- * we now have metrics that enable the quantification of individual specialization*
+- * we now have metrics that enable the quantification of individual specialization (cleasby)*
 

### 2022-05-19 manuscript/Chapter3-manuscript.Rmd
update intro par 1 and last. rearrange ideas

@@
 Indeed, predator populations are often composed of an assemblage of individuals that specialize in different foraging strategies or resources [@estesIndividualVariationPrey2003, tinkerFoodLimitationLeads2008, kernaleguenDeterminantsIndividualForaging2015, @phillipsCausesConsequencesIndividual2017].
-It is now well established that such individual specialization cannot be attributed exclusively to sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003, bolnickEcologyIndividualsIncidence2003, Woo.etal2008, bolnickWhyIntraspecificTrait2011].
-Indeed, a growing body of evidence suggests that ecological interactions may act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011, @toscanoPersonalityForagingBehavior2016].
-For instance, competition, cooperation, and predation, are all expected to shape the foraging preferences of interacting individuals [].
-Yet, we have very limited knowledge on how intrinsic factors and ecological interactions reciprocally affect foraging specialization, and the underlying consequences of such among-individual differences for natural populations.
-*phillips 2017*
-
-*on connait peu sur l'interaction entre facteurs internes et externes, et encore moins les consequences de ces interactions (fitness, etc)*
+It is now well established that individual foraging specialization cannot be attributed exclusively to instrinsic factors such as sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003, bolnickEcologyIndividualsIncidence2003, Woo.etal2008, bolnickWhyIntraspecificTrait2011].
+A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011, @toscanoPersonalityForagingBehavior2016].
+Yet, we have very limited knowledge on how intrinsic factors and interactions with prey reciprocally affect predator foraging specialization, and the underlying ecological and fitness consequences of such among-individual differences [@phillipsCausesConsequencesIndividual2017].
 
 sexual, morphological, or age-related differences, while environmental heterogeneity is a prevailing external factor [@Weimerskirch2007, @ceiaIndividualSpecializationForaging2015, @phillipsCausesConsequencesIndividual2017, @Patrick.etal2021].
-
-*les drivers connus (age, sex, etc.), mais quand on contrôle on voit que la spécialisation est toujours là!!
-(bolnick, araujo, woo)* *(finir en mettant l'accent sur le fait que les interactions modulent aussi, mais qu'on sait très peu comment ça interagit avec les facteurs proximaux)*
 
@@
 
-(travailler ceci) An important question that remains unanswered is how can generalist and specialist individuals coexist within predator populations.
-If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate the causes and consequences of these two individual components.
-
 Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources].
@@
 [revoir ceia et ramos pour les sources]
+
+(travailler ceci) An important question that remains unanswered is how can generalist and specialist individuals coexist within predator populations.
+If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate the causes and consequences of these two individual components.
 
@@
 This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial.
-First, we hypothesize that individual hunting behaviour will change with hunting experience.
-If experience reduces the costs of switching tactics, then predators should become more flexible through time.
+First, we hypothesize that individual predator behaviour will change with hunting experience.
+If experience reduces the costs of switching between hunting tactics, then predators should become more flexible through time.
 Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time.
-Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator foraging behaviour.
+Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator hunting tactics.
 Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable.
 Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal.
-Specialist hunters should fare better when prey variability is lower, while flexible hunters will fare better when prey variability is higher.
+Specialist hunters should fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.

### 2022-05-19 manuscript/Chapter3-manuscript.Rmd
update MS and bib. Knit MS. dump file

@@
 
-Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002, @schreiberCommunityEffectsPhenotypic2011, @pettorelliChapterTwoIndividual2015, @Michalko.Pekar2016].
-Indeed, predator populations are often composed of an assemblage of individuals that specialize in different foraging strategies or resources [@estesIndividualVariationPrey2003, tinkerFoodLimitationLeads2008, kernaleguenDeterminantsIndividualForaging2015, @phillipsCausesConsequencesIndividual2017].
-It is now well established that individual foraging specialization cannot be attributed exclusively to instrinsic factors such as sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003, bolnickEcologyIndividualsIncidence2003, Woo.etal2008, bolnickWhyIntraspecificTrait2011].
-A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011, @toscanoPersonalityForagingBehavior2016].
-Yet, we have very limited knowledge on how intrinsic factors and interactions with prey reciprocally affect predator foraging specialization, and the underlying ecological and fitness consequences of such among-individual differences [@phillipsCausesConsequencesIndividual2017].
+Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016].
+Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015:@Phillips.etal2017].
+It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003;@bolnickEcologyIndividualsIncidence2003; @Woo.etal2008;@bolnickWhyIntraspecificTrait2011].
+A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016].
+For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [sources : Woo, Estes, tinker, etc] (*and the capacity to learn these strategies may be an important limiting factor to be successful*).
+Yet, we have very limited knowledge on how intrinsic factors and interactions with prey reciprocally affect predator foraging specialization, and the resulting ecological and fitness consequences of such among individual differences [@Phillips.etal2017].
 
-sexual, morphological, or age-related differences, while environmental heterogeneity is a prevailing external factor [@Weimerskirch2007, @ceiaIndividualSpecializationForaging2015, @phillipsCausesConsequencesIndividual2017, @Patrick.etal2021].
+environmental heterogeneity is a prevailing external factor [@Weimerskirch2007;@ceiaIndividualSpecializationForaging2015;@Phillips.etal2017;@Patrick.etal2021].
 
-*Ideas* : 
-- * we now have metrics that enable the quantification of individual specialization (cleasby)*
-
-A potential consequence of among-individual differences in foraging behavior is that they can lead to individual differences in the type of prey captured (i.e.
-individual niche specialization) [Woo et al., 2008, sources].
-There may thus exist a functional relationship linking individual foraging specialisation to specialisation in resource consumption [sources: Toscano et al.
-2016, etc, michalko et gibbons, Kerr, Tinker, Bowen].
 This would imply that predators need to develop foraging tactics that are fine tuned to specific prey attributes or prey types [sources: Phillips, Woo, etc.].
@@
 For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc].
-However, it remains largely unclear how extrinsinc and intrinsinct factors interact to shape these individual differences.
-Therefore, we still have limited knowledge on how individual foraging specialisation arises, and its ecological and community consequences.
+However, it remains largely unclear *accent sur le fait que on est pas sur les mécanismes qui associe la proie à la tactique*
 
@@
 
+Here, we collected individual behavioural data from players in *Dead by Daylight* to investigate how hunting experience and the behavioural variation in prey encountered shaped predator foraging specialization.
+This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial.
+First, we hypothesize that individual predator behaviour will change with hunting experience.
+If experience reduces the costs of switching between hunting tactics, then predators should become more flexible through time.
+Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time.
+Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator hunting tactics.
+Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable.
+Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal.
+Specialist hunters should fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
+
+# Squelette de l'intro
+
 - Paragraphe 1 : Importance of among-individual variation in foraging behaviour
@@
 
-# Dernier paragraphe intro (Thèsez-vous)
-Here, we collected individual behavioural data from players in *Dead by Daylight* to investigate how hunting experience and the behavioural variation in prey encountered shaped predator foraging specialization.
-This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial.
-First, we hypothesize that individual predator behaviour will change with hunting experience.
-If experience reduces the costs of switching between hunting tactics, then predators should become more flexible through time.
-Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time.
-Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator hunting tactics.
-Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable.
-Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal.
-Specialist hunters should fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
+*Ideas* : 
+- * we now have metrics that enable the quantification of individual specialization (cleasby)*

### 2022-05-19 manuscript/Chapter3-manuscript.Rmd
update MS introduction

@@
 Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015:@Phillips.etal2017].
-It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003;@bolnickEcologyIndividualsIncidence2003; @Woo.etal2008;@bolnickWhyIntraspecificTrait2011].
+It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@bolnickEcologyIndividualsIncidence2003;@bolnickWhyIntraspecificTrait2011].
 A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016].
-For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [sources : Woo, Estes, tinker, etc] (*and the capacity to learn these strategies may be an important limiting factor to be successful*).
-Yet, we have very limited knowledge on how intrinsic factors and interactions with prey reciprocally affect predator foraging specialization, and the resulting ecological and fitness consequences of such among individual differences [@Phillips.etal2017].
-
-environmental heterogeneity is a prevailing external factor [@Weimerskirch2007;@ceiaIndividualSpecializationForaging2015;@Phillips.etal2017;@Patrick.etal2021].
-
-This would imply that predators need to develop foraging tactics that are fine tuned to specific prey attributes or prey types [sources: Phillips, Woo, etc.].
-*ICI GARDER LES IDÉES MAIS METTRE L'ACCENT SUR LE FAIT QUE C'EST LES PROIES DISPONIBLES AU LIEU DES PROIES MANGÉES*
-
-For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc].
-However, it remains largely unclear *accent sur le fait que on est pas sur les mécanismes qui associe la proie à la tactique*
+For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn through experience how to effectively use them is essential to maintain foraging success.
+Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions [@Phillips.etal2017].
 
@@
 (parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)
+[*références learning : phillips, Haage(minks), Tinker (théorique), Weimerskirch ()*]
 
@@
 [revoir ceia et ramos pour les sources]
+
+sources générales sur heterogeneité[@Weimerskirch2007;@ceiaIndividualSpecializationForaging2015;@Phillips.etal2017;@Patrick.etal2021].
 

### 2022-05-19 manuscript/Chapter3-manuscript.Rmd
start paragraph 2 of intro

@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016].
-Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015:@Phillips.etal2017].
+Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
 It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@bolnickEcologyIndividualsIncidence2003;@bolnickWhyIntraspecificTrait2011].
@@
 For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn through experience how to effectively use them is essential to maintain foraging success.
-Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions [@Phillips.etal2017].
+Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions.
 
-Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources].
-Learning how to hunt is crucial for young predators to reach adulthood and survive.
-(check Urszan et al)
-(learning optimises return rates or foraging success)
+Learning how to hunt prey is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@heithausFeedingStrategiesTactics2018].
+Theory predicts that specialization through learning may result from past experiences in handling prey as well as a limited ability to retain complex learned skills for multiple prey types [@Tinker.etal2009].
+Empirical studies shows that learning can optimize the efficiency of foraging strategies (e.g.
+search and handling times, return rates) potentially via associative images or increased reliance on prey and environmental cues [@edwardsRoleExperienceDevelopment1994;@morseEffectExperienceHunting2000;@reidLearningHuntRole2010;@wilson-rankinLevelExperienceModulates2015].
+While this does not directly indicate foraging specialization, such optimization may reinforce the use of the same strategy (i.e.
+specialization) if its success is constant through repeated attempts.
+*parler des couts d'apprendre de quoi d'autre*
+
+*expliquer comment ça optimise*
+*expliquer comment ça peut mener aussi à de la plasticité*
+*parler des coûts*
+
 (apprentissage, search images, prior information)
@@
 (parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)
-[*références learning : phillips, Haage(minks), Tinker (théorique), Weimerskirch ()*]
+[*références learning : phillips, Haage(minks = learn mène à plasticité), Tinker (théorique), Weimerskirch (only suggest memory)*] *[courbin = switch souvent possiblement avec learn, Zango = suggère, Woo = suggère, Estes = suggère.]*
+
+*Wilson-Rankin: Because resources and their distribution vary both in time and space, foraging strategies must allow for the detection and response to fluctuations in resource levels* (Ishii et Shimada : learning = plasticity)
 
@@
 [revoir ceia et ramos pour les sources]
+*ce qu'il manque, c'est qu'on a aucune idée comment des différences individuelles de variabilité environnementale se traduisent par des différences de stratégies*
 

### 2022-05-20 manuscript/Chapter3-manuscript.Rmd
update ms intro ideas. update bib file

@@
 A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016].
-For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn through experience how to effectively use them is essential to maintain foraging success.
+For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn how to effectively use them is essential to maintain foraging success.
 Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions.
@@
 Learning how to hunt prey is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@heithausFeedingStrategiesTactics2018].
-Theory predicts that specialization through learning may result from past experiences in handling prey as well as a limited ability to retain complex learned skills for multiple prey types [@Tinker.etal2009].
-Empirical studies shows that learning can optimize the efficiency of foraging strategies (e.g.
-search and handling times, return rates) potentially via associative images or increased reliance on prey and environmental cues [@edwardsRoleExperienceDevelopment1994;@morseEffectExperienceHunting2000;@reidLearningHuntRole2010;@wilson-rankinLevelExperienceModulates2015].
-While this does not directly indicate foraging specialization, such optimization may reinforce the use of the same strategy (i.e.
+Theory predicts that specialization through learning may be driven by past experiences as well as a limited ability to retain multiple complex hunting skills [@Tinker.etal2009].
+Empirical studies show that learning enables predators to optimize the efficiency (e.g.
+search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@edwardsRoleExperienceDevelopment1994;@morseEffectExperienceHunting2000;@reidLearningHuntRole2010;@wilson-rankinLevelExperienceModulates2015].
+Such optimization may thus reinforce the use of the same tactic (i.e.
 specialization) if its success is constant through repeated attempts.
@@
 *parler des coûts*
+*pt dire en haut que ça optimise directement et mène à la spécialisation*
 
@@
 *Wilson-Rankin: Because resources and their distribution vary both in time and space, foraging strategies must allow for the detection and response to fluctuations in resource levels* (Ishii et Shimada : learning = plasticity)
+
+*un autre truc que je pourrais parler est le fait que si on assume que les individus deviennent meilleurs avec l'expertise (Dukas), on voit pourtant dans les études marines que les individus de groupes d'âges variés performent souvent de manière similaire.
+Ça amènerait bien l'autre paragraphe pour montrer que les interactions écologiques ont un rôle clé!!*
 
@@
 If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate the causes and consequences of these two individual components.
-
-Several studies have shown that individual specialists can outperform
+Several studies have shown that individual specialists can outperform.
+*[ici je crois que je vais changer un peu cela.
+C'est surtout des idées.
+Ici on veut souligner l'importance des deux mais rappeler comme d'habitude que c'est difficile à mesurer à travers le temps blabla.
+J'introduis ensuite le jeu vidéo]*
 

### 2022-05-20 manuscript/Chapter3-manuscript.Rmd
update introduction. second paragraph mostly done.

@@
 ---
-title: "Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame"
+title: "Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame"
 output: 
@@
 bibliography: references.bib
-csl: american-naturalist.csl
+csl: e-letters.csl
 ---
@@
 Learning how to hunt prey is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@heithausFeedingStrategiesTactics2018].
-Theory predicts that specialization through learning may be driven by past experiences as well as a limited ability to retain multiple complex hunting skills [@Tinker.etal2009].
-Empirical studies show that learning enables predators to optimize the efficiency (e.g.
+Theory predicts that learning may promote foraging specialization via past experiences, extensive practice, as well as a limited ability to retain multiple complex hunting skills [@Tinker.etal2009;@Dukas2019].
+From this perspective, learning is an optimizing process that enables foraging specialization.
+Empirical studies show that learning allows predators to optimize the efficiency (e.g.
 search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@edwardsRoleExperienceDevelopment1994;@morseEffectExperienceHunting2000;@reidLearningHuntRole2010;@wilson-rankinLevelExperienceModulates2015].
 Such optimization may thus reinforce the use of the same tactic (i.e.
-specialization) if its success is constant through repeated attempts.
-*parler des couts d'apprendre de quoi d'autre*
-
-*expliquer comment ça optimise*
-*expliquer comment ça peut mener aussi à de la plasticité*
-*parler des coûts*
-*pt dire en haut que ça optimise directement et mène à la spécialisation*
-
-(apprentissage, search images, prior information)
-(par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)
-(parler des études qui ont montré que certains spécialistes étaient meilleurs, mais que c'était confondu par l'âge)
-[*références learning : phillips, Haage(minks = learn mène à plasticité), Tinker (théorique), Weimerskirch (only suggest memory)*] *[courbin = switch souvent possiblement avec learn, Zango = suggère, Woo = suggère, Estes = suggère.]*
-
-*Wilson-Rankin: Because resources and their distribution vary both in time and space, foraging strategies must allow for the detection and response to fluctuations in resource levels* (Ishii et Shimada : learning = plasticity)
+specialization) if its success is constant each time a prey is encountered.
+It may also be costly to attempt different hunting tactics when prey are scarce or highly unpredictable [@estesIndividualVariationPrey2003;@Mery.Burns2010].
+An alternative mechanism is that learning may offset the costs/risks of switching foraging tactics as individuals gain experience and information on their prey or their environment, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013].
+In this case, switching between foraging tactics would be advantageous when resources are variable, as behavioural flexibility is often key for survival in novel environments [reviewed in @Snell-Rood2013].
+If learning is the mechanism leading to individual specialization, then it wouldn't explain why field studies often find that foraging specialists and generalists have similar hunting success irrespective of their age [@Woo.etal2008].
+*(ne peut pas être séparé de l'interaction car c'ets ce qui drive l'apprentissage)*
 
@@
 Ici on veut souligner l'importance des deux mais rappeler comme d'habitude que c'est difficile à mesurer à travers le temps blabla.
-J'introduis ensuite le jeu vidéo]*
+J'introduis ensuite le jeu vidéo]* *vidfeogames offer a good alternative to lab studies because proche de wild = observational*
+*(idéee: par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)*
 
@@
 Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator hunting tactics.
-Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable.
+Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize when encounters with prey are more variable.
 Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal.
@@
 - * we now have metrics that enable the quantification of individual specialization (cleasby)*
+
+*Ideas* : integrate the hypotheses of Glaudas et al. ?????
+
+\newpage
+# Litterature cited {.unnumbered}
+
+<div id="refs"></div>

### 2022-08-11 manuscript/Chapter3-manuscript.Rmd
updt MS. updt validation. updt loo 02A1. updt bib

@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016].
-Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
-It is now well established that individual foraging specialization cannot be attributed exclusively to intrinsic factors such as sexual, morphological, or age-related differences [@bolnickEcologyIndividualsIncidence2003;@bolnickWhyIntraspecificTrait2011].
-A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, may instead act as the major drivers of individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016].
-For instance, predators species often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to learn how to effectively use them is essential to maintain foraging success.
-Yet, we have very limited knowledge on how predator foraging specialization develops through experience and interactions with prey, and the resulting ecological consequences of such among individual behavioural differences for predator-prey interactions.
+Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017] (FIND SOME TERRESTRIAL ANIMAL REFS).
+A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can be major drivers of such individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016].
+When hunting, predators often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
+expertise).
+While the development of hunting expertise may be essential to maintain foraging success, we have have limited evidence for its role in predator foraging specialization, and the ecological/fitness consequences of such among individual behavioural differences for predator-prey interactions.
 
-Learning how to hunt prey is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@heithausFeedingStrategiesTactics2018].
-Theory predicts that learning may promote foraging specialization via past experiences, extensive practice, as well as a limited ability to retain multiple complex hunting skills [@Tinker.etal2009;@Dukas2019].
-From this perspective, learning is an optimizing process that enables foraging specialization.
-Empirical studies show that learning allows predators to optimize the efficiency (e.g.
+The integration of individual behavioral variation into studies of predator-prey interactions has been championned for some time, and a series of empirical papers have revelealed important insights on its consequences for functional responses, habitat use, and prey choice.
+However, a recurring challenge impeding empirical studies of predator-prey behavioral interactions is the difficulty of collecting data simultaneously on both the predator and prey.
+We have recently demonstrated that using an online predator-prey videogame can help uncover subtle details about the mechanisms shaping these behavioral interactions [@FraserFranco].
+
+*ici, mettre le paragraphe sur la variation individuelle, et ensuite expliquer ce qu'on cherche à comprendre dans la littérature écologique comportementale*
+
+The development of foraging strategies is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@heithausFeedingStrategiesTactics2018].
+Theory predicts that foraging specialization may emerge via learning, limitations in memorizing multiple complex hunting skills, and expertise [@Tinker.etal2009;@Dukas2019].
+[Dukas @Dukas2019] defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
+This body of work suggests that the development of expertise is an optimizing process that promotes foraging specialization.
+Empirical studies show that expertise allows predators to optimize the efficiency (e.g.
 search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@edwardsRoleExperienceDevelopment1994;@morseEffectExperienceHunting2000;@reidLearningHuntRole2010;@wilson-rankinLevelExperienceModulates2015].
@@
 It may also be costly to attempt different hunting tactics when prey are scarce or highly unpredictable [@estesIndividualVariationPrey2003;@Mery.Burns2010].
-An alternative mechanism is that learning may offset the costs/risks of switching foraging tactics as individuals gain experience and information on their prey or their environment, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013].
-In this case, switching between foraging tactics would be advantageous when resources are variable, as behavioural flexibility is often key for survival in novel environments [reviewed in @Snell-Rood2013].
-If learning is the mechanism leading to individual specialization, then it wouldn't explain why field studies often find that foraging specialists and generalists have similar hunting success irrespective of their age [@Woo.etal2008].
-*(ne peut pas être séparé de l'interaction car c'ets ce qui drive l'apprentissage)*
+An alternative mechanism is that expertise may offset the costs/risks of switching foraging tactics as individuals gain experience and information on their prey or their environment, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013].
+In this case, switching between foraging tactics would be advantageous when resources are variable, as behavioural flexibility is often key for survival in novel environments [reviewed in @Snell-Rood2013] (FIND OTHER REFS TO SUPPORT THIS MAYBE DAN SOL?).
 
@@
 Ça amènerait bien l'autre paragraphe pour montrer que les interactions écologiques ont un rôle clé!!*
+
+*ou juste dire que pour comprendre le role de l'expertise, il faut s'attarder à l'étudier avec la specialisation et voir les consequences pour la fitness ou issue des interactions predateur proie.
+ca introduit mieux je crois.
+dire genre que une théorie prédit que spécialisation est avantage quand proies peu variable, et ensuite ça lie bien l'hypothèse de variabilité que je décris en bas*
 
@@
 
-(travailler ceci) An important question that remains unanswered is how can generalist and specialist individuals coexist within predator populations.
-If foraging and resource specialisation can help maintain community stability by promoting species coexistence [sources: bolnick, araujo, wolf, etc], it is crucial that we develop studies that integrate the causes and consequences of these two individual components.
-Several studies have shown that individual specialists can outperform.
-*[ici je crois que je vais changer un peu cela.
-C'est surtout des idées.
-Ici on veut souligner l'importance des deux mais rappeler comme d'habitude que c'est difficile à mesurer à travers le temps blabla.
-J'introduis ensuite le jeu vidéo]* *vidfeogames offer a good alternative to lab studies because proche de wild = observational*
+ *Difficile de mesurer à travers le temps blabla. J'introduis ensuite le jeu vidéo* *vidfeogames offer a good alternative to lab studies because proche de wild = observational*
 *(idéee: par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)*

### 2022-08-11 manuscript/Chapter3-manuscript.Rmd
move dump ideas to tests. update intro MS.

@@
 
-The integration of individual behavioral variation into studies of predator-prey interactions has been championned for some time, and a series of empirical papers have revelealed important insights on its consequences for functional responses, habitat use, and prey choice.
-However, a recurring challenge impeding empirical studies of predator-prey behavioral interactions is the difficulty of collecting data simultaneously on both the predator and prey.
-We have recently demonstrated that using an online predator-prey videogame can help uncover subtle details about the mechanisms shaping these behavioral interactions [@FraserFranco].
-
-*ici, mettre le paragraphe sur la variation individuelle, et ensuite expliquer ce qu'on cherche à comprendre dans la littérature écologique comportementale*
+The integration of individual behavioral variation into studies of predator-prey interactions has gained traction in recent years, with a series of empirical papers revealing important consequences for functional responses, habitat use, and prey choice (REFS).
+However, an important and recurring challenge impeding empirical studies of predator-prey behavioral interactions, at the individual level, is the need of collecting data simultaneously on both the predator and prey.
+We have recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can uncover subtle details on the mechanisms shaping these interactions [@FraserFranco.etal2022].
+For instance, we tested the classical locomotor crossover hypothesis championed by @Huey.Pianka1981, and found support of its predictions only for active hunters, which concords with a recent experiment involving assassin bugs [@Matsumura.Miyatake2022a].
+Thus, general ecological patterns can potentially be derived from these virtual systems and may help in advacing the current gaps in predator-prey research.
+Other examples of virtual ecological studies show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity with prey partners has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes [Santostefano et al.
+in prep].
+Because these systems generate large volumes of data on prey and predators simultaneously throughout their lifetime in the game, they offer the opportunity of uncovering how expertise and prey behavior shape individual predator foraging specialization and its potential fitness consequences.
 
@@
 
-*un autre truc que je pourrais parler est le fait que si on assume que les individus deviennent meilleurs avec l'expertise (Dukas), on voit pourtant dans les études marines que les individus de groupes d'âges variés performent souvent de manière similaire.
-Ça amènerait bien l'autre paragraphe pour montrer que les interactions écologiques ont un rôle clé!!*
-
 *ou juste dire que pour comprendre le role de l'expertise, il faut s'attarder à l'étudier avec la specialisation et voir les consequences pour la fitness ou issue des interactions predateur proie.
 ca introduit mieux je crois.
-dire genre que une théorie prédit que spécialisation est avantage quand proies peu variable, et ensuite ça lie bien l'hypothèse de variabilité que je décris en bas*
+dire genre que une théorie prédit que spécialisation est avantage quand proies peu variable, et ensuite ça lie bien l'hypothèse de variabilité que je décris en bas.
+faire ressortir qu'il n'y a pas de consencus.
+There is right now no concencus as to whether blabla, (examples)*
 
-A number of long-term studies observed that generalist and specialist individuals can achieve similar fitness [sources: à partir de Woo].
+Some long-term studies show that generalist and specialist individuals can achieve similar fitness [sources: à partir de Woo].
 An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc, Courbin, Chang].
@@
 
- *Difficile de mesurer à travers le temps blabla. J'introduis ensuite le jeu vidéo* *vidfeogames offer a good alternative to lab studies because proche de wild = observational*
-*(idéee: par contre, décomposer l'âge de l'expérience est difficile, et particulièrement chez des espèces sur le terrain puisque ça peut impliquer des techniques invasives)*
-
-Here, we collected individual behavioural data from players in *Dead by Daylight* to investigate how hunting experience and the behavioural variation in prey encountered shaped predator foraging specialization.
-This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial.
-First, we hypothesize that individual predator behaviour will change with hunting experience.
-If experience reduces the costs of switching between hunting tactics, then predators should become more flexible through time.
-Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time.
-Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator hunting tactics.
-Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize when encounters with prey are more variable.
-Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal.
+Here, we analyze individual behavioural data provided by a videogame company from players in *Dead by Daylight* to test how hunting expertise and prey behaviour shape predator foraging specialization.
+*Dead by Daylight* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
+The data grants a high degree of precision on the behavioural interaction as both the predator and the four prey were measured simultaneously in each trial.
+First, we investigate how predators developped their individual hunting expertise.
+We hypothesize that predators should differ in the development of their expertise because they encounter varying levels of difficulty with the prey that they hunt.
+Second, we test the hypothesis that individual variation in foraging behaviour will change with expertise.
+If expertise reduces the costs of switching between hunting tactics, we predict that individual predators should become more flexible with time.
+Alternatively, if expertise enables the refinement of the hunting tactics, then individuals may instead specialize.
+Third, we evaluate how predator foraging specialization interacts with variation in prey behaviour.
+Whether predators specialize or not with expertise may depend on the behaviour of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
+Lastly, if individuals differ in their degree of foraging specialization, then we expect that the success of specialists and generalists will be equal.
 Specialist hunters should fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.

### 2022-08-11 manuscript/Chapter3-manuscript.Rmd
updated introduction. V1 almost done.

@@
 
-Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@limaPuttingPredatorsBack2002;@schreiberCommunityEffectsPhenotypic2011;@pettorelliChapterTwoIndividual2015;@Michalko.Pekar2016].
-Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@estesIndividualVariationPrey2003;@tinkerFoodLimitationLeads2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017] (FIND SOME TERRESTRIAL ANIMAL REFS).
-A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can be major drivers of such individual foraging specialization [@araujoEcologicalCausesIndividual2011;@toscanoPersonalityForagingBehavior2016].
-When hunting, predators often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@estesIndividualVariationPrey2003;@Woo.etal2008;@courbinShorttermPreyField2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
+Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Lima2002;@schreiberCommunityEffectsPhenotypic2011;@Pettorelli.etal2015;@Michalko.Pekar2016].
+Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017] (FIND SOME TERRESTRIAL ANIMAL REFS).
+A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can be major drivers of such individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
+When hunting, predators often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
 expertise).
@@
 
-The development of foraging strategies is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@heithausFeedingStrategiesTactics2018].
+The development of foraging strategies is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
 Theory predicts that foraging specialization may emerge via learning, limitations in memorizing multiple complex hunting skills, and expertise [@Tinker.etal2009;@Dukas2019].
-[Dukas @Dukas2019] defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
+@Dukas2019 defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
 This body of work suggests that the development of expertise is an optimizing process that promotes foraging specialization.
 Empirical studies show that expertise allows predators to optimize the efficiency (e.g.
-search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@edwardsRoleExperienceDevelopment1994;@morseEffectExperienceHunting2000;@reidLearningHuntRole2010;@wilson-rankinLevelExperienceModulates2015].
+search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@Reid.etal2010;@Wilson-Rankin2015].
 Such optimization may thus reinforce the use of the same tactic (i.e.
 specialization) if its success is constant each time a prey is encountered.
-It may also be costly to attempt different hunting tactics when prey are scarce or highly unpredictable [@estesIndividualVariationPrey2003;@Mery.Burns2010].
+It may also be costly to attempt different hunting tactics when prey are scarce or highly unpredictable [@Estes.etal2003;@Mery.Burns2010].
 An alternative mechanism is that expertise may offset the costs/risks of switching foraging tactics as individuals gain experience and information on their prey or their environment, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013].
@@
 faire ressortir qu'il n'y a pas de consencus.
-There is right now no concencus as to whether blabla, (examples)*
-
-Some long-term studies show that generalist and specialist individuals can achieve similar fitness [sources: à partir de Woo].
+There is right now no concencus as to whether blabla, (examples)* Some long-term studies show that generalist and specialist individuals can achieve similar fitness [sources: à partir de Woo].
 An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc, Courbin, Chang].
@@
 *ce qu'il manque, c'est qu'on a aucune idée comment des différences individuelles de variabilité environnementale se traduisent par des différences de stratégies*
-
-sources générales sur heterogeneité[@Weimerskirch2007;@ceiaIndividualSpecializationForaging2015;@Phillips.etal2017;@Patrick.etal2021].
+sources générales sur heterogeneité[@Weimerskirch2007;@Ceia.Ramos2015;@Phillips.etal2017;@Patrick.etal2021].
 
@@
 
-# Squelette de l'intro
-
-- Paragraphe 1 : Importance of among-individual variation in foraging behaviour
-
-- Paragraphe 2 : Factors shaping individual variation in foraging behaviour - the role of experience
-  (sources Weimerskirch, 2005, 2007) (explain mechanisms). Explain how it may unravel why foraging specialists are often thought to be more succesful.
-
-- Paragraphe 3: (Linking prey variability to experience (woo et al.)) how trophic interactions are probably the main driver of learning and experience
-
-- Paragraphe 4 (système qu'on utilise) (jeux vidéo : paragraphe le + court possible)
-
-- Paragraphe 5 (objectifs et hypotèses)
-
-*Idéé* :
-- Est-ce que ça se pourrait que les proies déterminent si les prédateurs se spécialize avec l'expérience ou plutôt deviennent flexible?
-Dans ce cas, j'utiliserais pas la covariance mais le comportement des proies en effet fixe sur la variance?
-ou il faudrait que je change les covariances?
-
-*Ideas* : 
-- * we now have metrics that enable the quantification of individual specialization (cleasby)*
-
-*Ideas* : integrate the hypotheses of Glaudas et al. ?????
-
 \newpage

### 2022-08-15 manuscript/Chapter3-manuscript.Rmd
update intro and references. Intro almost done.

@@
 \newpage
-# Abstract {.unnumbered}
+# ABSTRACT {.unnumbered}
 
-Keywords: foraging behaviour, individual specialization, experience, learning, prey predictability, online videogames
+Keywords: foraging behavior, individual specialization, experience, learning, prey predictability, online videogames
 
 \newpage
-# Introduction {.unnumbered}
+# INTRODUCTION {.unnumbered}
 
-Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Lima2002;@schreiberCommunityEffectsPhenotypic2011;@Pettorelli.etal2015;@Michalko.Pekar2016].
-Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017] (FIND SOME TERRESTRIAL ANIMAL REFS).
+Individual variation in predator foraging behavior is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
+Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
 A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can be major drivers of such individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
-When hunting, predators often use hunting techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
+When they hunt, predators often use techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
 expertise).
-While the development of hunting expertise may be essential to maintain foraging success, we have have limited evidence for its role in predator foraging specialization, and the ecological/fitness consequences of such among individual behavioural differences for predator-prey interactions.
+While the development of hunting expertise may be essential to maintain foraging success, we have have limited evidence for its role in predator foraging specialization, and the ecological/fitness consequences of such among individual behavioral differences for predator-prey interactions.
 
-The integration of individual behavioral variation into studies of predator-prey interactions has gained traction in recent years, with a series of empirical papers revealing important consequences for functional responses, habitat use, and prey choice (REFS).
-However, an important and recurring challenge impeding empirical studies of predator-prey behavioral interactions, at the individual level, is the need of collecting data simultaneously on both the predator and prey.
-We have recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can uncover subtle details on the mechanisms shaping these interactions [@FraserFranco.etal2022].
+The integration of individual behavioral variation in the study of predator-prey interactions has gained traction in recent years, with empirical studies revealing important consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
+However, an important and recurring challenge impeding research on predator-prey behavioral interactions, at the individual level, is the need of collecting data simultaneously on both the predator and prey.
+We have recently demonstrated with behavioral data from an online predator-prey videogame that virtual systems can help in overcoming this challenge, and uncover subtle details on the mechanisms shaping these interactions [@FraserFranco.etal2022].
 For instance, we tested the classical locomotor crossover hypothesis championed by @Huey.Pianka1981, and found support of its predictions only for active hunters, which concords with a recent experiment involving assassin bugs [@Matsumura.Miyatake2022a].
-Thus, general ecological patterns can potentially be derived from these virtual systems and may help in advacing the current gaps in predator-prey research.
-Other examples of virtual ecological studies show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity with prey partners has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes [Santostefano et al.
-in prep].
-Because these systems generate large volumes of data on prey and predators simultaneously throughout their lifetime in the game, they offer the opportunity of uncovering how expertise and prey behavior shape individual predator foraging specialization and its potential fitness consequences.
+Thus, general ecological patterns can potentially be derived from these virtual systems and may help in advancing the current gaps in predator-prey research.
+Other examples of virtual ecological studies show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity with prey partners has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
+in prep).
+Because virtual systems generate large volumes of data on prey and predators simultaneously throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of expertise and prey behavior on individual predator foraging specialization, and its potential fitness consequences.
 
@@
 This body of work suggests that the development of expertise is an optimizing process that promotes foraging specialization.
-Empirical studies show that expertise allows predators to optimize the efficiency (e.g.
-search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@Reid.etal2010;@Wilson-Rankin2015].
+Empirical studies on human and non-human hunters show that expertise allows them to optimize the efficiency (e.g.
+search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@macdonaldCrossculturalComparisonLearning2007;@Reid.etal2010;@Wilson-Rankin2015].
 Such optimization may thus reinforce the use of the same tactic (i.e.
@@
 An alternative mechanism is that expertise may offset the costs/risks of switching foraging tactics as individuals gain experience and information on their prey or their environment, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013].
-In this case, switching between foraging tactics would be advantageous when resources are variable, as behavioural flexibility is often key for survival in novel environments [reviewed in @Snell-Rood2013] (FIND OTHER REFS TO SUPPORT THIS MAYBE DAN SOL?).
+In this case, switching between foraging tactics would be advantageous when resources are variable, as behavioral flexibility is often key for survival in novel environments [reviewed in @Snell-Rood2013].
 
-*ou juste dire que pour comprendre le role de l'expertise, il faut s'attarder à l'étudier avec la specialisation et voir les consequences pour la fitness ou issue des interactions predateur proie.
-ca introduit mieux je crois.
-dire genre que une théorie prédit que spécialisation est avantage quand proies peu variable, et ensuite ça lie bien l'hypothèse de variabilité que je décris en bas.
-faire ressortir qu'il n'y a pas de consencus.
-There is right now no concencus as to whether blabla, (examples)* Some long-term studies show that generalist and specialist individuals can achieve similar fitness [sources: à partir de Woo].
-An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behaviour) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc, Courbin, Chang].
+There currently is a lack of consensus on whether specializing or flexible foraging is best in nature along with the ecological contexts favoring one strategy over the other.
+Studies investigating the fitness benefits of specialization show contrasting results; some report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
+ici, essayer de poser la question de genre cela nous fait se demander pourquoi se spécialiser??
+um peu comme woo a fait.
+ça va lier au fait ensuite que je parle des proies
+
+In predator-prey systems, some clues indicate that it may be intrinsically linked to the variability in prey that predators encounter throughout their lifetime. For instance,
+
+An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behavior) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc, Courbin, Chang].
 The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns.
@@
 [revoir ceia et ramos pour les sources]
-*ce qu'il manque, c'est qu'on a aucune idée comment des différences individuelles de variabilité environnementale se traduisent par des différences de stratégies*
+
+the capacity of ajusting to prey behavior may be key in a predator's success and survival
 sources générales sur heterogeneité[@Weimerskirch2007;@Ceia.Ramos2015;@Phillips.etal2017;@Patrick.etal2021].
 
-Here, we analyze individual behavioural data provided by a videogame company from players in *Dead by Daylight* to test how hunting expertise and prey behaviour shape predator foraging specialization.
+In this study, we analyze individual behavioral data from players in *Dead by Daylight* to test how hunting expertise and prey behavior shape predator foraging specialization.
 *Dead by Daylight* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
-The data grants a high degree of precision on the behavioural interaction as both the predator and the four prey were measured simultaneously in each trial.
-First, we investigate how predators developped their individual hunting expertise.
+The data grants a high degree of precision on the behavioral interaction as both the predator and the four prey were measured simultaneously in each trial.
+First, we investigate how predators developed their individual hunting expertise.
 We hypothesize that predators should differ in the development of their expertise because they encounter varying levels of difficulty with the prey that they hunt.
-Second, we test the hypothesis that individual variation in foraging behaviour will change with expertise.
+Second, we test the hypothesis that individual variation in foraging behavior will change with expertise.
 If expertise reduces the costs of switching between hunting tactics, we predict that individual predators should become more flexible with time.
 Alternatively, if expertise enables the refinement of the hunting tactics, then individuals may instead specialize.
-Third, we evaluate how predator foraging specialization interacts with variation in prey behaviour.
-Whether predators specialize or not with expertise may depend on the behaviour of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
+Third, we evaluate how predator foraging specialization interacts with variation in prey behavior.
+Whether predators specialize or not with expertise may depend on the behavior of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
 Lastly, if individuals differ in their degree of foraging specialization, then we expect that the success of specialists and generalists will be equal.
@@
 \newpage
-# Litterature cited {.unnumbered}
+# MATERIALS AND METHODS {.unnumbered}
+
+\newpage
+# RESULTS {.unnumbered}
+
+## The role of experience in the development of expertise
+
+\newpage
+# LITTERATURE CITED {.unnumbered}
 

### 2022-08-15 manuscript/Chapter3-manuscript.Rmd
update sentence in intro

@@
 
-There currently is a lack of consensus on whether specializing or flexible foraging is best in nature along with the ecological contexts favoring one strategy over the other.
-Studies investigating the fitness benefits of specialization show contrasting results; some report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
+There currently is a lack of consensus on the fitness consequences of specializing vs flexible foraging along with the ecological contexts favoring one strategy over the other.
+Studies investigating the benefits of specialization show contrasting results; some report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
 ici, essayer de poser la question de genre cela nous fait se demander pourquoi se spécialiser??

### 2022-08-16 manuscript/Chapter3-manuscript.Rmd
first draft of intro finished

@@
 expertise).
-While the development of hunting expertise may be essential to maintain foraging success, we have have limited evidence for its role in predator foraging specialization, and the ecological/fitness consequences of such among individual behavioral differences for predator-prey interactions.
+While the development of hunting expertise may be essential to maintain foraging success, we have have limited evidence for its role in predator foraging specialization, and the ecological/fitness consequences of such among individual behavioral differences for predator-prey interactions [@Dukas2019].
 
@@
 For instance, we tested the classical locomotor crossover hypothesis championed by @Huey.Pianka1981, and found support of its predictions only for active hunters, which concords with a recent experiment involving assassin bugs [@Matsumura.Miyatake2022a].
-Thus, general ecological patterns can potentially be derived from these virtual systems and may help in advancing the current gaps in predator-prey research.
-Other examples of virtual ecological studies show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity with prey partners has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
+Thus, virtual systems may be useful in identifying general ecological patterns, which may in turn help in advancing the current gaps in predator-prey research.
+Other examples of virtual ecological studies show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
 in prep).
@@
 This body of work suggests that the development of expertise is an optimizing process that promotes foraging specialization.
-Empirical studies on human and non-human hunters show that expertise allows them to optimize the efficiency (e.g.
+Empirical studies on human and non-human hunters show that expertise optimizes the efficiency (e.g.
 search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@macdonaldCrossculturalComparisonLearning2007;@Reid.etal2010;@Wilson-Rankin2015].
@@
 In this case, switching between foraging tactics would be advantageous when resources are variable, as behavioral flexibility is often key for survival in novel environments [reviewed in @Snell-Rood2013].
+*revoir cette phrase ça ressemble trop à l'autre.
+plutôt parler des processus cognitifs qui modulent cela*
 
-There currently is a lack of consensus on the fitness consequences of specializing vs flexible foraging along with the ecological contexts favoring one strategy over the other.
-Studies investigating the benefits of specialization show contrasting results; some report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
-ici, essayer de poser la question de genre cela nous fait se demander pourquoi se spécialiser??
-um peu comme woo a fait.
-ça va lier au fait ensuite que je parle des proies
-
-In predator-prey systems, some clues indicate that it may be intrinsically linked to the variability in prey that predators encounter throughout their lifetime. For instance,
-
-An emerging explanation is that temporal fluctuations in the predictability of resources (abundance, availability, behavior) may favor one or the other strategy depending on time scales [sources : Woo, Phillips, Ceia, etc, Courbin, Chang].
-The resource-predictability hypothesis advances that when resources are predictable, particularly on short time-scales, individual specialists should benefit from higher fitness returns.
-The rationale is that individuals should have higher prey delivery rates when they repeatedly employ the same foraging technique, as it is easier to assess prey predictability over shorter time-scales.
-In contrast, individual generalists should be advantaged over longer time scales, as resource parameters are expected to fluctuate.
-[revoir ceia et ramos pour les sources]
-
-the capacity of ajusting to prey behavior may be key in a predator's success and survival
-sources générales sur heterogeneité[@Weimerskirch2007;@Ceia.Ramos2015;@Phillips.etal2017;@Patrick.etal2021].
+There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging.
+Importantly, we have little information on the ecological contexts - except for competition - that favors one strategy over the other.
+This is reflected in the literature showing contrasting results in the links between specialization and fitness.
+For instance, some studies report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
+While identifying the relevant contexts mediating these fitness benefits is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey (e.g.
+abundance, availability, behavior) encounters throughout a predator's lifetime may be a key factor mediating the benefits of specializing [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
+The resource-predictability hypothesis advances that when resources are predictable, individual specialists should have higher delivery rates by reducing the energy and time required to search for and handle prey.
+In contrast, individual generalists should be advantaged when resources fluctuate, as fine adjustments to prey are key for a predator's success and survival.
 

### 2022-08-16 manuscript/Chapter3-manuscript.Rmd
started the methods section

@@
     reference_docx: Chapter3-styles.docx
+    fig_caption: yes
 bibliography: references.bib
@@
 ---
+
+```{r setup, include = FALSE}
+
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+
+library(data.table)
+library(brms)
+
+```
 
@@
 
+## Study system
+
+## Data collection
+
+## Behaviors
+
+## Statistical analyses
+
+### Software and computer components
+
+### Effect of experience on hunting success
+
+### Foraging tactics at each level of experience
+
 \newpage
@@
 
-## The role of experience in the development of expertise
+## Effect of experience on hunting success
+
+Contrary to our predictions, individual predators did not differ in the development of their expertise, as the best model was the one with a general population trend with varying intercepts only (Table x.).
+Moreover, we did not detect a relationship between experience (i.e.
+the cumulative amount of matches played) and hunting success, such that players did not optimize their success with increasing experience as we expected (Figure 1 A).
+However, predators did differ in their average hunting success across the study period (Figure 1 B).
+
+```{r out.width = "100%", fig.cap = "**Figure 1.** Results from the Bayesian generalized additive mixed model.
+(A) Fitted (solid) line displaying the posterior predicted values relating the predators' hunting success to their cumulative experience.
+Here, we transformed the hunting success and cumulative experience back to their original scale (i.e.
+the amount of prey captured and the number of matches played respectively).
+The band around the solid line represents the 95% credible intervals.
+(B) The estimated posterior predicted mean hunting success of each predator player.
+We display the hunting success back-transformed to its original scale."}
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure1.png"))
+```
 

### 2022-08-17 code/05_code_figures/05_figure1.R
update figure 1 with glmm

@@ -14,61 +14,62 @@
 
 # Load librairies and model ------------------------------------------------
 
-library(brms)
-library(data.table)
-library(ggplot2)
-
-mod1 <- readRDS("./outputs/02_outputs_models/02A1_GAMM.rds")
+ library(brms)
+ library(data.table)
+ library(ggplot2)
+ 
+ mod <- readRDS("./outputs/02_outputs_models/02A3_GLMM.rds")
 
 
 
 # Load the data ------------------------------------------------------------
 
-data <- fread("./data/FraserFrancoetalXXXX-data.csv",
-              select = c("predator_id",
-                         "pred_game_duration",
-                         "pred_speed",
-                         "prey_avg_speed",
-                         "cumul_xp_killer",
-                         "total_xp_killer",
-                         "hunting_success"))
-
-data <- unique(data)
-
+ data <- fread("./data/FraserFrancoetalXXXX-data.csv",
+               select = c("predator_id",
+                          "pred_game_duration",
+                          "pred_speed",
+                          "prey_avg_speed",
+                          "cumul_xp_killer",
+                          "total_xp_killer",
+                          "hunting_success"))
+ 
+ data <- unique(data)
+ data[, predator_id := as.factor(predator_id)]
 
 
 # Post processing preparations for custom family ---------------------------
 
-expose_functions(mod1, vectorize = TRUE)
-
-# Define the log likelihood function
-log_lik_beta_binomial2 <- function(i, prep) {
-  mu <- brms::get_dpar(prep, "mu", i = i)
-  phi <- brms::get_dpar(prep, "phi", i = i)
-  trials <- prep$data$vint1[i]
-  y <- prep$data$Y[i]
-  beta_binomial2_lpmf(y, mu, phi, trials)
-}
-
-# Define function for posterior_predict
-posterior_predict_beta_binomial2 <- function(i, prep, ...) {
-  mu <- brms::get_dpar(prep, "mu", i = i)
-  phi <- brms::get_dpar(prep, "phi", i = i)
-  trials <- prep$data$vint1[i]
-  beta_binomial2_rng(mu, phi, trials)
-}
-
-# Define function for posterior_epred
-posterior_epred_beta_binomial2 <- function(prep) {
-  mu <- brms::get_dpar(prep, "mu")
-  trials <- prep$data$vint1
[…]

### 2022-08-18 manuscript/Chapter3-manuscript.Rmd
update MS based on changes in fig1
updated fig1. added fig2. update with MS

@@
 
-```{r out.width = "100%", fig.cap = "**Figure 1.** Results from the Bayesian generalized additive mixed model.
+```{r out.width = "100%", fig.cap = "**Figure 1.** Results from the Bayesian generalized linear mixed model.
 (A) Fitted (solid) line displaying the posterior predicted values relating the predators' hunting success to their cumulative experience.
@@
 
+blablabla figure 2
+
+```{r out.width = "100%", fig.cap = "**Figure 2.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience.
+(A) Coefficient of variation for the among individual differences in average behavior.
+(B) Coefficient fo variation for the among individual differences in within individual variance (i.e.
+specialization)."}
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure2.png"))
+```
+
 \newpage

### 2022-08-18 code/05_code_figures/05_figure1.R

@@ -12,7 +12,7 @@
 
 
 
-# Load librairies and model ------------------------------------------------
+# Load libraries and model -------------------------------------------------
 
  library(brms)
  library(data.table)
@@ -241,7 +241,7 @@
             legend.position = "top",
             legend.key = element_rect(fill = "transparent"),
             legend.title = element_text(size = 15),
-            legend.text = element_text(size = 12))
+            legend.text = element_text(size = 14))
 
 # ==========================================================================
 # ==========================================================================

### 2022-08-18 code/05_code_figures/05_figure2.R

@@ -1,0 +1,183 @@
+# =======================================================================
+
+#                   Plot the coefficients of variation
+
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 1. Import the libraries and data
+# =======================================================================
+
+ # Libraries
+ library(data.table)
+ library(ggplot2)
+ library(ggpubr)
+
+ # CV table
+ path <- "./outputs/04_outputs_model-processing"
+ tab <- readRDS(file.path(path, "04_CV-table.rds"))
+ 
+ # Rename the XP variable
+ tab[xp_level == "novice", xp_level := "Below 150"]
+ tab[xp_level == "interm", xp_level := "Between 150 and 300"]
+ tab[xp_level == "advanced", xp_level := "Above 300"]
+ 
+ # Rename the behaviour names
+ tab[variable == "Zspeed", variable := "Predator speed"]
+ tab[variable == "Zpreyspeed", variable := "Prey speed"]
+
+ # Reorder factors
+ tab[, xp_level := factor(xp_level, levels = c("Below 150",
+                                               "Between 150 and 300",
+                                               "Above 300"))]
+ 
+ # Encode Parameter and variable as factor
+ tab[, ":=" (Parameter = as.factor(Parameter),
+             variable = as.factor(variable))]
+ 
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 2. Prepare the figure options
+# =======================================================================
+
+
+# Set custom theme -----------------------------------------------------
+
+ custom_theme <- theme(# axis values size
+                       axis.text.x = element_text(face = "plain", 
+                                                  size = 15,
+                                                  color = "black"),
+                       axis.text.y = element_text(face = "plain", 
+                                                  size = 15,
+                                                  color = "black"),
+                       # axis ticks lenght
+                       axis.ticks.length = unit(.15, "cm"),
+                       # axis ticks width
+                       axis.ticks = element_line(size = 0.90, 
+                                                 color = "black"),
+                       # axis titles size
+                       axis.title = element_text(size = 17, 
+                                                 face = "plain",
+                                                 color = "black"),
+                       axis.line = element_line(size = 0.95,
+                                                color = "black"),
[…]

### 2022-08-19 code/05_code_figures/05_figure2.R
update fig2. create fig4

@@ -106,7 +106,7 @@
      scale_y_continuous(breaks = seq(0.1, 0.4, 0.1),
                         limits = c(0.02, 0.48)) +
 
-     ylab("CV (mean)\n") +
+     ylab("Coefficient of variation (mean)\n") +
      xlab("\nBehavior") +
      
      custom_theme +
@@ -137,7 +137,7 @@
      scale_y_continuous(breaks = seq(0.1, 0.4, 0.1),
                         limits = c(0.02, 0.48)) +
 
-     ylab("CV (sigma)\n") +
+     ylab("Coefficient of variation (IIV)\n") +
      xlab("\nBehavior") +
      
      custom_theme +
@@ -171,13 +171,3 @@
 
 # =======================================================================
 # =======================================================================
-
-
-
-
-
-
-
-
-
-

### 2022-08-19 code/05_code_figures/05_figure4.R
update fig4 and added R file

@@ -1,0 +1,365 @@
+# =======================================================================
+
+#                Plot the correlations between variables
+
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 1. Import data and libraries
+# =======================================================================
+
+
+# Load libraries and model data -----------------------------------------
+
+ # Libraries
+ library(brms)
+ library(data.table)
+ library(ggplot2)
+ library(ggpubr)
+ 
+ # Model
+ fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
+ 
+ # ID table
+ id_tab <- readRDS("./tests/04_id-draws.rds")
+ 
+
+
+# Load raw data ---------------------------------------------------------
+
+ # Data
+ data <- fread("./data/FraserFrancoetalXXXX-data.csv",
+               select = c("predator_id",
+                          "pred_game_duration",
+                          "pred_speed",
+                          "prey_avg_speed",
+                          "cumul_xp_killer",
+                          "total_xp_killer",
+                          "hunting_success"))
+ 
+ data <- unique(data)
+
+ # Predator id as factor
+ data[, predator_id := as.factor(predator_id)]
+
+ # Calculate total xp
+ data[total_xp_killer < 150,
+      xp_level := "novice"]
+ 
+ data[total_xp_killer %between% c(150, 299),
+      xp_level := "interm"]
+ 
+ data[total_xp_killer > 300,
+      xp_level := "advanced"]
+
+ # Encode the variable as a factor
+ data[, xp_level := as.factor(xp_level)]
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 3. Custom theme for plots
+# =======================================================================
+
+ # Custom plot theme
+ custom_theme <- theme(# axis values size
+                       axis.text.x = element_text(face = "plain", 
+                                                  size = 15,
+                                                  color = "black"),
+                       axis.text.y = element_text(face = "plain", 
+                                                  size = 15,
+                                                  color = "black"),
+                       # axis ticks lenght
+                       axis.ticks.length = unit(.15, "cm"),
[…]

### 2022-08-19 code/04_code_model-processing/04_id-draws.R
added id draws table .rds + .R files

@@ -1,0 +1,161 @@
+# =======================================================================
+
+#              Prepare a table to process behavioral types
+
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 1. Prepare the script
+# =======================================================================
+
+# load libraries
+library(brms)
+library(data.table)
+
+# import model
+fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
+
+# Load data
+data <- fread("./data/FraserFrancoetalXXXX-data.csv",
+              select = c("predator_id",
+                         "pred_game_duration",
+                         "pred_speed",
+                         "prey_avg_speed",
+                         "cumul_xp_killer",
+                         "total_xp_killer",
+                         "hunting_success"))
+
+data <- unique(data)
+
+# Predator id as factor
+data[, predator_id := as.factor(predator_id)]
+
+
+data[cumul_xp_killer < 150,
+     xp_level := "novice"]
+
+data[cumul_xp_killer %between% c(150, 299),
+     xp_level := "intermediate"]
+
+data[cumul_xp_killer >= 300,
+     xp_level := "advanced"]
+
+# Encode the variable as a factor
+data[, xp_level := as.factor(xp_level)]
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 2. Extract the posterior draws of each player
+# =======================================================================
+
+draws <- data.table(
+    as_draws_df(
+        fit,
+        variable = c("^r_predator_id__"),
+        regex = TRUE)
+)
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 3. Reshape the table and save
+# =======================================================================
+
+
+
+# Long format -----------------------------------------------------------
+
+draws <- melt(draws,
+              measure = patterns("^r_predator_id"),
+              variable.name = "ID_raw")
+
+draws[, c(1:3) := NULL]
+
+
+
+# Add variables ---------------------------------------------------------
+
+# Add xp level
+draws[, xp_level := ifelse(ID_raw %like% "novice", "novice", "unknown")]
+draws[ID_raw %like% "interm", xp_level := "interm"]
+draws[ID_raw %like% "advanced", xp_level := "advanced"]
+
[…]

### 2022-08-19 code/05_code_figures/05_figure4.R
update figure 4

@@ -271,7 +271,7 @@ plot3 <- ggplot() +
     scale_x_continuous(breaks = seq(-2, 2, 2),
                        limits = c(-3.5, 2.5)) +
     
-    ylab("Predator speed (IIV)\n") +
+    ylab("Predator speed (mean)\n") +
     xlab("\nHunting success (mean)") +
     labs(title = "Advanced \nCorrelation = -0.152 (-0.304, 0.011)") +
     

### 2022-08-19 manuscript/Chapter3-manuscript.Rmd
added figure 3 to MS. might delete later
update MS with correct figure 4

@@
 
+blablabla figure 3
+
+```{r out.width = "100%", fig.cap = "**Figure 3.** Title (A) Novice. (B) Advanced."}
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure3.png"))
+```
+
+blablabla figure 4
+
+```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novice. (C) and (D) Advanced."}
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure4.png"))
+```
+
 \newpage

### 2022-08-19 manuscript/Chapter3-manuscript.Rmd
update refs and introduction MS

@@
 specialization) if its success is constant each time a prey is encountered.
-It may also be costly to attempt different hunting tactics when prey are scarce or highly unpredictable [@Estes.etal2003;@Mery.Burns2010].
+It may also be costly to attempt different hunting tactics by trial and error when prey are scarce or highly unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
 An alternative mechanism is that expertise may offset the costs/risks of switching foraging tactics as individuals gain experience and information on their prey or their environment, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013].
-In this case, switching between foraging tactics would be advantageous when resources are variable, as behavioral flexibility is often key for survival in novel environments [reviewed in @Snell-Rood2013].
-*revoir cette phrase ça ressemble trop à l'autre.
-plutôt parler des processus cognitifs qui modulent cela*
+To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, followed by higher performance at later stages of development [reviewed in @Snell-Rood2013].
 
@@
 For instance, some studies report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
-While identifying the relevant contexts mediating these fitness benefits is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey (e.g.
-abundance, availability, behavior) encounters throughout a predator's lifetime may be a key factor mediating the benefits of specializing [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
+While quantifying the fitness consequences of specialization is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey (e.g.
+abundance, availability, behavior) encounters throughout a predator's lifetime may be a key factor [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
 The resource-predictability hypothesis advances that when resources are predictable, individual specialists should have higher delivery rates by reducing the energy and time required to search for and handle prey.
-In contrast, individual generalists should be advantaged when resources fluctuate, as fine adjustments to prey are key for a predator's success and survival.
+In contrast, individual generalists should be advantaged when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
 

### 2022-09-19 manuscript/Chapter3-manuscript.Rmd
added paragraph describind study system. 1st draft

@@
 There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging.
-Importantly, we have little information on the ecological contexts - except for competition - that favors one strategy over the other.
+Importantly, we have little information on the ecological contexts - except for competition - that favor one strategy over the other.
 This is reflected in the literature showing contrasting results in the links between specialization and fitness.
 For instance, some studies report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
-While quantifying the fitness consequences of specialization is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey (e.g.
-abundance, availability, behavior) encounters throughout a predator's lifetime may be a key factor [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
+While quantifying the fitness consequences of specialization is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
 The resource-predictability hypothesis advances that when resources are predictable, individual specialists should have higher delivery rates by reducing the energy and time required to search for and handle prey.
 In contrast, individual generalists should be advantaged when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
+This hypothesis has however not been tested in systems where behavioral interactions are simultaneously monitored between individuals.
 
@@
 Whether predators specialize or not with expertise may depend on the behavior of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
-Lastly, if individuals differ in their degree of foraging specialization, then we expect that the success of specialists and generalists will be equal.
-Specialist hunters should fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
+Lastly, if individuals differ in their degree of foraging specialization, then we expect specialist hunters to fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
 
@@
 ## Study system
+
+*Dead by Daylight* is a survival horror asymmetric multiplayer online game developed by the videogame company Behavior Interactive Inc.
+In this game, players get to chose if they wish to play has a predator or a prey.
+The objective of the predator player is to search, stalk, and hunt the four prey players across a virtual environment.
+The objective of the four prey players is to forage for resources in the form of generators that once activated, will enable them to escape through an exit door and win the match.
+Each player, predator or prey, can chose an avatar with abilities that encourage specific play styles (e.g.
+bolder vs cautious prey, or ambush vs roaming predator).
+During our study period, the game offered X playable predator avatars, and X prey avatars.
+The virtual environment where matches take place is composed of fixed and procedurally generated items (e.g.
+vegetation, mazes, buildings) that constitute its structure.
+Some of these environments are larger than others, with varying levels or buildings.
+However, we have previously shown that they generally do not influence the behavior nor hunting success of the predator, which is probably due to a feature where predators have visual cues on the generators [@FraserFranco.etal2022].
+
+Game objectives and what prey and predators can do...
 

### 2022-09-22 manuscript/Chapter3-manuscript.Rmd
update methods

@@
 
-*Dead by Daylight* is a survival horror asymmetric multiplayer online game developed by the videogame company Behavior Interactive Inc.
+*Dead by Daylight* is a survival horror asymmetric multiplayer online game developed by Behavior Interactive Inc.
 In this game, players get to chose if they wish to play has a predator or a prey.
 The objective of the predator player is to search, stalk, and hunt the four prey players across a virtual environment.
-The objective of the four prey players is to forage for resources in the form of generators that once activated, will enable them to escape through an exit door and win the match.
+The objective of the four prey players is to forage for resources in the form of generators that once activated, will enable them to escape through one of two exit doors and win the match.
 Each player, predator or prey, can chose an avatar with abilities that encourage specific play styles (e.g.
 bolder vs cautious prey, or ambush vs roaming predator).
-During our study period, the game offered X playable predator avatars, and X prey avatars.
+During our study period, the game offered 23 playable predator avatars.
 The virtual environment where matches take place is composed of fixed and procedurally generated items (e.g.
@@
 However, we have previously shown that they generally do not influence the behavior nor hunting success of the predator, which is probably due to a feature where predators have visual cues on the generators [@FraserFranco.etal2022].
+There were 35 virtual game environments available for play during our study period.
 

### 2022-09-23 manuscript/Chapter3-manuscript.Rmd
update methods MS

@@
 library(brms)
+
+```
+
+```{r}
+
+path <- file.path(here::here(), "data")
+dat <- fread(file.path(path, "FraserFrancoetalXXXX-data.csv"),
+             select = c("match_encode_id", "game_mode",
+                        "realm_id", "environment_id", "predator_avatar_id",
+                        "predator_id", "pred_game_duration",
+                        "total_xp_killer", "cumul_xp_killer", "hunting_success",
+                        "pred_speed", "prey_avg_speed"))
+
+dat <- unique(dat)
+dat[, c(1:6) := lapply(.SD, function (x) as.factor(x)), .SDcols = c(1:6)]
 
@@
 
-In this study, we analyze individual behavioral data from players in *Dead by Daylight* to test how hunting expertise and prey behavior shape predator foraging specialization.
-*Dead by Daylight* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
+In this study, we analyze individual behavioral data from players in *Dead by Daylight* (*DBD*) to test how hunting expertise and prey behavior shape predator foraging specialization.
+*DBD* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
 The data grants a high degree of precision on the behavioral interaction as both the predator and the four prey were measured simultaneously in each trial.
@@
 
-*Dead by Daylight* is a survival horror asymmetric multiplayer online game developed by Behavior Interactive Inc.
+*DBD* is a survival horror asymmetric multiplayer online game developed by Behavior Interactive Inc.
 In this game, players get to chose if they wish to play has a predator or a prey.
 The objective of the predator player is to search, stalk, and hunt the four prey players across a virtual environment.
-The objective of the four prey players is to forage for resources in the form of generators that once activated, will enable them to escape through one of two exit doors and win the match.
+The objective of the four prey players is to forage for resources in the form of generators that once activated, will enable them to escape through one of two exit doors.
+A match ends when the predator kills all the prey available (i.e.
+that haven't escaped), or when the last prey left escapes the virtual environment.
 Each player, predator or prey, can chose an avatar with abilities that encourage specific play styles (e.g.
@@
 Some of these environments are larger than others, with varying levels or buildings.
-However, we have previously shown that they generally do not influence the behavior nor hunting success of the predator, which is probably due to a feature where predators have visual cues on the generators [@FraserFranco.etal2022].
+However, we have previously shown that they generally do not influence the behavior nor hunting success of the predator, which is probably due to a game feature enabling predators to have visual cues on the generators [@FraserFranco.etal2022].
 There were 35 virtual game environments available for play during our study period.
 
-Game objectives and what prey and predators can do...
+Individual predators in *DBD* display variation in the hunting strategies that they use.
+Some specialize at hunting at high speeds and covering space in the environment, while others prefer to stalk and ambush their prey [@FraserFranco.etal2022].
+They also display flexibility in the use of these tactics by switching between them across matches.
+The expression of these tactics and their success is highly dependent on the behavior of the prey group.
+The prey need to forage for resources while maintaining a high level of attention on the predator cues to avoid being detected and chased.
+Some prey contribute to the group's success by healing or helping others escape the predator, while other self-centered individuals play alone and attempt to escape by themselves [@Cere.etal2021].
+Predators must be wary of how the prey behave to chose the right way to capture them.
+Thus, *DBD* simulates a highly dynamic system where both predators and prey must constantly adapt to each other to be successful.
 
 ## Data collection
+
+We were provided with raw datasets from the videogame company that spanned a period of 6 months of matches recorded for each player.
+
+# (mean = `r toString(format(round(mean(data$space_covered_rate, na.rm = TRUE), digits = 2) (pour écrire dans le texte)
 

### 2022-09-23 code/02_code_models/02A1_GAMM.R
update GAMM files

@@ -35,6 +35,7 @@ folder <- file.path("/home", "maxime11", "projects", "def-monti",
 # Load data on compute canada
 data <- fread(file.path(folder, "FraserFrancoetalXXXX-data.csv"),
               select = c("predator_id",
+                         "pred_game_mode",
                          "hunting_success",
                          "pred_game_duration",
                          "pred_speed",
@@ -49,6 +50,7 @@ data <- fread(file.path(folder, "FraserFrancoetalXXXX-data.csv"),
 #                         "cumul_xp_killer"))
 
 data <- unique(data)
+data <- data[pred_game_mode == "Online"]
 
 # Predator id as factor
 data[, predator_id := as.factor(predator_id)]
@@ -63,7 +65,7 @@ standardize <- function (x) {(x - mean(x, na.rm = TRUE)) /
 data[, c("Zgame_duration",
          "Zspeed",
          "Zcumul_xp") := lapply(.SD, standardize), 
-       .SDcols = c(3:5)]
+       .SDcols = c(4:6)]
 
 # ==========================================================================
 # ==========================================================================

### 2022-09-23 code/02_code_models/02A2_GAMM.R

@@ -35,6 +35,7 @@ folder <- file.path("/home", "maxime11", "projects", "def-monti",
 # Load data
 data <- fread(file.path(folder, "FraserFrancoetalXXXX-data.csv"),
               select = c("predator_id",
+                         "pred_game_mode",
                          "hunting_success",
                          "pred_game_duration",
                          "pred_speed",
@@ -50,6 +51,7 @@ data <- fread(file.path(folder, "FraserFrancoetalXXXX-data.csv"),
 #                         "hunting_success"))
 
 data <- unique(data)
+data <- data[pred_game_mode == "Online"]
 
 # Predator id as factor
 data[, predator_id := as.factor(predator_id)]
@@ -64,7 +66,7 @@ standardize <- function (x) {(x - mean(x, na.rm = TRUE)) /
 data[, c("Zgame_duration",
          "Zspeed",
          "Zcumul_xp") := lapply(.SD, standardize), 
-       .SDcols = c(3:5)]
+       .SDcols = c(4:6)]
 
 # ==========================================================================
 # ==========================================================================

### 2022-09-23 jobs_slurm/02A1_GAMM.sh

@@ -3,7 +3,7 @@
 #SBATCH --nodes=1
 #SBATCH --cpus-per-task=48
 #SBATCH --mem=32000M
-#SBATCH --time=00-06:30
+#SBATCH --time=00-08:30
 #SBATCH --mail-user=fraser_franco.maxime@courrier.uqam.ca
 #SBATCH --mail-type=ALL
 

### 2022-09-23 manuscript/Chapter3-manuscript.Rmd
update methods MS

@@
 dat <- fread(file.path(path, "FraserFrancoetalXXXX-data.csv"),
-             select = c("match_encode_id", "game_mode",
+             select = c("pred_timestamp", "match_encode_id", "pred_game_mode",
                         "realm_id", "environment_id", "predator_avatar_id",
@@
 dat <- unique(dat)
-dat[, c(1:6) := lapply(.SD, function (x) as.factor(x)), .SDcols = c(1:6)]
+dat <- dat[pred_game_mode == "Online"]
+dat[, c(2:7) := lapply(.SD, function (x) as.factor(x)), .SDcols = c(2:7)]
+
+# To have a date column
+dat[, date := as.POSIXct(sub(" .*", "", pred_timestamp))]
 
@@
 
-We were provided with raw datasets from the videogame company that spanned a period of 6 months of matches recorded for each player.
+We were provided raw data by the videogame company that spanned a period of 6 months of gameplay recorded for every player.
+The first recorded match was played on `r toString(format(min(dat$date)))`, and the last one on `r toString(format(max(dat$date)))`.
+We applied cleaning and filtering procedures on the raw data to produce a synthetic dataset for our analyses.
+The data that we analyzed were for matches where players did not know each other.
+We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero.
+Moreover, we used our knowledge of the game to delete any matches where players were potentially hacking, or not playing has the game is supposed to be played.
+These matches were not considered as player experience.
 
-# (mean = `r toString(format(round(mean(data$space_covered_rate, na.rm = TRUE), digits = 2) (pour écrire dans le texte)
+After the cleaning and filtering procedures, our synthetic dataset consists of a population of `r toString(format(length(unique(dat$predator_id))))` predator players who played a total of `r toString(format(length(unique(dat$match_encode_id))))` matches.
+All the matches we analyzed lasted between `r toString(format(round(min(dat$pred_game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$pred_game_duration / 60))), digits = 2)` minutes (mean = `r toString(format(round(mean(dat$pred_game_duration / 60))), digits = 2)`).
+For every match, we report the predator player's anonymous ID, its avatar, the game environment, the predator player's experience along with its speed, and the average speed of the group of prey it encountered.
 
-## Behaviors
+## Variables
 

### 2022-09-29 manuscript/Chapter3-manuscript.Rmd
update MS and new gam01A1 output

@@
 We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero.
-Moreover, we used our knowledge of the game to delete any matches where players were potentially hacking, or not playing has the game is supposed to be played.
+Moreover, we used our knowledge of the game to delete any matches where players were potentially hacking, or not playing the game has it is supposed to be played.
 These matches were not considered as player experience.
 
-After the cleaning and filtering procedures, our synthetic dataset consists of a population of `r toString(format(length(unique(dat$predator_id))))` predator players who played a total of `r toString(format(length(unique(dat$match_encode_id))))` matches.
-All the matches we analyzed lasted between `r toString(format(round(min(dat$pred_game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$pred_game_duration / 60))), digits = 2)` minutes (mean = `r toString(format(round(mean(dat$pred_game_duration / 60))), digits = 2)`).
+After cleaning and filtering the raw data, we obtained a population of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(format(length(unique(dat$match_encode_id))))` matches.
+The predator players' experience varied between `r toString(format(min(dat$total_xp_killer)))` and `r toString(format(max(dat$total_xp_killer)))` matches played.
+These matches lasted between `r toString(format(round(min(dat$pred_game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$pred_game_duration / 60))), digits = 2)` minutes (mean = `r toString(format(round(mean(dat$pred_game_duration / 60))), digits = 2)`).
 For every match, we report the predator player's anonymous ID, its avatar, the game environment, the predator player's experience along with its speed, and the average speed of the group of prey it encountered.
@@
 ## Variables
+
+The behaviors that we analyzed were the predator's average speed and the average speed of the prey encountered by the predator.
+The predator's average speed is measured as the average distance per second traveled during a match (m/s).
 

### 2022-09-30 manuscript/Chapter3-manuscript.Rmd
update methods ms. add notes after talk with PO

@@
 We applied cleaning and filtering procedures on the raw data to produce a synthetic dataset for our analyses.
-The data that we analyzed were for matches where players did not know each other.
+The data that we analyzed was for matches where players did not know each other.
 We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero.
-Moreover, we used our knowledge of the game to delete any matches where players were potentially hacking, or not playing the game has it is supposed to be played.
+Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game has it is supposed to be played.
 These matches were not considered as player experience.
@@
 
-The behaviors that we analyzed were the predator's average speed and the average speed of the prey encountered by the predator.
-The predator's average speed is measured as the average distance per second traveled during a match (m/s).
+The behaviors we analyzed were the predator's average speed and the average speed of the prey encountered by the predator.
+The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`).
+For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed), digits = 2), nsmall = 2))`).
 

### 2022-09-30 code/05_code_figures/05_figure1.R

@@ -18,8 +18,8 @@
  library(data.table)
  library(ggplot2)
  
- mod <- readRDS("./outputs/02_outputs_models/02A3_GLMM.rds")
-mod <- readRDS("./outputs/02_outputs_models/02A1_GAMM.rds")
+ #mod <- readRDS("./outputs/02_outputs_models/02A3_GLMM.rds")
+ mod <- readRDS("./outputs/02_outputs_models/02A1_GAMM.rds")
 
 
 # Load the data ------------------------------------------------------------

### 2022-10-03 manuscript/Chapter3-manuscript.Rmd
added package versions (MS) and cmdstanr to bib

@@
 
-The behaviors we analyzed were the predator's average speed and the average speed of the prey encountered by the predator.
+We analyzed the predator's average speed and the average speed of the prey encountered by the predator.
 The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`).
 For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed), digits = 2), nsmall = 2))`).
+Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(round(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
+Lastly, the predator's experience was defined as the number of matches played within the study period.
 
@@
 ### Software and computer components
+
+All our statistical analyses were performed on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster provided by the Digital Research Alliance of Canada.
+Cedar runs CentOS Linux 7 as an operating system,
+
+cmdstan-2.28.2 cmdstanr_0.4.0 brms 2.16.3
 

### 2022-10-03 manuscript/Chapter3-manuscript.Rmd
update dhmlm and manuscript

@@
 Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(round(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
-Lastly, the predator's experience was defined as the number of matches played within the study period.
+Lastly, the predator's cumulative experience was defined as the number of matches played prior to the match being monitored.
+For example, the first match of a player would have a cumulative experience value of 0, while the 10^th match would have a value of 9.
 
@@
 
-### Software and computer components
+### Software and computer specifications
 
-All our statistical analyses were performed on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster provided by the Digital Research Alliance of Canada.
-Cedar runs CentOS Linux 7 as an operating system,
-
-cmdstan-2.28.2 cmdstanr_0.4.0 brms 2.16.3
+All our statistical analyses were conducted on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster provided by the Digital Research Alliance of Canada.
+The operating system for Cedar is CentOS Linux 7.
+The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo sampling with the package "brms" version 2.16.3 [@Burkner2017], and "cmdstanr" version 0.4.0 [@Gabry2021] as the backend for estimation (cmdstan installation version 2.28.2).
 
 ### Effect of experience on hunting success
+
+We estimated the relationship between hunting success and experience using a Bayesian generalized additive mixed model with thin plate regression splines.
+Because a maximum of four prey can be captured, we used the beta-binomial family distribution to estimate the success of predators while controlling for overdispersion.
+The model parameters were estimated with a logit link function, while the dispersion parameter ($\phi$) was estimated with an identity link.
+The model had the following form :
+
+\[
+\begin{align}
+logit (P_{ij}) &= (\beta_{0} + id_{0,i} + \phi_{0,ij}) \\
+&\text{ } + \text{ } \beta_{1} \textit{time}_{i} \\
+&\text{ } + \text{ } f(\textit{cumul. xp}_{i}) \\
+\end{align}
+\tag{1}
+\]
+
+The number of knots was set to 10.
 

### 2022-10-03 code/02_code_models/02B_DHMLM.R

@@ -105,10 +105,10 @@ data[, environment_id := as.factor(environment_id)]
 #     xp_level := "advanced"]
 
 # This is before when I had fewer data
-data[cumul_xp_killer < 150,
+data[cumul_xp_killer < 100,
      xp_level := "novice"]
 
-data[cumul_xp_killer %between% c(150, 299),
+data[cumul_xp_killer %between% c(100, 299),
      xp_level := "intermediate"]
 
 data[cumul_xp_killer >= 300,

### 2022-10-03 manuscript/Chapter3-manuscript.Rmd
update MS

@@
 When they hunt, predators often use techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
-expertise).
-While the development of hunting expertise may be essential to maintain foraging success, we have have limited evidence for its role in predator foraging specialization, and the ecological/fitness consequences of such among individual behavioral differences for predator-prey interactions [@Dukas2019].
+experience).
+While the development of hunting experience may be essential to maintain foraging success, we have have limited evidence for its role in predator foraging specialization, and the ecological/fitness consequences of such among individual behavioral differences for predator-prey interactions [@Dukas2019].
 
@@
 However, an important and recurring challenge impeding research on predator-prey behavioral interactions, at the individual level, is the need of collecting data simultaneously on both the predator and prey.
-We have recently demonstrated with behavioral data from an online predator-prey videogame that virtual systems can help in overcoming this challenge, and uncover subtle details on the mechanisms shaping these interactions [@FraserFranco.etal2022].
+We have recently demonstrated with behavioral data from an online predator-prey videogame that virtual systems can help in overcoming this challenge, and uncover details on the mechanisms shaping these interactions [@FraserFranco.etal2022].
 For instance, we tested the classical locomotor crossover hypothesis championed by @Huey.Pianka1981, and found support of its predictions only for active hunters, which concords with a recent experiment involving assassin bugs [@Matsumura.Miyatake2022a].
 Thus, virtual systems may be useful in identifying general ecological patterns, which may in turn help in advancing the current gaps in predator-prey research.
-Other examples of virtual ecological studies show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
+Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
 in prep).
-Because virtual systems generate large volumes of data on prey and predators simultaneously throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of expertise and prey behavior on individual predator foraging specialization, and its potential fitness consequences.
+Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behavior on individual predator foraging specialization along with its potential fitness consequences.
 
@@
 This body of work suggests that the development of expertise is an optimizing process that promotes foraging specialization.
-Empirical studies on human and non-human hunters show that expertise optimizes the efficiency (e.g.
+Empirical studies on human and non-human hunters show that experience optimizes the efficiency (e.g.
 search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@macdonaldCrossculturalComparisonLearning2007;@Reid.etal2010;@Wilson-Rankin2015].
@@
 It may also be costly to attempt different hunting tactics by trial and error when prey are scarce or highly unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
-An alternative mechanism is that expertise may offset the costs/risks of switching foraging tactics as individuals gain experience and information on their prey or their environment, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013].
+An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset by gaining experience and information on their prey, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013].
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, followed by higher performance at later stages of development [reviewed in @Snell-Rood2013].
@@
 There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging.
-Importantly, we have little information on the ecological contexts - except for competition - that favor one strategy over the other.
+Importantly, we have limited information on the ecological contexts - except for competition - that favor one strategy over the other.
 This is reflected in the literature showing contrasting results in the links between specialization and fitness.
@@
 In contrast, individual generalists should be advantaged when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-This hypothesis has however not been tested in systems where behavioral interactions are simultaneously monitored between individuals.
+This hypothesis has however not been tested in systems where behavioral interactions are simultaneously monitored between predator and prey individuals.
 
@@
 *DBD* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
-The data grants a high degree of precision on the behavioral interaction as both the predator and the four prey were measured simultaneously in each trial.
+The data grants a high degree of precision on the behavioral interaction as both the predator and the four prey are measured simultaneously in each trial.
 First, we investigate how predators developed their individual hunting expertise.
 We hypothesize that predators should differ in the development of their expertise because they encounter varying levels of difficulty with the prey that they hunt.
-Second, we test the hypothesis that individual variation in foraging behavior will change with expertise.
-If expertise reduces the costs of switching between hunting tactics, we predict that individual predators should become more flexible with time.
-Alternatively, if expertise enables the refinement of the hunting tactics, then individuals may instead specialize.
+Second, we test the hypothesis that individual variation in foraging behavior will change with experience.
+If experience reduces the costs of switching between hunting tactics, we predict that individual predators should become more flexible with time.
+Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize.
 Third, we evaluate how predator foraging specialization interacts with variation in prey behavior.
-Whether predators specialize or not with expertise may depend on the behavior of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
+Whether predators specialize or not with experience may depend on the behavior of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
 Lastly, if individuals differ in their degree of foraging specialization, then we expect specialist hunters to fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
@@
 
-All our statistical analyses were conducted on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster provided by the Digital Research Alliance of Canada.
+All our statistical analyses were executed on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster maintained by the Digital Research Alliance of Canada.
 The operating system for Cedar is CentOS Linux 7.
@@
 
+*expliquer avant que j'ai fait 2 modèles et que j'ai comparé par LOO afin de déterminer si la relation entre le succès et l'expérience variait d'un joueur à l'autre.
+Dire que j'ai suivi le workflow the Perdersen, Wood, etc.*
+
 We estimated the relationship between hunting success and experience using a Bayesian generalized additive mixed model with thin plate regression splines.
-Because a maximum of four prey can be captured, we used the beta-binomial family distribution to estimate the success of predators while controlling for overdispersion.
-The model parameters were estimated with a logit link function, while the dispersion parameter ($\phi$) was estimated with an identity link.
+Because a maximum of four prey can be captured, we used the beta-binomial family distribution to estimate the probability of capturing all prey while controlling for overdispersion.
+The model parameters were estimated with a logit link function with the number of knots set to ten, while the dispersion parameter ($\phi$) was estimated with an identity link.
 The model had the following form :
@@
 \begin{align}
-logit (P_{ij}) &= (\beta_{0} + id_{0,i} + \phi_{0,ij}) \\
+logit (P_{i}) &= (\beta_{0} + id_{0,i}) \\
 &\text{ } + \text{ } \beta_{1} \textit{time}_{i} \\
@@
 
-The number of knots was set to 10.
+where $P_{i}$ is drawn from a Beta distribution ($P_{i} ~ Beta(a_{i}, b_{i})$) with shape ($a_{i} = \frac{P_{i}}{\phi}$) and scale ($b_{i} = \frac{1 - P_{i}}{\phi}$) parameters.
+Here, $\beta_{0}$ is the general intercept estimating the mean hunting success, and $id_{0,i}$ is the random intercepts term for the the predator player ID, for which we assumed followed a Gaussian distribution with estimated variance ($id_{0,i} ~ N(0, V_{id})$).
+We controlled for the match duration
 

### 2022-10-10 manuscript/Chapter3-manuscript.Rmd
added tables. updated 02A1GAMM.R, updated MS

@@
 The objective of the predator player is to search, stalk, and hunt the four prey players across a virtual environment.
-The objective of the four prey players is to forage for resources in the form of generators that once activated, will enable them to escape through one of two exit doors.
+The objective of the four prey players is to forage for resources while avoiding the predator.
+The resources take the the form of power generators that once activated, will enable the prey to escape through one of two exit doors.
 A match ends when the predator kills all the prey available (i.e.
-that haven't escaped), or when the last prey left escapes the virtual environment.
+that haven't escaped), or when the last remaining prey escapes the virtual environment.
 Each player, predator or prey, can chose an avatar with abilities that encourage specific play styles (e.g.
@@
 During our study period, the game offered 23 playable predator avatars.
-The virtual environment where matches take place is composed of fixed and procedurally generated items (e.g.
-vegetation, mazes, buildings) that constitute its structure.
-Some of these environments are larger than others, with varying levels or buildings.
-However, we have previously shown that they generally do not influence the behavior nor hunting success of the predator, which is probably due to a game feature enabling predators to have visual cues on the generators [@FraserFranco.etal2022].
+The virtual environment where matches take place is composed of fixed and procedurally generated habitat components, such as vegetation, mazes, and buildings.
+Some of these environments are larger than others, with varying structural complexity.
+However, we have previously shown that predators display only minimal changes in behavior and hunting success across the environments, probably due to a game feature enabling predators to have visual cues on the generators [@FraserFranco.etal2022].
 There were 35 virtual game environments available for play during our study period.
@@
 We applied cleaning and filtering procedures on the raw data to produce a synthetic dataset for our analyses.
-The data that we analyzed was for matches where players did not know each other.
+We only analyzed matches where players did not know each other (i.e.
+"Online" mode).
 We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero.
@@
 
-After cleaning and filtering the raw data, we obtained a population of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(format(length(unique(dat$match_encode_id))))` matches.
+Our population consists of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(format(length(unique(dat$match_encode_id))))` matches.
 The predator players' experience varied between `r toString(format(min(dat$total_xp_killer)))` and `r toString(format(max(dat$total_xp_killer)))` matches played.
@@
 
-*expliquer avant que j'ai fait 2 modèles et que j'ai comparé par LOO afin de déterminer si la relation entre le succès et l'expérience variait d'un joueur à l'autre.
-Dire que j'ai suivi le workflow the Perdersen, Wood, etc.*
+We tested whether predators varied in the development of their expertise by computing 3 Bayesian generalized additive mixed models with thin plate regression splines.
+Here, we estimated the relationship between hunting success (i.e.
+number of prey captured) and the predators' cumulative experience (i.e.
+number of matches played before the current match).
+We parametrized the models with increasing complexity following @Pedersen.etal2019.
+The first model was the simplest, with a common global smoothing function for all observations and random intercepts for the predator ID.
+In this model, we assume that individuals have the same development of expertise, with the model estimating a trend for the average individual (i.e.
+global smoother).
+For the second model, we included varying group-level smoothers for the predator ID.
+In this model, we assume that individuals share a similar relationship between success and experience, but that this relationship can vary (e.g.
+individual 1 has a steeper curve than individual 2).
+This enabled us to test whether predators differed in the development of their expertise.
+In the third model, we kept the group-level smoothers for the predators, but removed the global smoother.
+This allows each individual to have a unique relationship between success and experience without penalization by the global smoother.
+Thus, this model assumes that predators do not share a common relationship between success and experience.
+For all three models, we controlled for the match duration.
 
-We estimated the relationship between hunting success and experience using a Bayesian generalized additive mixed model with thin plate regression splines.
-Because a maximum of four prey can be captured, we used the beta-binomial family distribution to estimate the probability of capturing all prey while controlling for overdispersion.
-The model parameters were estimated with a logit link function with the number of knots set to ten, while the dispersion parameter ($\phi$) was estimated with an identity link.
-The model had the following form :
+Because a maximum of four prey can be captured in the game, we used the beta-binomial family distribution to estimate the probability of capturing all prey while controlling for overdispersion.
+The model parameters were estimated with a logit link function, while the dispersion parameter ($\phi$) was estimated with an identity link.
+The probability of capturing the four prey $P_{i}$ is drawn from a Beta distribution ($P_{i} ~ Beta(a_{i}, b_{i})$) with shape ($a_{i} = \frac{P_{i}}{\phi}$) and scale ($b_{i} = \frac{1 - P_{i}}{\phi}$) parameters.
+We employed the default number of basis functions (K) in "brms" for the model to estimate the relationship between hunting success and experience.
+We assumed that the random intercepts for the predator ID $id_{0,i}$ followed a Gaussian distribution with estimated variance ($id_{0,i} ~ N(0, V_{id})$).
+We parametrized all the models to run 4 MCMC chains with 1000 posterior samples for each parameter.
+We ran 2500 iterations for the first model with a thinning set to 8, and 1500 iterations with a thinning set to 4 for the second and third models.
+The first 500 iterations were used as warmups for all models.
+We provide a description on how we specified the priors of each model in the supporting information.
 
-\[
-\begin{align}
-logit (P_{i}) &= (\beta_{0} + id_{0,i}) \\
-&\text{ } + \text{ } \beta_{1} \textit{time}_{i} \\
-&\text{ } + \text{ } f(\textit{cumul. xp}_{i}) \\
-\end{align}
-\tag{1}
-\]
+After fitting the 3 models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017].
 
-where $P_{i}$ is drawn from a Beta distribution ($P_{i} ~ Beta(a_{i}, b_{i})$) with shape ($a_{i} = \frac{P_{i}}{\phi}$) and scale ($b_{i} = \frac{1 - P_{i}}{\phi}$) parameters.
-Here, $\beta_{0}$ is the general intercept estimating the mean hunting success, and $id_{0,i}$ is the random intercepts term for the the predator player ID, for which we assumed followed a Gaussian distribution with estimated variance ($id_{0,i} ~ N(0, V_{id})$).
-We controlled for the match duration
+```{r}
+#\[
+#\begin{align}
+#logit (P_{i}) &= (\beta_{0} + id_{0,i}) \\
+#&\text{ } + \text{ } \beta_{1} \textit{match duration}_{i} \\
+#&\text{ } + \text{ } f(\textit{cumulative xp}_{i}) \\
+#\end{align}
+#\tag{1}
+#\]
+```
 

### 2022-10-10 code/02_code_models/02A1_GAMM.R

@@ -139,7 +139,7 @@ priors <- c(
   # priors on smooth terms
   set_prior("cauchy(0, 2)",
             class = "sds",
-            coef = "s(Zcumul_xp)"),      
+            coef = "s(Zcumul_xp)"),
   # priors on phi
   set_prior("normal(2, 0.5)",
             class = "phi")

### 2022-10-10 code/03_code_model-validation/03_A_models-draws.R

@@ -26,7 +26,7 @@ library(ggplot2)
 # Import model in R session
 mod1 <- readRDS("./outputs/02_outputs_models/02A1_GAMM.rds")
 mod2 <- readRDS("./outputs/02_outputs_models/02A2_GAMM.rds")
-mod3 <- readRDS("./outputs/02_outputs_models/02A3_GLMM.rds")
+mod3 <- readRDS("./outputs/02_outputs_models/02A3_GAMM.rds")
 
 
 # Extract posterior draws
@@ -105,6 +105,17 @@ ggplot(posterior_fit1) +
   #             fill = "steelblue",
   #             color = "black",
   #             alpha = 0.6) +
+  geom_density(aes(sds_sZcumul_xp_1),
+               fill = "#FC4E07",
+               color = "black",
+               alpha = 0.6) + 
+  theme_classic()  
+
+ggplot(posterior_fit1) +
+  geom_density(aes(prior_sds_sZcumul_xp_1),
+               fill = "steelblue",
+               color = "black",
+               alpha = 0.6) +
   geom_density(aes(sds_sZcumul_xp_1),
                fill = "#FC4E07",
                color = "black",
@@ -283,7 +294,7 @@ ggplot(posterior_fit3) +
 
 # Game duration
 ggplot(posterior_fit3) +
-  geom_density(aes(prior_b),
+  geom_density(aes(prior_b_Zgame_duration),
                fill = "steelblue",
                color = "black",
                alpha = 0.6) +
@@ -293,27 +304,39 @@ ggplot(posterior_fit3) +
                alpha = 0.6) + 
   theme_classic()
 
-
-# slope term of cumul xp
+# not sure what this is but refers to predator ID
 ggplot(posterior_fit3) +
-  geom_density(aes(prior_b),
+  geom_density(aes(prior_sds_sZcumul_xppredator_id_1),
                fill = "steelblue",
                color = "black",
                alpha = 0.6) +
-  geom_density(aes(b_Zcumul_xp),
+  geom_density(aes(sds_sZcumul_xppredator_id_1),
                fill = "#FC4E07",
                color = "black",
                alpha = 0.6) + 
   theme_classic()
 
 
-# Standard deviation of predator ID
+# not sure what this is but refers to predator ID
 ggplot(posterior_fit3) +
-  geom_density(aes(prior_sd_predator_id),
+  geom_density(aes(prior_sds_sZcumul_xppredator_id_2),
                fill = "steelblue",
                color = "black",
[…]

### 2022-10-10 code/04_code_model-processing/04_id-draws.R

@@ -121,7 +121,7 @@
  path <- "./outputs/04_outputs_model-processing"
 
  # Save
- saveRDS(draws, file = file.path(path, "04_id-draws.rds")
+ saveRDS(draws, file = file.path(path, "04_id-draws.rds"))
 
 # =======================================================================
 # =======================================================================

### 2022-10-10 code/05_code_tables/05_loo-cv_table.R

@@ -1,0 +1,108 @@
+
+# ===========================================================================
+
+#                         Code to produce Table I                           #
+
+# ===========================================================================
+
+
+
+
+
+# ===========================================================================
+# 1. Load librairies and import table
+# ===========================================================================
+
+# Load libraries
+library(data.table)
+library(flextable)
+library(officer)
+library(dplyr)
+
+# Source the files
+path <- file.path("./outputs/03_outputs_model-validation")
+loo_tab <- data.table(readRDS(file.path(path, "03A_lootable.rds")))
+
+# Add model column
+loo_tab[, model := c("Global smoother (GS)",
+                     "GS + group-level smoothers",
+                     "Group-level smoothers only")]
+
+# Reorder columns
+loo_tab <- loo_tab[, c(9, 1:8)]
+
+# ===========================================================================
+# ===========================================================================
+
+
+
+
+
+# ===========================================================================
+# 3. Compute the table using flextable
+# ===========================================================================
+
+# Prepare the table parameters ----------------------------------------------
+
+# Custom header
+my_header <- data.frame(
+  col_keys = c("model",
+               "elpd_diff",
+               "se_diff",
+               "elpd_loo",
+               "se_elpd_loo"),
+  line1 = c("model",
+            "elpd \ndifference",
+            "sd \ndifference",
+            "elpd loo \nvalue",
+            "elpd loo standard error"),
+  stringsAsFactors = FALSE
+)
+
+# Custom theme
+my_theme <- function(x, ...) {
+  x <- colformat_double(x, big.mark = " ", 
+                        decimal.mark = ".",
+                        digits = 2)
+  x <- set_table_properties(x, layout = "fixed")
+  x <- border_remove(x)
+  std_border <- fp_border(width = 1, color = "black")
+  x <- hline_top(x, part = "all", border = std_border)
+  x <- hline_bottom(x, part = "all", border = std_border)
+  autofit(x)
+}
+
+
+
+# Create the table ----------------------------------------------------------
+
+loo_table <- loo_tab %>%
+  select(model, elpd_diff, se_diff, elpd_loo, se_elpd_loo) %>%
+  flextable(col_keys = my_header$col_keys) %>%
+  set_header_df(mapping = my_header, key = "col_keys") %>%
+  my_theme() %>%
+  merge_v(part = "header") %>%
+  merge_h(part = "header") %>%
[…]

### 2022-10-10 manuscript/Chapter3-manuscript.Rmd
updated MS + word. added tables. first sketch.

@@
 library(brms)
+library(flextable)
+library(officer)
 
@@
 For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed), digits = 2), nsmall = 2))`).
-Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(round(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
+Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
 Lastly, the predator's cumulative experience was defined as the number of matches played prior to the match being monitored.
@@
 
-```{r out.width = "100%", fig.cap = "**Figure 1.** Results from the Bayesian generalized linear mixed model.
-(A) Fitted (solid) line displaying the posterior predicted values relating the predators' hunting success to their cumulative experience.
-Here, we transformed the hunting success and cumulative experience back to their original scale (i.e.
-the amount of prey captured and the number of matches played respectively).
-The band around the solid line represents the 95% credible intervals.
-(B) The estimated posterior predicted mean hunting success of each predator player.
-We display the hunting success back-transformed to its original scale."}
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure1.png"))
+```{r, ft.align = "left"}
+
+tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))
+
+set_caption(
+  tab1,
+  caption = "LOO table",
+  style = "Table Caption"
+)
+
+```
+
+<br>
+
+blablabla
+
+```{r, ft.align = "left"}
+
+tab2 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table2.rds"))
+
+set_caption(
+  tab2,
+  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother",
+  style = "Table Caption"
+)
+
 ```
@@
 specialization)."}
+
 knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure2.png"))
+
 ```
@@
 ```{r out.width = "100%", fig.cap = "**Figure 3.** Title (A) Novice. (B) Advanced."}
+
 knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure3.png"))
+
 ```
@@
 ```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novice. (C) and (D) Advanced."}
+
 knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure4.png"))
+
 ```

### 2022-10-10 code/05_code_tables/05A1_GAMM-table.R

@@ -1,16 +1,15 @@
+# ===========================================================================
+
+#                         Code to produce Table II                         #
 
 # ===========================================================================
 
-#                         Code to produce Table I                           #
-
-# ===========================================================================
-
 
 
 
 
 # ===========================================================================
-# 1. Load librairies and import table
+# 1. Load librairies and import the model
 # ===========================================================================
 
 # Load libraries
@@ -19,17 +18,36 @@ library(flextable)
 library(officer)
 library(dplyr)
 
-# Source the files
-path <- file.path("./outputs/03_outputs_model-validation")
-loo_tab <- data.table(readRDS(file.path(path, "03A_lootable.rds")))
+# Import the model
+path <- file.path("./outputs/02_outputs_models")
+mod1 <- readRDS(file.path(path, "02A1_GAMM.rds"))
 
-# Add model column
-loo_tab[, model := c("Global smoother (GS)",
-                     "GS + group-level smoothers",
-                     "Group-level smoothers only")]
+# ===========================================================================
+# ===========================================================================
 
-# Reorder columns
-loo_tab <- loo_tab[, c(9, 1:8)]
+
+
+
+
+# ===========================================================================
+# 2. Extract the posterior means of each parameter
+# ===========================================================================
+
+# Extract the posterior estimates
+estim <- data.table(posterior_summary(mod1)[1:6, ], keep.rownames = TRUE)
+
+# Rename the parameters
+estim[rn == "b_Intercept", rn := "Intercept"]
+estim[rn == "b_Zgame_duration", rn := "Z game duration"]
+estim[rn == "bs_sZcumul_xp_1", rn := "f(Z cumulative xp)"]
+estim[rn == "sds_sZcumul_xp_1", rn := "SD f(Z cumulative xp)"]
+estim[rn == "sds_spredator_id_1", rn := "SD predator ID"]
+
+# Round values
+estim[, c(2:5) := 
+        lapply(.SD,
+               function (x) round(x,digits = 3)),
+      .SDcols = c(2:5)]
 
 # ===========================================================================
 # ===========================================================================
@@ -46,16 +64,13 @@ loo_tab <- loo_tab[, c(9, 1:8)]
 
 # Custom header
 my_header <- data.frame(
[…]

### 2022-10-12 manuscript/Chapter2-SupInfo.Rmd
renamed files from chap3 to chap2

---
title: "Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter2-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: e-letters.csl
---

### 2022-10-12 manuscript/Chapter2-manuscript.Rmd
renamed files from chap3 to chap2

--- 2022-10-10 manuscript/Chapter3-manuscript.Rmd
@@
   word_document:
-    reference_docx: Chapter3-styles.docx
+    reference_docx: Chapter2-styles.docx
     fig_caption: yes

### 2022-10-12 manuscript/Chapter2-SupInfo.Rmd
update supinfo

@@
 ---
+
+```{r setup, include = FALSE}
+
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
+
+library(data.table)
+library(brms)
+library(flextable)
+library(officer)
+
+```
+
+need to talk about priors here for the gamms etc
+
+```{r, ft.align = "left"}
+
+tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))
+
+set_caption(
+  tab1,
+  caption = "LOO table",
+  style = "Table Caption"
+)
+
+```

### 2022-10-12 manuscript/Chapter2-manuscript.Rmd
update MS methods

@@
 We analyzed the predator's average speed and the average speed of the prey encountered by the predator.
-The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`).
-For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed), digits = 2), nsmall = 2))`).
+The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`).
+For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`).
 Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
 Lastly, the predator's cumulative experience was defined as the number of matches played prior to the match being monitored.
-For example, the first match of a player would have a cumulative experience value of 0, while the 10^th match would have a value of 9.
+For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.
 
@@
 
-We tested whether predators varied in the development of their expertise by computing 3 Bayesian generalized additive mixed models with thin plate regression splines.
-Here, we estimated the relationship between hunting success (i.e.
+We tested whether predators varied in the development of their expertise by computing 3 Bayesian generalized additive mixed models (GAMM) with thin plate regression splines that estimated the relationship between hunting success (i.e.
 number of prey captured) and the predators' cumulative experience (i.e.
 number of matches played before the current match).
-We parametrized the models with increasing complexity following @Pedersen.etal2019.
+We parametrized the models following the method by @Pedersen.etal2019.
 The first model was the simplest, with a common global smoothing function for all observations and random intercepts for the predator ID.
@@
 The model parameters were estimated with a logit link function, while the dispersion parameter ($\phi$) was estimated with an identity link.
-The probability of capturing the four prey $P_{i}$ is drawn from a Beta distribution ($P_{i} ~ Beta(a_{i}, b_{i})$) with shape ($a_{i} = \frac{P_{i}}{\phi}$) and scale ($b_{i} = \frac{1 - P_{i}}{\phi}$) parameters.
+The probability of capturing the four prey $P_{i}$ is drawn from a Beta distribution ($P_{i} \sim Beta(a_{i}, b_{i})$) with shape ($a_{i} = \frac{P_{i}}{\phi}$) and scale ($b_{i} = \frac{1 - P_{i}}{\phi}$) parameters.
 We employed the default number of basis functions (K) in "brms" for the model to estimate the relationship between hunting success and experience.
-We assumed that the random intercepts for the predator ID $id_{0,i}$ followed a Gaussian distribution with estimated variance ($id_{0,i} ~ N(0, V_{id})$).
-We parametrized all the models to run 4 MCMC chains with 1000 posterior samples for each parameter.
+We assumed that the random intercepts for the predator ID ($id_{0,i}$) followed a Gaussian distribution with estimated variance ($id_{0,i} \sim N(0, V_{id})$).
+We parametrized all models to run 4 MCMC chains with 1000 posterior samples.
 We ran 2500 iterations for the first model with a thinning set to 8, and 1500 iterations with a thinning set to 4 for the second and third models.
-The first 500 iterations were used as warmups for all models.
-We provide a description on how we specified the priors of each model in the supporting information.
-
+The first 500 iterations were used as warmups.
+We provide a description on how we specified the priors for each model in the supporting information.
 After fitting the 3 models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017].
@@
 
+We proceeded to test whether foraging behavior changes with experience, and compare the success of generalists vs specialists, using a multivariate double hierarchical linear model (MDHLM) [@@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a]
+
 \newpage
@@
 
-```{r, ft.align = "left"}
-
-tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))
-
-set_caption(
-  tab1,
-  caption = "LOO table",
-  style = "Table Caption"
-)
-
-```
-
 <br>
@@
 
-tab2 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table2.rds"))
+tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table2.rds"))
 
 set_caption(
-  tab2,
+  tab1,
   caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother",

### 2022-10-12 manuscript/Chapter2-manuscript.Rmd
update MS and refs

@@
 In this game, players get to chose if they wish to play has a predator or a prey.
-The objective of the predator player is to search, stalk, and hunt the four prey players across a virtual environment.
+The objective of the predator player is to hunt and capture the four prey players across a virtual environment.
 The objective of the four prey players is to forage for resources while avoiding the predator.
-The resources take the the form of power generators that once activated, will enable the prey to escape through one of two exit doors.
+The resources are in the form of power generators that once activated, will enable the prey to escape through one of two exit doors.
+The composition of the predator and prey group for a match is determined by a skill-based matchmaking algorithm.
 A match ends when the predator kills all the prey available (i.e.
@@
 They also display flexibility in the use of these tactics by switching between them across matches.
-The expression of these tactics and their success is highly dependent on the behavior of the prey group.
+The expression of these tactics and their success is also shaped by the behavior of the prey group.
 The prey need to forage for resources while maintaining a high level of attention on the predator cues to avoid being detected and chased.
@@
 These matches were not considered as player experience.
+We then proceeded to partition the player population by total experience, and randomly sampled players to have a uniform representation of total gameplay experience.
+To optimize the representation of gameplay experience at advanced levels, we set the maximum amount of matches at 500 for these players.
+For instance, there could be a large difference in gameplay between 300-500 and 500-1000 matches.
+Players that played above 500 matches represented only ~2% of the population.
 
@@
 The operating system for Cedar is CentOS Linux 7.
-The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo sampling with the package "brms" version 2.16.3 [@Burkner2017], and "cmdstanr" version 0.4.0 [@Gabry2021] as the backend for estimation (cmdstan installation version 2.28.2).
+The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo sampling with the package "brms" version 2.16.3 [@Burkner2017], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the backend for estimation (cmdstan installation version 2.28.2).
 
@@
 
-We tested whether predators varied in the development of their expertise by computing 3 Bayesian generalized additive mixed models (GAMM) with thin plate regression splines that estimated the relationship between hunting success (i.e.
+We tested whether predators varied in the development of their expertise by computing 3 Bayesian generalized additive mixed models (GAMM) with thin plate regression splines estimating the relationship between hunting success (i.e.
 number of prey captured) and the predators' cumulative experience (i.e.
@@
 Because a maximum of four prey can be captured in the game, we used the beta-binomial family distribution to estimate the probability of capturing all prey while controlling for overdispersion.
-The model parameters were estimated with a logit link function, while the dispersion parameter ($\phi$) was estimated with an identity link.
+The model parameters were estimated with a logit link function, while the dispersion parameter ($\phi$) was estimated with an identity link for all models.
 The probability of capturing the four prey $P_{i}$ is drawn from a Beta distribution ($P_{i} \sim Beta(a_{i}, b_{i})$) with shape ($a_{i} = \frac{P_{i}}{\phi}$) and scale ($b_{i} = \frac{1 - P_{i}}{\phi}$) parameters.
-We employed the default number of basis functions (K) in "brms" for the model to estimate the relationship between hunting success and experience.
+We employed the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
 We assumed that the random intercepts for the predator ID ($id_{0,i}$) followed a Gaussian distribution with estimated variance ($id_{0,i} \sim N(0, V_{id})$).
@@
 
-### Foraging tactics at each level of experience
+### Foraging behavior and success, prey behavior, and their relationships, at each level of experience
 
-We proceeded to test whether foraging behavior changes with experience, and compare the success of generalists vs specialists, using a multivariate double hierarchical linear model (MDHLM) [@@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a]
+We proceeded to test whether foraging behavior changes with experience, and compare the success of generalists vs specialists, using a multivariate double hierarchical linear model (MDHLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
+
+expliquer comment j'ai partitionné l'expérience basée sur les résultats du GAMM
+expliquer que j'ai calculé le coefficient de variation pour comparer le comportement
 

### 2022-10-13 manuscript/Chapter2-manuscript.Rmd
updated fig 2 and 3 + MS

@@
 
-Because a maximum of four prey can be captured in the game, we used the beta-binomial family distribution to estimate the probability of capturing all prey while controlling for overdispersion.
-The model parameters were estimated with a logit link function, while the dispersion parameter ($\phi$) was estimated with an identity link for all models.
-The probability of capturing the four prey $P_{i}$ is drawn from a Beta distribution ($P_{i} \sim Beta(a_{i}, b_{i})$) with shape ($a_{i} = \frac{P_{i}}{\phi}$) and scale ($b_{i} = \frac{1 - P_{i}}{\phi}$) parameters.
+Because a maximum of four prey can be captured in the game, and to control for overdispersion, we computed the three models using a modified version of the beta-binomial distribution implemented in "brms" (for an overview, see https://paul-buerkner.github.io/brms/articles/brms_customfamilies.html).
+Thus, hunting success was estimated as the probability of capturing the four prey ($p_i$), drawn from a Beta distribution ($p_i \sim Beta(\mu_i, \phi) = Beta(\alpha = \mu\phi, \beta = (1 - \mu)\phi)$) with mean ($\mu \in [0,1]$) and shape ($\phi > 0$) parameters.
+We employed a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the shape parameter ($\phi$) was estimated with an identity link for all models.
+
 We employed the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
@@
 
-We proceeded to test whether foraging behavior changes with experience, and compare the success of generalists vs specialists, using a multivariate double hierarchical linear model (MDHLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
+We proceeded to test whether foraging behavior changes with experience, and compare the success of generalists vs specialists, using a multivariate double hierarchical generalized linear model (MDHGLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
 
@@
 
-Contrary to our predictions, individual predators did not differ in the development of their expertise, as the best model was the one with a general population trend with varying intercepts only (Table x.).
-Moreover, we did not detect a relationship between experience (i.e.
-the cumulative amount of matches played) and hunting success, such that players did not optimize their success with increasing experience as we expected (Figure 1 A).
-However, predators did differ in their average hunting success across the study period (Figure 1 B).
-
-<br>
-
-blablabla
+Contrary to our predictions, individual predators did not differ in the development of their expertise, as the best model was the one with a global smoother with varying intercepts only (Table S1 in the supporting information).
+The model detected only a weak relationship between hunting success and experience (i.e.
+the cumulative amount of matches played), such that players did not substantially optimize their success with increasing experience as we expected (Table 1 and Figure S1 in the supporting information).
+However, predators did differ in their average hunting success across the study period (Figure S1).
+*peut être coder un autre modèle où je contrôle pour les proies afin de voir si les différences de succès disparaissent*
 
@@
   tab1,
-  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother",
+  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother. The values are presented on the logit scale",
   style = "Table Caption"
@@
 
+## Effect of experience on the development of behavioral specialization
+
+```{r out.width = "100%", fig.cap = "**Figure 1.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience.
+(A) Coefficient of variation for the among individual differences in average behavior.
+(B) Coefficient fo variation for the among individual differences in intra individual variance (i.e.
+specialization)."}
+
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure1.png"))
+
+```
+
 blablabla figure 2
 
-```{r out.width = "100%", fig.cap = "**Figure 2.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience.
-(A) Coefficient of variation for the among individual differences in average behavior.
-(B) Coefficient fo variation for the among individual differences in within individual variance (i.e.
-specialization)."}
+```{r out.width = "100%", fig.cap = "**Figure 2.** Distribution of the intra individual behavioral variation (i.e.
+specialization) of predators when they were (A) novices and (B) advanced.
+The red band displays the 95% CI of the intercept for the intra individual variance in predator speed."}
 
@@
 
-blablabla figure 3
+## Relationship between behavioral specialization and prey variability
 
-```{r out.width = "100%", fig.cap = "**Figure 3.** Title (A) Novice. (B) Advanced."}
+```{r out.width = "100%", fig.cap = "**Figure 3.** Full correlation matrix of the MDHGLM relating the mean and IIV speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+Starting from the upper part of the plot are displayed the five parameters for novice predators (gray), the five for intermediate predators (yellow), and the five for advanced predators (blue).
+Larger dark blue circles indicate stronger positive correlations, while larger dark red circles indicate stronger negative correlations.
+The black squares indicate correlations between different experience levels."}
 
@@
 
-blablabla figure 4
+## Hunting success of behavioral specialists vs generalists
 
-```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novice. (C) and (D) Advanced."}
+*relationship between IIV of prey and success fades with experience*
+
+```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novices. (C) and (D) Advanced."}
 

### 2022-10-13 code/05_code_figures/05_figure2.R

@@ -23,7 +23,7 @@
  library(ggridges)
  
  # import model
- fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
+ #fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
  fit <- readRDS("./tests/02B_DHMLM.rds")
  
 
@@ -33,8 +33,11 @@
  # Data
  data <- fread("./data/FraserFrancoetalXXXX-data.csv",
                select = c("predator_id",
+                          "pred_game_mode",
                           "total_xp_killer",
                           "pred_speed"))
+ 
+ data <- data[pred_game_mode == "Online"]
  
  # Extract standard deviation of speed
  sd_speed1 <- sd(data[total_xp_killer < 100]$pred_speed)
@@ -107,6 +110,13 @@ setnames(draws, "value", "speed_sigma")
 
 # Transform  ------------------------------------------------------------
 
+# Add population intercept
+int1 <- fixef(fit, pars = "sigma_speednovice_Intercept")[1]
+int2 <- fixef(fit, pars = "sigma_speedadvanced_Intercept")[1]
+
+draws[xp_level == "novice", speed_sigma := speed_sigma + int1]
+draws[xp_level == "advanced", speed_sigma := speed_sigma + int2]
+
 # Back transform to original scale (sigma is on log scale)
 draws[, exp_speed_sigma := exp(speed_sigma)]
 
@@ -167,109 +177,115 @@ table <- merge(unique(data[, "predator_id"]),
 
 # Plot experts ----------------------------------------------------------
 
-#scaled_breaks1 <- c(0.2 / sd_speed1,
-#                    0.6 / sd_speed1,
-#                    1.0 / sd_speed1,
-#                    1.4 / sd_speed1)
+ #scaled_breaks1 <- c(0.2 / sd_speed1,
+ #                    0.6 / sd_speed1,
+ #                    1.0 / sd_speed1,
+ #                    1.4 / sd_speed1)
+ 
+ # Extract 95% CI of intercepts
+ int1min <- exp(fixef(fit, pars = "sigma_speednovice_Intercept")[3])
+ int1max <- exp(fixef(fit, pars = "sigma_speednovice_Intercept")[4])
+ int2min <- exp(fixef(fit, pars = "sigma_speedadvanced_Intercept")[3])
+ int2max <- exp(fixef(fit, pars = "sigma_speedadvanced_Intercept")[4])
 
-
-# Plot the distributions of advanced players
[…]

### 2022-10-18 manuscript/Chapter2-manuscript.Rmd
update methods. methods done.

@@
     fig_caption: yes
+    pandoc_args: ["-Fpandoc-crossref"] # to have eq. numbers
 bibliography: references.bib
@@
 These matches lasted between `r toString(format(round(min(dat$pred_game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$pred_game_duration / 60))), digits = 2)` minutes (mean = `r toString(format(round(mean(dat$pred_game_duration / 60))), digits = 2)`).
-For every match, we report the predator player's anonymous ID, its avatar, the game environment, the predator player's experience along with its speed, and the average speed of the group of prey it encountered.
+The following information is collected and reported for every match : the player's anonymous ID, its avatar, the game environment, the predator player's experience along with its speed, and the average speed of the group of prey it encountered.
 
@@
 We employed the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
-We assumed that the random intercepts for the predator ID ($id_{0,i}$) followed a Gaussian distribution with estimated variance ($id_{0,i} \sim N(0, V_{id})$).
-We parametrized all models to run 4 MCMC chains with 1000 posterior samples.
-We ran 2500 iterations for the first model with a thinning set to 8, and 1500 iterations with a thinning set to 4 for the second and third models.
+We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated variance ($id \sim N(0,\ I\ \sigma^2_{id})$).
+We parametrized all models to run 4 MCMC chains with 1000 posterior samples for each parameter.
+To do so, we ran 2500 iterations for the first model with a thinning set to 8, and 1500 iterations with a thinning set to 4 for the second and third models.
 The first 500 iterations were used as warmups.
@@
 We proceeded to test whether foraging behavior changes with experience, and compare the success of generalists vs specialists, using a multivariate double hierarchical generalized linear model (MDHGLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
+We categorized the predators by their experience using the predicted values from the GAMM (see Figure S1 in the supporting information).
+We assigned the status of "novice" to any predator player that had a cumulative experience below 100 matches.
+For example, a predator player that played 500 matches in total would be labelled as a novice in its first 100 matches.
+Following this logic, we labelled predators as "intermediate" hunters when they had a cumulative experience between 100 and 299 and matches.
+For the third and last group, we defined predators as "advanced" hunters when they had a cumulative experience equal or above 300, with a maximum of 499 matches.
 
-expliquer comment j'ai partitionné l'expérience basée sur les résultats du GAMM
-expliquer que j'ai calculé le coefficient de variation pour comparer le comportement
+For each level of experience (i.e.
+novice, intermediate, advanced), we estimated the mean speed of individual predators, and an heterogeneous structure of the residuals such that we could estimate their intra individual variance (IIV) in speed (i.e.
+specialization).
+We followed the same structure for the preys' speed to estimate among individual differences in the mean and variance in speed of the prey encountered by predators.
+For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean hunting success.
+For all variables, we controlled for the duration of the match standardized in mean and unit variance.
+The model has the following form, with each equation repeated three times (i.e.
+one for each level of experience) :
+
+$$
+\begin{align}
+speed_{pred} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
+log(\sigma^2_{e,\ pred}) &= X_{d} + Z\ id_{d}
+\end{align}
+$${#eq:eqn1}
+
+$$
+\begin{align}
+speed_{prey} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
+log(\sigma^2_{e,\ prey}) &= X_{d} + Z\ id_{d}
+\end{align}
+$${#eq:eqn2}
+
+$$
+\begin{align}
+success_{pred} &= \text{ } X_{m}\ b_m + Z\ id_{m} + e
+\end{align}
+$${#eq:eqn3}
+
+where $env \sim N(0,\ I\ \sigma^2_{env})$, $av \sim N(0,\ I\ \sigma^2_{av})$, and $id \sim N(0,\ I\ \sigma^2_{id})$.
+$b$ is the vector of fixed effects with its incidence matrix $X$.
+$env$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$.
+The variance parameters $\sigma^2_{env}$, $\sigma^2_{av}$, and $\sigma^2_{id}$, correspond to the among environment, among avatar, and among individual variances, respectively.
+$I$ is the identity matrix, with $I,\ \sigma^2$ indicating that the random effects are independently and identically distributed.
+The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively.
+The first two equations were parametrized with a Gaussian distribution family, while the third equation was parametrized with a beta-binomial distribution family.
+We parametrized the model to run 4 MCMC chains with 1000 posterior samples for each parameter.
+To do so, we ran 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups.
+We explain how we specified the priors for the MDHGLM in the supporting information.
+
+We estimated the correlation between the individual random effect on the mean and on the dispersion within each trait (e.g.
+$cor(\sigma^2_{id_{m}\ pred}\ \sigma^2_{id_{d}\ pred})$) and among each trait (e.g.
+$cor(\sigma^2_{id_{m}\ pred}\ \sigma^2_{id_{d}\ prey})$) within a level of experience.
+We also evaluated these correlations among the different levels of experience (e.g.
+$cor(\sigma^2_{id_{m}\ pred\ novice}\ \sigma^2_{id_{d}\ pred\ intermediate})$).
+The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviors across each developmental stage.
+The correlations were estimated using a multivariate Gaussian distribution.
+
+Lastly we calculated the coefficient of variation in the mean (termed $CV_I$) and dispersion (termed $CV_p$) part of the predator's speed for each stage of experience, allowing us to report standardized effect sizes of individual variance for comparison across traits and studies [@cleasbyQuantifyingPredictabilityBehaviour2015;@Holtmann.etal2017;@Dingemanse.etal2022].
+This also allowed us to evaluate whether predators displayed increasing/decreasing differences in specialization at each stage of experience.
 
@@
 
-```{r, ft.align = "left"}
+```{r table1, ft.align = "left"}
 
@@
   tab1,
-  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother. The values are presented on the logit scale",
+  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother. The values are presented on the logit scale.",
   style = "Table Caption"
@@
 
-```{r out.width = "100%", fig.cap = "**Figure 1.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience.
+```{r fig1, out.width = "100%", fig.cap = "**Figure 1.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience.
 (A) Coefficient of variation for the among individual differences in average behavior.
@@
 
-```{r out.width = "100%", fig.cap = "**Figure 2.** Distribution of the intra individual behavioral variation (i.e.
+```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Distribution of the intra individual behavioral variation (i.e.
 specialization) of predators when they were (A) novices and (B) advanced.
@@
 
-```{r out.width = "100%", fig.cap = "**Figure 3.** Full correlation matrix of the MDHGLM relating the mean and IIV speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Full correlation matrix of the MDHGLM relating the mean and IIV speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
 Starting from the upper part of the plot are displayed the five parameters for novice predators (gray), the five for intermediate predators (yellow), and the five for advanced predators (blue).
@@
 
-```{r out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novices. (C) and (D) Advanced."}
+```{r fig4, out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novices. (C) and (D) Advanced."}
 

### 2022-12-20 code/02_code_models/02A3_prey-GAMM.R
added 02A3_prey-GAMM model

@@ -1,0 +1,169 @@
+# ==========================================================================
+
+#         GAMM model S - individual curves without common smoother
+#                              hunting success
+
+# ==========================================================================
+
+
+
+
+
+# ==========================================================================
+# 1. Prepare the data
+# ==========================================================================
+
+
+
+# Load packages ------------------------------------------------------------
+
+# Detect cores
+options(mc.cores = parallel::detectCores())
+
+# Load libraries
+library(data.table)
+library(brms)
+library(parallel)
+
+
+
+# Load data ----------------------------------------------------------------
+
+# Folder path Compute Canada
+folder <- file.path("/home", "maxime11", "projects", "def-monti", 
+                    "maxime11", "phd_project", "data")
+
+# Load data
+data <- fread(file.path(folder, "FraserFrancoetalXXXX-data.csv"),
+              select = c("predator_id",
+                         "hunting_success",
+                         "prey_avg_speed",
+                         "game_duration",
+                         "cumul_xp_pred"))
+
+# Project path for testing
+#data <- fread("./data/FraserFrancoetalXXXX-data.csv",
+#              select = c("predator_id",
+#                         "hunting_success"
+#                         "game_duration",
+#                         "cumul_xp_pred",))
+
+# Predator id as factor
+data[, predator_id := as.factor(predator_id)]
+
+
+
+# Standardise the variables (Z-scores) -------------------------------------
+
+standardize <- function (x) {(x - mean(x, na.rm = TRUE)) / 
+                              sd(x, na.rm = TRUE)}
+
+data[, c(
+    "Zprey_speed",
+    "Zgame_duration",
+    "Zcumul_xp"
+    ) := lapply(.SD, standardize), 
+       .SDcols = c(3:5)]
+
+# ==========================================================================
+# ==========================================================================
+
+
+
+
+
+# ==========================================================================
+# 2. Parametrize the model
+# ==========================================================================
+
+
+
+# Compute the custom family ------------------------------------------------
+
+beta_binomial2 <- custom_family(
+  "beta_binomial2", dpars = c("mu", "phi"),
+  links = c("logit", "log"), lb = c(NA, 0),
+  type = "int", vars = "vint1[n]"
+)
+
+
+
+# Function -----------------------------------------------------------------
+
+stan_funs <- "
+  real beta_binomial2_lpmf(int y, real mu, real phi, int T) {
[…]

### 2022-12-20 jobs_slurm/02A3_prey-GAMM.sh

@@ -1,0 +1,16 @@
+#!/bin/bash
+#SBATCH --account=def-monti
+#SBATCH --nodes=1
+#SBATCH --cpus-per-task=48
+#SBATCH --mem=64000M
+#SBATCH --time=1-15:00
+#SBATCH --mail-user=fraser_franco.maxime@courrier.uqam.ca
+#SBATCH --mail-type=ALL
+
+module load StdEnv/2020
+module load gcc/9.3.0
+module load r-bundle-bioconductor/3.14
+module load r/4.1.2
+
+#export R_LIBS=~/.local/R/$EBVERSIONR/
+Rscript 02A3_prey-GAMM.R

### 2022-12-20 code/05_code_figures/05_figure1.R
changed order of figure numbers

@@ -1,173 +1,211 @@
-# =======================================================================
+# ==========================================================================
 
-#                   Plot the coefficients of variation
+#                          Plot 02A1 GAMM model
 
-# =======================================================================
-
-
+# ==========================================================================
 
 
 
-# =======================================================================
-# 1. Import the libraries and data
-# =======================================================================
+# ==========================================================================
+# 1. Prepare script
+# ==========================================================================
 
- # Libraries
+
+
+# Load libraries and model -------------------------------------------------
+
+ library(brms)
  library(data.table)
  library(ggplot2)
  library(ggpubr)
-
- # CV table
- path <- "./outputs/04_outputs_model-processing"
- tab <- readRDS(file.path(path, "04_CV-table.rds"))
+ library(viridis)
  
- # Rename the XP variable
- tab[xp_level == "novice", xp_level := "Novice"]
- tab[xp_level == "interm", xp_level := "Intermediate"]
- tab[xp_level == "advanced", xp_level := "Advanced"]
+ path <- file.path(getwd(), "outputs", "02_outputs_models")
+
+ mod1 <- readRDS(file.path(path, "02A3_GAMM.rds"))
+ mod2 <- readRDS(file.path(path, "02A3_prey-GAMM.rds"))
+
+
  
- # Rename the behaviour names
- tab[variable == "pred_speed", variable := "Predator speed"]
- tab[variable == "prey_speed", variable := "Prey speed"]
+# Load the data ------------------------------------------------------------
 
- # Reorder factors
- tab[, xp_level := factor(xp_level, levels = c("Novice",
-                                               "Intermediate",
-                                               "Advanced"))]
+ data <- fread("./data/FraserFrancoetalXXXX-data.csv",
+               select = c("predator_id",
+                          "game_duration",
+                          "pred_speed",
+                          "prey_avg_speed",
+                          "cumul_xp_pred",
+                          "total_xp_pred",
+                          "hunting_success",
+                          "latency_1st_capture",
+                          "chase_count",
+                          "chase_count_success"))
  
- # Encode Parameter and variable as factor
- tab[, ":=" (Parameter = as.factor(Parameter),
-             variable = as.factor(variable))]
+ data[, predator_id := as.factor(predator_id)]
+
+
+
+# Post processing preparations for custom family ---------------------------
+
[…]

### 2022-12-20 code/05_code_figures/05_figure2.R

@@ -1,6 +1,6 @@
 # =======================================================================
 
-#          Plot distribution of players from novice to advanced
+#                   Plot the coefficients of variation
 
 # =======================================================================
 
@@ -9,47 +9,35 @@
 
 
 # =======================================================================
-# 1. Prepare the script
+# 1. Import the libraries and data
 # =======================================================================
-
-
-# Load libraries and model ----------------------------------------------
 
  # Libraries
- library(brms)
  library(data.table)
  library(ggplot2)
  library(ggpubr)
- library(ggridges)
- 
- # import model
- #fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
- fit <- readRDS("./tests/02B_DHMLM.rds")
- 
 
+ # CV table
+ path <- "./outputs/04_outputs_model-processing"
+ tab <- readRDS(file.path(path, "04_CV-table.rds"))
+ 
+ # Rename the XP variable
+ tab[xp_level == "novice", xp_level := "Novice"]
+ tab[xp_level == "interm", xp_level := "Intermediate"]
+ tab[xp_level == "advanced", xp_level := "Advanced"]
+ 
+ # Rename the behaviour names
+ tab[variable == "pred_speed", variable := "Predator speed"]
+ tab[variable == "prey_speed", variable := "Prey speed"]
 
-# Load data ------------------------------------------------------------
+ # Reorder factors
+ tab[, xp_level := factor(xp_level, levels = c("Novice",
+                                               "Intermediate",
+                                               "Advanced"))]
  
- # Data
- data <- fread("./data/FraserFrancoetalXXXX-data.csv",
-               select = c("predator_id",
-                          "pred_game_mode",
-                          "total_xp_killer",
-                          "pred_speed"))
- 
- data <- data[pred_game_mode == "Online"]
- 
- # Extract standard deviation of speed
- sd_speed1 <- sd(data[total_xp_killer < 100]$pred_speed)
- sd_speed2 <- sd(data[total_xp_killer >= 300]$pred_speed)
-
- # Filter only for advanced players
- data <- data[total_xp_killer >= 300]
- 
- data <- unique(data)
- 
- # Predator id as factor
- data[, predator_id := as.factor(predator_id)]
+ # Encode Parameter and variable as factor
+ tab[, ":=" (Parameter = as.factor(Parameter),
+             variable = as.factor(variable))]
  
 # =======================================================================
 # =======================================================================
@@ -59,260 +47,126 @@
 
 
[…]

### 2022-12-20 code/05_code_figures/05_figure3.R

@@ -1,6 +1,6 @@
 # =======================================================================
 
-#                    Plot the full correlation matrix
+#          Plot distribution of players from novice to advanced
 
 # =======================================================================
 
@@ -9,127 +9,311 @@
 
 
 # =======================================================================
-# 1. Import data and libraries
+# 1. Prepare the script
 # =======================================================================
 
 
-# Load libraries and model data -----------------------------------------
+# Load libraries and model ----------------------------------------------
 
  # Libraries
  library(brms)
- library(corrplot)
- library(export)
-
- # Model
+ library(data.table)
+ library(ggplot2)
+ library(ggpubr)
+ library(ggridges)
+ 
+ # import model
  #fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
  fit <- readRDS("./tests/02B_DHMLM.rds")
  
+
+
+# Load data ------------------------------------------------------------
+ 
+ # Data
+ data <- fread("./data/FraserFrancoetalXXXX-data.csv",
+               select = c("predator_id",
+                          "pred_game_mode",
+                          "total_xp_killer",
+                          "pred_speed"))
+ 
+ data <- data[pred_game_mode == "Online"]
+ 
+ # Extract standard deviation of speed
+ sd_speed1 <- sd(data[total_xp_killer < 100]$pred_speed)
+ sd_speed2 <- sd(data[total_xp_killer >= 300]$pred_speed)
+
+ # Filter only for advanced players
+ data <- data[total_xp_killer >= 300]
+ 
+ data <- unique(data)
+ 
+ # Predator id as factor
+ data[, predator_id := as.factor(predator_id)]
+ 
 # =======================================================================
 # =======================================================================
- 
- 
- 
- 
- 
-# =======================================================================
-# 2. Prepare a matrix to plot
-# =======================================================================
- 
- 
-# Prepare the correlation matrix ----------------------------------------
- 
- # Extract the full object
- ar <- VarCorr(fit)
- 
- # Extract the covariances from the object
- cov <- ar$predator_id$cov
- 
- # Extract the covariance matrix
- vcovmat <- cov[,1,]
- 
- # Transform to correlation matrix
- cormat <- cov2cor(vcovmat)
 
 
 
-# Arrange the correlation matrix ----------------------------------------
- 
- # Change rownames
- rownames(cormat) <- c("mean speed", "IIV speed",
-                       "mean speed", "IIV speed",
-                       "mean speed", "IIV speed",
[…]

### 2022-12-20 code/05_code_figures/05_figure4.R

@@ -1,6 +1,6 @@
 # =======================================================================
 
-#                Plot the correlations between variables
+#                    Plot the full correlation matrix
 
 # =======================================================================
 
@@ -17,577 +17,119 @@
 
  # Libraries
  library(brms)
- library(data.table)
- library(ggplot2)
- library(ggpubr)
- 
+ library(corrplot)
+ library(export)
+
  # Model
  #fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
  fit <- readRDS("./tests/02B_DHMLM.rds")
  
- # ID table
- path <- "./outputs/04_outputs_model-processing"
- id_tab <- readRDS(file.path(path, "04_id-draws.rds"))
+# =======================================================================
+# =======================================================================
+ 
+ 
+ 
+ 
+ 
+# =======================================================================
+# 2. Prepare a matrix to plot
+# =======================================================================
+ 
+ 
+# Prepare the correlation matrix ----------------------------------------
+ 
+ # Extract the full object
+ ar <- VarCorr(fit)
+ 
+ # Extract the covariances from the object
+ cov <- ar$predator_id$cov
+ 
+ # Extract the covariance matrix
+ vcovmat <- cov[,1,]
+ 
+ # Transform to correlation matrix
+ cormat <- cov2cor(vcovmat)
+
+
+
+# Arrange the correlation matrix ----------------------------------------
+ 
+ # Change rownames
+ rownames(cormat) <- c("mean speed", "IIV speed",
+                       "mean speed", "IIV speed",
+                       "mean speed", "IIV speed",
+                       "mean prey speed", "IIV prey speed",
+                       "mean prey speed", "IIV prey speed",
+                       "mean prey speed", "IIV prey speed",
+                       "mean success",
+                       "mean success",
+                       "mean success")
+ 
+ # Change colnames
+ colnames(cormat) <- c("mean speed", "IIV speed",
+                       "mean speed", "IIV speed",
+                       "mean speed", "IIV speed",
+                       "mean prey speed", "IIV prey speed",
+                       "mean prey speed", "IIV prey speed",
+                       "mean prey speed", "IIV prey speed",
+                       "mean success",
+                       "mean success",
+                       "mean success")
+
+ # Reorder by XP level in order
+ cormat_ord <- cormat[c(1, 2, 7, 8, 13,
+                        3, 4, 9, 10, 14,
+                        5, 6, 11, 12, 15),
[…]

### 2022-12-20 code/05_code_figures/05_figure5.R

@@ -1,0 +1,593 @@
+# =======================================================================
+
+#                Plot the correlations between variables
+
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 1. Import data and libraries
+# =======================================================================
+
+
+# Load libraries and model data -----------------------------------------
+
+ # Libraries
+ library(brms)
+ library(data.table)
+ library(ggplot2)
+ library(ggpubr)
+ 
+ # Model
+ #fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
+ fit <- readRDS("./tests/02B_DHMLM.rds")
+ 
+ # ID table
+ path <- "./outputs/04_outputs_model-processing"
+ id_tab <- readRDS(file.path(path, "04_id-draws.rds"))
+ 
+
+
+# Load raw data ---------------------------------------------------------
+
+ # Data
+ data <- fread("./data/FraserFrancoetalXXXX-data.csv",
+               select = c("predator_id",
+                          "pred_game_mode",
+                          "pred_game_duration",
+                          "pred_speed",
+                          "prey_avg_speed",
+                          "cumul_xp_killer",
+                          "total_xp_killer",
+                          "hunting_success"))
+ 
+ data <- unique(data)
+ data <- data[pred_game_mode == "Online"]
+
+ # Calculate total xp
+ data[total_xp_killer < 100,
+      xp_level := "novice"]
+ 
+ data[total_xp_killer %between% c(100, 299),
+      xp_level := "interm"]
+ 
+ data[total_xp_killer > 300,
+      xp_level := "advanced"]
+
+ # Encode variables as a factor
+ data[, xp_level := as.factor(xp_level)]
+ data[, predator_id := as.factor(predator_id)]
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 3. Custom theme for plots
+# =======================================================================
+
+ # Custom plot theme
+ custom_theme <- theme(# axis values size
+                       axis.text.x = element_text(face = "plain", 
+                                                  size = 15,
+                                                  color = "black"),
[…]

### 2022-12-20 code/05_code_figures/05_figureS1.R

@@ -1,256 +1,0 @@
-# ==========================================================================
-
-#                          Plot 02A1 GAMM model
-
-# ==========================================================================
-
-
-
-# ==========================================================================
-# 1. Prepare script
-# ==========================================================================
-
-
-
-# Load libraries and model -------------------------------------------------
-
- library(brms)
- library(data.table)
- library(ggplot2)
- library(ggpubr)
- 
- path <- file.path(getwd(), "outputs", "02_outputs_models")
-
- mod1 <- readRDS(file.path(path, "02A1_GAMM.rds"))
- mod4 <- readRDS(file.path(path, "02A4_GAMM.rds"))
- mod7 <- readRDS(file.path(path, "02A7_GAMM.rds"))
-
-
- 
-# Load the data ------------------------------------------------------------
-
- data <- fread("./data/FraserFrancoetalXXXX-data.csv",
-               select = c("predator_id",
-                          "game_duration",
-                          "pred_speed",
-                          "prey_avg_speed",
-                          "cumul_xp_pred",
-                          "total_xp_pred",
-                          "hunting_success",
-                          "latency_1st_capture",
-                          "chase_count",
-                          "chase_count_success"))
- 
- data[, predator_id := as.factor(predator_id)]
-
-
-
-# Post processing preparations for custom family ---------------------------
-
- expose_functions(mod1, vectorize = TRUE)
- 
- # Define the log likelihood function
- log_lik_beta_binomial2 <- function(i, prep) {
-   mu <- brms::get_dpar(prep, "mu", i = i)
-   phi <- brms::get_dpar(prep, "phi", i = i)
-   trials <- prep$data$vint1[i]
-   y <- prep$data$Y[i]
-   beta_binomial2_lpmf(y, mu, phi, trials)
- }
- 
- # Define function for posterior_predict
- posterior_predict_beta_binomial2 <- function(i, prep, ...) {
-   mu <- brms::get_dpar(prep, "mu", i = i)
-   phi <- brms::get_dpar(prep, "phi", i = i)
-   trials <- prep$data$vint1[i]
-   beta_binomial2_rng(mu, phi, trials)
- }
- 
- # Define function for posterior_epred
- posterior_epred_beta_binomial2 <- function(prep) {
-   mu <- brms::get_dpar(prep, "mu")
-   trials <- prep$data$vint1
-   trials <- matrix(trials, nrow = nrow(mu), ncol = ncol(mu), byrow = TRUE)
-   mu * trials
- }
-
-
-
[…]

### 2022-12-20 code/05_code_figures/05_figure5.R
renamed table files and moved figure 5 to dump

@@ -1,593 +1,0 @@
-# =======================================================================
-
-#                Plot the correlations between variables
-
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 1. Import data and libraries
-# =======================================================================
-
-
-# Load libraries and model data -----------------------------------------
-
- # Libraries
- library(brms)
- library(data.table)
- library(ggplot2)
- library(ggpubr)
- 
- # Model
- #fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
- fit <- readRDS("./tests/02B_DHMLM.rds")
- 
- # ID table
- path <- "./outputs/04_outputs_model-processing"
- id_tab <- readRDS(file.path(path, "04_id-draws.rds"))
- 
-
-
-# Load raw data ---------------------------------------------------------
-
- # Data
- data <- fread("./data/FraserFrancoetalXXXX-data.csv",
-               select = c("predator_id",
-                          "pred_game_mode",
-                          "pred_game_duration",
-                          "pred_speed",
-                          "prey_avg_speed",
-                          "cumul_xp_killer",
-                          "total_xp_killer",
-                          "hunting_success"))
- 
- data <- unique(data)
- data <- data[pred_game_mode == "Online"]
-
- # Calculate total xp
- data[total_xp_killer < 100,
-      xp_level := "novice"]
- 
- data[total_xp_killer %between% c(100, 299),
-      xp_level := "interm"]
- 
- data[total_xp_killer > 300,
-      xp_level := "advanced"]
-
- # Encode variables as a factor
- data[, xp_level := as.factor(xp_level)]
- data[, predator_id := as.factor(predator_id)]
-
-# =======================================================================
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 3. Custom theme for plots
-# =======================================================================
-
- # Custom plot theme
- custom_theme <- theme(# axis values size
-                       axis.text.x = element_text(face = "plain", 
-                                                  size = 15,
-                                                  color = "black"),
-                       axis.text.y = element_text(face = "plain", 
[…]

### 2022-12-20 code/05_code_tables/05_tableS1.R

@@ -20,7 +20,8 @@ library(dplyr)
 
 # Import the model
 path <- file.path("./outputs/02_outputs_models")
-mod1 <- readRDS(file.path(path, "02A1_GAMM.rds"))
+mod1 <- readRDS(file.path(path, "02A3_GAMM.rds"))
+mod2 <- readRDS(file.path(path, "02A3_prey-GAMM.rds"))
 
 # ===========================================================================
 # ===========================================================================

### 2022-12-20 manuscript/Chapter2-manuscript.Rmd
updated introduction based on Clint's comments

@@
 path <- file.path(here::here(), "data")
-dat <- fread(file.path(path, "FraserFrancoetalXXXX-data.csv"),
-             select = c("pred_timestamp", "match_encode_id", "pred_game_mode",
-                        "realm_id", "environment_id", "predator_avatar_id",
-                        "predator_id", "pred_game_duration",
-                        "total_xp_killer", "cumul_xp_killer", "hunting_success",
-                        "pred_speed", "prey_avg_speed"))
 
-dat <- unique(dat)
-dat <- dat[pred_game_mode == "Online"]
-dat[, c(2:7) := lapply(.SD, function (x) as.factor(x)), .SDcols = c(2:7)]
+dat <- fread(
+  file.path(path, "FraserFrancoetalXXXX-data.csv"),
+  select = c("timestamp", "match_id", "realm_id",
+             "environment_id", "avatar_id", "predator_id",
+             "game_duration", "total_xp_pred", "cumul_xp_pred",
+             "hunting_success", "pred_speed", "prey_avg_speed"))
+
+dat[, c(2:6) := lapply(.SD, function (x) as.factor(x)), .SDcols = c(2:6)]
 
 # To have a date column
-dat[, date := as.POSIXct(sub(" .*", "", pred_timestamp))]
+dat[, date := as.POSIXct(sub(" .*", "", timestamp))]
 
@@
 
-Keywords: foraging behavior, individual specialization, experience, learning, prey predictability, online videogames
+Keywords: foraging behaviour, individual specialization, experience, learning, prey predictability, online videogames
 
@@
 
-Individual variation in predator foraging behavior is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations are often composed of assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
+Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
+Indeed, predator populations often comprise assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
 A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can be major drivers of such individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
@@
 experience).
-While the development of hunting experience may be essential to maintain foraging success, we have have limited evidence for its role in predator foraging specialization, and the ecological/fitness consequences of such among individual behavioral differences for predator-prey interactions [@Dukas2019].
+While hunting experience may be essential to maintain or improve foraging success, we have have limited evidence for either its role in predator foraging specialization or the ecological/fitness consequences of such among individual behavioural differences on predator-prey interactions [@Dukas2019].
 
-The integration of individual behavioral variation in the study of predator-prey interactions has gained traction in recent years, with empirical studies revealing important consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
-However, an important and recurring challenge impeding research on predator-prey behavioral interactions, at the individual level, is the need of collecting data simultaneously on both the predator and prey.
-We have recently demonstrated with behavioral data from an online predator-prey videogame that virtual systems can help in overcoming this challenge, and uncover details on the mechanisms shaping these interactions [@FraserFranco.etal2022].
-For instance, we tested the classical locomotor crossover hypothesis championed by @Huey.Pianka1981, and found support of its predictions only for active hunters, which concords with a recent experiment involving assassin bugs [@Matsumura.Miyatake2022a].
-Thus, virtual systems may be useful in identifying general ecological patterns, which may in turn help in advancing the current gaps in predator-prey research.
+The integration of individual behavioural variation in the study of predator-prey interactions has gained traction in recent years, with empirical studies revealing important consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
+However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
+We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge, and uncover details of the mechanisms shaping these interactions [@FraserFranco.etal2022].
+For instance, we found that the classical locomotor crossover hypothesis [@Huey.Pianka1981] applied only for cursorial hunters [see also: @Matsumura.Miyatake2022a], suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
 Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
 in prep).
-Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behavior on individual predator foraging specialization along with its potential fitness consequences.
+Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with its potential fitness consequences.
 
@@
 
-There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging.
-Importantly, we have limited information on the ecological contexts - except for competition - that favor one strategy over the other.
+There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging (REFERENCES).
+Importantly, we have limited information on the ecological contexts - except for competition - that favour one strategy over the other.
 This is reflected in the literature showing contrasting results in the links between specialization and fitness.
-For instance, some studies report increasing benefits of specializing [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
+For instance, some studies report increasing benefits of specialization [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
 While quantifying the fitness consequences of specialization is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
-The resource-predictability hypothesis advances that when resources are predictable, individual specialists should have higher delivery rates by reducing the energy and time required to search for and handle prey.
-In contrast, individual generalists should be advantaged when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-This hypothesis has however not been tested in systems where behavioral interactions are simultaneously monitored between predator and prey individuals.
+The resource-predictability hypothesis argues that when resources are predictable, individual specialists should have higher delivery rates by reducing the energy and time required to search for and handle prey.
+In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
+This hypothesis has, however, not been tested in systems where behavioural interactions are simultaneously monitored between predator and prey individuals.
 
-In this study, we analyze individual behavioral data from players in *Dead by Daylight* (*DBD*) to test how hunting expertise and prey behavior shape predator foraging specialization.
+In this study, we analyze individual behavioural data from players in *Dead by Daylight* (*DBD*) to test how hunting expertise and prey behaviour shape predator foraging specialization.
 *DBD* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
-The data grants a high degree of precision on the behavioral interaction as both the predator and the four prey are measured simultaneously in each trial.
+The data grants a high degree of precision on the behavioural interaction as both the predator and the four prey are measured simultaneously in each trial.
 First, we investigate how predators developed their individual hunting expertise.
-We hypothesize that predators should differ in the development of their expertise because they encounter varying levels of difficulty with the prey that they hunt.
-Second, we test the hypothesis that individual variation in foraging behavior will change with experience.
+We hypothesize that predators should differ in the development of their expertise because they encounter varying levels of difficulty with the prey that they pursue.
+Second, we test the hypothesis that individual variation in foraging behaviour will change with experience.
 If experience reduces the costs of switching between hunting tactics, we predict that individual predators should become more flexible with time.
 Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize.
-Third, we evaluate how predator foraging specialization interacts with variation in prey behavior.
-Whether predators specialize or not with experience may depend on the behavior of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
+Third, we evaluate how predator foraging specialization interacts with variation in prey behaviour.
+Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
 Lastly, if individuals differ in their degree of foraging specialization, then we expect specialist hunters to fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
@@
 
-*DBD* is a survival horror asymmetric multiplayer online game developed by Behavior Interactive Inc.
-In this game, players get to chose if they wish to play has a predator or a prey.
-The objective of the predator player is to hunt and capture the four prey players across a virtual environment.
+*DBD* is a survival asymmetric multiplayer online game developed by Behaviour Interactive Inc.
+In this game, players get to choose if they wish to play as a predator or a prey.
+The objective of the predator-player is to hunt and capture the four prey players across a virtual environment.
 The objective of the four prey players is to forage for resources while avoiding the predator.
-The resources are in the form of power generators that once activated, will enable the prey to escape through one of two exit doors.
+The resources are in the form of power generators that, once activated, will enable the prey to escape through one of two exit doors.
 The composition of the predator and prey group for a match is determined by a skill-based matchmaking algorithm.
 A match ends when the predator kills all the prey available (i.e.
-that haven't escaped), or when the last remaining prey escapes the virtual environment.
-Each player, predator or prey, can chose an avatar with abilities that encourage specific play styles (e.g.
-bolder vs cautious prey, or ambush vs roaming predator).
+that have not escaped), or when the last remaining prey escapes the virtual environment.
+Each player, predator or prey, can choose an avatar with abilities that encourage specific play styles (e.g.
+bold vs cautious prey, or ambush vs roaming predator).
 During our study period, the game offered 23 playable predator avatars.
@@
 Some of these environments are larger than others, with varying structural complexity.
-However, we have previously shown that predators display only minimal changes in behavior and hunting success across the environments, probably due to a game feature enabling predators to have visual cues on the generators [@FraserFranco.etal2022].
-There were 35 virtual game environments available for play during our study period.
+However, we have previously shown that predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling predators to have visual cues of the generators [@FraserFranco.etal2022].
+There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during our study period.
 
@@
 They also display flexibility in the use of these tactics by switching between them across matches.
-The expression of these tactics and their success is also shaped by the behavior of the prey group.
-The prey need to forage for resources while maintaining a high level of attention on the predator cues to avoid being detected and chased.
-Some prey contribute to the group's success by healing or helping others escape the predator, while other self-centered individuals play alone and attempt to escape by themselves [@Cere.etal2021].
-Predators must be wary of how the prey behave to chose the right way to capture them.
-Thus, *DBD* simulates a highly dynamic system where both predators and prey must constantly adapt to each other to be successful.
+The expression of these tactics and their success is also shaped by the behaviour of the prey group.
+The prey need to forage for resources while paying attention to the predator to avoid being detected and chased.
+Some prey contribute to the group's success by healing or helping others escape the predator, while others play alone and attempt to escape by themselves [@Cere.etal2021].
+Predators must be wary of how the prey behave to choose the right way to capture them.
+Thus, *DBD* simulates a highly dynamic system where both predators and prey must constantly adjust to each other to be successful.
 
@@
 
-We were provided raw data by the videogame company that spanned a period of 6 months of gameplay recorded for every player.
+The videogame company provided data that spanned a period of 6 months of gameplay recorded for every player.
 The first recorded match was played on `r toString(format(min(dat$date)))`, and the last one on `r toString(format(max(dat$date)))`.
-We applied cleaning and filtering procedures on the raw data to produce a synthetic dataset for our analyses.
-We only analyzed matches where players did not know each other (i.e.
+We cleaned and filtered the raw data to produce a dataset appropriate for our analyses.
+We analyzed only matches where players did not know each other (i.e.
 "Online" mode).
@@
 Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game has it is supposed to be played.
-These matches were not considered as player experience.
-We then proceeded to partition the player population by total experience, and randomly sampled players to have a uniform representation of total gameplay experience.
-To optimize the representation of gameplay experience at advanced levels, we set the maximum amount of matches at 500 for these players.
+We then partitioned the player population by total experience, and sampled players that played 300 matches or more.
+To optimize the representation of gameplay experience at advanced levels, we set the maximum number of matches at 500 for these players.
 For instance, there could be a large difference in gameplay between 300-500 and 500-1000 matches.
@@
 
-Our population consists of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(format(length(unique(dat$match_encode_id))))` matches.
-The predator players' experience varied between `r toString(format(min(dat$total_xp_killer)))` and `r toString(format(max(dat$total_xp_killer)))` matches played.
-These matches lasted between `r toString(format(round(min(dat$pred_game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$pred_game_duration / 60))), digits = 2)` minutes (mean = `r toString(format(round(mean(dat$pred_game_duration / 60))), digits = 2)`).
-The following information is collected and reported for every match : the player's anonymous ID, its avatar, the game environment, the predator player's experience along with its speed, and the average speed of the group of prey it encountered.
+Our population consists of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(formatC(length(unique(dat$match_id)), big.mark = " "))` matches.
+The predator-players' experience varied between `r toString(format(min(dat$total_xp_pred)))` and `r toString(format(max(dat$total_xp_pred)))` matches played.
+These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)` minutes (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)` minutes).
+The following information is collected and reported for every match : the player's anonymous ID, its avatar, the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.
 
@@
 We analyzed the predator's average speed and the average speed of the prey encountered by the predator.
-The predator's average speed is measured as the average distance per second traveled during a match (m/s) (mean = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))`, sd = `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`).
-For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group, also measured in meters per second (mean = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`, sd = mean = `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`).
+The predator's average speed is measured as the average distance per second traveled during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`).
+For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group ($\overline{x}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`).
 Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
@@
 
-We tested whether predators varied in the development of their expertise by computing 3 Bayesian generalized additive mixed models (GAMM) with thin plate regression splines estimating the relationship between hunting success (i.e.
+*ajouter la description sur les autres variables de performance*
+
+We tested whether predators varied in the development of their expertise using three Bayesian generalized additive mixed models (GAMM) with thin plate regression splines.
+These models estimate the relationship between hunting success (i.e.
 number of prey captured) and the predators' cumulative experience (i.e.
 number of matches played before the current match).
-We parametrized the models following the method by @Pedersen.etal2019.
+We parametrized the models following the method of @Pedersen.etal2019.
 The first model was the simplest, with a common global smoothing function for all observations and random intercepts for the predator ID.
@@
 Thus, this model assumes that predators do not share a common relationship between success and experience.
-For all three models, we controlled for the match duration.
+We included match duration as a covariate in all three models.
 
-Because a maximum of four prey can be captured in the game, and to control for overdispersion, we computed the three models using a modified version of the beta-binomial distribution implemented in "brms" (for an overview, see https://paul-buerkner.github.io/brms/articles/brms_customfamilies.html).
-Thus, hunting success was estimated as the probability of capturing the four prey ($p_i$), drawn from a Beta distribution ($p_i \sim Beta(\mu_i, \phi) = Beta(\alpha = \mu\phi, \beta = (1 - \mu)\phi)$) with mean ($\mu \in [0,1]$) and shape ($\phi > 0$) parameters.
-We employed a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the shape parameter ($\phi$) was estimated with an identity link for all models.
+Because a maximum of four prey can be captured in the game, and to control for overdispersion, we computed the three models using a modified version of the beta-binomial distribution implemented in "brms".
+Thus, hunting success was estimated as the probability of capturing the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
+We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link for all models.
 
-We employed the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
+We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
 We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated variance ($id \sim N(0,\ I\ \sigma^2_{id})$).
-We parametrized all models to run 4 MCMC chains with 1000 posterior samples for each parameter.
-To do so, we ran 2500 iterations for the first model with a thinning set to 8, and 1500 iterations with a thinning set to 4 for the second and third models.
-The first 500 iterations were used as warmups.
-We provide a description on how we specified the priors for each model in the supporting information.
-After fitting the 3 models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017].
+We defined all models to run four MCMC chains with 1000 posterior samples for each parameter.
+To do so, we ran 2500 iterations for the first model with a thinning set to eight, and 1500 iterations with a thinning set to four for the second and third models; burn-in was set to 500 iterations in each model.
+We provide a description of how we specified the priors for each model in the supporting information.
+After fitting the three models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
 
@@
 
-### Foraging behavior and success, prey behavior, and their relationships, at each level of experience
+### Foraging behaviour and success, prey behaviour, and their relationships, at each level of experience
 
-We proceeded to test whether foraging behavior changes with experience, and compare the success of generalists vs specialists, using a multivariate double hierarchical generalized linear model (MDHGLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
-We categorized the predators by their experience using the predicted values from the GAMM (see Figure S1 in the supporting information).
-We assigned the status of "novice" to any predator player that had a cumulative experience below 100 matches.
+We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
+We categorized the predators by their experience based on the predicted values from the GAMM (see Figure S1 in the supporting information).
+We assigned the status of "novice" to any predator-player that had a cumulative experience below 100 matches.
 For example, a predator player that played 500 matches in total would be labelled as a novice in its first 100 matches.
@@
 For each level of experience (i.e.
-novice, intermediate, advanced), we estimated the mean speed of individual predators, and an heterogeneous structure of the residuals such that we could estimate their intra individual variance (IIV) in speed (i.e.
+novice, intermediate, advanced), we estimated the mean speed of individual predators, and a heterogeneous structure of the residuals such that we could estimate their intra-individual variance (IIV) in speed (i.e.
 specialization).
@@
 The first two equations were parametrized with a Gaussian distribution family, while the third equation was parametrized with a beta-binomial distribution family.
-We parametrized the model to run 4 MCMC chains with 1000 posterior samples for each parameter.
+We parametrized the model to run four MCMC chains with 1000 posterior samples for each parameter.
 To do so, we ran 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups.
@@
 $cor(\sigma^2_{id_{m}\ pred\ novice}\ \sigma^2_{id_{d}\ pred\ intermediate})$).
-The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviors across each developmental stage.
+The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each developmental stage.
 The correlations were estimated using a multivariate Gaussian distribution.
@@
 
-## Effect of experience on the development of behavioral specialization
+## Effect of experience on the development of behavioural specialization
 
 ```{r fig1, out.width = "100%", fig.cap = "**Figure 1.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience.
-(A) Coefficient of variation for the among individual differences in average behavior.
+(A) Coefficient of variation for the among individual differences in average behaviour.
 (B) Coefficient fo variation for the among individual differences in intra individual variance (i.e.
@@
 
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Distribution of the intra individual behavioral variation (i.e.
+```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Distribution of the intra individual behavioural variation (i.e.
 specialization) of predators when they were (A) novices and (B) advanced.
@@
 
-## Relationship between behavioral specialization and prey variability
+## Relationship between behavioural specialization and prey variability
 
@@
 
-## Hunting success of behavioral specialists vs generalists
+## Hunting success of behavioural specialists vs generalists
 

### 2022-12-20 code/04_code_model-processing/04_CV-table.R
run CV table

@@ -24,25 +24,21 @@
  # Data
  data <- fread("./data/FraserFrancoetalXXXX-data.csv",
                select = c("predator_id",
-                          "pred_game_mode",
-                          "pred_game_duration",
+                          "game_duration",
                           "pred_speed",
                           "prey_avg_speed",
-                          "cumul_xp_killer",
-                          "total_xp_killer",
+                          "cumul_xp_pred",
+                          "total_xp_pred",
                           "hunting_success"))
  
- data <- unique(data)
- data <- data[pred_game_mode == "Online"]
- 
  # Experience column
- data[cumul_xp_killer < 100,
+ data[cumul_xp_pred < 100,
       xp_level := "novice"]
  
- data[cumul_xp_killer %between% c(100, 299),
+ data[cumul_xp_pred %between% c(100, 299),
       xp_level := "intermediate"]
  
- data[cumul_xp_killer >= 300,
+ data[cumul_xp_pred >= 300,
       xp_level := "advanced"]
  
  # Encode variables as a factor
@@ -54,8 +50,8 @@
 # Load model output -----------------------------------------------------
  
  # Model object
- fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
- fit <- readRDS("./tests/02B_DHMLM.rds")
+ path <- file.path(getwd(), "outputs", "02_outputs_models")
+ fit <- readRDS(file.path(path, "02B_DHMLM.rds"))
 
  # Extract draws for sd of mu and sigma
  draws <- data.table(
@@ -117,7 +113,6 @@
  table[Parameter == "mu", value := value^2]
  table[Parameter == "sigma", value := exp(value^2)]
  
-
 # =======================================================================
 # =======================================================================
 
@@ -211,16 +206,16 @@
 
  cv_tab <- unique(cv_tab[, c(1:3, 5:7)])
 
-# Round values to 3 digits
-cv_tab[, c(4:6) := lapply(.SD, function (x) {round(x, digits = 3)}),
-         .SDcols = c(4:6)]
+ # Round values to 3 digits
+ cv_tab[, c(4:6) := lapply(.SD, function (x) {round(x, digits = 3)}),
+          .SDcols = c(4:6)]
 
 
 
 # Save the table --------------------------------------------------------
 
-path <- "./outputs/04_outputs_model-processing"
-saveRDS(cv_tab, file = file.path(path, "04_CV-table.rds"))
+ path <- file.path(getwd(),"outputs", "04_outputs_model-processing")
[…]

### 2022-12-20 code/04_code_model-processing/04_id-draws.R
update id draws

@@ -17,31 +17,27 @@
  library(data.table)
  
  # import model
+ path<- file.path(getwd(), "outputs", "02_outputs_models")
  fit <- readRDS("./outputs/02_outputs_models/02B_DHMLM.rds")
- fit <- readRDS("./tests/02B_DHMLM.rds")
  
  # Load data
  data <- fread("./data/FraserFrancoetalXXXX-data.csv",
                select = c("predator_id",
-                          "pred_game_mode",
-                          "pred_game_duration",
+                          "game_duration",
                           "pred_speed",
                           "prey_avg_speed",
-                          "cumul_xp_killer",
-                          "total_xp_killer",
+                          "cumul_xp_pred",
+                          "total_xp_pred",
                           "hunting_success"))
  
- data <- unique(data)
- data <- data[pred_game_mode == "Online"]
- 
  # Experience column
- data[cumul_xp_killer < 100,
+ data[cumul_xp_pred < 100,
       xp_level := "novice"]
  
- data[cumul_xp_killer %between% c(100, 299),
+ data[cumul_xp_pred %between% c(100, 299),
       xp_level := "intermediate"]
  
- data[cumul_xp_killer >= 300,
+ data[cumul_xp_pred >= 300,
       xp_level := "advanced"]
  
  # Encode variables as a factor
@@ -118,10 +114,10 @@
 # Save the table --------------------------------------------------------
 
  # Path
- path <- "./outputs/04_outputs_model-processing"
+ path1 <- file.path("outputs", "04_outputs_model-processing")
 
  # Save
- saveRDS(draws, file = file.path(path, "04_id-draws.rds"))
+ saveRDS(draws, file = file.path(path1, "04_id-draws.rds"))
 
 # =======================================================================
 # =======================================================================

### 2022-12-22 code/05_code_figures/05_figure1.R
update figures code and outputs

@@ -79,27 +79,24 @@
 # Setup a custom theme for the plot ----------------------------------------
  
  custom_theme <- theme(
-   # axis values size
-   axis.text.x = element_text(face = "plain", 
-                              size = 12,
-                              color = "black"),
-   axis.text.y = element_text(face = "plain", 
-                              size = 12,
-                              color = "black"),
-   # axis ticks lenght
-   axis.ticks.length = unit(.15, "cm"),
-   # axis ticks width
-   axis.ticks = element_line(size = 0.90, 
+    # axis values size
+    axis.text = element_text(face = "plain", 
+                             size = 14,
                              color = "black"),
-   # axis titles size
-   axis.title = element_text(size = 14, 
-                             face = "plain",
+    # axis ticks lenght
+    axis.ticks.length = unit(.15, "cm"),
+    # axis ticks width
+    axis.ticks = element_line(size = 0.90, 
+                              color = "black"),
+    # axis titles size
+    axis.title = element_text(size = 16, 
+                              face = "plain",
+                              color = "black"),
+    axis.line = element_line(size = 0.95,
                              color = "black"),
-   axis.line = element_line(size = 0.95,
-                            color = "black"),
-   legend.position = "none",
-   panel.grid = element_blank(),
-   panel.background = element_blank()
+    legend.position = "none",
+    panel.grid = element_blank(),
+    panel.background = element_blank()
  )
 
 # ==========================================================================
@@ -152,12 +149,12 @@
                           color = predator_id)) +
     geom_line(size = 1) +
     scale_color_viridis(discrete = TRUE, option = "D") + #B
-    ylab("Hunting success") +
+    ylab("Hunting success\n") +
     scale_y_continuous(breaks = seq(0, 1, 0.25),
                        limits = c(0, 1)) +
     scale_x_continuous(breaks = scaled_breaks,
                        labels = seq(0, 500, 100)) +
-    xlab("Cumulative experience") +
+    xlab("\nCumulative experience") +
     custom_theme
  
  gamm_plot2 <- ggplot(tab2,
@@ -165,12 +162,12 @@
                           y = plogis(estimate__),
                           color = predator_id)) +
     geom_line(size = 1) +
-    ylab("Hunting success") +
+    ylab("Hunting success\n") +
     scale_y_continuous(breaks = seq(0, 1, 0.25),
                        limits = c(0, 1)) +
     scale_x_continuous(breaks = scaled_breaks,
                        labels = seq(0, 500, 100)) +
[…]

### 2022-12-22 code/05_code_figures/05_figure2.R

@@ -53,27 +53,26 @@
 
 # Set custom theme -----------------------------------------------------
 
- custom_theme <- theme(# axis values size
-                       axis.text.x = element_text(face = "plain", 
-                                                  size = 15,
-                                                  color = "black"),
-                       axis.text.y = element_text(face = "plain", 
-                                                  size = 15,
-                                                  color = "black"),
-                       # axis ticks lenght
-                       axis.ticks.length = unit(.15, "cm"),
-                       # axis ticks width
-                       axis.ticks = element_line(size = 0.90, 
-                                                 color = "black"),
-                       # axis titles size
-                       axis.title = element_text(size = 17, 
-                                                 face = "plain",
-                                                 color = "black"),
-                       axis.line = element_line(size = 0.95,
-                                                color = "black"),
-                       panel.grid = element_blank(),
-                       panel.background = element_blank())
-
+ custom_theme <- theme(
+    # axis values size
+    axis.text = element_text(face = "plain", 
+                             size = 12,
+                             color = "black"),
+    # axis ticks lenght
+    axis.ticks.length = unit(.15, "cm"),
+    # axis ticks width
+    axis.ticks = element_line(size = 0.90, 
+                              color = "black"),
+    # axis titles size
+    axis.title = element_text(size = 14, 
+                              face = "plain",
+                              color = "black"),
+    axis.line = element_line(size = 0.95,
+                             color = "black"),
+    panel.grid = element_blank(),
+    panel.background = element_blank()
+ )
+ 
 # =======================================================================
 # =======================================================================
 
@@ -98,9 +97,9 @@
                      size = 0.8,
                      position = position_dodge(width = 0.3)) +
  
-     scale_shape_manual(name = "Total experience :",
+     scale_shape_manual(name = "Experience level :",
                          values = c(15, 16, 17)) +
-     scale_color_manual(name = "Total experience :",
+     scale_color_manual(name = "Experience level :",
                         values = c("#999999", "#E69F00", "#00AFBB")) +
      
      scale_y_continuous(breaks = seq(0.1, 0.6, 0.1),
@@ -130,9 +129,9 @@
                      size = 0.8,
                      position = position_dodge(width = 0.3)) +
  
-     scale_shape_manual(name = "Total experience :",
+     scale_shape_manual(name = "Experience level :",
                          values = c(15, 16, 17)) +
[…]

### 2022-12-22 code/05_code_figures/05_figure3.R

@@ -137,7 +137,7 @@ draws <- draws[, average_speed_sigma := mean(exp_speed_sigma),
 
  custom_theme <- theme(# axis values size
                         axis.text.x = element_text(face = "plain", 
-                                                   size = 12,
+                                                   size = 14,
                                                    color = "black"),
                         axis.text.y = element_text(face = "plain", 
                                                    size = 5,
@@ -148,7 +148,7 @@ draws <- draws[, average_speed_sigma := mean(exp_speed_sigma),
                         axis.ticks = element_line(size = 0.90, 
                                                   color = "black"),
                         # axis titles size
-                        axis.title = element_text(size = 14, 
+                        axis.title = element_text(size = 16, 
                                                   face = "plain",
                                                   color = "black"),
                         axis.line = element_line(size = 0.95,
@@ -203,7 +203,7 @@ draws <- draws[, average_speed_sigma := mean(exp_speed_sigma),
      #                   limits = c(0, 4)) +
      
      ylab("Predator ID\n") +
-     xlab("\nIntra individual standard deviation (m/s)") +
+     xlab("\nIntra individual SD (m/s)") +
      labs(title = "Novice \nIntercept = 0.273 (0.260, 0.288)") +
      
      custom_theme +
@@ -265,7 +265,7 @@ draws <- draws[, average_speed_sigma := mean(exp_speed_sigma),
      #                                       name = "Within individual variance (m/s)\n")) +
  
      ylab("Predator ID\n") +
-     xlab("\nIntra individual standard deviation (m/s)") +
+     xlab("\nIntra individual SD (m/s)") +
      labs(title = "Advanced \nIntercept = 0.282 (0.267, 0.299)") +
  
      custom_theme +
@@ -298,8 +298,8 @@ draws <- draws[, average_speed_sigma := mean(exp_speed_sigma),
  # Save figure
  ggexport(figure,
           filename = file.path(path, "05_figure3.png"),
-          width = 3500,
-          height = 1800,
+          width = 2500,
+          height = 1600,
           res = 300)
 
 # =======================================================================

### 2022-12-22 manuscript/Chapter2-manuscript.Rmd
update ms version (V2) including results

@@
 library(officer)
+library(tidyr)
 
@@
 
-*ajouter la description sur les autres variables de performance*
-
 We tested whether predators varied in the development of their expertise using three Bayesian generalized additive mixed models (GAMM) with thin plate regression splines.
@@
 We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
-We categorized the predators by their experience based on the predicted values from the GAMM (see Figure S1 in the supporting information).
+We categorized the predators by their experience based on the number of matches they played (i.e.
+their cumulative experience).
 We assigned the status of "novice" to any predator-player that had a cumulative experience below 100 matches.
@@
 Following this logic, we labelled predators as "intermediate" hunters when they had a cumulative experience between 100 and 299 and matches.
-For the third and last group, we defined predators as "advanced" hunters when they had a cumulative experience equal or above 300, with a maximum of 499 matches.
+For the third and last group, we defined predators as "advanced" hunters when they had a cumulative experience equal or above 300, with a maximum of 499 cumulated matches.
 
@@
 The variance parameters $\sigma^2_{env}$, $\sigma^2_{av}$, and $\sigma^2_{id}$, correspond to the among environment, among avatar, and among individual variances, respectively.
-$I$ is the identity matrix, with $I,\ \sigma^2$ indicating that the random effects are independently and identically distributed.
+$I$ is the identity matrix, with $I\sigma^2$ indicating that the random effects are independently and identically distributed.
 The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively.
-The first two equations were parametrized with a Gaussian distribution family, while the third equation was parametrized with a beta-binomial distribution family.
+Equations (1) and (2) were parametrized with a Gaussian distribution family (predator and prey speed), while equation (3) was parametrized with a beta-binomial distribution family (predator hunting success).
 We parametrized the model to run four MCMC chains with 1000 posterior samples for each parameter.
 To do so, we ran 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups.
-We explain how we specified the priors for the MDHGLM in the supporting information.
+We explain how we specified the priors of the MDHGLM in the supporting information.
 
@@
 
-Contrary to our predictions, individual predators did not differ in the development of their expertise, as the best model was the one with a global smoother with varying intercepts only (Table S1 in the supporting information).
-The model detected only a weak relationship between hunting success and experience (i.e.
-the cumulative amount of matches played), such that players did not substantially optimize their success with increasing experience as we expected (Table 1 and Figure S1 in the supporting information).
-However, predators did differ in their average hunting success across the study period (Figure S1).
-*peut être coder un autre modèle où je contrôle pour les proies afin de voir si les différences de succès disparaissent*
+Our results confirm that individual predators displayed important differences in the development of their expertise, as the best model was the one with group-level smoothers exclusively (Table I).
+For instance, some predators steadily increased their hunting success with experience, while others maintained either a high or low success across their experience (Figure 1A).
+Moreover, some individuals show a decrease in hunting success with experience.
+Another pattern that emerged was that some individuals optimized their success at an experience level that was below what we considered as "advanced" (i.e.
+>300 matches played).
 
@@
 
-tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table2.rds"))
+tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))
+
+tab1 <- autofit(tab1)
+
+tab1 <- tab1 %>% 
+  footnote(
+    i = 1, j = 1,
+    part = "header",
+    value = as_paragraph(
+      "* 'elpd' refers to the 'expected log pointwise density' and is the value chosen to select the best model"),
+    ref_symbols = " "
+  ) %>%
+  fontsize(size = 11, part = "all") %>%
+  font(fontname = "Times New Roman", part = "all")
 
@@
   tab1,
-  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother. The values are presented on the logit scale.",
+  caption = "Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience.",
   style = "Table Caption"
@@
 
+Paragraphe qui parle des différences entre figure 1 A et B, soit, lorsqu'on contrôle pour l'effet des proies.
+
 ## Effect of experience on the development of behavioural specialization
 
-```{r fig1, out.width = "100%", fig.cap = "**Figure 1.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience.
-(A) Coefficient of variation for the among individual differences in average behaviour.
-(B) Coefficient fo variation for the among individual differences in intra individual variance (i.e.
+Contrary to our predictions, we detected only minimal differences in movement speed among individual predators, and these differences did not change with experience (Figure 2A).
+However, individuals differed in their degree of flexibility, and these differences tended to increase, yet marginally, with experience (Figure 2B).
+Overall, individual predators appeared to have encountered prey with similar average speeds (Figure 2A), and our results do not support our prediction that predators would encounter prey with varying levels of speed (Figure 2B).
+
+```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience.
+(A) Coefficient of variation of the among individual differences in average behaviour.
+(B) Coefficient fo variation of the among individual differences in intra individual variance (i.e.
 specialization)."}
-
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure1.png"))
-
-```
-
-blablabla figure 2
-
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Distribution of the intra individual behavioural variation (i.e.
-specialization) of predators when they were (A) novices and (B) advanced.
-The red band displays the 95% CI of the intercept for the intra individual variance in predator speed."}
 
@@
 
-## Relationship between behavioural specialization and prey variability
+We predicted that, with experience, predators would become either increasingly flexible, or, more specialized.
+Here, we found that predators became generally more flexible with experience, but this increase in flexibility was only minimal (Figure 3 A and B).
+Thus we cannot conclude that experience had an important effect on behavioural specialization.
+Yet, as we have outlined in Figure 2, it appears that among individual differences in specialization increase when individuals are advanced compared to when they are novice (Figure 3 A and B).
 
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Full correlation matrix of the MDHGLM relating the mean and IIV speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
-Starting from the upper part of the plot are displayed the five parameters for novice predators (gray), the five for intermediate predators (yellow), and the five for advanced predators (blue).
-Larger dark blue circles indicate stronger positive correlations, while larger dark red circles indicate stronger negative correlations.
-The black squares indicate correlations between different experience levels."}
+```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Distribution of the intra individual behavioural variation (i.e.
+specialization) of predators when they were (A) novices and then (B) advanced hunters.
+The red band displays the 95% CI of the intercept for the intra individual standard deviation in predator speed."}
 
@@
 
-## Hunting success of behavioural specialists vs generalists
+## Relationship between behavioural specialization and prey variability
 
-*relationship between IIV of prey and success fades with experience*
+At all experience levels, predators that were on average faster were also travelling faster in all their matches (i.e.
+they were more specialized at travelling fast).
+Thus, slower predators were also more flexible in their movement through time (Figure 4).
+This pattern became stronger as predators gained experience (Figure 4).
+In general, predators tended to be faster and also more specialized in this strategy when they encountered prey that were on average faster (Figure 4).
+Moreover, predators favored and specialized in a faster foraging mode when encounters with prey were more predictable, and these relationships also became stronger with experience (Figure 4).
 
-```{r fig4, out.width = "100%", fig.cap = "**Figure 4.** Title (A) and (B) Novices. (C) and (D) Advanced."}
+The foraging strategies of predators, that is, the correlations between the mean and variance of speed, remained structurally stable among the levels of experience.
+For instance, novice predators that tended to be faster also kept this strategy as they gained experience (Figure 4 inside the black squares).
+Overall, we detected the same patterns for within-experience state correlations.
+The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that behavioural changes in predators occurred as they gained experience.
+
+```{r fig4, out.width = "100%", fig.cap = "**Figure 4.** Full correlation matrix of the MDHGLM relating the mean and IIV speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+Starting from the upper part of the plot are displayed the five parameters for novice predators (gray), the five for intermediate predators (yellow), and the five for advanced predators (blue).
+Larger dark blue circles indicate stronger positive correlations, while larger dark red circles indicate stronger negative correlations.
+The black squares indicate correlations between different experience levels (i.e.
+character states)."}
 
@@
 
+## Hunting success of behavioural specialists vs generalists
+
+We did not detect significant relationships between the predators' average nor intra individual variation in speed and hunting success (Figure 4), indicating that both slow/flexible and fast/specialist predators were both equally successful.
+However, when predators were novice, there was a strong positive correlation between the variation in prey that they encountered and their hunting success.
+Hence, novice individuals that experienced more unpredictable prey encounters at this stage were also more successful.
+This relationship was decoupled at the later experience levels, such that unpredictable encounters at intermediate and advanced stages were not associated with hunting success anymore.
+
 \newpage

### 2023-01-10 manuscript/Chapter2-manuscript.Rmd
update styles, ms, and ms rmd

@@
 
-In this study, we analyze individual behavioural data from players in *Dead by Daylight* (*DBD*) to test how hunting expertise and prey behaviour shape predator foraging specialization.
+In this study, we analyze individual behavioural data from players in *Dead by Daylight* (*DBD*) to test how hunting experience and prey behaviour shape predator foraging specialization.
 *DBD* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
@@
 Our results confirm that individual predators displayed important differences in the development of their expertise, as the best model was the one with group-level smoothers exclusively (Table I).
-For instance, some predators steadily increased their hunting success with experience, while others maintained either a high or low success across their experience (Figure 1A).
-Moreover, some individuals show a decrease in hunting success with experience.
+For instance, with experience, some predators steadily increased their hunting success while others displayed a decrease in prey capture (Figure 1A).
+Otherwise, there were players that maintained either a high or low success across their experience (Figure 1A).
 Another pattern that emerged was that some individuals optimized their success at an experience level that was below what we considered as "advanced" (i.e.
@@
 
-Paragraphe qui parle des différences entre figure 1 A et B, soit, lorsqu'on contrôle pour l'effet des proies.
+We predicted that the relationship between hunting success and experience would differ among predators because they should encounter different prey.
+However, after controlling for prey speed, we did not find evidence confirming our hypothesis, such that differences among predators in the relationship between hunting success and experience remained mostly the same (Figure 1B).
+
+```{r fig1, out.width = "100%", fig.cap = "**Figure 1.** Among individual differences in the development of hunting expertise.
+The predators' hunting success (i.e.
+the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e.
+the number of matches played prior to each observation) is on the x axis.
+Each fitted curve represents an individual predator.
+(A) A generalized additive mixed model where we do not control for prey speed (B) A generalized additive model where we control for prey speed."}
+
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure1.png"))
+
+```
 

### 2023-01-10 manuscript/Chapter2-SupInfo.Rmd
update ms version (V2) including results
updated styles, ms, supmat, fig S1 S2, and fig1 code

@@
 
-```{r, ft.align = "left"}
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Among individual differences in the development of hunting expertise.
+The predators' hunting success (i.e.
+the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e.
+the number of matches played prior to each observation) is on the x axis.
+Each fitted curve represents an individual predator.
+(A) Individuals with the greatest increase in hunting success with experience (B) Individuals with the greatest decrease in hunting success with experience."}
+
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS1.png"))
+
+```
+
+```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Distribution of the intra individual behavioural variation (i.e.
+specialization) of predators with the greatest increase in hunting success (A and B) and greatest decrease (B and C) in hunting success when they were novices (A and C) and then (B and D) advanced hunters."}
+
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS2.png"))
+
+```
+
+```{r tableS1, eval = FALSE, ft.align = "left"}
 
@@
   tab1,
-  caption = "LOO table",
+  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother. The values are presented on the logit scale.",
   style = "Table Caption"

### 2023-01-10 code/05_code_figures/05_figure1.R

@@ -113,10 +113,9 @@
 
 
 # Prepare the plot ---------------------------------------------------------
- 
- # Conditions back-transforms to probability scale
 
- # With intercept using built-in function
+ # Using built-in function
+ # With conditional_smooths, the predictions are on the link scale
  fig1 <- conditional_smooths(mod1, method = "fitted", robust = FALSE)
  fig2 <- conditional_smooths(mod2, method = "fitted", robust = FALSE)
  
@@ -137,11 +136,6 @@
 
  
 # Produce the plot --------------------------------------------------------
- 
- # With conditional_effects, the predictions are on the original scale of y
- # With conditional_smooths, the predictions are on the link scale
- # conditional effects in GAMM context cannot handle the mean population trend
- # IDK why is that.
 
  gamm_plot1 <- ggplot(tab1,
                       aes(x = Zcumul_xp,

### 2023-01-10 code/05_code_figures/05_figureS1-S2.R

@@ -1,0 +1,479 @@
+# ==========================================================================
+
+#                         expertise-variance plot
+
+# ==========================================================================
+
+
+
+
+
+# ==========================================================================
+# 1. Prepare script
+# ==========================================================================
+
+
+# Load libraries and models ------------------------------------------------
+
+library(brms)
+library(data.table)
+library(ggplot2)
+library(ggridges)
+library(ggpubr)
+
+path <- file.path(getwd(), "outputs", "02_outputs_models")
+
+fit1 <- readRDS(file.path(path, "02A3_GAMM.rds"))
+fit2 <- readRDS(file.path(path, "02B_DHMLM.rds"))
+
+
+
+# Load the data ------------------------------------------------------------
+
+data <- fread("./data/FraserFrancoetalXXXX-data.csv",
+              select = c("predator_id",
+                         "game_duration",
+                         "pred_speed",
+                         "prey_avg_speed",
+                         "cumul_xp_pred",
+                         "total_xp_pred",
+                         "hunting_success",
+                         "latency_1st_capture",
+                         "chase_count",
+                         "chase_count_success"))
+
+data[, predator_id := as.factor(predator_id)]
+
+
+
+# Post processing preparations for custom family ---------------------------
+
+expose_functions(fit1, vectorize = TRUE)
+
+# Define the log likelihood function
+log_lik_beta_binomial2 <- function(i, prep) {
+  mu <- brms::get_dpar(prep, "mu", i = i)
+  phi <- brms::get_dpar(prep, "phi", i = i)
+  trials <- prep$data$vint1[i]
+  y <- prep$data$Y[i]
+  beta_binomial2_lpmf(y, mu, phi, trials)
+}
+
+# Define function for posterior_predict
+posterior_predict_beta_binomial2 <- function(i, prep, ...) {
+  mu <- brms::get_dpar(prep, "mu", i = i)
+  phi <- brms::get_dpar(prep, "phi", i = i)
+  trials <- prep$data$vint1[i]
+  beta_binomial2_rng(mu, phi, trials)
+}
+
+# Define function for posterior_epred
+posterior_epred_beta_binomial2 <- function(prep) {
+  mu <- brms::get_dpar(prep, "mu")
+  trials <- prep$data$vint1
+  trials <- matrix(trials, nrow = nrow(mu), ncol = ncol(mu), byrow = TRUE)
+  mu * trials
+}
+
+
+
+# Setup a custom theme for the plot ----------------------------------------
+
+custom_theme <- theme(
+  # axis values size
[…]

### 2023-01-10 code/05_code_tables/05_tableS1.R

@@ -17,6 +17,7 @@ library(data.table)
 library(flextable)
 library(officer)
 library(dplyr)
+library(brms)
 
 # Import the model
 path <- file.path("./outputs/02_outputs_models")

### 2023-01-11 manuscript/Chapter2-manuscript.Rmd
some updates based on PO's comments.

@@
 experience).
-While hunting experience may be essential to maintain or improve foraging success, we have have limited evidence for either its role in predator foraging specialization or the ecological/fitness consequences of such among individual behavioural differences on predator-prey interactions [@Dukas2019].
+While hunting experience may be essential to maintain or improve foraging success, we have limited empirical assessments of its role in predator foraging specialization [@Dukas2019], nor its consequences on predator-prey interactions.
 
@@
 However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
-We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge, and uncover details of the mechanisms shaping these interactions [@FraserFranco.etal2022].
+We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge and help uncovering the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
 For instance, we found that the classical locomotor crossover hypothesis [@Huey.Pianka1981] applied only for cursorial hunters [see also: @Matsumura.Miyatake2022a], suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
@@
 This hypothesis has, however, not been tested in systems where behavioural interactions are simultaneously monitored between predator and prey individuals.
+Thus, uncovering the mechanisms shaping direct predator-prey interactions would enable researchers to better predict the behavioural decisions of predators when they are hunting.
 
@@
 *DBD* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
-The data grants a high degree of precision on the behavioural interaction as both the predator and the four prey are measured simultaneously in each trial.
-First, we investigate how predators developed their individual hunting expertise.
+The data grants a high degree of precision on the behavioural interaction as the behaviour of both the predator and the four prey is monitored simultaneously in each trial.
+First, we investigate how predators develop their individual hunting expertise.
 We hypothesize that predators should differ in the development of their expertise because they encounter varying levels of difficulty with the prey that they pursue.
+For example, a predator may face more difficulty than other individuals if it encountered prey that were more elusive.
 Second, we test the hypothesis that individual variation in foraging behaviour will change with experience.
@@
 Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
-Lastly, if individuals differ in their degree of foraging specialization, then we expect specialist hunters to fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
+Lastly, if individuals differ in their degree of foraging specialization, then we expect specialized hunters to fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
 
@@
 *DBD* is a survival asymmetric multiplayer online game developed by Behaviour Interactive Inc.
-In this game, players get to choose if they wish to play as a predator or a prey.
-The objective of the predator-player is to hunt and capture the four prey players across a virtual environment.
-The objective of the four prey players is to forage for resources while avoiding the predator.
-The resources are in the form of power generators that, once activated, will enable the prey to escape through one of two exit doors.
+In this game, players can play as a predator or a prey.
+The objective of the predator is to hunt and capture the four prey across a virtual environment.
+The objective of the four prey is to forage for resources while avoiding the predator.
+The resources are in the form of power generators that, once they are all activated, will enable the prey to escape through one of two exit doors.
 The composition of the predator and prey group for a match is determined by a skill-based matchmaking algorithm.
@@
 bold vs cautious prey, or ambush vs roaming predator).
-During our study period, the game offered 23 playable predator avatars.
+During our study period, the game offered 23 predator avatars.
 The virtual environment where matches take place is composed of fixed and procedurally generated habitat components, such as vegetation, mazes, and buildings.
@@
 
-Individual predators in *DBD* display variation in the hunting strategies that they use.
-Some specialize at hunting at high speeds and covering space in the environment, while others prefer to stalk and ambush their prey [@FraserFranco.etal2022].
-They also display flexibility in the use of these tactics by switching between them across matches.
+In *DBD*, some individual predators specialize on hunting at high speeds and covering space in the environment, while others prefer to stalk and ambush their prey [@FraserFranco.etal2022].
+Individuals are also flexible in the use of these tactics by switching between them across matches.
 The expression of these tactics and their success is also shaped by the behaviour of the prey group.
@@
 For instance, there could be a large difference in gameplay between 300-500 and 500-1000 matches.
-Players that played above 500 matches represented only ~2% of the population.
+Players that played above 500 matches represented ~2% of the population.
 
@@
 We analyzed the predator's average speed and the average speed of the prey encountered by the predator.
-The predator's average speed is measured as the average distance per second traveled during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`).
-For the prey, we averaged the travel speed of the four individuals within a match to obtain the average speed of the group ($\overline{x}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`).
-Hunting success was defined as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
-Lastly, the predator's cumulative experience was defined as the number of matches played prior to the match being monitored.
+The predator's average speed is measured as the average distance traveled per second during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`).
+We measured the preys' average speed as the average travel speed of the four individual prey within a match ($\overline{x}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`).
+We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
+Lastly, we defined the predator's cumulative experience as the number of matches played prior to the match being monitored.
 For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.
@@
 We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated variance ($id \sim N(0,\ I\ \sigma^2_{id})$).
-We defined all models to run four MCMC chains with 1000 posterior samples for each parameter.
+We estimated the parameters in all models using four MCMC chains with 1000 posterior samples for each parameter.
 To do so, we ran 2500 iterations for the first model with a thinning set to eight, and 1500 iterations with a thinning set to four for the second and third models; burn-in was set to 500 iterations in each model.
@@
 
-where $env \sim N(0,\ I\ \sigma^2_{env})$, $av \sim N(0,\ I\ \sigma^2_{av})$, and $id \sim N(0,\ I\ \sigma^2_{id})$.
+where $env$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$.
 $b$ is the vector of fixed effects with its incidence matrix $X$.
-$env$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$.
+The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively.
+We assumed that all random effects followed a Gaussian distribution with estimated variance ($env \sim N(0,\ I\ \sigma^2_{env})$, $av \sim N(0,\ I\ \sigma^2_{av})$, and $id \sim N(0,\ I\ \sigma^2_{id})$).
 The variance parameters $\sigma^2_{env}$, $\sigma^2_{av}$, and $\sigma^2_{id}$, correspond to the among environment, among avatar, and among individual variances, respectively.
 $I$ is the identity matrix, with $I\sigma^2$ indicating that the random effects are independently and identically distributed.
-The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively.
+Here, we assume that the residuals vary among individuals where $e \sim N(0,\ Diag\ [\sigma^2_{e}])$, $[\frac{id_m}{id_v}] \sim N\left(\begin{array}{cc} 0 \\ \\ 0 \end{array},\ \Sigma_{id} \otimes\ I \right)$, and $\Sigma_{id}$ is a variance covariance matrix of the individual identity random effect.
 Equations (1) and (2) were parametrized with a Gaussian distribution family (predator and prey speed), while equation (3) was parametrized with a beta-binomial distribution family (predator hunting success).
@@
 $cor(\sigma^2_{id_{m}\ pred}\ \sigma^2_{id_{d}\ prey})$) within a level of experience.
+In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible.
+In the second case, the correlations enables us to estimate, for example, whether slower/faster (or more specialized/flexible) predators encountered prey that were faster/slower, or if slower/faster predators had lower/greater hunting success.
 We also evaluated these correlations among the different levels of experience (e.g.
@@
 The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each developmental stage.
-The correlations were estimated using a multivariate Gaussian distribution.
+The correlations were estimated assuming a multivariate Gaussian distribution.
 
@@
 Contrary to our predictions, we detected only minimal differences in movement speed among individual predators, and these differences did not change with experience (Figure 2A).
-However, individuals differed in their degree of flexibility, and these differences tended to increase, yet marginally, with experience (Figure 2B).
-Overall, individual predators appeared to have encountered prey with similar average speeds (Figure 2A), and our results do not support our prediction that predators would encounter prey with varying levels of speed (Figure 2B).
+However, individuals differed in their degree of flexibility, and these differences increased marginally with experience (Figure 2B).
+Overall, individual predators encountered prey with similar average speeds (Figure 2A), and our results do not support our prediction that predators would encounter prey with varying levels of speed (Figure 2B).
 
@@
 
-At all experience levels, predators that were on average faster were also travelling faster in all their matches (i.e.
+```{r}
+
+# =======================================================================
+
+# Extract the correlations to report values in the text
+
+# =======================================================================
+
+# =======================================================================
+# Prepare the draws
+# =======================================================================
+
+ # Model
+ path <- here::here("outputs", "02_outputs_models")
+ fit <- readRDS(file.path(path, "02B_DHMLM.rds"))
+
+ # Extract te draws
+ draws <- data.table(
+     as_draws_df(
+         fit,
+         variable = c("cor"),
+         regex = TRUE)
+ )
+
+ draws[, c(106:109) := NULL]
+
+ # =======================================================================
+ # =======================================================================
+
+ # =======================================================================
+# 2. Transform the draws table
+# =======================================================================
+
+# Reshape the table -----------------------------------------------------
+
+ # Long format
+ table <- melt(draws,
+               measure = patterns("^cor_predator_id"),
+               variable.name = "correlation")
+
+ # Summarize the values (means + 95% CI) ---------------------------------
+
+ # Intervals
+ lower_interval <- function (x) {coda::HPDinterval(as.mcmc(x), 0.95)[1]}
+ upper_interval <- function (x) {coda::HPDinterval(as.mcmc(x), 0.95)[2]}
+
+ table[, ":=" (mean = mean(value),
+               lower_ci = lower_interval(value),
+               upper_ci = upper_interval(value)),
+       by = .(correlation)]
+
+ cor_tab <- unique(table[, c(1, 3:5)])
+
+ # Round values to 3 digits
+ cor_tab[, c(2:4) := lapply(.SD, function (x) {round(x, digits = 3)}),
+         .SDcols = c(2:4)]
+
+# =======================================================================
+# =======================================================================
+
+```
+
+At all experience levels, predators that were on average faster were also travelling faster in all their matches ($cor_{novice}$ = `r toString(format(cor_tab[1,2]))` [`r toString(format(cor_tab[1,3]))`, `r toString(format(cor_tab[1,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[6,2]))` [`r toString(format(cor_tab[6,3]))`, `r toString(format(cor_tab[6,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[15,2]))` [`r toString(format(cor_tab[15,3]))`, `r toString(format(cor_tab[15,4]))`]) (i.e.
 they were more specialized at travelling fast).
@@
 This pattern became stronger as predators gained experience (Figure 4).
-In general, predators tended to be faster and also more specialized in this strategy when they encountered prey that were on average faster (Figure 4).
+In general, predators tended to be faster when they encountered prey that were on average faster ($cor_{novice}$, $cor_{interm}$, $cor_{adv}$) (Figure 4).
+They were also more specialized at being fast when prey were on average faster (Figure 4).
+
 Moreover, predators favored and specialized in a faster foraging mode when encounters with prey were more predictable, and these relationships also became stronger with experience (Figure 4).

### 2023-01-26 manuscript/Chapter2-manuscript.Rmd
added versions of MS

@@
 ---
-title: "Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame"
+title: "Experience and prey behaviour jointly shape individual foraging specialisation and success in a predator-prey videogame"
 output: 
@@
 For each level of experience (i.e.
-novice, intermediate, advanced), we estimated the mean speed of individual predators, and a heterogeneous structure of the residuals such that we could estimate their intra-individual variance (IIV) in speed (i.e.
-specialization).
+novice, intermediate, advanced), we estimated the mean speed of individual predators, and a heterogeneous structure of the residuals such that we could estimate their intra-individual variation (IIV) in speed (i.e.
+specialization/flexibility).
 We followed the same structure for the preys' speed to estimate among individual differences in the mean and variance in speed of the prey encountered by predators.
 For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean hunting success.
-For all variables, we controlled for the duration of the match standardized in mean and unit variance.
+For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered.
+The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank).
+We used the mean rank of the four prey and applied a square-root transformation.
+For the predator's hunting success, we controlled for the square-root of the duration of the match.
 The model has the following form, with each equation repeated three times (i.e.
@@
 $I$ is the identity matrix, with $I\sigma^2$ indicating that the random effects are independently and identically distributed.
-Here, we assume that the residuals vary among individuals where $e \sim N(0,\ Diag\ [\sigma^2_{e}])$, $[\frac{id_m}{id_v}] \sim N\left(\begin{array}{cc} 0 \\ \\ 0 \end{array},\ \Sigma_{id} \otimes\ I \right)$, and $\Sigma_{id}$ is a variance covariance matrix of the individual identity random effect.
+Here, we assume that the residuals vary among individuals where $e \sim N(0,\ Diag\ [\sigma^2_{e}])$, $[\begin{array}{cc} id_m \\ id_v \end{array}] \sim N\left(\begin{array}{cc} 0 \\ \\ 0 \end{array},\ \Sigma_{id} \otimes\ I \right)$, and $\Sigma_{id}$ is a variance covariance matrix of the individual identity random effect.
 Equations (1) and (2) were parametrized with a Gaussian distribution family (predator and prey speed), while equation (3) was parametrized with a beta-binomial distribution family (predator hunting success).
@@
 In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible.
-In the second case, the correlations enables us to estimate, for example, whether slower/faster (or more specialized/flexible) predators encountered prey that were faster/slower, or if slower/faster predators had lower/greater hunting success.
+In the second case, the correlations enables us to estimate, for example, whether predators that encountered prey that were faster/slower adopted a slower/faster (or more specialized/flexible) strategy, or if slower/faster predators had lower/greater hunting success.
 We also evaluated these correlations among the different levels of experience (e.g.
@@
 
-Lastly we calculated the coefficient of variation in the mean (termed $CV_I$) and dispersion (termed $CV_p$) part of the predator's speed for each stage of experience, allowing us to report standardized effect sizes of individual variance for comparison across traits and studies [@cleasbyQuantifyingPredictabilityBehaviour2015;@Holtmann.etal2017;@Dingemanse.etal2022].
+Lastly we calculated the intra-class correlation coefficients ($ICC$, i.e.
+repeatability) of each random effect on the mean part of the predator's speed and prey speed to estimate the percentage of variation in speed attributed to differences among environments, avatars, and individuals.
+We also report the coefficient of variation in the mean (termed $CV_I$) and dispersion (termed $CV_p$) part of the predator and prey's speed, at each stage of experience, to report standardized effect sizes of individual variance for comparison across traits and studies [@cleasbyQuantifyingPredictabilityBehaviour2015;@Holtmann.etal2017;@Dingemanse.etal2022].
 This also allowed us to evaluate whether predators displayed increasing/decreasing differences in specialization at each stage of experience.
@@
 Our results confirm that individual predators displayed important differences in the development of their expertise, as the best model was the one with group-level smoothers exclusively (Table I).
-For instance, with experience, some predators steadily increased their hunting success while others displayed a decrease in prey capture (Figure 1A).
+For instance, with experience, some predators steadily increased their hunting success while others displayed a decrease in prey capture (Figure 1A-S1A-S1B).
 Otherwise, there were players that maintained either a high or low success across their experience (Figure 1A).
@@
 
-Contrary to our predictions, we detected only minimal differences in movement speed among individual predators, and these differences did not change with experience (Figure 2A).
-However, individuals differed in their degree of flexibility, and these differences increased marginally with experience (Figure 2B).
-Overall, individual predators encountered prey with similar average speeds (Figure 2A), and our results do not support our prediction that predators would encounter prey with varying levels of speed (Figure 2B).
+We detected among individual differences in the average movement speed of predators ($ICC\ predator\ ID$, Table 2).
+These differences decreased at the intermediate stage, and increased at the advanced stage (Table 2).
+Among-individual differences in mean predator speed was slightly higher at the advanced stage compared to the novice stage (Table 2).
+However, the highest amount of variation in mean predator speed was due to differences among predator avatars, and differences increased with experience ($ICC\ avatar\ ID$, Table 2).
+We did not detect variation in mean predator speed among the virtual environments ($ICC\ environment\ ID$, Table 2).
+Individual predators displayed considerable differences in their degree of specialization, and these differences increased with experience ($CV_p\ predator\ ID$, Table 2).
+Thus, the predator population is composed of individual specialists and generalists in their movement speed, and individuals further distinguish themselves in these strategies as they gain experience (Figure 2).
 
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Coefficient of variation for the predator's speed and for the speed of the prey encountered at each level of experience.
-(A) Coefficient of variation of the among individual differences in average behaviour.
-(B) Coefficient fo variation of the among individual differences in intra individual variance (i.e.
-specialization)."}
+We predicted that, with experience, predators would become either increasingly flexible, or, more specialized.
+Our results do not support our prediction, as the pattern was more complex.
+Indeed, we found that predators became more flexible with experience at the intermediate stage, but when they became advanced hunters, they returned to a level of flexibility similar to when they were novices ($Intercept$, Table 2, Figure 2).
+Thus, instead of increasing linearly, our results suggest that behavioural specialization changed in a nonlinear (quadratic) manner with experience.
 
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure2.png"))
+```{r table2, ft.align = "left"}
+
+tab2 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table2.rds"))
+
+tab2 <- autofit(tab2)
+
+tab2 <- tab2 %>% 
+  footnote(
+    i = 1, j = 1,
+    part = "header",
+    value = as_paragraph(
+      "* We applied the exponent to the intercept values of sigma parameters, estimated on a log scale, and then squared them, such that values are mean posterior residual variances.
+We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale."),
+    ref_symbols = " "
+  ) %>%
+  font(fontname = "Times New Roman", part = "all") %>%
+  width(j = c(1:5), width = 3.7, unit = "cm")
+
+set_caption(
+  tab2,
+  caption = "Posterior mean estimates and 95% credible intervals computed by the multivariate double-hierarchical generalized linear model of predator speed, prey speed, and predator hunting success.",
+  style = "Table Caption"
+)
 
@@
 
-We predicted that, with experience, predators would become either increasingly flexible, or, more specialized.
-Here, we found that predators became generally more flexible with experience, but this increase in flexibility was only minimal (Figure 3 A and B).
-Thus we cannot conclude that experience had an important effect on behavioural specialization.
-Yet, as we have outlined in Figure 2, it appears that among individual differences in specialization increase when individuals are advanced compared to when they are novice (Figure 3 A and B).
+As we predicted, individual predators encountered prey with varying levels of speed ($ICC\ predator\ ID$, Table 2).
+Similar to the predator's speed, prey encounters varied more among predators at the novice and advanced levels, and predators differed more in the mean speed of prey that they encountered at the advanced stage (Table 2).
+Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster.
+These encounters also varied slightly among the predator avatars and virtual environments, but did not change with experience (Table 2).
+However, predators differed only weakly in the variability between prey encounters that they experienced ($CV_p\ predator\ ID$, Table 2).
+Hence, while predators did differ in the mean speed of the prey that they encountered, they all experienced similar degrees of variation among encounters (Table 2).
 
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Distribution of the intra individual behavioural variation (i.e.
+```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Distribution of the intra individual behavioural variation (i.e.
 specialization) of predators when they were (A) novices and then (B) advanced hunters.
@@
 
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure3.png"))
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure2.png"))
 
@@
 
- # Extract te draws
+ # Extract the draws
  draws <- data.table(
@@
 
-At all experience levels, predators that were on average faster were also travelling faster in all their matches ($cor_{novice}$ = `r toString(format(cor_tab[1,2]))` [`r toString(format(cor_tab[1,3]))`, `r toString(format(cor_tab[1,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[6,2]))` [`r toString(format(cor_tab[6,3]))`, `r toString(format(cor_tab[6,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[15,2]))` [`r toString(format(cor_tab[15,3]))`, `r toString(format(cor_tab[15,4]))`]) (i.e.
+At all experience levels, predators that were on average faster (mean) were also travelling faster in all their matches (IIV) ($cor_{novice}$ = `r toString(format(cor_tab[1,2]))` [`r toString(format(cor_tab[1,3]))`, `r toString(format(cor_tab[1,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[6,2]))` [`r toString(format(cor_tab[6,3]))`, `r toString(format(cor_tab[6,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[15,2]))` [`r toString(format(cor_tab[15,3]))`, `r toString(format(cor_tab[15,4]))`]) (i.e.
 they were more specialized at travelling fast).
-Thus, slower predators were also more flexible in their movement through time (Figure 4).
-This pattern became stronger as predators gained experience (Figure 4).
-In general, predators tended to be faster when they encountered prey that were on average faster ($cor_{novice}$, $cor_{interm}$, $cor_{adv}$) (Figure 4).
-They were also more specialized at being fast when prey were on average faster (Figure 4).
+Thus, slower predators were also more flexible in their movement through time (Figure 3).
+In general, predators tended to be faster (mean) when they encountered prey that were on average faster (mean) ($cor_{novice}$ = `r toString(format(cor_tab[16,2]))` [`r toString(format(cor_tab[16,3]))`, `r toString(format(cor_tab[16,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[31,2]))` [`r toString(format(cor_tab[31,3]))`, `r toString(format(cor_tab[31,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[50,2]))` [`r toString(format(cor_tab[50,3]))`, `r toString(format(cor_tab[50,4]))`]) (Figure 4).
+At the three experience levels, there were only weak correlations between predator IIV and mean prey speed ($cor_{novice}$ = `r toString(format(cor_tab[17,2]))` [`r toString(format(cor_tab[17,3]))`, `r toString(format(cor_tab[17,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[32,2]))` [`r toString(format(cor_tab[32,3]))`, `r toString(format(cor_tab[32,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[51,2]))` [`r toString(format(cor_tab[51,3]))`, `r toString(format(cor_tab[51,4]))`]) (Figure 3).
+Similarly, predators specialized in a faster foraging mode (IIV) when encounters with prey were more predictable (IIV) ($cor_{novice}$ = `r toString(format(cor_tab[23,2]))` [`r toString(format(cor_tab[23,3]))`, `r toString(format(cor_tab[23,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[40,2]))` [`r toString(format(cor_tab[40,3]))`, `r toString(format(cor_tab[40,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[61,2]))` [`r toString(format(cor_tab[61,3]))`, `r toString(format(cor_tab[61,4]))`]), but the correlations were weak (Figure 3).
+In the four cases described above, the correlations became stronger as predators gained experience (Figure 3).
 
-Moreover, predators favored and specialized in a faster foraging mode when encounters with prey were more predictable, and these relationships also became stronger with experience (Figure 4).
-
-The foraging strategies of predators, that is, the correlations between the mean and variance of speed, remained structurally stable among the levels of experience.
-For instance, novice predators that tended to be faster also kept this strategy as they gained experience (Figure 4 inside the black squares).
+The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience.
+For instance, novice predators that tended to be faster also kept this strategy as they gained experience (Figure 3 inside the black squares).
 Overall, we detected the same patterns for within-experience state correlations.
@@
 
-```{r fig4, out.width = "100%", fig.cap = "**Figure 4.** Full correlation matrix of the MDHGLM relating the mean and IIV speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Full correlation matrix of the MDHGLM relating the mean and IIV speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
 Starting from the upper part of the plot are displayed the five parameters for novice predators (gray), the five for intermediate predators (yellow), and the five for advanced predators (blue).
@@
 
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure4.png"))
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure3.png"))
 
@@
 
-We did not detect significant relationships between the predators' average nor intra individual variation in speed and hunting success (Figure 4), indicating that both slow/flexible and fast/specialist predators were both equally successful.
-However, when predators were novice, there was a strong positive correlation between the variation in prey that they encountered and their hunting success.
-Hence, novice individuals that experienced more unpredictable prey encounters at this stage were also more successful.
-This relationship was decoupled at the later experience levels, such that unpredictable encounters at intermediate and advanced stages were not associated with hunting success anymore.
+We did not detect strong correlations between the predators' average speed and hunting success ($cor_{novice}$ = `r toString(format(cor_tab[67,2]))` [`r toString(format(cor_tab[67,3]))`, `r toString(format(cor_tab[67,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[81,2]))` [`r toString(format(cor_tab[81,3]))`, `r toString(format(cor_tab[81,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[96,2]))` [`r toString(format(cor_tab[96,3]))`, `r toString(format(cor_tab[96,4]))`]), nor between the IIV in speed and hunting success ($cor_{novice}$ = `r toString(format(cor_tab[68,2]))` [`r toString(format(cor_tab[68,3]))`, `r toString(format(cor_tab[68,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[82,2]))` [`r toString(format(cor_tab[82,3]))`, `r toString(format(cor_tab[82,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[97,2]))` [`r toString(format(cor_tab[97,3]))`, `r toString(format(cor_tab[97,4]))`]), suggesting that both slower/flexible and faster/specialist predators were both equally successful (Figure 3).
+However, when predators were novice, there was a strong negative correlation between the average speed of the prey that they encountered and their hunting success ($cor_{novice}$ = `r toString(format(cor_tab[73,2]))` [`r toString(format(cor_tab[73,3]))`, `r toString(format(cor_tab[68,4]))`]).
+Hence, novice individuals that encountered faster prey were less successful.
+This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore ($cor_{interm}$ = `r toString(format(cor_tab[87,2]))` [`r toString(format(cor_tab[87,3]))`, `r toString(format(cor_tab[87,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[102,2]))` [`r toString(format(cor_tab[102,3]))`, `r toString(format(cor_tab[102,4]))`]).
+
+# Discussion
 

### 2023-01-31 code/05_code_figures/05_figureS3.R
added code for figure S3

@@ -1,0 +1,275 @@
+# ===========================================================================
+
+#                        Code to produce Table S3                           #
+
+# ===========================================================================
+
+
+
+
+
+# ===========================================================================
+# 1. Load libraries and import the model fit
+# ===========================================================================
+
+
+# Load libraries
+library(data.table)
+library(flextable)
+library(officer)
+library(dplyr)
+library(brms)
+
+# path
+path <- file.path(getwd(), "outputs")
+
+# Import the model
+fit <- readRDS(
+  file.path(path, "02_outputs_models", "02B_DHMLM.rds")
+)
+
+# Import the CV table
+cv <- readRDS(
+  file.path(path, "04_outputs_model-processing", "04_CV-table.rds")
+)
+
+# ===========================================================================
+# ===========================================================================
+
+
+
+
+
+# ===========================================================================
+# 1. ICC table
+# ===========================================================================
+
+
+# Prepare data --------------------------------------------------------------
+
+# Extract the random effect variances
+var_draws <- data.table(
+  as_draws_df(
+    fit, variable = "^sd_", regex = TRUE
+  )
+)
+
+var_draws[, c(4,6,8,10,12,14,28:30) := NULL]
+
+
+# Extract the residual variance (intercepts)
+var_draws1 <- data.table(
+  as_draws_df(
+    fit, variable = c(
+      "b_sigma_speednovice_Intercept",
+      "b_sigma_speedinterm_Intercept",
+      "b_sigma_speedadvanced_Intercept",
+      "b_sigma_preyspeednovice_Intercept",
+      "b_sigma_preyspeedinterm_Intercept",
+      "b_sigma_preyspeedadvanced_Intercept"
+    )
+  )
+)
+
+var_draws1[, c(7:9) := NULL]
+
+
+# Combine the tables
+var_draws <- cbind(var_draws, var_draws1)
+
+
+
+# Calculate parameters -------------------------------------------------------
+
+# Take the exponent of sigma parameters
+var_draws[
[…]

### 2023-01-31 code/05_code_tables/05_table2.R
updated table 2 with SD's instead

@@ -28,11 +28,6 @@
    file.path(path, "02_outputs_models", "02B_DHMLM.rds")
  )
 
- # Import the CV table
- cv <- readRDS(
-   file.path(path, "04_outputs_model-processing", "04_CV-table.rds")
- )
-
 # ===========================================================================
 # ===========================================================================
 
@@ -94,8 +89,8 @@
  # Create trait column
  eff_tab[
    , trait := rep(c(
-     "mu predator speed", "sigma predator speed", 
-     "mu prey speed", "sigma prey speed", "mu success"), 
+     "mean predator speed", "sigma predator speed", 
+     "mean prey speed", "sigma prey speed", "mean success"), 
      6
    )
  ]
@@ -104,9 +99,9 @@
  eff_tab[
     , parameter := rep(
        c(
-          rep("Intercept", 5),
-          rep("Mean prey rank", 4),
-          "Match duration"
+          rep("intercept", 5),
+          rep("mean prey rank", 4),
+          "match duration"
        ),
        3
     )
@@ -131,6 +126,9 @@
  # Reorder columns
  eff_tab <- eff_tab[, c(1,2,5,4,3)]
  
+ # Reorder rows
+ eff_tab <- eff_tab[c(1,2,7,8,3,4,9,10,5,6)]
+ 
 # ===========================================================================
 # ===========================================================================
 
@@ -146,104 +144,35 @@
 # Prepare data --------------------------------------------------------------
  
  # Extract the random effect variances
- var_draws <- data.table(
+ sd_draws <- data.table(
     as_draws_df(
        fit, variable = "^sd_", regex = TRUE
     )
  )
  
- var_draws[, c(4,6,8,10,12,14,28:30) := NULL]
-
- 
- # Extract the residual variance (intercepts)
- var_draws1 <- data.table(
-    as_draws_df(
-       fit, variable = c(
-          "b_sigma_speednovice_Intercept",
-          "b_sigma_speedinterm_Intercept",
-          "b_sigma_speedadvanced_Intercept",
-          "b_sigma_preyspeednovice_Intercept",
-          "b_sigma_preyspeedinterm_Intercept",
-          "b_sigma_preyspeedadvanced_Intercept"
-       )
-    )
- )
- 
- var_draws1[, c(7:9) := NULL]
- 
- 
- # Combine the tables
[…]

### 2023-01-31 code/05_code_tables/05_tableS1.R
added table S1 (correlation matrix)

@@ -1,0 +1,287 @@
+# ===========================================================================
+
+#                        Code to produce Table S1                           #
+
+# ===========================================================================
+
+
+
+
+
+# ===========================================================================
+# 1. Load libraries and import the model fit
+# ===========================================================================
+
+ # Load libraries
+ library(data.table)
+ library(flextable)
+ library(officer)
+ library(dplyr)
+ library(brms)
+ 
+ # path
+ path <- file.path(getwd(), "outputs")
+ 
+ # Import the model
+ fit <- readRDS(
+   file.path(path, "02_outputs_models", "02B_DHMLM.rds")
+ )
+# ===========================================================================
+# ===========================================================================
+
+
+
+
+
+# ===========================================================================
+# 2. Correlation matrix
+# ===========================================================================
+
+
+# Prepare the correlation matrix --------------------------------------------
+ 
+ # Extract the full object
+ ar <- VarCorr(fit)
+ 
+ # Extract the covariances from the object
+ cov <- ar$predator_id$cov
+ 
+ # Extract the covariance matrix
+ vcov_mat <- cov[,1,] # covariance
+ upper_vcov_mat <- cov[,4,] # upper ci
+ lower_vcov_mat <- cov[,3,] # lower ci
+ 
+ # Transform to correlation matrix
+ cormat <- cov2cor(vcov_mat)
+ upper_cormat <- cov2cor(upper_vcov_mat)
+ lower_cormat <- cov2cor(lower_vcov_mat)
+
+
+
+# Arrange the correlation matrix ----------------------------------------
+ 
+ # Reorder by XP level in order
+ cormat_ord <- cormat[
+   c(1, 2, 7, 8, 13,
+     3, 4, 9, 10, 14,
+     5, 6, 11, 12, 15),
+   c(1, 2, 7, 8, 13,
+     3, 4, 9, 10, 14,
+     5, 6, 11, 12, 15)
+ ]
+ 
+ upper_cormat_ord <- upper_cormat[
+   c(1, 2, 7, 8, 13,
+     3, 4, 9, 10, 14,
+     5, 6, 11, 12, 15),
+   c(1, 2, 7, 8, 13,
+     3, 4, 9, 10, 14,
+     5, 6, 11, 12, 15)
+ ] 
+ 
+ lower_cormat_ord <- lower_cormat[
+   c(1, 2, 7, 8, 13,
+     3, 4, 9, 10, 14,
+     5, 6, 11, 12, 15),
[…]

### 2023-01-31 manuscript/Chapter2-SupInfo.Rmd
updated supmat

@@
 ---
-title: "Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame"
+title: "Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame"
 output: 
@@
 ```
-
-```{r tableS1, eval = FALSE, ft.align = "left"}
-
-tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))
-
-set_caption(
-  tab1,
-  caption = "Posterior mean values, standard errors, and 95% credible intervals for the GAMM with a common global smoother. The values are presented on the logit scale.",
-  style = "Table Caption"
-)
-
-```

### 2023-01-31 manuscript/Chapter2-manuscript.Rmd
updated MS (need to update results text)

@@
 ---
-title: "Experience and prey behaviour jointly shape individual foraging specialisation and success in a predator-prey videogame"
+title: "Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame"
 output: 
@@
 library(flextable)
-library(officer)
+#library(officer)
 library(tidyr)
@@
 
-```{r}
-#\[
-#\begin{align}
-#logit (P_{i}) &= (\beta_{0} + id_{0,i}) \\
-#&\text{ } + \text{ } \beta_{1} \textit{match duration}_{i} \\
-#&\text{ } + \text{ } f(\textit{cumulative xp}_{i}) \\
-#\end{align}
-#\tag{1}
-#\]
-```
-
 ### Foraging behaviour and success, prey behaviour, and their relationships, at each level of experience
@@
 
-```{r table1, ft.align = "left"}
-
-tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))
-
-tab1 <- autofit(tab1)
-
-tab1 <- tab1 %>% 
-  footnote(
-    i = 1, j = 1,
-    part = "header",
-    value = as_paragraph(
-      "* 'elpd' refers to the 'expected log pointwise density' and is the value chosen to select the best model"),
-    ref_symbols = " "
-  ) %>%
-  fontsize(size = 11, part = "all") %>%
-  font(fontname = "Times New Roman", part = "all")
-
-set_caption(
-  tab1,
-  caption = "Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience.",
-  style = "Table Caption"
-)
-
-```
-
 We predicted that the relationship between hunting success and experience would differ among predators because they should encounter different prey.
@@
     value = as_paragraph(
-      "* We applied the exponent to the intercept values of sigma parameters, estimated on a log scale, and then squared them, such that values are mean posterior residual variances.
+      "* We applied the exponent to the parameter values for sigma (intercepts and predator ID), estimated on a log scale, such that values are mean posterior standard deviations (SD).
 We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale."),
@@
 )
-
 ```
@@
 
-```{r}
+```{r, eval=FALSE}
 
@@
 
-At all experience levels, predators that were on average faster (mean) were also travelling faster in all their matches (IIV) ($cor_{novice}$ = `r toString(format(cor_tab[1,2]))` [`r toString(format(cor_tab[1,3]))`, `r toString(format(cor_tab[1,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[6,2]))` [`r toString(format(cor_tab[6,3]))`, `r toString(format(cor_tab[6,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[15,2]))` [`r toString(format(cor_tab[15,3]))`, `r toString(format(cor_tab[15,4]))`]) (i.e.
-they were more specialized at travelling fast).
-Thus, slower predators were also more flexible in their movement through time (Figure 3).
-In general, predators tended to be faster (mean) when they encountered prey that were on average faster (mean) ($cor_{novice}$ = `r toString(format(cor_tab[16,2]))` [`r toString(format(cor_tab[16,3]))`, `r toString(format(cor_tab[16,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[31,2]))` [`r toString(format(cor_tab[31,3]))`, `r toString(format(cor_tab[31,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[50,2]))` [`r toString(format(cor_tab[50,3]))`, `r toString(format(cor_tab[50,4]))`]) (Figure 4).
-At the three experience levels, there were only weak correlations between predator IIV and mean prey speed ($cor_{novice}$ = `r toString(format(cor_tab[17,2]))` [`r toString(format(cor_tab[17,3]))`, `r toString(format(cor_tab[17,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[32,2]))` [`r toString(format(cor_tab[32,3]))`, `r toString(format(cor_tab[32,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[51,2]))` [`r toString(format(cor_tab[51,3]))`, `r toString(format(cor_tab[51,4]))`]) (Figure 3).
-Similarly, predators specialized in a faster foraging mode (IIV) when encounters with prey were more predictable (IIV) ($cor_{novice}$ = `r toString(format(cor_tab[23,2]))` [`r toString(format(cor_tab[23,3]))`, `r toString(format(cor_tab[23,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[40,2]))` [`r toString(format(cor_tab[40,3]))`, `r toString(format(cor_tab[40,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[61,2]))` [`r toString(format(cor_tab[61,3]))`, `r toString(format(cor_tab[61,4]))`]), but the correlations were weak (Figure 3).
-In the four cases described above, the correlations became stronger as predators gained experience (Figure 3).
+At all experience levels, predators that were on average faster (mean) were also travelling faster in all their matches (IIV) (Figure 3-S1).
+Thus, faster predators specialized at travelling fast, while slower predators were more flexible in their movement through time.
+In general, predators tended to be faster (mean) when they encountered prey that were on average faster (mean) (Figure 3-S1).
+At the three experience levels, there were only weak correlations between predator IIV and mean prey speed (Figure 3-S1).
+Similarly, predators specialized in a faster foraging mode (IIV) when encounters with prey were more predictable (IIV), but the correlations were weak (Figure 3-S1).
+In the four cases described above, the correlations became stronger as predators gained experience (Figure 3-S1).
 
@@
 
-We did not detect strong correlations between the predators' average speed and hunting success ($cor_{novice}$ = `r toString(format(cor_tab[67,2]))` [`r toString(format(cor_tab[67,3]))`, `r toString(format(cor_tab[67,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[81,2]))` [`r toString(format(cor_tab[81,3]))`, `r toString(format(cor_tab[81,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[96,2]))` [`r toString(format(cor_tab[96,3]))`, `r toString(format(cor_tab[96,4]))`]), nor between the IIV in speed and hunting success ($cor_{novice}$ = `r toString(format(cor_tab[68,2]))` [`r toString(format(cor_tab[68,3]))`, `r toString(format(cor_tab[68,4]))`], $cor_{interm}$ = `r toString(format(cor_tab[82,2]))` [`r toString(format(cor_tab[82,3]))`, `r toString(format(cor_tab[82,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[97,2]))` [`r toString(format(cor_tab[97,3]))`, `r toString(format(cor_tab[97,4]))`]), suggesting that both slower/flexible and faster/specialist predators were both equally successful (Figure 3).
-However, when predators were novice, there was a strong negative correlation between the average speed of the prey that they encountered and their hunting success ($cor_{novice}$ = `r toString(format(cor_tab[73,2]))` [`r toString(format(cor_tab[73,3]))`, `r toString(format(cor_tab[68,4]))`]).
+We did not detect strong correlations between the predators' average speed and hunting success (Figure 3-S1), nor between the IIV in speed and hunting success (Figure 3-S1), suggesting that both slower/flexible and faster/specialist predators were both equally successful.
+However, when predators were novice, there was a strong negative correlation between the average speed of the prey that they encountered and their hunting success (Figure 3-S1).
 Hence, novice individuals that encountered faster prey were less successful.
-This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore ($cor_{interm}$ = `r toString(format(cor_tab[87,2]))` [`r toString(format(cor_tab[87,3]))`, `r toString(format(cor_tab[87,4]))`], $cor_{adv}$ = `r toString(format(cor_tab[102,2]))` [`r toString(format(cor_tab[102,3]))`, `r toString(format(cor_tab[102,4]))`]).
+This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3-S1).
 

### 2023-02-02 manuscript/Chapter2-SupInfo.Rmd
update supmat

@@
 ---
-title: "Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame"
+title: "Online supporting information for : \nHunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame"
 output: 
@@
 ```
+
+```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM."}
+
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS4.png"))
+
+```

### 2023-02-02 code/05_code_figures/05_figureS4.R
update fig s4

@@ -15,6 +15,7 @@
 # Load libraries
 library(brms)
 library(ggplot2)
+library(viridis)
 
 path <- file.path(getwd(), "outputs", "02_outputs_models")
 fit <- readRDS(file.path(path, "02B_DHMLM.rds"))
@@ -191,36 +192,36 @@ fig <- ggplot(
     tab,
     aes(x = test, y = Estimate, fill = trait, shape = trait)
 ) +
-geom_hline(
-    yintercept = 0, size = 1, colour = "red",
-    linetype = "dashed", alpha = 0.5
-) +
-geom_pointrange(
-    aes(ymin = CI.Lower, ymax = CI.Upper),
-    size = 0.8, position = position_dodge(width = 0.8)
-) +
-scale_shape_manual(
-    name = "Trait :",
-    values = c(22,23,24,25,21)
-) +
-scale_fill_viridis(
-    name = "Trait :",
-    discrete = TRUE, option = "D"
-) +
-ylab("\nEstimate") +
-coord_flip() +
-theme_bw() +
-facet_wrap(~ group) +
-theme(
-    axis.title.y = element_blank(),
-    axis.text = element_text(face = "plain", size = 12, color = "black"),
-    axis.title = element_text(size = 14, face = "plain", color = "black"),
-    strip.text = element_text(size = 12),
-    legend.position = "top",
-    legend.key = element_rect(fill = "transparent"),
-    legend.title = element_text(size = 14),
-    legend.text = element_text(size = 12)
-)
+    geom_hline(
+        yintercept = 0, size = 1, colour = "red",
+        linetype = "dashed", alpha = 0.5
+    ) +
+    geom_pointrange(
+        aes(ymin = CI.Lower, ymax = CI.Upper),
+        size = 0.8, position = position_dodge(width = 0.8)
+    ) +
+    scale_shape_manual(
+        name = "Trait :",
+        values = c(22,23,24,25,21)
+    ) +
+    scale_fill_viridis(
+        name = "Trait :",
+        discrete = TRUE, option = "D"
+    ) +
+    ylab("\nEstimate") +
+    coord_flip() +
+    theme_bw() +
+    facet_wrap(~ group) +
+    theme(
+        axis.title.y = element_blank(),
+        axis.text = element_text(face = "plain", size = 11, color = "black"),
+        axis.title = element_text(size = 13, face = "plain", color = "black"),
+        strip.text = element_text(size = 11),
+        legend.position = "top",
[…]

### 2023-02-08 code/05_code_tables/05_tableS1.R
updated code for table S1

@@ -237,50 +237,61 @@
  # Create the table ----------------------------------------------------------
 
  cor_table <-
-   # Select table content
-   table %>%
-   select(my_header$col_keys) %>%
-   flextable() %>%
-   
-   # modify column names
-   set_header_df(mapping = my_header, key = "col_keys") %>%
-   # modify row names on column 1
-   mk_par(j = 1, value = as_paragraph(column_names[-1])) %>%
-   # Add header rows (for XP levels)
-   add_header_row(
-     values = c(NA, "Novice", "Intermediate", "Advanced"),
-     colwidths = c(1, 5, 5, 5)
-   ) %>%
-   
-   # Add theme
-   my_theme() %>%
-   # Add borders
-   hline(
-     i = 1, part = "header",
-     border = fp_border(width = 1, color = "black")
-   ) %>%
-   hline_top(
-     part = "header",
-     border = fp_border(width = 1, color = "black")
-   ) %>%
-   hline_bottom(
-     part = "body", 
-     border = fp_border(width = 1, color = "black")
-   ) %>%
-   
-   # Customizing the table layout
-   fontsize(size = 9, part = "all") %>%
-   font(fontname = "Times New Roman", part = "all") %>%
-   #width(j = c(1:16), width = 3.7, unit = "cm") %>%
-   align(align = "left", part = "all", j = 1) %>%
-   align(align = "center", part = "all", j = c(2:16))
+    # Select table content
+    table %>%
+    select(my_header$col_keys) %>%
+    flextable() %>%
+    
+    # modify column names
+    set_header_df(mapping = my_header, key = "col_keys") %>%
+    # modify row names on column 1
+    mk_par(j = 1, value = as_paragraph(column_names[-c(1)])) %>%
+    # Add header rows (for XP levels)
+    add_header_row(
+       values = c(NA, "Novice", "Intermediate", "Advanced"),
+       colwidths = c(1, 5, 5, 5)
+    ) %>%
+    
+    # Add theme
+    my_theme() %>%
+    # Add borders
+    hline(
+       i = 1, part = "header",
+       border = fp_border(width = 1, color = "black")
+    ) %>%
+    hline_top(
+       part = "header",
+       border = fp_border(width = 1, color = "black")
+    ) %>%
+    hline_bottom(
+       part = "body", 
+       border = fp_border(width = 1, color = "black")
+    ) %>%
+    
+    # Customizing the table layout
[…]

### 2023-02-08 manuscript/Chapter2-manuscript.Rmd
updated MS - arranged hypotheses and methods

@@
 ---
-title: "Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame"
+title: "Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame"
 output: 
@@
 library(flextable)
-#library(officer)
+library(officer)
 library(tidyr)
@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals specializing in different foraging strategies or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
+Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
 A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can be major drivers of such individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
@@
 
-The development of foraging strategies is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
+The development of foraging tactics is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
 Theory predicts that foraging specialization may emerge via learning, limitations in memorizing multiple complex hunting skills, and expertise [@Tinker.etal2009;@Dukas2019].
@@
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, followed by higher performance at later stages of development [reviewed in @Snell-Rood2013].
+However, individuals may face different challenges during their lifetime, which could lead to both mechanisms operating at the same time within a population.
 
-There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging (REFERENCES).
-Importantly, we have limited information on the ecological contexts - except for competition - that favour one strategy over the other.
+There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging.
+Importantly, we have limited information on the ecological contexts - except for competition - that favour specialization over flexibility.
 This is reflected in the literature showing contrasting results in the links between specialization and fitness.
@@
 This hypothesis has, however, not been tested in systems where behavioural interactions are simultaneously monitored between predator and prey individuals.
-Thus, uncovering the mechanisms shaping direct predator-prey interactions would enable researchers to better predict the behavioural decisions of predators when they are hunting.
+Thus, uncovering the mechanisms shaping direct predator-prey interactions would enable researchers to better predict the behavioural decisions that predators take when they are hunting.
 
-In this study, we analyze individual behavioural data from players in *Dead by Daylight* (*DBD*) to test how hunting experience and prey behaviour shape predator foraging specialization.
+In this study, we analyze individual behavioural data from players in *Dead by Daylight* (*DBD*) to test how hunting experience shapes predator foraging specialization during direct behavioural interactions with prey.
 *DBD* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
@@
 First, we investigate how predators develop their individual hunting expertise.
-We hypothesize that predators should differ in the development of their expertise because they encounter varying levels of difficulty with the prey that they pursue.
-For example, a predator may face more difficulty than other individuals if it encountered prey that were more elusive.
-Second, we test the hypothesis that individual variation in foraging behaviour will change with experience.
-If experience reduces the costs of switching between hunting tactics, we predict that individual predators should become more flexible with time.
-Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize.
+We hypothesize that predators should differ in the development of their expertise, partly because they encounter varying levels of difficulty with the prey that they pursue.
+For example, a predator may face greater difficulty than other individuals if it more often encountered prey that were elusive [@FraserFranco.etal2022].
+Second, we test the hypothesis that experience will shape foraging specialization.
+If experience reduces the costs of switching between hunting tactics, we predict that the predator population should become more flexible.
+Alternatively, if experience enables the refinement of the hunting tactics, then the predator population may instead specialize.
+Otherwise, if both mechanisms operate at the same time, then we should see no change with experience at the population level, but differences in specialization among individuals should increase.
 Third, we evaluate how predator foraging specialization interacts with variation in prey behaviour.
@@
 For instance, there could be a large difference in gameplay between 300-500 and 500-1000 matches.
-Players that played above 500 matches represented ~2% of the population.
+Players that played more than 500 matches represented ~2% of the population.
 
@@
 We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
-We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated variance ($id \sim N(0,\ I\ \sigma^2_{id})$).
+We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$).
 We estimated the parameters in all models using four MCMC chains with 1000 posterior samples for each parameter.
@@
 For each level of experience (i.e.
-novice, intermediate, advanced), we estimated the mean speed of individual predators, and a heterogeneous structure of the residuals such that we could estimate their intra-individual variation (IIV) in speed (i.e.
-specialization/flexibility).
-We followed the same structure for the preys' speed to estimate among individual differences in the mean and variance in speed of the prey encountered by predators.
+novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and, employing a heterogeneous structure of the residuals, the intra-individual standard deviation in speed of every individual (which we call the dispersion part of the model).
+Thus, in the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e.
+fast or slow), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization.
+We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation in speed of the prey encountered by predators.
 For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean hunting success.
-For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered.
+For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered on both the mean and dispersion part of the equation.
 The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank).
@@
 speed_{pred} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
-log(\sigma^2_{e,\ pred}) &= X_{d} + Z\ id_{d}
+log(\sigma_{e,\ pred}) &= X_{d} + Z\ id_{d}
 \end{align}
@@
 speed_{prey} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
-log(\sigma^2_{e,\ prey}) &= X_{d} + Z\ id_{d}
+log(\sigma_{e,\ prey}) &= X_{d} + Z\ id_{d}
 \end{align}
@@
 The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively.
-We assumed that all random effects followed a Gaussian distribution with estimated variance ($env \sim N(0,\ I\ \sigma^2_{env})$, $av \sim N(0,\ I\ \sigma^2_{av})$, and $id \sim N(0,\ I\ \sigma^2_{id})$).
-The variance parameters $\sigma^2_{env}$, $\sigma^2_{av}$, and $\sigma^2_{id}$, correspond to the among environment, among avatar, and among individual variances, respectively.
-$I$ is the identity matrix, with $I\sigma^2$ indicating that the random effects are independently and identically distributed.
-Here, we assume that the residuals vary among individuals where $e \sim N(0,\ Diag\ [\sigma^2_{e}])$, $[\begin{array}{cc} id_m \\ id_v \end{array}] \sim N\left(\begin{array}{cc} 0 \\ \\ 0 \end{array},\ \Sigma_{id} \otimes\ I \right)$, and $\Sigma_{id}$ is a variance covariance matrix of the individual identity random effect.
+We assumed that all random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$, $av \sim N(0,\ I\ \sigma_{av})$, and $id \sim N(0,\ I\ \sigma_{id})$).
+The parameters $\sigma_{env}$, $\sigma_{av}$, and $\sigma_{id}$, correspond to the among environment, among avatar, and among individual standard deviations, respectively.
+$I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
+Here, we assume that the residuals vary among individuals where $e \sim N(0,\ Diag\ [\sigma_{e}])$, $[\begin{array}{cc} id_m \\ id_v \end{array}] \sim N\left(\begin{array}{cc} 0 \\ \\ 0 \end{array},\ \Sigma_{id} \otimes\ I \right)$, and $\Sigma_{id}$ is a variance covariance matrix of the individual identity random effect.
 Equations (1) and (2) were parametrized with a Gaussian distribution family (predator and prey speed), while equation (3) was parametrized with a beta-binomial distribution family (predator hunting success).
@@
 We estimated the correlation between the individual random effect on the mean and on the dispersion within each trait (e.g.
-$cor(\sigma^2_{id_{m}\ pred}\ \sigma^2_{id_{d}\ pred})$) and among each trait (e.g.
-$cor(\sigma^2_{id_{m}\ pred}\ \sigma^2_{id_{d}\ prey})$) within a level of experience.
+$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ pred})$) and among each trait (e.g.
+$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ prey})$) within a level of experience.
 In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible.
-In the second case, the correlations enables us to estimate, for example, whether predators that encountered prey that were faster/slower adopted a slower/faster (or more specialized/flexible) strategy, or if slower/faster predators had lower/greater hunting success.
+In the second case, the correlations enables us to estimate, for example, whether predators that encountered prey that were faster/slower adopted a slower/faster (or more specialized/flexible) tactic, or if slower/faster predators had lower/greater hunting success.
 We also evaluated these correlations among the different levels of experience (e.g.
-$cor(\sigma^2_{id_{m}\ pred\ novice}\ \sigma^2_{id_{d}\ pred\ intermediate})$).
+$cor(\sigma_{id_{m}\ pred\ novice}\ \sigma_{id_{d}\ pred\ intermediate})$).
 The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each developmental stage.
 The correlations were estimated assuming a multivariate Gaussian distribution.
-
-Lastly we calculated the intra-class correlation coefficients ($ICC$, i.e.
-repeatability) of each random effect on the mean part of the predator's speed and prey speed to estimate the percentage of variation in speed attributed to differences among environments, avatars, and individuals.
-We also report the coefficient of variation in the mean (termed $CV_I$) and dispersion (termed $CV_p$) part of the predator and prey's speed, at each stage of experience, to report standardized effect sizes of individual variance for comparison across traits and studies [@cleasbyQuantifyingPredictabilityBehaviour2015;@Holtmann.etal2017;@Dingemanse.etal2022].
-This also allowed us to evaluate whether predators displayed increasing/decreasing differences in specialization at each stage of experience.
+We also report additional analyses, such as variance partitioning, and coefficients of variation, in the supporting information.
 
@@
 Our results confirm that individual predators displayed important differences in the development of their expertise, as the best model was the one with group-level smoothers exclusively (Table I).
-For instance, with experience, some predators steadily increased their hunting success while others displayed a decrease in prey capture (Figure 1A-S1A-S1B).
+For instance, with experience, some predators steadily increased their hunting success while others displayed a decrease in prey capture (Figure 1A-S1).
 Otherwise, there were players that maintained either a high or low success across their experience (Figure 1A).
@@
 
-We predicted that the relationship between hunting success and experience would differ among predators because they should encounter different prey.
-However, after controlling for prey speed, we did not find evidence confirming our hypothesis, such that differences among predators in the relationship between hunting success and experience remained mostly the same (Figure 1B).
+```{r table1, ft.align = "left"}
+
+tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))
+
+tab1 <- autofit(tab1)
+
+tab1 <- tab1 %>% 
+  footnote(
+    i = 1, j = 1,
+    part = "header",
+    value = as_paragraph(
+      "* 'elpd' refers to the 'expected log pointwise density' and is the value chosen to select the best model."),
+    ref_symbols = " "
+  ) %>%
+  font(fontname = "Times New Roman", part = "all") %>%
+  fontsize(size = 11, part = "all")
+
+set_caption(
+  tab1,
+  caption = "Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience",
+  style = "Table Caption"
+)
+
+```
+
+We predicted that the relationship between hunting success and experience would vary among predators because they should differ in the type of prey that they encounter.
+However, after controlling for prey speed, we did not find evidence confirming our hypothesis, such that differences among predators in the relationship between hunting success and experience remained stable (Figure 1B).
 
@@
 
-We detected among individual differences in the average movement speed of predators ($ICC\ predator\ ID$, Table 2).
-These differences decreased at the intermediate stage, and increased at the advanced stage (Table 2).
-Among-individual differences in mean predator speed was slightly higher at the advanced stage compared to the novice stage (Table 2).
-However, the highest amount of variation in mean predator speed was due to differences among predator avatars, and differences increased with experience ($ICC\ avatar\ ID$, Table 2).
-We did not detect variation in mean predator speed among the virtual environments ($ICC\ environment\ ID$, Table 2).
-Individual predators displayed considerable differences in their degree of specialization, and these differences increased with experience ($CV_p\ predator\ ID$, Table 2).
-Thus, the predator population is composed of individual specialists and generalists in their movement speed, and individuals further distinguish themselves in these strategies as they gain experience (Figure 2).
+At the population level, we predicted that with experience, predators would become either increasingly flexible or specialized.
+However, our results do not support our prediction, as the pattern was more complex.
+In the dispersion part of the model (i.e.
+sigma predator speed), we indeed found that predators became more flexible with experience at the intermediate stage ($Intercept$, Table 2 and Figure S4).
+However, when they became advanced hunters, they expressed a similar level of flexibility to when they were novices ($Intercept$, Table 2 and Figure S4).
+Thus, instead of increasing linearly, our results suggest that population-level behavioural specialization changed in a nonlinear (quadratic) fashion with experience.
 
-We predicted that, with experience, predators would become either increasingly flexible, or, more specialized.
-Our results do not support our prediction, as the pattern was more complex.
-Indeed, we found that predators became more flexible with experience at the intermediate stage, but when they became advanced hunters, they returned to a level of flexibility similar to when they were novices ($Intercept$, Table 2, Figure 2).
-Thus, instead of increasing linearly, our results suggest that behavioural specialization changed in a nonlinear (quadratic) manner with experience.
+At the individual level, we detected differences in the average movement speed among predators ($SD\ predator\ ID$, Table 2).
+These differences remained stable (although they decreased minimally) at the intermediate stage (Table 2 and Figure S4), and increased at the advanced stage to a level higher than when predators were novice (Table 2 and Figure S4).
+The largest proportion of variation in mean predator speed was attributed to differences among predator avatars ($ICC\ avatar\ ID$, Table S1), and these differences increased with experience ($SD\ avatar\ ID$, Table 2).
+The variation in mean predator speed among the virtual environments was very low ($SD\ environment\ ID$, Table 2).
+For the dispersion part of the model (i.e.
+sigma predator speed), predators displayed considerable differences in their degree of hunting specialization, which also increased with experience ($SD\ predator\ ID$, Table 2 and Figure S4).
+Thus, the predator population is composed of both specialist and flexible moving individuals, and individuals further distinguish themselves as specialist/flexible hunters with experience (Figure 2).
 
@@
   font(fontname = "Times New Roman", part = "all") %>%
-  width(j = c(1:5), width = 3.7, unit = "cm")
+  width(j = c(1,3,4,5), width = 3.7, unit = "cm") %>%
+  width(j = 2, width = 3.2, unit = "cm")
 
@@
   tab2,
-  caption = "Posterior mean estimates and 95% credible intervals computed by the multivariate double-hierarchical generalized linear model of predator speed, prey speed, and predator hunting success.",
+  caption = "Posterior mean estimates and their 95% credible intervals computed from the MDHGLM of predator speed, prey speed, and predator hunting success.",
   style = "Table Caption"
 )
+
 ```
 
-As we predicted, individual predators encountered prey with varying levels of speed ($ICC\ predator\ ID$, Table 2).
-Similar to the predator's speed, prey encounters varied more among predators at the novice and advanced levels, and predators differed more in the mean speed of prey that they encountered at the advanced stage (Table 2).
-Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster.
-These encounters also varied slightly among the predator avatars and virtual environments, but did not change with experience (Table 2).
-However, predators differed only weakly in the variability between prey encounters that they experienced ($CV_p\ predator\ ID$, Table 2).
-Hence, while predators did differ in the mean speed of the prey that they encountered, they all experienced similar degrees of variation among encounters (Table 2).
+As we predicted, predators differed in the speed of the prey that they encountered.
+Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period ($SD\ predator\ ID$, Table 2).
+These differences were greater when predators reached an advanced level of hunting experience (Table 2 and Figure S4).
+In addition, individuals experienced largely distinct degrees of variability among their encounters with the prey ($SD\ predator\ ID$, Table 2).
+Hence, some predators experienced stable/predictable encounters with their prey, while others experienced unstable/unpredictable encounters with their prey throughout the study period.
 
@@
 
+Outline of the main results
+
+## Individuals differ in the development of their expertise
+
+## Specialization does not change with experience at the population level
+
+## Individuals either specialize or increase their flexiblity with experience
+
+## Experience strenghens predator-prey interactions
+
+## Experience dampens the relationship between behaviour and success
+
 \newpage

### 2023-02-09 manuscript/Chapter2-manuscript.Rmd
update text methods and results

@@
 Thus, in the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e.
-fast or slow), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization.
+fast or slow), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization/flexibility (i.e.
+intra-individual variability).
 We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation in speed of the prey encountered by predators.
@@
 These differences remained stable (although they decreased minimally) at the intermediate stage (Table 2 and Figure S4), and increased at the advanced stage to a level higher than when predators were novice (Table 2 and Figure S4).
-The largest proportion of variation in mean predator speed was attributed to differences among predator avatars ($ICC\ avatar\ ID$, Table S1), and these differences increased with experience ($SD\ avatar\ ID$, Table 2).
-The variation in mean predator speed among the virtual environments was very low ($SD\ environment\ ID$, Table 2).
 For the dispersion part of the model (i.e.
 sigma predator speed), predators displayed considerable differences in their degree of hunting specialization, which also increased with experience ($SD\ predator\ ID$, Table 2 and Figure S4).
-Thus, the predator population is composed of both specialist and flexible moving individuals, and individuals further distinguish themselves as specialist/flexible hunters with experience (Figure 2).
+Thus, the predator population is composed of both specialist and flexible moving individuals, and they further distinguish themselves as specialist/flexible hunters as they gain experience (Figure 2).
 
@@
 
-At all experience levels, predators that were on average faster (mean) were also travelling faster in all their matches (IIV) (Figure 3-S1).
+At all experience levels, predators that were on average faster (mean) had also a lower intra-individual variability (IIV) across their matches (Figure 3 and Table S1).
 Thus, faster predators specialized at travelling fast, while slower predators were more flexible in their movement through time.
-In general, predators tended to be faster (mean) when they encountered prey that were on average faster (mean) (Figure 3-S1).
-At the three experience levels, there were only weak correlations between predator IIV and mean prey speed (Figure 3-S1).
-Similarly, predators specialized in a faster foraging mode (IIV) when encounters with prey were more predictable (IIV), but the correlations were weak (Figure 3-S1).
-In the four cases described above, the correlations became stronger as predators gained experience (Figure 3-S1).
+In general, predators that encountered prey that were on average faster (mean) tended to be faster (mean) (Figure 3 and Table S1).
+At the three experience levels, there were only weak correlations between predator IIV and mean prey speed (Figure 3 and Table S1).
+However, predators that experienced more predictable encounters with their prey (IIV) specialized in a faster hunting tactic (IIV) (Figure 3 and Table S1).
+For all the results described above, the correlations became stronger as predators gained experience (Figure 3 and Table S1).
 
-The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience.
-For instance, novice predators that tended to be faster also kept this strategy as they gained experience (Figure 3 inside the black squares).
-Overall, we detected the same patterns for within-experience state correlations.
-The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that behavioural changes in predators occurred as they gained experience.
+The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience (Figure 3 inside the black circles and Table S1).
+For instance, novice predators that tended to be faster also kept this strategy as they gained experience (Figure 3 inside the black squares and Table S1).
+Overall, we detected the same patterns than those from the within-experience state correlations described above.
+The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that the behavioural tactics of predators were more similar among experience levels closer in time (Figure 3 inside the black circles and Table S1).
 
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Full correlation matrix of the MDHGLM relating the mean and IIV speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Full correlation matrix of the MDHGLM relating the mean and intra individual variability (IIV) in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
 Starting from the upper part of the plot are displayed the five parameters for novice predators (gray), the five for intermediate predators (yellow), and the five for advanced predators (blue).
@@
 
-We did not detect strong correlations between the predators' average speed and hunting success (Figure 3-S1), nor between the IIV in speed and hunting success (Figure 3-S1), suggesting that both slower/flexible and faster/specialist predators were both equally successful.
-However, when predators were novice, there was a strong negative correlation between the average speed of the prey that they encountered and their hunting success (Figure 3-S1).
+We did not detect strong correlations between the predators' average speed and their hunting success (Figure 3 and Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Table S1), suggesting that both slower/flexible and faster/specialist predators were both equally successful.
+However, when predators were novice, there was a strong negative correlation between the average speed of the prey that they encountered and their hunting success (Figure 3 and Table S1).
 Hence, novice individuals that encountered faster prey were less successful.
-This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3-S1).
+This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Table S1).
 
@@
 
-## Experience strenghens predator-prey interactions
+## Experience strenghtens predator-prey interactions
 

### 2023-02-15 manuscript/Chapter2-manuscript.Rmd
update ref on MS

@@
 It may also be costly to attempt different hunting tactics by trial and error when prey are scarce or highly unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
-An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset by gaining experience and information on their prey, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013].
+An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset by gaining experience and information on their prey, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;Kelley.Magurran2011;@Snell-Rood2013].
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, followed by higher performance at later stages of development [reviewed in @Snell-Rood2013].

### 2023-02-15 code/05_code_figures/05_figureS3.R
update fig s3 title code

@@ -1,6 +1,6 @@
 # ===========================================================================
 
-#                        Code to produce Table S3                           #
+#                        Code to produce Figure S3                          #
 
 # ===========================================================================
 

### 2023-02-15 manuscript/Chapter2-SupInfo.Rmd
update supmat

--- 2023-01-31 manuscript/Chapter2-SupInfo.Rmd
@@
 ---
-title: "Hunting experience and prey behaviour shape individual foraging specialisation in a predator-prey videogame"
+title: |
+     Online supporting information for \
+     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame
+
 output: 
@@
 
+\newpage
+# Materials and methods
+
+## Statistical analyses
+
+### Prior specifications
+
 need to talk about priors here for the gamms etc
+
+### Variance partitionning
+
+We calculated the intra-class correlation coefficients ($ICC$, i.e.
+repeatability) of each random effect on the mean part of the predator's speed and prey speed to estimate the percentage of variation in speed attributed to differences among environments, avatars, and individuals.
+We also report the coefficient of variation in the mean (termed $CV_I$) and dispersion (termed $CV_p$) part of the predator and prey's speed, at each stage of experience, to report standardized effect sizes of individual variation for comparison across traits and studies [@cleasbyQuantifyingPredictabilityBehaviour2015;@Holtmann.etal2017;@Dingemanse.etal2022].
+This also allowed us to evaluate whether predators displayed increasing/decreasing differences in specialization at each stage of experience.
+
+\newpage
+# Results
 
@@
 ```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Distribution of the intra individual behavioural variation (i.e.
-specialization) of predators with the greatest increase in hunting success (A and B) and greatest decrease (B and C) in hunting success when they were novices (A and C) and then (B and D) advanced hunters."}
+specialization) of predators with the greatest increase in hunting success (A and B) and greatest decrease (C and D) in hunting success when they were novices (A and C) and then (B and D) advanced hunters."}
 
@@
 ```
+
+```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
+The test is displayed on the y axis (i.e.
+whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis.
+Each panel represent the experience level groups that are being compared."}
+
+knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS4.png"))
+
+```

### 2023-02-17 manuscript/Chapter2-manuscript.Rmd
started writting the discussion. 1st parargraph

@@
 
-The integration of individual behavioural variation in the study of predator-prey interactions has gained traction in recent years, with empirical studies revealing important consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
-However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
-We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge and help uncovering the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
-For instance, we found that the classical locomotor crossover hypothesis [@Huey.Pianka1981] applied only for cursorial hunters [see also: @Matsumura.Miyatake2022a], suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
-Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
-in prep).
-Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with its potential fitness consequences.
-
 The development of foraging tactics is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
@@
 @Dukas2019 defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
-This body of work suggests that the development of expertise is an optimizing process that promotes foraging specialization.
+This body of work suggests that the development of expertise through extensive practice is an optimizing process that promotes foraging specialization.
 Empirical studies on human and non-human hunters show that experience optimizes the efficiency (e.g.
@@
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, followed by higher performance at later stages of development [reviewed in @Snell-Rood2013].
-However, individuals may face different challenges during their lifetime, which could lead to both mechanisms operating at the same time within a population.
+However, individuals may differ in the challenges that they face during their lifetime, which could lead to both mechanisms operating at the same time within a predator population.
 
@@
 Thus, uncovering the mechanisms shaping direct predator-prey interactions would enable researchers to better predict the behavioural decisions that predators take when they are hunting.
+
+The integration of individual behavioural variation in the study of predator-prey interactions has gained traction in recent years, with empirical studies revealing important consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
+However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
+We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge and help uncovering the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
+For instance, we found that the classical locomotor crossover hypothesis [@Huey.Pianka1981] applied only for cursorial hunters [see also: @Matsumura.Miyatake2022a], suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
+Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
+in prep).
+Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with its potential fitness consequences.
 
@@
 We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$).
-We estimated the parameters in all models using four MCMC chains with 1000 posterior samples for each parameter.
+We used Gaussian priors for the game duration ($N(0,\ 1)$), the intercept ($N(0,\ 0.5)$), and the precision paremeter ($N(2,\ 0.5)$).
+We employed the default Student t priors for the smoothing parameter ($t(3,\ 0,\ 2.5)$).
+In all models, we specified four MCMC chains to estimate the parameters, with 1000 posterior samples for each parameter.
 To do so, we ran 2500 iterations for the first model with a thinning set to eight, and 1500 iterations with a thinning set to four for the second and third models; burn-in was set to 500 iterations in each model.
-We provide a description of how we specified the priors for each model in the supporting information.
 After fitting the three models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
@@
 
-Our results confirm that individual predators displayed important differences in the development of their expertise, as the best model was the one with group-level smoothers exclusively (Table I).
+Our results confirm that individual predators displayed substantial differences in the development of their expertise, as the best model was the one with group-level smoothers exclusively (Table I).
 For instance, with experience, some predators steadily increased their hunting success while others displayed a decrease in prey capture (Figure 1A-S1).
@@
 
-Outline of the main results
+For decades, hunting experience has been hypothesized to play a major role in predator-prey interactions [].
+Yet, the lack of empirical evidence has led the existing literature to predict conflicting outcomes [].
+It has thus remained unclear whether predators specialize in their tactic with experience, how such specialization emerges depending on the type of prey that predators encounter, and whether specialization with experience leads to an increase in hunting success.
+We adressed these questions by capitalizing on an online videogame system simulating a predator-prey interaction, where both the predator and the prey behaviours are simultaneously monitored.
+Our results show that experience does not generate responses at the population level.
+Instead, experience appears to be a property of individuals, such that each predator developed, through extensive practice, their own behavioural trajectory.
+Individuals became increasingly distinct hunters with experience; some specialized at fast-paced hunting, while others adopted a slower and more flexible tactic.
+The predators' tactics were also associated with prey encounters, such that those that adopted a specialized cursorial tactic experienced more predictable encounters, while slower and flexible hunters experienced more unpredictable encounters, with no difference in success between the two types of hunters.
+With experience, this predator-prey behavioural relationship grew stronger, while the relationship between the prey's behaviour and hunting success diminished.
+Together, our observations suggest that predators use their experience to adjust their hunting tactic, and the degree at which they specialize in it, based on the prey that they encountered throughout their lifetime.
+Moreover, the stronger predator-prey interaction through experience may imply the emergence of an arms race mediated through learning.
 
-## Individuals differ in the development of their expertise
+## The role of hunting experience on the predator's foraging behaviour
 
-## Specialization does not change with experience at the population level
+- Individuals differ in the development of their expertise
 
-## Individuals either specialize or increase their flexiblity with experience
+- Specialization does not change with experience at the population level
 
-## Experience strenghtens predator-prey interactions
+- Individuals either specialize or increase their flexiblity with experience
 
-## Experience dampens the relationship between behaviour and success
+*This has important implications for future theoretical models predicting a directional increase in specialization or flexibility.
+should incorporate individual variation if both mechanisms operate at the same time*
+
+## Predator-prey interactions change with experience
+
+- Experience strenghtens predator-prey interactions
+
+- Experience dampens the relationship between behaviour and success
 

### 2023-02-21 manuscript/Chapter2-manuscript.Rmd
update hypotheses

@@
 
-In this study, we analyze individual behavioural data from players in *Dead by Daylight* (*DBD*) to test how hunting experience shapes predator foraging specialization during direct behavioural interactions with prey.
-*DBD* is an online videogame simulating a predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
-The data grants a high degree of precision on the behavioural interaction as the behaviour of both the predator and the four prey is monitored simultaneously in each trial.
+In this study, we test how hunting experience shapes predator foraging specialization using individual behavioural data from players in the online videogame *Dead by Daylight* (*DBD*).
+*DBD* simulates a direct predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
+The data grants a high degree of precision on the behavioural interaction, as the behaviour of both the predator and the four prey is monitored simultaneously in each trial.
 First, we investigate how predators develop their individual hunting expertise.
@@
 Otherwise, if both mechanisms operate at the same time, then we should see no change with experience at the population level, but differences in specialization among individuals should increase.
-Third, we evaluate how predator foraging specialization interacts with variation in prey behaviour.
-Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize when encounters are less predictable.
-Lastly, if individuals differ in their degree of foraging specialization, then we expect specialized hunters to fare better when prey variability is lower, while flexible hunters should fare better when prey variability is higher.
+Third, we evaluate how predator foraging specialization emerges from behavioural interactions with prey.
+Whether predators specialize or not with experience should depend on the behaviour of their prey.
+We expect that predators that experienced more predictable encounters with their prey will specialize, while predators that experienced unpredictable encounters with their prey should adopt a flexible hunting strategy.
+If we detect such prey-dependent fine-tuning, then specialist and flexible hunters should attain equal success.
 

### 2023-02-21 manuscript/Chapter2-manuscript.Rmd
include prior description mdhglm

@@
 Here, we assume that the residuals vary among individuals where $e \sim N(0,\ Diag\ [\sigma_{e}])$, $[\begin{array}{cc} id_m \\ id_v \end{array}] \sim N\left(\begin{array}{cc} 0 \\ \\ 0 \end{array},\ \Sigma_{id} \otimes\ I \right)$, and $\Sigma_{id}$ is a variance covariance matrix of the individual identity random effect.
-Equations (1) and (2) were parametrized with a Gaussian distribution family (predator and prey speed), while equation (3) was parametrized with a beta-binomial distribution family (predator hunting success).
+
+We parameterized equations (1) and (2) with a Gaussian distribution family (predator and prey speed), and employed a beta-binomial distribution family for equation (3) (predator hunting success).
+We employed Gaussian priors for the prey rank ($N(2.5,\ 1)$) and game duration ($N(10,\ 2)$) on the mean part of the model, and the default priors in "brms" for the dispersion part.
+We used the default Student t priors in "brms" for the intercepts on the mean and dispersion part of the equation.
+For hunting success, we applied a Gaussian prior on the precision parameter ($N(2,\ 1)$).
+For every predicted variable, we applied a half-Gaussian on the random effects for the mean part of the model ($N(0,\ 1)$), and the default "brms" Student t prior for the dispersion part of the model.
 We parametrized the model to run four MCMC chains with 1000 posterior samples for each parameter.
 To do so, we ran 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups.
-We explain how we specified the priors of the MDHGLM in the supporting information.
 
@@
 The correlations were estimated assuming a multivariate Gaussian distribution.
-We also report additional analyses, such as variance partitioning, and coefficients of variation, in the supporting information.
+We additionaly report variance partitioning and coefficients of variations in the supporting information.
 
@@
 
-For decades, hunting experience has been hypothesized to play a major role in predator-prey interactions [].
+Hunting experience has long been hypothesized to play an important role in predator-prey interactions [].
 Yet, the lack of empirical evidence has led the existing literature to predict conflicting outcomes [].

### 2023-02-21 manuscript/Chapter2-SupInfo.Rmd
remove priors supmat. need to add priors in ms
update supmat

@@
 \newpage
-# Materials and methods
-
-## Statistical analyses
-
-### Prior specifications
-
-need to talk about priors here for the gamms etc
-
-### Variance partitionning
-
-We calculated the intra-class correlation coefficients ($ICC$, i.e.
-repeatability) of each random effect on the mean part of the predator's speed and prey speed to estimate the percentage of variation in speed attributed to differences among environments, avatars, and individuals.
-We also report the coefficient of variation in the mean (termed $CV_I$) and dispersion (termed $CV_p$) part of the predator and prey's speed, at each stage of experience, to report standardized effect sizes of individual variation for comparison across traits and studies [@cleasbyQuantifyingPredictabilityBehaviour2015;@Holtmann.etal2017;@Dingemanse.etal2022].
-This also allowed us to evaluate whether predators displayed increasing/decreasing differences in specialization at each stage of experience.
-
-\newpage
-# Results
 

### 2023-02-24 manuscript/Chapter2-manuscript.Rmd
minor text update in methods MS
update MS

@@
 ---
-title: "Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame"
+title: "Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame"
 output: 
@@
 bibliography: references.bib
-csl: e-letters.csl
+csl: ecology.csl
 ---
@@
 
+Journal name : Ecology
+
+Manuscript type : article
+
+Authors : Maxime Fraser Franco^1^, Francesca Santostefano^1,2^, Julien G. A. Martin^3^, Clint D. Kelly^1^, Pierre-Olivier Montiglio^1^
+
+Affiliations : ^1^ Département des Sciences Biologiques, Université du Québec à Montréal, Montréal, QC, Canada.
+^2^ Centre for Ecology and Conservation, Penryn Campus, University of Exeter, Cornwall, United Kingdom.
+^3^ Department of Biology, University of Ottawa, Ottawa, ON, Canada.
+
+Corresponding author : fraser_franco.maxime@courrier.uqam.ca
+
+Open research statement : The data and code used to produce the results in this manuscript are freely available on GitHub https://github.com/quantitative-ecologist/experience-hunting-tactics
+
+Keywords: foraging behaviour, individual specialization, learning, behavioural plasticity, prey predictability, online videogames
+
 \newpage
 # ABSTRACT {.unnumbered}
-
-Keywords: foraging behaviour, individual specialization, experience, learning, prey predictability, online videogames
 
@@
 It may also be costly to attempt different hunting tactics by trial and error when prey are scarce or highly unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
-An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset by gaining experience and information on their prey, leading to increased individual foraging flexibility [@Ishii.Shimada2010;@Mery.Burns2010;Kelley.Magurran2011;@Snell-Rood2013].
+An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset by gaining experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;Kelley.Magurran2011;@Snell-Rood2013].
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, followed by higher performance at later stages of development [reviewed in @Snell-Rood2013].
@@
 This is reflected in the literature showing contrasting results in the links between specialization and fitness.
-For instance, some studies report increasing benefits of specialization [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
+For instance, some studies report increasing benefits of specialization [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
 While quantifying the fitness consequences of specialization is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
@@
 In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-This hypothesis has, however, not been tested in systems where behavioural interactions are simultaneously monitored between predator and prey individuals.
-Thus, uncovering the mechanisms shaping direct predator-prey interactions would enable researchers to better predict the behavioural decisions that predators take when they are hunting.
+At the phenotypic interface, empirical evidence shows coevolutionary patterns of predator-prey phenotypic matching across space and time [@Kishida.etal2006;@Hanifin.etal2008;@Reimche.etal2020].
+However, we do not know how experience influences these interactions in systems where behavioural interactions between predators and prey are directly monitored.
+Thus, uncovering how learning mechanisms shape direct predator-prey interactions would enable researchers to better predict the behavioural decisions that predators take when they are hunting.
 
@@
 
-\newpage
 # MATERIALS AND METHODS {.unnumbered}
@@
 The operating system for Cedar is CentOS Linux 7.
-The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo sampling with the package "brms" version 2.16.3 [@Burkner2017], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the backend for estimation (cmdstan installation version 2.28.2).
+The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
 
@@
 To do so, we ran 2500 iterations for the first model with a thinning set to eight, and 1500 iterations with a thinning set to four for the second and third models; burn-in was set to 500 iterations in each model.
+We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.05, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021].
 After fitting the three models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
@@
 The correlations were estimated assuming a multivariate Gaussian distribution.
-We additionaly report variance partitioning and coefficients of variations in the supporting information.
+We additionally report variance partitioning and coefficients of variations in the supporting information.
 
-\newpage
 # RESULTS {.unnumbered}
@@
 
-Hunting experience has long been hypothesized to play an important role in predator-prey interactions [].
-Yet, the lack of empirical evidence has led the existing literature to predict conflicting outcomes [].
-It has thus remained unclear whether predators specialize in their tactic with experience, how such specialization emerges depending on the type of prey that predators encounter, and whether specialization with experience leads to an increase in hunting success.
-We adressed these questions by capitalizing on an online videogame system simulating a predator-prey interaction, where both the predator and the prey behaviours are simultaneously monitored.
-Our results show that experience does not generate responses at the population level.
-Instead, experience appears to be a property of individuals, such that each predator developed, through extensive practice, their own behavioural trajectory.
-Individuals became increasingly distinct hunters with experience; some specialized at fast-paced hunting, while others adopted a slower and more flexible tactic.
-The predators' tactics were also associated with prey encounters, such that those that adopted a specialized cursorial tactic experienced more predictable encounters, while slower and flexible hunters experienced more unpredictable encounters, with no difference in success between the two types of hunters.
-With experience, this predator-prey behavioural relationship grew stronger, while the relationship between the prey's behaviour and hunting success diminished.
-Together, our observations suggest that predators use their experience to adjust their hunting tactic, and the degree at which they specialize in it, based on the prey that they encountered throughout their lifetime.
-Moreover, the stronger predator-prey interaction through experience may imply the emergence of an arms race mediated through learning.
+Hunting experience is predicted to imbue an increase in predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009;@Dukas2019].
+Other lines of research view learning from experience as a form of behavioural plasticity [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022], with theoretical models predicting an increase in flexibility from experience when resources are variable [@Stephens1993].
+Our results challenge the hypothesis that experience generates population-level behavioural responses.
+Instead, experience appears to be a property of individuals, such that each predator developed, through extensive practice, their own behavioural trajectory; some specialized at fast-paced hunting, while others adopted a slower and more flexible tactic.
+The predators' tactics were matched to prey encounters, such that specialized cursorial hunters experienced more predictable encounters, while slower and flexible hunters experienced more unpredictable encounters, with no difference in success between the two predator-types.
+This predator-prey behavioural matching grew stronger with predator experience, while the relationship between the prey's behaviour and hunting success diminished.
+Together, our observations suggest that predators learn to adjust their hunting tactic with experience, and the degree at which they specialize in it, based on the behaviour of the prey that they encountered throughout their lifetime.
+Moreover, the intensification of the interaction through experience suggests that learning may be a catalyst for predator-prey's arms races.
 
-## The role of hunting experience on the predator's foraging behaviour
+## How hunting experience shapes foraging behaviour
 
-- Individuals differ in the development of their expertise
+*- Individuals differ in the development of their expertise*
+One of the main results of our study is that predators develop their own... (parler d'expertise et comportement)
 
-- Specialization does not change with experience at the population level
+*- Specialization does not change with experience at the population level*
 
-- Individuals either specialize or increase their flexiblity with experience
+*- Individuals either specialize or increase their flexiblity with experience*
 
-*This has important implications for future theoretical models predicting a directional increase in specialization or flexibility.
-should incorporate individual variation if both mechanisms operate at the same time*
+This has important implications for future theoretical models predicting a directional increase in specialization or flexibility.
+should incorporate individual variation if both mechanisms operate at the same time.
 
-## Predator-prey interactions change with experience
+**keep Warburton, 2003 in mind as a ref**
+**Check Endler 1991 too from Kelley and Magurran**
+**Try to find again the ref saying that high speed prey are more difficult**
 
-- Experience strenghtens predator-prey interactions
+## Consequences of hunting experience for predator-prey interactions
 
-- Experience dampens the relationship between behaviour and success
+*- Experience strengthens predator-prey interactions*
+
+Contrary to Hanifin et al. 2008, we find a directional symmetry (i.e. trait matching).
+Our results are similar to Szopa-Comley and Ioannou 2022. Adjustments based on prey. Le predateur s'ajuste dans le traitement unpredictable.
+In abrams 2000, we read : "The interaction of predator and prey traits in determining capture rate seems to be the most important factor determining the stability of the entire system.
+Most studies in which cycles are a commonly observed outcome assume that the predator maximizes its rate of capture of the prey by matching the prey's phenotype"
+We can also read : "If there is sufficiently strong stabilizing selection based on the costs of extreme trait values in both species, then stable equilibria are likely"
+In Reimche et al. 2020 : in the discussion we can read that we still don't understand the factors driving phenotypic (mis)matching. In my case, it appears that learning may play a role.
+Revoir mes résultats dans le cadre des résultats de Glaudas et al. 2019. Les 2 concordent bien.
+Voir Miszei comme exemple parmi d'autres pour trait matching.
+check Mougi etal. 2011 for arms-races based on phenotypic plasticity!
+
+Our results also have implications also for predator-prey models of trait-matching, because such models are usually studied at the evolutionary scale.
+
+*- Experience dampens the relationship between behaviour and success*
+
+**Check if I should add the role of phenotypic matching in the intro, and the role of learning**
+
+# Aknowledgements
+
+...
+
+# Conflict of Interest Statement
+
+The authors declare no conflict of interest
 
 \newpage
-# LITTERATURE CITED {.unnumbered}
+# REFERENCES {.unnumbered}
 

### 2023-02-24 manuscript/Chapter2-manuscript.Rmd
update MS. re-added v4 updated.

@@
 It may also be costly to attempt different hunting tactics by trial and error when prey are scarce or highly unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
-An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset by gaining experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;Kelley.Magurran2011;@Snell-Rood2013].
+An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset by gaining experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, followed by higher performance at later stages of development [reviewed in @Snell-Rood2013].
@@
 Together, our observations suggest that predators learn to adjust their hunting tactic with experience, and the degree at which they specialize in it, based on the behaviour of the prey that they encountered throughout their lifetime.
-Moreover, the intensification of the interaction through experience suggests that learning may be a catalyst for predator-prey's arms races.
+Moreover, the intensification of the interaction through experience suggests that learning may be a catalyst for predator-prey arms races.
 

### 2023-02-27 manuscript/Chapter2-manuscript.Rmd
update MS intro + 1st par discussion

@@
 dat <- fread(
-  file.path(path, "FraserFrancoetalXXXX-data.csv"),
+  file.path(path, "FraserFrancoetal2023-data.csv"),
   select = c("timestamp", "match_id", "realm_id",
@@
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, followed by higher performance at later stages of development [reviewed in @Snell-Rood2013].
-However, individuals may differ in the challenges that they face during their lifetime, which could lead to both mechanisms operating at the same time within a predator population.
+However, predators can differ in the challenges that they face during their lifetime, which could lead to both mechanisms operating at the same time within a predator population.
+For instance, some individuals may constantly encounter faster prey, which are proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@FraserFranco.etal2022].
 
@@
 In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-At the phenotypic interface, empirical evidence shows coevolutionary patterns of predator-prey phenotypic matching across space and time [@Kishida.etal2006;@Hanifin.etal2008;@Reimche.etal2020].
-However, we do not know how experience influences these interactions in systems where behavioural interactions between predators and prey are directly monitored.
-Thus, uncovering how learning mechanisms shape direct predator-prey interactions would enable researchers to better predict the behavioural decisions that predators take when they are hunting.
+At the phenotypic interface, empirical evidence shows that predators often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
+Yet, a recurring question that emerges from these studies is if and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011].
+Thus, uncovering the role of learning in predator-prey systems where interactions are directly monitored would enable researchers to better predict the behavioural decisions and success of predators when they are hunting.
 
@@
 in prep).
-Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with its potential fitness consequences.
+Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with their potential fitness consequences.
 
@@
 We hypothesize that predators should differ in the development of their expertise, partly because they encounter varying levels of difficulty with the prey that they pursue.
-For example, a predator may face greater difficulty than other individuals if it more often encountered prey that were elusive [@FraserFranco.etal2022].
+For example, a predator may face greater difficulty than other individuals if it more often encountered prey that were elusive.
 Second, we test the hypothesis that experience will shape foraging specialization.
@@
 Together, our observations suggest that predators learn to adjust their hunting tactic with experience, and the degree at which they specialize in it, based on the behaviour of the prey that they encountered throughout their lifetime.
-Moreover, the intensification of the interaction through experience suggests that learning may be a catalyst for predator-prey arms races.
+Moreover, the behavioural escalation through experience suggests that learning may be a catalyst for predator-prey arms races.
 
@@
 
-**Check if I should add the role of phenotypic matching in the intro, and the role of learning**
+**Check if I should add the role of phenotypic matching in the intro, and the role of learning [added a sentence]**
+**may add a sentence to better explain why prey difficulty is important. See Prokopenko and also Novak**
+**garder en tête l'étude de Lima AmNat sur purposeful unpredictability**
+**Iannou also found strong among individual differences in slopes of trial number**
 

### 2023-03-09 manuscript/Chapter2-manuscript.Rmd
updated the discussion

@@
 @Dukas2019 defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
-This body of work suggests that the development of expertise through extensive practice is an optimizing process that promotes foraging specialization.
+This body of work suggests that the development of expertise through extensive practice is an optimizing process that should promote foraging specialization.
 Empirical studies on human and non-human hunters show that experience optimizes the efficiency (e.g.
@@
 
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Distribution of the intra individual behavioural variation (i.e.
-specialization) of predators when they were (A) novices and then (B) advanced hunters.
-The red band displays the 95% CI of the intercept for the intra individual standard deviation in predator speed."}
+```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
+The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters."}
 
@@
 
-Hunting experience is predicted to imbue an increase in predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009;@Dukas2019].
+Hunting experience is predicted to imbue an increase in predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
 Other lines of research view learning from experience as a form of behavioural plasticity [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022], with theoretical models predicting an increase in flexibility from experience when resources are variable [@Stephens1993].
-Our results challenge the hypothesis that experience generates population-level behavioural responses.
-Instead, experience appears to be a property of individuals, such that each predator developed, through extensive practice, their own behavioural trajectory; some specialized at fast-paced hunting, while others adopted a slower and more flexible tactic.
+Our results challenge the hypothesis that experience should generate a directional population-level increase in behavioural specialization or plasticity.
+Instead, the consequences from experience appear to be a property of individuals, such that each predator developed, through extensive practice, their own expertise and behavioural trajectory; some specialized at fast-paced hunting, while others adopted a slower and more flexible tactic.
 The predators' tactics were matched to prey encounters, such that specialized cursorial hunters experienced more predictable encounters, while slower and flexible hunters experienced more unpredictable encounters, with no difference in success between the two predator-types.
@@
 
-## How hunting experience shapes foraging behaviour
+## The development of expertise with hunting experience
 
-*- Individuals differ in the development of their expertise*
-One of the main results of our study is that predators develop their own... (parler d'expertise et comportement)
+Empirical studies in humans and animals show that proficiency in a given task often increases nonlinearly with experience, and stabilizes when an expert level is reached [reviewed in @Dukas2019].
+However, these patterns are derived from models that assume the same increase in expertise for each individual, and their data do not include repeated measures of individual success through time.
+In contrast with these studies, our analyses revealed that there was no population increase in expertise; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition.
+For instance, many predators increased their success (Figure S1A), but others displayed a decrease in success (Figure S1B) or no change in success at all with experience.
+We predicted that this would occur because predators should differ in the type of prey that they encounter, as some may be easier to capture than others.
+This is often the case in nature as prey can use variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
+However, our results show that the speed of the prey did not shape individual differences in skill aquisition by predators, even if they differed in the prey that they encountered.
+This was unexpected, because prey speed is an important predictor of predator success in this system [@FraserFranco.etal2022] as well as in others [@Walker.etal2005;@Kelley.Magurran2011].
+Despite that other antipredator tactics may mediate these individual responses by predators, it is likely that individual differences in motivation and perseverance, attention span, or memory retention were also major causes [@Warburton2003;@morand-ferronStudyingEvolutionaryEcology2016;@Dukas2019].
+For instance, a persevering predator may increase its success much more steadily than an unmotivated predator that quickly abandons a chase.
+Another factor that may explain differences in the development of expertise is the time delay between hunting events, such that a predator that played 300 matches in the span of six months may not retain information (e.g.
+prey escape patterns or muscle memory) as well as one that played 300 matches in the span of 6 days.
+While this has not been tested yet in a predator-prey interaction, it is hypothesized that a greater delay between exposure events should attenuate or even negate the relationship between cumulative experience and success as a result of forgetting [@Endler1991;@Wright.etal2022].
 
-*- Specialization does not change with experience at the population level*
+## Changes in individual hunting specialization with experience and consequences for predator-prey interactions
 
-*- Individuals either specialize or increase their flexiblity with experience*
+We detected a similar pattern for foraging specialization, such that individual differences increased with experience, while specialization at the population level remained stable.
+*parler du patron non linéaire et donner quelques potentielles explications liées à l'exploration + grande chez les juvéniles*.
+*Je peux citer les sources de Phillips et al : Thiers 2014 et Grissac 2016*.
 
-This has important implications for future theoretical models predicting a directional increase in specialization or flexibility.
-should incorporate individual variation if both mechanisms operate at the same time.
+Predators that experienced predictable encounters with their prey specialized in hunting at high speeds, while those that experienced more unpredictable encounters adopted a slower and flexible strategy.
+This is similar to other studies finding that fast-paced hunting is a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022].
+On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty.
+Interestingly, both specialist and flexible hunters fine-tuned their tactic to their prey as they gained experience, suggesting that they learned how to hunt their prey.
+In that regard, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning to adjust their degree of specialization based on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
+This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period.
+Therefore, our results have important implications for future predator-prey models, which should incorporate individual variation in learning and prey encounters to better predict under which ecological contexts specialization should be favoured over flexibility.
 
-**keep Warburton, 2003 in mind as a ref**
-**Check Endler 1991 too from Kelley and Magurran**
-**Try to find again the ref saying that high speed prey are more difficult**
-
-## Consequences of hunting experience for predator-prey interactions
-
+*je peux commencer à plug le arms race dans ce paragraphe.*
+*il faut aussi que je parle du fait que la variation dans le succès de capture a diminué avec l'XP*
 *- Experience strengthens predator-prey interactions*
+*- Experience dampens the relationship between behaviour and success*
 
@@
 
-Our results also have implications also for predator-prey models of trait-matching, because such models are usually studied at the evolutionary scale.
-
-*- Experience dampens the relationship between behaviour and success*
-
-**Check if I should add the role of phenotypic matching in the intro, and the role of learning [added a sentence]**
-**may add a sentence to better explain why prey difficulty is important. See Prokopenko and also Novak**
 **garder en tête l'étude de Lima AmNat sur purposeful unpredictability**
 **Iannou also found strong among individual differences in slopes of trial number**
+
+*Our results also have implications also for predator-prey models of trait-matching, because such models are usually studied at the evolutionary scale.*
 

### 2023-03-10 manuscript/Chapter2-manuscript.Rmd
knitted the changes

@@
 
-Keywords: foraging behaviour, individual specialization, learning, behavioural plasticity, prey predictability, online videogames
+Keywords: foraging behaviour, individual specialization, behavioural plasticity, learning, prey predictability, virtual ecology
 
@@
 
-```{r, eval=FALSE}
-
-# =======================================================================
-
-# Extract the correlations to report values in the text
-
-# =======================================================================
-
-# =======================================================================
-# Prepare the draws
-# =======================================================================
-
- # Model
- path <- here::here("outputs", "02_outputs_models")
- fit <- readRDS(file.path(path, "02B_DHMLM.rds"))
-
- # Extract the draws
- draws <- data.table(
-     as_draws_df(
-         fit,
-         variable = c("cor"),
-         regex = TRUE)
- )
-
- draws[, c(106:109) := NULL]
-
- # =======================================================================
- # =======================================================================
-
- # =======================================================================
-# 2. Transform the draws table
-# =======================================================================
-
-# Reshape the table -----------------------------------------------------
-
- # Long format
- table <- melt(draws,
-               measure = patterns("^cor_predator_id"),
-               variable.name = "correlation")
-
- # Summarize the values (means + 95% CI) ---------------------------------
-
- # Intervals
- lower_interval <- function (x) {coda::HPDinterval(as.mcmc(x), 0.95)[1]}
- upper_interval <- function (x) {coda::HPDinterval(as.mcmc(x), 0.95)[2]}
-
- table[, ":=" (mean = mean(value),
-               lower_ci = lower_interval(value),
-               upper_ci = upper_interval(value)),
-       by = .(correlation)]
-
- cor_tab <- unique(table[, c(1, 3:5)])
-
- # Round values to 3 digits
- cor_tab[, c(2:4) := lapply(.SD, function (x) {round(x, digits = 3)}),
-         .SDcols = c(2:4)]
-
-# =======================================================================
-# =======================================================================
-
-```
-
 At all experience levels, predators that were on average faster (mean) had also a lower intra-individual variability (IIV) across their matches (Figure 3 and Table S1).
@@
 This is often the case in nature as prey can use variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-However, our results show that the speed of the prey did not shape individual differences in skill aquisition by predators, even if they differed in the prey that they encountered.
+However, our results show that the speed of the prey did not shape individual differences in skill acquisition by predators, even if they differed in the prey that they encountered.
 This was unexpected, because prey speed is an important predictor of predator success in this system [@FraserFranco.etal2022] as well as in others [@Walker.etal2005;@Kelley.Magurran2011].
@@
 prey escape patterns or muscle memory) as well as one that played 300 matches in the span of 6 days.
-While this has not been tested yet in a predator-prey interaction, it is hypothesized that a greater delay between exposure events should attenuate or even negate the relationship between cumulative experience and success as a result of forgetting [@Endler1991;@Wright.etal2022].
+While this has not been formally tested, it is hypothesized that a greater delay between exposure events should attenuate or even negate the relationship between cumulative experience and success as a result of forgetting [@Endler1991;@Wright.etal2022].
 
@@
 
+```{r eval = FALSE}
 *je peux commencer à plug le arms race dans ce paragraphe.*
@@
 
+```
+
 # Aknowledgements

### 2023-03-13 code/02_code_models/02B2_DHMLM.R
update dhmlmd model 2

@@ -57,10 +57,10 @@ data[, predator_avatar_id := as.factor(avatar_id)]
 
 # Group players by experience
 data[, player_type := "empty"]
-data[total_xp_pred < 50, player_type := "<50"]
-data[total_xp_pred %between% c(50, 99), player_type := ">=50<100"]
-data[total_xp_pred %between% c(100, 299), player_type := ">=100<300"]
-data[total_xp_pred >= 300, player_type := ">=300"]
+data[total_xp_pred < 50, player_type := "early_quitters"]
+data[total_xp_pred %between% c(50, 99), player_type := "mid_quitters"]
+data[total_xp_pred %between% c(100, 299), player_type := "slightly_engaged"]
+data[total_xp_pred >= 300, player_type := "engaged"]
 
 data[, player_type := as.factor(player_type)]
 data[, total_xp_pred := player_type]
@@ -110,7 +110,7 @@ data[, c("sqrt_game_duration", "sqrt_prey_avg_rank") :=
 
 pred_speed <- bf(
   pred_speed ~
-      1 + sqrt_prey_avg_rank +
+      0 + sqrt_prey_avg_rank +
       cumul_xp_pred +
       total_xp_pred +
  #     cumul_xp_pred : total_xp_pred +
@@ -130,7 +130,7 @@ pred_speed <- bf(
 
 prey_speed <- bf(
   prey_avg_speed ~
-      1 + sqrt_prey_avg_rank +
+      0 + sqrt_prey_avg_rank +
       cumul_xp_pred +
       total_xp_pred +
 #      cumul_xp_pred : total_xp_pred +
@@ -172,7 +172,7 @@ stanvars <- stanvar(scode = stan_funs, block = "functions")
 # Sub models
 success <- bf(
   hunting_success | vint(4) ~ 
-      1 + sqrt_game_duration +
+      0 + sqrt_game_duration +
       cumul_xp_pred +
       total_xp_pred +
 #      cumul_xp_pred : total_xp_pred +
@@ -196,12 +196,21 @@ priors <- c(
             resp = c("predspeed",
                      "preyavgspeed")),
   # Prior on total XP
-  set_prior("normal(0, 1)", 
+  set_prior("normal(3, 1)", 
             class = "b",
-            coef = "total_xp_pred",
+            coef = c("total_xp_predearly_quitters",
+                     "total_xp_predengaged",
+                     "total_xp_predmid_quitters",
+                     "total_xp_predslightly_engaged"),
             resp = c("predspeed",
-                     "preyavgspeed",
[…]

### 2023-03-13 manuscript/Chapter2-manuscript.Rmd
update fig 2 caption. add notes MS

@@
 ```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
-The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters."}
+The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
+Both figure panels are ordered by ascending degree of increase in either specialization or flexibility."}
 
@@
 Therefore, our results have important implications for future predator-prey models, which should incorporate individual variation in learning and prey encounters to better predict under which ecological contexts specialization should be favoured over flexibility.
+*important de faire ressortir que c'est seulement 10% des gens qui ont vraiment changé leur comportement de beaucoup.
+Ainsi ça va être + nuancé et me permettre de dire que certains ne répondent pas à l'expérience*.*affirmer que pt qu'ils répondent à d'autres expériences, mais que des contraintes logistiques nous empêchent de savoir quoi*
 

### 2023-03-14 manuscript/Chapter2-manuscript.Rmd
first draft of discussion complete

@@
 Other lines of research view learning from experience as a form of behavioural plasticity [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022], with theoretical models predicting an increase in flexibility from experience when resources are variable [@Stephens1993].
-Our results challenge the hypothesis that experience should generate a directional population-level increase in behavioural specialization or plasticity.
+Our results challenge the hypothesis that experience should generate a directional increase in behavioural specialization or plasticity in a population.
 Instead, the consequences from experience appear to be a property of individuals, such that each predator developed, through extensive practice, their own expertise and behavioural trajectory; some specialized at fast-paced hunting, while others adopted a slower and more flexible tactic.
@@
 
-Empirical studies in humans and animals show that proficiency in a given task often increases nonlinearly with experience, and stabilizes when an expert level is reached [reviewed in @Dukas2019].
-However, these patterns are derived from models that assume the same increase in expertise for each individual, and their data do not include repeated measures of individual success through time.
-In contrast with these studies, our analyses revealed that there was no population increase in expertise; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition.
+Empirical research in humans and animals show that the proficiency in a given task often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
+However, these results are derived from models that assume the same increase in expertise for each individual, and the data from these studies does not include repeated measures of individual success through time.
+In contrast, our analyses revealed that there was no population increase in expertise; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition.
 For instance, many predators increased their success (Figure S1A), but others displayed a decrease in success (Figure S1B) or no change in success at all with experience.
@@
 This is often the case in nature as prey can use variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-However, our results show that the speed of the prey did not shape individual differences in skill acquisition by predators, even if they differed in the prey that they encountered.
-This was unexpected, because prey speed is an important predictor of predator success in this system [@FraserFranco.etal2022] as well as in others [@Walker.etal2005;@Kelley.Magurran2011].
+However, the speed of the prey did not shape individual differences in expertise acquisition by predators, even if they differed in the prey that they encountered.
+This was unexpected, because prey speed is an important predictor of predator success in this system as well as in others [@Walker.etal2005;@Kelley.Magurran2011;@FraserFranco.etal2022].
 Despite that other antipredator tactics may mediate these individual responses by predators, it is likely that individual differences in motivation and perseverance, attention span, or memory retention were also major causes [@Warburton2003;@morand-ferronStudyingEvolutionaryEcology2016;@Dukas2019].
@@
 prey escape patterns or muscle memory) as well as one that played 300 matches in the span of 6 days.
-While this has not been formally tested, it is hypothesized that a greater delay between exposure events should attenuate or even negate the relationship between cumulative experience and success as a result of forgetting [@Endler1991;@Wright.etal2022].
+While this has not been formally tested, it is hypothesized that a greater delay between exposure events should attenuate or even negate the relationship between cumulative experience and success, as a result of forgetting [@Endler1991;@Wright.etal2022].
 
@@
 
-We detected a similar pattern for foraging specialization, such that individual differences increased with experience, while specialization at the population level remained stable.
-*parler du patron non linéaire et donner quelques potentielles explications liées à l'exploration + grande chez les juvéniles*.
-*Je peux citer les sources de Phillips et al : Thiers 2014 et Grissac 2016*.
-
+The predator population displayed an increase in foraging flexibility when they reached an intermediate level of experience.
+As they reached an advanced level of experience, they returned to a level of flexibility that was similar to when they were novices.
+This is comonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016].
+Thus, the predators in *DBD* were probably exploring and refining different tactics at this stage of their development in the game.
+Interestingly, individuals became increasingly distinct in their level of foraging specialization with experience, which was related to the degree of variability in prey encounters.
 Predators that experienced predictable encounters with their prey specialized in hunting at high speeds, while those that experienced more unpredictable encounters adopted a slower and flexible strategy.
@@
 On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty.
-Interestingly, both specialist and flexible hunters fine-tuned their tactic to their prey as they gained experience, suggesting that they learned how to hunt their prey.
+As they gained experience, predators increasingly matched their tactic to their prey, suggesting that they learned how to hunt them throughout repeated interactions.
 In that regard, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning to adjust their degree of specialization based on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
 This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period.
-Therefore, our results have important implications for future predator-prey models, which should incorporate individual variation in learning and prey encounters to better predict under which ecological contexts specialization should be favoured over flexibility.
-*important de faire ressortir que c'est seulement 10% des gens qui ont vraiment changé leur comportement de beaucoup.
-Ainsi ça va être + nuancé et me permettre de dire que certains ne répondent pas à l'expérience*.*affirmer que pt qu'ils répondent à d'autres expériences, mais que des contraintes logistiques nous empêchent de savoir quoi*
+
+An emerging pattern reported in predator-prey research is that predators and prey often match their phenotype to one another (i.e.
+positive trait covariances), which appears to be driven by an arms-race-like reciprocal phenotypic plasticity [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@Mougi.etal2011;@McGhee.etal2013].
+From an evolutionary perspective, @BrodieIII.BrodieJr.1999 showed in the garter snake (*Thamnophis sirtalis*) - roughskin newt (*Taricha granulosa*) system that such escalations may occur when prey develop defensive traits, which leads to stronger selection in predators, resulting in counteradaptations that circumvent the prey's defenses.
+In our system, the predator's success is negatively correlated to the prey's speed, which is an effective antipredator tactic [@FraserFranco.etal2022].
+However, as the covariance between the predator's speed and the speed of the prey encountered increased with experience, reminiscent of an arms race, we found that the fitness consequences of the preys' speed on predators decreased with experience.
+Moreover, this pattern was followed by a decrease in among individual variation in success with experience.
+This has important implications for the role of experience on predator-prey interactions, as we found that learning enables predators to effectively develop countermeasures to the prey's defenses at nonevolutionary timescales.
+It also provides empirical evidence to the idea that reciprocal phenotypic plasticy through learning may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
+
+## Conclusions
 
 ```{r eval = FALSE}
-*je peux commencer à plug le arms race dans ce paragraphe.*
-*il faut aussi que je parle du fait que la variation dans le succès de capture a diminué avec l'XP*
-*- Experience strengthens predator-prey interactions*
-*- Experience dampens the relationship between behaviour and success*
+
+*duckworth en tete*
 
 Contrary to Hanifin et al. 2008, we find a directional symmetry (i.e. trait matching).
-Our results are similar to Szopa-Comley and Ioannou 2022. Adjustments based on prey. Le predateur s'ajuste dans le traitement unpredictable.
+
 In abrams 2000, we read : "The interaction of predator and prey traits in determining capture rate seems to be the most important factor determining the stability of the entire system.
@@
 We can also read : "If there is sufficiently strong stabilizing selection based on the costs of extreme trait values in both species, then stable equilibria are likely"
-In Reimche et al. 2020 : in the discussion we can read that we still don't understand the factors driving phenotypic (mis)matching. In my case, it appears that learning may play a role.
+
+In Reimche et al. 2020 : in the discussion we can read that we still dont understand the factors driving phenotypic (mis)matching. In my case, it appears that learning may play a role.
 Revoir mes résultats dans le cadre des résultats de Glaudas et al. 2019. Les 2 concordent bien.
-Voir Miszei comme exemple parmi d'autres pour trait matching.
-check Mougi etal. 2011 for arms-races based on phenotypic plasticity!
+
+Voir Miszei comme exemple parmi dautres pour trait matching.
+
+check Mougi etal. 2011 for arms-races based on phenotypic plasticity (modèle théorique)
+
+voir Edgell : prey-induced plasticity leads to covariance between predator-prey trait
 
@@
 
-*Our results also have implications also for predator-prey models of trait-matching, because such models are usually studied at the evolutionary scale.*
+Phrases de conclusion :
+
+Our results also have implications also for predator-prey models of trait-matching, because such models are usually studied at the evolutionary scale.
+
+Therefore, our results have important implications for future predator-prey models, which should incorporate individual variation in learning and prey encounters to better predict under which ecological contexts specialization should be favoured over flexibility.
+---> pour la conclusion
+
+important de faire ressortir que c'est seulement 10% des gens qui ont vraiment changé leur comportement de beaucoup.
+Ainsi ça va être + nuancé et me permettre de dire que certains ne répondent pas à l'expérience*.*affirmer que pt qu'ils répondent à d'autres expériences, mais que des contraintes logistiques nous empêchent de savoir quoi
 

### 2023-03-15 manuscript/Chapter2-manuscript.Rmd
knit latest version with full discussion
add some notes on the caveats in the MS

@@
 
+# Some caveats
+
+"différences entre individus dans les proies rencontées : la direction peut être des 2 côtés, soit c'est parce que le prédateur drive le fait que les proies sont plus variables en général.
+Ou c'est parce qu'il rencontre des proies variables et donc il adopte cette stratégie."
+
+"parler de matchmaking pourrait influencer courbes (moins de variance intermediare car proche de la moyenne de skill)"
+
+"faire la distinction que certains optimisent, certains sont moins bon, donc ça varie dans la population."
+
 Phrases de conclusion :
@@
 
-# Aknowledgements
+# AKNOWLEDGEMENTS
 
@@
 
-# Conflict of Interest Statement
+# CONFLICT OF INTEREST STATEMENT
 
@@
 
-\newpage
 # REFERENCES {.unnumbered}

### 2023-03-23 manuscript/Chapter2-manuscript.Rmd
notes to do
integrated most of Clint's comments. Updated equations based on Julien.

@@
 
+Authorship statement : With MFF as the leader, all authors participated in conceiving the ideas behind the study.
+MFF prepared the data, conducted the analyses, and wrote the manuscript.
+All authors reviewed and accepted the final version of the manuscript.
+
 Open research statement : The data and code used to produce the results in this manuscript are freely available on GitHub https://github.com/quantitative-ecologist/experience-hunting-tactics
 
-Keywords: foraging behaviour, individual specialization, behavioural plasticity, learning, prey predictability, virtual ecology
+Keywords: foraging behaviour, arms race, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology
 
@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
-A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can be major drivers of such individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
+Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or on different resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
+A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can drive such individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
 When they hunt, predators often use techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
 experience).
-While hunting experience may be essential to maintain or improve foraging success, we have limited empirical assessments of its role in predator foraging specialization [@Dukas2019], nor its consequences on predator-prey interactions.
+While hunting experience may be essential to maintain or improve foraging success, we have few empirical assessments of its role in predator foraging specialization [@Dukas2019] and its consequences on predator-prey interactions.
 
@@
 Yet, a recurring question that emerges from these studies is if and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011].
-Thus, uncovering the role of learning in predator-prey systems where interactions are directly monitored would enable researchers to better predict the behavioural decisions and success of predators when they are hunting.
+Thus, uncovering the role of learning in predator-prey systems where interactions are directly monitored would enable researchers to better predict the behavioural decisions and the success of predators when they are hunting.
 
@@
 However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
-We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge and help uncovering the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
-For instance, we found that the classical locomotor crossover hypothesis [@Huey.Pianka1981] applied only for cursorial hunters [see also: @Matsumura.Miyatake2022a], suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
+We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge and help uncover the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
+For instance, we found that the classical locomotor crossover hypothesis [@Huey.Pianka1981] applied only to cursorial hunters [see also: @Matsumura.Miyatake2022a], suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
 Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
@@
 
-*DBD* is a survival asymmetric multiplayer online game developed by Behaviour Interactive Inc.
-In this game, players can play as a predator or a prey.
+*DBD* is a survival asymmetric (i.e.
+a game where the gameplay  mechanics differ between two groups) multiplayer online game developed by Behaviour Interactive Inc, in which players can play either as a predator or a prey.
 The objective of the predator is to hunt and capture the four prey across a virtual environment.
-The objective of the four prey is to forage for resources while avoiding the predator.
+The objective of the four prey is to search for resources while avoiding the predator.
 The resources are in the form of power generators that, once they are all activated, will enable the prey to escape through one of two exit doors.
@@
 Some prey contribute to the group's success by healing or helping others escape the predator, while others play alone and attempt to escape by themselves [@Cere.etal2021].
-Predators must be wary of how the prey behave to choose the right way to capture them.
+Predators must learn how the prey behave and then decide how best to capture them.
 Thus, *DBD* simulates a highly dynamic system where both predators and prey must constantly adjust to each other to be successful.
@@
 The videogame company provided data that spanned a period of 6 months of gameplay recorded for every player.
-The first recorded match was played on `r toString(format(min(dat$date)))`, and the last one on `r toString(format(max(dat$date)))`.
+The first recorded match was played on `r toString(format(min(dat$date)))` and the last one on `r toString(format(max(dat$date)))`.
 We cleaned and filtered the raw data to produce a dataset appropriate for our analyses.
@@
 The predator-players' experience varied between `r toString(format(min(dat$total_xp_pred)))` and `r toString(format(max(dat$total_xp_pred)))` matches played.
-These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)` minutes (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)` minutes).
+These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)`-min (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)`-min).
 The following information is collected and reported for every match : the player's anonymous ID, its avatar, the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.
+
+We recognize that we could have introduced a bias in our analyses since we sampled individuals who stayed in the game for at least 300 matches.
+For instance, these players may already be used to play videogames, and thus, could differ in the way they play at early stages of their experience in the game.
+To ensure that this was not the case, we randomly sampled players that played between 20 and 50 matches, between 51 and 100 matches, and between 101 and 300 matches.
+We then took the first 20 matches played by these players, including those from our sampled population, and compared their average behaviour using a Bayesian hierarchical linear model.
+We found that neither of the four groups differed in their average speed (Table SX), which gives us confidence that our player population was not biased.
 
@@
 We analyzed the predator's average speed and the average speed of the prey encountered by the predator.
-The predator's average speed is measured as the average distance traveled per second during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))`).
-We measured the preys' average speed as the average travel speed of the four individual prey within a match ($\overline{x}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))`).
+The predator's average speed is measured as the average distance traveled per second during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
+We measured the preys' average speed as the average travel speed of the four individual prey within a match ($\overline{x}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
 We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
@@
 For each level of experience (i.e.
-novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and, employing a heterogeneous structure of the residuals, the intra-individual standard deviation in speed of every individual (which we call the dispersion part of the model).
+novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model) and, by using a heterogeneous structure of the residuals, the intra-individual standard deviation of speed for every individual (which we call the dispersion part of the model).
 Thus, in the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e.
@@
 intra-individual variability).
-We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation in speed of the prey encountered by predators.
+We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the prey encountered by predators.
 For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean hunting success.
@@
 For the predator's hunting success, we controlled for the square-root of the duration of the match.
-The model has the following form, with each equation repeated three times (i.e.
-one for each level of experience) :
+
+We estimated the correlation between the individual random effect on the mean and on the dispersion within each trait (e.g.
+$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ pred})$) and among each trait (e.g.
+$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ prey})$) within a level of experience.
+In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible.
+In the second case, the correlations enables us to estimate, for example, whether predators that encountered prey that were faster/slower adopted a slower/faster (or more specialized/flexible) tactic, or if slower/faster predators had lower/greater hunting success.
+We also evaluated these correlations among the different levels of experience (e.g.
+$cor(\sigma_{id_{m}\ pred\ novice}\ \sigma_{id_{d}\ pred\ intermediate})$).
+The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each of three developmental stages.
+
+The full model has the following form, with each equation repeated three times (i.e. one for each level of experience) :
 
@@
 speed_{pred} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
-log(\sigma_{e,\ pred}) &= X_{d} + Z\ id_{d}
+log(\sigma_{e,\ pred}) &= X_{d}\ b_{d} + Z\ id_{d}
 \end{align}
@@
 speed_{prey} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
-log(\sigma_{e,\ prey}) &= X_{d} + Z\ id_{d}
+log(\sigma_{e,\ prey}) &= X_{d}\ b_{d} + Z\ id_{d}
 \end{align}
@@
 The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively.
-We assumed that all random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$, $av \sim N(0,\ I\ \sigma_{av})$, and $id \sim N(0,\ I\ \sigma_{id})$).
+On the mean part of the model, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$ and $av \sim N(0,\ I\ \sigma_{av})$).
+$I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
+The residuals are assumed to follow a Gaussian distribution ($e \sim N(0,\ \sigma_{e})$).
+On the dispersion part of the model, the residuals vary among individuals, allowing us to estimate among individual differences in specialization.
+The individual identity random effects on both the mean and dispersion parts follow a multivariate Gaussian distribution $[\begin{array}{cc} id_m \\ id_d \end{array}] \sim MVN(0,\ \Sigma_{id})$ where $\Sigma_{id}$ is a 15x15 variance-covariance matrix.
 The parameters $\sigma_{env}$, $\sigma_{av}$, and $\sigma_{id}$, correspond to the among environment, among avatar, and among individual standard deviations, respectively.
-$I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
-Here, we assume that the residuals vary among individuals where $e \sim N(0,\ Diag\ [\sigma_{e}])$, $[\begin{array}{cc} id_m \\ id_v \end{array}] \sim N\left(\begin{array}{cc} 0 \\ \\ 0 \end{array},\ \Sigma_{id} \otimes\ I \right)$, and $\Sigma_{id}$ is a variance covariance matrix of the individual identity random effect.
 
-We parameterized equations (1) and (2) with a Gaussian distribution family (predator and prey speed), and employed a beta-binomial distribution family for equation (3) (predator hunting success).
-We employed Gaussian priors for the prey rank ($N(2.5,\ 1)$) and game duration ($N(10,\ 2)$) on the mean part of the model, and the default priors in "brms" for the dispersion part.
+We parameterized equations (1) and (2) with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation (3) (predator hunting success).
+We used Gaussian priors for the prey rank ($N(2.5,\ 1)$) and game duration ($N(10,\ 2)$) on the mean part of the model, and the default priors in "brms" for the dispersion part.
 We used the default Student t priors in "brms" for the intercepts on the mean and dispersion part of the equation.
@@
 For every predicted variable, we applied a half-Gaussian on the random effects for the mean part of the model ($N(0,\ 1)$), and the default "brms" Student t prior for the dispersion part of the model.
-We parametrized the model to run four MCMC chains with 1000 posterior samples for each parameter.
-To do so, we ran 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups.
-
-We estimated the correlation between the individual random effect on the mean and on the dispersion within each trait (e.g.
-$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ pred})$) and among each trait (e.g.
-$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ prey})$) within a level of experience.
-In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible.
-In the second case, the correlations enables us to estimate, for example, whether predators that encountered prey that were faster/slower adopted a slower/faster (or more specialized/flexible) tactic, or if slower/faster predators had lower/greater hunting success.
-We also evaluated these correlations among the different levels of experience (e.g.
-$cor(\sigma_{id_{m}\ pred\ novice}\ \sigma_{id_{d}\ pred\ intermediate})$).
-The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each developmental stage.
-The correlations were estimated assuming a multivariate Gaussian distribution.
+We parametrized the model to run four MCMC chains with 1000 posterior samples for each parameter by completing 2500 iterations having a thinning set to 8, with the first 500 iterations used as warmups.
+We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.05, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021].
+We also performed posterior predictive checks which showed an adequate fit of the model (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
 We additionally report variance partitioning and coefficients of variations in the supporting information.
@@
 
-Our results confirm that individual predators displayed substantial differences in the development of their expertise, as the best model was the one with group-level smoothers exclusively (Table I).
-For instance, with experience, some predators steadily increased their hunting success while others displayed a decrease in prey capture (Figure 1A-S1).
-Otherwise, there were players that maintained either a high or low success across their experience (Figure 1A).
-Another pattern that emerged was that some individuals optimized their success at an experience level that was below what we considered as "advanced" (i.e.
+Our results confirm that individual predators display substantial differences in the development of their expertise, as the best model included group-level smoothers exclusively (Table I).
+For instance, some predators steadily increased (Figure 1A-S1A), while others decreased (Figure 1A-S1B), their hunting success with greater experience, and others whose success did not change with experience (Figure 1A).
+Another pattern that emerged was that some individuals optimized their success at an experience level that was below what we considered "advanced" (i.e.
 >300 matches played).
@@
 We predicted that the relationship between hunting success and experience would vary among predators because they should differ in the type of prey that they encounter.
-However, after controlling for prey speed, we did not find evidence confirming our hypothesis, such that differences among predators in the relationship between hunting success and experience remained stable (Figure 1B).
+However, after controlling for prey speed, we did not find evidence confirming this prediction, because differences among predators remained stable (Figure 1B).
 
@@
 Each fitted curve represents an individual predator.
-(A) A generalized additive mixed model where we do not control for prey speed (B) A generalized additive model where we control for prey speed."}
+(A) A generalized additive mixed model where we do not control for prey speed (B) A generalized additive mixed model where we control for prey speed."}
 
@@
 
-At the population level, we predicted that with experience, predators would become either increasingly flexible or specialized.
-However, our results do not support our prediction, as the pattern was more complex.
-In the dispersion part of the model (i.e.
-sigma predator speed), we indeed found that predators became more flexible with experience at the intermediate stage ($Intercept$, Table 2 and Figure S4).
-However, when they became advanced hunters, they expressed a similar level of flexibility to when they were novices ($Intercept$, Table 2 and Figure S4).
-Thus, instead of increasing linearly, our results suggest that population-level behavioural specialization changed in a nonlinear (quadratic) fashion with experience.
-
-At the individual level, we detected differences in the average movement speed among predators ($SD\ predator\ ID$, Table 2).
-These differences remained stable (although they decreased minimally) at the intermediate stage (Table 2 and Figure S4), and increased at the advanced stage to a level higher than when predators were novice (Table 2 and Figure S4).
-For the dispersion part of the model (i.e.
-sigma predator speed), predators displayed considerable differences in their degree of hunting specialization, which also increased with experience ($SD\ predator\ ID$, Table 2 and Figure S4).
-Thus, the predator population is composed of both specialist and flexible moving individuals, and they further distinguish themselves as specialist/flexible hunters as they gain experience (Figure 2).
+At the population level, we predicted that predators would become either increasingly flexible or specialized with more experience.
+However, our results do not support this prediction.
+Indeed, the observed pattern is more complex than expected given that predators became more flexible with experience at intermediate levels of experience (i.e.
+intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Figure S4), but then return to novice-levels with advanced experience (i.e.
+intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Figure S4).
+Thus, our analyses suggest that population-level behavioural specialization changes nonlinearly (quadratic) with experience rather than linearly.
 
@@
     value = as_paragraph(
-      "* We applied the exponent to the parameter values for sigma (intercepts and predator ID), estimated on a log scale, such that values are mean posterior standard deviations (SD).
+      "* We exponentiated the dispersion parameters (i.e.
+sigma) which are estimated on a log scale.
 We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale."),
@@
   font(fontname = "Times New Roman", part = "all") %>%
-  width(j = c(1,3,4,5), width = 3.7, unit = "cm") %>%
-  width(j = 2, width = 3.2, unit = "cm")
+  width(j = c(2,3,4,5), width = 3.7, unit = "cm") %>%
+  width(j = 1, width = 3.2, unit = "cm")
 
@@
   tab2,
-  caption = "Posterior mean estimates and their 95% credible intervals computed from the MDHGLM of predator speed, prey speed, and predator hunting success.",
+  caption = "Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
   style = "Table Caption"
@@
 
-As we predicted, predators differed in the speed of the prey that they encountered.
-Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period ($SD\ predator\ ID$, Table 2).
-These differences were greater when predators reached an advanced level of hunting experience (Table 2 and Figure S4).
-In addition, individuals experienced largely distinct degrees of variability among their encounters with the prey ($SD\ predator\ ID$, Table 2).
-Hence, some predators experienced stable/predictable encounters with their prey, while others experienced unstable/unpredictable encounters with their prey throughout the study period.
+At the individual level, we detected differences in the mean movement speed among predators (i.e.
+the standard deviation of the mean speed for the predator ID; Table 3).
+These differences largely remained stable to the intermediate stage and then increased at the advanced stage to a level higher than when predators were novice (Table 3 and Figure S4).
+For the dispersion part of the model, predators displayed considerable differences in their degree of hunting specialization, which also increased with experience (i.e.
+the standard deviation of sigma for the predator ID increases with experience; Table 3 and Figure S4).
+Thus, the predator population is composed of both specialist and flexible individuals, and they further distinguish themselves as specialist/flexible hunters as they gain experience (Figure 2).
+
+```{r table3, ft.align = "left"}
+
+tab3 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table3.rds"))
+
+tab3 <- autofit(tab3)
+
+tab3 <- tab3 %>% 
+  footnote(
+    i = 1, j = 1,
+    part = "header",
+    value = as_paragraph(
+      "* We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations."),
+    ref_symbols = " "
+  ) %>%
+  font(fontname = "Times New Roman", part = "all") %>%
+  width(j = c(2,3,4,5), width = 3.7, unit = "cm") %>%
+  width(j = 1, width = 3.2, unit = "cm")
+
+set_caption(
+  tab3,
+  caption = "Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+  style = "Table Caption"
+)
+
+```
+
+As we predicted, predators differed in the mean speed of the prey that they encountered.
+Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period (i.e.
+the standard deviation of the mean prey speed for the predator ID; Table 3).
+These differences were greater when predators reached an advanced level of hunting experience (i.e.
+the standard deviation of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Figure S4).
+In addition, individuals experienced largely distinct degrees of variability among their encounters with the prey.
+Hence, some predators experienced stable/predictable encounters with their prey, while others experienced unstable/unpredictable encounters with their prey throughout the study period (i.e.
+the standard deviation of sigma prey speed for the predator ID; Table 3).
 
@@
 
-At all experience levels, predators that were on average faster (mean) had also a lower intra-individual variability (IIV) across their matches (Figure 3 and Table S1).
+At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV) across their matches (Figure 3 and Table S1).
 Thus, faster predators specialized at travelling fast, while slower predators were more flexible in their movement through time.
@@
 However, predators that experienced more predictable encounters with their prey (IIV) specialized in a faster hunting tactic (IIV) (Figure 3 and Table S1).
-For all the results described above, the correlations became stronger as predators gained experience (Figure 3 and Table S1).
+For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Table S1).
 
-The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience (Figure 3 inside the black circles and Table S1).
-For instance, novice predators that tended to be faster also kept this strategy as they gained experience (Figure 3 inside the black squares and Table S1).
-Overall, we detected the same patterns than those from the within-experience state correlations described above.
-The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that the behavioural tactics of predators were more similar among experience levels closer in time (Figure 3 inside the black circles and Table S1).
+The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience (Figure 3 inside the black squares and Table S1).
+For example, novice predators that tended to be faster maintained this strategy as they gained experience (Figure 3 inside the black squares and Table S1).
+Overall, we detected the same patterns as those from the within-experience state correlations described above.
+The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that the hunting strategies of predators were more similar among experience levels closer in time (Figure 3 inside the black squares and Table S1).
 
@@
 
-We did not detect strong correlations between the predators' average speed and their hunting success (Figure 3 and Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Table S1), suggesting that both slower/flexible and faster/specialist predators were both equally successful.
-However, when predators were novice, there was a strong negative correlation between the average speed of the prey that they encountered and their hunting success (Figure 3 and Table S1).
+We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
+However, when predators were novice, there was a strong negative correlation between the mean speed of the prey that they encountered and their hunting success (Figure 3 and Table S1).
 Hence, novice individuals that encountered faster prey were less successful.
 This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Table S1).
+Thus, the consequences of hunting faster prey were reduced at greater experience levels.
 
-# Discussion
+# DISCUSSION
 
-Hunting experience is predicted to imbue an increase in predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
-Other lines of research view learning from experience as a form of behavioural plasticity [@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022], with theoretical models predicting an increase in flexibility from experience when resources are variable [@Stephens1993].
-Our results challenge the hypothesis that experience should generate a directional increase in behavioural specialization or plasticity in a population.
+Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
+However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
+Our results show that both mechanisms operated simultaneously, such that there was no directional increase in behavioural specialization or plasticity in the population.
 Instead, the consequences from experience appear to be a property of individuals, such that each predator developed, through extensive practice, their own expertise and behavioural trajectory; some specialized at fast-paced hunting, while others adopted a slower and more flexible tactic.
@@
 This predator-prey behavioural matching grew stronger with predator experience, while the relationship between the prey's behaviour and hunting success diminished.
-Together, our observations suggest that predators learn to adjust their hunting tactic with experience, and the degree at which they specialize in it, based on the behaviour of the prey that they encountered throughout their lifetime.
-Moreover, the behavioural escalation through experience suggests that learning may be a catalyst for predator-prey arms races.
+Together, our observations suggest that predators adjust their hunting tactic with experience, and the degree at which they specialize in it, to the behaviour of the prey that they encountered throughout their lifetime in the game.
+Moreover, the predator-prey behavioural escalation through experience suggests that learning may be a catalyst for arms races.
 
@@
 
-Empirical research in humans and animals show that the proficiency in a given task often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
+Empirical research in humans and animals shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
 However, these results are derived from models that assume the same increase in expertise for each individual, and the data from these studies does not include repeated measures of individual success through time.
@@
 This is often the case in nature as prey can use variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-However, the speed of the prey did not shape individual differences in expertise acquisition by predators, even if they differed in the prey that they encountered.
+However, prey speed in our study did not shape individual differences in expertise acquisition by predators, even if predators differed in the prey that they encountered.
 This was unexpected, because prey speed is an important predictor of predator success in this system as well as in others [@Walker.etal2005;@Kelley.Magurran2011;@FraserFranco.etal2022].
@@
 For instance, a persevering predator may increase its success much more steadily than an unmotivated predator that quickly abandons a chase.
-Another factor that may explain differences in the development of expertise is the time delay between hunting events, such that a predator that played 300 matches in the span of six months may not retain information (e.g.
-prey escape patterns or muscle memory) as well as one that played 300 matches in the span of 6 days.
-While this has not been formally tested, it is hypothesized that a greater delay between exposure events should attenuate or even negate the relationship between cumulative experience and success, as a result of forgetting [@Endler1991;@Wright.etal2022].
+Another factor that may explain differences in the development of expertise is the time delay between hunting events.
+For example, a predator that played 300 matches in the span of six months might forget more critical information (e.g.
+prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days.
+While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between cumulative experience and success [@Endler1991;@Wright.etal2022].
 
@@
 
-The predator population displayed an increase in foraging flexibility when they reached an intermediate level of experience.
-As they reached an advanced level of experience, they returned to a level of flexibility that was similar to when they were novices.
-This is comonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016].
+The predator population displayed an increase in foraging flexibility when reaching the intermediate level of experience.
+As it reached an advanced level of experience, it returned to a level of flexibility that was similar to novice levels.
+This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016].
 Thus, the predators in *DBD* were probably exploring and refining different tactics at this stage of their development in the game.
 Interestingly, individuals became increasingly distinct in their level of foraging specialization with experience, which was related to the degree of variability in prey encounters.
-Predators that experienced predictable encounters with their prey specialized in hunting at high speeds, while those that experienced more unpredictable encounters adopted a slower and flexible strategy.
+Predators that experienced predictable encounters with their prey specialized in hunting at high speeds, while those that experienced less predictable encounters adopted a slower and flexible strategy.
 This is similar to other studies finding that fast-paced hunting is a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022].
 On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty.
-As they gained experience, predators increasingly matched their tactic to their prey, suggesting that they learned how to hunt them throughout repeated interactions.
-In that regard, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning to adjust their degree of specialization based on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
+Importantly, 13% of the predator population displayed the greatest (i.e.
+> than 0.2 standard deviations) change in foraging specialization/flexibility with experience, while 43% remained relatively stable, and the remaining 56% displayed lower changes.
+Thus, while individual differences in specialization did increase with experience, they were in part driven by a proportion of the population that displayed greater changes in behaviour compared to others.
+
+As they gained experience, predators increasingly matched their tactic to their prey, suggesting that they learned how to hunt via repeated interactions.
+However, while the mean speed of predators was strongly and increasingly matched to the mean speed of the prey, further investigations revealed that this apparent increase was driven largely by one individual.
+Yet, predators also adjusted their degree of flexibility to their prey even if the change was not very strong (Figure 3 and Table S1).
+In that regard, despite that only a portion of the population displayed large changes in specialization, and that adjustments to the prey were not as strong as we expected, our results still provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning to adjust their degree of specialization based on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
 This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period.
@@
 From an evolutionary perspective, @BrodieIII.BrodieJr.1999 showed in the garter snake (*Thamnophis sirtalis*) - roughskin newt (*Taricha granulosa*) system that such escalations may occur when prey develop defensive traits, which leads to stronger selection in predators, resulting in counteradaptations that circumvent the prey's defenses.
-In our system, the predator's success is negatively correlated to the prey's speed, which is an effective antipredator tactic [@FraserFranco.etal2022].
-However, as the covariance between the predator's speed and the speed of the prey encountered increased with experience, reminiscent of an arms race, we found that the fitness consequences of the preys' speed on predators decreased with experience.
+In our system, the predator's success is negatively correlated with the prey's speed, which is an effective antipredator tactic [@FraserFranco.etal2022].
+However, the current study showed that as the covariance between predator speed and prey speed increased with experience, reminiscent of an arms race, we found that the consequences of hunting faster prey decreased with experience.
 Moreover, this pattern was followed by a decrease in among individual variation in success with experience.
-This has important implications for the role of experience on predator-prey interactions, as we found that learning enables predators to effectively develop countermeasures to the prey's defenses at nonevolutionary timescales.
-It also provides empirical evidence to the idea that reciprocal phenotypic plasticy through learning may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
+This has important implications for the role of experience on predator-prey interactions, as we found that learning enables predators to effectively develop countermeasures to the prey's defenses within their lifetime (i.e.
+at nonevolutionary timescales).
+It also provides empirical evidence for the hypothesis that reciprocal phenotypic plasticity through learning may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
 
 ## Conclusions
+
+The interactions of predator and prey traits are probably the most important processes involved in population cycles and are expected to occur when predators match their phenotype to their prey [@abramsEvolutionPredatorPreyInteractions2000].
+Yet, its has remained largely unknown whether this matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
+By capitalizing on a virtual predator-prey system where we could directly monitor interactions, we found that experience drives individual specialization, and that predators adjust their behaviour to their prey.
+Moreover, individuals displayed large differences in the development of their expertise, which could result from differences in learning, as we found that almost half the population did not change their behaviour with experience.
+Our results have implications for predator-prey models of trait-matching, because such models are often studied at evolutionary timescales.
+Therefore, future studies should incorporate individual variation in learning and prey encounters to better predict under which ecological contexts specialization should be favoured over flexibility.
+Lastly, virtual systems are increasingly recognized among ecologists as effective systems to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
+We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
 
@@
 
+"covariance est drivé par un individu pour la moyenne"
+
+À faire :
+
+- parler du sampling et du modèle pour tester les biais dans les méthodes [done]
+- dans mon dernier paragraphe, parler du fait que les proies aussi s'ajustent
+
 Phrases de conclusion :
+
+Début de la conclusion, revenir brièvement sur notre système et les jeux. Les petits avantages
 
@@
 ---> pour la conclusion
-
-important de faire ressortir que c'est seulement 10% des gens qui ont vraiment changé leur comportement de beaucoup.
-Ainsi ça va être + nuancé et me permettre de dire que certains ne répondent pas à l'expérience*.*affirmer que pt qu'ils répondent à d'autres expériences, mais que des contraintes logistiques nous empêchent de savoir quoi
 

### 2023-03-27 manuscript/Chapter2-manuscript.Rmd
update MS with new references style

@@
     pandoc_args: ["-Fpandoc-crossref"] # to have eq. numbers
-bibliography: references.bib
-csl: ecology.csl
+bibliography: references2.bib
+csl: chicago-author-date.csl
 ---
@@
 To do so, we ran 2500 iterations for the first model with a thinning set to eight, and 1500 iterations with a thinning set to four for the second and third models; burn-in was set to 500 iterations in each model.
-We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.05, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021].
+We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.05, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021a].
 After fitting the three models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
@@
 We parametrized the model to run four MCMC chains with 1000 posterior samples for each parameter by completing 2500 iterations having a thinning set to 8, with the first 500 iterations used as warmups.
-We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.05, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021].
+We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.05, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021a].
 We also performed posterior predictive checks which showed an adequate fit of the model (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
-We additionally report variance partitioning and coefficients of variations in the supporting information.
+We additionally report variance partitioning and coefficients of variations in the supporting information (Appendix S1).
 
@@
 Our results confirm that individual predators display substantial differences in the development of their expertise, as the best model included group-level smoothers exclusively (Table I).
-For instance, some predators steadily increased (Figure 1A-S1A), while others decreased (Figure 1A-S1B), their hunting success with greater experience, and others whose success did not change with experience (Figure 1A).
+For instance, some predators steadily increased (Figure 1A, Appendix S1: Figure S1A), while others decreased (Figure 1A, Appendix S1: Figure S1B), their hunting success with greater experience, and others whose success did not change with experience (Figure 1A).
 Another pattern that emerged was that some individuals optimized their success at an experience level that was below what we considered "advanced" (i.e.
@@
 Indeed, the observed pattern is more complex than expected given that predators became more flexible with experience at intermediate levels of experience (i.e.
-intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Figure S4), but then return to novice-levels with advanced experience (i.e.
-intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Figure S4).
+intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S4), but then return to novice-levels with advanced experience (i.e.
+intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Appendix S1: Figure S4).
 Thus, our analyses suggest that population-level behavioural specialization changes nonlinearly (quadratic) with experience rather than linearly.
@@
 the standard deviation of the mean speed for the predator ID; Table 3).
-These differences largely remained stable to the intermediate stage and then increased at the advanced stage to a level higher than when predators were novice (Table 3 and Figure S4).
+These differences largely remained stable to the intermediate stage and then increased at the advanced stage to a level higher than when predators were novice (Table 3 and Appendix S1: Figure S4).
 For the dispersion part of the model, predators displayed considerable differences in their degree of hunting specialization, which also increased with experience (i.e.
-the standard deviation of sigma for the predator ID increases with experience; Table 3 and Figure S4).
+the standard deviation of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S4).
 Thus, the predator population is composed of both specialist and flexible individuals, and they further distinguish themselves as specialist/flexible hunters as they gain experience (Figure 2).
@@
 These differences were greater when predators reached an advanced level of hunting experience (i.e.
-the standard deviation of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Figure S4).
+the standard deviation of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S4).
 In addition, individuals experienced largely distinct degrees of variability among their encounters with the prey.
@@
 
-At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV) across their matches (Figure 3 and Table S1).
+At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV) across their matches (Figure 3 and Appendix S2: Table S1).
 Thus, faster predators specialized at travelling fast, while slower predators were more flexible in their movement through time.
-In general, predators that encountered prey that were on average faster (mean) tended to be faster (mean) (Figure 3 and Table S1).
-At the three experience levels, there were only weak correlations between predator IIV and mean prey speed (Figure 3 and Table S1).
-However, predators that experienced more predictable encounters with their prey (IIV) specialized in a faster hunting tactic (IIV) (Figure 3 and Table S1).
-For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Table S1).
+In general, predators that encountered prey that were on average faster (mean) tended to be faster (mean) (Figure 3 and Appendix S2: Table S1).
+At the three experience levels, there were only weak correlations between predator IIV and mean prey speed (Figure 3 and Appendix S2: Table S1).
+However, predators that experienced more predictable encounters with their prey (IIV) specialized in a faster hunting tactic (IIV) (Figure 3 and Appendix S2: Table S1).
+For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Appendix S2: Table S1).
 
-The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience (Figure 3 inside the black squares and Table S1).
-For example, novice predators that tended to be faster maintained this strategy as they gained experience (Figure 3 inside the black squares and Table S1).
+The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience (Figure 3 inside the black squares and Appendix S2: Table S1).
+For example, novice predators that tended to be faster maintained this strategy as they gained experience (Figure 3 inside the black squares and Appendix S2: Table S1).
 Overall, we detected the same patterns as those from the within-experience state correlations described above.
-The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that the hunting strategies of predators were more similar among experience levels closer in time (Figure 3 inside the black squares and Table S1).
+The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that the hunting strategies of predators were more similar among experience levels closer in time (Figure 3 inside the black squares and Appendix S2: Table S1).
 
@@
 
-We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
-However, when predators were novice, there was a strong negative correlation between the mean speed of the prey that they encountered and their hunting success (Figure 3 and Table S1).
+We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Appendix S2: Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Appendix S2: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
+However, when predators were novice, there was a strong negative correlation between the mean speed of the prey that they encountered and their hunting success (Figure 3 and Appendix S2: Table S1).
 Hence, novice individuals that encountered faster prey were less successful.
-This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Table S1).
+This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Appendix S2: Table S1).
 Thus, the consequences of hunting faster prey were reduced at greater experience levels.
@@
 In contrast, our analyses revealed that there was no population increase in expertise; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition.
-For instance, many predators increased their success (Figure S1A), but others displayed a decrease in success (Figure S1B) or no change in success at all with experience.
+For instance, many predators increased their success (Appendix S1: Figure S1A), but others displayed a decrease in success (Appendix S1: Figure S1B) or no change in success at all with experience.
 We predicted that this would occur because predators should differ in the type of prey that they encounter, as some may be easier to capture than others.

### 2023-03-28 manuscript/Chapter2-manuscript.Rmd
updated MS version names

@@
 However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-Our results show that both mechanisms operated simultaneously, such that there was no directional increase in behavioural specialization or plasticity in the population.
+Our results show that both mechanisms operated simultaneously, such that there was no directional increase in behavioural specialization or flexibility in the population.
 Instead, the consequences from experience appear to be a property of individuals, such that each predator developed, through extensive practice, their own expertise and behavioural trajectory; some specialized at fast-paced hunting, while others adopted a slower and more flexible tactic.
@@
 Empirical research in humans and animals shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
-However, these results are derived from models that assume the same increase in expertise for each individual, and the data from these studies does not include repeated measures of individual success through time.
+However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data includes repeated measures of individual success through time.
 In contrast, our analyses revealed that there was no population increase in expertise; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition.
@@
 prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days.
-While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between cumulative experience and success [@Endler1991;@Wright.etal2022].
+While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
 
@@
 This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016].
-Thus, the predators in *DBD* were probably exploring and refining different tactics at this stage of their development in the game.
+Thus, the predators in *DBD* were probably exploring and refining different tactics at this stage of experience.
 Interestingly, individuals became increasingly distinct in their level of foraging specialization with experience, which was related to the degree of variability in prey encounters.
@@
 On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty.
-Importantly, 13% of the predator population displayed the greatest (i.e.
-> than 0.2 standard deviations) change in foraging specialization/flexibility with experience, while 43% remained relatively stable, and the remaining 56% displayed lower changes.
+Importantly, 13% of the predator population displayed the greatest change in foraging specialization/flexibility with experience (i.e.
+$\ge$ 0.2 change in standard deviation), 56% displayed lower changes (i.e.
+>0.05 and <0.2 change in standard deviation), while 43% remained relatively stable (i.e.
+$\le$ 0.05 change in standard deviation).
 Thus, while individual differences in specialization did increase with experience, they were in part driven by a proportion of the population that displayed greater changes in behaviour compared to others.
@@
 However, while the mean speed of predators was strongly and increasingly matched to the mean speed of the prey, further investigations revealed that this apparent increase was driven largely by one individual.
-Yet, predators also adjusted their degree of flexibility to their prey even if the change was not very strong (Figure 3 and Table S1).
+Yet, predators also adjusted their degree of flexibility to their prey even if the change was not very strong (Figure 3 and Appendix S2: Table S1).
 In that regard, despite that only a portion of the population displayed large changes in specialization, and that adjustments to the prey were not as strong as we expected, our results still provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning to adjust their degree of specialization based on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
@@
 In our system, the predator's success is negatively correlated with the prey's speed, which is an effective antipredator tactic [@FraserFranco.etal2022].
-However, the current study showed that as the covariance between predator speed and prey speed increased with experience, reminiscent of an arms race, we found that the consequences of hunting faster prey decreased with experience.
+However, we found that as the covariance between predator speed and prey speed increased with experience, reminiscent of an arms race, the consequences of hunting faster prey decreased with experience.
 Moreover, this pattern was followed by a decrease in among individual variation in success with experience.
-This has important implications for the role of experience on predator-prey interactions, as we found that learning enables predators to effectively develop countermeasures to the prey's defenses within their lifetime (i.e.
+This has important implications for the role of experience on predator-prey interactions, as our results suggest that learning enables predators to effectively develop countermeasures to the prey's defenses within their lifetime (i.e.
 at nonevolutionary timescales).
@@
 The interactions of predator and prey traits are probably the most important processes involved in population cycles and are expected to occur when predators match their phenotype to their prey [@abramsEvolutionPredatorPreyInteractions2000].
-Yet, its has remained largely unknown whether this matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
+Yet, its has remained largely unknown whether this trait-matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
 By capitalizing on a virtual predator-prey system where we could directly monitor interactions, we found that experience drives individual specialization, and that predators adjust their behaviour to their prey.
@@
 Our results have implications for predator-prey models of trait-matching, because such models are often studied at evolutionary timescales.
-Therefore, future studies should incorporate individual variation in learning and prey encounters to better predict under which ecological contexts specialization should be favoured over flexibility.
+Therefore, future studies should incorporate individual variation in experience to better predict under which ecological contexts specialization should be favoured over flexibility.
 Lastly, virtual systems are increasingly recognized among ecologists as effective systems to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
@@
 ```{r eval = FALSE}
+
+Discussion :
+
+- peut-être ajouter le fait que malgré que la vitesse soit mieux pour les proies, elles pourraient buffer ça en étant + imprévisibles.
+
+- peut être ajouter que l'escalade est aussi dû au fait que la proie pourrait être plus susceptible à la prédation en étant rapide car elle s'expose plus.
 

### 2023-03-28 manuscript/Chapter2-manuscript.Rmd
updated the MS with new figures

@@
 In the second case, the correlations enables us to estimate, for example, whether predators that encountered prey that were faster/slower adopted a slower/faster (or more specialized/flexible) tactic, or if slower/faster predators had lower/greater hunting success.
-We also evaluated these correlations among the different levels of experience (e.g.
+As a complement, the model also estimated correlations among the different levels of experience (e.g.
 $cor(\sigma_{id_{m}\ pred\ novice}\ \sigma_{id_{d}\ pred\ intermediate})$).
 The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each of three developmental stages.
+We present the character-state analyses as additional material in the Appendix S2 because they were not part of our initial objectives.
 
@@
 
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Full correlation matrix of the MDHGLM relating the mean and intra individual variability (IIV) in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
-Starting from the upper part of the plot are displayed the five parameters for novice predators (gray), the five for intermediate predators (yellow), and the five for advanced predators (blue).
-Larger dark blue circles indicate stronger positive correlations, while larger dark red circles indicate stronger negative correlations.
-The black squares indicate correlations between different experience levels (i.e.
-character states)."}
+```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Correlation matrices of the MDHGLM relating the mean and intra individual variability (IIV) in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+Larger dark blue circles indicate stronger positive correlations (positive values on the color legend), while larger dark red circles indicate stronger negative correlations (negative values on the color legend).
+A) Correlations when predators were novice hunters.
+B) Correlations when predators were at an intermediate level of experience.
+C) Correlations when predators were advanced hunters."}
 

### 2023-03-29 manuscript/Chapter2-manuscript.Rmd
integrate most of Francesca's comments

@@
 Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or on different resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
-A growing body of evidence suggests that ecological interactions, such as predator-prey interactions, can drive such individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
+A growing body of evidence suggests that ecological interactions such as predator-prey interactions can drive this individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
 When they hunt, predators often use techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
@@
 @Dukas2019 defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
-This body of work suggests that the development of expertise through extensive practice is an optimizing process that should promote foraging specialization.
+It is described as the relationship between success and cumulative experience, where extensive practice optimizes success when individuals reach an advanced level of experience.
 Empirical studies on human and non-human hunters show that experience optimizes the efficiency (e.g.
 search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@macdonaldCrossculturalComparisonLearning2007;@Reid.etal2010;@Wilson-Rankin2015].
-Such optimization may thus reinforce the use of the same tactic (i.e.
-specialization) if its success is constant each time a prey is encountered.
+This body of work suggests that such optimization may thus promote individual foraging specialization (e.g.
+repeatedly using fast attacks) if the success of a hunting tactic is constant each time a prey is encountered.
 It may also be costly to attempt different hunting tactics by trial and error when prey are scarce or highly unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
-An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset by gaining experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
-To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, followed by higher performance at later stages of development [reviewed in @Snell-Rood2013].
-However, predators can differ in the challenges that they face during their lifetime, which could lead to both mechanisms operating at the same time within a predator population.
-For instance, some individuals may constantly encounter faster prey, which are proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@FraserFranco.etal2022].
+An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset through extensive practive, as individuals gain experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
+To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
+However, predators can differ in the challenges that they face during their lifetime, which could result in both mechanisms operating at the same time within a predator population.
+For instance, some individuals may constantly encounter faster prey, which are proven to be more difficult to hunt in simulation and empirical studies [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
+Thus, whether predators specialize or increase their flexibility with experience, learning to adjust their tactic to their prey should be essential to optimize their success.
 
-There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging.
-Importantly, we have limited information on the ecological contexts - except for competition - that favour specialization over flexibility.
+There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging [@Phillips.etal2017].
 This is reflected in the literature showing contrasting results in the links between specialization and fitness.
 For instance, some studies report increasing benefits of specialization [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
-While quantifying the fitness consequences of specialization is a daunting task, in predator-prey systems, some clues indicate that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
-The resource-predictability hypothesis argues that when resources are predictable, individual specialists should have higher delivery rates by reducing the energy and time required to search for and handle prey.
+This may in part be due to the limited information we have on the ecological contexts favouring specialization over flexibility in nature.
+However, in predator-prey systems, many studies have outlined that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
+The resource-predictability hypothesis argues that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
 In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-At the phenotypic interface, empirical evidence shows that predators often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
-Yet, a recurring question that emerges from these studies is if and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011].
+When predators directly interact with their prey, empirical evidence shows that they often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
+Yet, a recurring question that emerges from these studies is whether and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011].
 Thus, uncovering the role of learning in predator-prey systems where interactions are directly monitored would enable researchers to better predict the behavioural decisions and the success of predators when they are hunting.
@@
 However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
-We recently demonstrated with behavioural data from an online predator-prey videogame that virtual systems can overcome this challenge and help uncover the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
-For instance, we found that the classical locomotor crossover hypothesis [@Huey.Pianka1981] applied only to cursorial hunters [see also: @Matsumura.Miyatake2022a], suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
+We recently demonstrated with behavioural data from an online predator-prey videogame, called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge and help uncover the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
+For instance, we found that some individual predators hunt at high speeds and cover space in the environment, while others prefer to stalk and ambush their prey.
+Individuals are also flexible in the use of these tactics by switching between them across matches.
+The expression of these tactics and their success is also shaped by the speed of the prey, where faster prey are more difficult to hunt.
+The prey need to forage for resources while paying attention to the predator to avoid being detected and chased.
+Some prey contribute to the group's success by healing or helping others escape the predator, while others play alone and attempt to escape by themselves [@Cere.etal2021].
+Predators must learn how the prey behave and then decide how best to capture them.
+Thus, *DBD* simulates a highly dynamic system where both predators and prey must adjust to each other, suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
 Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
 in prep).
-Because virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with their potential fitness consequences.
+Virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game under realistic ecological scenarios.
+Hence, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with their potential fitness consequences.
 
-In this study, we test how hunting experience shapes predator foraging specialization using individual behavioural data from players in the online videogame *Dead by Daylight* (*DBD*).
+In this study, we test how hunting experience shapes predator foraging specialization using individual behavioural data from players in the online videogame *Dead by Daylight*.
 *DBD* simulates a direct predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
-The data grants a high degree of precision on the behavioural interaction, as the behaviour of both the predator and the four prey is monitored simultaneously in each trial.
+The data grants a high degree of precision on the behavioural interaction, as the behaviour of both the predator and the four prey along with the predator's success are monitored simultaneously in each trial.
 First, we investigate how predators develop their individual hunting expertise.
@@
 The objective of the four prey is to search for resources while avoiding the predator.
-The resources are in the form of power generators that, once they are all activated, will enable the prey to escape through one of two exit doors.
+The resources are in the form of power generators that, once all activated, will enable the prey to escape through one of two exit doors.
 The composition of the predator and prey group for a match is determined by a skill-based matchmaking algorithm.
@@
 Some of these environments are larger than others, with varying structural complexity.
-However, we have previously shown that predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling predators to have visual cues of the generators [@FraserFranco.etal2022].
+However, predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling them to have visual cues of the generators [@FraserFranco.etal2022].
 There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during our study period.
-
-In *DBD*, some individual predators specialize on hunting at high speeds and covering space in the environment, while others prefer to stalk and ambush their prey [@FraserFranco.etal2022].
-Individuals are also flexible in the use of these tactics by switching between them across matches.
-The expression of these tactics and their success is also shaped by the behaviour of the prey group.
-The prey need to forage for resources while paying attention to the predator to avoid being detected and chased.
-Some prey contribute to the group's success by healing or helping others escape the predator, while others play alone and attempt to escape by themselves [@Cere.etal2021].
-Predators must learn how the prey behave and then decide how best to capture them.
-Thus, *DBD* simulates a highly dynamic system where both predators and prey must constantly adjust to each other to be successful.
 
@@
 We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero.
-Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game has it is supposed to be played.
-We then partitioned the player population by total experience, and sampled players that played 300 matches or more.
+Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game as it is supposed to be played.
+We then sampled players that played 300 matches or more.
 To optimize the representation of gameplay experience at advanced levels, we set the maximum number of matches at 500 for these players.
@@
 These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)`-min (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)`-min).
-The following information is collected and reported for every match : the player's anonymous ID, its avatar, the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.
+The following information is collected and reported for every match : the player's anonymous ID, its avatar (i.e.
+the predator character chosen with its specific powers-gameplay mechanics), the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.
 
@@
 For instance, these players may already be used to play videogames, and thus, could differ in the way they play at early stages of their experience in the game.
-To ensure that this was not the case, we randomly sampled players that played between 20 and 50 matches, between 51 and 100 matches, and between 101 and 300 matches.
+To ensure that our sample was not biased, the videogame company provided a random sample of players that played between 20 and 50 matches, between 51 and 100 matches, and between 101 and 300 matches from the same timeframe as our current sample.
 We then took the first 20 matches played by these players, including those from our sampled population, and compared their average behaviour using a Bayesian hierarchical linear model.
@@
 
-We analyzed the predator's average speed and the average speed of the prey encountered by the predator.
+We analyzed the predator's average speed and the average speed of the prey group encountered by the predator.
 The predator's average speed is measured as the average distance traveled per second during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
@@
 We employed the default Student t priors for the smoothing parameter ($t(3,\ 0,\ 2.5)$).
-In all models, we specified four MCMC chains to estimate the parameters, with 1000 posterior samples for each parameter.
-To do so, we ran 2500 iterations for the first model with a thinning set to eight, and 1500 iterations with a thinning set to four for the second and third models; burn-in was set to 500 iterations in each model.
-We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.05, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021a].
 After fitting the three models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
 
-### Foraging behaviour and success, prey behaviour, and their relationships, at each level of experience
+### Changes in foraging behaviour and predator-prey interactions with experience
 
@@
 their cumulative experience).
-We assigned the status of "novice" to any predator-player that had a cumulative experience below 100 matches.
+Since we monitored all predator players throughout their experience, they appeared in all of the three following experience categories.
+First, we assigned predators the status of "novice" when they had a cumulative experience below 100 matches.
 For example, a predator player that played 500 matches in total would be labelled as a novice in its first 100 matches.
 Following this logic, we labelled predators as "intermediate" hunters when they had a cumulative experience between 100 and 299 and matches.
-For the third and last group, we defined predators as "advanced" hunters when they had a cumulative experience equal or above 300, with a maximum of 499 cumulated matches.
+Lastly, we defined predators as "advanced" hunters when they had a cumulative experience equal or above 300, with a maximum of 499 cumulated matches.
 
@@
 Thus, in the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e.
-fast or slow), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization/flexibility (i.e.
+along the slow-fast continuum), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization/flexibility (i.e.
 intra-individual variability).
-We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the prey encountered by predators.
+We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the prey groups encountered by predators.
 For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean hunting success.
-For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered on both the mean and dispersion part of the equation.
+For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered as proxy for prey skills on both the mean and dispersion part of the equation.
 The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank).
@@
 The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each of three developmental stages.
-We present the character-state analyses as additional material in the Appendix S2 because they were not part of our initial objectives.
+We present the character-state analyses as additional material in the Appendix S2 as they were not part of our initial objectives.
 
@@
 For every predicted variable, we applied a half-Gaussian on the random effects for the mean part of the model ($N(0,\ 1)$), and the default "brms" Student t prior for the dispersion part of the model.
-We parametrized the model to run four MCMC chains with 1000 posterior samples for each parameter by completing 2500 iterations having a thinning set to 8, with the first 500 iterations used as warmups.
+
+### Markov Chain Monte Carlo settings
+
+We parametrized every model described above to run four MCMC chains with 1000 posterior samples for each parameter.
+We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table I), and 1500 iterations with a thinning set to four for the additive model with a global smoother and group-level smoothers as well as for the additive model with group-level smoothers only (Table I).
+Burn-in was set to 500 iterations in each model.
+We parametrized the MDHGLM to run 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups.
 We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.05, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021a].
-We also performed posterior predictive checks which showed an adequate fit of the model (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
-We additionally report variance partitioning and coefficients of variations in the supporting information (Appendix S1).
+We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
 
@@
 We predicted that the relationship between hunting success and experience would vary among predators because they should differ in the type of prey that they encounter.
-However, after controlling for prey speed, we did not find evidence confirming this prediction, because differences among predators remained stable (Figure 1B).
+However, after controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained stable (Figure 1B).
 
@@
 However, our results do not support this prediction.
-Indeed, the observed pattern is more complex than expected given that predators became more flexible with experience at intermediate levels of experience (i.e.
-intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S4), but then return to novice-levels with advanced experience (i.e.
+Indeed, the observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e.
+intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S4), but then return to novice-levels of flexibility with advanced experience (i.e.
 intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Appendix S1: Figure S4).
@@
     value = as_paragraph(
-      "* We exponentiated the dispersion parameters (i.e.
+      as_sup("a "),
+      "We exponentiated the dispersion parameters (i.e.
 sigma) which are estimated on a log scale.
-We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale."),
+We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale.",
+      as_sup("\nb "),
+      "The intercept values on the mean part of the equation for all traits indicate average behaviour and success at the population level.
+The intercept values on the dispersion (i.e.
+sigma) part of the equation for predator speed indicate behavioural specialization at the population level."
+    ),
     ref_symbols = " "
@@
 At the individual level, we detected differences in the mean movement speed among predators (i.e.
-the standard deviation of the mean speed for the predator ID; Table 3).
-These differences largely remained stable to the intermediate stage and then increased at the advanced stage to a level higher than when predators were novice (Table 3 and Appendix S1: Figure S4).
-For the dispersion part of the model, predators displayed considerable differences in their degree of hunting specialization, which also increased with experience (i.e.
-the standard deviation of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S4).
-Thus, the predator population is composed of both specialist and flexible individuals, and they further distinguish themselves as specialist/flexible hunters as they gain experience (Figure 2).
+the intercept of the mean speed for the predator ID; Table 3).
+These differences remained stable to the intermediate stage and then increased at the advanced stage to a level higher than when predators were novice (Table 3 and Appendix S1: Figure S4).
+For the dispersion part of the model, predators displayed considerable differences in their degree of hunting specialization, and these differences increased with experience (i.e.
+the intercept of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S4).
+Thus, the predator population is composed of both specialist and flexible individuals, and they further differentiate themselves as specialist/flexible hunters as they gain experience (Figure 2).
 
@@
     value = as_paragraph(
-      "* We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations."),
+      as_sup("a "),
+      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
+      as_sup("\nb "),
+      "The intercept values on the mean part of the equation for all traits indicate among individual differences in average behaviour and success.",
+      as_sup("\nc "),
+      "The intercept values on the dispersion (i.e.
+sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization.
+For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
+    ),
     ref_symbols = " "
@@
 
-As we predicted, predators differed in the mean speed of the prey that they encountered.
+As we predicted, predators differed in the mean speed of the prey that they encountered across matches.
 Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period (i.e.
-the standard deviation of the mean prey speed for the predator ID; Table 3).
+the intercept of the mean prey speed for the predator ID; Table 3).
 These differences were greater when predators reached an advanced level of hunting experience (i.e.
-the standard deviation of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S4).
+the intercept of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S4).
 In addition, individuals experienced largely distinct degrees of variability among their encounters with the prey.
 Hence, some predators experienced stable/predictable encounters with their prey, while others experienced unstable/unpredictable encounters with their prey throughout the study period (i.e.
-the standard deviation of sigma prey speed for the predator ID; Table 3).
+the intercept of sigma prey speed for the predator ID; Table 3).
 
@@
 Thus, faster predators specialized at travelling fast, while slower predators were more flexible in their movement through time.
-In general, predators that encountered prey that were on average faster (mean) tended to be faster (mean) (Figure 3 and Appendix S2: Table S1).
+In general, predators that encountered groups of prey that were on average faster (mean) tended to be faster (mean) (Figure 3 and Appendix S2: Table S1).
 At the three experience levels, there were only weak correlations between predator IIV and mean prey speed (Figure 3 and Appendix S2: Table S1).
@@
 For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Appendix S2: Table S1).
-
-The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience (Figure 3 inside the black squares and Appendix S2: Table S1).
-For example, novice predators that tended to be faster maintained this strategy as they gained experience (Figure 3 inside the black squares and Appendix S2: Table S1).
-Overall, we detected the same patterns as those from the within-experience state correlations described above.
-The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that the hunting strategies of predators were more similar among experience levels closer in time (Figure 3 inside the black squares and Appendix S2: Table S1).
 
@@
 We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Appendix S2: Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Appendix S2: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
-However, when predators were novice, there was a strong negative correlation between the mean speed of the prey that they encountered and their hunting success (Figure 3 and Appendix S2: Table S1).
+However, when predators were novice, there was a strong negative correlation between their hunting success and the mean speed of the prey that they encountered (Figure 3 and Appendix S2: Table S1).
 Hence, novice individuals that encountered faster prey were less successful.
@@
 However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-Our results show that both mechanisms operated simultaneously, such that there was no directional increase in behavioural specialization or flexibility in the population.
-Instead, the consequences from experience appear to be a property of individuals, such that each predator developed, through extensive practice, their own expertise and behavioural trajectory; some specialized at fast-paced hunting, while others adopted a slower and more flexible tactic.
+Our results show that there was no directional increase in either behavioural specialization or flexibility with experience in the population.
+Instead, the consequences of gaining experience appear to be a property of individuals.
+We found that each predator developed, through extensive practice, their own expertise and behavioural trajectory, with some specializing in fast-paced hunting, and others adopting a slower and more flexible tactic.
 The predators' tactics were matched to prey encounters, such that specialized cursorial hunters experienced more predictable encounters, while slower and flexible hunters experienced more unpredictable encounters, with no difference in success between the two predator-types.
-This predator-prey behavioural matching grew stronger with predator experience, while the relationship between the prey's behaviour and hunting success diminished.
-Together, our observations suggest that predators adjust their hunting tactic with experience, and the degree at which they specialize in it, to the behaviour of the prey that they encountered throughout their lifetime in the game.
+This predator-prey behavioural matching grew stronger with predator experience, while the strenght of the relationship between hunting success and prey behaviour decreased.
+Together, our observations suggest that predators in *DBD* adjust their hunting tactic with experience, and the degree to which they specialize in it, to the behaviour of the prey that they encounter throughout their lifetime in the game.
 Moreover, the predator-prey behavioural escalation through experience suggests that learning may be a catalyst for arms races.
@@
 However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data includes repeated measures of individual success through time.
-In contrast, our analyses revealed that there was no population increase in expertise; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition.
+In contrast, our analyses revealed that there was no population increase in expertise over time; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition.
 For instance, many predators increased their success (Appendix S1: Figure S1A), but others displayed a decrease in success (Appendix S1: Figure S1B) or no change in success at all with experience.
-We predicted that this would occur because predators should differ in the type of prey that they encounter, as some may be easier to capture than others.
+We predicted that this could occur because predators should differ in the type of prey that they encounter, as some may be easier to capture than others.
 This is often the case in nature as prey can use variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
@@
 Thus, the predators in *DBD* were probably exploring and refining different tactics at this stage of experience.
-Interestingly, individuals became increasingly distinct in their level of foraging specialization with experience, which was related to the degree of variability in prey encounters.
-Predators that experienced predictable encounters with their prey specialized in hunting at high speeds, while those that experienced less predictable encounters adopted a slower and flexible strategy.
+Interestingly, differences in individual foraging specialization among players increased with experience, which was related to the degree of variability in prey encounters.
+Predators that experienced predictable encounters with their prey across matches specialized in hunting at high speeds, while those that experienced less predictable encounters adopted a slower and flexible strategy.
 This is similar to other studies finding that fast-paced hunting is a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022].
@@
 Yet, its has remained largely unknown whether this trait-matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where we could directly monitor interactions, we found that experience drives individual specialization, and that predators adjust their behaviour to their prey.
+By capitalizing on a virtual predator-prey system where we could directly monitor interactions, we found that experience drives individual variation in specialization, and that predators adjust their tactic to the behaviour of their prey.
 Moreover, individuals displayed large differences in the development of their expertise, which could result from differences in learning, as we found that almost half the population did not change their behaviour with experience.
@@
 ```{r eval = FALSE}
+
+Older text from the character-state :
+"The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience (Figure 3 inside the black squares and Appendix S2: Table S1).
+For example, novice predators that tended to be faster maintained this strategy as they gained experience (Figure 3 inside the black squares and Appendix S2: Table S1).
+Overall, we detected the same patterns as those from the within-experience state correlations described above.
+The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that the hunting strategies of predators were more similar among experience levels closer in time (Figure 3 inside the black squares and Appendix S2: Table S1)."
 
@@
 
-# AKNOWLEDGEMENTS
+# ACKNOWLEDGEMENTS
 

### 2023-03-30 manuscript/Chapter2-manuscript.Rmd
integrated some of PO's changes

@@
 Authorship statement : With MFF as the leader, all authors participated in conceiving the ideas behind the study.
-MFF prepared the data, conducted the analyses, and wrote the manuscript.
+MFF prepared the data, conducted the analyses, and wrote the manuscript with input from all coauthors.
 All authors reviewed and accepted the final version of the manuscript.
@@
 However, in predator-prey systems, many studies have outlined that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
-The resource-predictability hypothesis argues that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
+The resource-predictability (or resource-heterogeneity) hypothesis argues that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
 In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-When predators directly interact with their prey, empirical evidence shows that they often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
+When predator-prey interactions are directly observed, empirical evidence shows that predators often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
 Yet, a recurring question that emerges from these studies is whether and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011].
@@
 We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the prey groups encountered by predators.
-For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean hunting success.
+For the mean part of the model, it allows us to test whether individual predators differed in the average speed of the groups of prey encountered across the study.
+For the dispersion part, it allows us to test whether individual predators differed in the (dis)similarity of the groups of prey encountered across the study (i.e.
+if resource heterogeneity was higher for some individuals compared to others).
+For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean prey capture.
 For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered as proxy for prey skills on both the mean and dispersion part of the equation.
@@
 
-At the population level, we predicted that predators would become either increasingly flexible or specialized with more experience.
-However, our results do not support this prediction.
+At the population level, predators did not change their mean speed with experience (i.e.
+intercept of the mean predator speed; Table 2).
+Moreover, there was no directional increase in foraging flexibility or specialization with experience.
 Indeed, the observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e.
@@
       as_sup("\nb "),
-      "The intercept values on the mean part of the equation for all traits indicate average behaviour and success at the population level.
+      "The intercept values on the mean part of the equation for all traits indicate mean behaviour and success at the population level.
 The intercept values on the dispersion (i.e.
@@
 the intercept of the mean speed for the predator ID; Table 3).
-These differences remained stable to the intermediate stage and then increased at the advanced stage to a level higher than when predators were novice (Table 3 and Appendix S1: Figure S4).
-For the dispersion part of the model, predators displayed considerable differences in their degree of hunting specialization, and these differences increased with experience (i.e.
+These differences remained stable from the novice to the intermediate stages, and then increased at the advanced stage to reach a level higher than when predators were novice (Table 3 and Appendix S1: Figure S4).
+Predators displayed considerable differences in their degree of hunting specialization, and these differences increased with experience (i.e.
 the intercept of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S4).
-Thus, the predator population is composed of both specialist and flexible individuals, and they further differentiate themselves as specialist/flexible hunters as they gain experience (Figure 2).
+Thus, as individual predators gain experience, the population becomes more heterogeneous, with an assemblage of both specialist and flexible hunters.
+Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 2).
+Importantly, 13% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
+$\ge$0.2 change in standard deviation), 56% displayed lower changes (i.e.
+>0.05 and <0.2 change in standard deviation), while 43% remained relatively stable (i.e.
+$\le$0.05 change in standard deviation).
 
@@
       as_sup("\nb "),
-      "The intercept values on the mean part of the equation for all traits indicate among individual differences in average behaviour and success.",
+      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
       as_sup("\nc "),
@@
 the intercept of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S4).
-In addition, individuals experienced largely distinct degrees of variability among their encounters with the prey.
-Hence, some predators experienced stable/predictable encounters with their prey, while others experienced unstable/unpredictable encounters with their prey throughout the study period (i.e.
+In addition, individuals differed in the heterogeneity of the groups of prey encountered across the study period.
+Hence, some predators encountered prey groups with similar average speeds, while others encountered prey groups with different average speeds throughout the study period (i.e.
 the intercept of sigma prey speed for the predator ID; Table 3).
@@
 The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
-Both figure panels are ordered by ascending degree of increase in either specialization or flexibility."}
+Both figure panels are ordered by ascending degree of increase in either specialization or flexibility.
+We selected the individuals displayed in the figure by first substracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles.
+Individuals on panel A have an increase in specialization $\ge$0.2 standard deviations, while those on panel B have an increase in flexibility $\ge$"0.28 standard deviations.}
 
@@
 
-At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV) across their matches (Figure 3 and Appendix S2: Table S1).
-Thus, faster predators specialized at travelling fast, while slower predators were more flexible in their movement through time.
-In general, predators that encountered groups of prey that were on average faster (mean) tended to be faster (mean) (Figure 3 and Appendix S2: Table S1).
-At the three experience levels, there were only weak correlations between predator IIV and mean prey speed (Figure 3 and Appendix S2: Table S1).
-However, predators that experienced more predictable encounters with their prey (IIV) specialized in a faster hunting tactic (IIV) (Figure 3 and Appendix S2: Table S1).
+At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV; Figure 3 and Appendix S2: Table S1).
+Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time.
+Predators that were on average faster (mean) also encountered groups of prey that were on average faster (mean) (Figure 3 and Appendix S2: Table S1).
+At the three experience levels, there were only weak correlations between IIV in predator speed and mean prey speed (Figure 3 and Appendix S2: Table S1).
+However, predators that encountered groups of prey with similar speeds (IIV) specialized in their hunting tactic (IIV) (Figure 3 and Appendix S2: Table S1).
+Hence, predators that encountered groups of prey with similar average speeds were more specialized, while those that encountered groups of prey with different average speeds were more flexible.
 For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Appendix S2: Table S1).
@@
 We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Appendix S2: Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Appendix S2: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
-However, when predators were novice, there was a strong negative correlation between their hunting success and the mean speed of the prey that they encountered (Figure 3 and Appendix S2: Table S1).
-Hence, novice individuals that encountered faster prey were less successful.
+However, novice individuals that encountered groups of prey with faster speeds were less successful (Figure 3 and Appendix S2: Table S1).
 This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Appendix S2: Table S1).
@@
 Our results show that there was no directional increase in either behavioural specialization or flexibility with experience in the population.
-Instead, the consequences of gaining experience appear to be a property of individuals.
-We found that each predator developed, through extensive practice, their own expertise and behavioural trajectory, with some specializing in fast-paced hunting, and others adopting a slower and more flexible tactic.
-The predators' tactics were matched to prey encounters, such that specialized cursorial hunters experienced more predictable encounters, while slower and flexible hunters experienced more unpredictable encounters, with no difference in success between the two predator-types.
-This predator-prey behavioural matching grew stronger with predator experience, while the strenght of the relationship between hunting success and prey behaviour decreased.
-Together, our observations suggest that predators in *DBD* adjust their hunting tactic with experience, and the degree to which they specialize in it, to the behaviour of the prey that they encounter throughout their lifetime in the game.
+Instead, both mechanisms operated simultaneously, such that each individual predator developed their own expertise and behavioural trajectory over successive encounters with prey; some specialized in fast-paced hunting, and others adopted a slower and more flexible tactic.
+The predators' tactics were matched to speed of the prey that they encountered, such that specialized cursorial hunters encountered similar groups of prey, while slower and flexible hunters encountered varying groups of prey, with no difference in success between the two types of hunters.
+This predator-prey behavioural matching grew stronger with predator experience, while the strenght of the relationship between the predator's hunting success and prey behaviour decreased.
+Together, our observations suggest that predators in *DBD* learn to adjust their hunting tactic to the behaviour of the prey that they encounter throughout their lifetime in the game.
 Moreover, the predator-prey behavioural escalation through experience suggests that learning may be a catalyst for arms races.
@@
 In contrast, our analyses revealed that there was no population increase in expertise over time; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition.
-For instance, many predators increased their success (Appendix S1: Figure S1A), but others displayed a decrease in success (Appendix S1: Figure S1B) or no change in success at all with experience.
-We predicted that this could occur because predators should differ in the type of prey that they encounter, as some may be easier to capture than others.
-This is often the case in nature as prey can use variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-However, prey speed in our study did not shape individual differences in expertise acquisition by predators, even if predators differed in the prey that they encountered.
-This was unexpected, because prey speed is an important predictor of predator success in this system as well as in others [@Walker.etal2005;@Kelley.Magurran2011;@FraserFranco.etal2022].
-Despite that other antipredator tactics may mediate these individual responses by predators, it is likely that individual differences in motivation and perseverance, attention span, or memory retention were also major causes [@Warburton2003;@morand-ferronStudyingEvolutionaryEcology2016;@Dukas2019].
+Many predators increased their success (Appendix S1: Figure S1A), but others displayed a decrease in success (Appendix S1: Figure S1B) or no change in success at all with experience.
+We predicted that this could occur because predators could differ in the prey that they encounter by chance, as some may be easier and others more difficult to capture.
+In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
+In *DBD* we showed in a previous study that faster speed and space coverage is an effective antipredator strategy used by the prey [@FraserFranco.etal2022].
+Other studies also show that faster escapes are effective to escape predation [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
+Yet, prey speed in our current study did not shape individual differences in expertise acquisition by predators, even if predators differed in the prey that they encountered.
+It is however possible that other antipredator tactics mediated these individual predator responses, as we focused solely on prey speed at the group level.
+For example, unpredictable escapes and turning angles are important locomotor traits enabling prey to confuse human and non-human predators during the attack sequence [@Jones.etal2011;@Briffa2013;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018], which could prove to be difficult for a predator to learn and adjust to if it more often encountered prey using these tactics.
+
+Alternatively, it is possible that individual differences in learning were also major causes, irrespective of differences in prey encounters [@Warburton2003;@morand-ferronStudyingEvolutionaryEcology2016;@Dukas2019].
+*ici je pourrais plutot parler de différences d'apprentissage.
+Il pourrait même être + difficile d'apprendre à capturer des proies selon leur comportement car ça ne donne pas toujours autant de signaux directs que la coloration par exemple.
+Trouver des sources pour la coloration...ajouter que c'est irrespective of prey behaviour pour différencier par rapport à l'explication d'en haut*
+
  For instance, a persevering predator may increase its success much more steadily than an unmotivated predator that quickly abandons a chase.
@@
 prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days.
+
  While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
@@
 On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty.
-Importantly, 13% of the predator population displayed the greatest change in foraging specialization/flexibility with experience (i.e.
-$\ge$ 0.2 change in standard deviation), 56% displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation), while 43% remained relatively stable (i.e.
-$\le$ 0.05 change in standard deviation).
+
+ici une phrase qui rappelle que pas tout le monde a appris
  Thus, while individual differences in specialization did increase with experience, they were in part driven by a proportion of the population that displayed greater changes in behaviour compared to others.

### 2023-03-30 manuscript/Chapter2-manuscript.Rmd
move notes in MS to the notes file

@@
 
-```{r eval = FALSE}
-
-Older text from the character-state :
-"The foraging strategies of predators, that is, the correlations between the mean and IIV of speed, remained structurally stable among the levels of experience (Figure 3 inside the black squares and Appendix S2: Table S1).
-For example, novice predators that tended to be faster maintained this strategy as they gained experience (Figure 3 inside the black squares and Appendix S2: Table S1).
-Overall, we detected the same patterns as those from the within-experience state correlations described above.
-The correlations between trait values were also stronger among novice-intermediate and intermediate-advanced states than between novice-advanced states, indicating that the hunting strategies of predators were more similar among experience levels closer in time (Figure 3 inside the black squares and Appendix S2: Table S1)."
-
-Discussion :
-
-- peut-être ajouter le fait que malgré que la vitesse soit mieux pour les proies, elles pourraient buffer ça en étant + imprévisibles.
-
-- peut être ajouter que l'escalade est aussi dû au fait que la proie pourrait être plus susceptible à la prédation en étant rapide car elle s'expose plus.
-
-*duckworth en tete*
-
-Contrary to Hanifin et al. 2008, we find a directional symmetry (i.e. trait matching).
-
-In abrams 2000, we read : "The interaction of predator and prey traits in determining capture rate seems to be the most important factor determining the stability of the entire system.
-Most studies in which cycles are a commonly observed outcome assume that the predator maximizes its rate of capture of the prey by matching the prey's phenotype"
-We can also read : "If there is sufficiently strong stabilizing selection based on the costs of extreme trait values in both species, then stable equilibria are likely"
-
-In Reimche et al. 2020 : in the discussion we can read that we still dont understand the factors driving phenotypic (mis)matching. In my case, it appears that learning may play a role.
-Revoir mes résultats dans le cadre des résultats de Glaudas et al. 2019. Les 2 concordent bien.
-
-Voir Miszei comme exemple parmi dautres pour trait matching.
-
-check Mougi etal. 2011 for arms-races based on phenotypic plasticity (modèle théorique)
-
-voir Edgell : prey-induced plasticity leads to covariance between predator-prey trait
-
-**garder en tête l'étude de Lima AmNat sur purposeful unpredictability**
-**Iannou also found strong among individual differences in slopes of trial number**
-
-# Some caveats
-
-"différences entre individus dans les proies rencontées : la direction peut être des 2 côtés, soit c'est parce que le prédateur drive le fait que les proies sont plus variables en général.
-Ou c'est parce qu'il rencontre des proies variables et donc il adopte cette stratégie."
-
-"parler de matchmaking pourrait influencer courbes (moins de variance intermediare car proche de la moyenne de skill)"
-
-"faire la distinction que certains optimisent, certains sont moins bon, donc ça varie dans la population."
-
-"covariance est drivé par un individu pour la moyenne"
-
-À faire :
-
-- parler du sampling et du modèle pour tester les biais dans les méthodes [done]
-- dans mon dernier paragraphe, parler du fait que les proies aussi s'ajustent
-
-Phrases de conclusion :
-
-Début de la conclusion, revenir brièvement sur notre système et les jeux. Les petits avantages
-
-Our results also have implications also for predator-prey models of trait-matching, because such models are usually studied at the evolutionary scale.
-
-Therefore, our results have important implications for future predator-prey models, which should incorporate individual variation in learning and prey encounters to better predict under which ecological contexts specialization should be favoured over flexibility.
----> pour la conclusion
-
-```
-
 # ACKNOWLEDGEMENTS

### 2023-04-03 manuscript/Chapter2-manuscript.Rmd
update discussion

@@
 However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data includes repeated measures of individual success through time.
-In contrast, our analyses revealed that there was no population increase in expertise over time; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition.
-Many predators increased their success (Appendix S1: Figure S1A), but others displayed a decrease in success (Appendix S1: Figure S1B) or no change in success at all with experience.
-We predicted that this could occur because predators could differ in the prey that they encounter by chance, as some may be easier and others more difficult to capture.
+Our analyses revealed that there was no population increase in expertise over time; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition (Figure 1, Appendix S1: Figure S1A-S1B).
+We predicted that this would occur if, by chance, predators differed in the prey that they encountered, because some may be easier and others more difficult to capture.
 In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-In *DBD* we showed in a previous study that faster speed and space coverage is an effective antipredator strategy used by the prey [@FraserFranco.etal2022].
-Other studies also show that faster escapes are effective to escape predation [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
-Yet, prey speed in our current study did not shape individual differences in expertise acquisition by predators, even if predators differed in the prey that they encountered.
-It is however possible that other antipredator tactics mediated these individual predator responses, as we focused solely on prey speed at the group level.
-For example, unpredictable escapes and turning angles are important locomotor traits enabling prey to confuse human and non-human predators during the attack sequence [@Jones.etal2011;@Briffa2013;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018], which could prove to be difficult for a predator to learn and adjust to if it more often encountered prey using these tactics.
+In *DBD* we previously showed that faster speed and space coverage is an effective antipredator strategy used by the prey [@FraserFranco.etal2022].
+Other studies have also found that faster escapes are effective to escape predation [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
+Yet, despite that predators differed in the prey that they encountered, prey speed did not shape individual differences in expertise acquisition.
+It is however possible that other antipredator tactics mediated these individual responses.
+For example, it is well known in *DBD* that some prey groups use mobbing to confuse the predator or prevent it from capturing an injured individual.
+However, like natural predator-prey systems, direct predator-mobbing in *DBD* is dangerous and requires coordinated actions that are learned through experience [@Graw.Manser2007;@Dutour.etal2016;@Pitman.etal2017;@Dutour.etal2019;@Rampim.etal2020;@Szymkowiak2021], and was thus probably not a pervasive antipredator strategy.
+Other antipredator tactics known to confuse human and non-human predators during the attack sequence are unpredictable escapes and turning angles [@Jones.etal2011;@Briffa2013;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018].
+While predators can adjust to unpredictable prey escapes [@Szopa-Comley.Ioannou2022], it could still be more arduous for a predator to learn and optimize its hunting success if it more often encountered prey using these tactics.
 
-Alternatively, it is possible that individual differences in learning were also major causes, irrespective of differences in prey encounters [@Warburton2003;@morand-ferronStudyingEvolutionaryEcology2016;@Dukas2019].
-*ici je pourrais plutot parler de différences d'apprentissage.
-Il pourrait même être + difficile d'apprendre à capturer des proies selon leur comportement car ça ne donne pas toujours autant de signaux directs que la coloration par exemple.
-Trouver des sources pour la coloration...ajouter que c'est irrespective of prey behaviour pour différencier par rapport à l'explication d'en haut*
-
- For instance, a persevering predator may increase its success much more steadily than an unmotivated predator that quickly abandons a chase.
-Another factor that may explain differences in the development of expertise is the time delay between hunting events.
-For example, a predator that played 300 matches in the span of six months might forget more critical information (e.g.
+Alternatively, it is possible that individual variation in learning rates due to the time delay between hunting events drove the observed differences in expertise acquisition, irrespective of the prey groups that predators encountered.
+For example, in *DBD*, a predator that played 300 matches in the span of six months might forget more critical information (e.g.
 prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days.
-
 While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
+Moreover, the predators in *DBD* may have differed in their capacity to process cues related to prey detection.
+For example, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
+@Szopa-Comley.etal2020 also found consistent among individual variation in the capacity to detect cryptic and conspicuous prey in three-spined sticklebacks (*Gasterosteus aculeatus*).
+Thus, individual predators should differ in their expertise if they do not learn equally how to exploit the visual cues that facilitate prey detection [@dukasEvolutionaryBiologyAnimal2004;@Dukas2019;@Wright.etal2022].
 

### 2023-04-14 manuscript/Chapter2-manuscript.Rmd
Discussion finished (if everything OK)

@@
 bibliography: references2.bib
-csl: chicago-author-date.csl
+csl: ecology.csl
 ---
@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or on different resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@kernaleguenDeterminantsIndividualForaging2015;@Phillips.etal2017].
+Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or on different resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@Kernaleguen.etal2015;@Phillips.etal2017].
 A growing body of evidence suggests that ecological interactions such as predator-prey interactions can drive this individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
@@
 Empirical studies on human and non-human hunters show that experience optimizes the efficiency (e.g.
-search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@macdonaldCrossculturalComparisonLearning2007;@Reid.etal2010;@Wilson-Rankin2015].
+search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
 This body of work suggests that such optimization may thus promote individual foraging specialization (e.g.
@@
 In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-When predator-prey interactions are directly observed, empirical evidence shows that predators often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
+When predator-prey interactions are directly observed, empirical evidence shows that predators often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
 Yet, a recurring question that emerges from these studies is whether and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011].
@@
 
-We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@leeDoubleHierarchicalGeneralized2006;@cleasbyQuantifyingPredictabilityBehaviour2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
+We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
 We categorized the predators by their experience based on the number of matches they played (i.e.
@@
 Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 2).
-Importantly, 13% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
-$\ge$0.2 change in standard deviation), 56% displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation), while 43% remained relatively stable (i.e.
+Importantly, 12.6% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
+$\ge$0.2 change in standard deviation), 44.7% displayed lower changes (i.e.
+>0.05 and <0.2 change in standard deviation), while 42.7% remained relatively stable (i.e.
 $\le$0.05 change in standard deviation).
@@
 We selected the individuals displayed in the figure by first substracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles.
-Individuals on panel A have an increase in specialization $\ge$0.2 standard deviations, while those on panel B have an increase in flexibility $\ge$"0.28 standard deviations.}
+Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.28 standard deviations."}
 
@@
 However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-Our results show that there was no directional increase in either behavioural specialization or flexibility with experience in the population.
-Instead, both mechanisms operated simultaneously, such that each individual predator developed their own expertise and behavioural trajectory over successive encounters with prey; some specialized in fast-paced hunting, and others adopted a slower and more flexible tactic.
-The predators' tactics were matched to speed of the prey that they encountered, such that specialized cursorial hunters encountered similar groups of prey, while slower and flexible hunters encountered varying groups of prey, with no difference in success between the two types of hunters.
-This predator-prey behavioural matching grew stronger with predator experience, while the strenght of the relationship between the predator's hunting success and prey behaviour decreased.
+Our results show that there was no directional increase in either behavioural specialization or flexibility with experience at the population level.
+Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with prey; some specialized in fast-paced hunting, and others adopted a slower and more flexible tactic with experience.
+Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period.
+With experience, predators increasingly matched their tactic to the speed of the prey that they encountered, which simultaneously relaxed the negative consequences of encountering faster prey.
 Together, our observations suggest that predators in *DBD* learn to adjust their hunting tactic to the behaviour of the prey that they encounter throughout their lifetime in the game.
-Moreover, the predator-prey behavioural escalation through experience suggests that learning may be a catalyst for arms races.
+The resulting reciprocal behavioural escalation between the predators and the prey suggests that learning may be a catalyst for arms races [@Agrawal2001;@Kishida.etal2006;@Mougi.Kishida2009;@Mougi.etal2011].
 
@@
 In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-In *DBD* we previously showed that faster speed and space coverage is an effective antipredator strategy used by the prey [@FraserFranco.etal2022].
+In *DBD* we previously showed that faster speed and space coverage is an effective antipredator strategy used by the prey making them more difficult to capture [@FraserFranco.etal2022].
 Other studies have also found that faster escapes are effective to escape predation [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
@@
 
-Alternatively, it is possible that individual variation in learning rates due to the time delay between hunting events drove the observed differences in expertise acquisition, irrespective of the prey groups that predators encountered.
+Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition, irrespective of the prey groups that predators encountered.
 For example, in *DBD*, a predator that played 300 matches in the span of six months might forget more critical information (e.g.
@@
 While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
-Moreover, the predators in *DBD* may have differed in their capacity to process cues related to prey detection.
+Moreover, the predators in *DBD* may have differed in their ability to detect prey.
 For example, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
@@
 This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016].
-Thus, the predators in *DBD* were probably exploring and refining different tactics at this stage of experience.
-Interestingly, differences in individual foraging specialization among players increased with experience, which was related to the degree of variability in prey encounters.
-Predators that experienced predictable encounters with their prey across matches specialized in hunting at high speeds, while those that experienced less predictable encounters adopted a slower and flexible strategy.
-This is similar to other studies finding that fast-paced hunting is a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022].
-On the contrary, instead of focusing solely on one tactic, predators that experienced unpredictable encounters probably adjusted their behaviour to minimize the consequences of uncertainty.
+Thus, predators in *DBD* were probably exploring and refining different tactics at this stage of experience.
+Within the population, individuals became increasingly distinct in their tactics as well as in their specialization with experience, which was related to the degree of variability in prey encounters.
+Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy.
+Fast-paced hunting is indeed a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when hunting prey that use unpredictable escapes [@Szopa-Comley.Ioannou2022].
+This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period.
+Interestingly, the behavioural response (i.e.
+tactic use and specialization) to experience by individual predators differed.
+For instance, 42.7% of the population did not alter their degree of specialization with experience (i.e.
+remaining either faster and more specialized, or slower and more flexible), while 57.3% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience.
+Thus, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning at varying degrees how to specialize on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
 
-ici une phrase qui rappelle que pas tout le monde a appris
- Thus, while individual differences in specialization did increase with experience, they were in part driven by a proportion of the population that displayed greater changes in behaviour compared to others.
-
-As they gained experience, predators increasingly matched their tactic to their prey, suggesting that they learned how to hunt via repeated interactions.
-However, while the mean speed of predators was strongly and increasingly matched to the mean speed of the prey, further investigations revealed that this apparent increase was driven largely by one individual.
-Yet, predators also adjusted their degree of flexibility to their prey even if the change was not very strong (Figure 3 and Appendix S2: Table S1).
-In that regard, despite that only a portion of the population displayed large changes in specialization, and that adjustments to the prey were not as strong as we expected, our results still provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning to adjust their degree of specialization based on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
-This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period.
-
-An emerging pattern reported in predator-prey research is that predators and prey often match their phenotype to one another (i.e.
-positive trait covariances), which appears to be driven by an arms-race-like reciprocal phenotypic plasticity [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@Mougi.etal2011;@McGhee.etal2013].
-From an evolutionary perspective, @BrodieIII.BrodieJr.1999 showed in the garter snake (*Thamnophis sirtalis*) - roughskin newt (*Taricha granulosa*) system that such escalations may occur when prey develop defensive traits, which leads to stronger selection in predators, resulting in counteradaptations that circumvent the prey's defenses.
-In our system, the predator's success is negatively correlated with the prey's speed, which is an effective antipredator tactic [@FraserFranco.etal2022].
-However, we found that as the covariance between predator speed and prey speed increased with experience, reminiscent of an arms race, the consequences of hunting faster prey decreased with experience.
-Moreover, this pattern was followed by a decrease in among individual variation in success with experience.
-This has important implications for the role of experience on predator-prey interactions, as our results suggest that learning enables predators to effectively develop countermeasures to the prey's defenses within their lifetime (i.e.
-at nonevolutionary timescales).
-It also provides empirical evidence for the hypothesis that reciprocal phenotypic plasticity through learning may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
+As predators gained experience, their tactic was increasingly matched to the speed of their prey.
+One interpretation could be that both predators and prey learned from each other in an arms-race-like reciprocal relationship [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@Mougi.etal2011].
+For instance, predators that encountered faster prey could have learned to increase their speed to better capture them, resulting in an increase in the speed of the prey to circumvent the predator's attacks.
+In this type of system, faster prey should be better at escaping both slower and faster predators [@Mougi.etal2011], which concords with what we previously observed in this sytem [@FraserFranco.etal2022].
+@BrodieIII.BrodieJr.1999 argue that when prey express defensive phenotypes (e.g.
+physical armaments or venom), selection on predators should be strong because the consequences of being injured are greater than missing a meal.
+If predators improve their exploitative ability, then an arms-race should emerge, and the consequences of hunting dangerous prey should decrease [@BrodieIII.BrodieJr.1999].
+Similarly, we found that has the predator gained experience, the negative consequences of encountering prey groups with higher speeds were relaxed, and the variation in success among predators decreased.
+However, in an arms-race, faster predators would have successfully preyed upon faster and slower prey and would have obtained higher success than slower predators [@Mougi.etal2011], which was not the case in the present study.
+A more likely interaction scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible preyed upon different prey but achieved equal success.
+Thus predators in *DBD* appear to optimize their success by learning to match their tactic to their prey with experience, suggesting that learning through reciprocal interactions may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
 
@@
 
-The interactions of predator and prey traits are probably the most important processes involved in population cycles and are expected to occur when predators match their phenotype to their prey [@abramsEvolutionPredatorPreyInteractions2000].
+The interactions of predator and prey traits are probably the most important processes involved in population cycles and should occur when predators match their phenotype to their prey [@abramsEvolutionPredatorPreyInteractions2000].
 Yet, its has remained largely unknown whether this trait-matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where we could directly monitor interactions, we found that experience drives individual variation in specialization, and that predators adjust their tactic to the behaviour of their prey.
-Moreover, individuals displayed large differences in the development of their expertise, which could result from differences in learning, as we found that almost half the population did not change their behaviour with experience.
-Our results have implications for predator-prey models of trait-matching, because such models are often studied at evolutionary timescales.
-Therefore, future studies should incorporate individual variation in experience to better predict under which ecological contexts specialization should be favoured over flexibility.
+By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise.
+With experience, half of the predator population changed their behaviour by developping either a specialized or flexible tactic that was matched to the speed of their prey.
+Our results could be useful to guide predator-prey models of trait-matching, which are often studied at evolutionary timescales.
+For instance, future studies could incorporate individual variation in experience in their models to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility.
 Lastly, virtual systems are increasingly recognized among ecologists as effective systems to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].

### 2023-04-17 manuscript/Chapter2-manuscript.Rmd
document does not rely on pandoc crossref anymore. update equations

@@
     fig_caption: yes
-    pandoc_args: ["-Fpandoc-crossref"] # to have eq. numbers
+    #pandoc_args: ["-Fpandoc-crossref"] # to have eq. numbers
 bibliography: references2.bib
@@
 
-The full model has the following form, with each equation repeated three times (i.e. one for each level of experience) :
+The full model has the following form, with each equation repeated three times (i.e. one for each level of experience):
 
-$$
-\begin{align}
-speed_{pred} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
-log(\sigma_{e,\ pred}) &= X_{d}\ b_{d} + Z\ id_{d}
-\end{align}
-$${#eq:eqn1}
+```{r model_equations, ft.align = "left"}
 
-$$
-\begin{align}
-speed_{prey} &= \text{ } X_{m}\ b_m + M\ env_{m} + N\ av_{m} + Z\ id_{m} + e \\
-log(\sigma_{e,\ prey}) &= X_{d}\ b_{d} + Z\ id_{d}
-\end{align}
-$${#eq:eqn2}
+# Prepare equations
+eqs <- c(
+  "speed_{pred} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
+  "log(\\sigma_{e,pred}) = X_{d}\\ b_{d} + Z\\ id_{d}",
+  "speed_{prey} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
+  "log(\\sigma_{e,prey}) = X_{d}\\ b_{d} + Z\\ id_{d}",
+  "success_{pred} = X_{m}\\ b_{m} + Z\\ id_{m} + e"
+)
+eqs_num <- c(
+    "(eqn. 1.1)",
+    "(eqn. 1.2)",
+    "(eqn. 2.1)",
+    "(eqn. 2.2)",
+    "(eqn. 3)"
+)
 
-$$
-\begin{align}
-success_{pred} &= \text{ } X_{m}\ b_m + Z\ id_{m} + e
-\end{align}
-$${#eq:eqn3}
+# Combine into a dataframe
+df <- data.frame(
+    formula = eqs,
+    number = eqs_num
+)
+
+# Create a table to display on Word
+ft <- flextable(df)
+
+ft <- compose(
+  x = ft, j = 1,
+  value = as_paragraph(
+    as_equation(formula, height = .5)
+  )
+)
+
+# Customize table
+my_theme <- function(x, ...) {
+  x <- colformat_double(x, big.mark = " ",
+                        decimal.mark = ".",
+                        digits = 2)
+  x <- border_remove(x)
+  x <- delete_part(x, part = "header")
+  x <- align(x, j = 1, align = "left", part = "body")
+  x <- align(x, j = 2, align = "right", part = "body")
+  x <- font(x, fontname = "Times New Roman", part = "body")
+  x <- fontsize(x, size = 12, part = "body")
+  x <- width(x, j = 1, width = 10, unit = "cm")
+  x <- width(x, j = 2, width = 6.51, unit = "cm")
+}
+
+ft <- my_theme(x = ft)
+ft
+
+```
 
@@
 
-We parameterized equations (1) and (2) with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation (3) (predator hunting success).
-We used Gaussian priors for the prey rank ($N(2.5,\ 1)$) and game duration ($N(10,\ 2)$) on the mean part of the model, and the default priors in "brms" for the dispersion part.
-We used the default Student t priors in "brms" for the intercepts on the mean and dispersion part of the equation.
+We parameterized equations 1.1 to 2.2 with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation 3 (predator hunting success).
+We used Gaussian priors for the prey rank ($N(2.5,\ 1)$) and game duration ($N(10,\ 2)$) on the mean part of the model (equations 1.1, 2.1, and 3), and the default priors in "brms" for the dispersion part (equations 1.2 and 2.2).
+We used the default Student t priors in "brms" for the intercepts on the mean and dispersion part of the model.
 For hunting success, we applied a Gaussian prior on the precision parameter ($N(2,\ 1)$).
-For every predicted variable, we applied a half-Gaussian on the random effects for the mean part of the model ($N(0,\ 1)$), and the default "brms" Student t prior for the dispersion part of the model.
+For every predicted variable, we applied a half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part of the model (equations 1.1, 2.1, and 3), and the default "brms" Student t prior for the dispersion part of the model (equations 1.2 and 2.2).
 
@@
   font(fontname = "Times New Roman", part = "all") %>%
-  width(j = c(2,3,4,5), width = 3.7, unit = "cm") %>%
+  width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
   width(j = 1, width = 3.2, unit = "cm")

### 2023-04-18 manuscript/Chapter2-manuscript.Rmd
updated MS. full code for tables no to prevent bug

@@
     fig_caption: yes
-    #pandoc_args: ["-Fpandoc-crossref"] # to have eq. numbers
 bibliography: references2.bib
@@
 library(officer)
-library(tidyr)
+library(dplyr)
 
@@
 
-dat[, c(2:6) := lapply(.SD, function (x) as.factor(x)), .SDcols = c(2:6)]
+dat[, c(2:6) := lapply(.SD, function(x) as.factor(x)), .SDcols = c(2:6)]
 
@@
 
+# Transform values as a mathematical formula
 ft <- compose(
@@
 
+# Apply theme and print
 ft <- my_theme(x = ft)
@@
 We parametrized every model described above to run four MCMC chains with 1000 posterior samples for each parameter.
-We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table I), and 1500 iterations with a thinning set to four for the additive model with a global smoother and group-level smoothers as well as for the additive model with group-level smoothers only (Table I).
-Burn-in was set to 500 iterations in each model.
+We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table I), and 1500 iterations with a thinning set to four for the additive model with global and group-level smoothers and for the additive model with group-level smoothers only (Table I).
+We set the first 500 iterations in each model as warmups.
 We parametrized the MDHGLM to run 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups.
-We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.05, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021a].
+We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021a].
 We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
@@
 
-tab1 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table1.rds"))
+# ===========================================================================
+# 1. Import the model fit
+# ===========================================================================
 
+# Open the loo table
+path <- file.path(here::here("outputs", "03_outputs_model-validation"))
+loo_tab <- data.table(readRDS(file.path(path, "03A_lootable.rds")))
+
+# Add model column
+loo_tab[, model := c("Group-level smoothers only",
+                     "Global smoother + group-level smoothers",
+                     "Global smoother only")]
+
+# Reorder columns
+loo_tab <- loo_tab[, c(9, 1:8)]
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 2. Compute the table using flextable
+# ===========================================================================
+
+# Prepare the table parameters ----------------------------------------------
+
+# Custom header
+my_header <- data.frame(
+   col_keys = c("model",
+                "elpd_diff",
+                "se_diff",
+                "elpd_loo",
+                "se_elpd_loo"),
+   line1 = c("model",
+             "elpd \ndifference",
+             "sd \ndifference",
+             "elpd loo \nvalue",
+             "elpd loo \nstandard error"),
+   stringsAsFactors = FALSE
+)
+
+# Custom theme
+my_theme <- function(x, ...) {
+   x <- colformat_double(x, big.mark = " ",
+                         decimal.mark = ".",
+                         digits = 2)
+   x <- set_table_properties(x, layout = "fixed")
+   x <- border_remove(x)
+   std_border <- fp_border(width = 1, color = "black")
+   x <- hline_top(x, part = "all", border = std_border)
+   x <- hline_bottom(x, part = "all", border = std_border)
+   autofit(x)
+}
+
+# Create the table ----------------------------------------------------------
+
+tab1 <- loo_tab %>%
+   select(model, elpd_diff, se_diff, elpd_loo, se_elpd_loo) %>%
+   flextable(col_keys = my_header$col_keys) %>%
+   set_header_df(mapping = my_header, key = "col_keys") %>%
+   my_theme() %>%
+   merge_v(part = "header") %>%
+   merge_h(part = "header") %>%
+   fontsize(size = 10, part = "all") %>%
+   font(fontname = "Times New Roman", part = "all") %>%
+   align(align = "left", part = "all", j = 1) %>%
+   align(align = "center", part = "all", j = 2) %>%
+   align(align = "center", part = "all", j = 3) %>%
+   align(align = "center", part = "all", j = 4) %>%
+   align(align = "center", part = "all", j = 5)
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 3. Customize and print the table
+# ===========================================================================
+
+# Autofit to window
 tab1 <- autofit(tab1)
 
+# Add a footnote
 tab1 <- tab1 %>%
@@
     value = as_paragraph(
-      "* 'elpd' refers to the 'expected log pointwise density' and is the value chosen to select the best model."),
+      "* 'elpd' refers to the expected log pointwise density and is the value chosen to select the best model."),
     ref_symbols = " "
@@
 
+# Table caption
 set_caption(
@@
 )
+
+# ===========================================================================
+# ===========================================================================
+
 ```
@@
 
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure1.png"))
+knitr::include_graphics(
+  here::here("outputs", "05_outputs_figures", "05_figure1.png")
+)
 
@@
 
-tab2 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table2.rds"))
+# ===========================================================================
+# 1. Import the model fit
+# ===========================================================================
 
+# path
+path <- file.path(here::here("outputs"))
+
+# Import the model
+fit <- readRDS(
+  file.path(path, "02_outputs_models", "02B_DHMLM.rds")
+)
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 2. Fixed effects table
+# ===========================================================================
+
+# Prepare the table ---------------------------------------------------------
+
+# Extract the fixed effects from the model
+eff_tab <- data.table(fixef(fit), keep.rownames = TRUE)
+eff_tab <- eff_tab[, c(1, 2, 4:5)]
+
+# Rename variables
+setnames(
+  eff_tab,
+  c("rn", "Q2.5", "Q97.5"),
+  c("parameter", "lower_ci", "upper_ci")
+)
+
+# Add a column that specifies the experience level
+eff_tab[parameter %like% "novice", xp_level := "novice"]
+eff_tab[parameter %like% "interm", xp_level := "intermediate"]
+eff_tab[parameter %like% "advanced", xp_level := "advanced"]
+
+# Back transform success
+eff_tab[
+  parameter %like% "success",
+  c(2:4) := lapply(.SD, function(x) {plogis(x)}),
+  .SDcols = c(2:4)
+]
+
+# Back transform sigma
+eff_tab[
+  parameter %like% "sigma",
+  c(2:4) := lapply(.SD, function(x) {exp(x)}),
+  .SDcols = c(2:4)
+]
+
+# Round values to 3 digits
+eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 3)]
+
+# Reorganize the table ------------------------------------------------------
+
+# reorder columns, and then rows based on xp level
+eff_tab <- eff_tab[, c(5, 1:4)]
+setorder(
+  eff_tab,
+  cols = -"xp_level"
+)
+
+# Create trait column
+eff_tab[
+  , trait := rep(c(
+    "predator speed", "predator speed",
+    "prey speed", "prey speed", "hunting success"),
+    6
+  )
+]
+
+# Rename parameter
+eff_tab[
+   , parameter := rep(
+      c(
+         rep(c("intercept (mean)", "intercept (sigma)"), 2),
+         "intercept (mean)",
+         rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
+         "match duration (mean)"
+      ),
+      3
+   )
+]
+
+# Paste upper and lower ci with estimate
+eff_tab[, estimate := paste(format(Estimate, digits = 3), "(")]
+eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 3), sep = "")]
+eff_tab[, estimate := paste(estimate, ",", sep = "")]
+eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 3), sep = " ")]
+eff_tab[, estimate := paste(estimate, ")", sep = "")]
+eff_tab[, c("Estimate", "lower_ci", "upper_ci") := NULL]
+
+# Reshape
+eff_tab <- dcast(
+  eff_tab,
+  trait + parameter ~ xp_level,
+  value.var = "estimate"
+)
+
+# Reorder columns
+eff_tab <- eff_tab[, c(1, 2, 5, 4, 3)]
+
+# Reorder rows
+table <- eff_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]
+
+# Because I can't align hunting success properly
+table[10, 1] <- " "
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 3. Create the table using flextable
+# ===========================================================================
+
+# Prepare the table parameters ----------------------------------------------
+
+# Custom header
+my_header <- data.frame(
+  col_keys = c("trait", "parameter",
+               "novice", "intermediate", "advanced"),
+  line1 = c("Trait",
+            "Parameter",
+            "Novice",
+            "Intermediate",
+            "Advanced"),
+  stringsAsFactors = FALSE
+)
+
+# Custom theme
+my_theme <- function(x, ...) {
+  x <- colformat_double(x, big.mark = " ",
+                        decimal.mark = ".",
+                        digits = 3)
+  x <- set_table_properties(x, layout = "fixed")
+  x <- border_remove(x)
+  std_border <- fp_border(width = 1, color = "black")
+  x <- hline_top(x, part = "all", border = std_border)
+  x <- hline_bottom(x, part = "all", border = std_border)
+  autofit(x)
+}
+
+# Create the table ----------------------------------------------------------
+
+tab2 <-
+
+  # table structure
+  table %>%
+  select(trait, parameter,
+         novice, intermediate, advanced) %>%
+  flextable(col_keys = my_header$col_keys) %>%
+  set_header_df(mapping = my_header, key = "col_keys") %>%
+  my_theme() %>%
+  # Align repeated rows on column 1
+  merge_v(j = 1) %>%
+  valign(j = 1, valign = "top", part = "body") %>%
+  # font
+  fontsize(size = 10, part = "all") %>%
+  font(fontname = "Times New Roman", part = "all") %>%
+
+  # Align text
+  align(align = "left", part = "all", j = 1) %>%
+  align(align = "left", part = "all", j = 2) %>%
+  align(align = "center", part = "all", j = 3) %>%
+  align(align = "center", part = "all", j = 4) %>%
+  align(align = "center", part = "all", j = 5)
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 4. Customize and print the table
+# ===========================================================================
+
+# Autofit to window size
 tab2 <- autofit(tab2)
 
+# Table footnote
 tab2 <- tab2 %>%
@@
 )
+
+# ===========================================================================
+# ===========================================================================
 
@@
 
-tab3 <- readRDS(here::here("outputs", "05_outputs_tables", "05_table3.rds"))
+# ===========================================================================
+# 1. Import the model fit
+# ===========================================================================
 
+# path
+path <- file.path(here::here("outputs"))
+
+# Import the model
+fit <- readRDS(
+  file.path(path, "02_outputs_models", "02B_DHMLM.rds")
+)
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 2. Random effects table
+# ===========================================================================
+
+# Prepare data --------------------------------------------------------------
+
+# Extract the random effect variances
+sd_draws <- data.table(
+   as_draws_df(
+      fit, variable = "^sd_", regex = TRUE
+   )
+)
+
+sd_draws[, c(28:30) := NULL]
+
+# Calculate parameters -------------------------------------------------------
+
+# Take the exponent of sigma parameters
+sd_draws[
+   , c("sd_predator_id__sigma_speednovice_Intercept",
+       "sd_predator_id__sigma_speedinterm_Intercept",
+       "sd_predator_id__sigma_speedadvanced_Intercept",
+       "sd_predator_id__sigma_preyspeednovice_Intercept",
+       "sd_predator_id__sigma_preyspeedinterm_Intercept",
+       "sd_predator_id__sigma_preyspeedadvanced_Intercept"
+   )
+   := lapply(.SD, function(x) {exp(x)}),
+   .SDcols = c(
+      "sd_predator_id__sigma_speednovice_Intercept",
+      "sd_predator_id__sigma_speedinterm_Intercept",
+      "sd_predator_id__sigma_speedadvanced_Intercept",
+      "sd_predator_id__sigma_preyspeednovice_Intercept",
+      "sd_predator_id__sigma_preyspeedinterm_Intercept",
+      "sd_predator_id__sigma_preyspeedadvanced_Intercept"
+   )
+]
+
+# Reshape the table -----------------------------------------------------------
+
+ranef_tab <- melt(
+   sd_draws,
+   variable.name = "parameter"
+)
+
+# Summarize the values (means + 95% CI) --------------------------------------
+
+# Intervals
+lower_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[1]
+}
+upper_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+# Summarize values
+ranef_tab[, ":=" (mean = mean(value),
+                  lower_ci = lower_interval(value),
+                  upper_ci = upper_interval(value)),
+          by = .(parameter)]
+
+ranef_tab <- unique(ranef_tab[, .(parameter, mean, lower_ci, upper_ci)])
+ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], 3)]
+
+# Rearrange the table --------------------------------------------------------
+
+# Add a column that specifies the experience level
+ranef_tab[parameter %like% "novice", xp_level := "novice"]
+ranef_tab[parameter %like% "interm", xp_level := "intermediate"]
+ranef_tab[parameter %like% "advanced", xp_level := "advanced"]
+
+# Paste upper and lower ci with estimate
+ranef_tab[, estimate := paste(format(mean, digits = 3), "(")]
+ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 3), sep = "")]
+ranef_tab[, estimate := paste(estimate, ",", sep = "")]
+ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 3), sep = " ")]
+ranef_tab[, estimate := paste(estimate, ")", sep = "")]
+ranef_tab[, c("mean", "lower_ci", "upper_ci") := NULL]
+
+# Parameter column
+ranef_tab[
+   , parameter1 := ifelse(
+       parameter %like% "predator_id__sigma",
+       "predator ID (sigma)",
+       "predator ID (mean)"
+   )
+]
+ranef_tab[parameter %like% "avatar", parameter1 := "avatar (mean)"]
+ranef_tab[parameter %like% "env", parameter1 := "environment (mean)"]
+
+# Trait column
+ranef_tab[
+   , trait := ifelse(
+       parameter %like% "preyspeed",
+       "prey speed",
+       "predator speed"
+   )
+]
+ranef_tab[parameter %like% "success", trait := "hunting success"]
+
+# Remove old parameter column and replace by new
+ranef_tab[, parameter := NULL]
+setnames(ranef_tab, "parameter1", "parameter")
+
+# Reshape
+ranef_tab <- dcast(
+   ranef_tab,
+   trait + parameter ~ xp_level,
+   value.var = "estimate"
+)
+
+# Reorder columns
+ranef_tab <- ranef_tab[, c(1, 2, 5, 4, 3)]
+
+# Reorder rows
+table <- ranef_tab[c(1:5, 6:9)]
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 3. Create the table using flextable
+# ===========================================================================
+
+# Prepare the table parameters ----------------------------------------------
+
+# Custom header
+my_header <- data.frame(
+  col_keys = c("trait", "parameter",
+               "novice", "intermediate", "advanced"),
+  line1 = c("Trait",
+            "Parameter",
+            "Novice",
+            "Intermediate",
+            "Advanced"),
+  stringsAsFactors = FALSE
+)
+
+# Custom theme
+my_theme <- function(x, ...) {
+  x <- colformat_double(x, big.mark = " ",
+                        decimal.mark = ".",
+                        digits = 3)
+  x <- set_table_properties(x, layout = "fixed")
+  x <- border_remove(x)
+  std_border <- fp_border(width = 1, color = "black")
+  x <- hline_top(x, part = "all", border = std_border)
+  x <- hline_bottom(x, part = "all", border = std_border)
+  autofit(x)
+}
+
+# Create the table ----------------------------------------------------------
+
+tab3 <-
+
+  # table structure
+  table %>%
+  select(trait, parameter,
+         novice, intermediate, advanced) %>%
+  flextable(col_keys = my_header$col_keys) %>%
+  set_header_df(mapping = my_header, key = "col_keys") %>%
+  my_theme() %>%
+
+  # Align repeated rows on column 1
+  merge_v(j = 1) %>%
+  valign(j = 1, valign = "top", part = "body") %>%
+  # font
+  fontsize(size = 10, part = "all") %>%
+  font(fontname = "Times New Roman", part = "all") %>%
+
+  # Align text
+  align(align = "left", part = "all", j = 1) %>%
+  align(align = "left", part = "all", j = 2) %>%
+  align(align = "center", part = "all", j = 3) %>%
+  align(align = "center", part = "all", j = 4) %>%
+  align(align = "center", part = "all", j = 5)
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 4. Customize and print the table
+# ===========================================================================
+
+# Autofit to window
 tab3 <- autofit(tab3)
 
+# Add footnote
 tab3 <- tab3 %>%
@@
 
+# Add table caption
 set_caption(
@@
 
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure2.png"))
+knitr::include_graphics(
+  here::here("outputs", "05_outputs_figures", "05_figure2.png")
+)
 
@@
 
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure3.png"))
-
+knitr::include_graphics(
+  here::here("outputs", "05_outputs_figures", "05_figure3.png")
+)
 ```

### 2023-04-18 code/05_code_tables/05_table1.R
deleted table files. now embedded within MS

@@ -1,106 +1,0 @@
-
-# ===========================================================================
-
-#                         Code to produce Table 1                           #
-
-# ===========================================================================
-
-
-
-
-
-# ===========================================================================
-# 1. Load libraries and import table
-# ===========================================================================
-
-# Load libraries
-library(data.table)
-library(flextable)
-library(officer)
-library(dplyr)
-
- # Open the files
- path <- file.path(getwd(), "outputs", "03_outputs_model-validation")
- loo_tab <- data.table(readRDS(file.path(path, "03A_lootable.rds")))
- 
- # Add model column
- loo_tab[, model := c("Group-level smoothers only",
-                      "Global smoother + group-level smoothers",
-                      "Global smoother only")]
- 
- # Reorder columns
- loo_tab <- loo_tab[, c(9, 1:8)]
-
-# ===========================================================================
- # ===========================================================================
- 
- 
- 
- 
- 
- # ===========================================================================
- # 3. Compute the table using flextable
- # ===========================================================================
- 
- # Prepare the table parameters ----------------------------------------------
- 
- # Custom header
- my_header <- data.frame(
-    col_keys = c("model",
-                 "elpd_diff",
-                 "se_diff",
-                 "elpd_loo",
-                 "se_elpd_loo"),
-    line1 = c("model",
-              "elpd \ndifference",
-              "sd \ndifference",
-              "elpd loo \nvalue",
-              "elpd loo \nstandard error"),
-    stringsAsFactors = FALSE
- )
- 
- # Custom theme
- my_theme <- function(x, ...) {
-    x <- colformat_double(x, big.mark = " ", 
-                          decimal.mark = ".",
-                          digits = 2)
-    x <- set_table_properties(x, layout = "fixed")
-    x <- border_remove(x)
-    std_border <- fp_border(width = 1, color = "black")
-    x <- hline_top(x, part = "all", border = std_border)
-    x <- hline_bottom(x, part = "all", border = std_border)
-    autofit(x)
- }
- 
- 
- 
- # Create the table ----------------------------------------------------------
- 
- loo_table <- loo_tab %>%
-    select(model, elpd_diff, se_diff, elpd_loo, se_elpd_loo) %>%
-    flextable(col_keys = my_header$col_keys) %>%
-    set_header_df(mapping = my_header, key = "col_keys") %>%
-    my_theme() %>%
[…]

### 2023-04-18 code/05_code_tables/05_table2.R

@@ -1,210 +1,0 @@
-# ===========================================================================
-
-#                         Code to produce Table 2                           #
-
-# ===========================================================================
-
-
-
-
-
-# ===========================================================================
-# 1. Load libraries and import the model fit
-# ===========================================================================
-
-
- # Load libraries
- library(data.table)
- library(flextable)
- library(officer)
- library(dplyr)
- library(brms)
-
- # path
- path <- file.path(getwd(), "outputs")
-  
- # Import the model
- fit <- readRDS(
-   file.path(path, "02_outputs_models", "02B_DHMLM.rds")
- )
-
-# ===========================================================================
-# ===========================================================================
-
-
-
-
-
-# ===========================================================================
-# 2. Fixed effects table
-# ===========================================================================
-
-
-# Prepare the table ---------------------------------------------------------
-
- # Extract the fixed effects from the model
- eff_tab <- data.table(fixef(fit), keep.rownames = T)
- eff_tab <- eff_tab[, c(1, 2, 4:5)]
-
- # Rename variables
- setnames(
-   eff_tab, 
-   c("rn", "Q2.5", "Q97.5"), 
-   c("parameter", "lower_ci", "upper_ci")
- )
-
- # Add a column that specifies the experience level
- eff_tab[parameter %like% "novice", xp_level := "novice"]
- eff_tab[parameter %like% "interm", xp_level := "intermediate"]
- eff_tab[parameter %like% "advanced", xp_level := "advanced"]
- 
- # Back transform success
- eff_tab[
-   parameter %like% "success", 
-   c(2:4) := lapply(.SD, function (x) {plogis(x)}),
-   .SDcols = c(2:4)
- ]
- 
- # Back transform sigma
- eff_tab[
-   parameter %like% "sigma", 
-   c(2:4) := lapply(.SD, function (x) {exp(x)}),
-   .SDcols = c(2:4)
- ]
- 
- # Round values to 3 digits
- eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 3)]
-
-
-
-# Reorganize the table ------------------------------------------------------
- 
- # reorder columns, and then rows based on xp level
- eff_tab <- eff_tab[, c(5, 1:4)]
- setorder(
-   eff_tab, 
-   cols = -"xp_level"
- )
- 
- # Create trait column
- eff_tab[
[…]

### 2023-04-18 code/05_code_tables/05_table3.R

@@ -1,235 +1,0 @@
-# ===========================================================================
-
-#                         Code to produce Table 3                           #
-
-# ===========================================================================
-
-
-
-
-
-# ===========================================================================
-# 1. Load libraries and import the model fit
-# ===========================================================================
-
-
- # Load libraries
- library(data.table)
- library(flextable)
- library(officer)
- library(dplyr)
- library(brms)
-
- # path
- path <- file.path(getwd(), "outputs")
-  
- # Import the model
- fit <- readRDS(
-   file.path(path, "02_outputs_models", "02B_DHMLM.rds")
- )
-
-# ===========================================================================
-# ===========================================================================
-
-
-
-
-
-# ===========================================================================
-# 2. Random effects table
-# ===========================================================================
-
-
-# Prepare data --------------------------------------------------------------
- 
- # Extract the random effect variances
- sd_draws <- data.table(
-    as_draws_df(
-       fit, variable = "^sd_", regex = TRUE
-    )
- )
- 
- sd_draws[, c(28:30) := NULL]
-
-
-
-# Calculate parameters -------------------------------------------------------
- 
- # Take the exponent of sigma parameters
- sd_draws[
-    , c("sd_predator_id__sigma_speednovice_Intercept",
-        "sd_predator_id__sigma_speedinterm_Intercept",
-        "sd_predator_id__sigma_speedadvanced_Intercept",
-        "sd_predator_id__sigma_preyspeednovice_Intercept",
-        "sd_predator_id__sigma_preyspeedinterm_Intercept",
-        "sd_predator_id__sigma_preyspeedadvanced_Intercept"
-    ) 
-    := lapply(.SD, function (x) {exp(x)}),
-    .SDcols = c(
-       "sd_predator_id__sigma_speednovice_Intercept",
-       "sd_predator_id__sigma_speedinterm_Intercept",
-       "sd_predator_id__sigma_speedadvanced_Intercept",
-       "sd_predator_id__sigma_preyspeednovice_Intercept",
-       "sd_predator_id__sigma_preyspeedinterm_Intercept",
-       "sd_predator_id__sigma_preyspeedadvanced_Intercept"
-    )
- ]
-
-
-
[…]

### 2023-04-18 manuscript/Chapter2-manuscript.Rmd
Minor updates to text. added acknowledgements

@@
 We recently demonstrated with behavioural data from an online predator-prey videogame, called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge and help uncover the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
-For instance, we found that some individual predators hunt at high speeds and cover space in the environment, while others prefer to stalk and ambush their prey.
-Individuals are also flexible in the use of these tactics by switching between them across matches.
-The expression of these tactics and their success is also shaped by the speed of the prey, where faster prey are more difficult to hunt.
+For instance, we found that some individual predators hunt at high speeds, while others prefer to stalk and ambush their prey.
+Individuals also flexibly switch between these tactics, and their success is shaped by the speed of the prey, where faster prey are more difficult to capture.
 The prey need to forage for resources while paying attention to the predator to avoid being detected and chased.
-Some prey contribute to the group's success by healing or helping others escape the predator, while others play alone and attempt to escape by themselves [@Cere.etal2021].
-Predators must learn how the prey behave and then decide how best to capture them.
+The prey can contribute to the group's success by healing or helping others escape the predator, or be selfish and attempt to escape by themselves [@Cere.etal2021].
+Predators must learn how the prey behave and decide how best to capture them.
 Thus, *DBD* simulates a highly dynamic system where both predators and prey must adjust to each other, suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
@@
 Virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game under realistic ecological scenarios.
-Hence, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with their potential fitness consequences.
+Hence, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization and performance.
 
@@
 Together, our observations suggest that predators in *DBD* learn to adjust their hunting tactic to the behaviour of the prey that they encounter throughout their lifetime in the game.
-The resulting reciprocal behavioural escalation between the predators and the prey suggests that learning may be a catalyst for arms races [@Agrawal2001;@Kishida.etal2006;@Mougi.Kishida2009;@Mougi.etal2011].
 
@@
 
-Empirical research in humans and animals shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
-However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data includes repeated measures of individual success through time.
-Our analyses revealed that there was no population increase in expertise over time; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition (Figure 1, Appendix S1: Figure S1A-S1B).
+Empirical research shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
+However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data has repeated measures of individual success through time.
+Our analyses revealed that there was no population increase in expertise over time.
+As we mentioned before, the matchmaking pairs players using a rank-based system, and this result may thus be due to predators being paired with prey of similar skills.
+However, if this was solely due to the ranking system, we would have found a similar flat relationship for every predator.
+Instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition (Figure 1, Appendix S1: Figure S1A-S1B).
+
 We predicted that this would occur if, by chance, predators differed in the prey that they encountered, because some may be easier and others more difficult to capture.
 In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-In *DBD* we previously showed that faster speed and space coverage is an effective antipredator strategy used by the prey making them more difficult to capture [@FraserFranco.etal2022].
-Other studies have also found that faster escapes are effective to escape predation [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
-Yet, despite that predators differed in the prey that they encountered, prey speed did not shape individual differences in expertise acquisition.
-It is however possible that other antipredator tactics mediated these individual responses.
+In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
+Yet, prey speed did not shape individual differences in expertise acquisition, but other antipredator tactics may be involved.
 For example, it is well known in *DBD* that some prey groups use mobbing to confuse the predator or prevent it from capturing an injured individual.
@@
 While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
-Moreover, the predators in *DBD* may have differed in their ability to detect prey.
+Moreover, the predators may have differed in their ability to detect prey.
 For example, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
@@
 However, in an arms-race, faster predators would have successfully preyed upon faster and slower prey and would have obtained higher success than slower predators [@Mougi.etal2011], which was not the case in the present study.
-A more likely interaction scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible preyed upon different prey but achieved equal success.
+A more likely scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible preyed upon different prey but achieved equal success.
 Thus predators in *DBD* appear to optimize their success by learning to match their tactic to their prey with experience, suggesting that learning through reciprocal interactions may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
@@
 The interactions of predator and prey traits are probably the most important processes involved in population cycles and should occur when predators match their phenotype to their prey [@abramsEvolutionPredatorPreyInteractions2000].
-Yet, its has remained largely unknown whether this trait-matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
+Yet, it has remained largely unknown whether this trait-matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
 By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise.
 With experience, half of the predator population changed their behaviour by developping either a specialized or flexible tactic that was matched to the speed of their prey.
-Our results could be useful to guide predator-prey models of trait-matching, which are often studied at evolutionary timescales.
-For instance, future studies could incorporate individual variation in experience in their models to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility.
-Lastly, virtual systems are increasingly recognized among ecologists as effective systems to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
+Our results have potential applications for predator-prey models of trait-matching.
+For instance, future studies could incorporate individual variation in experience or learning in their models to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility.
+Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
 We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
@@
 
-...
+We warmly thank Behaviour Interactive Inc.
+for our collaboration which helps in advancing predator-prey science.
+We thank Julien Céré who smoothly managed the communication between us and the company, and Marine Dupuy who helped us prepare the data used in this study.
+We thank Alastair J.
+Wilson for insightful comments on the results.
+We also thank all members of Pierre-Olivier Montiglio's laboratory who provided useful feedback on earlier versions on this work.
+This work was supported by an NSERC postgraduate doctoral scholarship (569716-2022).
 

### 2023-04-19 code/02_code_models/02B_DHMLM.R
clean MV code

@@ -153,34 +153,34 @@ data[, ":=" (speed_novice        = ifelse(xp_level == "novice", pred_speed, NA),
 speed_novice <- bf(
   speed_novice | subset(sub1) ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id) +
+      (1 | a | predator_id) +
       (1 | environment_id) +
       (1 | avatar_id),
-  sigma ~  
+  sigma ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id)
+      (1 | a | predator_id)
 ) + gaussian()
 
 speed_intermediate <- bf(
   speed_interm | subset(sub2) ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id) +
+      (1 | a | predator_id) +
       (1 | environment_id) +
       (1 | avatar_id),
-  sigma ~  
+  sigma ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id)
+      (1 | a | predator_id)
 ) + gaussian()
 
 speed_advanced <- bf(
   speed_advanced | subset(sub3) ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id) +
+      (1 | a | predator_id) +
       (1 | environment_id) +
       (1 | avatar_id),
-  sigma ~  
+  sigma ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id)
+      (1 | a | predator_id)
 ) + gaussian()
 
 
@@ -190,34 +190,34 @@ speed_advanced <- bf(
 prey_speed_novice <- bf(
   prey_speed_novice | subset(sub1) ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id) +
+      (1 | a | predator_id) +
       (1 | environment_id) +
       (1 | avatar_id),
-  sigma ~  
+  sigma ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id)
+      (1 | a | predator_id)
 ) + gaussian()
 
 prey_speed_intermediate <- bf(
   prey_speed_interm | subset(sub2) ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id) +
+      (1 | a | predator_id) +
       (1 | environment_id) +
       (1 | avatar_id),
-  sigma ~ 
+  sigma ~
       1 + sqrt_prey_avg_rank +
-      (1 |a| predator_id)
[…]

### 2023-04-19 manuscript/Chapter2-manuscript.Rmd
apply some of Fran's comments in MS

@@
 It may also be costly to attempt different hunting tactics by trial and error when prey are scarce or highly unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
-An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset through extensive practive, as individuals gain experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
+Alternatively, the costs/risks faced by hunters when switching foraging tactics may be offset through extensive practive, as individuals gain experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
-However, predators can differ in the challenges that they face during their lifetime, which could result in both mechanisms operating at the same time within a predator population.
+However, predators can differ in the challenges that they face during their lifetime, which could result in both processes (i.e.
+specialization and flexibility) operating at the same time within a predator population.
 For instance, some individuals may constantly encounter faster prey, which are proven to be more difficult to hunt in simulation and empirical studies [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
@@
 This may in part be due to the limited information we have on the ecological contexts favouring specialization over flexibility in nature.
-However, in predator-prey systems, many studies have outlined that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
+However, in predator-prey systems, many studies have outlined that fluctuations in the predictability of resources throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
 The resource-predictability (or resource-heterogeneity) hypothesis argues that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
@@
 We hypothesize that predators should differ in the development of their expertise, partly because they encounter varying levels of difficulty with the prey that they pursue.
-For example, a predator may face greater difficulty than other individuals if it more often encountered prey that were elusive.
+For example, a predator may face greater difficulty than other individuals if it more often encountered groups of prey that were elusive.
 Second, we test the hypothesis that experience will shape foraging specialization.
@@
 Alternatively, if experience enables the refinement of the hunting tactics, then the predator population may instead specialize.
-Otherwise, if both mechanisms operate at the same time, then we should see no change with experience at the population level, but differences in specialization among individuals should increase.
-Third, we evaluate how predator foraging specialization emerges from behavioural interactions with prey.
+Otherwise, if both processes operate at the same time, then we should see no change with experience at the population level, but differences in specialization among individuals should increase.
+Third, we evaluate how predator foraging specialization emerges from behavioural interactions with the prey.
 Whether predators specialize or not with experience should depend on the behaviour of their prey.
-We expect that predators that experienced more predictable encounters with their prey will specialize, while predators that experienced unpredictable encounters with their prey should adopt a flexible hunting strategy.
-If we detect such prey-dependent fine-tuning, then specialist and flexible hunters should attain equal success.
+We expect predators that experienced more predictable encounters with their prey to specialize, while predators that experienced unpredictable encounters with their prey should adopt a flexible hunting strategy.
+If we detect such prey-dependent fine-tuning, then specialist and flexible hunters should attain equal success because both should have learned to optimize their hunting style to their prey.
 
@@
 Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game as it is supposed to be played.
-We then sampled players that played 300 matches or more.
-To optimize the representation of gameplay experience at advanced levels, we set the maximum number of matches at 500 for these players.
-For instance, there could be a large difference in gameplay between 300-500 and 500-1000 matches.
-Players that played more than 500 matches represented ~2% of the population.
+We then sampled players that played 300 matches or more, and monitored all their matches from the first to a maximum of 500 matches.
 
@@
 Thus, predators in *DBD* were probably exploring and refining different tactics at this stage of experience.
-Within the population, individuals became increasingly distinct in their tactics as well as in their specialization with experience, which was related to the degree of variability in prey encounters.
+Within the population, differences in individual foraging specialization among predators increased with experience, which was related to the degree of variability in prey encounters.
 Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy.
@@
 However, in an arms-race, faster predators would have successfully preyed upon faster and slower prey and would have obtained higher success than slower predators [@Mougi.etal2011], which was not the case in the present study.
-A more likely scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible preyed upon different prey but achieved equal success.
+A more likely scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible preyed upon different prey, but they both achieved equal success.
 Thus predators in *DBD* appear to optimize their success by learning to match their tactic to their prey with experience, suggesting that learning through reciprocal interactions may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
@@
 With experience, half of the predator population changed their behaviour by developping either a specialized or flexible tactic that was matched to the speed of their prey.
+Overall, both type of hunters achieved equal hunting success.
 Our results have potential applications for predator-prey models of trait-matching.

### 2023-04-23 manuscript/Chapter2-SupInfo.Rmd
update supmat added tables for bias test

@@
 library(tidyr)
+
+```
+
+\newpage
+
+```{r tableprep, include = FALSE}
+
+# ===========================================================================
+# 1. Extract the fixed effects from the MV model
+# ===========================================================================
+
+# Prepare the table ---------------------------------------------------------
+
+# Model fit
+fit <- readRDS(
+  here::here("outputs", "02_outputs_models", "02B2_DHMLM.rds")
+)
+
+# Fixed effects table
+results <- data.table(
+  round(summary(fit)$fixed, digits = 3)[, 1:4],
+  keep.rownames = TRUE
+)
+
+setnames(results, "rn", "parameter")
+
+results[parameter %like% "predspeed", trait := "predator speed"][
+  parameter %like% "preyavgspeed", trait := "prey speed"][
+    parameter %like% "success", trait := "hunting success"
+  ]
+
+# mu parameters table
+tabs1 <- results[
+    !(parameter %like% "sigma"),
+    c(6, 1, 2, 4, 5)
+]
+
+# sigma parameters table
+tabs2 <- results[
+    parameter %like% "sigma",
+    c(6, 1, 2, 4, 5)
+]
+
+# Rename parameter values ---------------------------------------------------
+
+# Rename
+tabs1[,
+  parameter := c(
+    rep(
+      c("prey rank",
+        "cumulative experience",
+        "group 1",
+        "group 4",
+        "group 2",
+        "group 3"),
+      2
+    ),
+      c("game duration",
+        "cumulative experience",
+        "group 1",
+        "group 4",
+        "group 2",
+        "group 3")
+  )
+]
+# Reorder rows
+tabs1 <- tabs1[
+  c(1:3, 5, 6, 4,
+    7:9, 11, 12, 10,
+    13:15, 17, 18, 16)
+]
+
+# Rename
+tabs2[,
+  parameter := rep(
+    c("prey rank",
+      "cumulative experience",
+      "group 1",
+      "group 4",
+      "group 2",
+      "group 3"),
+    2
+  )
+]
+
+# Reorder
+tabs2 <- tabs2[
+  c(1:3, 5, 6, 4,
+    7:9, 11, 12, 10)
+]
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 2. Compute the table using flextable
+# ===========================================================================
+
+# Prepare the table parameters ----------------------------------------------
+
+# Custom header
+my_header <- data.frame(
+   col_keys = c("trait",
+                "parameter",
+                "Estimate",
+                "l-95% CI",
+                "u-95% CI"),
+   line1 = c("Trait",
+             "Parameter",
+             "Value",
+             "lower 95% CI",
+             "upper 95% CI"),
+   stringsAsFactors = FALSE
+)
+
+# Custom theme
+my_theme <- function(x, ...) {
+   x <- colformat_double(x, big.mark = " ",
+                         decimal.mark = ".",
+                         digits = 2)
+   x <- set_table_properties(x, layout = "fixed")
+   x <- border_remove(x)
+   std_border <- fp_border(width = 1, color = "black")
+   x <- hline_top(x, part = "all", border = std_border)
+   x <- hline_bottom(x, part = "all", border = std_border)
+   autofit(x)
+}
+
+```
+
+```{r tables1, ft.align = "left"}
+# Create the table ----------------------------------------------------------
+
+tabs1f <- tabs1 %>%
+  flextable(col_keys = my_header$col_keys) %>%
+  set_header_df(mapping = my_header, key = "col_keys") %>%
+  my_theme() %>%
+  merge_v(j = 1) %>%
+  valign(j = 1, valign = "top", part = "body") %>%
+  align(align = "left", part = "all", j = c(1, 2)) %>%
+  align(align = "center", part = "all", j = 3) %>%
+  align(align = "center", part = "all", j = 4) %>%
+  align(align = "center", part = "all", j = 5) %>%
+  footnote(
+    i = 1, j = 1,
+    part = "header",
+    value = as_paragraph(
+      as_sup("a "),
+      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299"
+    ),
+    ref_symbols = " "
+  ) %>%
+  set_caption(
+    tabs1,
+    caption = "Fixed effects table on the mean part of the model",
+    style = "Table Caption"
+  ) %>%
+  fontsize(size = 10, part = "all") %>%
+  fontsize(size = 12, part = "footer") %>%
+  font(fontname = "Times New Roman", part = "all")
+
+tabs1f
+
+# ===========================================================================
+# ===========================================================================
+
+```
+
+\newpage
+
+```{r tableS2, ft.align = "left"}
+
+tabs2f <- tabs2 %>%
+  flextable(col_keys = my_header$col_keys) %>%
+  set_header_df(mapping = my_header, key = "col_keys") %>%
+  my_theme() %>%
+  merge_v(j = 1) %>%
+  valign(j = 1, valign = "top", part = "body") %>%
+  align(align = "left", part = "all", j = c(1, 2)) %>%
+  align(align = "center", part = "all", j = 3) %>%
+  align(align = "center", part = "all", j = 4) %>%
+  align(align = "center", part = "all", j = 5) %>%
+  footnote(
+    i = 1, j = 1,
+    part = "header",
+    value = as_paragraph(
+      as_sup("a "),
+      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299"
+    ),
+    ref_symbols = " "
+  ) %>%
+  set_caption(
+    tabs2,
+    caption = "Fixed effects table on the dispersion part of the model",
+    style = "Table Caption"
+  ) %>%
+  fontsize(size = 10, part = "all") %>%
+  fontsize(size = 12, part = "footer") %>%
+  font(fontname = "Times New Roman", part = "all")
+
+tabs2f
 

### 2023-04-25 code/04_code_figures/figureS3.R
update appendix1 fig s3

@@ -1,275 +1,243 @@
-# ===========================================================================
+# =======================================================================
 
-#                        Code to produce Figure S3                          #
+#                       Code to produce Figure S3                       #
 
-# ===========================================================================
-
-
+# =======================================================================
 
 
 
-# ===========================================================================
-# 1. Load libraries and import the model fit
-# ===========================================================================
 
+
+# =======================================================================
+# 1. Load libraries and import model
+# =======================================================================
 
 # Load libraries
-library(data.table)
-library(flextable)
-library(officer)
-library(dplyr)
 library(brms)
+library(ggplot2)
+library(viridis)
 
-# path
-path <- file.path(getwd(), "outputs")
+path <- file.path(getwd(), "outputs", "01_outputs_models")
+fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
 
-# Import the model
-fit <- readRDS(
-  file.path(path, "02_outputs_models", "02B_DHMLM.rds")
-)
-
-# Import the CV table
-cv <- readRDS(
-  file.path(path, "04_outputs_model-processing", "04_CV-table.rds")
-)
-
-# ===========================================================================
-# ===========================================================================
+# =======================================================================
+# =======================================================================
 
 
 
 
 
-# ===========================================================================
-# 1. ICC table
-# ===========================================================================
+# =======================================================================
+# 2. Estimate differences between experience levels
+# =======================================================================
+
+# a -> Compare novices vs intermediate
[…]

### 2023-04-25 code/04_code_figures/figureS4.R
old code figs4 now figs3

@@ -1,243 +1,0 @@
-# =======================================================================
-
-#                       Code to produce Figure S3                       #
-
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 1. Load libraries and import model
-# =======================================================================
-
-# Load libraries
-library(brms)
-library(ggplot2)
-library(viridis)
-
-path <- file.path(getwd(), "outputs", "02_outputs_models")
-fit <- readRDS(file.path(path, "02B_DHMLM.rds"))
-
-# =======================================================================
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 2. Estimate differences between experience levels
-# =======================================================================
-
-# a -> Compare novices vs intermediate
-# b -> Compare intermediate with advanced
-# c-> Compare novices with advanced
-
-
-# Do predators become increasingly flexible? ----------------------------
-
-hyp1a <- "exp(sigma_speednovice_Intercept) < exp(sigma_speedinterm_Intercept)"
-hyp1b <- "exp(sigma_speedinterm_Intercept) > exp(sigma_speedadvanced_Intercept)"
-hyp1c <- "exp(sigma_speednovice_Intercept) > exp(sigma_speedadvanced_Intercept)"
-hyp1 <- hypothesis(x = fit, hypothesis = c(hyp1a, hyp1b, hyp1c))
-
-
-
-# Does individual variation in avg speed change with XP? ----------------
-
-hyp2a <- "exp(predator_id__speednovice_Intercept) > exp(predator_id__speedinterm_Intercept)"
-hyp2b <- "exp(predator_id__speedinterm_Intercept) < exp(predator_id__speedadvanced_Intercept)"
-hyp2c <- "exp(predator_id__speednovice_Intercept) < exp(predator_id__speedadvanced_Intercept)"
-hyp2 <- hypothesis(x = fit, hypothesis = c(hyp2a, hyp2b, hyp2c), class = "sd")
-
-
-
-# Does individual variation in speed var. change with XP? ---------------
-
-hyp3a <- "exp(predator_id__sigma_speednovice_Intercept) < exp(predator_id__sigma_speedinterm_Intercept)"
[…]

### 2023-04-25 manuscript/Chapter2-appendix1.Rmd
update appendix1

--- 2023-04-23 manuscript/Chapter2-SupInfo.Rmd
@@
 title: |
-     Online supporting information for \
-     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame
+     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame: \
+     Appendix 1
 
@@
 fit <- readRDS(
-  here::here("outputs", "02_outputs_models", "02B2_DHMLM.rds")
+  here::here("outputs", "01_outputs_models", "B2_DHMLM.rds")
 )
@@
 
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS1.png"))
+knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS1.png"))
 
@@
 
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS2.png"))
+knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS2.png"))
 
@@
 
-```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
+```{r figS3, out.width = "100%", fig.cap = "**Figure S3.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
 The test is displayed on the y axis (i.e.
@@
 
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS4.png"))
+knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS3.png"))
 

### 2023-04-25 code/04_code_figures/figureS1-S2.R

@@ -21,10 +21,10 @@ library(ggplot2)
 library(ggridges)
 library(ggpubr)
 
-path <- file.path(getwd(), "outputs", "02_outputs_models")
+path <- file.path(getwd(), "outputs", "01_outputs_models")
 
-fit1 <- readRDS(file.path(path, "02A3_GAMM.rds"))
-fit2 <- readRDS(file.path(path, "02B_DHMLM.rds"))
+fit1 <- readRDS(file.path(path, "A3_GAMM.rds"))
+fit2 <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
 
 
 
@@ -81,16 +81,16 @@ posterior_epred_beta_binomial2 <- function(prep) {
 
 custom_theme <- theme(
   # axis values size
-  axis.text = element_text(face = "plain", 
+  axis.text = element_text(face = "plain",
                            size = 14,
                            color = "black"),
   # axis ticks lenght
   axis.ticks.length = unit(.15, "cm"),
   # axis ticks width
-  axis.ticks = element_line(size = 0.90, 
+  axis.ticks = element_line(size = 0.90,
                             color = "black"),
   # axis titles size
-  axis.title = element_text(size = 16, 
+  axis.title = element_text(size = 16,
                             face = "plain",
                             color = "black"),
   axis.line = element_line(size = 0.95,
@@ -197,8 +197,8 @@ tab1 <- data.table(tab1)
 
 # Calculate 1st and final value
 tab1[, ":=" (
-  first = min(Zcumul_xp), 
-  last = max(Zcumul_xp)), 
+  first = min(Zcumul_xp),
+  last = max(Zcumul_xp)),
   by = predator_id]
 
 tab1[, equal1 := ifelse(Zcumul_xp == first, 1, 0), by = predator_id]
@@ -219,8 +219,8 @@ tab2 <- dcast(
 tab2[, difference := max - min]
 
 table <- merge(
-  tab1[, .(predator_id, Zcumul_xp, estimate__)], 
-  tab2[, .(predator_id, difference)], 
+  tab1[, .(predator_id, Zcumul_xp, estimate__)],
+  tab2[, .(predator_id, difference)],
   by = "predator_id"
 )
 
@@ -232,7 +232,11 @@ table <- unique(
   ]
 )
 draws <- draws[, .(predator_id, xp_level, exp_speed_sigma, average_speed_sigma)]
[…]

### 2023-04-25 manuscript/Chapter2-appendix3.Rmd
prepared appendix1 file

--- 2023-04-18 manuscript/Chapter2-manuscript.Rmd
@@
 ---
-title: "Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame"
+title: |
+     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame: \
+    Appendix 3
 output: 
@@
     fig_caption: yes
-bibliography: references2.bib
+bibliography: references.bib
 csl: ecology.csl
@@
 library(officer)
-library(dplyr)
+library(tidyr)
 
@@
 
-```{r}
+\newpage
 
-path <- file.path(here::here(), "data")
-
-dat <- fread(
-  file.path(path, "FraserFrancoetal2023-data.csv"),
-  select = c("timestamp", "match_id", "realm_id",
-             "environment_id", "avatar_id", "predator_id",
-             "game_duration", "total_xp_pred", "cumul_xp_pred",
-             "hunting_success", "pred_speed", "prey_avg_speed"))
-
-dat[, c(2:6) := lapply(.SD, function(x) as.factor(x)), .SDcols = c(2:6)]
-
-# To have a date column
-dat[, date := as.POSIXct(sub(" .*", "", timestamp))]
-
-```
-
-Journal name : Ecology
-
-Manuscript type : article
-
-Authors : Maxime Fraser Franco^1^, Francesca Santostefano^1,2^, Julien G. A. Martin^3^, Clint D. Kelly^1^, Pierre-Olivier Montiglio^1^
-
-Affiliations : ^1^ Département des Sciences Biologiques, Université du Québec à Montréal, Montréal, QC, Canada.
-^2^ Centre for Ecology and Conservation, Penryn Campus, University of Exeter, Cornwall, United Kingdom.
-^3^ Department of Biology, University of Ottawa, Ottawa, ON, Canada.
-
-Corresponding author : fraser_franco.maxime@courrier.uqam.ca
-
-Authorship statement : With MFF as the leader, all authors participated in conceiving the ideas behind the study.
-MFF prepared the data, conducted the analyses, and wrote the manuscript with input from all coauthors.
-All authors reviewed and accepted the final version of the manuscript.
-
-Open research statement : The data and code used to produce the results in this manuscript are freely available on GitHub https://github.com/quantitative-ecologist/experience-hunting-tactics
-
-Keywords: foraging behaviour, arms race, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology
-
-\newpage
-# ABSTRACT {.unnumbered}
-
-\newpage
-# INTRODUCTION {.unnumbered}
-
-Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or on different resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@Kernaleguen.etal2015;@Phillips.etal2017].
-A growing body of evidence suggests that ecological interactions such as predator-prey interactions can drive this individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
-When they hunt, predators often use techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
-experience).
-While hunting experience may be essential to maintain or improve foraging success, we have few empirical assessments of its role in predator foraging specialization [@Dukas2019] and its consequences on predator-prey interactions.
-
-The development of foraging tactics is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
-Theory predicts that foraging specialization may emerge via learning, limitations in memorizing multiple complex hunting skills, and expertise [@Tinker.etal2009;@Dukas2019].
-@Dukas2019 defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
-It is described as the relationship between success and cumulative experience, where extensive practice optimizes success when individuals reach an advanced level of experience.
-Empirical studies on human and non-human hunters show that experience optimizes the efficiency (e.g.
-search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
-This body of work suggests that such optimization may thus promote individual foraging specialization (e.g.
-repeatedly using fast attacks) if the success of a hunting tactic is constant each time a prey is encountered.
-It may also be costly to attempt different hunting tactics by trial and error when prey are scarce or highly unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
-An alternative mechanism is that the costs/risks faced by hunters when switching foraging tactics may be offset through extensive practive, as individuals gain experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
-To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
-However, predators can differ in the challenges that they face during their lifetime, which could result in both mechanisms operating at the same time within a predator population.
-For instance, some individuals may constantly encounter faster prey, which are proven to be more difficult to hunt in simulation and empirical studies [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-Thus, whether predators specialize or increase their flexibility with experience, learning to adjust their tactic to their prey should be essential to optimize their success.
-
-There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging [@Phillips.etal2017].
-This is reflected in the literature showing contrasting results in the links between specialization and fitness.
-For instance, some studies report increasing benefits of specialization [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
-This may in part be due to the limited information we have on the ecological contexts favouring specialization over flexibility in nature.
-However, in predator-prey systems, many studies have outlined that fluctuations in the predictability of prey encounters throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
-The resource-predictability (or resource-heterogeneity) hypothesis argues that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
-In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-When predator-prey interactions are directly observed, empirical evidence shows that predators often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
-Yet, a recurring question that emerges from these studies is whether and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011].
-Thus, uncovering the role of learning in predator-prey systems where interactions are directly monitored would enable researchers to better predict the behavioural decisions and the success of predators when they are hunting.
-
-The integration of individual behavioural variation in the study of predator-prey interactions has gained traction in recent years, with empirical studies revealing important consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
-However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
-We recently demonstrated with behavioural data from an online predator-prey videogame, called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge and help uncover the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
-For instance, we found that some individual predators hunt at high speeds and cover space in the environment, while others prefer to stalk and ambush their prey.
-Individuals are also flexible in the use of these tactics by switching between them across matches.
-The expression of these tactics and their success is also shaped by the speed of the prey, where faster prey are more difficult to hunt.
-The prey need to forage for resources while paying attention to the predator to avoid being detected and chased.
-Some prey contribute to the group's success by healing or helping others escape the predator, while others play alone and attempt to escape by themselves [@Cere.etal2021].
-Predators must learn how the prey behave and then decide how best to capture them.
-Thus, *DBD* simulates a highly dynamic system where both predators and prey must adjust to each other, suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
-Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
-in prep).
-Virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game under realistic ecological scenarios.
-Hence, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization along with their potential fitness consequences.
-
-In this study, we test how hunting experience shapes predator foraging specialization using individual behavioural data from players in the online videogame *Dead by Daylight*.
-*DBD* simulates a direct predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
-The data grants a high degree of precision on the behavioural interaction, as the behaviour of both the predator and the four prey along with the predator's success are monitored simultaneously in each trial.
-First, we investigate how predators develop their individual hunting expertise.
-We hypothesize that predators should differ in the development of their expertise, partly because they encounter varying levels of difficulty with the prey that they pursue.
-For example, a predator may face greater difficulty than other individuals if it more often encountered prey that were elusive.
-Second, we test the hypothesis that experience will shape foraging specialization.
-If experience reduces the costs of switching between hunting tactics, we predict that the predator population should become more flexible.
-Alternatively, if experience enables the refinement of the hunting tactics, then the predator population may instead specialize.
-Otherwise, if both mechanisms operate at the same time, then we should see no change with experience at the population level, but differences in specialization among individuals should increase.
-Third, we evaluate how predator foraging specialization emerges from behavioural interactions with prey.
-Whether predators specialize or not with experience should depend on the behaviour of their prey.
-We expect that predators that experienced more predictable encounters with their prey will specialize, while predators that experienced unpredictable encounters with their prey should adopt a flexible hunting strategy.
-If we detect such prey-dependent fine-tuning, then specialist and flexible hunters should attain equal success.
-
-# MATERIALS AND METHODS {.unnumbered}
-
-## Study system
-
-*DBD* is a survival asymmetric (i.e.
-a game where the gameplay  mechanics differ between two groups) multiplayer online game developed by Behaviour Interactive Inc, in which players can play either as a predator or a prey.
-The objective of the predator is to hunt and capture the four prey across a virtual environment.
-The objective of the four prey is to search for resources while avoiding the predator.
-The resources are in the form of power generators that, once all activated, will enable the prey to escape through one of two exit doors.
-The composition of the predator and prey group for a match is determined by a skill-based matchmaking algorithm.
-A match ends when the predator kills all the prey available (i.e.
-that have not escaped), or when the last remaining prey escapes the virtual environment.
-Each player, predator or prey, can choose an avatar with abilities that encourage specific play styles (e.g.
-bold vs cautious prey, or ambush vs roaming predator).
-During our study period, the game offered 23 predator avatars.
-The virtual environment where matches take place is composed of fixed and procedurally generated habitat components, such as vegetation, mazes, and buildings.
-Some of these environments are larger than others, with varying structural complexity.
-However, predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling them to have visual cues of the generators [@FraserFranco.etal2022].
-There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during our study period.
-
-## Data collection
-
-The videogame company provided data that spanned a period of 6 months of gameplay recorded for every player.
-The first recorded match was played on `r toString(format(min(dat$date)))` and the last one on `r toString(format(max(dat$date)))`.
-We cleaned and filtered the raw data to produce a dataset appropriate for our analyses.
-We analyzed only matches where players did not know each other (i.e.
-"Online" mode).
-We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero.
-Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game as it is supposed to be played.
-We then sampled players that played 300 matches or more.
-To optimize the representation of gameplay experience at advanced levels, we set the maximum number of matches at 500 for these players.
-For instance, there could be a large difference in gameplay between 300-500 and 500-1000 matches.
-Players that played more than 500 matches represented ~2% of the population.
-
-Our population consists of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(formatC(length(unique(dat$match_id)), big.mark = " "))` matches.
-The predator-players' experience varied between `r toString(format(min(dat$total_xp_pred)))` and `r toString(format(max(dat$total_xp_pred)))` matches played.
-These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)`-min (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)`-min).
-The following information is collected and reported for every match : the player's anonymous ID, its avatar (i.e.
-the predator character chosen with its specific powers-gameplay mechanics), the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.
-
-We recognize that we could have introduced a bias in our analyses since we sampled individuals who stayed in the game for at least 300 matches.
-For instance, these players may already be used to play videogames, and thus, could differ in the way they play at early stages of their experience in the game.
-To ensure that our sample was not biased, the videogame company provided a random sample of players that played between 20 and 50 matches, between 51 and 100 matches, and between 101 and 300 matches from the same timeframe as our current sample.
-We then took the first 20 matches played by these players, including those from our sampled population, and compared their average behaviour using a Bayesian hierarchical linear model.
-We found that neither of the four groups differed in their average speed (Table SX), which gives us confidence that our player population was not biased.
-
-## Variables
-
-We analyzed the predator's average speed and the average speed of the prey group encountered by the predator.
-The predator's average speed is measured as the average distance traveled per second during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
-We measured the preys' average speed as the average travel speed of the four individual prey within a match ($\overline{x}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
-We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
-Lastly, we defined the predator's cumulative experience as the number of matches played prior to the match being monitored.
-For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.
-
-## Statistical analyses
-
-### Software and computer specifications
-
-All our statistical analyses were executed on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster maintained by the Digital Research Alliance of Canada.
-The operating system for Cedar is CentOS Linux 7.
-The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
-
-### Effect of experience on hunting success
-
-We tested whether predators varied in the development of their expertise using three Bayesian generalized additive mixed models (GAMM) with thin plate regression splines.
-These models estimate the relationship between hunting success (i.e.
-number of prey captured) and the predators' cumulative experience (i.e.
-number of matches played before the current match).
-We parametrized the models following the method of @Pedersen.etal2019.
-The first model was the simplest, with a common global smoothing function for all observations and random intercepts for the predator ID.
-In this model, we assume that individuals have the same development of expertise, with the model estimating a trend for the average individual (i.e.
-global smoother).
-For the second model, we included varying group-level smoothers for the predator ID.
-In this model, we assume that individuals share a similar relationship between success and experience, but that this relationship can vary (e.g.
-individual 1 has a steeper curve than individual 2).
-This enabled us to test whether predators differed in the development of their expertise.
-In the third model, we kept the group-level smoothers for the predators, but removed the global smoother.
-This allows each individual to have a unique relationship between success and experience without penalization by the global smoother.
-Thus, this model assumes that predators do not share a common relationship between success and experience.
-We included match duration as a covariate in all three models.
-
-Because a maximum of four prey can be captured in the game, and to control for overdispersion, we computed the three models using a modified version of the beta-binomial distribution implemented in "brms".
-Thus, hunting success was estimated as the probability of capturing the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
-We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link for all models.
-
-We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
-We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$).
-We used Gaussian priors for the game duration ($N(0,\ 1)$), the intercept ($N(0,\ 0.5)$), and the precision paremeter ($N(2,\ 0.5)$).
-We employed the default Student t priors for the smoothing parameter ($t(3,\ 0,\ 2.5)$).
-After fitting the three models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
-
-### Changes in foraging behaviour and predator-prey interactions with experience
-
-We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
-We categorized the predators by their experience based on the number of matches they played (i.e.
-their cumulative experience).
-Since we monitored all predator players throughout their experience, they appeared in all of the three following experience categories.
-First, we assigned predators the status of "novice" when they had a cumulative experience below 100 matches.
-For example, a predator player that played 500 matches in total would be labelled as a novice in its first 100 matches.
-Following this logic, we labelled predators as "intermediate" hunters when they had a cumulative experience between 100 and 299 and matches.
-Lastly, we defined predators as "advanced" hunters when they had a cumulative experience equal or above 300, with a maximum of 499 cumulated matches.
-
-For each level of experience (i.e.
-novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model) and, by using a heterogeneous structure of the residuals, the intra-individual standard deviation of speed for every individual (which we call the dispersion part of the model).
-Thus, in the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e.
-along the slow-fast continuum), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization/flexibility (i.e.
-intra-individual variability).
-We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the prey groups encountered by predators.
-For the mean part of the model, it allows us to test whether individual predators differed in the average speed of the groups of prey encountered across the study.
-For the dispersion part, it allows us to test whether individual predators differed in the (dis)similarity of the groups of prey encountered across the study (i.e.
-if resource heterogeneity was higher for some individuals compared to others).
-For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean prey capture.
-For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered as proxy for prey skills on both the mean and dispersion part of the equation.
-The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank).
-We used the mean rank of the four prey and applied a square-root transformation.
-For the predator's hunting success, we controlled for the square-root of the duration of the match.
-
-We estimated the correlation between the individual random effect on the mean and on the dispersion within each trait (e.g.
-$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ pred})$) and among each trait (e.g.
-$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ prey})$) within a level of experience.
-In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible.
-In the second case, the correlations enables us to estimate, for example, whether predators that encountered prey that were faster/slower adopted a slower/faster (or more specialized/flexible) tactic, or if slower/faster predators had lower/greater hunting success.
-As a complement, the model also estimated correlations among the different levels of experience (e.g.
-$cor(\sigma_{id_{m}\ pred\ novice}\ \sigma_{id_{d}\ pred\ intermediate})$).
-The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each of three developmental stages.
-We present the character-state analyses as additional material in the Appendix S2 as they were not part of our initial objectives.
-
-The full model has the following form, with each equation repeated three times (i.e. one for each level of experience):
-
-```{r model_equations, ft.align = "left"}
-
-# Prepare equations
-eqs <- c(
-  "speed_{pred} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
-  "log(\\sigma_{e,pred}) = X_{d}\\ b_{d} + Z\\ id_{d}",
-  "speed_{prey} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
-  "log(\\sigma_{e,prey}) = X_{d}\\ b_{d} + Z\\ id_{d}",
-  "success_{pred} = X_{m}\\ b_{m} + Z\\ id_{m} + e"
-)
-eqs_num <- c(
-    "(eqn. 1.1)",
-    "(eqn. 1.2)",
-    "(eqn. 2.1)",
-    "(eqn. 2.2)",
-    "(eqn. 3)"
-)
-
-# Combine into a dataframe
-df <- data.frame(
-    formula = eqs,
-    number = eqs_num
-)
-
-# Create a table to display on Word
-ft <- flextable(df)
-
-# Transform values as a mathematical formula
-ft <- compose(
-  x = ft, j = 1,
-  value = as_paragraph(
-    as_equation(formula, height = .5)
-  )
-)
-
-# Customize table
-my_theme <- function(x, ...) {
-  x <- colformat_double(x, big.mark = " ",
-                        decimal.mark = ".",
-                        digits = 2)
-  x <- border_remove(x)
-  x <- delete_part(x, part = "header")
-  x <- align(x, j = 1, align = "left", part = "body")
-  x <- align(x, j = 2, align = "right", part = "body")
-  x <- font(x, fontname = "Times New Roman", part = "body")
-  x <- fontsize(x, size = 12, part = "body")
-  x <- width(x, j = 1, width = 10, unit = "cm")
-  x <- width(x, j = 2, width = 6.51, unit = "cm")
-}
-
-# Apply theme and print
-ft <- my_theme(x = ft)
-ft
-
-```
-
-where $env$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$.
-$b$ is the vector of fixed effects with its incidence matrix $X$.
-The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively.
-On the mean part of the model, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$ and $av \sim N(0,\ I\ \sigma_{av})$).
-$I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
-The residuals are assumed to follow a Gaussian distribution ($e \sim N(0,\ \sigma_{e})$).
-On the dispersion part of the model, the residuals vary among individuals, allowing us to estimate among individual differences in specialization.
-The individual identity random effects on both the mean and dispersion parts follow a multivariate Gaussian distribution $[\begin{array}{cc} id_m \\ id_d \end{array}] \sim MVN(0,\ \Sigma_{id})$ where $\Sigma_{id}$ is a 15x15 variance-covariance matrix.
-The parameters $\sigma_{env}$, $\sigma_{av}$, and $\sigma_{id}$, correspond to the among environment, among avatar, and among individual standard deviations, respectively.
-
-We parameterized equations 1.1 to 2.2 with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation 3 (predator hunting success).
-We used Gaussian priors for the prey rank ($N(2.5,\ 1)$) and game duration ($N(10,\ 2)$) on the mean part of the model (equations 1.1, 2.1, and 3), and the default priors in "brms" for the dispersion part (equations 1.2 and 2.2).
-We used the default Student t priors in "brms" for the intercepts on the mean and dispersion part of the model.
-For hunting success, we applied a Gaussian prior on the precision parameter ($N(2,\ 1)$).
-For every predicted variable, we applied a half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part of the model (equations 1.1, 2.1, and 3), and the default "brms" Student t prior for the dispersion part of the model (equations 1.2 and 2.2).
-
-### Markov Chain Monte Carlo settings
-
-We parametrized every model described above to run four MCMC chains with 1000 posterior samples for each parameter.
-We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table I), and 1500 iterations with a thinning set to four for the additive model with global and group-level smoothers and for the additive model with group-level smoothers only (Table I).
-We set the first 500 iterations in each model as warmups.
-We parametrized the MDHGLM to run 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups.
-We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021a].
-We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
-
-# RESULTS {.unnumbered}
-
-## Effect of experience on hunting success
-
-Our results confirm that individual predators display substantial differences in the development of their expertise, as the best model included group-level smoothers exclusively (Table I).
-For instance, some predators steadily increased (Figure 1A, Appendix S1: Figure S1A), while others decreased (Figure 1A, Appendix S1: Figure S1B), their hunting success with greater experience, and others whose success did not change with experience (Figure 1A).
-Another pattern that emerged was that some individuals optimized their success at an experience level that was below what we considered "advanced" (i.e.
->300 matches played).
-
-```{r table1, ft.align = "left"}
-
-# ===========================================================================
-# 1. Import the model fit
-# ===========================================================================
-
-# Open the loo table
-path <- file.path(here::here("outputs", "03_outputs_model-validation"))
-loo_tab <- data.table(readRDS(file.path(path, "03A_lootable.rds")))
-
-# Add model column
-loo_tab[, model := c("Group-level smoothers only",
-                     "Global smoother + group-level smoothers",
-                     "Global smoother only")]
-
-# Reorder columns
-loo_tab <- loo_tab[, c(9, 1:8)]
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 2. Compute the table using flextable
-# ===========================================================================
-
-# Prepare the table parameters ----------------------------------------------
-
-# Custom header
-my_header <- data.frame(
-   col_keys = c("model",
-                "elpd_diff",
-                "se_diff",
-                "elpd_loo",
-                "se_elpd_loo"),
-   line1 = c("model",
-             "elpd \ndifference",
-             "sd \ndifference",
-             "elpd loo \nvalue",
-             "elpd loo \nstandard error"),
-   stringsAsFactors = FALSE
-)
-
-# Custom theme
-my_theme <- function(x, ...) {
-   x <- colformat_double(x, big.mark = " ",
-                         decimal.mark = ".",
-                         digits = 2)
-   x <- set_table_properties(x, layout = "fixed")
-   x <- border_remove(x)
-   std_border <- fp_border(width = 1, color = "black")
-   x <- hline_top(x, part = "all", border = std_border)
-   x <- hline_bottom(x, part = "all", border = std_border)
-   autofit(x)
-}
-
-# Create the table ----------------------------------------------------------
-
-tab1 <- loo_tab %>%
-   select(model, elpd_diff, se_diff, elpd_loo, se_elpd_loo) %>%
-   flextable(col_keys = my_header$col_keys) %>%
-   set_header_df(mapping = my_header, key = "col_keys") %>%
-   my_theme() %>%
-   merge_v(part = "header") %>%
-   merge_h(part = "header") %>%
-   fontsize(size = 10, part = "all") %>%
-   font(fontname = "Times New Roman", part = "all") %>%
-   align(align = "left", part = "all", j = 1) %>%
-   align(align = "center", part = "all", j = 2) %>%
-   align(align = "center", part = "all", j = 3) %>%
-   align(align = "center", part = "all", j = 4) %>%
-   align(align = "center", part = "all", j = 5)
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 3. Customize and print the table
-# ===========================================================================
-
-# Autofit to window
-tab1 <- autofit(tab1)
-
-# Add a footnote
-tab1 <- tab1 %>%
-  footnote(
-    i = 1, j = 1,
-    part = "header",
-    value = as_paragraph(
-      "* 'elpd' refers to the expected log pointwise density and is the value chosen to select the best model."),
-    ref_symbols = " "
-  ) %>%
-  font(fontname = "Times New Roman", part = "all") %>%
-  fontsize(size = 11, part = "all")
-
-# Table caption
-set_caption(
-  tab1,
-  caption = "Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience",
-  style = "Table Caption"
-)
-
-# ===========================================================================
-# ===========================================================================
-
-```
-
-We predicted that the relationship between hunting success and experience would vary among predators because they should differ in the type of prey that they encounter.
-However, after controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained stable (Figure 1B).
-
-```{r fig1, out.width = "100%", fig.cap = "**Figure 1.** Among individual differences in the development of hunting expertise.
-The predators' hunting success (i.e.
-the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e.
-the number of matches played prior to each observation) is on the x axis.
-Each fitted curve represents an individual predator.
-(A) A generalized additive mixed model where we do not control for prey speed (B) A generalized additive mixed model where we control for prey speed."}
-
-knitr::include_graphics(
-  here::here("outputs", "05_outputs_figures", "05_figure1.png")
-)
-
-```
-
-## Effect of experience on the development of behavioural specialization
-
-At the population level, predators did not change their mean speed with experience (i.e.
-intercept of the mean predator speed; Table 2).
-Moreover, there was no directional increase in foraging flexibility or specialization with experience.
-Indeed, the observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e.
-intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S4), but then return to novice-levels of flexibility with advanced experience (i.e.
-intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Appendix S1: Figure S4).
-Thus, our analyses suggest that population-level behavioural specialization changes nonlinearly (quadratic) with experience rather than linearly.
-
-```{r table2, ft.align = "left"}
+```{r tableS1, ft.align = "left"}
 
@@
 fit <- readRDS(
-  file.path(path, "02_outputs_models", "02B_DHMLM.rds")
+  file.path(path, "01_outputs_models", "B1_DHMLM.rds")
 )
@@
   my_theme() %>%
+
   # Align repeated rows on column 1
@@
   valign(j = 1, valign = "top", part = "body") %>%
-  # font
-  fontsize(size = 10, part = "all") %>%
-  font(fontname = "Times New Roman", part = "all") %>%
 
@@
   align(align = "center", part = "all", j = 4) %>%
-  align(align = "center", part = "all", j = 5)
+  align(align = "center", part = "all", j = 5) %>%
 
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 4. Customize and print the table
-# ===========================================================================
-
-# Autofit to window size
-tab2 <- autofit(tab2)
-
-# Table footnote
-tab2 <- tab2 %>%
+  # Footnote
   footnote(
@@
   ) %>%
+
+  # Table caption
+  set_caption(
+    caption = "Table S1. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    style = "Table Caption"
+  ) %>%
+
+  # Font options
   font(fontname = "Times New Roman", part = "all") %>%
+  fontsize(size = 10, part = "all") %>%
+  fontsize(size = 12, part = "footer") %>%
   width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
@@
 
-# Table caption
-set_caption(
-  tab2,
-  caption = "Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
-  style = "Table Caption"
-)
+tab2
 
@@
 
-At the individual level, we detected differences in the mean movement speed among predators (i.e.
-the intercept of the mean speed for the predator ID; Table 3).
-These differences remained stable from the novice to the intermediate stages, and then increased at the advanced stage to reach a level higher than when predators were novice (Table 3 and Appendix S1: Figure S4).
-Predators displayed considerable differences in their degree of hunting specialization, and these differences increased with experience (i.e.
-the intercept of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S4).
-Thus, as individual predators gain experience, the population becomes more heterogeneous, with an assemblage of both specialist and flexible hunters.
-Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 2).
-Importantly, 12.6% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
-$\ge$0.2 change in standard deviation), 44.7% displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation), while 42.7% remained relatively stable (i.e.
-$\le$0.05 change in standard deviation).
+\newpage
 
-```{r table3, ft.align = "left"}
+```{r tableS2, ft.align = "left"}
 
@@
   align(align = "center", part = "all", j = 4) %>%
-  align(align = "center", part = "all", j = 5)
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 4. Customize and print the table
-# ===========================================================================
-
-# Autofit to window
-tab3 <- autofit(tab3)
+  align(align = "center", part = "all", j = 5) %>%
 
   # Add footnote
-tab3 <- tab3 %>%
   footnote(
@@
   ) %>%
+
+  # Add table caption
+  set_caption(
+    caption = "Table 3. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    style = "Table Caption"
+  ) %>%
+
+  # Font options
   font(fontname = "Times New Roman", part = "all") %>%
+  fontsize(size = 10, part = "all") %>%
+  fontsize(size = 12, part = "footer") %>%
   width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
@@
 
-# Add table caption
-set_caption(
-  tab3,
-  caption = "Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
-  style = "Table Caption"
-)
+tab3
 
@@
 
-As we predicted, predators differed in the mean speed of the prey that they encountered across matches.
-Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period (i.e.
-the intercept of the mean prey speed for the predator ID; Table 3).
-These differences were greater when predators reached an advanced level of hunting experience (i.e.
-the intercept of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S4).
-In addition, individuals differed in the heterogeneity of the groups of prey encountered across the study period.
-Hence, some predators encountered prey groups with similar average speeds, while others encountered prey groups with different average speeds throughout the study period (i.e.
-the intercept of sigma prey speed for the predator ID; Table 3).
-
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
-The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
-Both figure panels are ordered by ascending degree of increase in either specialization or flexibility.
-We selected the individuals displayed in the figure by first substracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles.
-Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.28 standard deviations."}
+```{r figS3, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
+The test is displayed on the y axis (i.e.
+whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis.
+Each panel represent the experience level groups that are being compared."}
 
 knitr::include_graphics(
-  here::here("outputs", "05_outputs_figures", "05_figure2.png")
+    here::here(
+        "outputs", "04_outputs_figures",
+        "appendix3_figureS1.png"
+    )
 )
@@
 ```
-
-## Relationship between behavioural specialization and prey variability
-
-At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV; Figure 3 and Appendix S2: Table S1).
-Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time.
-Predators that were on average faster (mean) also encountered groups of prey that were on average faster (mean) (Figure 3 and Appendix S2: Table S1).
-At the three experience levels, there were only weak correlations between IIV in predator speed and mean prey speed (Figure 3 and Appendix S2: Table S1).
-However, predators that encountered groups of prey with similar speeds (IIV) specialized in their hunting tactic (IIV) (Figure 3 and Appendix S2: Table S1).
-Hence, predators that encountered groups of prey with similar average speeds were more specialized, while those that encountered groups of prey with different average speeds were more flexible.
-For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Appendix S2: Table S1).
-
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Correlation matrices of the MDHGLM relating the mean and intra individual variability (IIV) in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
-Larger dark blue circles indicate stronger positive correlations (positive values on the color legend), while larger dark red circles indicate stronger negative correlations (negative values on the color legend).
-A) Correlations when predators were novice hunters.
-B) Correlations when predators were at an intermediate level of experience.
-C) Correlations when predators were advanced hunters."}
-
-knitr::include_graphics(
-  here::here("outputs", "05_outputs_figures", "05_figure3.png")
-)
-```
-
-## Hunting success of behavioural specialists vs generalists
-
-We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Appendix S2: Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Appendix S2: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
-However, novice individuals that encountered groups of prey with faster speeds were less successful (Figure 3 and Appendix S2: Table S1).
-This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Appendix S2: Table S1).
-Thus, the consequences of hunting faster prey were reduced at greater experience levels.
-
-# DISCUSSION
-
-Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
-However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-Our results show that there was no directional increase in either behavioural specialization or flexibility with experience at the population level.
-Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with prey; some specialized in fast-paced hunting, and others adopted a slower and more flexible tactic with experience.
-Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period.
-With experience, predators increasingly matched their tactic to the speed of the prey that they encountered, which simultaneously relaxed the negative consequences of encountering faster prey.
-Together, our observations suggest that predators in *DBD* learn to adjust their hunting tactic to the behaviour of the prey that they encounter throughout their lifetime in the game.
-The resulting reciprocal behavioural escalation between the predators and the prey suggests that learning may be a catalyst for arms races [@Agrawal2001;@Kishida.etal2006;@Mougi.Kishida2009;@Mougi.etal2011].
-
-## The development of expertise with hunting experience
-
-Empirical research in humans and animals shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
-However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data includes repeated measures of individual success through time.
-Our analyses revealed that there was no population increase in expertise over time; instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition (Figure 1, Appendix S1: Figure S1A-S1B).
-We predicted that this would occur if, by chance, predators differed in the prey that they encountered, because some may be easier and others more difficult to capture.
-In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-In *DBD* we previously showed that faster speed and space coverage is an effective antipredator strategy used by the prey making them more difficult to capture [@FraserFranco.etal2022].
-Other studies have also found that faster escapes are effective to escape predation [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
-Yet, despite that predators differed in the prey that they encountered, prey speed did not shape individual differences in expertise acquisition.
-It is however possible that other antipredator tactics mediated these individual responses.
-For example, it is well known in *DBD* that some prey groups use mobbing to confuse the predator or prevent it from capturing an injured individual.
-However, like natural predator-prey systems, direct predator-mobbing in *DBD* is dangerous and requires coordinated actions that are learned through experience [@Graw.Manser2007;@Dutour.etal2016;@Pitman.etal2017;@Dutour.etal2019;@Rampim.etal2020;@Szymkowiak2021], and was thus probably not a pervasive antipredator strategy.
-Other antipredator tactics known to confuse human and non-human predators during the attack sequence are unpredictable escapes and turning angles [@Jones.etal2011;@Briffa2013;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018].
-While predators can adjust to unpredictable prey escapes [@Szopa-Comley.Ioannou2022], it could still be more arduous for a predator to learn and optimize its hunting success if it more often encountered prey using these tactics.
-
-Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition, irrespective of the prey groups that predators encountered.
-For example, in *DBD*, a predator that played 300 matches in the span of six months might forget more critical information (e.g.
-prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days.
-While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
-Moreover, the predators in *DBD* may have differed in their ability to detect prey.
-For example, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
-@Szopa-Comley.etal2020 also found consistent among individual variation in the capacity to detect cryptic and conspicuous prey in three-spined sticklebacks (*Gasterosteus aculeatus*).
-Thus, individual predators should differ in their expertise if they do not learn equally how to exploit the visual cues that facilitate prey detection [@dukasEvolutionaryBiologyAnimal2004;@Dukas2019;@Wright.etal2022].
-
-## Changes in individual hunting specialization with experience and consequences for predator-prey interactions
-
-The predator population displayed an increase in foraging flexibility when reaching the intermediate level of experience.
-As it reached an advanced level of experience, it returned to a level of flexibility that was similar to novice levels.
-This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016].
-Thus, predators in *DBD* were probably exploring and refining different tactics at this stage of experience.
-Within the population, individuals became increasingly distinct in their tactics as well as in their specialization with experience, which was related to the degree of variability in prey encounters.
-Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy.
-Fast-paced hunting is indeed a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when hunting prey that use unpredictable escapes [@Szopa-Comley.Ioannou2022].
-This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period.
-Interestingly, the behavioural response (i.e.
-tactic use and specialization) to experience by individual predators differed.
-For instance, 42.7% of the population did not alter their degree of specialization with experience (i.e.
-remaining either faster and more specialized, or slower and more flexible), while 57.3% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience.
-Thus, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning at varying degrees how to specialize on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
-
-As predators gained experience, their tactic was increasingly matched to the speed of their prey.
-One interpretation could be that both predators and prey learned from each other in an arms-race-like reciprocal relationship [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@Mougi.etal2011].
-For instance, predators that encountered faster prey could have learned to increase their speed to better capture them, resulting in an increase in the speed of the prey to circumvent the predator's attacks.
-In this type of system, faster prey should be better at escaping both slower and faster predators [@Mougi.etal2011], which concords with what we previously observed in this sytem [@FraserFranco.etal2022].
-@BrodieIII.BrodieJr.1999 argue that when prey express defensive phenotypes (e.g.
-physical armaments or venom), selection on predators should be strong because the consequences of being injured are greater than missing a meal.
-If predators improve their exploitative ability, then an arms-race should emerge, and the consequences of hunting dangerous prey should decrease [@BrodieIII.BrodieJr.1999].
-Similarly, we found that has the predator gained experience, the negative consequences of encountering prey groups with higher speeds were relaxed, and the variation in success among predators decreased.
-However, in an arms-race, faster predators would have successfully preyed upon faster and slower prey and would have obtained higher success than slower predators [@Mougi.etal2011], which was not the case in the present study.
-A more likely interaction scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible preyed upon different prey but achieved equal success.
-Thus predators in *DBD* appear to optimize their success by learning to match their tactic to their prey with experience, suggesting that learning through reciprocal interactions may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
-
-## Conclusions
-
-The interactions of predator and prey traits are probably the most important processes involved in population cycles and should occur when predators match their phenotype to their prey [@abramsEvolutionPredatorPreyInteractions2000].
-Yet, its has remained largely unknown whether this trait-matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise.
-With experience, half of the predator population changed their behaviour by developping either a specialized or flexible tactic that was matched to the speed of their prey.
-Our results could be useful to guide predator-prey models of trait-matching, which are often studied at evolutionary timescales.
-For instance, future studies could incorporate individual variation in experience in their models to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility.
-Lastly, virtual systems are increasingly recognized among ecologists as effective systems to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
-We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
-
-# ACKNOWLEDGEMENTS
-
-...
-
-# CONFLICT OF INTEREST STATEMENT
-
-The authors declare no conflict of interest
-
-# REFERENCES {.unnumbered}
-
-<div id="refs"></div>

### 2023-04-25 manuscript/Chapter2-appendix1.Rmd
update appendix1 file

@@
 
+\newpage
+
 ```{r tables1, ft.align = "left"}
@@
 
-knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS1.png"))
+knitr::include_graphics(
+  here::here(
+    "outputs", "04_outputs_figures",
+    "appendix1_figureS1.png"
+  )
+)
 
@@
 
-knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS2.png"))
+knitr::include_graphics(
+  here::here(
+    "outputs", "04_outputs_figures",
+    "appendix1_figureS2.png"
+  )
+)
 
@@
 
-knitr::include_graphics(here::here("outputs", "04_outputs_figures", "appendix1_figureS3.png"))
+knitr::include_graphics(
+  here::here(
+    "outputs", "04_outputs_figures",
+    "appendix1_figureS3.png"
+  )
+)
 

### 2023-04-26 code/04_code_figures/appendix1_figureS4.R
change figure S file names. added S4

@@ -1,0 +1,151 @@
+# =======================================================================
+
+#                       Code to produce Figure S4                       #
+
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 1. Load libraries and import model
+# =======================================================================
+
+# Load libraries
+library(brms)
+library(ggplot2)
+library(data.table)
+
+path <- file.path(getwd(), "outputs", "01_outputs_models")
+fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 2. Estimate differences between novices and advanced levels
+# =======================================================================
+
+
+cors <- as_draws_df(fit, variable = "cor", regex = TRUE)
+cors <- data.table(cors)
+cors <- cors[, !c(".chain", ".iteration", ".draw")]
+
+cors <- melt(cors)
+cors <- cors[!(variable %like% "prior")]
+
+cors1 <- cors[!(variable %like% "interm")]
+cors1 <- cors1[!(variable %like% "novice")]
+cors2 <- cors[!(variable %like% "interm")]
+cors2 <- cors2[!(variable %like% "advanced")]
+
+setnames(cors1, c("variable", "value"), c("variable_adv", "value_adv"))
+setnames(cors2, c("variable", "value"), c("variable_nov", "value_nov"))
+
+
+tab <- cbind(cors1, cors2)
+tab[, difference_cor := value_adv - value_nov]
+
+
+# Intervals
+lower_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[1]
+}
+upper_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+tab[
+  , ":="(
+    median_difference = median(difference_cor),
+    lower_ci_difference = lower_interval(difference_cor),
+    upper_ci_difference = upper_interval(difference_cor)),
+  by = variable_adv
+]
+
+tab <- unique(
+  tab[
+    , .(
+      variable_adv, median_difference,
+      lower_ci_difference, upper_ci_difference
+    )
+  ]
+)
+
+tab[, c(2:4) := round(tab[, c(2:4)], digits = 2)]
+
+
+names <- c(
+  "(mean speed, IIV speed)", "(mean speed, mean prey speed)",
+  "(IIV speed, mean prey speed)", "(mean speed, IIV prey speed)",
[…]

### 2023-04-26 manuscript/Chapter2-appendix1.Rmd
update appendix 1

@@
 ```
-
-\newpage
 
@@
 ```
+
+```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice.
+The difference is displayed on the x axis and the parameter correlations are displayed on the y axis."}
+
+knitr::include_graphics(
+  here::here(
+    "outputs", "04_outputs_figures",
+    "appendix1_figureS4.png"
+  )
+)
+
+```

### 2023-04-26 manuscript/Chapter2-appendix1.Rmd
update tables in all .Rmd files

@@
     fig_caption: yes
-bibliography: references.bib
+bibliography: references2.bib
 csl: ecology.csl
@@
 ```
+
+\newpage
 
@@
 results <- data.table(
-  round(summary(fit)$fixed, digits = 3)[, 1:4],
+  round(summary(fit)$fixed, digits = 2)[, 1:4],
   keep.rownames = TRUE
@@
 
-\newpage
-
 ```{r tables1, ft.align = "left"}
@@
       as_sup("a "),
-      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299"
+      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299 (i.e. group in the main text)"
     ),
@@
     tabs1,
-    caption = "Fixed effects table on the mean part of the model",
+    caption = "Table S1. Fixed effects table on the mean part of the DHMLM comparing random groups of players with different matches played to the group presented in the main text.",
     style = "Table Caption"
@@
     tabs2,
-    caption = "Fixed effects table on the dispersion part of the model",
+    caption = "Table S2. Fixed effects table on the dispersion part of the DHMLM comparing random groups of players with different matches played to the group presented in the main text.",
     style = "Table Caption"

### 2023-04-26 manuscript/Chapter2-appendix3.Rmd
update tables in all .Rmd files

@@
      Appendix 3
+
 output: 
@@
 # Round values to 3 digits
-eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 3)]
+eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 2)]
 
@@
 # Paste upper and lower ci with estimate
-eff_tab[, estimate := paste(format(Estimate, digits = 3), "(")]
-eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 3), sep = "")]
+eff_tab[, estimate := paste(format(Estimate, digits = 2), "(")]
+eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
 eff_tab[, estimate := paste(estimate, ",", sep = "")]
-eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 3), sep = " ")]
+eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
 eff_tab[, estimate := paste(estimate, ")", sep = "")]
@@
                         decimal.mark = ".",
-                        digits = 3)
-  x <- set_table_properties(x, layout = "fixed")
+                        digits = 2)
   x <- border_remove(x)
@@
   x <- hline_bottom(x, part = "all", border = std_border)
-  autofit(x)
+  x <- width(x, j = 1, width = 2.84, unit = "cm")
+  x <- width(x, j = 2, width = 3.78, unit = "cm")
+  x <- width(x, j = c(3:5), width = 3.3, unit = "cm")
 }
@@
   set_caption(
-    caption = "Table S1. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    caption = "Table S1.
+Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
+The coefficients are from the model that includes the outlier.",
     style = "Table Caption"
@@
   fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer") %>%
-  width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
-  width(j = 1, width = 3.2, unit = "cm")
+  fontsize(size = 12, part = "footer")
 
@@
 ranef_tab <- unique(ranef_tab[, .(parameter, mean, lower_ci, upper_ci)])
-ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], 3)]
+ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], digits = 2)]
 
@@
 # Paste upper and lower ci with estimate
-ranef_tab[, estimate := paste(format(mean, digits = 3), "(")]
-ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 3), sep = "")]
+ranef_tab[, estimate := paste(format(mean, digits = 2), "(")]
+ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
 ranef_tab[, estimate := paste(estimate, ",", sep = "")]
-ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 3), sep = " ")]
+ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
 ranef_tab[, estimate := paste(estimate, ")", sep = "")]
@@
 # Reorder rows
-table <- ranef_tab[c(1:5, 6:9)]
+table <- ranef_tab[c(2:9, 1)]
 
@@
                         decimal.mark = ".",
-                        digits = 3)
-  x <- set_table_properties(x, layout = "fixed")
+                        digits = 2)
+  x <- set_table_properties(x, layout = "autofit")
   x <- border_remove(x)
@@
   set_caption(
-    caption = "Table 3. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    caption = "Table S2.
+Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
+The coefficients are from the model that includes the outlier.",
     style = "Table Caption"
@@
   fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer") %>%
-  width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
-  width(j = 1, width = 3.2, unit = "cm")
+  fontsize(size = 12, part = "footer")
+
+tab3 <- autofit(tab3)
 
@@
 
-```{r figS3, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
+\newpage
+
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
 The test is displayed on the y axis (i.e.

### 2023-04-26 manuscript/Chapter2-manuscript.Rmd
update tables in all .Rmd files

@@
 
-Keywords: foraging behaviour, arms race, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology
+Keywords: foraging behaviour, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology
 
@@
 
+Many predator-prey systems are driven by reciprocal interactions where one responds to changes in the behaviour of the other.
+However, the mechanisms driving these individual responses are only beginning to be explored, in part because of the challenges associated with monitoring direct predator-prey interactions.
+In this study, we used a virtual predator-prey system (the online game *Dead by Daylight*) to test how hunting experience shapes individual foraging specialization and success in predators across repeated interactions with their prey.
+With increasing experience, predators fine-tuned their tactics to the behaviour of their prey.
+Individuals that adopted a flexible tactic (i.e.
+generalists) encountered groups of prey with varying speeds, and those that adopted a cursorial and specialized tactic (i.e.
+specialists) encountered groups of prey with similar speeds throughout the study period.
+Our results suggest that experience enables predators to learn how to optimize their tactics to the type of prey that they encounter (i.e.
+fast or slow), which may act as a stabilizing mechanism promoting behavioural diversification in predator-prey systems.
+
 \newpage
@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or on different resources irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@Kernaleguen.etal2015;@Phillips.etal2017].
-A growing body of evidence suggests that ecological interactions such as predator-prey interactions can drive this individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016].
-When they hunt, predators often use techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
+Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or on different prey irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@Kernaleguen.etal2015;@Phillips.etal2017].
+A growing body of evidence suggests that reciprocal interactions between predators and prey could drive this individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
+For instance, predators often hunt using techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
 experience).
@@
 In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-When predator-prey interactions are directly observed, empirical evidence shows that predators often match, among other types of traits [see @Kishida.etal2006;@Hanifin.etal2008;@Brousseau.etal2018;@Reimche.etal2020], their locomotor and behavioural traits to those of their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
-Yet, a recurring question that emerges from these studies is whether and how the behavioural adjustments of predators reflect individual differences in experience/learning [@Kelley.Magurran2011].
+When predator-prey interactions are directly observed, empirical evidence shows that predators often match their locomotor and behavioural traits to those of their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
+Yet, a recurring question emerging from these studies is whether the mechanism driving such behavioural adjustments by predators involves individual differences in experience/learning [@Kelley.Magurran2011].
 Thus, uncovering the role of learning in predator-prey systems where interactions are directly monitored would enable researchers to better predict the behavioural decisions and the success of predators when they are hunting.
@@
 However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
-We recently demonstrated with behavioural data from an online predator-prey videogame, called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge and help uncover the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
-For instance, we found that some individual predators hunt at high speeds, while others prefer to stalk and ambush their prey.
-Individuals also flexibly switch between these tactics, and their success is shaped by the speed of the prey, where faster prey are more difficult to capture.
-The prey need to forage for resources while paying attention to the predator to avoid being detected and chased.
+We recently demonstrated, using an online predator-prey videogame called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge and help uncover the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
+In this dynamic virtual system, four prey players need to forage for resources while avoiding a predator player.
 The prey can contribute to the group's success by healing or helping others escape the predator, or be selfish and attempt to escape by themselves [@Cere.etal2021].
-Predators must learn how the prey behave and decide how best to capture them.
-Thus, *DBD* simulates a highly dynamic system where both predators and prey must adjust to each other, suggesting that virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
-Other studies on virtual predator-prey systems show that predation regimes can drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
+The predators' hunting tactics and their success are largely driven by the movement of the prey, where faster prey are more difficult to capture [@FraserFranco.etal2022].
+Predators should thus benefit from learning how the prey behave to be successful.
+Other studies using virtual predator-prey systems show that predation regimes drives individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
 in prep).
-Virtual predator-prey systems generate large volumes of data on interacting players throughout their lifetime in the game under realistic ecological scenarios.
-Hence, they offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization and performance.
+These examples outline how virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
+They also generate large volumes of data on interacting players throughout their lifetime in the game under realistic ecological scenarios.
+Hence, virtual systems offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization and performance.
 
@@
 
+We predicted that the relationship between hunting success and experience would vary among predators because they should differ in the type of prey that they encounter.
+However, after controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained stable (Figure 1B).
+
+## Effect of experience on the development of behavioural specialization
+
+At the population level, predators did not change their mean speed with experience (i.e.
+intercept of the mean predator speed; Table 2).
+Moreover, there was no directional increase in foraging flexibility or specialization with experience.
+Indeed, the observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e.
+intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S3), but then return to novice-levels of flexibility with advanced experience (i.e.
+intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Appendix S1: Figure S3).
+Thus, our analyses suggest that population-level behavioural specialization changes nonlinearly (quadratic) with experience rather than linearly.
+
+At the individual level, we detected differences in the mean movement speed among predators (i.e.
+the intercept of the mean speed for the predator ID; Table 3).
+These differences remained stable from the novice to the intermediate stages, and then increased at the advanced stage to reach a level higher than when predators were novice (Table 3 and Appendix S1: Figure S3).
+Predators displayed considerable differences in their degree of hunting specialization, and these differences increased with experience (i.e.
+the intercept of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S3).
+Thus, as individual predators gain experience, the population becomes more heterogeneous, with an assemblage of both specialist and flexible hunters.
+Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 2).
+Importantly, 12.6% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
+$\ge$0.2 change in standard deviation), 44.7% displayed lower changes (i.e.
+>0.05 and <0.2 change in standard deviation), while 42.7% remained relatively stable (i.e.
+$\le$0.05 change in standard deviation).
+
+As we predicted, predators differed in the mean speed of the prey that they encountered across matches.
+Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period (i.e.
+the intercept of the mean prey speed for the predator ID; Table 3).
+These differences were greater when predators reached an advanced level of hunting experience (i.e.
+the intercept of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S3).
+In addition, individuals differed in the heterogeneity of the groups of prey encountered across the study period.
+Hence, some predators encountered prey groups with similar average speeds, while others encountered prey groups with different average speeds throughout the study period (i.e.
+the intercept of sigma prey speed for the predator ID; Table 3).
+
+## Relationship between behavioural specialization and prey variability
+
+At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV; Figure 3 and Appendix S2: Table S1).
+Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time.
+Predators that were on average faster (mean) also encountered groups of prey that were on average faster (mean) (Figure 3 and Appendix S2: Table S1).
+At the three experience levels, there were only weak correlations between IIV in predator speed and mean prey speed (Figure 3 and Appendix S2: Table S1).
+However, predators that encountered groups of prey with similar speeds (IIV) specialized in their hunting tactic (IIV) (Figure 3 and Appendix S2: Table S1).
+Hence, predators that encountered groups of prey with similar average speeds were more specialized, while those that encountered groups of prey with different average speeds were more flexible.
+For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Appendix S2: Table S1).
+
+## Hunting success of behavioural specialists vs generalists
+
+We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Appendix S2: Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Appendix S2: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
+However, novice individuals that encountered groups of prey with faster speeds were less successful (Figure 3 and Appendix S2: Table S1).
+This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Appendix S2: Table S1).
+Thus, the consequences of hunting faster prey were reduced at greater experience levels.
+
+# DISCUSSION
+
+Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
+However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
+Our results show that there was no directional increase in either behavioural specialization or flexibility with experience at the population level.
+Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with prey; some specialized in fast-paced hunting, and others adopted a slower and more flexible tactic with experience.
+Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period.
+With experience, predators increasingly matched their tactic to the speed of the prey that they encountered, which simultaneously relaxed the negative consequences of encountering faster prey.
+Together, our observations suggest that predators in *DBD* learn to adjust their hunting tactic to the behaviour of the prey that they encounter throughout their lifetime in the game.
+
+## The development of expertise with hunting experience
+
+Empirical research shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
+However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data has repeated measures of individual success through time.
+Our analyses revealed that there was no population increase in expertise over time.
+As we mentioned before, the matchmaking pairs players using a rank-based system, and this result may thus be due to predators being paired with prey of similar skills.
+However, if this was solely due to the ranking system, we would have found a similar flat relationship for every predator.
+Instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition (Figure 1, Appendix S1: Figure S1A-S1B).
+
+We predicted that this would occur if, by chance, predators differed in the prey that they encountered, because some may be easier and others more difficult to capture.
+In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
+In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
+Yet, prey speed did not shape individual differences in expertise acquisition, but other antipredator tactics may be involved.
+For example, it is well known in *DBD* that some prey groups use mobbing to confuse the predator or prevent it from capturing an injured individual.
+However, like natural predator-prey systems, direct predator-mobbing in *DBD* is dangerous and requires coordinated actions that are learned through experience [@Graw.Manser2007;@Dutour.etal2016;@Pitman.etal2017;@Dutour.etal2019;@Szymkowiak2021], and was thus probably not a pervasive antipredator strategy.
+Other antipredator tactics known to confuse human and non-human predators during the attack sequence are unpredictable escapes and turning angles [@Jones.etal2011;@Briffa2013;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018].
+While predators can adjust to unpredictable prey escapes [@Szopa-Comley.Ioannou2022], it could still be more arduous for a predator to learn and optimize its hunting success if it more often encountered prey using these tactics.
+
+Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition, irrespective of the prey groups that predators encountered.
+For example, in *DBD*, a predator that played 300 matches in the span of six months might forget more critical information (e.g.
+prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days.
+While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
+Moreover, the predators may have differed in their ability to detect prey.
+For example, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
+@Szopa-Comley.etal2020 also found consistent among individual variation in the capacity to detect cryptic and conspicuous prey in three-spined sticklebacks (*Gasterosteus aculeatus*).
+Thus, individual predators should differ in their expertise if they do not learn equally how to exploit the visual cues that facilitate prey detection.
+
+## Changes in individual hunting specialization with experience and consequences for predator-prey interactions
+
+The predator population displayed an increase in foraging flexibility when reaching the intermediate level of experience.
+As it reached an advanced level of experience, it returned to a level of flexibility that was similar to novice levels.
+This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016].
+Thus, predators in *DBD* were probably exploring and refining different tactics at this stage of experience.
+Within the population, differences in individual foraging specialization among predators increased with experience, which was related to the degree of variability in prey encounters.
+Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy.
+Fast-paced hunting is indeed a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when hunting prey that use unpredictable escapes [@Szopa-Comley.Ioannou2022].
+This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period.
+Interestingly, the behavioural response (i.e.
+tactic use and specialization) to experience by individual predators differed.
+For instance, 42.7% of the population did not alter their degree of specialization with experience (i.e.
+remaining either faster and more specialized, or slower and more flexible), while 57.3% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience.
+Thus, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning at varying degrees how to specialize on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
+
+As predators gained experience, their tactic was increasingly matched to the speed of their prey.
+One interpretation could be that both predators and prey learned from each other in an arms-race-like reciprocal relationship [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@Mougi.etal2011].
+For instance, predators that encountered faster prey could have learned to increase their speed to better capture them, resulting in an increase in the speed of the prey to circumvent the predator's attacks.
+In this type of system, faster prey should be better at escaping both slower and faster predators [@Mougi.etal2011], which concords with what we previously observed in this sytem [@FraserFranco.etal2022].
+@BrodieIII.BrodieJr.1999 argue that when prey express defensive phenotypes (e.g.
+physical armaments or venom), selection on predators should be strong because the consequences of being injured are greater than missing a meal.
+If predators improve their exploitative ability, then an arms-race should emerge, and the consequences of hunting dangerous prey should decrease [@BrodieIII.BrodieJr.1999].
+Similarly, we found that has the predator gained experience, the negative consequences of encountering prey groups with higher speeds were relaxed, and the variation in success among predators decreased.
+However, in an arms-race, faster predators would have successfully preyed upon faster and slower prey and would have obtained higher success than slower predators [@Mougi.etal2011], which was not the case in the present study.
+A more likely scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success.
+Thus predators in *DBD* appear to optimize their success by learning to match their tactic to their prey with experience, suggesting that learning through reciprocal interactions may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
+
+## Conclusions
+
+Trait-mediated predator-prey interactions are important processes involved in population cycles and should occur when predators match their phenotype to their prey [@abramsEvolutionPredatorPreyInteractions2000].
+Yet, it has remained largely unknown whether this trait-matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
+By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise.
+With experience, half of the predator population changed their behaviour by developping either a specialized or flexible tactic that was matched to the speed of their prey.
+Overall, both type of hunters achieved equal hunting success.
+Our results have potential applications for predator-prey models of trait-matching.
+For instance, simulation studies could incorporate individual variation in experience or learning to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility.
+Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
+We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
+
+# ACKNOWLEDGEMENTS
+
+We warmly thank Behaviour Interactive Inc.
+for our collaboration which helps in advancing predator-prey science.
+We thank Julien Céré who managed the communication between us and the company, and Marine Dupuy who helped us prepare the data used in this study.
+We thank Alastair J.
+Wilson for insightful comments on the results.
+We also thank all members of Pierre-Olivier Montiglio's laboratory who provided useful feedback on earlier versions on this work.
+This work was supported by an NSERC postgraduate doctoral scholarship (569716-2022).
+
+# CONFLICT OF INTEREST STATEMENT
+
+The authors declare no conflict of interest
+
+\newpage
+
+# REFERENCES {.unnumbered}
+
+<div id="refs"></div>
+
+\newpage
+
+# TABLES
+
 ```{r table1, ft.align = "left"}
@@
 # Open the loo table
-path <- file.path(here::here("outputs", "03_outputs_model-validation"))
-loo_tab <- data.table(readRDS(file.path(path, "03A_lootable.rds")))
+path <- file.path(here::here("outputs", "02_outputs_model-validation"))
+loo_tab <- data.table(readRDS(file.path(path, "A1-3_lootable.rds")))
 
@@
                          digits = 2)
-   x <- set_table_properties(x, layout = "fixed")
+   x <- set_table_properties(x, layout = "autofit")
    x <- border_remove(x)
@@
    x <- hline_bottom(x, part = "all", border = std_border)
-   autofit(x)
 }
@@
   my_theme() %>%
-   merge_v(part = "header") %>%
-   merge_h(part = "header") %>%
-   fontsize(size = 10, part = "all") %>%
-   font(fontname = "Times New Roman", part = "all") %>%
   align(align = "left", part = "all", j = 1) %>%
@@
   align(align = "center", part = "all", j = 4) %>%
-   align(align = "center", part = "all", j = 5)
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 3. Customize and print the table
-# ===========================================================================
-
-# Autofit to window
-tab1 <- autofit(tab1)
-
-# Add a footnote
-tab1 <- tab1 %>%
+  align(align = "center", part = "all", j = 5) %>%
   footnote(
@@
   ) %>%
-  font(fontname = "Times New Roman", part = "all") %>%
-  fontsize(size = 11, part = "all")
 
@@
   set_caption(
-  tab1,
-  caption = "Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience",
+    caption = "Table 1. Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience.",
     style = "Table Caption"
-)
+  ) %>%
+
+  # Font options
+  font(fontname = "Times New Roman", part = "all") %>%
+  fontsize(size = 10, part = "all") %>%
+  fontsize(size = 12, part = "footer")
+
+tab1
 
@@
 
-We predicted that the relationship between hunting success and experience would vary among predators because they should differ in the type of prey that they encounter.
-However, after controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained stable (Figure 1B).
-
-```{r fig1, out.width = "100%", fig.cap = "**Figure 1.** Among individual differences in the development of hunting expertise.
-The predators' hunting success (i.e.
-the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e.
-the number of matches played prior to each observation) is on the x axis.
-Each fitted curve represents an individual predator.
-(A) A generalized additive mixed model where we do not control for prey speed (B) A generalized additive mixed model where we control for prey speed."}
-
-knitr::include_graphics(
-  here::here("outputs", "05_outputs_figures", "05_figure1.png")
-)
-
-```
-
-## Effect of experience on the development of behavioural specialization
-
-At the population level, predators did not change their mean speed with experience (i.e.
-intercept of the mean predator speed; Table 2).
-Moreover, there was no directional increase in foraging flexibility or specialization with experience.
-Indeed, the observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e.
-intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S4), but then return to novice-levels of flexibility with advanced experience (i.e.
-intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Appendix S1: Figure S4).
-Thus, our analyses suggest that population-level behavioural specialization changes nonlinearly (quadratic) with experience rather than linearly.
+\newpage
 
@@
 fit <- readRDS(
-  file.path(path, "02_outputs_models", "02B_DHMLM.rds")
+  file.path(path, "01_outputs_models", "B1_DHMLM-no-outlier.rds")
 )
@@
   align(align = "center", part = "all", j = 4) %>%
-  align(align = "center", part = "all", j = 5)
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 4. Customize and print the table
-# ===========================================================================
-
-# Autofit to window size
-tab2 <- autofit(tab2)
-
-# Table footnote
-tab2 <- tab2 %>%
+  align(align = "center", part = "all", j = 5) %>%
+
+  # Footnote
   footnote(
@@
   ) %>%
-  font(fontname = "Times New Roman", part = "all") %>%
-  width(j = c(2, 3, 4, 5), width = 3.7, unit = "cm") %>%
-  width(j = 1, width = 3.2, unit = "cm")
 
@@
   set_caption(
-  tab2,
-  caption = "Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    caption = "Table 2. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
     style = "Table Caption"
-)
+  ) %>%
+
+  # Font options
+  font(fontname = "Times New Roman", part = "all") %>%
+  fontsize(size = 10, part = "all") %>%
+  fontsize(size = 12, part = "footer")
+
+tab2
 
@@
 
-At the individual level, we detected differences in the mean movement speed among predators (i.e.
-the intercept of the mean speed for the predator ID; Table 3).
-These differences remained stable from the novice to the intermediate stages, and then increased at the advanced stage to reach a level higher than when predators were novice (Table 3 and Appendix S1: Figure S4).
-Predators displayed considerable differences in their degree of hunting specialization, and these differences increased with experience (i.e.
-the intercept of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S4).
-Thus, as individual predators gain experience, the population becomes more heterogeneous, with an assemblage of both specialist and flexible hunters.
-Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 2).
-Importantly, 12.6% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
-$\ge$0.2 change in standard deviation), 44.7% displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation), while 42.7% remained relatively stable (i.e.
-$\le$0.05 change in standard deviation).
+\newpage
 
@@
   x <- hline_bottom(x, part = "all", border = std_border)
-  autofit(x)
 }
@@
   set_caption(
-  tab3,
-  caption = "Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    caption = "Table 3. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
     style = "Table Caption"
-)
+  ) %>%
+
+  # Font options
+  font(fontname = "Times New Roman", part = "all") %>%
+  fontsize(size = 10, part = "all") %>%
+  fontsize(size = 12, part = "footer")
+
+tab3
 
@@
 
-As we predicted, predators differed in the mean speed of the prey that they encountered across matches.
-Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period (i.e.
-the intercept of the mean prey speed for the predator ID; Table 3).
-These differences were greater when predators reached an advanced level of hunting experience (i.e.
-the intercept of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S4).
-In addition, individuals differed in the heterogeneity of the groups of prey encountered across the study period.
-Hence, some predators encountered prey groups with similar average speeds, while others encountered prey groups with different average speeds throughout the study period (i.e.
-the intercept of sigma prey speed for the predator ID; Table 3).
-
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
+\newpage
+
+# FIGURE CAPTIONS
+
+**Figure 1.** Among individual differences in the development of hunting expertise.
+The predators' hunting success (i.e.
+the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e.
+the number of matches played prior to each observation) is on the x axis.
+Each fitted curve represents an individual predator.
+(A) A generalized additive mixed model where we do not control for prey speed (B) A generalized additive mixed model where we control for prey speed.
+
+**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
 The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
 Both figure panels are ordered by ascending degree of increase in either specialization or flexibility.
-We selected the individuals displayed in the figure by first substracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles.
-Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.28 standard deviations."}
-
-knitr::include_graphics(
-  here::here("outputs", "05_outputs_figures", "05_figure2.png")
-)
-
-```
-
-## Relationship between behavioural specialization and prey variability
-
-At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV; Figure 3 and Appendix S2: Table S1).
-Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time.
-Predators that were on average faster (mean) also encountered groups of prey that were on average faster (mean) (Figure 3 and Appendix S2: Table S1).
-At the three experience levels, there were only weak correlations between IIV in predator speed and mean prey speed (Figure 3 and Appendix S2: Table S1).
-However, predators that encountered groups of prey with similar speeds (IIV) specialized in their hunting tactic (IIV) (Figure 3 and Appendix S2: Table S1).
-Hence, predators that encountered groups of prey with similar average speeds were more specialized, while those that encountered groups of prey with different average speeds were more flexible.
-For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Appendix S2: Table S1).
-
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3.** Correlation matrices of the MDHGLM relating the mean and intra individual variability (IIV) in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+We selected the individuals displayed in the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles.
+Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.28 standard deviations.
+
+**Figure 3.** Correlation matrices of the MDHGLM relating the mean and intra individual variability (IIV) in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
 Larger dark blue circles indicate stronger positive correlations (positive values on the color legend), while larger dark red circles indicate stronger negative correlations (negative values on the color legend).
@@
 B) Correlations when predators were at an intermediate level of experience.
-C) Correlations when predators were advanced hunters."}
+C) Correlations when predators were advanced hunters.
+
+\newpage
+
+# FIGURES
+
+```{r fig1, out.width = "100%", fig.cap = "**Figure 1**"}
 
 knitr::include_graphics(
-  here::here("outputs", "05_outputs_figures", "05_figure3.png")
-)
+  here::here("outputs", "04_outputs_figures", "figure1.png")
+)
+
 ```
 
-## Hunting success of behavioural specialists vs generalists
-
-We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Appendix S2: Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Appendix S2: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
-However, novice individuals that encountered groups of prey with faster speeds were less successful (Figure 3 and Appendix S2: Table S1).
-This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Appendix S2: Table S1).
-Thus, the consequences of hunting faster prey were reduced at greater experience levels.
-
-# DISCUSSION
-
-Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
-However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-Our results show that there was no directional increase in either behavioural specialization or flexibility with experience at the population level.
-Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with prey; some specialized in fast-paced hunting, and others adopted a slower and more flexible tactic with experience.
-Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period.
-With experience, predators increasingly matched their tactic to the speed of the prey that they encountered, which simultaneously relaxed the negative consequences of encountering faster prey.
-Together, our observations suggest that predators in *DBD* learn to adjust their hunting tactic to the behaviour of the prey that they encounter throughout their lifetime in the game.
-
-## The development of expertise with hunting experience
-
-Empirical research shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
-However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data has repeated measures of individual success through time.
-Our analyses revealed that there was no population increase in expertise over time.
-As we mentioned before, the matchmaking pairs players using a rank-based system, and this result may thus be due to predators being paired with prey of similar skills.
-However, if this was solely due to the ranking system, we would have found a similar flat relationship for every predator.
-Instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition (Figure 1, Appendix S1: Figure S1A-S1B).
-
-We predicted that this would occur if, by chance, predators differed in the prey that they encountered, because some may be easier and others more difficult to capture.
-In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
-Yet, prey speed did not shape individual differences in expertise acquisition, but other antipredator tactics may be involved.
-For example, it is well known in *DBD* that some prey groups use mobbing to confuse the predator or prevent it from capturing an injured individual.
-However, like natural predator-prey systems, direct predator-mobbing in *DBD* is dangerous and requires coordinated actions that are learned through experience [@Graw.Manser2007;@Dutour.etal2016;@Pitman.etal2017;@Dutour.etal2019;@Rampim.etal2020;@Szymkowiak2021], and was thus probably not a pervasive antipredator strategy.
-Other antipredator tactics known to confuse human and non-human predators during the attack sequence are unpredictable escapes and turning angles [@Jones.etal2011;@Briffa2013;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018].
-While predators can adjust to unpredictable prey escapes [@Szopa-Comley.Ioannou2022], it could still be more arduous for a predator to learn and optimize its hunting success if it more often encountered prey using these tactics.
-
-Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition, irrespective of the prey groups that predators encountered.
-For example, in *DBD*, a predator that played 300 matches in the span of six months might forget more critical information (e.g.
-prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days.
-While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
-Moreover, the predators may have differed in their ability to detect prey.
-For example, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
-@Szopa-Comley.etal2020 also found consistent among individual variation in the capacity to detect cryptic and conspicuous prey in three-spined sticklebacks (*Gasterosteus aculeatus*).
-Thus, individual predators should differ in their expertise if they do not learn equally how to exploit the visual cues that facilitate prey detection [@dukasEvolutionaryBiologyAnimal2004;@Dukas2019;@Wright.etal2022].
-
-## Changes in individual hunting specialization with experience and consequences for predator-prey interactions
-
-The predator population displayed an increase in foraging flexibility when reaching the intermediate level of experience.
-As it reached an advanced level of experience, it returned to a level of flexibility that was similar to novice levels.
-This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016].
-Thus, predators in *DBD* were probably exploring and refining different tactics at this stage of experience.
-Within the population, differences in individual foraging specialization among predators increased with experience, which was related to the degree of variability in prey encounters.
-Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy.
-Fast-paced hunting is indeed a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when hunting prey that use unpredictable escapes [@Szopa-Comley.Ioannou2022].
-This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period.
-Interestingly, the behavioural response (i.e.
-tactic use and specialization) to experience by individual predators differed.
-For instance, 42.7% of the population did not alter their degree of specialization with experience (i.e.
-remaining either faster and more specialized, or slower and more flexible), while 57.3% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience.
-Thus, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning at varying degrees how to specialize on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
-
-As predators gained experience, their tactic was increasingly matched to the speed of their prey.
-One interpretation could be that both predators and prey learned from each other in an arms-race-like reciprocal relationship [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@Mougi.etal2011].
-For instance, predators that encountered faster prey could have learned to increase their speed to better capture them, resulting in an increase in the speed of the prey to circumvent the predator's attacks.
-In this type of system, faster prey should be better at escaping both slower and faster predators [@Mougi.etal2011], which concords with what we previously observed in this sytem [@FraserFranco.etal2022].
-@BrodieIII.BrodieJr.1999 argue that when prey express defensive phenotypes (e.g.
-physical armaments or venom), selection on predators should be strong because the consequences of being injured are greater than missing a meal.
-If predators improve their exploitative ability, then an arms-race should emerge, and the consequences of hunting dangerous prey should decrease [@BrodieIII.BrodieJr.1999].
-Similarly, we found that has the predator gained experience, the negative consequences of encountering prey groups with higher speeds were relaxed, and the variation in success among predators decreased.
-However, in an arms-race, faster predators would have successfully preyed upon faster and slower prey and would have obtained higher success than slower predators [@Mougi.etal2011], which was not the case in the present study.
-A more likely scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible preyed upon different prey, but they both achieved equal success.
-Thus predators in *DBD* appear to optimize their success by learning to match their tactic to their prey with experience, suggesting that learning through reciprocal interactions may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
-
-## Conclusions
-
-The interactions of predator and prey traits are probably the most important processes involved in population cycles and should occur when predators match their phenotype to their prey [@abramsEvolutionPredatorPreyInteractions2000].
-Yet, it has remained largely unknown whether this trait-matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise.
-With experience, half of the predator population changed their behaviour by developping either a specialized or flexible tactic that was matched to the speed of their prey.
-Overall, both type of hunters achieved equal hunting success.
-Our results have potential applications for predator-prey models of trait-matching.
-For instance, future studies could incorporate individual variation in experience or learning in their models to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility.
-Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
-We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
-
-# ACKNOWLEDGEMENTS
-
-We warmly thank Behaviour Interactive Inc.
-for our collaboration which helps in advancing predator-prey science.
-We thank Julien Céré who smoothly managed the communication between us and the company, and Marine Dupuy who helped us prepare the data used in this study.
-We thank Alastair J.
-Wilson for insightful comments on the results.
-We also thank all members of Pierre-Olivier Montiglio's laboratory who provided useful feedback on earlier versions on this work.
-This work was supported by an NSERC postgraduate doctoral scholarship (569716-2022).
-
-# CONFLICT OF INTEREST STATEMENT
-
-The authors declare no conflict of interest
-
-# REFERENCES {.unnumbered}
-
-<div id="refs"></div>
+\newpage
+
+```{r fig2, out.width = "100%", fig.cap = "**Figure 2**"}
+
+knitr::include_graphics(
+  here::here("outputs", "04_outputs_figures", "figure2.png")
+)
+
+```
+
+\newpage
+
+```{r fig3, out.width = "100%", fig.cap = "**Figure 3**"}
+
+knitr::include_graphics(
+  here::here("outputs", "04_outputs_figures", "figure3.png")
+)
+
+```

### 2023-04-26 code/04_code_figures/appendix1_figureS1-S2.R
update figure SX names in header. added appendix 3 fig S2. renamed S figs

@@ -1,6 +1,6 @@
 # ==========================================================================
 
-#                         expertise-variance plot
+#             Code to produce Appendix 1 : Figure S1 and S2                #
 
 # ==========================================================================
 

### 2023-04-26 code/04_code_figures/appendix3_figureS1.R

@@ -1,0 +1,243 @@
+# =======================================================================
+
+#               Code to produce Appendix 3 : Figure S1                  #
+
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 1. Load libraries and import model
+# =======================================================================
+
+# Load libraries
+library(brms)
+library(ggplot2)
+library(viridis)
+
+path <- file.path(getwd(), "outputs", "01_outputs_models")
+fit <- readRDS(file.path(path, "B1_DHMLM.rds"))
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 2. Estimate differences between experience levels
+# =======================================================================
+
+# a -> Compare novices vs intermediate
+# b -> Compare intermediate with advanced
+# c-> Compare novices with advanced
+
+
+# Do predators become increasingly flexible? ----------------------------
+
+hyp1a <- "exp(sigma_speednovice_Intercept) < exp(sigma_speedinterm_Intercept)"
+hyp1b <- "exp(sigma_speedinterm_Intercept) > exp(sigma_speedadvanced_Intercept)"
+hyp1c <- "exp(sigma_speednovice_Intercept) > exp(sigma_speedadvanced_Intercept)"
+hyp1 <- hypothesis(x = fit, hypothesis = c(hyp1a, hyp1b, hyp1c))
+
+
+
+# Does individual variation in avg speed change with XP? ----------------
+
+hyp2a <- "exp(predator_id__speednovice_Intercept) > exp(predator_id__speedinterm_Intercept)"
+hyp2b <- "exp(predator_id__speedinterm_Intercept) < exp(predator_id__speedadvanced_Intercept)"
+hyp2c <- "exp(predator_id__speednovice_Intercept) < exp(predator_id__speedadvanced_Intercept)"
+hyp2 <- hypothesis(x = fit, hypothesis = c(hyp2a, hyp2b, hyp2c), class = "sd")
+
+
+
+# Does individual variation in speed var. change with XP? ---------------
+
+hyp3a <- "exp(predator_id__sigma_speednovice_Intercept) < exp(predator_id__sigma_speedinterm_Intercept)"
[…]

### 2023-04-26 code/04_code_figures/appendix3_figureS2.R

@@ -1,6 +1,6 @@
 # =======================================================================
 
-#               Code to produce Appendix 1 : Figure S4                  #
+#               Code to produce Appendix 3 : Figure S2                  #
 
 # =======================================================================
 
@@ -18,7 +18,7 @@ library(ggplot2)
 library(data.table)
 
 path <- file.path(getwd(), "outputs", "01_outputs_models")
-fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
+fit <- readRDS(file.path(path, "B1_DHMLM.rds"))
 
 # =======================================================================
 # =======================================================================
@@ -139,7 +139,7 @@ path <- file.path(getwd(), "outputs", "04_outputs_figures")
 
 # Export
 ggsave(
-  filename = file.path(path, "appendix1_figureS4.png"),
+  filename = file.path(path, "appendix3_figureS2.png"),
   plot = fig,
   width = 15, height = 10, # 32 14
   #scale = 1.2,

### 2023-04-26 manuscript/Chapter2-appendix3.Rmd
update fig titles in appendix3

@@
 whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis.
-Each panel represent the experience level groups that are being compared."}
+Each panel represent the experience level groups that are being compared.
+The results are from the model that includes the outlier."}
 
@@
 ```
+
+```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice.
+The difference is displayed on the x axis and the parameter correlations are displayed on the y axis.
+The results are from the MDHGLM that includes the outlier."}
+
+knitr::include_graphics(
+  here::here(
+    "outputs", "04_outputs_figures",
+    "appendix3_figureS2.png"
+  )
+)
+
+```

### 2023-04-27 code/04_code_figures/appendix1_figureS3.R
changed appendix1 fig S3 and S4

@@ -16,6 +16,7 @@
 library(brms)
 library(ggplot2)
 library(viridis)
+library(data.table)
 
 path <- file.path(getwd(), "outputs", "01_outputs_models")
 fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
@@ -36,192 +37,228 @@ fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
 # c-> Compare novices with advanced
 
 
-# Do predators become increasingly flexible? ----------------------------
+# Extract the posterior samples -----------------------------------------
 
-hyp1a <- "exp(sigma_speednovice_Intercept) < exp(sigma_speedinterm_Intercept)"
-hyp1b <- "exp(sigma_speedinterm_Intercept) > exp(sigma_speedadvanced_Intercept)"
-hyp1c <- "exp(sigma_speednovice_Intercept) > exp(sigma_speedadvanced_Intercept)"
-hyp1 <- hypothesis(x = fit, hypothesis = c(hyp1a, hyp1b, hyp1c))
-
-
-
-# Does individual variation in avg speed change with XP? ----------------
-
-hyp2a <- "exp(predator_id__speednovice_Intercept) > exp(predator_id__speedinterm_Intercept)"
-hyp2b <- "exp(predator_id__speedinterm_Intercept) < exp(predator_id__speedadvanced_Intercept)"
-hyp2c <- "exp(predator_id__speednovice_Intercept) < exp(predator_id__speedadvanced_Intercept)"
-hyp2 <- hypothesis(x = fit, hypothesis = c(hyp2a, hyp2b, hyp2c), class = "sd")
-
-
-
-# Does individual variation in speed var. change with XP? ---------------
-
-hyp3a <- "exp(predator_id__sigma_speednovice_Intercept) < exp(predator_id__sigma_speedinterm_Intercept)"
-hyp3b <- "exp(predator_id__sigma_speedinterm_Intercept) < exp(predator_id__sigma_speedadvanced_Intercept)"
-hyp3c <- "exp(predator_id__speednovice_Intercept) < exp(predator_id__speedadvanced_Intercept)"
-hyp3 <- hypothesis(x = fit, hypothesis = c(hyp3a, hyp3b, hyp3c), class = "sd")
-
-
-
-# Do predators differ in the avg speed of prey encountered? -------------
-
[…]

### 2023-04-27 code/04_code_figures/appendix1_figureS4.R

@@ -53,18 +53,36 @@ tab[, difference_cor := value_adv - value_nov]
 
 
 # Intervals
-lower_interval <- function(x) {
+lower_95 <- function(x) {
   coda::HPDinterval(as.mcmc(x), 0.95)[1]
 }
-upper_interval <- function(x) {
+upper_95 <- function(x) {
   coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+lower_80 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.80)[1]
+}
+upper_80 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.80)[2]
+}
+
+lower_50 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.50)[1]
+}
+upper_50 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.50)[2]
 }
 
 tab[
   , ":="(
     median_difference = median(difference_cor),
-    lower_ci_difference = lower_interval(difference_cor),
-    upper_ci_difference = upper_interval(difference_cor)),
+    lower_ci_95 = lower_95(difference_cor),
+    upper_ci_95 = upper_95(difference_cor),
+    lower_ci_80 = lower_80(difference_cor),
+    upper_ci_80 = upper_80(difference_cor),
+    lower_ci_50 = lower_50(difference_cor),
+    upper_ci_50 = upper_50(difference_cor)),
   by = variable_adv
 ]
 
@@ -72,12 +90,14 @@ tab <- unique(
   tab[
     , .(
       variable_adv, median_difference,
-      lower_ci_difference, upper_ci_difference
+      lower_ci_95, upper_ci_95,
+      lower_ci_80, upper_ci_80,
+      lower_ci_50, upper_ci_50
     )
   ]
 )
 
-tab[, c(2:4) := round(tab[, c(2:4)], digits = 2)]
+tab[, c(2:8) := round(tab[, c(2:8)], digits = 2)]
 
 
 names <- c(
@@ -103,6 +123,12 @@ tab[, variable_adv := names]
 
 # Compute plots ---------------------------------------------------------
 
+colors <- c(
+  "0.95" = "gray91",
+  "0.80" = "gray71",
+  "0.50" = "gray21"
+)
+
 fig <- ggplot(
   tab,
   aes(x = variable_adv, y = median_difference)
@@ -111,12 +137,37 @@ fig <- ggplot(
[…]

### 2023-04-27 code/04_code_figures/appendix3_figureS2.R
update appendix3 fig S2

@@ -53,18 +53,37 @@ tab[, difference_cor := value_adv - value_nov]
 
 
 # Intervals
-lower_interval <- function(x) {
+# Intervals
+lower_95 <- function(x) {
   coda::HPDinterval(as.mcmc(x), 0.95)[1]
 }
-upper_interval <- function(x) {
+upper_95 <- function(x) {
   coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+lower_80 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.80)[1]
+}
+upper_80 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.80)[2]
+}
+
+lower_50 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.50)[1]
+}
+upper_50 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.50)[2]
 }
 
 tab[
   , ":="(
     median_difference = median(difference_cor),
-    lower_ci_difference = lower_interval(difference_cor),
-    upper_ci_difference = upper_interval(difference_cor)),
+    lower_ci_95 = lower_95(difference_cor),
+    upper_ci_95 = upper_95(difference_cor),
+    lower_ci_80 = lower_80(difference_cor),
+    upper_ci_80 = upper_80(difference_cor),
+    lower_ci_50 = lower_50(difference_cor),
+    upper_ci_50 = upper_50(difference_cor)),
   by = variable_adv
 ]
 
@@ -72,13 +91,14 @@ tab <- unique(
   tab[
     , .(
       variable_adv, median_difference,
-      lower_ci_difference, upper_ci_difference
+      lower_ci_95, upper_ci_95,
+      lower_ci_80, upper_ci_80,
+      lower_ci_50, upper_ci_50
     )
   ]
 )
 
-tab[, c(2:4) := round(tab[, c(2:4)], digits = 2)]
-
+tab[, c(2:8) := round(tab[, c(2:8)], digits = 2)]
 
 names <- c(
   "(mean speed, IIV speed)", "(mean speed, mean prey speed)",
@@ -103,6 +123,12 @@ tab[, variable_adv := names]
 
 # Compute plots ---------------------------------------------------------
 
+colors <- c(
+  "0.95" = "gray91",
+  "0.80" = "gray71",
+  "0.50" = "gray21"
+)
+
 fig <- ggplot(
   tab,
[…]

### 2023-04-27 code/04_code_figures/appendix1_figureS3.R
update appendix3 figure S1

@@ -269,7 +269,7 @@ path <- file.path(getwd(), "outputs", "04_outputs_figures")
 
 # Export
 ggsave(
-  filename = file.path(path, "appendix1_figureS3-test.png"),
+  filename = file.path(path, "appendix1_figureS3.png"),
   plot = fig,
   width = 32, height = 14, # 32 14
   units = "cm",

### 2023-04-27 code/04_code_figures/appendix3_figureS1.R

@@ -1,6 +1,6 @@
 # =======================================================================
 
-#               Code to produce Appendix 3 : Figure S1                  #
+#                       Code to produce Figure S3                       #
 
 # =======================================================================
 
@@ -16,6 +16,7 @@
 library(brms)
 library(ggplot2)
 library(viridis)
+library(data.table)
 
 path <- file.path(getwd(), "outputs", "01_outputs_models")
 fit <- readRDS(file.path(path, "B1_DHMLM.rds"))
@@ -36,192 +37,228 @@ fit <- readRDS(file.path(path, "B1_DHMLM.rds"))
 # c-> Compare novices with advanced
 
 
-# Do predators become increasingly flexible? ----------------------------
+# Extract the posterior samples -----------------------------------------
 
-hyp1a <- "exp(sigma_speednovice_Intercept) < exp(sigma_speedinterm_Intercept)"
-hyp1b <- "exp(sigma_speedinterm_Intercept) > exp(sigma_speedadvanced_Intercept)"
-hyp1c <- "exp(sigma_speednovice_Intercept) > exp(sigma_speedadvanced_Intercept)"
-hyp1 <- hypothesis(x = fit, hypothesis = c(hyp1a, hyp1b, hyp1c))
-
-
-
-# Does individual variation in avg speed change with XP? ----------------
-
-hyp2a <- "exp(predator_id__speednovice_Intercept) > exp(predator_id__speedinterm_Intercept)"
-hyp2b <- "exp(predator_id__speedinterm_Intercept) < exp(predator_id__speedadvanced_Intercept)"
-hyp2c <- "exp(predator_id__speednovice_Intercept) < exp(predator_id__speedadvanced_Intercept)"
-hyp2 <- hypothesis(x = fit, hypothesis = c(hyp2a, hyp2b, hyp2c), class = "sd")
-
-
-
-# Does individual variation in speed var. change with XP? ---------------
-
-hyp3a <- "exp(predator_id__sigma_speednovice_Intercept) < exp(predator_id__sigma_speedinterm_Intercept)"
-hyp3b <- "exp(predator_id__sigma_speedinterm_Intercept) < exp(predator_id__sigma_speedadvanced_Intercept)"
-hyp3c <- "exp(predator_id__speednovice_Intercept) < exp(predator_id__speedadvanced_Intercept)"
-hyp3 <- hypothesis(x = fit, hypothesis = c(hyp3a, hyp3b, hyp3c), class = "sd")
-
-
-
[…]

### 2023-04-27 manuscript/Chapter2-appendix1.Rmd
update appendices 1 and 3

@@
 
-```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice.
+```{r figS4, out.width = "80%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice.
 The difference is displayed on the x axis and the parameter correlations are displayed on the y axis."}

### 2023-04-27 manuscript/Chapter2-appendix3.Rmd
update appendices 1 and 3

@@
 
-```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice.
+```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice.
 The difference is displayed on the x axis and the parameter correlations are displayed on the y axis.

### 2023-04-28 manuscript/Chapter2-appendix1.Rmd
update appendix 1

@@
 
-```{r figS3, out.width = "100%", fig.cap = "**Figure S3.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
-The test is displayed on the y axis (i.e.
-whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis.
-Each panel represent the experience level groups that are being compared."}
+```{r figS3, out.width = "100%", fig.cap = "**Figure S3.** Posterior median differences and credible intervals comparing the parameter values predicted by the MDHGLM between each predator experience level.
+Each panel represent the experience levels that are compared.
+The parameter being compared is displayed on the y axis (e.g.
+whether the standard deviation of predator ID on the mean differs when the population was intermediate vs novice), and the difference is displayed on the x axis."}
 
@@
 
-```{r figS4, out.width = "80%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice.
-The difference is displayed on the x axis and the parameter correlations are displayed on the y axis."}
+```{r figS4, out.width = "80%", fig.cap = "**Figure S4.** Posterior median differences and credible intervals comparing the correlations between traits when predators were advanced vs novice.
+The median difference is displayed on the x axis and the trait correlations being compared are displayed on the y axis."}
 

### 2023-05-02 code/04_code_figures/appendix1_figureS1-S2.R
updated appendixS1 figure S1

@@ -1,498 +1,0 @@
-# ==========================================================================
-
-#             Code to produce Appendix 1 : Figure S1 and S2                #
-
-# ==========================================================================
-
-
-
-
-
-# ==========================================================================
-# 1. Prepare script
-# ==========================================================================
-
-
-# Load libraries and models ------------------------------------------------
-
-library(brms)
-library(data.table)
-library(ggplot2)
-library(ggridges)
-library(ggpubr)
-
-path <- file.path(getwd(), "outputs", "01_outputs_models")
-
-fit1 <- readRDS(file.path(path, "A3_GAMM.rds"))
-fit2 <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
-
-
-
-# Load the data ------------------------------------------------------------
-
-data <- fread("./data/FraserFrancoetalXXXX-data.csv",
-              select = c("predator_id",
-                         "game_duration",
-                         "pred_speed",
-                         "prey_avg_speed",
-                         "cumul_xp_pred",
-                         "total_xp_pred",
-                         "hunting_success",
-                         "latency_1st_capture",
-                         "chase_count",
-                         "chase_count_success"))
-
-data[, predator_id := as.factor(predator_id)]
-
-
-
-# Post processing preparations for custom family ---------------------------
-
-expose_functions(fit1, vectorize = TRUE)
-
-# Define the log likelihood function
-log_lik_beta_binomial2 <- function(i, prep) {
-  mu <- brms::get_dpar(prep, "mu", i = i)
-  phi <- brms::get_dpar(prep, "phi", i = i)
-  trials <- prep$data$vint1[i]
-  y <- prep$data$Y[i]
-  beta_binomial2_lpmf(y, mu, phi, trials)
-}
-
-# Define function for posterior_predict
-posterior_predict_beta_binomial2 <- function(i, prep, ...) {
-  mu <- brms::get_dpar(prep, "mu", i = i)
-  phi <- brms::get_dpar(prep, "phi", i = i)
-  trials <- prep$data$vint1[i]
-  beta_binomial2_rng(mu, phi, trials)
-}
-
-# Define function for posterior_epred
-posterior_epred_beta_binomial2 <- function(prep) {
-  mu <- brms::get_dpar(prep, "mu")
-  trials <- prep$data$vint1
-  trials <- matrix(trials, nrow = nrow(mu), ncol = ncol(mu), byrow = TRUE)
-  mu * trials
-}
-
-
-
-# Setup a custom theme for the plot ----------------------------------------
-
[…]

### 2023-05-02 code/04_code_figures/appendix1_figureS1.R

@@ -1,0 +1,279 @@
+# ==========================================================================
+
+#                Code to produce Appendix 1 : Figure S1                    #
+
+# ==========================================================================
+
+
+
+
+
+# ==========================================================================
+# 1. Prepare script
+# ==========================================================================
+
+
+# Load libraries and models ------------------------------------------------
+
+library(brms)
+library(data.table)
+library(ggplot2)
+library(ggpubr)
+
+path <- file.path(getwd(), "outputs", "01_outputs_models")
+
+fit1 <- readRDS(file.path(path, "A2_GAMM-prey.rds"))
+
+
+
+# Load the data ------------------------------------------------------------
+
+data <- fread("./data/FraserFrancoetal2023-data.csv",
+              select = c("predator_id",
+                         "game_duration",
+                         "pred_speed",
+                         "prey_avg_speed",
+                         "cumul_xp_pred",
+                         "total_xp_pred",
+                         "hunting_success"))
+
+data[, predator_id := as.factor(predator_id)]
+
+
+
+# Post processing preparations for custom family ---------------------------
+
+expose_functions(fit1, vectorize = TRUE)
+
+# Define the log likelihood function
+log_lik_beta_binomial2 <- function(i, prep) {
+  mu <- brms::get_dpar(prep, "mu", i = i)
+  phi <- brms::get_dpar(prep, "phi", i = i)
+  trials <- prep$data$vint1[i]
+  y <- prep$data$Y[i]
+  beta_binomial2_lpmf(y, mu, phi, trials)
+}
+
+# Define function for posterior_predict
+posterior_predict_beta_binomial2 <- function(i, prep, ...) {
+  mu <- brms::get_dpar(prep, "mu", i = i)
+  phi <- brms::get_dpar(prep, "phi", i = i)
+  trials <- prep$data$vint1[i]
+  beta_binomial2_rng(mu, phi, trials)
+}
+
+# Define function for posterior_epred
+posterior_epred_beta_binomial2 <- function(prep) {
+  mu <- brms::get_dpar(prep, "mu")
+  trials <- prep$data$vint1
+  trials <- matrix(trials, nrow = nrow(mu), ncol = ncol(mu), byrow = TRUE)
+  mu * trials
+}
+
+
+
+# Setup a custom theme for the plot ----------------------------------------
+
+custom_theme <- theme(
+  # axis values size
+  axis.text = element_text(face = "plain",
+                           size = 14,
+                           color = "black"),
[…]

### 2023-05-02 manuscript/Chapter2-manuscript.Rmd
modifications du MS et notes pour revamp

@@
 
+parler du % de joueurs qui ont eu une augmentation vs % qui ont eu une diminution
+
 ## Effect of experience on the development of behavioural specialization
@@
 At the population level, predators did not change their mean speed with experience (i.e.
-intercept of the mean predator speed; Table 2).
+intercept of the mean predator speed; Table 2 and Appendix S1: Figure S3).
 Moreover, there was no directional increase in foraging flexibility or specialization with experience.
@@
 # DISCUSSION
+
+retravailler ici pour moins faire comme si il y avait un gros cluster. C'est surtout un continuum.
 
@@
 path <- file.path(here::here("outputs", "02_outputs_model-validation"))
-loo_tab <- data.table(readRDS(file.path(path, "A1-3_lootable.rds")))
+loo_tab <- data.table(readRDS(file.path(path, "A1-3_loo-cv-table.rds")))
 
 # Add model column
-loo_tab[, model := c("Group-level smoothers only",
-                     "Global smoother + group-level smoothers",
-                     "Global smoother only")]
+loo_tab[
+  , model := c(
+    "prey speed + group-level smoothers",
+    "predator xp + prey speed + group-level smoothers",
+    "group-level smoothers",
+    "predator xp + group-level smoothers",
+    "predator xp"
+    )
+ ]
 
@@
     value = as_paragraph(
-      "* 'elpd' refers to the expected log pointwise density and is the value chosen to select the best model."),
+      as_sup("a "),
+      "'elpd' refers to the expected log pointwise density and is the value chosen to select the best model.",
+      as_sup("\nb "),
+      "'xp' is an acronym for experience"),
     ref_symbols = " "
@@
   set_caption(
-    caption = "Table 1. Leave-one-out cross-validation table of the three hierarchical GAMMs relating hunting success to player experience.",
+    caption = "Table 1. Leave-one-out cross-validation table of the five hierarchical GAMMs relating hunting success to player experience.",
     style = "Table Caption"
@@
 tab1
-
-# ===========================================================================
-# ===========================================================================
-
-```
-
-\newpage
-
-```{r table2, ft.align = "left"}
-
-# ===========================================================================
-# 1. Import the model fit
-# ===========================================================================
-
-# path
-path <- file.path(here::here("outputs"))
-
-# Import the model
-fit <- readRDS(
-  file.path(path, "01_outputs_models", "B1_DHMLM-no-outlier.rds")
-)
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 2. Fixed effects table
-# ===========================================================================
-
-# Prepare the table ---------------------------------------------------------
-
-# Extract the fixed effects from the model
-eff_tab <- data.table(fixef(fit), keep.rownames = TRUE)
-eff_tab <- eff_tab[, c(1, 2, 4:5)]
-
-# Rename variables
-setnames(
-  eff_tab,
-  c("rn", "Q2.5", "Q97.5"),
-  c("parameter", "lower_ci", "upper_ci")
-)
-
-# Add a column that specifies the experience level
-eff_tab[parameter %like% "novice", xp_level := "novice"]
-eff_tab[parameter %like% "interm", xp_level := "intermediate"]
-eff_tab[parameter %like% "advanced", xp_level := "advanced"]
-
-# Back transform success
-eff_tab[
-  parameter %like% "success",
-  c(2:4) := lapply(.SD, function(x) {plogis(x)}),
-  .SDcols = c(2:4)
-]
-
-# Back transform sigma
-eff_tab[
-  parameter %like% "sigma",
-  c(2:4) := lapply(.SD, function(x) {exp(x)}),
-  .SDcols = c(2:4)
-]
-
-# Round values to 3 digits
-eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 2)]
-
-# Reorganize the table ------------------------------------------------------
-
-# reorder columns, and then rows based on xp level
-eff_tab <- eff_tab[, c(5, 1:4)]
-setorder(
-  eff_tab,
-  cols = -"xp_level"
-)
-
-# Create trait column
-eff_tab[
-  , trait := rep(c(
-    "predator speed", "predator speed",
-    "prey speed", "prey speed", "hunting success"),
-    6
-  )
-]
-
-# Rename parameter
-eff_tab[
-   , parameter := rep(
-      c(
-         rep(c("intercept (mean)", "intercept (sigma)"), 2),
-         "intercept (mean)",
-         rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
-         "match duration (mean)"
-      ),
-      3
-   )
-]
-
-# Paste upper and lower ci with estimate
-eff_tab[, estimate := paste(format(Estimate, digits = 2), "(")]
-eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
-eff_tab[, estimate := paste(estimate, ",", sep = "")]
-eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
-eff_tab[, estimate := paste(estimate, ")", sep = "")]
-eff_tab[, c("Estimate", "lower_ci", "upper_ci") := NULL]
-
-# Reshape
-eff_tab <- dcast(
-  eff_tab,
-  trait + parameter ~ xp_level,
-  value.var = "estimate"
-)
-
-# Reorder columns
-eff_tab <- eff_tab[, c(1, 2, 5, 4, 3)]
-
-# Reorder rows
-table <- eff_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]
-
-# Because I can't align hunting success properly
-table[10, 1] <- " "
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 3. Create the table using flextable
-# ===========================================================================
-
-# Prepare the table parameters ----------------------------------------------
-
-# Custom header
-my_header <- data.frame(
-  col_keys = c("trait", "parameter",
-               "novice", "intermediate", "advanced"),
-  line1 = c("Trait",
-            "Parameter",
-            "Novice",
-            "Intermediate",
-            "Advanced"),
-  stringsAsFactors = FALSE
-)
-
-# Custom theme
-my_theme <- function(x, ...) {
-  x <- colformat_double(x, big.mark = " ",
-                        decimal.mark = ".",
-                        digits = 2)
-  x <- border_remove(x)
-  std_border <- fp_border(width = 1, color = "black")
-  x <- hline_top(x, part = "all", border = std_border)
-  x <- hline_bottom(x, part = "all", border = std_border)
-  x <- width(x, j = 1, width = 2.84, unit = "cm")
-  x <- width(x, j = 2, width = 3.78, unit = "cm")
-  x <- width(x, j = c(3:5), width = 3.3, unit = "cm")
-}
-
-# Create the table ----------------------------------------------------------
-
-tab2 <-
-
-  # table structure
-  table %>%
-  select(trait, parameter,
-         novice, intermediate, advanced) %>%
-  flextable(col_keys = my_header$col_keys) %>%
-  set_header_df(mapping = my_header, key = "col_keys") %>%
-  my_theme() %>%
-
-  # Align repeated rows on column 1
-  merge_v(j = 1) %>%
-  valign(j = 1, valign = "top", part = "body") %>%
-
-  # Align text
-  align(align = "left", part = "all", j = 1) %>%
-  align(align = "left", part = "all", j = 2) %>%
-  align(align = "center", part = "all", j = 3) %>%
-  align(align = "center", part = "all", j = 4) %>%
-  align(align = "center", part = "all", j = 5) %>%
-
-  # Footnote
-  footnote(
-    i = 1, j = 1,
-    part = "header",
-    value = as_paragraph(
-      as_sup("a "),
-      "We exponentiated the dispersion parameters (i.e.
-sigma) which are estimated on a log scale.
-We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale.",
-      as_sup("\nb "),
-      "The intercept values on the mean part of the equation for all traits indicate mean behaviour and success at the population level.
-The intercept values on the dispersion (i.e.
-sigma) part of the equation for predator speed indicate behavioural specialization at the population level."
-    ),
-    ref_symbols = " "
-  ) %>%
-
-  # Table caption
-  set_caption(
-    caption = "Table 2. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
-    style = "Table Caption"
-  ) %>%
-
-  # Font options
-  font(fontname = "Times New Roman", part = "all") %>%
-  fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer")
-
-tab2
-
-# ===========================================================================
-# ===========================================================================
-
-```
-
-\newpage
-
-```{r table3, ft.align = "left"}
-
-# ===========================================================================
-# 1. Import the model fit
-# ===========================================================================
-
-# path
-path <- file.path(here::here("outputs"))
-
-# Import the model
-fit <- readRDS(
-  file.path(path, "01_outputs_models", "B1_DHMLM-no-outlier.rds")
-)
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 2. Random effects table
-# ===========================================================================
-
-# Prepare data --------------------------------------------------------------
-
-# Extract the random effect variances
-sd_draws <- data.table(
-   as_draws_df(
-      fit, variable = "^sd_", regex = TRUE
-   )
-)
-
-sd_draws[, c(28:30) := NULL]
-
-# Calculate parameters -------------------------------------------------------
-
-# Take the exponent of sigma parameters
-sd_draws[
-   , c("sd_predator_id__sigma_speednovice_Intercept",
-       "sd_predator_id__sigma_speedinterm_Intercept",
-       "sd_predator_id__sigma_speedadvanced_Intercept",
-       "sd_predator_id__sigma_preyspeednovice_Intercept",
-       "sd_predator_id__sigma_preyspeedinterm_Intercept",
-       "sd_predator_id__sigma_preyspeedadvanced_Intercept"
-   )
-   := lapply(.SD, function(x) {exp(x)}),
-   .SDcols = c(
-      "sd_predator_id__sigma_speednovice_Intercept",
-      "sd_predator_id__sigma_speedinterm_Intercept",
-      "sd_predator_id__sigma_speedadvanced_Intercept",
-      "sd_predator_id__sigma_preyspeednovice_Intercept",
-      "sd_predator_id__sigma_preyspeedinterm_Intercept",
-      "sd_predator_id__sigma_preyspeedadvanced_Intercept"
-   )
-]
-
-# Reshape the table -----------------------------------------------------------
-
-ranef_tab <- melt(
-   sd_draws,
-   variable.name = "parameter"
-)
-
-# Summarize the values (means + 95% CI) --------------------------------------
-
-# Intervals
-lower_interval <- function(x) {
-  coda::HPDinterval(as.mcmc(x), 0.95)[1]
-}
-upper_interval <- function(x) {
-  coda::HPDinterval(as.mcmc(x), 0.95)[2]
-}
-
-# Summarize values
-ranef_tab[, ":=" (mean = mean(value),
-                  lower_ci = lower_interval(value),
-                  upper_ci = upper_interval(value)),
-          by = .(parameter)]
-
-ranef_tab <- unique(ranef_tab[, .(parameter, mean, lower_ci, upper_ci)])
-ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], digits = 2)]
-
-# Rearrange the table --------------------------------------------------------
-
-# Add a column that specifies the experience level
-ranef_tab[parameter %like% "novice", xp_level := "novice"]
-ranef_tab[parameter %like% "interm", xp_level := "intermediate"]
-ranef_tab[parameter %like% "advanced", xp_level := "advanced"]
-
-# Paste upper and lower ci with estimate
-ranef_tab[, estimate := paste(format(mean, digits = 2), "(")]
-ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
-ranef_tab[, estimate := paste(estimate, ",", sep = "")]
-ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
-ranef_tab[, estimate := paste(estimate, ")", sep = "")]
-ranef_tab[, c("mean", "lower_ci", "upper_ci") := NULL]
-
-# Parameter column
-ranef_tab[
-   , parameter1 := ifelse(
-       parameter %like% "predator_id__sigma",
-       "predator ID (sigma)",
-       "predator ID (mean)"
-   )
-]
-ranef_tab[parameter %like% "avatar", parameter1 := "avatar (mean)"]
-ranef_tab[parameter %like% "env", parameter1 := "environment (mean)"]
-
-# Trait column
-ranef_tab[
-   , trait := ifelse(
-       parameter %like% "preyspeed",
-       "prey speed",
-       "predator speed"
-   )
-]
-ranef_tab[parameter %like% "success", trait := "hunting success"]
-
-# Remove old parameter column and replace by new
-ranef_tab[, parameter := NULL]
-setnames(ranef_tab, "parameter1", "parameter")
-
-# Reshape
-ranef_tab <- dcast(
-   ranef_tab,
-   trait + parameter ~ xp_level,
-   value.var = "estimate"
-)
-
-# Reorder columns
-ranef_tab <- ranef_tab[, c(1, 2, 5, 4, 3)]
-
-# Reorder rows
-table <- ranef_tab[c(2:9, 1)]
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 3. Create the table using flextable
-# ===========================================================================
-
-# Prepare the table parameters ----------------------------------------------
-
-# Custom header
-my_header <- data.frame(
-  col_keys = c("trait", "parameter",
-               "novice", "intermediate", "advanced"),
-  line1 = c("Trait",
-            "Parameter",
-            "Novice",
-            "Intermediate",
-            "Advanced"),
-  stringsAsFactors = FALSE
-)
-
-# Custom theme
-my_theme <- function(x, ...) {
-  x <- colformat_double(x, big.mark = " ",
-                        decimal.mark = ".",
-                        digits = 2)
-  x <- set_table_properties(x, layout = "autofit")
-  x <- border_remove(x)
-  std_border <- fp_border(width = 1, color = "black")
-  x <- hline_top(x, part = "all", border = std_border)
-  x <- hline_bottom(x, part = "all", border = std_border)
-}
-
-# Create the table ----------------------------------------------------------
-
-tab3 <-
-
-  # table structure
-  table %>%
-  select(trait, parameter,
-         novice, intermediate, advanced) %>%
-  flextable(col_keys = my_header$col_keys) %>%
-  set_header_df(mapping = my_header, key = "col_keys") %>%
-  my_theme() %>%
-
-  # Align repeated rows on column 1
-  merge_v(j = 1) %>%
-  valign(j = 1, valign = "top", part = "body") %>%
-  # font
-  fontsize(size = 10, part = "all") %>%
-  font(fontname = "Times New Roman", part = "all") %>%
-
-  # Align text
-  align(align = "left", part = "all", j = 1) %>%
-  align(align = "left", part = "all", j = 2) %>%
-  align(align = "center", part = "all", j = 3) %>%
-  align(align = "center", part = "all", j = 4) %>%
-  align(align = "center", part = "all", j = 5) %>%
-
-  # Add footnote
-  footnote(
-    i = 1, j = 1,
-    part = "header",
-    value = as_paragraph(
-      as_sup("a "),
-      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
-      as_sup("\nb "),
-      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
-      as_sup("\nc "),
-      "The intercept values on the dispersion (i.e.
-sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization.
-For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
-    ),
-    ref_symbols = " "
-  ) %>%
-
-  # Add table caption
-  set_caption(
-    caption = "Table 3. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
-    style = "Table Caption"
-  ) %>%
-
-  # Font options
-  font(fontname = "Times New Roman", part = "all") %>%
-  fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer")
-
-tab3
-
 # ===========================================================================

### 2023-05-02 code/04_code_figures/figure4-c.R
update fig4. appendix1 fig S4 is now within fig4

@@ -101,11 +101,11 @@ tab[, c(2:8) := round(tab[, c(2:8)], digits = 2)]
 
 
 names <- c(
-  "(mean speed, IIV speed)", "(mean speed, mean prey speed)",
-  "(IIV speed, mean prey speed)", "(mean speed, IIV prey speed)",
-  "(IIV speed, IIV prey speed)", "(mean prey speed, IIV prey speed)",
-  "(mean speed, mean success)", "(IIV speed, mean success)",
-  "(mean prey speed, mean success)", "(IIV prey speed, mean success)"
+  "mean speed\n IIV speed", "mean speed\n mean prey speed",
+  "IIV speed\n mean prey speed", "mean speed\n IIV prey speed",
+  "IIV speed\n IIV prey speed", "mean prey speed\n IIV prey speed",
+  "mean speed\n mean success", "IIV speed\n mean success",
+  "mean prey speed\n mean success", "IIV prey speed\n mean success"
 )
 tab[, variable_adv := names]
 
@@ -137,46 +137,47 @@ fig <- ggplot(
     yintercept = 0, linewidth = 1, colour = "red",
     linetype = "dashed", alpha = 0.5
   ) +
-  #geom_pointrange(
-  #  aes(ymin = lower_ci_95, ymax = upper_ci_95),
-  #  size = 0.5, position = position_dodge(width = 0.8)
-  #) +
   geom_linerange(
     aes(ymin = lower_ci_95,
         ymax = upper_ci_95,
         color = "0.95"),
-    size = 1,
+    linewidth = 1,
     key_glyph = "path"
-    ) +
+  ) +
   geom_linerange(
     aes(ymin = lower_ci_80,
         ymax = upper_ci_80,
         color = "0.80"),
-    size = 1,
+    linewidth = 1,
     key_glyph = "path"
-    ) +
+  ) +
   geom_linerange(
     aes(ymin = lower_ci_50,
         ymax = upper_ci_50,
         color = "0.50"),
-    size = 1,
+    linewidth = 1,
     key_glyph = "path"
-    ) +
+  ) +
   geom_point(size = 3, color = "black") +
-  ylab("\nPosterior median difference") +
+  ylab("Posterior median difference\n") +
   scale_y_continuous(breaks = seq(-0.2, 0.2, 0.1)) +
   scale_color_manual(
     name = "Density:",
-    values = colors) +
-  coord_flip() +
+    values = colors
+  ) +
   theme_bw() +
   theme(
-    axis.title.y = element_blank(),
[…]

### 2023-05-02 code/04_code_figures/figure4-raw.R

@@ -127,7 +127,7 @@
 
   # Export to powerpoint
  graph2ppt(
-    file = file.path(path, "05_figure3raw-test.pptx"),
+    file = file.path(path, "figure4-raw.pptx"),
     width = 10, height = 6
  )
 
@@ -146,7 +146,7 @@
 
  # add 2nd slide
  graph2ppt(
-    file = file.path(path, "05_figure3raw-test.pptx"),
+    file = file.path(path, "figure4-raw.pptx"),
     width = 10, height = 6, append = TRUE
  )
 
@@ -165,7 +165,7 @@
 
  # add 3rd slide
  graph2ppt(
-    file = file.path(path, "05_figure3raw-test.pptx"),
+    file = file.path(path, "figure4-raw.pptx"),
     width = 10, height = 6, append = TRUE
  )
 

### 2023-05-02 manuscript/Chapter2-appendix1.Rmd
update appendix 1

--- 2023-04-27 manuscript/Chapter2-appendix1.Rmd
@@
   word_document:
-    reference_docx: Chapter2-styles.docx
+    reference_docx: Chapter2-styles-appendix.docx
     fig_caption: yes
@@
 
+Journal name : Ecology
+
+Authors : Maxime Fraser Franco, Francesca Santostefano, Julien G. A. Martin, Clint D. Kelly, Pierre-Olivier Montiglio
+
 \newpage
 
-```{r tableprep, include = FALSE}
+```{r tableS1, ft.align = "left"}
 
 # ===========================================================================
-# 1. Extract the fixed effects from the MV model
+# 1. Import the model fit
 # ===========================================================================
 
-# Prepare the table ---------------------------------------------------------
+# path
+path <- file.path(here::here("outputs"))
 
-# Model fit
+# Import the model
 fit <- readRDS(
-  here::here("outputs", "01_outputs_models", "B2_DHMLM.rds")
+  file.path(path, "01_outputs_models", "B1_DHMLM-no-outlier.rds")
 )
-
-# Fixed effects table
-results <- data.table(
-  round(summary(fit)$fixed, digits = 2)[, 1:4],
-  keep.rownames = TRUE
-)
-
-setnames(results, "rn", "parameter")
-
-results[parameter %like% "predspeed", trait := "predator speed"][
-  parameter %like% "preyavgspeed", trait := "prey speed"][
-    parameter %like% "success", trait := "hunting success"
-  ]
-
-# mu parameters table
-tabs1 <- results[
-    !(parameter %like% "sigma"),
-    c(6, 1, 2, 4, 5)
-]
-
-# sigma parameters table
-tabs2 <- results[
-    parameter %like% "sigma",
-    c(6, 1, 2, 4, 5)
-]
-
-# Rename parameter values ---------------------------------------------------
-
-# Rename
-tabs1[,
-  parameter := c(
-    rep(
-      c("prey rank",
-        "cumulative experience",
-        "group 1",
-        "group 4",
-        "group 2",
-        "group 3"),
-      2
-    ),
-      c("game duration",
-        "cumulative experience",
-        "group 1",
-        "group 4",
-        "group 2",
-        "group 3")
-  )
-]
-# Reorder rows
-tabs1 <- tabs1[
-  c(1:3, 5, 6, 4,
-    7:9, 11, 12, 10,
-    13:15, 17, 18, 16)
-]
-
-# Rename
-tabs2[,
-  parameter := rep(
-    c("prey rank",
-      "cumulative experience",
-      "group 1",
-      "group 4",
-      "group 2",
-      "group 3"),
-    2
-  )
-]
-
-# Reorder
-tabs2 <- tabs2[
-  c(1:3, 5, 6, 4,
-    7:9, 11, 12, 10)
-]
 
@@
 # ===========================================================================
-# 2. Compute the table using flextable
+# 2. Fixed effects table
+# ===========================================================================
+
+# Prepare the table ---------------------------------------------------------
+
+# Extract the fixed effects from the model
+eff_tab <- data.table(fixef(fit), keep.rownames = TRUE)
+eff_tab <- eff_tab[, c(1, 2, 4:5)]
+
+# Rename variables
+setnames(
+  eff_tab,
+  c("rn", "Q2.5", "Q97.5"),
+  c("parameter", "lower_ci", "upper_ci")
+)
+
+# Add a column that specifies the experience level
+eff_tab[parameter %like% "novice", xp_level := "novice"]
+eff_tab[parameter %like% "interm", xp_level := "intermediate"]
+eff_tab[parameter %like% "advanced", xp_level := "advanced"]
+
+# Back transform success
+eff_tab[
+  parameter %like% "success",
+  c(2:4) := lapply(.SD, function(x) {plogis(x)}),
+  .SDcols = c(2:4)
+]
+
+# Back transform sigma
+eff_tab[
+  parameter %like% "sigma",
+  c(2:4) := lapply(.SD, function(x) {exp(x)}),
+  .SDcols = c(2:4)
+]
+
+# Round values to 3 digits
+eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 2)]
+
+# Reorganize the table ------------------------------------------------------
+
+# reorder columns, and then rows based on xp level
+eff_tab <- eff_tab[, c(5, 1:4)]
+setorder(
+  eff_tab,
+  cols = -"xp_level"
+)
+
+# Create trait column
+eff_tab[
+  , trait := rep(c(
+    "predator speed", "predator speed",
+    "prey speed", "prey speed", "hunting success"),
+    6
+  )
+]
+
+# Rename parameter
+eff_tab[
+   , parameter := rep(
+      c(
+         rep(c("intercept (mean)", "intercept (sigma)"), 2),
+         "intercept (mean)",
+         rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
+         "match duration (mean)"
+      ),
+      3
+   )
+]
+
+# Paste upper and lower ci with estimate
+eff_tab[, estimate := paste(format(Estimate, digits = 2), "(")]
+eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
+eff_tab[, estimate := paste(estimate, ",", sep = "")]
+eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
+eff_tab[, estimate := paste(estimate, ")", sep = "")]
+eff_tab[, c("Estimate", "lower_ci", "upper_ci") := NULL]
+
+# Reshape
+eff_tab <- dcast(
+  eff_tab,
+  trait + parameter ~ xp_level,
+  value.var = "estimate"
+)
+
+# Reorder columns
+eff_tab <- eff_tab[, c(1, 2, 5, 4, 3)]
+
+# Reorder rows
+table <- eff_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]
+
+# Because I can't align hunting success properly
+table[10, 1] <- " "
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 3. Create the table using flextable
 # ===========================================================================
@@
 my_header <- data.frame(
-   col_keys = c("trait",
-                "parameter",
-                "Estimate",
-                "l-95% CI",
-                "u-95% CI"),
+  col_keys = c("trait", "parameter",
+               "novice", "intermediate", "advanced"),
   line1 = c("Trait",
             "Parameter",
-             "Value",
-             "lower 95% CI",
-             "upper 95% CI"),
+            "Novice",
+            "Intermediate",
+            "Advanced"),
   stringsAsFactors = FALSE
@@
                         digits = 2)
-   x <- set_table_properties(x, layout = "fixed")
   x <- border_remove(x)
@@
   x <- hline_bottom(x, part = "all", border = std_border)
-   autofit(x)
+  x <- width(x, j = 1, width = 2.84, unit = "cm")
+  x <- width(x, j = 2, width = 3.78, unit = "cm")
+  x <- width(x, j = c(3:5), width = 3.3, unit = "cm")
 }
 
-```
-
-```{r tables1, ft.align = "left"}
 # Create the table ----------------------------------------------------------
 
-tabs1f <- tabs1 %>%
+tab1 <-
+
+  # table structure
+  table %>%
+  select(trait, parameter,
+         novice, intermediate, advanced) %>%
   flextable(col_keys = my_header$col_keys) %>%
@@
   my_theme() %>%
+
+  # Align repeated rows on column 1
   merge_v(j = 1) %>%
   valign(j = 1, valign = "top", part = "body") %>%
-  align(align = "left", part = "all", j = c(1, 2)) %>%
+
+  # Align text
+  align(align = "left", part = "all", j = 1) %>%
+  align(align = "left", part = "all", j = 2) %>%
   align(align = "center", part = "all", j = 3) %>%
@@
   align(align = "center", part = "all", j = 5) %>%
+
+  # Footnote
   footnote(
@@
       as_sup("a "),
-      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299 (i.e. group in the main text)"
+      "We exponentiated the dispersion parameters (i.e.
+sigma) which are estimated on a log scale.
+We back-transformed the hunting success values, estimated on a logit scale, back to a probability scale.",
+      as_sup("\nb "),
+      "The intercept values on the mean part of the equation for all traits indicate mean behaviour and success at the population level.
+The intercept values on the dispersion (i.e.
+sigma) part of the equation for predator speed indicate behavioural specialization at the population level."
     ),
@@
   ) %>%
+
+  # Table caption
   set_caption(
-    tabs1,
-    caption = "Table S1. Fixed effects table on the mean part of the DHMLM comparing random groups of players with different matches played to the group presented in the main text.",
+    caption = "Table S1. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
     style = "Table Caption"
   ) %>%
+
+  # Font options
+  font(fontname = "Times New Roman", part = "all") %>%
   fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer") %>%
-  font(fontname = "Times New Roman", part = "all")
+  fontsize(size = 12, part = "footer")
 
-tabs1f
+tab1
 
@@
 
-tabs2f <- tabs2 %>%
+# ===========================================================================
+# 1. Import the model fit
+# ===========================================================================
+
+# path
+path <- file.path(here::here("outputs"))
+
+# Import the model
+fit <- readRDS(
+  file.path(path, "01_outputs_models", "B1_DHMLM-no-outlier.rds")
+)
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 2. Random effects table
+# ===========================================================================
+
+# Prepare data --------------------------------------------------------------
+
+# Extract the random effect variances
+sd_draws <- data.table(
+   as_draws_df(
+      fit, variable = "^sd_", regex = TRUE
+   )
+)
+
+sd_draws[, c(28:30) := NULL]
+
+# Calculate parameters -------------------------------------------------------
+
+# Take the exponent of sigma parameters
+sd_draws[
+   , c("sd_predator_id__sigma_speednovice_Intercept",
+       "sd_predator_id__sigma_speedinterm_Intercept",
+       "sd_predator_id__sigma_speedadvanced_Intercept",
+       "sd_predator_id__sigma_preyspeednovice_Intercept",
+       "sd_predator_id__sigma_preyspeedinterm_Intercept",
+       "sd_predator_id__sigma_preyspeedadvanced_Intercept"
+   )
+   := lapply(.SD, function(x) {exp(x)}),
+   .SDcols = c(
+      "sd_predator_id__sigma_speednovice_Intercept",
+      "sd_predator_id__sigma_speedinterm_Intercept",
+      "sd_predator_id__sigma_speedadvanced_Intercept",
+      "sd_predator_id__sigma_preyspeednovice_Intercept",
+      "sd_predator_id__sigma_preyspeedinterm_Intercept",
+      "sd_predator_id__sigma_preyspeedadvanced_Intercept"
+   )
+]
+
+# Reshape the table -----------------------------------------------------------
+
+ranef_tab <- melt(
+   sd_draws,
+   variable.name = "parameter"
+)
+
+# Summarize the values (means + 95% CI) --------------------------------------
+
+# Intervals
+lower_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[1]
+}
+upper_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+# Summarize values
+ranef_tab[, ":=" (mean = mean(value),
+                  lower_ci = lower_interval(value),
+                  upper_ci = upper_interval(value)),
+          by = .(parameter)]
+
+ranef_tab <- unique(ranef_tab[, .(parameter, mean, lower_ci, upper_ci)])
+ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], digits = 2)]
+
+# Rearrange the table --------------------------------------------------------
+
+# Add a column that specifies the experience level
+ranef_tab[parameter %like% "novice", xp_level := "novice"]
+ranef_tab[parameter %like% "interm", xp_level := "intermediate"]
+ranef_tab[parameter %like% "advanced", xp_level := "advanced"]
+
+# Paste upper and lower ci with estimate
+ranef_tab[, estimate := paste(format(mean, digits = 2), "(")]
+ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
+ranef_tab[, estimate := paste(estimate, ",", sep = "")]
+ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
+ranef_tab[, estimate := paste(estimate, ")", sep = "")]
+ranef_tab[, c("mean", "lower_ci", "upper_ci") := NULL]
+
+# Parameter column
+ranef_tab[
+   , parameter1 := ifelse(
+       parameter %like% "predator_id__sigma",
+       "predator ID (sigma)",
+       "predator ID (mean)"
+   )
+]
+ranef_tab[parameter %like% "avatar", parameter1 := "avatar (mean)"]
+ranef_tab[parameter %like% "env", parameter1 := "environment (mean)"]
+
+# Trait column
+ranef_tab[
+   , trait := ifelse(
+       parameter %like% "preyspeed",
+       "prey speed",
+       "predator speed"
+   )
+]
+ranef_tab[parameter %like% "success", trait := "hunting success"]
+
+# Remove old parameter column and replace by new
+ranef_tab[, parameter := NULL]
+setnames(ranef_tab, "parameter1", "parameter")
+
+# Reshape
+ranef_tab <- dcast(
+   ranef_tab,
+   trait + parameter ~ xp_level,
+   value.var = "estimate"
+)
+
+# Reorder columns
+ranef_tab <- ranef_tab[, c(1, 2, 5, 4, 3)]
+
+# Reorder rows
+table <- ranef_tab[c(2:9, 1)]
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 3. Create the table using flextable
+# ===========================================================================
+
+# Prepare the table parameters ----------------------------------------------
+
+# Custom header
+my_header <- data.frame(
+  col_keys = c("trait", "parameter",
+               "novice", "intermediate", "advanced"),
+  line1 = c("Trait",
+            "Parameter",
+            "Novice",
+            "Intermediate",
+            "Advanced"),
+  stringsAsFactors = FALSE
+)
+
+# Custom theme
+my_theme <- function(x, ...) {
+  x <- colformat_double(x, big.mark = " ",
+                        decimal.mark = ".",
+                        digits = 2)
+  x <- set_table_properties(x, layout = "autofit")
+  x <- border_remove(x)
+  std_border <- fp_border(width = 1, color = "black")
+  x <- hline_top(x, part = "all", border = std_border)
+  x <- hline_bottom(x, part = "all", border = std_border)
+}
+
+# Create the table ----------------------------------------------------------
+
+tab2 <-
+
+  # table structure
+  table %>%
+  select(trait, parameter,
+         novice, intermediate, advanced) %>%
   flextable(col_keys = my_header$col_keys) %>%
@@
   my_theme() %>%
+
+  # Align repeated rows on column 1
   merge_v(j = 1) %>%
   valign(j = 1, valign = "top", part = "body") %>%
-  align(align = "left", part = "all", j = c(1, 2)) %>%
+  # font
+  fontsize(size = 10, part = "all") %>%
+  font(fontname = "Times New Roman", part = "all") %>%
+
+  # Align text
+  align(align = "left", part = "all", j = 1) %>%
+  align(align = "left", part = "all", j = 2) %>%
   align(align = "center", part = "all", j = 3) %>%
@@
   align(align = "center", part = "all", j = 5) %>%
+
+  # Add footnote
   footnote(
@@
       as_sup("a "),
-      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299 (i.e. group in the main text)"
+      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
+      as_sup("\nb "),
+      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
+      as_sup("\nc "),
+      "The intercept values on the dispersion (i.e.
+sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization.
+For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
     ),
@@
   ) %>%
+
+  # Add table caption
   set_caption(
-    tabs2,
-    caption = "Table S2. Fixed effects table on the dispersion part of the DHMLM comparing random groups of players with different matches played to the group presented in the main text.",
+    caption = "Table S2. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
     style = "Table Caption"
   ) %>%
+
+  # Font options
+  font(fontname = "Times New Roman", part = "all") %>%
   fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer") %>%
-  font(fontname = "Times New Roman", part = "all")
+  fontsize(size = 12, part = "footer")
 
-tabs2f
+tab2
+
+# ===========================================================================
+# ===========================================================================
 
@@
 ```
-
-```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Distribution of the intra individual behavioural variation (i.e.
-specialization) of predators with the greatest increase in hunting success (A and B) and greatest decrease (C and D) in hunting success when they were novices (A and C) and then (B and D) advanced hunters."}
-
-knitr::include_graphics(
-  here::here(
-    "outputs", "04_outputs_figures",
-    "appendix1_figureS2.png"
-  )
-)
-
-```
-
-```{r figS3, out.width = "100%", fig.cap = "**Figure S3.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
-The test is displayed on the y axis (i.e.
-whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis.
-Each panel represent the experience level groups that are being compared."}
-
-knitr::include_graphics(
-  here::here(
-    "outputs", "04_outputs_figures",
-    "appendix1_figureS3.png"
-  )
-)
-
-```
-
-```{r figS4, out.width = "80%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice.
-The difference is displayed on the x axis and the parameter correlations are displayed on the y axis."}
-
-knitr::include_graphics(
-  here::here(
-    "outputs", "04_outputs_figures",
-    "appendix1_figureS4.png"
-  )
-)
-
-```

### 2023-05-02 manuscript/Chapter2-appendix2.Rmd
new appendix 2

--- 2023-04-23 manuscript/Chapter2-SupInfo.Rmd
@@
 title: |
-     Online supporting information for \
-     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame
+     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame: \
+     Appendix 2
 
@@
   word_document:
-    reference_docx: Chapter2-styles.docx
+    reference_docx: Chapter2-styles-appendix.docx
     fig_caption: yes
-bibliography: references.bib
+bibliography: references2.bib
 csl: ecology.csl
@@
 
+Journal name : Ecology
+
+Authors : Maxime Fraser Franco, Francesca Santostefano, Julien G. A. Martin, Clint D. Kelly, Pierre-Olivier Montiglio
+
 \newpage
@@
 
-```{r tables1, ft.align = "left"}
+```{r tableS1, ft.align = "left"}
 # Create the table ----------------------------------------------------------
@@
 ```
-
-\newpage
-
-```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Among individual differences in the development of hunting expertise.
-The predators' hunting success (i.e.
-the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e.
-the number of matches played prior to each observation) is on the x axis.
-Each fitted curve represents an individual predator.
-(A) Individuals with the greatest increase in hunting success with experience (B) Individuals with the greatest decrease in hunting success with experience."}
-
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS1.png"))
-
-```
-
-```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Distribution of the intra individual behavioural variation (i.e.
-specialization) of predators with the greatest increase in hunting success (A and B) and greatest decrease (C and D) in hunting success when they were novices (A and C) and then (B and D) advanced hunters."}
-
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS2.png"))
-
-```
-
-```{r figS4, out.width = "100%", fig.cap = "**Figure S4.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
-The test is displayed on the y axis (i.e.
-whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis.
-Each panel represent the experience level groups that are being compared."}
-
-knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figureS4.png"))
-
-```

### 2023-05-02 manuscript/Chapter2-appendix3.Rmd
update appendix 3

@@
 ```
+
+Journal name : Ecology
+
+Authors : Maxime Fraser Franco, Francesca Santostefano, Julien G. A. Martin, Clint D. Kelly, Pierre-Olivier Montiglio
 

### 2023-05-02 manuscript/Chapter2-manuscript.Rmd
update appendix 3

@@
 
+need to redo the results and change all figure and table references
+
 ## Effect of experience on hunting success
@@
 
-**Figure 2.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
+**Figure 2.** Posterior median differences and credible intervals comparing the parameter values predicted by the MDHGLM between each predator experience level.
+Each panel represent the experience levels that are compared.
+The parameter being compared is displayed on the y axis (e.g.
+whether the standard deviation of predator ID on the mean differs when the population was intermediate vs novice), and the difference is displayed on the x axis.
+
+**Figure 3.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
 The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
@@
 
-**Figure 3.** Correlation matrices of the MDHGLM relating the mean and intra individual variability (IIV) in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+**Figure 4.** Correlation matrices of the MDHGLM relating the mean and intra individual variability (IIV) in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
 Larger dark blue circles indicate stronger positive correlations (positive values on the color legend), while larger dark red circles indicate stronger negative correlations (negative values on the color legend).
 A) Correlations when predators were novice hunters.
-B) Correlations when predators were at an intermediate level of experience.
-C) Correlations when predators were advanced hunters.
+B) Correlations when predators were advanced hunters.
+C) Posterior median differences and credible intervals comparing the correlations between traits when predators were advanced vs novice.
+The median difference is displayed on the x axis and the trait correlations being compared are displayed on the y axis.
 
@@
 ```
+
+\newpage
+
+```{r fig4, out.width = "100%", fig.cap = "**Figure 4**"}
+
+knitr::include_graphics(
+  here::here("outputs", "04_outputs_figures", "figure4.png")
+)
+
+```

### 2023-05-03 code/04_code_figures/figure1.R
update fig1

@@ -76,31 +76,6 @@
    mu * trials
  }
 
-
-
-# Setup a custom theme for the plot ----------------------------------------
-
- custom_theme <- theme(
-    # axis values size
-    axis.text = element_text(face = "plain",
-                             size = 14,
-                             color = "black"),
-    # axis ticks lenght
-    axis.ticks.length = unit(.15, "cm"),
-    # axis ticks width
-    axis.ticks = element_line(linewidth = 0.90,
-                              color = "black"),
-    # axis titles size
-    axis.title = element_text(size = 16,
-                              face = "plain",
-                              color = "black"),
-    axis.line = element_line(linewidth = 0.95,
-                             color = "black"),
-    legend.position = "none",
-    panel.grid = element_blank(),
-    panel.background = element_blank()
- )
-
 # ==========================================================================
 # ==========================================================================
 
@@ -214,6 +189,31 @@
  tabA2_prey_a <- tabA2_prey_a[cumul_xp <= total_xp_pred, ]
  tabA3_prey <- tabA3_prey[cumul_xp <= total_xp_pred, ]
 
+ 
+ 
+# Setup a custom theme for the plot ----------------------------------------
+ 
+ custom_theme <- theme(
+   # axis values size
+   axis.text = element_text(face = "plain",
+                            size = 14,
+                            color = "black"),
+   # axis ticks lenght
+   axis.ticks.length = unit(.15, "cm"),
+   # axis ticks width
+   axis.ticks = element_line(linewidth = 0.90,
+                             color = "black"),
+   # axis titles size
+   axis.title = element_text(size = 16,
+                             face = "plain",
+                             color = "black"),
+   axis.line = element_line(linewidth = 0.95,
+                            color = "black"),
+   legend.position = "none",
+   panel.grid = element_blank(),
+   panel.background = element_blank()
+ )
+
 
 
 # Produce the plot --------------------------------------------------------
@@ -278,7 +278,8 @@
      aes(label = paste("y =", round(min(tabA2_prey_b$estimate__ / 4), digits = 2)),
          y = min(tabA2_prey_b$estimate__ / 4) + 0.15,
          x = min(tabA2_prey_b$Zcumul_xp) + 0.5),
-     color = "#5ec962"
+     color = "#5ec962",
+     size = 5
      ) +
    geom_vline(
[…]

### 2023-05-03 manuscript/Chapter2-manuscript.Rmd
update MS fig1

@@
 The first recorded match was played on `r toString(format(min(dat$date)))` and the last one on `r toString(format(max(dat$date)))`.
-We cleaned and filtered the raw data to produce a dataset appropriate for our analyses.
 We analyzed only matches where players did not know each other (i.e.
@@
 The following information is collected and reported for every match : the player's anonymous ID, its avatar (i.e.
-the predator character chosen with its specific powers-gameplay mechanics), the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.
+the predator character chosen with its specific skill-gameplay mechanics), the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.
 
@@
 For instance, these players may already be used to play videogames, and thus, could differ in the way they play at early stages of their experience in the game.
-To ensure that our sample was not biased, the videogame company provided a random sample of players that played between 20 and 50 matches, between 51 and 100 matches, and between 101 and 300 matches from the same timeframe as our current sample.
+To ensure that our sample was not biased, we compared a random sample of players that played between 20 and 50 matches, between 51 and 100 matches, and between 101 and 300 matches from the same timeframe with our sampled population.
 We then took the first 20 matches played by these players, including those from our sampled population, and compared their average behaviour using a Bayesian hierarchical linear model.
-We found that neither of the four groups differed in their average speed (Table SX), which gives us confidence that our player population was not biased.
+We found that neither of the four groups differed in their average speed (Appendix 2: Table S1-S2), which gives us confidence that our player population was not biased.
 
@@
 
-We tested whether predators varied in the development of their expertise using three Bayesian generalized additive mixed models (GAMM) with thin plate regression splines.
+We tested whether predators varied in the development of their expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin plate regression splines.
 These models estimate the relationship between hunting success (i.e.
@@
 Thus, this model assumes that predators do not share a common relationship between success and experience.
-We included match duration as a covariate in all three models.
+The fourth and fifth model were a reproduction of the second and third model respectively, where we also included the prey group's average speed to assess their effect on the relationship between success and experience.
+We included match duration as a covariate in all five models.
 
-Because a maximum of four prey can be captured in the game, and to control for overdispersion, we computed the three models using a modified version of the beta-binomial distribution implemented in "brms".
+Because a maximum of four prey can be captured in the game, and to control for overdispersion, we computed the five models using a modified version of the beta-binomial distribution implemented in "brms".
 Thus, hunting success was estimated as the probability of capturing the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
@@
 We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$).
-We used Gaussian priors for the game duration ($N(0,\ 1)$), the intercept ($N(0,\ 0.5)$), and the precision paremeter ($N(2,\ 0.5)$).
-We employed the default Student t priors for the smoothing parameter ($t(3,\ 0,\ 2.5)$).
-After fitting the three models, we proceeded to select the one with the best predictive accuracy using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
+We used Gaussian weakly informative priors for the intercept ($N(0,\ 0.5)$) and the global trend of cumulative experience ($N(0,\ 2)$).
+Based on previous results [@FraserFranco.etal2022], we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system.
+We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0, 0.5)$).
+We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
 
@@
 For each level of experience (i.e.
-novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model) and, by using a heterogeneous structure of the residuals, the intra-individual standard deviation of speed for every individual (which we call the dispersion part of the model).
-Thus, in the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e.
+novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and by explicitly modelling the residuals, the intra-individual standard deviation of speed for every individual (which we call the dispersion part of the model).
+In the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e.
 along the slow-fast continuum), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization/flexibility (i.e.
-intra-individual variability).
-We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the prey groups encountered by predators.
+intra-individual variability, IIV).
+We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the groups of prey encountered by predators.
 For the mean part of the model, it allows us to test whether individual predators differed in the average speed of the groups of prey encountered across the study.
@@
 if resource heterogeneity was higher for some individuals compared to others).
-For hunting success, we only modeled the mean part of the equation to estimate among individual differences in mean prey capture.
+For hunting success, we modeled the mean part of the equation to estimate among individual differences in mean prey capture.
 For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered as proxy for prey skills on both the mean and dispersion part of the equation.
@@
 We used the mean rank of the four prey and applied a square-root transformation.
-For the predator's hunting success, we controlled for the square-root of the duration of the match.
+For the predator's hunting success, we controlled for the square-root of the game duration.
 
@@
 In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible.
-In the second case, the correlations enables us to estimate, for example, whether predators that encountered prey that were faster/slower adopted a slower/faster (or more specialized/flexible) tactic, or if slower/faster predators had lower/greater hunting success.
+In the second case, it enables us to estimate, for example, whether predators that adopted a slower/faster (or more specialized/flexible) tactic encountered prey that were faster/slower, or if slower/faster predators had lower/greater hunting success.
 As a complement, the model also estimated correlations among the different levels of experience (e.g.
@@
 The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each of three developmental stages.
-We present the character-state analyses as additional material in the Appendix S2 as they were not part of our initial objectives.
+We present the character-state analyses in the Appendix S4 as they were not part of our initial objectives.
 
@@
 We parameterized equations 1.1 to 2.2 with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation 3 (predator hunting success).
-We used Gaussian priors for the prey rank ($N(2.5,\ 1)$) and game duration ($N(10,\ 2)$) on the mean part of the model (equations 1.1, 2.1, and 3), and the default priors in "brms" for the dispersion part (equations 1.2 and 2.2).
-We used the default Student t priors in "brms" for the intercepts on the mean and dispersion part of the model.
-For hunting success, we applied a Gaussian prior on the precision parameter ($N(2,\ 1)$).
-For every predicted variable, we applied a half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part of the model (equations 1.1, 2.1, and 3), and the default "brms" Student t prior for the dispersion part of the model (equations 1.2 and 2.2).
+We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1)$) and game duration ($N(0.5,\ 0.5)$) on the mean (equations 1.1, 2.1, and 3) and on the dispersion part of the model (equations 1.2 and 2.2).
+We used a weakly informative Gaussian prior ($N(0,\ 1)$) for the intercepts on the mean and dispersion part of the model.
+For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1)$).
+For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part and the dispersion part of the model.
+We used a regularizing $LKJ(2)$ prior on the correlation matrix.
+
+After inspection of the results, we found that many parameters values were in the direction of our predictions, but they were largely driven by the very slow speed of one individual predator.
+Removing this individual reduced the estimates by a significant margin.
+To remain conservative, we thus present the results of the model without this individual in the main text, and provide the results of the model including it in the Appendix S3.
 
@@
 
-Our results confirm that individual predators display substantial differences in the development of their expertise, as the best model included group-level smoothers exclusively (Table I).
-For instance, some predators steadily increased (Figure 1A, Appendix S1: Figure S1A), while others decreased (Figure 1A, Appendix S1: Figure S1B), their hunting success with greater experience, and others whose success did not change with experience (Figure 1A).
-Another pattern that emerged was that some individuals optimized their success at an experience level that was below what we considered "advanced" (i.e.
->300 matches played).
+Out of all five models, the two that best predicted the data, with an almost identical expected log pointwise density (elpd), were the model with group-level smoothers exclusively while controlling for prey speed and the model including a global smoother of predator experience along with group-level smoothers and prey speed (Table 1).
+Thus, prey speed was an important predictor of the predators' hunting success.
+
+Our results confirm that predators differ substantially in the relationship between hunting success and cumulative experience (i.e.
+expertise: Figure 1A-B).
+For instance, the success of some predators steadily increased with experience (Figure 1B, Appendix S1: Figure S1A) while others showed a decrease in success with experience (Figure 1B, Appendix S1: Figure S1B).
+Overall, `r toString(scales::percent(191/253))` of the population displayed a >10% increase in hunting success, `r toString(scales::percent(37/253))` displayed a >10% decrease in hunting success, and the remaining `r toString(scales::percent(25/253))` had a lesser change in success ranging between -10% and +10%.
 
 We predicted that the relationship between hunting success and experience would vary among predators because they should differ in the type of prey that they encounter.
-However, after controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained stable (Figure 1B).
-
-parler du % de joueurs qui ont eu une augmentation vs % qui ont eu une diminution
+After controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained important (Figure 1A-B).
+However, many individual curves appear to be shifted upwards in the model where we control for prey speed (Figure 1B) vs in the model where we do not control for prey speed (Figure 1A).
+Moreover, in the models where we did not account for prey speed, the global trend of predator experience was nearly flat (results not shown).
+Yet, we see that there is an increase up to 13% in the probability of capturing all prey with experience in the population when we account for prey speed (Figure 1C).
+The maximum is attained around match 340 (i.e.
+advanced state).
+Prey speed was thus important in mediating the population and individual-level relationship between success and experience, but does appear to influence among individual differences in this relationship.
 
@@
 whether the standard deviation of predator ID on the mean differs when the population was intermediate vs novice), and the difference is displayed on the x axis.
+*développer pour expliquer mean et sigma réfère à quoi.
+prendre la légende du tableau en appendix 1*
 

### 2023-05-04 manuscript/Chapter2-manuscript.Rmd
update MS

@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics or on different prey irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@Kernaleguen.etal2015;@Phillips.etal2017].
-A growing body of evidence suggests that reciprocal interactions between predators and prey could drive this individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
-For instance, predators often hunt using techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their capacity to use them effectively is contingent on periods of extensive practice (i.e.
+Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@Kernaleguen.etal2015;@Phillips.etal2017].
+These individual behavioural differences have consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a], but the mechanisms underlying them remain unclear.
+A growing body of evidence suggests that reciprocal interactions between predators and prey could drive individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
+For instance, predators often hunt using techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their refinement is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
+Thus, the capacity of effectively using hunting tactics should be contingent on periods of extensive practice (i.e.
 experience).
-While hunting experience may be essential to maintain or improve foraging success, we have few empirical assessments of its role in predator foraging specialization [@Dukas2019] and its consequences on predator-prey interactions.
 
-The development of foraging tactics is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
-Theory predicts that foraging specialization may emerge via learning, limitations in memorizing multiple complex hunting skills, and expertise [@Tinker.etal2009;@Dukas2019].
+Theory predicts that foraging specialization may emerge via learning and expertise [@Tinker.etal2009;@Dukas2019].
 @Dukas2019 defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
-It is described as the relationship between success and cumulative experience, where extensive practice optimizes success when individuals reach an advanced level of experience.
-Empirical studies on human and non-human hunters show that experience optimizes the efficiency (e.g.
-search and handling times, return rates) of their foraging tactics potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
+It is described as the relationship between success and experience, where extensive practice optimizes success when individuals reach an advanced level of experience.
+Empirical studies on human and non-human hunters show that experience optimizes foraging efficiency (e.g.
+search and handling times, return rates) potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
 This body of work suggests that such optimization may thus promote individual foraging specialization (e.g.
-repeatedly using fast attacks) if the success of a hunting tactic is constant each time a prey is encountered.
-It may also be costly to attempt different hunting tactics by trial and error when prey are scarce or highly unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
-Alternatively, the costs/risks faced by hunters when switching foraging tactics may be offset through extensive practive, as individuals gain experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
+repeatedly using fast attacks) if the success of a tactic is constant through time.
+It may also be costly to test different tactics by trial and error when prey are scarce or unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
+Alternatively, the costs/risks faced by hunters when switching tactics may be offset through extensive practice, as individuals gain experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
@@
 specialization and flexibility) operating at the same time within a predator population.
-For instance, some individuals may constantly encounter faster prey, which are proven to be more difficult to hunt in simulation and empirical studies [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-Thus, whether predators specialize or increase their flexibility with experience, learning to adjust their tactic to their prey should be essential to optimize their success.
+For instance, some individuals may hunt in habitats where prey are faster, which are often proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
+It should thus be essential for predators to learn how to match their tactic to their prey to optimize their success.
 
@@
 For instance, some studies report increasing benefits of specialization [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
-This may in part be due to the limited information we have on the ecological contexts favouring specialization over flexibility in nature.
-However, in predator-prey systems, many studies have outlined that fluctuations in the predictability of resources throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
+This may in part be due to the limited information we have on the ecological contexts favoring specialization over flexibility.
+However, in predator-prey systems, many studies suggest that fluctuations in the predictability of resources throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
 The resource-predictability (or resource-heterogeneity) hypothesis argues that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
-In contrast, individual generalists should benefit when resources fluctuate, as fine adjustments to resources are key for a predator's success and survival [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-When predator-prey interactions are directly observed, empirical evidence shows that predators often match their locomotor and behavioural traits to those of their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
+In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
+There is now clear empirical evidence showing that predators match their locomotor and behavioural traits to those of their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
 Yet, a recurring question emerging from these studies is whether the mechanism driving such behavioural adjustments by predators involves individual differences in experience/learning [@Kelley.Magurran2011].
-Thus, uncovering the role of learning in predator-prey systems where interactions are directly monitored would enable researchers to better predict the behavioural decisions and the success of predators when they are hunting.
+Thus, uncovering the role of learning during direct predator-prey interactions would help in better predicting the behavioural decisions and the success of predators when they are hunting.
 
-The integration of individual behavioural variation in the study of predator-prey interactions has gained traction in recent years, with empirical studies revealing important consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
-However, an important and recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
-We recently demonstrated, using an online predator-prey videogame called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge and help uncover the mechanisms that shape predator-prey interactions [@FraserFranco.etal2022].
+A recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
+We recently demonstrated, using an online predator-prey videogame called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge [@FraserFranco.etal2022].
 In this dynamic virtual system, four prey players need to forage for resources while avoiding a predator player.
 The prey can contribute to the group's success by healing or helping others escape the predator, or be selfish and attempt to escape by themselves [@Cere.etal2021].
-The predators' hunting tactics and their success are largely driven by the movement of the prey, where faster prey are more difficult to capture [@FraserFranco.etal2022].
+The predators' hunting tactics and success are driven by the movement of the prey [@FraserFranco.etal2022].
 Predators should thus benefit from learning how the prey behave to be successful.
-Other studies using virtual predator-prey systems show that predation regimes drives individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
+Other virtual predator-prey studies show that predation regimes drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
 in prep).
@@
 They also generate large volumes of data on interacting players throughout their lifetime in the game under realistic ecological scenarios.
-Hence, virtual systems offer the opportunity to tackle fundamental questions about the role of experience and prey behaviour on individual predator foraging specialization and performance.
+Hence, virtual systems offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
 
@@
 Third, we evaluate how predator foraging specialization emerges from behavioural interactions with the prey.
-Whether predators specialize or not with experience should depend on the behaviour of their prey.
-We expect predators that experienced more predictable encounters with their prey to specialize, while predators that experienced unpredictable encounters with their prey should adopt a flexible hunting strategy.
+We expect predators that experienced more predictable encounters with their prey to specialize, while predators that experienced unpredictable encounters with their prey should adopt a flexible hunting tactic.
 If we detect such prey-dependent fine-tuning, then specialist and flexible hunters should attain equal success because both should have learned to optimize their hunting style to their prey.
@@
 The resources are in the form of power generators that, once all activated, will enable the prey to escape through one of two exit doors.
-The composition of the predator and prey group for a match is determined by a skill-based matchmaking algorithm.
+The composition of the predator and prey group in a match is determined by a skill-based matchmaking algorithm.
 A match ends when the predator kills all the prey available (i.e.
@@
 bold vs cautious prey, or ambush vs roaming predator).
-During our study period, the game offered 23 predator avatars.
-The virtual environment where matches take place is composed of fixed and procedurally generated habitat components, such as vegetation, mazes, and buildings.
+During our study period, the game offered `r toString(format(length(unique(dat$avatar_id))))` predator avatars.
+The virtual environments are composed of fixed and procedurally generated habitat components, such as vegetation, mazes, and buildings.
 Some of these environments are larger than others, with varying structural complexity.
 However, predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling them to have visual cues of the generators [@FraserFranco.etal2022].
-There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during our study period.
+There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during the study period.
 
@@
 We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$).
-We used Gaussian weakly informative priors for the intercept ($N(0,\ 0.5)$) and the global trend of cumulative experience ($N(0,\ 2)$).
+We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5)$) and the global trend of cumulative experience ($N(0,\ 2)$).
 Based on previous results [@FraserFranco.etal2022], we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system.
@@
 We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
-We categorized the predators by their experience based on the number of matches they played (i.e.
-their cumulative experience).
+We categorized predators by their experience based on the number of matches they played.
 Since we monitored all predator players throughout their experience, they appeared in all of the three following experience categories.
@@
 For each level of experience (i.e.
-novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and by explicitly modelling the residuals, the intra-individual standard deviation of speed for every individual (which we call the dispersion part of the model).
-In the mean part of the model, we could estimate among individual differences in the foraging tactic used by predators (i.e.
-along the slow-fast continuum), while in the dispersion part of the model, we could estimate among individual differences in foraging specialization/flexibility (i.e.
+novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and by explicitly modelling the residuals, the intra-individual standard deviation of speed of every individual (which we call the dispersion part of the model).
+From the mean part of the model, we could infer on among individual differences in the foraging tactic used by predators (i.e.
+along the slow-fast continuum), while in the dispersion part of the model, we could infer on among individual differences in foraging specialization (i.e.
 intra-individual variability, IIV).
 We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the groups of prey encountered by predators.
-For the mean part of the model, it allows us to test whether individual predators differed in the average speed of the groups of prey encountered across the study.
+For the mean part, it allows us to test whether individual predators differed in the average speed of the groups of prey encountered across the study.
 For the dispersion part, it allows us to test whether individual predators differed in the (dis)similarity of the groups of prey encountered across the study (i.e.
 if resource heterogeneity was higher for some individuals compared to others).
-For hunting success, we modeled the mean part of the equation to estimate among individual differences in mean prey capture.
-For the predator and the prey's speed, we controlled for the average rank of the prey that they encountered as proxy for prey skills on both the mean and dispersion part of the equation.
+We controlled for the square-root of the average rank of the prey that predators encountered as proxy for prey skills for the predator and the prey's speed (on both the mean and dispersion).
 The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank).
-We used the mean rank of the four prey and applied a square-root transformation.
-For the predator's hunting success, we controlled for the square-root of the game duration.
+For hunting success, we modeled the mean part of the equation to estimate among individual differences in mean prey capture and controlled for the square-root of the game duration.
 
@@
 The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively.
-On the mean part of the model, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$ and $av \sim N(0,\ I\ \sigma_{av})$).
+On the mean part, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$ and $av \sim N(0,\ I\ \sigma_{av})$).
 $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
 The residuals are assumed to follow a Gaussian distribution ($e \sim N(0,\ \sigma_{e})$).
-On the dispersion part of the model, the residuals vary among individuals, allowing us to estimate among individual differences in specialization.
+On the dispersion part, the residuals vary among individuals, allowing us to estimate among individual differences in specialization.
 The individual identity random effects on both the mean and dispersion parts follow a multivariate Gaussian distribution $[\begin{array}{cc} id_m \\ id_d \end{array}] \sim MVN(0,\ \Sigma_{id})$ where $\Sigma_{id}$ is a 15x15 variance-covariance matrix.
@@
 We parameterized equations 1.1 to 2.2 with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation 3 (predator hunting success).
-We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1)$) and game duration ($N(0.5,\ 0.5)$) on the mean (equations 1.1, 2.1, and 3) and on the dispersion part of the model (equations 1.2 and 2.2).
-We used a weakly informative Gaussian prior ($N(0,\ 1)$) for the intercepts on the mean and dispersion part of the model.
-For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1)$).
+We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1)$: eqn.
+1.1 to 2.2) and game duration ($N(0.5,\ 0.5)$: eqn.
+3).
+Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3, 0.5)$: eqn.
+1.1 and 2.1).
+Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,1)$: eqn 1.2 and 2.2).
+For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1)$: eqn.
+3) and a negative Gaussian prior ($N(-4, 1)$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration.
 For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part and the dispersion part of the model.
@@
 We parametrized every model described above to run four MCMC chains with 1000 posterior samples for each parameter.
-We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table I), and 1500 iterations with a thinning set to four for the additive model with global and group-level smoothers and for the additive model with group-level smoothers only (Table I).
-We set the first 500 iterations in each model as warmups.
-We parametrized the MDHGLM to run 2500 iterations with a thinning set to 8, with the first 500 iterations used as warmups.
-We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 for the bulk-ESS and tail-ESS [@Vehtari.etal2021a].
+We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table 1), and 1500 iterations with a thinning set to four for the other additive models.
+We set the first 500 iterations in each model as warm ups.
+We parametrized the MDHGLM to run 2500 iterations with a thinning set to eight, with the first 500 iterations used as warm ups.
+We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@Vehtari.etal2021a].
 We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
@@
 
-need to redo the results and change all figure and table references
+## Effect of experience on hunting success
 
-## Effect of experience on hunting success
+*revérifier cette section rapidement si ça marche toujours*
 
@@
 After controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained important (Figure 1A-B).
-However, many individual curves appear to be shifted upwards in the model where we control for prey speed (Figure 1B) vs in the model where we do not control for prey speed (Figure 1A).
+However, many individual curves appear to have shifted upwards in the model where we control for prey speed (Figure 1B) vs in the model where we do not control for prey speed (Figure 1A).
 Moreover, in the models where we did not account for prey speed, the global trend of predator experience was nearly flat (results not shown).
 Yet, we see that there is an increase up to 13% in the probability of capturing all prey with experience in the population when we account for prey speed (Figure 1C).
-The maximum is attained around match 340 (i.e.
-advanced state).
-Prey speed was thus important in mediating the population and individual-level relationship between success and experience, but does appear to influence among individual differences in this relationship.
 
@@
 
+*refaire cette section et couper si possible. figures et tables doivent être changées*
+
 At the population level, predators did not change their mean speed with experience (i.e.
-intercept of the mean predator speed; Table 2 and Appendix S1: Figure S3).
+intercept of the mean predator speed; Figure 1 and Appendix S1: Table 1).
 Moreover, there was no directional increase in foraging flexibility or specialization with experience.
-Indeed, the observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e.
+The observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e.
 intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S3), but then return to novice-levels of flexibility with advanced experience (i.e.
@@
 
-## Relationship between behavioural specialization and prey variability
+## Relationship between behavioural specialization and prey behaviour
 
@@
 
-retravailler ici pour moins faire comme si il y avait un gros cluster. C'est surtout un continuum.
+*retravailler ici pour moins faire comme si il y avait un gros cluster. C'est surtout un continuum.*
+
+*The maximum is attained around match 340 (i.e.
+advanced state).
+Prey speed was thus important in mediating the population and individual-level relationship between success and experience, but does appear to influence among individual differences in this relationship.*
 

### 2023-05-08 manuscript/Chapter2-manuscript.Rmd
updated MS to shorten some sentences. updated intro. notes still there

@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics irrespective of sexual, morphological, or age-related differences [@Estes.etal2003;@Tinker.etal2008;@Kernaleguen.etal2015;@Phillips.etal2017].
-These individual behavioural differences have consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a], but the mechanisms underlying them remain unclear.
-A growing body of evidence suggests that reciprocal interactions between predators and prey could drive individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
-For instance, predators often hunt using techniques that are fine-tuned to the type of prey that they encounter [@Davoren.etal2003;@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their refinement is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
-Thus, the capacity of effectively using hunting tactics should be contingent on periods of extensive practice (i.e.
-experience).
+Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics, with consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
+Despite the clear evidence that individual specialization is important for predator-prey interactions, its underlying mechanisms remain surprisingly unclear.
+However, it has recently been suggested that reciprocal interactions between predators and prey could drive individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
+For instance, predators often hunt using techniques that are fine-tuned to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their refinement is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
+Thus, the capacity of predators to effectively use hunting tactics should be contingent on periods of extensive practice (i.e.
+experience), which may result in different foraging specializations.
 
-Theory predicts that foraging specialization may emerge via learning and expertise [@Tinker.etal2009;@Dukas2019].
+Theory predicts that foraging specialization may emerge via learning and expertise acquisition [@Tinker.etal2009;@Dukas2019].
 @Dukas2019 defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
@@
 repeatedly using fast attacks) if the success of a tactic is constant through time.
-It may also be costly to test different tactics by trial and error when prey are scarce or unpredictable [@Dukas1998;@Estes.etal2003;@Mery.Burns2010].
+It may also be costly to test different tactics by trial and error when prey are scarce or unpredictable.
 Alternatively, the costs/risks faced by hunters when switching tactics may be offset through extensive practice, as individuals gain experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
@@
 This is reflected in the literature showing contrasting results in the links between specialization and fitness.
-For instance, some studies report increasing benefits of specialization [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
+Some studies report greater benefits when specializing [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
 This may in part be due to the limited information we have on the ecological contexts favoring specialization over flexibility.
-However, in predator-prey systems, many studies suggest that fluctuations in the predictability of resources throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Chang.etal2017;@Phillips.etal2017;@Courbin.etal2018].
-The resource-predictability (or resource-heterogeneity) hypothesis argues that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
-In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty [@Karkarey.etal2017;@Holm.etal2019;@Santoro.etal2019].
-There is now clear empirical evidence showing that predators match their locomotor and behavioural traits to those of their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022].
-Yet, a recurring question emerging from these studies is whether the mechanism driving such behavioural adjustments by predators involves individual differences in experience/learning [@Kelley.Magurran2011].
+However, in predator-prey systems, studies suggest that fluctuations in the predictability of resources throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017;@Courbin.etal2018].
+It is hypothesized that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
+In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty.
+While it is clear that predators can match their behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how?
+Given the dynamic nature of predator-prey interactions, it is unlikely that evolution alone could explain such behavioural adjustments by predators, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].
 Thus, uncovering the role of learning during direct predator-prey interactions would help in better predicting the behavioural decisions and the success of predators when they are hunting.
@@
 
-In this study, we test how hunting experience shapes predator foraging specialization using individual behavioural data from players in the online videogame *Dead by Daylight*.
+In this study, we test how hunting experience shapes predator foraging specialization using data from players in the online videogame *Dead by Daylight*.
 *DBD* simulates a direct predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
@@
 
-Because a maximum of four prey can be captured in the game, and to control for overdispersion, we computed the five models using a modified version of the beta-binomial distribution implemented in "brms".
-Thus, hunting success was estimated as the probability of capturing the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
+We computed the five models using a modified version of the beta-binomial distribution implemented in "brms".
+Hunting success was estimated as the probability of capturing the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
 We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link for all models.
-
 We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
@@
 
-We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@westneatBiologyHiddenResidual2014;@Mitchell.etal2016a;@ODea.etal2022].
 We categorized predators by their experience based on the number of matches they played.
@@
 
+We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
 For each level of experience (i.e.
 novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and by explicitly modelling the residuals, the intra-individual standard deviation of speed of every individual (which we call the dispersion part of the model).
-From the mean part of the model, we could infer on among individual differences in the foraging tactic used by predators (i.e.
+From the mean part of the model, we could infer on among individual differences in foraging tactics (i.e.
 along the slow-fast continuum), while in the dispersion part of the model, we could infer on among individual differences in foraging specialization (i.e.
 intra-individual variability, IIV).
-We followed the same structure for the preys' speed to estimate among individual differences in the mean and standard deviation of speed of the groups of prey encountered by predators.
-For the mean part, it allows us to test whether individual predators differed in the average speed of the groups of prey encountered across the study.
-For the dispersion part, it allows us to test whether individual predators differed in the (dis)similarity of the groups of prey encountered across the study (i.e.
+We followed the same structure for the preys' speed.
+For the mean part, we tested whether individual predators differed in the average speed of the groups of prey encountered across the study.
+For the dispersion part, we tested whether individual predators differed in how (dis)similar were the groups of prey they encountered across the study (i.e.
 if resource heterogeneity was higher for some individuals compared to others).
-We controlled for the square-root of the average rank of the prey that predators encountered as proxy for prey skills for the predator and the prey's speed (on both the mean and dispersion).
+We controlled for the square-root of the average rank of the prey group as proxy for prey skills for both the predator and the prey's speed (mean and dispersion).
 The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank).
-For hunting success, we modeled the mean part of the equation to estimate among individual differences in mean prey capture and controlled for the square-root of the game duration.
+For hunting success, we quantified among individual differences in mean prey capture and controlled for the square-root of the game duration.
 
@@
 In the second case, it enables us to estimate, for example, whether predators that adopted a slower/faster (or more specialized/flexible) tactic encountered prey that were faster/slower, or if slower/faster predators had lower/greater hunting success.
-As a complement, the model also estimated correlations among the different levels of experience (e.g.
-$cor(\sigma_{id_{m}\ pred\ novice}\ \sigma_{id_{d}\ pred\ intermediate})$).
-The latter "character-state" approach [@Via.Lande1985;@viaAdaptivePhenotypicPlasticity1995], enables us to investigate whether predators express similar behaviours across each of three developmental stages.
-We present the character-state analyses in the Appendix S4 as they were not part of our initial objectives.
 
@@
 
-After inspection of the results, we found that many parameters values were in the direction of our predictions, but they were largely driven by the very slow speed of one individual predator.
+After inspection of the results, we found that key parameter values were in the direction of our predictions, but they were largely driven by the very slow speed of one individual predator.
 Removing this individual reduced the estimates by a significant margin.
@@
 
-*revérifier cette section rapidement si ça marche toujours*
+*revérifier cette section rapidement si ça marche toujours. corriger le langage pour raccourcir sinon ça fait discussion un peu*
 
@@
 path <- file.path(here::here("outputs", "02_outputs_model-validation"))
-loo_tab <- data.table(readRDS(file.path(path, "A1-3_loo-cv-table.rds")))
+loo_tab <- data.table(readRDS(file.path(path, "GAMM_loo-cv-table.rds")))
 

### 2023-05-08 manuscript/Chapter2-appendix1.Rmd
notes on appendix 1
update appendix1

@@
 
+Update the plot legend to tell what is the *greatest increase*
+
 \newpage
@@
 
-# Extract the fixed effects from the model
-eff_tab <- data.table(fixef(fit), keep.rownames = TRUE)
-eff_tab <- eff_tab[, c(1, 2, 4:5)]
-
-# Rename variables
-setnames(
-  eff_tab,
-  c("rn", "Q2.5", "Q97.5"),
-  c("parameter", "lower_ci", "upper_ci")
+# Extract the fixed effects posterior samples
+b_draws <- data.table(
+  as_draws_df(
+    fit, variable = "^b_", regex = TRUE
+  )
 )
 
-# Add a column that specifies the experience level
-eff_tab[parameter %like% "novice", xp_level := "novice"]
-eff_tab[parameter %like% "interm", xp_level := "intermediate"]
-eff_tab[parameter %like% "advanced", xp_level := "advanced"]
+b_draws[, c(31:33) := NULL]
 
-# Back transform success
-eff_tab[
-  parameter %like% "success",
-  c(2:4) := lapply(.SD, function(x) {plogis(x)}),
-  .SDcols = c(2:4)
+# Back-transform the parameters ----------------------------------------------
+
+# Take the exponent of sigma parameters
+b_draws[
+  , c("b_sigma_speednovice_Intercept",
+      "b_sigma_speedinterm_Intercept",
+      "b_sigma_speedadvanced_Intercept",
+      "b_sigma_preyspeednovice_Intercept",
+      "b_sigma_preyspeedinterm_Intercept",
+      "b_sigma_preyspeedadvanced_Intercept",
+      "b_sigma_speednovice_sqrt_prey_avg_rank",
+      "b_sigma_speedinterm_sqrt_prey_avg_rank",
+      "b_sigma_speedadvanced_sqrt_prey_avg_rank",
+      "b_sigma_preyspeednovice_sqrt_prey_avg_rank",
+      "b_sigma_preyspeedinterm_sqrt_prey_avg_rank",
+      "b_sigma_preyspeedadvanced_sqrt_prey_avg_rank"
+  )
+  := lapply(.SD, function(x) {exp(x)}),
+  .SDcols = c(
+    "b_sigma_speednovice_Intercept",
+    "b_sigma_speedinterm_Intercept",
+    "b_sigma_speedadvanced_Intercept",
+    "b_sigma_preyspeednovice_Intercept",
+    "b_sigma_preyspeedinterm_Intercept",
+    "b_sigma_preyspeedadvanced_Intercept",
+    "b_sigma_speednovice_sqrt_prey_avg_rank",
+    "b_sigma_speedinterm_sqrt_prey_avg_rank",
+    "b_sigma_speedadvanced_sqrt_prey_avg_rank",
+    "b_sigma_preyspeednovice_sqrt_prey_avg_rank",
+    "b_sigma_preyspeedinterm_sqrt_prey_avg_rank",
+    "b_sigma_preyspeedadvanced_sqrt_prey_avg_rank"
+  )
 ]
 
-# Back transform sigma
-eff_tab[
-  parameter %like% "sigma",
-  c(2:4) := lapply(.SD, function(x) {exp(x)}),
-  .SDcols = c(2:4)
+# plogis for the success parameters
+# Take the exponent of sigma parameters
+b_draws[
+  , c("b_successnovice_Intercept",
+      "b_successinterm_Intercept",
+      "b_successadvanced_Intercept",
+      "b_successnovice_sqrt_game_duration",
+      "b_successinterm_sqrt_game_duration",
+      "b_successadvanced_sqrt_game_duration"
+  )
+  := lapply(.SD, function(x) {plogis(x)}),
+  .SDcols = c(
+    "b_successnovice_Intercept",
+    "b_successinterm_Intercept",
+    "b_successadvanced_Intercept",
+    "b_successnovice_sqrt_game_duration",
+    "b_successinterm_sqrt_game_duration",
+    "b_successadvanced_sqrt_game_duration"
+  )
 ]
 
-# Round values to 3 digits
-eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 2)]
+# Reshape the table -----------------------------------------------------------
 
-# Reorganize the table ------------------------------------------------------
+fixef_tab <- melt(
+  b_draws,
+  variable.name = "parameter"
+)
+
+# Summarize the values (medians + 95% CI) -------------------------------------
+
+# Intervals
+lower_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[1]
+}
+upper_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+# Summarize values
+fixef_tab[, ":=" (median = median(value),
+                  lower_ci = lower_interval(value),
+                  upper_ci = upper_interval(value)),
+          by = .(parameter)]
+
+fixef_tab <- unique(fixef_tab[, .(parameter, median, lower_ci, upper_ci)])
+fixef_tab[, c(2:4) := round(fixef_tab[, c(2:4)], digits = 2)]
+
+# Rearrange the table --------------------------------------------------------
+
+# Add a column that specifies the experience level
+fixef_tab[parameter %like% "novice", xp_level := "novice"]
+fixef_tab[parameter %like% "interm", xp_level := "intermediate"]
+fixef_tab[parameter %like% "advanced", xp_level := "advanced"]
+
+# Paste upper and lower ci with estimate
+fixef_tab[, estimate := paste(format(median, digits = 2), "(")]
+fixef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
+fixef_tab[, estimate := paste(estimate, ",", sep = "")]
+fixef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
+fixef_tab[, estimate := paste(estimate, ")", sep = "")]
+fixef_tab[, c("median", "lower_ci", "upper_ci") := NULL]
 
 # reorder columns, and then rows based on xp level
-eff_tab <- eff_tab[, c(5, 1:4)]
 setorder(
-  eff_tab,
+  fixef_tab,
   cols = -"xp_level"
@@
 # Create trait column
-eff_tab[
+fixef_tab[
   , trait := rep(c(
@@
 
-# Rename parameter
-eff_tab[
+# Rename parameter column
+fixef_tab[
   , parameter := rep(
@@
 
-# Paste upper and lower ci with estimate
-eff_tab[, estimate := paste(format(Estimate, digits = 2), "(")]
-eff_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
-eff_tab[, estimate := paste(estimate, ",", sep = "")]
-eff_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
-eff_tab[, estimate := paste(estimate, ")", sep = "")]
-eff_tab[, c("Estimate", "lower_ci", "upper_ci") := NULL]
-
 # Reshape
-eff_tab <- dcast(
-  eff_tab,
+fixef_tab <- dcast(
+  fixef_tab,
   trait + parameter ~ xp_level,
@@
 
-# Reorder columns
-eff_tab <- eff_tab[, c(1, 2, 5, 4, 3)]
-
-# Reorder rows
-table <- eff_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]
+# Reorder columns and rows
+fixef_tab <- fixef_tab[, c(1, 2, 5, 4, 3)]
+table <- fixef_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]
 
@@
   set_caption(
-    caption = "Table S1. Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    caption = "Table S1. Posterior medians and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
     style = "Table Caption"
@@
 # Summarize values
-ranef_tab[, ":=" (mean = mean(value),
+ranef_tab[, ":=" (median = median(value),
                   lower_ci = lower_interval(value),
@@
 
-ranef_tab <- unique(ranef_tab[, .(parameter, mean, lower_ci, upper_ci)])
+ranef_tab <- unique(ranef_tab[, .(parameter, median, lower_ci, upper_ci)])
 ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], digits = 2)]
@@
 # Paste upper and lower ci with estimate
-ranef_tab[, estimate := paste(format(mean, digits = 2), "(")]
+ranef_tab[, estimate := paste(format(median, digits = 2), "(")]
 ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
@@
 ranef_tab[, estimate := paste(estimate, ")", sep = "")]
-ranef_tab[, c("mean", "lower_ci", "upper_ci") := NULL]
+ranef_tab[, c("median", "lower_ci", "upper_ci") := NULL]
 
@@
       as_sup("\nb "),
-      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
+      "The standard deviation values on the mean part of the equation indicate, for all traits, among individual differences in mean behaviour, prey encountered, and success.",
       as_sup("\nc "),
-      "The intercept values on the dispersion (i.e.
-sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization.
-For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
+      "Values on the dispersion (i.e.
+sigma) for predator speed indicate among individual differences in behavioural specialization.
+For prey speed, they indicate among individual differences in the variability of prey encounters."
     ),
@@
   set_caption(
-    caption = "Table S2. Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    caption = "Table S2.
+Posterior medians and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
+All the reported values are standard deviations.",
     style = "Table Caption"

### 2023-05-09 manuscript/Chapter2-manuscript.Rmd
update manuscript

@@
 
-We recognize that we could have introduced a bias in our analyses since we sampled individuals who stayed in the game for at least 300 matches.
-For instance, these players may already be used to play videogames, and thus, could differ in the way they play at early stages of their experience in the game.
-To ensure that our sample was not biased, we compared a random sample of players that played between 20 and 50 matches, between 51 and 100 matches, and between 101 and 300 matches from the same timeframe with our sampled population.
-We then took the first 20 matches played by these players, including those from our sampled population, and compared their average behaviour using a Bayesian hierarchical linear model.
-We found that neither of the four groups differed in their average speed (Appendix 2: Table S1-S2), which gives us confidence that our player population was not biased.
-
-## Variables
-
 We analyzed the predator's average speed and the average speed of the prey group encountered by the predator.
@@
 For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.
+
+We recognize that we could have introduced a bias in our analyses since we sampled individuals who stayed in the game for at least 300 matches.
+For instance, these players may already be used to play videogames, and thus, could differ in the way they play at early stages of their experience in the game.
+To ensure that our sample was not biased, we compared a random sample of players that played between 20 and 50 matches, between 51 and 100 matches, and between 101 and 300 matches from the same timeframe with our sampled population.
+We then took the first 20 matches played by these players, including those from our sampled population, and compared their average behaviour using a Bayesian hierarchical linear model.
+We found that neither of the four groups differed in their average speed (Appendix 2: Table S1-S2), which gives us confidence that our player population was not biased.
 
@@
 
-We tested whether predators varied in the development of their expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin plate regression splines.
-These models estimate the relationship between hunting success (i.e.
+We tested whether predators varied in the development of their expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin plate regression splines, all of which estimated the relationship between hunting success (i.e.
 number of prey captured) and the predators' cumulative experience (i.e.
@@
 We parametrized the models following the method of @Pedersen.etal2019.
-The first model was the simplest, with a common global smoothing function for all observations and random intercepts for the predator ID.
+The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID.
 In this model, we assume that individuals have the same development of expertise, with the model estimating a trend for the average individual (i.e.
@@
 This allows each individual to have a unique relationship between success and experience without penalization by the global smoother.
-Thus, this model assumes that predators do not share a common relationship between success and experience.
-The fourth and fifth model were a reproduction of the second and third model respectively, where we also included the prey group's average speed to assess their effect on the relationship between success and experience.
+This model assumes that predators do not share a common relationship between success and experience.
+The fourth and fifth models were a reproduction of the second and third models respectively, where we included the prey group's average speed to assess its effect on the relationship between success and experience.
 We included match duration as a covariate in all five models.
@@
 Hunting success was estimated as the probability of capturing the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
-We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link for all models.
+We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link.
 We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
@@
 For each level of experience (i.e.
-novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and by explicitly modelling the residuals, the intra-individual standard deviation of speed of every individual (which we call the dispersion part of the model).
+novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and the intra-individual standard deviation of speed of every individual (which we call the dispersion part of the model).
 From the mean part of the model, we could infer on among individual differences in foraging tactics (i.e.
@@
 
-We estimated the correlation between the individual random effect on the mean and on the dispersion within each trait (e.g.
+The model estimated the correlation between the individual identity random effect on the mean and on the dispersion within each trait (e.g.
 $cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ pred})$) and among each trait (e.g.
@@
 
-After inspection of the results, we found that key parameter values were in the direction of our predictions, but they were largely driven by the very slow speed of one individual predator.
+After inspection of the results, we found that key parameter values for our hypotheses were in the direction of our predictions, but they were largely driven by the very slow speed of one predator.
 Removing this individual reduced the estimates by a significant margin.
@@
 
-We parametrized every model described above to run four MCMC chains with 1000 posterior samples for each parameter.
+We parametrized both the GAMMs and the MDHMLM to run four MCMC chains with 1000 posterior samples for each parameter.
 We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table 1), and 1500 iterations with a thinning set to four for the other additive models.
@@
 
-*revérifier cette section rapidement si ça marche toujours. corriger le langage pour raccourcir sinon ça fait discussion un peu*
-
-Out of all five models, the two that best predicted the data, with an almost identical expected log pointwise density (elpd), were the model with group-level smoothers exclusively while controlling for prey speed and the model including a global smoother of predator experience along with group-level smoothers and prey speed (Table 1).
-Thus, prey speed was an important predictor of the predators' hunting success.
-
-Our results confirm that predators differ substantially in the relationship between hunting success and cumulative experience (i.e.
+Out of all five models, the two that best predicted the data, with an almost identical expected log pointwise density (elpd), were the models that controlled for the prey group's speed (Table 1).
+Predators differed substantially in the relationship between hunting success and cumulative experience (i.e.
 expertise: Figure 1A-B).
 For instance, the success of some predators steadily increased with experience (Figure 1B, Appendix S1: Figure S1A) while others showed a decrease in success with experience (Figure 1B, Appendix S1: Figure S1B).
-Overall, `r toString(scales::percent(191/253))` of the population displayed a >10% increase in hunting success, `r toString(scales::percent(37/253))` displayed a >10% decrease in hunting success, and the remaining `r toString(scales::percent(25/253))` had a lesser change in success ranging between -10% and +10%.
+Overall, `r toString(scales::percent(191/253))` of the population displayed an >10% increase in hunting success, `r toString(scales::percent(37/253))` displayed a >10% decrease in hunting success, and the remaining `r toString(scales::percent(25/253))` had a lesser change in success ranging between -10% and +10%.
 
-We predicted that the relationship between hunting success and experience would vary among predators because they should differ in the type of prey that they encounter.
-After controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained important (Figure 1A-B).
+We predicted that the relationship between hunting success and experience would vary among predators because they should not encounter the same prey.
+After controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained important (Figure 1B).
 However, many individual curves appear to have shifted upwards in the model where we control for prey speed (Figure 1B) vs in the model where we do not control for prey speed (Figure 1A).
@@
 
-*refaire cette section et couper si possible. figures et tables doivent être changées*
+The mean speed of the predator population did not change with experience (i.e.
+intercept of predator speed (mean); Figure 2 and Appendix S1: Table S1).
+There was also strong evidence that foraging specialization in the population remained stable across experience levels (i.e.
+intercept of predator speed (sigma); Figure 2 and Appendix S1: Table S1).
 
-At the population level, predators did not change their mean speed with experience (i.e.
-intercept of the mean predator speed; Figure 1 and Appendix S1: Table 1).
-Moreover, there was no directional increase in foraging flexibility or specialization with experience.
-The observed pattern is more complex given that predators became more flexible with experience at intermediate levels of experience (i.e.
-intercept of sigma for predator speed is larger for intermediates than novices; Table 2 and Appendix S1: Figure S3), but then return to novice-levels of flexibility with advanced experience (i.e.
-intercept of sigma for predator speed is smaller for advanced players than intermediates; Table 2 and Appendix S1: Figure S3).
-Thus, our analyses suggest that population-level behavioural specialization changes nonlinearly (quadratic) with experience rather than linearly.
-
-At the individual level, we detected differences in the mean movement speed among predators (i.e.
-the intercept of the mean speed for the predator ID; Table 3).
-These differences remained stable from the novice to the intermediate stages, and then increased at the advanced stage to reach a level higher than when predators were novice (Table 3 and Appendix S1: Figure S3).
-Predators displayed considerable differences in their degree of hunting specialization, and these differences increased with experience (i.e.
-the intercept of sigma for the predator ID increases with experience; Table 3 and Appendix S1: Figure S3).
-Thus, as individual predators gain experience, the population becomes more heterogeneous, with an assemblage of both specialist and flexible hunters.
-Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 2).
+Individual predators differed slightly in their average movement speed, but differences did not increase at higher experience levels (i.e.
+predator ID (mean); Figure 2 and Appendix S1: Table S2).
+However, individuals displayed differences in their foraging specialization, with a 0.1 unit increase in standard deviation from novice to advanced (i.e.
+predator ID (sigma) is higher at the advanced level; Figure 2 and Appendix S1: Table S2).
+Thus, as individual predators gain experience, the population becomes slightly more heterogeneous along the specialist-flexible hunter continuum.
+Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 3).
 Importantly, 12.6% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
@@
 
-As we predicted, predators differed in the mean speed of the prey that they encountered across matches.
-Thus, some individuals encountered prey that were on average slower, while others encountered prey that where on average faster throughout the study period (i.e.
-the intercept of the mean prey speed for the predator ID; Table 3).
-These differences were greater when predators reached an advanced level of hunting experience (i.e.
-the intercept of the mean prey speed for the predator ID was higher at the advanced stage; Table 3 and Appendix S1: Figure S3).
-In addition, individuals differed in the heterogeneity of the groups of prey encountered across the study period.
-Hence, some predators encountered prey groups with similar average speeds, while others encountered prey groups with different average speeds throughout the study period (i.e.
-the intercept of sigma prey speed for the predator ID; Table 3).
+Contrary to predictions, there was strong evidence that predators did not differ in the speed of the prey groups that they encountered on average (i.e.
+predator ID (mean); Appendix S1: Table S2).
+Moreover, differences in standard deviation values across experience were negligible (i.e.
+predator ID (mean); Figure 2).
+However, individuals differed in the heterogeneity of the groups of prey encountered across the study period (i.e.
+predator ID (sigma); Appendix S1: Table S2).
+Hence, some predators encountered prey groups with similar average speeds, while others encountered prey groups with varying average speeds throughout the study period.
+The differences in the prey encountered among predators increased only slightly with experience (i.e.
+predator ID (sigma); Figure 2).
 
 ## Relationship between behavioural specialization and prey behaviour
+
+*continuer ici les modifications*
 
@@
 
-**Figure 2.** Posterior median differences and credible intervals comparing the parameter values predicted by the MDHGLM between each predator experience level.
-Each panel represent the experience levels that are compared.
-The parameter being compared is displayed on the y axis (e.g.
-whether the standard deviation of predator ID on the mean differs when the population was intermediate vs novice), and the difference is displayed on the x axis.
-*développer pour expliquer mean et sigma réfère à quoi.
-prendre la légende du tableau en appendix 1*
+**Figure 2.** Posterior median differences and credible intervals between each predator experience level's parameters.
+Each panel shows the experience levels that are compared.
+The parameter compared is on the y axis, and the difference of the values predicted by the MDHGLM is on the x axis.
+The intercepts correspond to mean population speed and specialization.
+The predator ID on the mean are individual differences in mean speed, mean speed of prey groups encountered, and success.
+The predator ID on the dispersion (i.e.
+sigma) are individual differences in specialization, and in the heterogeneity of prey encountered.
 

### 2023-05-09 code/04_code_figures/figure4-c.R
update code in fig4 c to add other y axis

@@ -129,6 +129,8 @@ colors <- c(
   "0.50" = "gray21"
 )
 
+scaleFUN <- function(x) sprintf("%.2f", x)
+
 fig <- ggplot(
   tab,
   aes(x = variable_adv, y = median_difference)
@@ -160,7 +162,14 @@ fig <- ggplot(
   ) +
   geom_point(size = 3, color = "black") +
   ylab("Posterior median difference\n") +
-  scale_y_continuous(breaks = seq(-0.2, 0.2, 0.1)) +
+  #scale_y_continuous(
+  #  labels = scaleFUN,
+  #  breaks = seq(-0.3, 0.3, 0.15),
+  #  limits = c(-0.3,0.3)
+  #  ) +
+  scale_y_continuous(
+    breaks = seq(-0.2, 0.2, 0.1)
+    ) +
   scale_color_manual(
     name = "Density:",
     values = colors

### 2023-05-09 manuscript/Chapter2-appendix1.Rmd
remove line in appendix1

@@
 # plogis for the success parameters
-# Take the exponent of sigma parameters
 b_draws[

### 2023-05-09 manuscript/Chapter2-manuscript.Rmd
finished updating the results

@@
 
-Out of all five models, the two that best predicted the data, with an almost identical expected log pointwise density (elpd), were the models that controlled for the prey group's speed (Table 1).
+Out of all five models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models that controlled for the prey group's speed (Table 1).
 Predators differed substantially in the relationship between hunting success and cumulative experience (i.e.
@@
 
-We predicted that the relationship between hunting success and experience would vary among predators because they should not encounter the same prey.
-After controlling for the mean speed of the prey group within a match, we did not find evidence confirming this prediction, because differences among predators remained important (Figure 1B).
-However, many individual curves appear to have shifted upwards in the model where we control for prey speed (Figure 1B) vs in the model where we do not control for prey speed (Figure 1A).
+We did not find evidence that differences among predators in the relationship between hunting success and experience was mediated by prey encounters because differences remained high even after controlling for the mean speed of the prey groups (Figure 1B).
+However, many individual curves appear to have shifted upwards after accounting for prey speed (Figure 1B) vs when we do not control for prey speed (Figure 1A).
 Moreover, in the models where we did not account for prey speed, the global trend of predator experience was nearly flat (results not shown).
@@
 
-## Effect of experience on the development of behavioural specialization
+## Effect of experience on behavioural specialization and hunting success
 
 The mean speed of the predator population did not change with experience (i.e.
-intercept of predator speed (mean); Figure 2 and Appendix S1: Table S1).
+intercept (mean) of predator speed; Figure 2 and Appendix S1: Table S1).
 There was also strong evidence that foraging specialization in the population remained stable across experience levels (i.e.
-intercept of predator speed (sigma); Figure 2 and Appendix S1: Table S1).
+intercept (sigma) of predator speed; Figure 2 and Appendix S1: Table S1).
+We did not find evidence that the predator population had a change in mean success with experience (intercept (mean) of hunting success; Figure 2 and Appendix S1: Table S1).
+There was, however, a decrease in among individual differences in success at the intermediate stage, which was maintained at the advanced stage (predator ID (mean) of hunting success; Figure 2 and Appendix S1: Table S2).
 
-Individual predators differed slightly in their average movement speed, but differences did not increase at higher experience levels (i.e.
+Individual predators differed slightly in their average movement speed across experience levels (i.e.
 predator ID (mean); Figure 2 and Appendix S1: Table S2).
-However, individuals displayed differences in their foraging specialization, with a 0.1 unit increase in standard deviation from novice to advanced (i.e.
+However, there was strong evidence that they displayed differences in foraging specialization, with a 0.1 unit increase in standard deviation from novice to advanced, indicating that differences increased slightly (i.e.
 predator ID (sigma) is higher at the advanced level; Figure 2 and Appendix S1: Table S2).
-Thus, as individual predators gain experience, the population becomes slightly more heterogeneous along the specialist-flexible hunter continuum.
 Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 3).
@@
 
-Contrary to predictions, there was strong evidence that predators did not differ in the speed of the prey groups that they encountered on average (i.e.
-predator ID (mean); Appendix S1: Table S2).
-Moreover, differences in standard deviation values across experience were negligible (i.e.
-predator ID (mean); Figure 2).
+Contrary to predictions, there was strong evidence that predators did not differ in the speed of the prey groups that they encountered on average across experience (i.e.
+predator ID (mean); Figure 2 and Appendix S1: Table S2).
 However, individuals differed in the heterogeneity of the groups of prey encountered across the study period (i.e.
@@
 
-*continuer ici les modifications*
+Predators that were on average faster (mean speed) had a lower intra-individual variability (IIV speed) (Figure 4A-B and Appendix S4: Table S1).
+Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time.
+As predators gained experience, these strategies were increasingly defined as there was a 0.16 unit increase in the correlation at the advanced stage (Figure 4C).
+Predators that were on average faster (mean speed) also encountered groups of prey that were on average faster (mean prey speed) and more similar (IIV prey speed) (Figure 4A-B and Appendix S4: Table S1).
+There was however only weak to no evidence that these correlations increased with experience (Figure 4C)
 
-At all experience levels, predators that were on average faster (mean) also had a lower intra-individual variability (IIV; Figure 3 and Appendix S2: Table S1).
-Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time.
-Predators that were on average faster (mean) also encountered groups of prey that were on average faster (mean) (Figure 3 and Appendix S2: Table S1).
-At the three experience levels, there were only weak correlations between IIV in predator speed and mean prey speed (Figure 3 and Appendix S2: Table S1).
-However, predators that encountered groups of prey with similar speeds (IIV) specialized in their hunting tactic (IIV) (Figure 3 and Appendix S2: Table S1).
-Hence, predators that encountered groups of prey with similar average speeds were more specialized, while those that encountered groups of prey with different average speeds were more flexible.
-For all the results described above, the correlations strengthen as predators gain experience (Figure 3 and Appendix S2: Table S1).
+There was almost no correlation between IIV in predator speed and mean prey speed when predators were novice (Figure 4A).
+There was however a 0.17 unit increase in this correlation at the advanced stage, such that specialist hunters at this stage tended to encounter faster prey (Figure 4C).
+The predator IIV in speed and IIV in prey speed were moderately positively correlated (Figure 4A-B and Appendix S4: Table S1).
+Hence, predators that encountered groups of prey with similar speeds were more specialized in their tactic, and those that encountered groups of prey with varying speeds were more flexible.
+We did not find evidence that this correlation increased with experience (Figure 4C).
 
@@
 
-We did not detect strong correlations between the predators' mean speed and their hunting success (Figure 3 and Appendix S2: Table S1), nor between the predators' IIV in speed and their hunting success (Figure 3 and Appendix S2: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
-However, novice individuals that encountered groups of prey with faster speeds were less successful (Figure 3 and Appendix S2: Table S1).
-This relationship was decoupled at the later experience levels, such that encounters with faster prey at intermediate and advanced stages were not as strongly correlated with hunting success anymore (Figure 3 and Appendix S2: Table S1).
-Thus, the consequences of hunting faster prey were reduced at greater experience levels.
+The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
+However, there was strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
+Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B and Appendix S4: Table S1).
+Both relationships remained structurally stable across experience (Figure 4-C)
 
@@
 ## Conclusions
+
+*simplifier la 1ere phrase*
 
@@
 
-**Figure 2.** Posterior median differences and credible intervals between each predator experience level's parameters.
+**Figure 2.** Posterior median differences and highest posterior density intervals between each predator experience level's parameters.
 Each panel shows the experience levels that are compared.
@@
 B) Correlations when predators were advanced hunters.
-C) Posterior median differences and credible intervals comparing the correlations between traits when predators were advanced vs novice.
-The median difference is displayed on the x axis and the trait correlations being compared are displayed on the y axis.
+C) Posterior median differences and highest posterior density intervals comparing the correlations between traits when predators were advanced vs novice.
+The differences were computed on the absolute values of the correlations since the signs did not change with experience, such that positive values indicate an increase in correlation at the advanced stage.
+The median difference is displayed on the y axis and the trait correlations being compared are displayed on the x axis.
 

### 2023-05-10 code/04_code_figures/figure1.R
update fig1

@@ -95,14 +95,14 @@
  tabA2_a <- conditional_effects(
   modA2, method = "fitted",
   effects = "Zcumul_xp:predator_id",
-  robust = FALSE, re_formula = NULL
+  robust = TRUE, re_formula = NULL
  )
  tabA2_a <- data.table(tabA2_a[[1]])
 
  # Cumulative XP global trend model A2
  tabA2_b <- conditional_effects(
   modA2, method = "fitted",
-  robust = FALSE, re_formula = NULL,
+  robust = TRUE, re_formula = NULL,
   effects = "Zcumul_xp",
   conditions = data.frame(predator_id = NA)
  )
@@ -112,14 +112,14 @@
  tabA2_prey_a <- conditional_effects(
   modA2_prey, method = "fitted",
   effects = "Zcumul_xp:predator_id",
-  robust = FALSE, re_formula = NULL
+  robust = TRUE, re_formula = NULL
  )
  tabA2_prey_a <- data.table(tabA2_prey_a[[1]])
 
  # Cumulative XP global trend model A2prey
  tabA2_prey_b <- conditional_effects(
   modA2_prey, method = "fitted",
-  robust = FALSE, re_formula = NULL,
+  robust = TRUE, re_formula = NULL,
   effects = "Zcumul_xp",
   conditions = data.frame(predator_id = NA)
  )
@@ -129,7 +129,7 @@
  tabA3 <- conditional_effects(
   modA3, method = "fitted",
   effects = "Zcumul_xp:predator_id",
-  robust = FALSE, re_formula = NULL
+  robust = TRUE, re_formula = NULL
  )
  tabA3 <- data.table(tabA3[[1]])
 
@@ -137,7 +137,7 @@
  tabA3_prey <- conditional_effects(
   modA3_prey, method = "fitted",
   effects = "Zcumul_xp:predator_id",
-  robust = FALSE, re_formula = NULL
+  robust = TRUE, re_formula = NULL
  )
  tabA3_prey <- data.table(tabA3_prey[[1]])
 
@@ -189,10 +189,10 @@
  tabA2_prey_a <- tabA2_prey_a[cumul_xp <= total_xp_pred, ]
  tabA3_prey <- tabA3_prey[cumul_xp <= total_xp_pred, ]
 
- 
- 
+
+
 # Setup a custom theme for the plot ----------------------------------------
- 
+
  custom_theme <- theme(
    # axis values size
    axis.text = element_text(face = "plain",
@@ -305,7 +305,7 @@
[…]

### 2023-05-10 manuscript/Chapter2-appendix1.Rmd
update appendix1

@@
 Authors : Maxime Fraser Franco, Francesca Santostefano, Julien G. A. Martin, Clint D. Kelly, Pierre-Olivier Montiglio
-
-Update the plot legend to tell what is the *greatest increase*
 
@@
 Each fitted curve represents an individual predator.
-(A) Individuals with the greatest increase in hunting success with experience (B) Individuals with the greatest decrease in hunting success with experience."}
+(A) Individuals with a >0.5 change in hunting success with experience (B) Individuals with a <-0.5 change in hunting success with experience.
+(C) Individuals with a change in hunting success between -0.5 and 0.5"}
 

### 2023-05-10 manuscript/Chapter2-manuscript.Rmd
repasse sur les résultats des GAMM ainsi que la discussion GAMM

@@
 
-Out of all five models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models that controlled for the prey group's speed (Table 1).
+```{r}
+
+# Open percentages table
+path <- file.path(here::here("outputs", "03_outputs_model-processing"))
+percent_tab <- data.table(readRDS(file.path(path, "GAMM_percentages.rds")))
+
+```
+
+Out of all five models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models accounting for the prey group's speed (Table 1).
 Predators differed substantially in the relationship between hunting success and cumulative experience (i.e.
 expertise: Figure 1A-B).
-For instance, the success of some predators steadily increased with experience (Figure 1B, Appendix S1: Figure S1A) while others showed a decrease in success with experience (Figure 1B, Appendix S1: Figure S1B).
-Overall, `r toString(scales::percent(191/253))` of the population displayed an >10% increase in hunting success, `r toString(scales::percent(37/253))` displayed a >10% decrease in hunting success, and the remaining `r toString(scales::percent(25/253))` had a lesser change in success ranging between -10% and +10%.
+We found evidence that these differences were in part mediated by prey speed because individuals had distinct patterns after we controlled for the mean speed of the prey groups compared to when we did not (Figure 1A-B).
+For instance, many individual curves shifted upwards.
+Precisely, the percentage of individuals that displayed a >0.5 increase in success changed from `r toString(scales::percent(percent_tab[2,]$percentage, accuracy = 0.1))` to `r toString(scales::percent(percent_tab[5,]$percentage, accuracy = 0.1))` after we accounted for prey speed (Appendix S1: Figure S1A).
+In this model (i.e.
+Figure 1B-C), `r toString(scales::percent(percent_tab[4,]$percentage, accuracy = 0.1))` of the population showed a >0.5 decrease in success (Appendix S1: Figure S1B), and the remaining `r toString(scales::percent(percent_tab[6,]$percentage, accuracy = 0.1))` displayed little to no change (between -0.5 and 0.5) in success across experience (Appendix S1: Figure S1C).
 
-We did not find evidence that differences among predators in the relationship between hunting success and experience was mediated by prey encounters because differences remained high even after controlling for the mean speed of the prey groups (Figure 1B).
-However, many individual curves appear to have shifted upwards after accounting for prey speed (Figure 1B) vs when we do not control for prey speed (Figure 1A).
-Moreover, in the models where we did not account for prey speed, the global trend of predator experience was nearly flat (results not shown).
+Moreover, all models where we did not account for prey speed had a global trend of predator experience that was nearly flat (results not shown).
 Yet, we see that there is an increase up to 13% in the probability of capturing all prey with experience in the population when we account for prey speed (Figure 1C).
@@
 Importantly, 12.6% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
-$\ge$0.2 change in standard deviation), 44.7% displayed lower changes (i.e.
+>0.2 change in standard deviation), 44.7% displayed lower changes (i.e.
 >0.05 and <0.2 change in standard deviation), while 42.7% remained relatively stable (i.e.
-$\le$0.05 change in standard deviation).
+<0.05 change in standard deviation).
 
@@
 
-There was almost no correlation between IIV in predator speed and mean prey speed when predators were novice (Figure 4A).
-There was however a 0.17 unit increase in this correlation at the advanced stage, such that specialist hunters at this stage tended to encounter faster prey (Figure 4C).
+There was almost no correlation between mean prey speed and IIV in predator speed when predators were novice (Figure 4A).
+There was however a 0.17 unit increase in this correlation at the advanced stage, such that advanced hunters that encountered faster prey tended to be more specialized (Figure 4C).
 The predator IIV in speed and IIV in prey speed were moderately positively correlated (Figure 4A-B and Appendix S4: Table S1).
-Hence, predators that encountered groups of prey with similar speeds were more specialized in their tactic, and those that encountered groups of prey with varying speeds were more flexible.
-We did not find evidence that this correlation increased with experience (Figure 4C).
+Hence, predators that encountered groups of prey with similar speeds were more specialized in their tactic while those that encountered groups of prey with varying speeds were more flexible.
+We did not however find evidence that this correlation increased with experience (Figure 4C).
 
@@
 
-*retravailler ici pour moins faire comme si il y avait un gros cluster. C'est surtout un continuum.*
-
-*The maximum is attained around match 340 (i.e.
-advanced state).
-Prey speed was thus important in mediating the population and individual-level relationship between success and experience, but does appear to influence among individual differences in this relationship.*
-
 Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
@@
 Our results show that there was no directional increase in either behavioural specialization or flexibility with experience at the population level.
-Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with prey; some specialized in fast-paced hunting, and others adopted a slower and more flexible tactic with experience.
+Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with prey; there was a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy.
 Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period.
-With experience, predators increasingly matched their tactic to the speed of the prey that they encountered, which simultaneously relaxed the negative consequences of encountering faster prey.
-Together, our observations suggest that predators in *DBD* learn to adjust their hunting tactic to the behaviour of the prey that they encounter throughout their lifetime in the game.
+With experience, predators increasingly matched their foraging specialization to the speed of the prey that they encountered, but they did not achieve greater success, probably because the prey were also matching their speed to the predator.
+Our observations suggest that predators in *DBD* learn to adjust foraging specialization to the behaviour of the prey that they encounter throughout their lifetime in the game.
 
@@
 Empirical research shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
-However, we cannot derive conclusions at the individual-level from these studies either because their models assume the same increase in expertise for each individual, or because it is unclear whether their data has repeated measures of individual success through time.
-Our analyses revealed that there was no population increase in expertise over time.
-As we mentioned before, the matchmaking pairs players using a rank-based system, and this result may thus be due to predators being paired with prey of similar skills.
-However, if this was solely due to the ranking system, we would have found a similar flat relationship for every predator.
-Instead, individual predators in *DBD* displayed distinct patterns of expertise acquisition (Figure 1, Appendix S1: Figure S1A-S1B).
-
+Our analyses revealed a similar trend, with a 13% population increase in success with experience.
+However, as we mentioned before, the matchmaking pairs players using a rank-based system, and the increase in expertise could have been even greater if predators were not paired with prey of similar skill.
+Individual predators in *DBD* also displayed distinct patterns of expertise acquisition.
 We predicted that this would occur if, by chance, predators differed in the prey that they encountered, because some may be easier and others more difficult to capture.
 In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;Martin.etal2022].
-Yet, prey speed did not shape individual differences in expertise acquisition, but other antipredator tactics may be involved.
-For example, it is well known in *DBD* that some prey groups use mobbing to confuse the predator or prevent it from capturing an injured individual.
-However, like natural predator-prey systems, direct predator-mobbing in *DBD* is dangerous and requires coordinated actions that are learned through experience [@Graw.Manser2007;@Dutour.etal2016;@Pitman.etal2017;@Dutour.etal2019;@Szymkowiak2021], and was thus probably not a pervasive antipredator strategy.
-Other antipredator tactics known to confuse human and non-human predators during the attack sequence are unpredictable escapes and turning angles [@Jones.etal2011;@Briffa2013;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018].
-While predators can adjust to unpredictable prey escapes [@Szopa-Comley.Ioannou2022], it could still be more arduous for a predator to learn and optimize its hunting success if it more often encountered prey using these tactics.
+In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
+Our results confirm that prey speed influenced expertise acquisition at the individual level to some extent.
+This is not surprising because capturing faster prey requires costly and specialized cognitive abilities and coordination [@Kelley.Magurran2011].
+However, even if we accounted for prey speed, there were still important differences in expertise acquisition, which suggests that other antipredator tactics may also be involved.
 
-Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition, irrespective of the prey groups that predators encountered.
+For example, two well known antipredator tactics known to confuse human and non-human predators during the attack sequence are unpredictable escapes and turning angles [@Jones.etal2011;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018].
+Yet, even if predators can adjust to unpredictable prey escapes [@Szopa-Comley.Ioannou2022], it could still be arduous for an individual to learn and optimize its hunting success if it more often encountered prey using these tactics.
+Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition.
 For example, in *DBD*, a predator that played 300 matches in the span of six months might forget more critical information (e.g.
@@
 While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
-Moreover, the predators may have differed in their ability to detect prey.
-For example, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
+Moreover, the predators could have differed in their ability to detect prey.
+For instance, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
 @Szopa-Comley.etal2020 also found consistent among individual variation in the capacity to detect cryptic and conspicuous prey in three-spined sticklebacks (*Gasterosteus aculeatus*).
-Thus, individual predators should differ in their expertise if they do not learn equally how to exploit the visual cues that facilitate prey detection.
+Thus, predators could differ in their expertise if they do not learn equally how to exploit the visual cues that facilitate prey detection.
 
 ## Changes in individual hunting specialization with experience and consequences for predator-prey interactions
+
+*je suis rendu ici pour la correction*
+*m'assurer que je nuance bien et que je fais pas ressortir que l'expérience c'est full important*
 
@@
 
+*ici il y a des changements importants à apporter*
+
 As predators gained experience, their tactic was increasingly matched to the speed of their prey.
@@
 
-*simplifier la 1ere phrase*
+*arranger la conclusion*
 
-Trait-mediated predator-prey interactions are important processes involved in population cycles and should occur when predators match their phenotype to their prey [@abramsEvolutionPredatorPreyInteractions2000].
-Yet, it has remained largely unknown whether this trait-matching results from predators learning how to capture their prey, in part because of the challenges of investigating direct interactions in the wild.
+Trait-mediated interactions that affect prey capture are the most important processes driving predator-prey dynamics [@abramsEvolutionPredatorPreyInteractions2000].
+While most studies assume that predators maximize prey capture by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
 By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise.
@@
 The authors declare no conflict of interest
-
-\newpage
 
@@
 Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.28 standard deviations.
+*check ici que les pourcentages font du sens*
 

### 2023-05-14 code/04_code_figures/appendix1_figureS2.R
appendix 1 figure S2

@@ -1,0 +1,237 @@
+# =======================================================================
+
+#             Plot the success of specialists vs generalists
+
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 1. Prepare the script
+# =======================================================================
+
+# load libraries
+library(brms)
+library(data.table)
+library(ggplot2)
+library(ggpubr)
+
+# import model
+fit <- readRDS(
+    "./outputs/01_outputs_models/B1_DHMLM-no-outlier.rds"
+)
+
+# Import ID table
+id_tab <- readRDS(
+    "./outputs/03_outputs_model-processing/DHMLM_id-draws.rds"
+)
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 2. Custom theme for plots
+# =======================================================================
+
+
+custom_theme <- theme(
+   # axis values size
+   axis.text = element_text(face = "plain",
+                            size = 14,
+                            color = "black"),
+   # axis ticks lenght
+   axis.ticks.length = unit(.15, "cm"),
+   # axis ticks width
+   axis.ticks = element_line(linewidth = 0.90,
+                             color = "black"),
+   # axis titles size
+   axis.title = element_text(size = 16,
+                             face = "plain",
+                             color = "black"),
+   axis.line = element_line(linewidth = 0.95,
+                            color = "black"),
+   legend.position = "none",
+   panel.grid = element_blank(),
+   panel.background = element_blank()
+ )
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 3. Compute the plot
+# =======================================================================
+
+
+# Novices table ---------------------------------------------------------
+
+id_tab1 <- id_tab[xp_level == "novice" &
+                  variable == "pred_speed" &
+                  sigma == 1][, ":=" (sigma = NULL,
+                                      xp_level = NULL,
+                                      variable = NULL)]
+setnames(id_tab1,
[…]

### 2023-05-14 manuscript/Chapter2-appendix1.Rmd
update appendix S1 with fig S2

@@
 ```
+
+```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Correlations between the predators' mean hunting success and intra individual variance in speed indicating differences in success between specialist and flexible hunters.
+Individuals with lower IIV are specialist hunters, while individuals with higher IIV are flexible hunters.
+(A) Correlation when predators were novice (B) Correlation when predators were advanced"}
+
+knitr::include_graphics(
+  here::here(
+    "outputs", "04_outputs_figures",
+    "appendix1_figureS2.png"
+  )
+)
+
+```

### 2023-05-16 manuscript/Chapter2-manuscript.Rmd
new MS version complete

@@
 
-Keywords: foraging behaviour, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology
+Keywords: foraging behaviour, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology, Dead by Daylight
 
@@
 path <- file.path(here::here("outputs", "03_outputs_model-processing"))
-percent_tab <- data.table(readRDS(file.path(path, "GAMM_percentages.rds")))
-
+percent_tab1 <- data.table(readRDS(file.path(path, "GAMM_percentages.rds")))
+percent_tab2 <- data.table(readRDS(file.path(path, "DHMLM_percentages.rds")))
 ```
@@
 For instance, many individual curves shifted upwards.
-Precisely, the percentage of individuals that displayed a >0.5 increase in success changed from `r toString(scales::percent(percent_tab[2,]$percentage, accuracy = 0.1))` to `r toString(scales::percent(percent_tab[5,]$percentage, accuracy = 0.1))` after we accounted for prey speed (Appendix S1: Figure S1A).
+Precisely, the percentage of individuals that displayed a >0.5 increase in success changed from `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` to `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` after we accounted for prey speed (Appendix S1: Figure S1A).
 In this model (i.e.
-Figure 1B-C), `r toString(scales::percent(percent_tab[4,]$percentage, accuracy = 0.1))` of the population showed a >0.5 decrease in success (Appendix S1: Figure S1B), and the remaining `r toString(scales::percent(percent_tab[6,]$percentage, accuracy = 0.1))` displayed little to no change (between -0.5 and 0.5) in success across experience (Appendix S1: Figure S1C).
+Figure 1B-C), `r toString(scales::percent(percent_tab1[4,]$percentage, accuracy = 0.1))` of the population showed a >0.5 decrease in success (Appendix S1: Figure S1B), and the remaining `r toString(scales::percent(percent_tab1[6,]$percentage, accuracy = 0.1))` displayed little to no change (between -0.5 and 0.5) in success across experience (Appendix S1: Figure S1C).
 
@@
 Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 3).
-Importantly, 12.6% of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
->0.2 change in standard deviation), 44.7% displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation), while 42.7% remained relatively stable (i.e.
+Importantly, `r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
+>0.2 change in standard deviation), `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e.
+>0.05 and <0.2 change in standard deviation), while `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))`remained relatively stable (i.e.
 <0.05 change in standard deviation).
@@
 The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
+This is further supported in the scatterplot showing no apparent relationship between success and IIV in speed (Appendix S1: Figure S2).
 However, there was strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
@@
 Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
-However, when resources vary, others predict that learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
+However, when resources vary, learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
 Our results show that there was no directional increase in either behavioural specialization or flexibility with experience at the population level.
-Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with prey; there was a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy.
+Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with the prey.
+There was a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy.
 Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period.
 With experience, predators increasingly matched their foraging specialization to the speed of the prey that they encountered, but they did not achieve greater success, probably because the prey were also matching their speed to the predator.
-Our observations suggest that predators in *DBD* learn to adjust foraging specialization to the behaviour of the prey that they encounter throughout their lifetime in the game.
+Our observations suggest that predators in *DBD* learn to adjust their foraging specialization, not to the variance, but to the mean behaviour of the prey that they encounter throughout their lifetime in the game.
 
@@
 Empirical research shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
-Our analyses revealed a similar trend, with a 13% population increase in success with experience.
-However, as we mentioned before, the matchmaking pairs players using a rank-based system, and the increase in expertise could have been even greater if predators were not paired with prey of similar skill.
+Our analyses revealed a similar trend, with a 13% population increase in success when predators became advanced hunters.
+However, because the game pairs players with similar skill, the increase in expertise could have potentially been greater if predators and prey were paired randomly.
 Individual predators in *DBD* also displayed distinct patterns of expertise acquisition.
@@
 This is not surprising because capturing faster prey requires costly and specialized cognitive abilities and coordination [@Kelley.Magurran2011].
-However, even if we accounted for prey speed, there were still important differences in expertise acquisition, which suggests that other antipredator tactics may also be involved.
 
-For example, two well known antipredator tactics known to confuse human and non-human predators during the attack sequence are unpredictable escapes and turning angles [@Jones.etal2011;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018].
-Yet, even if predators can adjust to unpredictable prey escapes [@Szopa-Comley.Ioannou2022], it could still be arduous for an individual to learn and optimize its hunting success if it more often encountered prey using these tactics.
+However, there were still important differences in expertise acquisition, which suggests that other antipredator tactics may also be involved.
+For example, a well known antipredator tactic associated with speed that confuses human and non-human predators during the attack sequence is unpredictable escapes [@Jones.etal2011;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018].
+This tactic compromises the predator's ability to anticipate prey escape routes, but they can adjust to it by using slower approaches before attacking [@Szopa-Comley.Ioannou2022].
+Yet, because unpredictability exploits the predator's cognition, slow learners could struggle to optimize their success if they often encounter prey using this tactic which is also extensively used in *DBD* (personal observation).
+
 Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition.
@@
 Moreover, the predators could have differed in their ability to detect prey.
-For instance, it is widely demonstrated that predators learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
+For instance, nonhuman predators can learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
 @Szopa-Comley.etal2020 also found consistent among individual variation in the capacity to detect cryptic and conspicuous prey in three-spined sticklebacks (*Gasterosteus aculeatus*).
@@
 
-*je suis rendu ici pour la correction*
-*m'assurer que je nuance bien et que je fais pas ressortir que l'expérience c'est full important*
-
-The predator population displayed an increase in foraging flexibility when reaching the intermediate level of experience.
-As it reached an advanced level of experience, it returned to a level of flexibility that was similar to novice levels.
-This is commonly observed in juvenile predators across the animal kingdom, because exploring and learning different tactics at this developmental stage is crucial to become a skillful hunter [@Vehanen2003;@Johnson.Wilbrecht2011;@Thiers.etal2014;@deGrissac.etal2016].
-Thus, predators in *DBD* were probably exploring and refining different tactics at this stage of experience.
-Within the population, differences in individual foraging specialization among predators increased with experience, which was related to the degree of variability in prey encounters.
+There were only weak differences among predators in tactic use (i.e.
+mean speed), but differences in specialization were important and related to how different were the groups of prey that they encountered.
 Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy.
 Fast-paced hunting is indeed a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when hunting prey that use unpredictable escapes [@Szopa-Comley.Ioannou2022].
-This is further supported by the fact that specialist and flexible hunters both achieved similar success throughout the study period.
+However, it remains uncertain whether this phenotypic matching enables predators with different degrees of specialization to achieve equal success within populations [@Woo.etal2008].
+Here, we found that all hunters along the flexible-specialist continuum achieved similar success throughout the study period (Appendix S1: Figure S2).
+Thus, our results provide direct evidence that predators matching their tactic to their prey may be key in maintaining behavioural diversification in predator-prey systems.
+
+Surprisingly, the effect of experience on foraging behaviour was much more subtle than we expected.
+For instance, the predator population maintained their speed and degree of specialization throughout the study period, and individual differences in mean speed did not change with experience.
+However, differences among predators in foraging specialisation did increase slightly with experience, with some individuals becoming increasingly flexible.
 Interestingly, the behavioural response (i.e.
-tactic use and specialization) to experience by individual predators differed.
-For instance, 42.7% of the population did not alter their degree of specialization with experience (i.e.
-remaining either faster and more specialized, or slower and more flexible), while 57.3% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience.
-Thus, our results provide direct evidence that the mechanism underlying the resource-predictability hypothesis may indeed involve predators learning at varying degrees how to specialize on their prey [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
+specialization) to experience by individual predators differed.
+For instance, 44% of the population did not alter their degree of specialization with experience (i.e.
+remaining either faster and more specialized, or slower and more flexible), while 56% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience.
+These changes were accompanied by predators increasingly matching their specialization to the mean speed of the prey groups across experience, instead of the variability between encounters.
+This suggests that it may be easier for predators to specialize on their prey by relying on mean cues (i.e.
+mean behaviour) instead of relying solely on resource heterogeneity [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
 
-*ici il y a des changements importants à apporter*
+It is likely that predators were also driving changes in prey behaviour because most predator-prey behavioural relationships remained stable even though half of the population switched from a specialist to a flexible strategy and vice-versa across experience.
+This implies that the prey were probably also learning how to avoid predation through repeated interactions.
+Our results concord with what @Mougi.etal2011 define as a matching response relationship, because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success.
+These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013], but their broader consequences remain unclear.
+Assuming that prey also learned during the interaction, which has been shown across many taxa [refs], we can deduce that learning from reciprocal interactions may contribute in stabilizing predator-prey systems, similar to Red Queen dynamics [@brockhurst2014].
 
-As predators gained experience, their tactic was increasingly matched to the speed of their prey.
-One interpretation could be that both predators and prey learned from each other in an arms-race-like reciprocal relationship [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@Mougi.etal2011].
-For instance, predators that encountered faster prey could have learned to increase their speed to better capture them, resulting in an increase in the speed of the prey to circumvent the predator's attacks.
-In this type of system, faster prey should be better at escaping both slower and faster predators [@Mougi.etal2011], which concords with what we previously observed in this sytem [@FraserFranco.etal2022].
-@BrodieIII.BrodieJr.1999 argue that when prey express defensive phenotypes (e.g.
-physical armaments or venom), selection on predators should be strong because the consequences of being injured are greater than missing a meal.
-If predators improve their exploitative ability, then an arms-race should emerge, and the consequences of hunting dangerous prey should decrease [@BrodieIII.BrodieJr.1999].
-Similarly, we found that has the predator gained experience, the negative consequences of encountering prey groups with higher speeds were relaxed, and the variation in success among predators decreased.
-However, in an arms-race, faster predators would have successfully preyed upon faster and slower prey and would have obtained higher success than slower predators [@Mougi.etal2011], which was not the case in the present study.
-A more likely scenario is that predators and prey in *DBD* were involved in a matching response relationship [@Mougi.etal2011], because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success.
-Thus predators in *DBD* appear to optimize their success by learning to match their tactic to their prey with experience, suggesting that learning through reciprocal interactions may attenuate selection exerted by prey on predators [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007].
+While experience did not alter most of the interaction, predators still managed to increase foraging specialization with increasing prey speed across experience, while individual differences in hunting success simultaneously decreased.
+When prey express defensive phenotypes such as high speeds, selection on predators should be strong because of the consequences of repeated failures.
+If predators improve their exploitative ability, then the consequences of hunting these prey should decrease [@BrodieIII.BrodieJr.1999].
+Similarly, theoretical studies predict that learning may attenuate selection [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007], but failing to account for reciprocal interactions may mask more complex outcomes.
+Here, learning appears to have reduced differences in success among predators, but success remained lower when predators hunted faster prey.
+Again, if prey learned how to avoid the predators, then this would explain why advanced hunters still struggled to achieve similar success against faster prey compared to slower prey.
+Thus, disentanling the consequences of learning from reciprocal interactions may reveal important insights on predator-prey interactions.
 
@@
 
-*arranger la conclusion*
-
 Trait-mediated interactions that affect prey capture are the most important processes driving predator-prey dynamics [@abramsEvolutionPredatorPreyInteractions2000].
-While most studies assume that predators maximize prey capture by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
+While most studies assume that predators maximize success by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
 By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise.
-With experience, half of the predator population changed their behaviour by developping either a specialized or flexible tactic that was matched to the speed of their prey.
-Overall, both type of hunters achieved equal hunting success.
+With experience, the population became increasingly distinct along a flexible-specialist continuum, while interactions remained largely stable.
+Overall, all hunters achieved similar hunting success.
 Our results have potential applications for predator-prey models of trait-matching.
@@
   , model := c(
-    "prey speed + group-level smoothers",
-    "predator xp + prey speed + group-level smoothers",
+    "predator xp + group-level smoothers + prey speed",
+    "group-level smoothers + prey speed",
     "group-level smoothers",
@@
 We selected the individuals displayed in the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles.
-Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.28 standard deviations.
-*check ici que les pourcentages font du sens*
+Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.27 standard deviations.
 

### 2023-05-23 manuscript/Chapter2-manuscript.Rmd
update intro based on PO and Julien comments. update refs

@@
 However, the mechanisms driving these individual responses are only beginning to be explored, in part because of the challenges associated with monitoring direct predator-prey interactions.
-In this study, we used a virtual predator-prey system (the online game *Dead by Daylight*) to test how hunting experience shapes individual foraging specialization and success in predators across repeated interactions with their prey.
-With increasing experience, predators fine-tuned their tactics to the behaviour of their prey.
+In this study, we used a virtual predator-prey system (the online game *Dead by Daylight*) to investigate if and how hunting experience shapes individual foraging specialization and success in predators across repeated interactions with their prey.
+
+*à modifier pour parler plutôt de l'interaction qui devient fine tuned (i.e. predators and prey)*
+We found that with increasing experience, predators fine-tuned their tactics to the behaviour of their prey.
 Individuals that adopted a flexible tactic (i.e.
@@
 specialists) encountered groups of prey with similar speeds throughout the study period.
+
 Our results suggest that experience enables predators to learn how to optimize their tactics to the type of prey that they encounter (i.e.
@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals specializing in different foraging tactics, with consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
+Indeed, predator populations often comprise assemblages of individuals specializing on different foraging tactics, with consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
 Despite the clear evidence that individual specialization is important for predator-prey interactions, its underlying mechanisms remain surprisingly unclear.
-However, it has recently been suggested that reciprocal interactions between predators and prey could drive individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
+It has recently been suggested, however, that reciprocal interactions between predators and prey could drive individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
 For instance, predators often hunt using techniques that are fine-tuned to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their refinement is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
@@
 For instance, some individuals may hunt in habitats where prey are faster, which are often proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-It should thus be essential for predators to learn how to match their tactic to their prey to optimize their success.
+It should thus be essential for predators to learn how to adjust their tactic to their prey to optimize their success.
 
-There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging [@Phillips.etal2017].
-This is reflected in the literature showing contrasting results in the links between specialization and fitness.
-Some studies report greater benefits when specializing [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019], some report that flexible foraging has greater benefits [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021], and others find equal benefits depending on timescales [@Woo.etal2008;@Potier.etal2015].
-This may in part be due to the limited information we have on the ecological contexts favoring specialization over flexibility.
-However, in predator-prey systems, studies suggest that fluctuations in the predictability of resources throughout a predator's lifetime may be a key factor shaping foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017;@Courbin.etal2018].
+There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging strategies [@Phillips.etal2017].
+This is reflected in the literature showing contrasting results in the links between specialization and fitness at the individual level.
+Some studies have found greater success for individuals that use specialized foraging tactics [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others found that individuals using flexible foraging tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021].
+This disrepancy may in part be due to the limited information we have on the ecological contexts favoring specialization over flexibility.
+However, many studies have found that both type of foragers can also attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018].
 It is hypothesized that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
-In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty.
-While it is clear that predators can match their behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how?
+In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty [@dall2010].
+While it is clear that predators can match their hunting behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how?
 Given the dynamic nature of predator-prey interactions, it is unlikely that evolution alone could explain such behavioural adjustments by predators, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].
@@
 A recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
-We recently demonstrated, using an online predator-prey videogame called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge [@FraserFranco.etal2022].
-In this dynamic virtual system, four prey players need to forage for resources while avoiding a predator player.
+We recently showed, using an online predator-prey videogame called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge [@FraserFranco.etal2022].
+In this dynamic virtual system, four prey players need to forage for resources while avoiding predation by a predator player.
 The prey can contribute to the group's success by healing or helping others escape the predator, or be selfish and attempt to escape by themselves [@Cere.etal2021].
@@
 in prep).
-These examples outline how virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance the current gaps in predator-prey research.
-They also generate large volumes of data on interacting players throughout their lifetime in the game under realistic ecological scenarios.
-Hence, virtual systems offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
+These examples outline how virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance predator-prey research.
+They also generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological scenarios.
+Hence, virtual systems, including *DBD*, offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
 
-In this study, we test how hunting experience shapes predator foraging specialization using data from players in the online videogame *Dead by Daylight*.
-*DBD* simulates a direct predator-prey interaction, where one predator player hunts four prey players in different virtual environments.
-The data grants a high degree of precision on the behavioural interaction, as the behaviour of both the predator and the four prey along with the predator's success are monitored simultaneously in each trial.
+In this study, we evaluated how hunting experience shapes predator foraging specialization and success using data from players in the online videogame *Dead by Daylight*.
 First, we investigate how predators develop their individual hunting expertise.
-We hypothesize that predators should differ in the development of their expertise, partly because they encounter varying levels of difficulty with the prey that they pursue.
-For example, a predator may face greater difficulty than other individuals if it more often encountered groups of prey that were elusive.
-Second, we test the hypothesis that experience will shape foraging specialization.
-If experience reduces the costs of switching between hunting tactics, we predict that the predator population should become more flexible.
-Alternatively, if experience enables the refinement of the hunting tactics, then the predator population may instead specialize.
-Otherwise, if both processes operate at the same time, then we should see no change with experience at the population level, but differences in specialization among individuals should increase.
-Third, we evaluate how predator foraging specialization emerges from behavioural interactions with the prey.
-We expect predators that experienced more predictable encounters with their prey to specialize, while predators that experienced unpredictable encounters with their prey should adopt a flexible hunting tactic.
+We hypothesize that predators should differ in the development of their expertise if they encountered varying levels of difficulty with the prey that they pursued.
+For example, a predator may face greater difficulty than other individuals if it encountered elusive groups of prey more often.
+Second, we test the hypothesis that experience will shape individual foraging specialization.
+We define foraging tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e.
+IIV) in movement speed from one match to the next where low IIV translates to individual specialization.
+If experience reduces the costs of switching between low and high speeds, we predict that individuals (and thus the population) should all converge towards flexible speeds.
+If experience enables the refinement of the tactics to hunt specific types of prey, then all individuals may instead specialize in their speed.
+In both scenarios, among individual variation in IIV (i.e.
+individual specialization) should be low because everyone is either a specialist or a generalist, but the population variance should either increase (flexibility) or decrease (specialization).
+Alternatively, both processes may operate at the same time if behavioural interactions with the prey vary among predators, such that among individual variation in IIV should increase.
+In this case, we expect predators that experienced more predictable encounters with their prey (i.e.
+homogeneous groups across matches) to specialize in their speed, while predators that experienced unpredictable encounters with their prey (i.e.
+heterogeneous groups across matches) should adopt flexible movement speeds.
 If we detect such prey-dependent fine-tuning, then specialist and flexible hunters should attain equal success because both should have learned to optimize their hunting style to their prey.

### 2023-05-24 manuscript/Chapter2-manuscript.Rmd
test pour montrer github

@@
 
-Journal name : Ecology
+Journal name : Ecology test
 
@@
 Despite the clear evidence that individual specialization is important for predator-prey interactions, its underlying mechanisms remain surprisingly unclear.
-It has recently been suggested, however, that reciprocal interactions between predators and prey could drive individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
+One hypothesis suggests that reciprocal interactions between predators and prey could drive individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
 For instance, predators often hunt using techniques that are fine-tuned to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their refinement is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
@@
 a game where the gameplay mechanics differ between two groups) multiplayer online game developed by Behaviour Interactive Inc, in which players can play either as a predator or a prey.
-The objective of the predator is to hunt and capture the four prey across a virtual environment.
-The objective of the four prey is to search for resources while avoiding the predator.
+Every match includes only one predator and four preys.
+The objective of the predator is to hunt and capture the prey, and the objective of the prey is to search for resources while avoiding the predator.
 The resources are in the form of power generators that, once all activated, will enable the prey to escape through one of two exit doors.
@@
 
-The videogame company provided data that spanned a period of 6 months of gameplay recorded for every player.
-The first recorded match was played on `r toString(format(min(dat$date)))` and the last one on `r toString(format(max(dat$date)))`.
-We analyzed only matches where players did not know each other (i.e.
+The videogame company provided data that spanned a period of 6 months of gameplay recorded for every player from `r toString(format(min(dat$date)))` to `r toString(format(max(dat$date)))`.
+We only analyzed matches where players did not know each other (i.e.
 "Online" mode).
-We filtered any matches where players were inactive, such as when speed values were equal to, or very close to, zero.
-Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game as it is supposed to be played.
+We filtered any matches where players were inactive, such as when average distances traveled per second (i.e.
+speed) were equal to, or very close to, zero.
+Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game as intended.
 We then sampled players that played 300 matches or more, and monitored all their matches from the first to a maximum of 500 matches.
@@
 We analyzed the predator's average speed and the average speed of the prey group encountered by the predator.
-The predator's average speed is measured as the average distance traveled per second during a match ($\overline{x}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
-We measured the preys' average speed as the average travel speed of the four individual prey within a match ($\overline{x}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
-We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
+The predator's average speed is measured as the average distance traveled per second during a match ($\overline{speed}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
+We measured the preys' average speed as the average travel speed of the four individual prey within a match ($\overline{prey speed}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
+We defined hunting success as the number of prey captured during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
 Lastly, we defined the predator's cumulative experience as the number of matches played prior to the match being monitored.
 For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.
+We also categorized predators for each match by their experience based on the number of matches they played before.
+We labeled predators as novices for matches with less than 100 matches played, intermediate between 100 and 299 matches played, and advanced when cumulative experience was above 299 matches (max 499).
+Since we monitored all predator players throughout their experience, they appeared in all the three experience categories.
 
-We recognize that we could have introduced a bias in our analyses since we sampled individuals who stayed in the game for at least 300 matches.
-For instance, these players may already be used to play videogames, and thus, could differ in the way they play at early stages of their experience in the game.
-To ensure that our sample was not biased, we compared a random sample of players that played between 20 and 50 matches, between 51 and 100 matches, and between 101 and 300 matches from the same timeframe with our sampled population.
-We then took the first 20 matches played by these players, including those from our sampled population, and compared their average behaviour using a Bayesian hierarchical linear model.
-We found that neither of the four groups differed in their average speed (Appendix 2: Table S1-S2), which gives us confidence that our player population was not biased.
+We recognize that we could have biased our analyses by retaining only individuals who played for at least 300 matches.
+For example, these individuals might be experienced videogame players and could thus already be playing optimally in their first matches in *DBD*.
+To verify that our sample was not biased, we compared a random sample of players that played either 20 to 50 matches, 51 to 100 matches, or 101 to 300 matches during the same timeframe as our sampled population.
+We then took the first 20 matches played by these players, including those from our sampled population, and compared their average speed using a Bayesian hierarchical linear model.
+We found that all four groups had similar average speeds (Appendix 2: Table S1-S2), which indicates an absence of bias due to data sampling.
 
@@
 
+The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
 All our statistical analyses were executed on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster maintained by the Digital Research Alliance of Canada.
 The operating system for Cedar is CentOS Linux 7.
-The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
 
@@
 
-We tested whether predators varied in the development of their expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin plate regression splines, all of which estimated the relationship between hunting success (i.e.
+We tested whether predators varied in the development of their expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e.
 number of prey captured) and the predators' cumulative experience (i.e.
 number of matches played before the current match).
-We parametrized the models following the method of @Pedersen.etal2019.
+We parameterized the models following the method of @Pedersen.etal2019.
 The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID.
-In this model, we assume that individuals have the same development of expertise, with the model estimating a trend for the average individual (i.e.
+In this model, we assume that predators have the same development of expertise, with the model estimating a trend for the average individual (i.e.
 global smoother).
 For the second model, we included varying group-level smoothers for the predator ID.
-In this model, we assume that individuals share a similar relationship between success and experience, but that this relationship can vary (e.g.
-individual 1 has a steeper curve than individual 2).
+Here, we assume that predators share a similar relationship between success and experience, but that this relationship can vary among individuals (e.g.
+predator 1 has a steeper curve than predator 2).
 This enabled us to test whether predators differed in the development of their expertise.
 In the third model, we kept the group-level smoothers for the predators, but removed the global smoother.
-This allows each individual to have a unique relationship between success and experience without penalization by the global smoother.
 This model assumes that predators do not share a common relationship between success and experience.
 The fourth and fifth models were a reproduction of the second and third models respectively, where we included the prey group's average speed to assess its effect on the relationship between success and experience.
-We included match duration as a covariate in all five models.
+We included the standardized match duration and average prey rank (a proxy for prey skill) as covariates in all five models.
+The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank), and failing to account for it would prevent us from detecting a change in the predator's foraging success with experience.
 
@@
 
-We categorized predators by their experience based on the number of matches they played.
-Since we monitored all predator players throughout their experience, they appeared in all of the three following experience categories.
-First, we assigned predators the status of "novice" when they had a cumulative experience below 100 matches.
-For example, a predator player that played 500 matches in total would be labelled as a novice in its first 100 matches.
-Following this logic, we labelled predators as "intermediate" hunters when they had a cumulative experience between 100 and 299 and matches.
-Lastly, we defined predators as "advanced" hunters when they had a cumulative experience equal or above 300, with a maximum of 499 cumulated matches.
-
 We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
@@
 if resource heterogeneity was higher for some individuals compared to others).
-We controlled for the square-root of the average rank of the prey group as proxy for prey skills for both the predator and the prey's speed (mean and dispersion).
-The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank).
+We controlled for the standardized average rank of the prey group for both the predator and the prey's speed (mean and dispersion).
 For hunting success, we quantified among individual differences in mean prey capture and controlled for the square-root of the game duration.

### 2023-05-30 code/01_code_models/B1_DHMLM-no-outlier.R
forgot to add rank to dhmlm. send to CC again

@@ -258,19 +258,25 @@ stanvars <- stanvar(scode = stan_funs, block = "functions")
 # Sub models
 success_novice <- bf(
   success_novice | vint(4) + subset(sub1) ~
-      1 + Zgame_duration +
+      1 +
+      Zgame_duration +
+      Zprey_avg_rank +
       (1 | a | predator_id)
 ) + beta_binomial2
 
 success_interm <- bf(
   success_interm | vint(4) + subset(sub2) ~
-      1 + Zgame_duration +
+      1 +
+      Zgame_duration +
+      Zprey_avg_rank +
       (1 | a | predator_id)
 ) + beta_binomial2
 
 success_advanced <- bf(
   success_advanced | vint(4) + subset(sub3) ~
-      1 + Zgame_duration +
+      1 +
+      Zgame_duration +
+      Zprey_avg_rank +
       (1 | a | predator_id)
 ) + beta_binomial2
 
@@ -299,7 +305,10 @@ priors <- c(
               "speedadvanced",
               "preyspeednovice",
               "preyspeedinterm",
-              "preyspeedadvanced"
+              "preyspeedadvanced",
+              "successnovice",
+              "successinterm",
+              "successadvanced"
             )
   ),
   # Prior on sigma prey rank

### 2023-05-30 code/01_code_models/B1_DHMLM.R

@@ -255,19 +255,25 @@ stanvars <- stanvar(scode = stan_funs, block = "functions")
 # Sub models
 success_novice <- bf(
   success_novice | vint(4) + subset(sub1) ~
-      1 + Zgame_duration +
+      1 +
+      Zgame_duration +
+      Zprey_avg_rank +
       (1 | a | predator_id)
 ) + beta_binomial2
 
 success_interm <- bf(
   success_interm | vint(4) + subset(sub2) ~
-      1 + Zgame_duration +
+      1 +
+      Zgame_duration +
+      Zprey_avg_rank +
       (1 | a | predator_id)
 ) + beta_binomial2
 
 success_advanced <- bf(
   success_advanced | vint(4) + subset(sub3) ~
-      1 + Zgame_duration +
+      1 +
+      Zgame_duration +
+      Zprey_avg_rank +
       (1 | a | predator_id)
 ) + beta_binomial2
 
@@ -296,7 +302,10 @@ priors <- c(
               "speedadvanced",
               "preyspeednovice",
               "preyspeedinterm",
-              "preyspeedadvanced"
+              "preyspeedadvanced",
+              "successnovice",
+              "successinterm",
+              "successadvanced"
             )
   ),
   # Prior on sigma prey rank

### 2023-05-30 manuscript/Chapter2-appendix1.Rmd
update appendix1 but will have to do it again

@@
       "b_sigma_preyspeedadvanced_Intercept",
-      "b_sigma_speednovice_sqrt_prey_avg_rank",
-      "b_sigma_speedinterm_sqrt_prey_avg_rank",
-      "b_sigma_speedadvanced_sqrt_prey_avg_rank",
-      "b_sigma_preyspeednovice_sqrt_prey_avg_rank",
-      "b_sigma_preyspeedinterm_sqrt_prey_avg_rank",
-      "b_sigma_preyspeedadvanced_sqrt_prey_avg_rank"
+      "b_sigma_speednovice_Zprey_avg_rank",
+      "b_sigma_speedinterm_Zprey_avg_rank",
+      "b_sigma_speedadvanced_Zprey_avg_rank",
+      "b_sigma_preyspeednovice_Zprey_avg_rank",
+      "b_sigma_preyspeedinterm_Zprey_avg_rank",
+      "b_sigma_preyspeedadvanced_Zprey_avg_rank"
   )
@@
     "b_sigma_preyspeedadvanced_Intercept",
-    "b_sigma_speednovice_sqrt_prey_avg_rank",
-    "b_sigma_speedinterm_sqrt_prey_avg_rank",
-    "b_sigma_speedadvanced_sqrt_prey_avg_rank",
-    "b_sigma_preyspeednovice_sqrt_prey_avg_rank",
-    "b_sigma_preyspeedinterm_sqrt_prey_avg_rank",
-    "b_sigma_preyspeedadvanced_sqrt_prey_avg_rank"
+    "b_sigma_speednovice_Zprey_avg_rank",
+    "b_sigma_speedinterm_Zprey_avg_rank",
+    "b_sigma_speedadvanced_Zprey_avg_rank",
+    "b_sigma_preyspeednovice_Zprey_avg_rank",
+    "b_sigma_preyspeedinterm_Zprey_avg_rank",
+    "b_sigma_preyspeedadvanced_Zprey_avg_rank"
   )
@@
       "b_successadvanced_Intercept",
-      "b_successnovice_sqrt_game_duration",
-      "b_successinterm_sqrt_game_duration",
-      "b_successadvanced_sqrt_game_duration"
+      "b_successnovice_Zgame_duration",
+      "b_successinterm_Zgame_duration",
+      "b_successadvanced_Zgame_duration"
   )
@@
     "b_successadvanced_Intercept",
-    "b_successnovice_sqrt_game_duration",
-    "b_successinterm_sqrt_game_duration",
-    "b_successadvanced_sqrt_game_duration"
+    "b_successnovice_Zgame_duration",
+    "b_successinterm_Zgame_duration",
+    "b_successadvanced_Zgame_duration"
   )
@@
 
-```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Among individual differences in the development of hunting expertise.
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Among individual differences in the development of hunting expertise in the model where we do not account for prey speed and average rank.
 The predators' hunting success (i.e.
@@
 Each fitted curve represents an individual predator.
-(A) Individuals with a >0.5 change in hunting success with experience (B) Individuals with a <-0.5 change in hunting success with experience.
-(C) Individuals with a change in hunting success between -0.5 and 0.5"}
+(A) Individuals with a >0.5 unit increase in hunting success with experience (B) Individuals with a <-0.5 unit decrease in hunting success with experience.
+(C) Individuals that maintained a stable hunting success (between -0.5 and 0.5 unit change in hunting success)"}
 
@@
 
-```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Correlations between the predators' mean hunting success and intra individual variance in speed indicating differences in success between specialist and flexible hunters.
+```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Correlations between the predators' mean hunting success (y axis) and intra individual variance in speed (x axis) to test for differences in success between specialist and flexible hunters.
 Individuals with lower IIV are specialist hunters, while individuals with higher IIV are flexible hunters.

### 2023-05-31 manuscript/Chapter2-manuscript.Rmd
updated the methods. might need to revisit

@@
 We define foraging tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e.
-IIV) in movement speed from one match to the next where low IIV translates to individual specialization.
+IIV) in movement speed from one match to the next, where low IIV translates to individual specialization.
 If experience reduces the costs of switching between low and high speeds, we predict that individuals (and thus the population) should all converge towards flexible speeds.
@@
 In this case, we expect predators that experienced more predictable encounters with their prey (i.e.
-homogeneous groups across matches) to specialize in their speed, while predators that experienced unpredictable encounters with their prey (i.e.
+similar groups across matches) to specialize in their speed, while predators that experienced unpredictable encounters with their prey (i.e.
 heterogeneous groups across matches) should adopt flexible movement speeds.
-If we detect such prey-dependent fine-tuning, then specialist and flexible hunters should attain equal success because both should have learned to optimize their hunting style to their prey.
+If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success probably because they learned from experience how to adjust their hunting style to their prey.
 
@@
 The predator-players' experience varied between `r toString(format(min(dat$total_xp_pred)))` and `r toString(format(max(dat$total_xp_pred)))` matches played.
-These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)`-min (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)`-min).
+These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)` min (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)` min).
 The following information is collected and reported for every match : the player's anonymous ID, its avatar (i.e.
@@
 We analyzed the predator's average speed and the average speed of the prey group encountered by the predator.
-The predator's average speed is measured as the average distance traveled per second during a match ($\overline{speed}$ = `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
-We measured the preys' average speed as the average travel speed of the four individual prey within a match ($\overline{prey speed}$ = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
-We defined hunting success as the number of prey captured during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
+The predator's average speed is measured as the average distance traveled per second during a match (mean= `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
+We measured the preys' average speed as the average travel speed of the four individual prey within a match (mean = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
+We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
 Lastly, we defined the predator's cumulative experience as the number of matches played prior to the match being monitored.
 For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.
-We also categorized predators for each match by their experience based on the number of matches they played before.
-We labeled predators as novices for matches with less than 100 matches played, intermediate between 100 and 299 matches played, and advanced when cumulative experience was above 299 matches (max 499).
-Since we monitored all predator players throughout their experience, they appeared in all the three experience categories.
+We also categorized predators for each match based on their cumulated experience.
+We labeled predators as novices for matches where they had cumulated less than 100 matches, intermediate for matches where they had cumulated between 100 and 299 matches, and advanced for matches where they had cumulated more than 299 matches (max 499).
+Since our goal was to monitor predator players throughout their experience and that they all played at least 300 matches, they appeared in all the three experience categories.
 
 We recognize that we could have biased our analyses by retaining only individuals who played for at least 300 matches.
-For example, these individuals might be experienced videogame players and could thus already be playing optimally in their first matches in *DBD*.
+For example, these individuals might be experienced videogame players and could thus already be playing like experts in their first matches in *DBD*.
 To verify that our sample was not biased, we compared a random sample of players that played either 20 to 50 matches, 51 to 100 matches, or 101 to 300 matches during the same timeframe as our sampled population.
 We then took the first 20 matches played by these players, including those from our sampled population, and compared their average speed using a Bayesian hierarchical linear model.
-We found that all four groups had similar average speeds (Appendix 2: Table S1-S2), which indicates an absence of bias due to data sampling.
+We found that all four groups had similar average speeds as predators (Appendix 2: Table S1-S2), which indicates an absence of bias due to data sampling.
 
@@
 
-We tested whether predators varied in the development of their expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e.
-number of prey captured) and the predators' cumulative experience (i.e.
+We tested how prey influence the development of predator expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e.
+number of prey consumed) and the predators' cumulative experience (i.e.
 number of matches played before the current match).
@@
 For the second model, we included varying group-level smoothers for the predator ID.
-Here, we assume that predators share a similar relationship between success and experience, but that this relationship can vary among individuals (e.g.
+Here, we assume that individual predators share a similar relationship between success and experience, but that this relationship can vary among them (e.g.
 predator 1 has a steeper curve than predator 2).
 This enabled us to test whether predators differed in the development of their expertise.
-In the third model, we kept the group-level smoothers for the predators, but removed the global smoother.
+In the third model, we kept the group-level smoothers for the individual predators, but removed the global smoother.
 This model assumes that predators do not share a common relationship between success and experience.
@@
 We computed the five models using a modified version of the beta-binomial distribution implemented in "brms".
-Hunting success was estimated as the probability of capturing the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
+Hunting success was estimated as the probability of consuming the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
 We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link.
@@
 We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5)$) and the global trend of cumulative experience ($N(0,\ 2)$).
-Based on previous results [@FraserFranco.etal2022], we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system.
+Following @FraserFranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system.
 We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0, 0.5)$).
@@
 
-We tested whether foraging behaviour changed with experience, and compared the success of generalists vs specialists, using a multivariate, double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
-For each level of experience (i.e.
-novice, intermediate, advanced), the model estimated the mean speed of every individual (which we call the mean part of the model), and the intra-individual standard deviation of speed of every individual (which we call the dispersion part of the model).
-From the mean part of the model, we could infer on among individual differences in foraging tactics (i.e.
-along the slow-fast continuum), while in the dispersion part of the model, we could infer on among individual differences in foraging specialization (i.e.
-intra-individual variability, IIV).
-We followed the same structure for the preys' speed.
-For the mean part, we tested whether individual predators differed in the average speed of the groups of prey encountered across the study.
-For the dispersion part, we tested whether individual predators differed in how (dis)similar were the groups of prey they encountered across the study (i.e.
+We tested whether foraging behaviour changed with experience, and compared the success of flexible vs specialist hunters, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
+We fitted the model on the predator's speed ($Y_{1}$), the prey's speed ($Y_{2}$), and the predator's hunting success ($Y_{3}$), which allowed us to simultaneously estimate three distinct components for each experience level.
+The first component is among individual variation in mean speed and success (the mean part of the model), allowing to test for individual differences in tactic use (i.e.
+along the slow-fast continuum), in the mean speed of the prey encountered, and in prey consumption.
+The second component is among individual variation in intra-individual behavioural variation (IIV) (the dispersion part of the model), allowing us to test for individual differences in foraging specialization and in how (dis)similar was the speed of the groups of prey encountered (i.e.
 if resource heterogeneity was higher for some individuals compared to others).
-We controlled for the standardized average rank of the prey group for both the predator and the prey's speed (mean and dispersion).
-For hunting success, we quantified among individual differences in mean prey capture and controlled for the square-root of the game duration.
+The third component consists of pairwise comparisons between the individual identity random effect variances on the mean and dispersion part of the model across traits and experience levels, computed as a 15x15 (co)variance matrix.
+This allows us to assess whether predators that are on average slower/faster are more specialized or flexible, whether predators that adopted a slower/faster (or more specialized/flexible) tactic encountered prey that were faster/slower, and whether slower/faster predators had lower/greater hunting success.
 
-The model estimated the correlation between the individual identity random effect on the mean and on the dispersion within each trait (e.g.
-$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ pred})$) and among each trait (e.g.
-$cor(\sigma_{id_{m}\ pred}\ \sigma_{id_{d}\ prey})$) within a level of experience.
-In the first case, this allows us to assess, for example, whether predators that are on average slower/faster are more specialized or flexible.
-In the second case, it enables us to estimate, for example, whether predators that adopted a slower/faster (or more specialized/flexible) tactic encountered prey that were faster/slower, or if slower/faster predators had lower/greater hunting success.
+We controlled for the standardized average rank of the prey group for both the predator and the prey's speed on both the mean and the dispersion parts of the model.
+We included random effects for the game environment, the predator avatar, and the individual predator identity on the mean part of the model, and an individual identity random effect exclusively on the dispersion part.
+For hunting success, we modeled the mean part only and controlled for the standardized mean prey rank and game duration, and included an individual identity random effect.
 
-The full model has the following form, with each equation repeated three times (i.e. one for each level of experience):
+The model can be written as:
 
@@
 eqs <- c(
-  "speed_{pred} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
-  "log(\\sigma_{e,pred}) = X_{d}\\ b_{d} + Z\\ id_{d}",
-  "speed_{prey} = X_{m}\\ b_{m} + M\\ env_{m} + N\\ av_{m} + Z\\ id_{m} + e",
-  "log(\\sigma_{e,prey}) = X_{d}\\ b_{d} + Z\\ id_{d}",
-  "success_{pred} = X_{m}\\ b_{m} + Z\\ id_{m} + e"
+  "Y_{1}(T_{j}) = X_{1}(T_{j})\\ b_{1}(T_{j}) + M_{1}(T_{j})\\ en_{1}(T_{j}) + N_{1}(T_{j})\\ av_{1}(T_{j}) + Z_{1}(T_{j})\\ id_{1}(T_{j}) + e_{1}(T_{j})",
+  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = X_{d1}(T_{j})\\ b_{d1}(T_{j}) + Z_{d1}(T_{j})\\ id_{d1}(T_{j})",
+  "Y_{2}(T_{j}) = X_{2}(T_{j})\\ b_{2}(T_{j}) + M_{2}(T_{j})\\ en_{2}(T_{j}) + N_{2}(T_{j})\\ av_{2}(T_{j}) + Z_{2}(T_{j})\\ id_{2}(T_{j}) + e_{2}(T_{j})",
+  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = X_{d2}(T_{j})\\ b_{d2}(T_{j}) + Z_{d2}(T_{j})\\ id_{d2}(T_{j})",
+  "Y_{3}(T_{j}) = X_{3}(T_{j})\\ b_{3}(T_{j}) + Z_{3}(T_{j})\\ id_{3}(T_{j}) + e_{3}(T_{j})"
 )
 eqs_num <- c(
-    "(eqn. 1.1)",
-    "(eqn. 1.2)",
-    "(eqn. 2.1)",
-    "(eqn. 2.2)",
-    "(eqn. 3)"
+    "(1.1)",
+    "(1.2)",
+    "(2.1)",
+    "(2.2)",
+    "(3)"
 )
@@
   x <- fontsize(x, size = 12, part = "body")
-  x <- width(x, j = 1, width = 10, unit = "cm")
-  x <- width(x, j = 2, width = 6.51, unit = "cm")
+  x <- width(x, j = 1, width = 15.25, unit = "cm")
+  x <- width(x, j = 2, width = 1.26, unit = "cm")
 }
@@
 
-where $env$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$.
-$b$ is the vector of fixed effects with its incidence matrix $X$.
-The $m$ and $d$ subscripts indicate that an estimate is from the mean or dispersion part of the model, respectively.
-On the mean part, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$ and $av \sim N(0,\ I\ \sigma_{av})$).
+where $j$ is the index of the experience levels.
+The model is fitted on $n$ experience levels ($n = 3$) denoted by $T_{j}$, where $j$ ranges from 1 to $n$, being the novice, intermediate, and advanced levels.
+The $b$ terms are vectors of fixed effects with their incidence matrices $X$.
+The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$.
+The $d$ subscript indicates that a term is from the dispersion part of the model.
+On the mean part for all traits and experience levels, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$ and $av \sim N(0,\ I\ \sigma_{av})$).
 $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
 The residuals are assumed to follow a Gaussian distribution ($e \sim N(0,\ \sigma_{e})$).
-On the dispersion part, the residuals vary among individuals, allowing us to estimate among individual differences in specialization.
-The individual identity random effects on both the mean and dispersion parts follow a multivariate Gaussian distribution $[\begin{array}{cc} id_m \\ id_d \end{array}] \sim MVN(0,\ \Sigma_{id})$ where $\Sigma_{id}$ is a 15x15 variance-covariance matrix.
-The parameters $\sigma_{env}$, $\sigma_{av}$, and $\sigma_{id}$, correspond to the among environment, among avatar, and among individual standard deviations, respectively.
+The individual identity random effects on both the mean and dispersion parts across all response variables and experience levels are indexed in vector $u$.
+The vector $u$ of individual identity random effects follows a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix.
+We parametrized equations 1.1 to 2.2 with a Gaussian distribution family and used a beta-binomial distribution family for equation 3.
 
-We parameterized equations 1.1 to 2.2 with a Gaussian distribution family (predator and prey speed) and used a beta-binomial distribution family for equation 3 (predator hunting success).
 We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1)$: eqn.
@@
 
-Out of all five models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models accounting for the prey group's speed (Table 1).
+Out of all five GAMM models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models accounting for the prey group's speed (Table 1).
 Predators differed substantially in the relationship between hunting success and cumulative experience (i.e.
@@
 Moreover, all models where we did not account for prey speed had a global trend of predator experience that was nearly flat (results not shown).
-Yet, we see that there is an increase up to 13% in the probability of capturing all prey with experience in the population when we account for prey speed (Figure 1C).
+Yet, we see that there is an increase up to 13% in the probability of consuming all prey with experience in the population when we account for prey speed (Figure 1C).
 
@@
 Our results concord with what @Mougi.etal2011 define as a matching response relationship, because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success.
-These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013], but their broader consequences remain unclear.
+These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a], but their broader consequences remain unclear.
 Assuming that prey also learned during the interaction, which has been shown across many taxa [refs], we can deduce that learning from reciprocal interactions may contribute in stabilizing predator-prey systems, similar to Red Queen dynamics [@brockhurst2014].
@@
 The predators' hunting success (i.e.
-the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e.
+the probability of consuming the four prey) is on the y axis, and the predators' cumulative experience (i.e.
 the number of matches played prior to each observation) is on the x axis.

### 2023-05-31 manuscript/Chapter2-appendix1.Rmd
update appendix 1

@@
 
-b_draws[, c(31:33) := NULL]
+b_draws[, c(34:36) := NULL]
 
@@
       "b_successinterm_Zgame_duration",
-      "b_successadvanced_Zgame_duration"
+      "b_successadvanced_Zgame_duration",
+      "b_successnovice_Zprey_avg_rank",
+      "b_successinterm_Zprey_avg_rank",
+      "b_successadvanced_Zprey_avg_rank"
   )
@@
     "b_successinterm_Zgame_duration",
-    "b_successadvanced_Zgame_duration"
+    "b_successadvanced_Zgame_duration",
+    "b_successnovice_Zprey_avg_rank",
+    "b_successinterm_Zprey_avg_rank",
+    "b_successadvanced_Zprey_avg_rank"
   )
@@
 # Create trait column
-fixef_tab[
-  , trait := rep(c(
-    "predator speed", "predator speed",
-    "prey speed", "prey speed", "hunting success"),
-    6
-  )
+fixef_tab[, trait := ""][
+  parameter %like% "success", trait := "hunting success"][
+    parameter %like% "speed", trait := "predator speed"][
+      parameter %like% "preyspeed", trait := "prey speed"
       ]
@@
       rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
-      "match duration (mean)"
+      "match duration (mean)", "prey rank (mean)"
     ),
@@
 fixef_tab <- fixef_tab[, c(1, 2, 5, 4, 3)]
-table <- fixef_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]
+table <- fixef_tab[c(4, 6, 5, 7, 8, 10, 9, 11, 1, 2, 3)]
 
-# Because I can't align hunting success properly
-table[10, 1] <- " "
+# Because I can't align the rows properly
+# in the flextable object
+table[c(2:4, 6:8, 10, 11), 1] <- " "
 
@@
   # Align repeated rows on column 1
-  merge_v(j = 1) %>%
+  #merge_v(j = 1) %>%
   valign(j = 1, valign = "top", part = "body") %>%
@@
   set_caption(
-    caption = "Table S1. Posterior medians and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    caption = "Table S1. Posterior medians and 95% HDP intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
     style = "Table Caption"

### 2023-05-31 manuscript/Chapter2-appendix1.Rmd
update appendix 1 fig legends

@@
   set_caption(
-    caption = "Table S1. Posterior medians and 95% HDP intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
+    caption = "Table S1. Posterior medians and 95% HPD intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
     style = "Table Caption"
@@
       as_sup("a "),
-      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
+      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale.",
       as_sup("\nb "),
@@
       as_sup("\nc "),
-      "Values on the dispersion (i.e.
+      "The standard deviation values on the dispersion part of the equation (i.e.
 sigma) for predator speed indicate among individual differences in behavioural specialization.
@@
   set_caption(
-    caption = "Table S2.
-Posterior medians and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
-All the reported values are standard deviations.",
+    caption = "Table S2. Posterior medians and 95% HPD intervals of the random effect standard deviations estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.",
     style = "Table Caption"
@@
 Each fitted curve represents an individual predator.
+The individual curves are separated by differences between their first and last predicted value, and displayed as such in three distinct panels.
 (A) Individuals with a >0.5 unit increase in hunting success with experience (B) Individuals with a <-0.5 unit decrease in hunting success with experience.
@@
 
-```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Correlations between the predators' mean hunting success (y axis) and intra individual variance in speed (x axis) to test for differences in success between specialist and flexible hunters.
+```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Correlations between the predators' mean hunting success (y axis) and intra individual variance in speed (x axis) to test for differences in success between individuals along the flexible-specialist hunter continuum.
+Each point represents the posterior median predicted value of an individual predator along with its 95% HPD interval.
 Individuals with lower IIV are specialist hunters, while individuals with higher IIV are flexible hunters.

### 2023-05-31 manuscript/Chapter2-appendix3.Rmd
update appendix 3

@@
 
-# Extract the fixed effects from the model
-eff_tab <- data.table(fixef(fit), keep.rownames = TRUE)
-eff_tab <- eff_tab[, c(1, 2, 4:5)]
-
-# Rename variables
-setnames(
-  eff_tab,
-  c("rn", "Q2.5", "Q97.5"),
-  c("parameter", "lower_ci", "upper_ci")
+# Extract the fixed effects posterior samples
+b_draws <- data.table(
+  as_draws_df(
+    fit, variable = "^b_", regex = TRUE
+  )
 )
 
-# Add a column that specifies the experience level
-eff_tab[parameter %like% "novice", xp_level := "novice"]
-eff_tab[parameter %like% "interm", xp_level := "intermediate"]
-eff_tab[parameter %like% "advanced", xp_level := "advanced"]
+b_draws[, c(34:36) := NULL]
 
-# Back transform success
-eff_tab[
-  parameter %like% "success",
-  c(2:4) := lapply(.SD, function(x) {plogis(x)}),
-  .SDcols = c(2:4)
+# Back-transform the parameters ----------------------------------------------
+
+# Take the exponent of sigma parameters
+b_draws[
+  , c("b_sigma_speednovice_Intercept",
+      "b_sigma_speedinterm_Intercept",
+      "b_sigma_speedadvanced_Intercept",
+      "b_sigma_preyspeednovice_Intercept",
+      "b_sigma_preyspeedinterm_Intercept",
+      "b_sigma_preyspeedadvanced_Intercept",
+      "b_sigma_speednovice_Zprey_avg_rank",
+      "b_sigma_speedinterm_Zprey_avg_rank",
+      "b_sigma_speedadvanced_Zprey_avg_rank",
+      "b_sigma_preyspeednovice_Zprey_avg_rank",
+      "b_sigma_preyspeedinterm_Zprey_avg_rank",
+      "b_sigma_preyspeedadvanced_Zprey_avg_rank"
+  )
+  := lapply(.SD, function(x) {exp(x)}),
+  .SDcols = c(
+    "b_sigma_speednovice_Intercept",
+    "b_sigma_speedinterm_Intercept",
+    "b_sigma_speedadvanced_Intercept",
+    "b_sigma_preyspeednovice_Intercept",
+    "b_sigma_preyspeedinterm_Intercept",
+    "b_sigma_preyspeedadvanced_Intercept",
+    "b_sigma_speednovice_Zprey_avg_rank",
+    "b_sigma_speedinterm_Zprey_avg_rank",
+    "b_sigma_speedadvanced_Zprey_avg_rank",
+    "b_sigma_preyspeednovice_Zprey_avg_rank",
+    "b_sigma_preyspeedinterm_Zprey_avg_rank",
+    "b_sigma_preyspeedadvanced_Zprey_avg_rank"
+  )
 ]
 
-# Back transform sigma
-eff_tab[
-  parameter %like% "sigma",
-  c(2:4) := lapply(.SD, function(x) {exp(x)}),
-  .SDcols = c(2:4)
+# plogis for the success parameters
+b_draws[
+  , c("b_successnovice_Intercept",
+      "b_successinterm_Intercept",
+      "b_successadvanced_Intercept",
+      "b_successnovice_Zgame_duration",
+      "b_successinterm_Zgame_duration",
+      "b_successadvanced_Zgame_duration",
+      "b_successnovice_Zprey_avg_rank",
+      "b_successinterm_Zprey_avg_rank",
+      "b_successadvanced_Zprey_avg_rank"
+  )
+  := lapply(.SD, function(x) {plogis(x)}),
+  .SDcols = c(
+    "b_successnovice_Intercept",
+    "b_successinterm_Intercept",
+    "b_successadvanced_Intercept",
+    "b_successnovice_Zgame_duration",
+    "b_successinterm_Zgame_duration",
+    "b_successadvanced_Zgame_duration",
+    "b_successnovice_Zprey_avg_rank",
+    "b_successinterm_Zprey_avg_rank",
+    "b_successadvanced_Zprey_avg_rank"
+  )
 ]
 
-# Round values to 3 digits
-eff_tab[, c(2:4) := round(eff_tab[, c(2:4)], digits = 2)]
+# Reshape the table -----------------------------------------------------------
 
-# Reorganize the table ------------------------------------------------------
+fixef_tab <- melt(
+  b_draws,
+  variable.name = "parameter"
+)
+
+# Summarize the values (medians + 95% CI) -------------------------------------
+
+# Intervals
+lower_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[1]
+}
+upper_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+# Summarize values
+fixef_tab[, ":=" (median = median(value),
+                  lower_ci = lower_interval(value),
+                  upper_ci = upper_interval(value)),
+          by = .(parameter)]
+
+fixef_tab <- unique(fixef_tab[, .(parameter, median, lower_ci, upper_ci)])
+fixef_tab[, c(2:4) := round(fixef_tab[, c(2:4)], digits = 2)]
+
+# Rearrange the table --------------------------------------------------------
+
+# Add a column that specifies the experience level
+fixef_tab[parameter %like% "novice", xp_level := "novice"]
+fixef_tab[parameter %like% "interm", xp_level := "intermediate"]
+fixef_tab[parameter %like% "advanced", xp_level := "advanced"]
+
+# Paste upper and lower ci with estimate
+fixef_tab[, estimate := paste(format(median, digits = 2), "(")]
+fixef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
+fixef_tab[, estimate := paste(estimate, ",", sep = "")]
+fixef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
+fixef_tab[, estimate := paste(estimate, ")", sep = "")]
+fixef_tab[, c("median", "lower_ci", "upper_ci") := NULL]
 
 # reorder columns, and then rows based on xp level
-eff_tab <- eff_tab[, c(5, 1:4)]
 setorder(
-  eff_tab,
+  fixef_tab,
   cols = -"xp_level"
@@
 # Create trait column
-eff_tab[
-  , trait := rep(c(
-    "predator speed", "predator speed",
-    "prey speed", "prey speed", "hunting success"),
-    6
-  )
+fixef_tab[, trait := ""][
+  parameter %like% "success", trait := "hunting success"][
+    parameter %like% "speed", trait := "predator speed"][
+      parameter %like% "preyspeed", trait := "prey speed"
       ]
 
-# Rename parameter
-eff_tab[
+# Rename parameter column
+fixef_tab[
   , parameter := rep(
@@
       rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
-         "match duration (mean)"
+      "match duration (mean)", "prey rank (mean)"
     ),
@@
 
-# Reorder columns
-eff_tab <- eff_tab[, c(1, 2, 5, 4, 3)]
+# Reorder columns and rows
+fixef_tab <- fixef_tab[, c(1, 2, 5, 4, 3)]
+table <- fixef_tab[c(4, 6, 5, 7, 8, 10, 9, 11, 1, 2, 3)]
 
-# Reorder rows
-table <- eff_tab[c(3, 5, 4, 6, 7, 9, 8, 10, 1, 2)]
-
-# Because I can't align hunting success properly
-table[10, 1] <- " "
+# Because I can't align the rows properly
+# in the flextable object
+table[c(2:4, 6:8, 10, 11), 1] <- " "
 
@@
 
-tab2 <-
+tab1 <-
 
@@
     caption = "Table S1.
-Posterior means and 95% credible intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
+Posterior medians and 95% HPD intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
 The coefficients are from the model that includes the outlier.",
@@
 
-tab2
+tab1
 
@@
 
-tab3 <-
+tab2 <-
 
@@
       as_sup("a "),
-      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale. All the reported values are standard deviations.",
+      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale.",
       as_sup("\nb "),
-      "The intercept values on the mean part of the equation for all traits indicate among individual differences in mean behaviour and success.",
+      "The standard deviation values on the mean part of the equation indicate, for all traits, among individual differences in mean behaviour, prey encountered, and success.",
       as_sup("\nc "),
-      "The intercept values on the dispersion (i.e.
-sigma) part of the equation for predator speed indicate among individual differences in behavioural specialization.
-For prey speed and hunting success, they indicate among individual differences in the variability of prey encounters and variability in hunting success, respectively."
+      "The standard deviation values on the dispersion part of the equation (i.e.
+sigma) for predator speed indicate among individual differences in behavioural specialization.
+For prey speed, they indicate among individual differences in the variability of prey encounters."
     ),
@@
     caption = "Table S2.
-Posterior means and 95% credible intervals of the random effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
+Posterior medians and 95% HPD intervals of the random effect standard deviations estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
 The coefficients are from the model that includes the outlier.",
@@
 
-tab3 <- autofit(tab3)
-
-tab3
+tab2
 
@@
 
-```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% credible intervals between the parameter values of each predator experience level predicted by the MDHGLM.
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences between the parameter values of each predator experience level predicted by the MDHGLM along with their and 95% HPD intervals.
 The test is displayed on the y axis (i.e.
-whether the group of interest has either a greater or smaller value), and the parameter value is displayed on the x axis.
-Each panel represent the experience level groups that are being compared.
+whether the experience level of interest has a greater or smaller value), and the parameter value is displayed on the x axis.
+Each panel represent the experience levels being compared.
 The results are from the model that includes the outlier."}
@@
 
-```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences and 95% credible intervals in the correlations of players when they were advanced vs novice.
+```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences in the correlations of players when they were advanced vs novice along with their 95% HPD intervals.
 The difference is displayed on the x axis and the parameter correlations are displayed on the y axis.
+Positive values indicate that the correlation was greater when predators where advanced, while negative values indicate that the correlation was greater when predators where novices.
 The results are from the MDHGLM that includes the outlier."}

### 2023-05-31 code/04_code_figures/appendix3_figureS1.R
update appendix3 fig S1

@@ -50,6 +50,56 @@ dt <- dt[, c(1:15, 54:68)]
 
 
 
+# Back-transform values -------------------------------------------------
+
+# Take the exponent of sigma parameters
+dt[
+  , c("b_sigma_speednovice_Intercept",
+      "b_sigma_speedinterm_Intercept",
+      "b_sigma_speedadvanced_Intercept",
+      "b_sigma_preyspeednovice_Intercept",
+      "b_sigma_preyspeedinterm_Intercept",
+      "b_sigma_preyspeedadvanced_Intercept",
+      "sd_predator_id__sigma_speednovice_Intercept",
+      "sd_predator_id__sigma_speedinterm_Intercept",
+      "sd_predator_id__sigma_speedadvanced_Intercept",
+      "sd_predator_id__sigma_preyspeednovice_Intercept",
+      "sd_predator_id__sigma_preyspeedinterm_Intercept",
+      "sd_predator_id__sigma_preyspeedadvanced_Intercept"
+  )
+  := lapply(.SD, function(x) {exp(x)}),
+  .SDcols = c(
+    "b_sigma_speednovice_Intercept",
+    "b_sigma_speedinterm_Intercept",
+    "b_sigma_speedadvanced_Intercept",
+    "b_sigma_preyspeednovice_Intercept",
+    "b_sigma_preyspeedinterm_Intercept",
+    "b_sigma_preyspeedadvanced_Intercept",
+    "sd_predator_id__sigma_speednovice_Intercept",
+    "sd_predator_id__sigma_speedinterm_Intercept",
+    "sd_predator_id__sigma_speedadvanced_Intercept",
+    "sd_predator_id__sigma_preyspeednovice_Intercept",
+    "sd_predator_id__sigma_preyspeedinterm_Intercept",
+    "sd_predator_id__sigma_preyspeedadvanced_Intercept"
+  )
+]
+
+# Back-transform hunting success
+dt[
+  , c("b_successnovice_Intercept",
+      "b_successinterm_Intercept",
+      "b_successadvanced_Intercept"
+  )
+  := lapply(.SD, function(x) {plogis(x)}),
+  .SDcols = c(
+    "b_successnovice_Intercept",
+    "b_successinterm_Intercept",
+    "b_successadvanced_Intercept"
+  )
+]
+
+
+
 # Prepare the data ------------------------------------------------------
 
 # Reshape the table

### 2023-05-31 manuscript/Chapter2-appendix3.Rmd
update appendix 3 with fig s2

@@
 
-```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences in the correlations of players when they were advanced vs novice along with their 95% HPD intervals.
-The difference is displayed on the x axis and the parameter correlations are displayed on the y axis.
+```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences in the correlations of players when they were advanced vs novice along with their 95% HPD intervals.
+The difference is displayed on the y axis and the parameter correlations are displayed on the x axis.
 Positive values indicate that the correlation was greater when predators where advanced, while negative values indicate that the correlation was greater when predators where novices.

### 2023-05-31 code/04_code_figures/appendix3_figureS2.R

@@ -106,11 +106,11 @@ tab <- unique(
 tab[, c(2:8) := round(tab[, c(2:8)], digits = 2)]
 
 names <- c(
-  "(mean speed, IIV speed)", "(mean speed, mean prey speed)",
-  "(IIV speed, mean prey speed)", "(mean speed, IIV prey speed)",
-  "(IIV speed, IIV prey speed)", "(mean prey speed, IIV prey speed)",
-  "(mean speed, mean success)", "(IIV speed, mean success)",
-  "(mean prey speed, mean success)", "(IIV prey speed, mean success)"
+  "mean speed\n IIV speed", "mean speed\n mean prey speed",
+  "IIV speed\n mean prey speed", "mean speed\n IIV prey speed",
+  "IIV speed\n IIV prey speed", "mean prey speed\n IIV prey speed",
+  "mean speed\n mean success", "IIV speed\n mean success",
+  "mean prey speed\n mean success", "IIV prey speed\n mean success"
 )
 tab[, variable_adv := names]
 
@@ -138,6 +138,8 @@ colors <- c(
   "0.50" = "gray21"
 )
 
+scaleFUN <- function(x) sprintf("%.2f", x)
+
 fig <- ggplot(
   tab,
   aes(x = variable_adv, y = median_difference)
@@ -146,10 +148,6 @@ fig <- ggplot(
     yintercept = 0, linewidth = 1, colour = "red",
     linetype = "dashed", alpha = 0.5
   ) +
-  #geom_pointrange(
-  #  aes(ymin = lower_ci_95, ymax = upper_ci_95),
-  #  size = 0.5, position = position_dodge(width = 0.8)
-  #) +
   geom_linerange(
     aes(ymin = lower_ci_95,
         ymax = upper_ci_95,
@@ -172,23 +170,34 @@ fig <- ggplot(
     key_glyph = "path"
   ) +
   geom_point(size = 3, color = "black") +
-  ylab("\nPosterior median difference") +
-  scale_y_continuous(breaks = seq(-0.2, 0.2, 0.1)) +
+  ylab("Posterior median difference\n") +
+  #scale_y_continuous(
+  #  labels = scaleFUN,
+  #  breaks = seq(-0.3, 0.3, 0.15),
+  #  limits = c(-0.3,0.3)
+  #  ) +
+  scale_y_continuous(
+    breaks = seq(-0.2, 0.2, 0.1)
+    ) +
   scale_color_manual(
     name = "Density:",
[…]

### 2023-05-31 code/04_code_figures/figure4-c.R

@@ -143,6 +143,22 @@ colors <- c(
 
 scaleFUN <- function(x) sprintf("%.2f", x)
 
+custom_theme <- theme(
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(
+      face = "plain", size = 11,
+      color = "black"),
+    axis.text.y = element_text(
+      face = "plain", size = 12,
+      color = "black"),
+    axis.title = element_text(size = 15, face = "plain", color = "black"),
+    panel.grid = element_blank(),
+    legend.position = "bottom",
+    legend.key = element_rect(fill = "transparent"),
+    legend.title = element_text(size = 15),
+    legend.text = element_text(size = 13)
+  )
+
 fig <- ggplot(
   tab,
   aes(x = variable_adv, y = median_difference)
@@ -187,21 +203,7 @@ fig <- ggplot(
     values = colors
   ) +
   theme_bw() +
-  theme(
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(
-      face = "plain", size = 11,
-      color = "black"),
-    axis.text.y = element_text(
-      face = "plain", size = 12,
-      color = "black"),
-    axis.title = element_text(size = 15, face = "plain", color = "black"),
-    panel.grid = element_blank(),
-    legend.position = "bottom",
-    legend.key = element_rect(fill = "transparent"),
-    legend.title = element_text(size = 15),
-    legend.text = element_text(size = 13)
-  )
+  custom_theme
 
 
 

### 2023-05-31 manuscript/Chapter2-appendix3.Rmd
update appendix S3

--- 2023-05-31 manuscript/Chapter2-appendix3.Rmd
@@
 
-```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences between the parameter values of each predator experience level predicted by the MDHGLM along with their and 95% HPD intervals.
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% HPD intervals comparing the parameter values predicted by the MDHGLM among each predator experience level.
 The test is displayed on the y axis (i.e.
@@
 
-```{r figS2, out.width = "80%", fig.cap = "**Figure S2.** Posterior median differences in the correlations of players when they were advanced vs novice along with their 95% HPD intervals.
-The difference is displayed on the x axis and the parameter correlations are displayed on the y axis.
+```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences and 95% HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels.
+The difference is displayed on the y axis and the correlated parameters are displayed on the x axis.
 Positive values indicate that the correlation was greater when predators where advanced, while negative values indicate that the correlation was greater when predators where novices.

### 2023-06-01 manuscript/Chapter2-appendix3.Rmd
update appendix S3 figure legends

@@
 
-```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% HPD intervals comparing the parameter values predicted by the MDHGLM among each predator experience level.
-The test is displayed on the y axis (i.e.
-whether the experience level of interest has a greater or smaller value), and the parameter value is displayed on the x axis.
-Each panel represent the experience levels being compared.
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% HPD intervals comparing the parameter values predicted by the MDHGLM among all predator experience levels.
+The parameter being compared is on the y axis, and the difference in parameter values between two experience levels is displayed on the x axis.
+The pairwise comparisons between experience levels are displayed across the three panels A, B, and C.
 The results are from the model that includes the outlier."}

### 2023-06-01 manuscript/Chapter2-appendix3.Rmd
updated appendix 3 legends

@@
 
-```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and 95% HPD intervals comparing the parameter values predicted by the MDHGLM among all predator experience levels.
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and HPD intervals comparing the parameter values predicted by the MDHGLM among all predator experience levels.
 The parameter being compared is on the y axis, and the difference in parameter values between two experience levels is displayed on the x axis.
@@
 
-```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences and 95% HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels.
+```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences and HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels.
 The difference is displayed on the y axis and the correlated parameters are displayed on the x axis.

### 2023-06-01 manuscript/Chapter2-manuscript.Rmd
forgot to remove a "test" text in journal name
updated MS methods, figure captions, and first paragraph of discussion with some ideas

@@
 
-Journal name : Ecology test
+Journal name : Ecology
 
@@
 
-We tested whether foraging behaviour changed with experience, and compared the success of flexible vs specialist hunters, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
-We fitted the model on the predator's speed ($Y_{1}$), the prey's speed ($Y_{2}$), and the predator's hunting success ($Y_{3}$), which allowed us to simultaneously estimate three distinct components for each experience level.
+We tested whether foraging behaviour changed with experience, and compared the success of predators along the flexible-specialist hunter continuum, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
+We fitted the model on the predator's speed ($Y_{1}$), the prey's speed ($Y_{2}$), and the predator's hunting success ($Y_{3}$), using a Gaussian distribution family for the predator and the prey's speed, and a beta-binomial distribution family for the predator's success.
+
+The model simultaneously estimated three distinct components for each experience level and each trait.
 The first component is among individual variation in mean speed and success (the mean part of the model), allowing to test for individual differences in tactic use (i.e.
@@
 # Prepare equations
+#eqs <- c(
+#  "Y_{1}(T_{j}) = X_{1}(T_{j})\\ b_{1}(T_{j}) + M_{1}(T_{j})\\ en_{1}(T_{j}) + N_{1}(T_{j})\\ av_{1}(T_{j}) + Z_{1}(T_{j})\\ #id_{1}(T_{j}) + e_{1}(T_{j})",
+#  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = X_{d1}(T_{j})\\ b_{d1}(T_{j}) + Z_{d1}(T_{j})\\ id_{d1}(T_{j})",
+#  "Y_{2}(T_{j}) = X_{2}(T_{j})\\ b_{2}(T_{j}) + M_{2}(T_{j})\\ en_{2}(T_{j}) + N_{2}(T_{j})\\ av_{2}(T_{j}) + Z_{2}(T_{j})\\ #id_{2}(T_{j}) + e_{2}(T_{j})",
+#  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = X_{d2}(T_{j})\\ b_{d2}(T_{j}) + Z_{d2}(T_{j})\\ id_{d2}(T_{j})",
+#  "Y_{3}(T_{j}) = X_{3}(T_{j})\\ b_{3}(T_{j}) + Z_{3}(T_{j})\\ id_{3}(T_{j}) + e_{3}(T_{j})"
+#)
+
 eqs <- c(
-  "Y_{1}(T_{j}) = X_{1}(T_{j})\\ b_{1}(T_{j}) + M_{1}(T_{j})\\ en_{1}(T_{j}) + N_{1}(T_{j})\\ av_{1}(T_{j}) + Z_{1}(T_{j})\\ id_{1}(T_{j}) + e_{1}(T_{j})",
-  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = X_{d1}(T_{j})\\ b_{d1}(T_{j}) + Z_{d1}(T_{j})\\ id_{d1}(T_{j})",
-  "Y_{2}(T_{j}) = X_{2}(T_{j})\\ b_{2}(T_{j}) + M_{2}(T_{j})\\ en_{2}(T_{j}) + N_{2}(T_{j})\\ av_{2}(T_{j}) + Z_{2}(T_{j})\\ id_{2}(T_{j}) + e_{2}(T_{j})",
-  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = X_{d2}(T_{j})\\ b_{d2}(T_{j}) + Z_{d2}(T_{j})\\ id_{d2}(T_{j})",
-  "Y_{3}(T_{j}) = X_{3}(T_{j})\\ b_{3}(T_{j}) + Z_{3}(T_{j})\\ id_{3}(T_{j}) + e_{3}(T_{j})"
+  "Y_{1}(T_{j}) = T^2_{j}(X_{1}\\ b_{1}) + T^2_{j}(M_{1}\\ en_{1}) + T^2_{j}(N_{1}\\ av_{1}) + T^2_{j}(Z_{1}\\ id_{1}) + e_{1}(T_{j})",
+  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = T^2_{j}(X_{d1}\\ b_{d1}) + T^2_{j}(Z_{d1}\\ id_{d1})",
+  "Y_{2}(T_{j}) = T^2_{j}(X_{2}\\ b_{2}) + T^2_{j}(M_{2}\\ en_{2}) + T^2_{j}(N_{2}\\ av_{2}) + T^2_{j}(Z_{2}\\ id_{2}) + e_{2}(T_{j})",
+  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = T^2_{j}(X_{d2}\\ b_{d2}) + T^2_{j}(Z_{d2}\\ id_{d2})",
+  "Y_{3}(T_{j}) = T^2_{j}(X_{3}\\ b_{3}) + T^2_{j}(Z_{3}\\ id_{3}) + e_{3}(T_{j})"
 )
+
 eqs_num <- c(
@@
 The $d$ subscript indicates that a term is from the dispersion part of the model.
-On the mean part for all traits and experience levels, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($env \sim N(0,\ I\ \sigma_{env})$ and $av \sim N(0,\ I\ \sigma_{av})$).
+On the mean part for all traits and experience levels, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en \sim N(0,\ I\ \sigma_{en})$ and $av \sim N(0,\ I\ \sigma_{av})$).
 $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
-The residuals are assumed to follow a Gaussian distribution ($e \sim N(0,\ \sigma_{e})$).
+The residuals are assumed to follow a Gaussian distribution ($e \sim N(0,\ Diag \{\sigma_{e}\})$) *explain here that each has their own individual variance*.
 The individual identity random effects on both the mean and dispersion parts across all response variables and experience levels are indexed in vector $u$.
 The vector $u$ of individual identity random effects follows a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix.
-We parametrized equations 1.1 to 2.2 with a Gaussian distribution family and used a beta-binomial distribution family for equation 3.
 
@@
 We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
+We report all the posterior parameter estimates using the median of the posterior distribution (or the mean if stated otherwise) with the highest posterior density (HPD) intervals at 50%, 80%, and 95%.
 
@@
 
-Hunting experience is predicted to increase predator foraging specialization when resources are predictable [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
-However, when resources vary, learning with experience should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-Our results show that there was no directional increase in either behavioural specialization or flexibility with experience at the population level.
-Instead, individual predators developed their own expertise and behavioural trajectory over successive encounters with the prey.
-There was a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy.
+Learning from experience is predicted to increase foraging specialization when predators encounter prey behaving predictably through time [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
+However, if predators encounter prey behaving unpredictably through time, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
+Our results show that predators substantially increased their hunting success with experience.
+While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, we found that individual predators developed their own expertise and behavioural trajectories over successive encounters with the prey.
+This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy.
+
+*parler directement du succès des tactiques ici?*
+
+*ici parler de la covariance qui suggère un ajustement par les deux. Peut être dire que c'était fortement corrélé, mais que ça changeait pas tant avec l'expérience*
 Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period.
-With experience, predators increasingly matched their foraging specialization to the speed of the prey that they encountered, but they did not achieve greater success, probably because the prey were also matching their speed to the predator.
+
+*ici, changer la phrase pour parler que l"interaction a changé, comme ça c'est aveugle au feedback*
+With experience, predators increasingly matched their foraging specialization to the speed of the prey that they encountered,
+
+but they did not achieve greater success, probably because the prey were also matching their speed to the predator.
 Our observations suggest that predators in *DBD* learn to adjust their foraging specialization, not to the variance, but to the mean behaviour of the prey that they encounter throughout their lifetime in the game.
@@
   , model := c(
-    "predator xp + group-level smoothers + prey speed",
-    "group-level smoothers + prey speed",
-    "group-level smoothers",
-    "predator xp + group-level smoothers",
-    "predator xp"
+    "predator xp + ID smoothers + prey rank + prey speed",
+    "ID smoothers + prey rank + prey speed",
+    "ID smoothers + prey rank",
+    "predator xp + ID smoothers + prey rank",
+    "predator xp + prey rank"
     )
@@
   set_caption(
-    caption = "Table 1. Leave-one-out cross-validation table of the five hierarchical GAMMs relating hunting success to player experience.",
+    caption = "Table 1. Leave-one-out cross-validation table of the five GAMMs relating hunting success to predator experience.",
     style = "Table Caption"
@@
 
-**Figure 1.** Among individual differences in the development of hunting expertise.
+**Figure 1.** Median posterior predictions of the development of predator hunting expertise.
 The predators' hunting success (i.e.
@@
 the number of matches played prior to each observation) is on the x axis.
-Each fitted curve represents an individual predator.
-(A) A generalized additive mixed model where we do not control for prey speed (B) A generalized additive mixed model where we control for prey speed.
+Panels A and C show among individual differences in the development of expertise, while panels B and D show the development of expertise for the average individual.
+(A-B) GAMM where we control for the average prey rank (C-D) GAMM where we control for the average prey rank and the average speed of the prey group.
 
-**Figure 2.** Posterior median differences and highest posterior density intervals between each predator experience level's parameters.
-Each panel shows the experience levels that are compared.
-The parameter compared is on the y axis, and the difference of the values predicted by the MDHGLM is on the x axis.
-The intercepts correspond to mean population speed and specialization.
-The predator ID on the mean are individual differences in mean speed, mean speed of prey groups encountered, and success.
-The predator ID on the dispersion (i.e.
-sigma) are individual differences in specialization, and in the heterogeneity of prey encountered.
+**Figure 2.** Median posterior differences and HPD intervals comparing the parameter values predicted by the MDHGLM among all predator experience levels.
+The parameter being compared is on the y axis, and the difference in parameter values between two experience levels is on the x axis.
+The pairwise comparisons between experience levels are displayed across the three panels A, B, and C.
+The population mean corresponds to the population's mean speed, mean speed of the prey encountered, and mean success.
+The population variation corresponds to the population's foraging specialization and variation in speed of the prey encountered.
+The individual variation in means corresponds to individual differences in mean speed, while individual variation in IIV indicates individual differences in foraging specialization and in the variation of the groups of prey encountered.
 
@@
 Both figure panels are ordered by ascending degree of increase in either specialization or flexibility.
-We selected the individuals displayed in the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selecting those with the greatest difference using the 25% and 75% quantiles.
-Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.27 standard deviations.
+We built the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selected those with the greatest difference using the 25% and 75% quantiles.
+Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.2 standard deviations.
 
-**Figure 4.** Correlation matrices of the MDHGLM relating the mean and intra individual variability (IIV) in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
-Larger dark blue circles indicate stronger positive correlations (positive values on the color legend), while larger dark red circles indicate stronger negative correlations (negative values on the color legend).
+**Figure 4.** Correlation matrices of the MDHGLM relating the mean and IIV in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+Larger dark blue circles indicate stronger positive correlations (positive values on the colour legend), while larger dark red circles indicate stronger negative correlations (negative values on the colour legend).
 A) Correlations when predators were novice hunters.
 B) Correlations when predators were advanced hunters.
-C) Posterior median differences and highest posterior density intervals comparing the correlations between traits when predators were advanced vs novice.
-The differences were computed on the absolute values of the correlations since the signs did not change with experience, such that positive values indicate an increase in correlation at the advanced stage.
-The median difference is displayed on the y axis and the trait correlations being compared are displayed on the x axis.
+C) Posterior median differences and HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels.
+The difference is displayed on the y axis and the correlated traits being compared are displayed on the x axis.Positive values indicate an increase in correlation strength from novice to the advanced stage, while negative values indicate stronger correlations when predators were novice.
 

### 2023-06-01 manuscript/Chapter2-manuscript.Rmd
added some elements to the hypotheses and updated the methods

@@
 Indeed, predator populations often comprise assemblages of individuals specializing on different foraging tactics, with consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
-Despite the clear evidence that individual specialization is important for predator-prey interactions, its underlying mechanisms remain surprisingly unclear.
+Despite clear evidence that individual specialization is important in predator-prey interactions, its underlying mechanisms remain surprisingly unclear.
 One hypothesis suggests that reciprocal interactions between predators and prey could drive individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
@@
 Theory predicts that foraging specialization may emerge via learning and expertise acquisition [@Tinker.etal2009;@Dukas2019].
-@Dukas2019 defines expertise as the characteristics, skills, and knowledge allowing individuals with extensive experience to outperform novices on complex tasks.
+@Dukas2019 defines expertise as the characteristics, skills, and knowledge that allow individuals with extensive experience to outperform novices on complex tasks.
 It is described as the relationship between success and experience, where extensive practice optimizes success when individuals reach an advanced level of experience.
@@
 Alternatively, the costs/risks faced by hunters when switching tactics may be offset through extensive practice, as individuals gain experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
-To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period of time, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
+To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
 However, predators can differ in the challenges that they face during their lifetime, which could result in both processes (i.e.
 specialization and flexibility) operating at the same time within a predator population.
-For instance, some individuals may hunt in habitats where prey are faster, which are often proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-It should thus be essential for predators to learn how to adjust their tactic to their prey to optimize their success.
+For example, some individuals may hunt in habitats where prey are faster, which are often proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
+Thus, it should be essential for predators to learn how to adjust their tactic to their prey to optimize their success.
 
@@
 Some studies have found greater success for individuals that use specialized foraging tactics [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others found that individuals using flexible foraging tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021].
-This disrepancy may in part be due to the limited information we have on the ecological contexts favoring specialization over flexibility.
+This disrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility.
 However, many studies have found that both type of foragers can also attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018].
@@
 Given the dynamic nature of predator-prey interactions, it is unlikely that evolution alone could explain such behavioural adjustments by predators, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].
-Thus, uncovering the role of learning during direct predator-prey interactions would help in better predicting the behavioural decisions and the success of predators when they are hunting.
+Thus, uncovering the role of learning during direct predator-prey interactions would help to predict the behavioural decisions and the success of predators when they are hunting.
 
-A recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and prey.
+A recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and the prey.
 We recently showed, using an online predator-prey videogame called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge [@FraserFranco.etal2022].
-In this dynamic virtual system, four prey players need to forage for resources while avoiding predation by a predator player.
-The prey can contribute to the group's success by healing or helping others escape the predator, or be selfish and attempt to escape by themselves [@Cere.etal2021].
+In this dynamic virtual system, four prey players need to forage for resources while avoiding predation by a fifth player.
+The prey can contribute to the group's success by healing or helping others escape from the predator, or be selfish and attempt to escape by themselves [@Cere.etal2021].
 The predators' hunting tactics and success are driven by the movement of the prey [@FraserFranco.etal2022].
@@
 in prep).
-These examples outline how virtual systems could be useful in identifying general ecological patterns, which might in turn help to advance predator-prey research.
+These examples outline how virtual systems could be useful in identifying general ecological patterns, which in turn might help to advance predator-prey research.
 They also generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological scenarios.
@@
 We define foraging tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e.
-IIV) in movement speed from one match to the next, where low IIV translates to individual specialization.
-If experience reduces the costs of switching between low and high speeds, we predict that individuals (and thus the population) should all converge towards flexible speeds.
-If experience enables the refinement of the tactics to hunt specific types of prey, then all individuals may instead specialize in their speed.
+IIV) in movement speed across matches, where low IIV translates to individual specialization (e.g.
+always using a fast tactic).
+If experience reduces the costs of switching between low and high speeds as predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds.
+If experience increases a tactic's efficiency for specific types of prey assuming that all individuals encounter similar groups of prey, then they may instead specialize in their speed.
 In both scenarios, among individual variation in IIV (i.e.
-individual specialization) should be low because everyone is either a specialist or a generalist, but the population variance should either increase (flexibility) or decrease (specialization).
+individual differences in specialization) should be low across experience because everyone is either a flexible or a specialist forager, but the population variance would either increase (flexibility) or decrease (specialization).
 Alternatively, both processes may operate at the same time if behavioural interactions with the prey vary among predators, such that among individual variation in IIV should increase.
@@
 
-*DBD* is a survival asymmetric (i.e.
-a game where the gameplay mechanics differ between two groups) multiplayer online game developed by Behaviour Interactive Inc, in which players can play either as a predator or a prey.
-Every match includes only one predator and four preys.
+*DBD* is a survival asymmetric multiplayer online game (i.e.
+a game where the gameplay mechanics differ between two groups) developed by Behaviour Interactive Inc, in which players can play either as a predator or a prey.
+Every match includes only one predator and four prey.
 The objective of the predator is to hunt and capture the prey, and the objective of the prey is to search for resources while avoiding the predator.
@@
 We labeled predators as novices for matches where they had cumulated less than 100 matches, intermediate for matches where they had cumulated between 100 and 299 matches, and advanced for matches where they had cumulated more than 299 matches (max 499).
-Since our goal was to monitor predator players throughout their experience and that they all played at least 300 matches, they appeared in all the three experience categories.
+Since our goal was to monitor predator players throughout their experience and that they all played at least 300 matches, they all appeared in each of the three experience categories.
 
@@
 
-The models were fitted in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
-All our statistical analyses were executed on Cedar (https://docs.alliancecan.ca/wiki/Cedar), a computer cluster maintained by the Digital Research Alliance of Canada.
-The operating system for Cedar is CentOS Linux 7.
+All models were fitted under a Bayesian framework in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
+The models were compiled on Cedar, a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
+The operating system for Cedar is CentOS Linux 7, and each model required 64GB of RAM with 48 cores to compile within $\le$5 days.
 
@@
 
-We tested how prey influence the development of predator expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e.
+We tested how prey influenced the development of predator expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e.
 number of prey consumed) and the predators' cumulative experience (i.e.
@@
 global smoother).
-For the second model, we included varying group-level smoothers for the predator ID.
+For the second model, we included varying individual smoothers for the predator ID.
 Here, we assume that individual predators share a similar relationship between success and experience, but that this relationship can vary among them (e.g.
@@
 This enabled us to test whether predators differed in the development of their expertise.
-In the third model, we kept the group-level smoothers for the individual predators, but removed the global smoother.
+In the third model, we kept the individual smoothers for the predators, but removed the global smoother.
 This model assumes that predators do not share a common relationship between success and experience.
@@
 The first component is among individual variation in mean speed and success (the mean part of the model), allowing to test for individual differences in tactic use (i.e.
-along the slow-fast continuum), in the mean speed of the prey encountered, and in prey consumption.
-The second component is among individual variation in intra-individual behavioural variation (IIV) (the dispersion part of the model), allowing us to test for individual differences in foraging specialization and in how (dis)similar was the speed of the groups of prey encountered (i.e.
+along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption.
+The second component is among individual variation in intra-individual behavioural variation (IIV) (the dispersion part of the model), allowing us to test for individual differences in foraging specialization and in how (dis)similar were the groups of prey encountered (i.e.
 if resource heterogeneity was higher for some individuals compared to others).
-The third component consists of pairwise comparisons between the individual identity random effect variances on the mean and dispersion part of the model across traits and experience levels, computed as a 15x15 (co)variance matrix.
+The third component consists of pairwise comparisons between the individual identity random effect standard deviations on the mean and dispersion part of the model within/across traits within experience levels, and within/across traits across experience levels, resulting in a 15x15 (co)variance matrix.
 This allows us to assess whether predators that are on average slower/faster are more specialized or flexible, whether predators that adopted a slower/faster (or more specialized/flexible) tactic encountered prey that were faster/slower, and whether slower/faster predators had lower/greater hunting success.
@@
 We controlled for the standardized average rank of the prey group for both the predator and the prey's speed on both the mean and the dispersion parts of the model.
-We included random effects for the game environment, the predator avatar, and the individual predator identity on the mean part of the model, and an individual identity random effect exclusively on the dispersion part.
+We included game environment and predator avatar random effects on the mean part of the model exclusively that were trait and experience specific (i.e.
+no covariance structure).
+We included individual predator identity random effects on the mean and dispersion parts.
 For hunting success, we modeled the mean part only and controlled for the standardized mean prey rank and game duration, and included an individual identity random effect.
@@
 The model is fitted on $n$ experience levels ($n = 3$) denoted by $T_{j}$, where $j$ ranges from 1 to $n$, being the novice, intermediate, and advanced levels.
-The $b$ terms are vectors of fixed effects with their incidence matrices $X$.
-The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their incidence matrices $M$, $N$, and $Z$.
+The $b$ terms are vectors of fixed effects with their design matrices $X$.
+The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their design matrices $M$, $N$, and $Z$.
 The $d$ subscript indicates that a term is from the dispersion part of the model.
@@
 $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
-The residuals are assumed to follow a Gaussian distribution ($e \sim N(0,\ Diag \{\sigma_{e}\})$) *explain here that each has their own individual variance*.
 The individual identity random effects on both the mean and dispersion parts across all response variables and experience levels are indexed in vector $u$.
-The vector $u$ of individual identity random effects follows a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix.
+The individual identity random effects contained in vector $u$ follow a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of the individual identity standard deviations $\sigma_{id_i}$ across all experience levels and response variables.
 
@@
 We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
-We report all the posterior parameter estimates using the median of the posterior distribution (or the mean if stated otherwise) with the highest posterior density (HPD) intervals at 50%, 80%, and 95%.
+We report all the posterior parameter estimates using the median of the posterior distribution with the highest posterior density (HPD) intervals at 50%, 80%, and 95%.
 

### 2023-06-02 manuscript/Chapter2-manuscript.Rmd
updated methods MS and figure captions

@@
 "Online" mode).
-We filtered any matches where players were inactive, such as when average distances traveled per second (i.e.
+We filtered any matches where players were inactive, such as when mean distances traveled per second (i.e.
 speed) were equal to, or very close to, zero.
@@
 The following information is collected and reported for every match : the player's anonymous ID, its avatar (i.e.
-the predator character chosen with its specific skill-gameplay mechanics), the game environment, the predator-player's experience along with its speed, and the average speed of the group of prey it encountered.
+the predator character chosen with its specific skill-gameplay mechanics), the game environment, the predator-player's experience along with its speed, the mean speed of the groups of prey the player encountered, and their mean rank (a proxy for prey skill).
+The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank), and failing to account for it would prevent us from detecting a change in the predator's foraging success with experience.
 
-We analyzed the predator's average speed and the average speed of the prey group encountered by the predator.
-The predator's average speed is measured as the average distance traveled per second during a match (mean= `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
-We measured the preys' average speed as the average travel speed of the four individual prey within a match (mean = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
+We analyzed the predator's mean speed and the mean speed of the prey group encountered by the predator.
+The predator's mean speed is measured as the mean distance traveled per second during a match (mean= `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
+We measured the preys' speed as the mean travel speed of the four individual prey in a match (mean = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
 We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
@@
 To verify that our sample was not biased, we compared a random sample of players that played either 20 to 50 matches, 51 to 100 matches, or 101 to 300 matches during the same timeframe as our sampled population.
-We then took the first 20 matches played by these players, including those from our sampled population, and compared their average speed using a Bayesian hierarchical linear model.
-We found that all four groups had similar average speeds as predators (Appendix 2: Table S1-S2), which indicates an absence of bias due to data sampling.
+We then took the first 20 matches played by these players, including those from our sampled population, and compared their mean speed using a Bayesian hierarchical linear model.
+We found that all four groups had similar mean speeds as predators (Appendix 2: Table S1-S2), which indicates an absence of bias due to data sampling.
 
@@
 This model assumes that predators do not share a common relationship between success and experience.
-The fourth and fifth models were a reproduction of the second and third models respectively, where we included the prey group's average speed to assess its effect on the relationship between success and experience.
-We included the standardized match duration and average prey rank (a proxy for prey skill) as covariates in all five models.
-The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank), and failing to account for it would prevent us from detecting a change in the predator's foraging success with experience.
+The fourth and fifth models were a reproduction of the second and third models respectively, where we included the prey speed to assess its effect on the relationship between success and experience.
+We included the standardized match duration and prey rank as covariates in all five models.
 
@@
 We tested whether foraging behaviour changed with experience, and compared the success of predators along the flexible-specialist hunter continuum, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
-We fitted the model on the predator's speed ($Y_{1}$), the prey's speed ($Y_{2}$), and the predator's hunting success ($Y_{3}$), using a Gaussian distribution family for the predator and the prey's speed, and a beta-binomial distribution family for the predator's success.
+We fitted the model on both the predator ($Y_{1}$) and prey ($Y_{2}$) speeds using a Gaussian error distribution, and on the predator's hunting success ($Y_{3}$) using a beta-binomial error distribution.
 
-The model simultaneously estimated three distinct components for each experience level and each trait.
-The first component is among individual variation in mean speed and success (the mean part of the model), allowing to test for individual differences in tactic use (i.e.
+The model simultaneously estimated three distinct individual components for each trait across experience levels.
+The first component, estimated on the mean part of the model, is among individual variation in mean speed and success.
+This allows to test for individual differences in tactic use (i.e.
 along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption.
-The second component is among individual variation in intra-individual behavioural variation (IIV) (the dispersion part of the model), allowing us to test for individual differences in foraging specialization and in how (dis)similar were the groups of prey encountered (i.e.
-if resource heterogeneity was higher for some individuals compared to others).
-The third component consists of pairwise comparisons between the individual identity random effect standard deviations on the mean and dispersion part of the model within/across traits within experience levels, and within/across traits across experience levels, resulting in a 15x15 (co)variance matrix.
-This allows us to assess whether predators that are on average slower/faster are more specialized or flexible, whether predators that adopted a slower/faster (or more specialized/flexible) tactic encountered prey that were faster/slower, and whether slower/faster predators had lower/greater hunting success.
+The second component, estimated on the dispersion part of the model, is among individual variation in intra-individual variation (IIV).
+This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization .
+The third component consists of pairwise comparisons between the individual identity standard deviations on the mean and dispersion part of the model among traits, among experience, and across traits and experience.
+This results in a 15x15 (co)variance matrix, allowing to describe the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.
 
-We controlled for the standardized average rank of the prey group for both the predator and the prey's speed on both the mean and the dispersion parts of the model.
-We included game environment and predator avatar random effects on the mean part of the model exclusively that were trait and experience specific (i.e.
-no covariance structure).
-We included individual predator identity random effects on the mean and dispersion parts.
-For hunting success, we modeled the mean part only and controlled for the standardized mean prey rank and game duration, and included an individual identity random effect.
+For the predator and the prey speed, we controlled for the standardized prey rank on both the mean and the dispersion parts of the model.
+We included game environment, predator avatar, and individual predator identity random effects on the mean part of the model.
+The dispersion part included individual predator identity random effects exclusively.
+For hunting success, we modeled the mean part only and controlled for the standardized prey rank and game duration, and included an individual identity random effect.
 
@@
 eqs_num <- c(
-    "(1.1)",
-    "(1.2)",
-    "(2.1)",
-    "(2.2)",
-    "(3)"
+    "(eqn. 1.1)",
+    "(eqn. 1.2)",
+    "(eqn. 2.1)",
+    "(eqn. 2.2)",
+    "(eqn. 3)"
 )
@@
   x <- fontsize(x, size = 12, part = "body")
-  x <- width(x, j = 1, width = 15.25, unit = "cm")
-  x <- width(x, j = 2, width = 1.26, unit = "cm")
+  x <- width(x, j = 1, width = 13, unit = "cm")
+  x <- width(x, j = 2, width = 2.26, unit = "cm")
 }
@@
 where $j$ is the index of the experience levels.
-The model is fitted on $n$ experience levels ($n = 3$) denoted by $T_{j}$, where $j$ ranges from 1 to $n$, being the novice, intermediate, and advanced levels.
+The model is fitted on the three experience levels denoted by $T_{j}$, where $j$ ranges from 1 to 3 (i.e.
+novice, intermediate, advanced).
 The $b$ terms are vectors of fixed effects with their design matrices $X$.
@@
 The $d$ subscript indicates that a term is from the dispersion part of the model.
-On the mean part for all traits and experience levels, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en \sim N(0,\ I\ \sigma_{en})$ and $av \sim N(0,\ I\ \sigma_{av})$).
+For all experience levels of the predator and prey speed, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en \sim N(0,\ I\ \sigma_{en})$ and $av \sim N(0,\ I\ \sigma_{av})$).
 $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
-The individual identity random effects on both the mean and dispersion parts across all response variables and experience levels are indexed in vector $u$.
-The individual identity random effects contained in vector $u$ follow a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of the individual identity standard deviations $\sigma_{id_i}$ across all experience levels and response variables.
+All the individual identity random effects (mean and dispersion) across all response variables and experience levels are indexed in vector $u$.
+The $u$ vector follows a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of the individual identity standard deviations $\sigma_{id_i}$ across all experience levels and response variables.
 
@@
 
-Individual predators differed slightly in their average movement speed across experience levels (i.e.
+Individual predators differed slightly in their mean speed across experience levels (i.e.
 predator ID (mean); Figure 2 and Appendix S1: Table S2).
@@
 
-Contrary to predictions, there was strong evidence that predators did not differ in the speed of the prey groups that they encountered on average across experience (i.e.
+Contrary to predictions, there was strong evidence that predators did not differ in the mean speed of the prey groups that they encountered across experience (i.e.
 predator ID (mean); Figure 2 and Appendix S1: Table S2).
@@
 predator ID (sigma); Appendix S1: Table S2).
-Hence, some predators encountered prey groups with similar average speeds, while others encountered prey groups with varying average speeds throughout the study period.
+Hence, some predators encountered prey groups with similar mean speeds, while others encountered prey groups with varying mean speeds throughout the study period.
 The differences in the prey encountered among predators increased only slightly with experience (i.e.
@@
 For instance, the predator population maintained their speed and degree of specialization throughout the study period, and individual differences in mean speed did not change with experience.
-However, differences among predators in foraging specialisation did increase slightly with experience, with some individuals becoming increasingly flexible.
+However, differences among predators in foraging specialization did increase slightly with experience, with some individuals becoming increasingly flexible.
 Interestingly, the behavioural response (i.e.
@@
 mean behaviour) instead of relying solely on resource heterogeneity [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
+
+*expliquer pourquoi les généralistes ont moins bien performé ici*
 
@@
 Panels A and C show among individual differences in the development of expertise, while panels B and D show the development of expertise for the average individual.
-(A-B) GAMM where we control for the average prey rank (C-D) GAMM where we control for the average prey rank and the average speed of the prey group.
-
-**Figure 2.** Median posterior differences and HPD intervals comparing the parameter values predicted by the MDHGLM among all predator experience levels.
-The parameter being compared is on the y axis, and the difference in parameter values between two experience levels is on the x axis.
-The pairwise comparisons between experience levels are displayed across the three panels A, B, and C.
-The population mean corresponds to the population's mean speed, mean speed of the prey encountered, and mean success.
-The population variation corresponds to the population's foraging specialization and variation in speed of the prey encountered.
-The individual variation in means corresponds to individual differences in mean speed, while individual variation in IIV indicates individual differences in foraging specialization and in the variation of the groups of prey encountered.
+(A-B) GAMM where we control for the prey rank (C-D) GAMM where we control for the prey rank and the speed of the prey group.
 

### 2023-06-03 manuscript/Chapter2-manuscript.Rmd
other changes across methods and results. update section titles

@@
 All models were fitted under a Bayesian framework in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
-The models were compiled on Cedar, a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
-The operating system for Cedar is CentOS Linux 7, and each model required 64GB of RAM with 48 cores to compile within $\le$5 days.
+The models were compiled on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
+Each required 64GB of RAM with 48 cores to compile within 5 days.
 
-### Effect of experience on hunting success
+### Development of expertise
 
@@
 number of matches played before the current match).
-We parameterized the models following the method of @Pedersen.etal2019.
+We parametrized the models following the method of @Pedersen.etal2019.
 The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID.
@@
 Following @FraserFranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system.
-We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0, 0.5)$).
+We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0,\ 0.5)$).
 We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
 
-### Changes in foraging behaviour and predator-prey interactions with experience
+### Foraging behaviour and predator-prey interactions across experience
 
@@
 along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption.
-The second component, estimated on the dispersion part of the model, is among individual variation in intra-individual variation (IIV).
+The second component, estimated on the dispersion part of the model by modeling the residuals, is among individual variation in intra-individual variation (IIV).
 This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization .
@@
 novice, intermediate, advanced).
+The $d$ subscript indicates that a term is from the dispersion part of the model.
 The $b$ terms are vectors of fixed effects with their design matrices $X$.
 The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their design matrices $M$, $N$, and $Z$.
-The $d$ subscript indicates that a term is from the dispersion part of the model.
 For all experience levels of the predator and prey speed, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en \sim N(0,\ I\ \sigma_{en})$ and $av \sim N(0,\ I\ \sigma_{av})$).
@@
 3).
-Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3, 0.5)$: eqn.
+Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3,\ 0.5)$: eqn.
 1.1 and 2.1).
-Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,1)$: eqn 1.2 and 2.2).
+Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,\ 1)$: eqn 1.2 and 2.2).
 For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1)$: eqn.
-3) and a negative Gaussian prior ($N(-4, 1)$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration.
+3) and a negative Gaussian prior ($N(-4,\ 1)$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration.
 For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part and the dispersion part of the model.
@@
 
-We parametrized both the GAMMs and the MDHMLM to run four MCMC chains with 1000 posterior samples for each parameter.
+We parametrized the GAMMs and the MDHGLM to run four MCMC chains with 1000 posterior samples for each parameter.
 We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table 1), and 1500 iterations with a thinning set to four for the other additive models.
@@
 
-## Effect of experience on hunting success
+## Development of expertise
 
@@
 percent_tab2 <- data.table(readRDS(file.path(path, "DHMLM_percentages.rds")))
+
+#fit1 <- readRDS(here::here("outputs", "01_outputs_models", "A2_GAMM-rank.rds"))
+#fit2 <- readRDS(here::here("outputs", "01_outputs_models", "A2_GAMM-speed-rank.rds"))
+#
+#fit1
+#fit2
 ```
 
-Out of all five GAMM models, the two that best predicted the data, with very similar expected log pointwise densities (elpd), were the models accounting for the prey group's speed (Table 1).
-Predators differed substantially in the relationship between hunting success and cumulative experience (i.e.
-expertise: Figure 1A-B).
-We found evidence that these differences were in part mediated by prey speed because individuals had distinct patterns after we controlled for the mean speed of the prey groups compared to when we did not (Figure 1A-B).
-For instance, many individual curves shifted upwards.
-Precisely, the percentage of individuals that displayed a >0.5 increase in success changed from `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` to `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` after we accounted for prey speed (Appendix S1: Figure S1A).
-In this model (i.e.
-Figure 1B-C), `r toString(scales::percent(percent_tab1[4,]$percentage, accuracy = 0.1))` of the population showed a >0.5 decrease in success (Appendix S1: Figure S1B), and the remaining `r toString(scales::percent(percent_tab1[6,]$percentage, accuracy = 0.1))` displayed little to no change (between -0.5 and 0.5) in success across experience (Appendix S1: Figure S1C).
+Out of all five GAMM models, two predicted the data the best and achieved similar expected log pointwise densities (elpd).
+Both models accounted for the prey group's rank and speed (Table 1).
+Models in which these effects were not accounted for resulted in no change in hunting success with experience (i.e.
+expertise) for the average individual (results not shown).
+Accounting for the prey rank resulted in a concave-shaped relationship, with the highest success ranging between 100 and 400 matches (Figure 1A).
+In the model where we additionally included the prey's speed, the effect of experience on hunting success for the average individual followed a diminishing returns curve, with predators optimizing their success after playing ~300 matches (Figure 1C).
+The curve shows there was a 39% increase in the probability of consuming all prey for the average individual between the first and the 400$^{th}$ match which has the highest predicted success (Figure 1C).
 
-Moreover, all models where we did not account for prey speed had a global trend of predator experience that was nearly flat (results not shown).
-Yet, we see that there is an increase up to 13% in the probability of consuming all prey with experience in the population when we account for prey speed (Figure 1C).
+The relationship between hunting success and cumulative experience differed among predators (Figure 1B and D).
+Only `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` of the population had an increase in success from the first match to the last in the model where we did not account for the prey's speed and rank (Appendix S1: Figure S1A).
+In contrast, accounting for both effects resulted in `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` of the population increasing its success with experience from the first match to the last.
+The prey speed alone also mediated individual differences in the relationship between success and experience.
+The standard deviation of the individual slopes component of the model accounting only for prey rank was equal to 9.72 ($95\%\ CI$: 9.30, 10.15), while the one for the model accounting for prey rank and speed was equal to 3.36 ($95\%\ CI$: 3.04, 3.71), indicating that individual differences in the development of expertise decreased when accounting for prey speed.
 
-## Effect of experience on behavioural specialization and hunting success
+## Changes in foraging behaviour, prey behaviour, and hunting success
 
-The mean speed of the predator population did not change with experience (i.e.
-intercept (mean) of predator speed; Figure 2 and Appendix S1: Table S1).
-There was also strong evidence that foraging specialization in the population remained stable across experience levels (i.e.
-intercept (sigma) of predator speed; Figure 2 and Appendix S1: Table S1).
-We did not find evidence that the predator population had a change in mean success with experience (intercept (mean) of hunting success; Figure 2 and Appendix S1: Table S1).
-There was, however, a decrease in among individual differences in success at the intermediate stage, which was maintained at the advanced stage (predator ID (mean) of hunting success; Figure 2 and Appendix S1: Table S2).
-
-Individual predators differed slightly in their mean speed across experience levels (i.e.
-predator ID (mean); Figure 2 and Appendix S1: Table S2).
-However, there was strong evidence that they displayed differences in foraging specialization, with a 0.1 unit increase in standard deviation from novice to advanced, indicating that differences increased slightly (i.e.
-predator ID (sigma) is higher at the advanced level; Figure 2 and Appendix S1: Table S2).
-Moreover, some individual predators switched from a flexible to a specialized hunting tactic, and vice-versa, as they gained experience (Figure 3).
-Importantly, `r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the predator population displayed a large change in foraging specialization/flexibility with experience (i.e.
->0.2 change in standard deviation), `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation), while `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))`remained relatively stable (i.e.
+The mean speed of the predator population remained stable with experience (Figure 2 and Appendix S1: Table S1).
+Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix S1: Table S1).
+At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix S1: Table S2).
+However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in IIV from novice to advanced (Figure 2).
+`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e.
+>0.2 change in standard deviation; Figure 3).
+In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e.
+>0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` almost no change with experience (i.e.
 <0.05 change in standard deviation).
 
-Contrary to predictions, there was strong evidence that predators did not differ in the mean speed of the prey groups that they encountered across experience (i.e.
-predator ID (mean); Figure 2 and Appendix S1: Table S2).
-However, individuals differed in the heterogeneity of the groups of prey encountered across the study period (i.e.
-predator ID (sigma); Appendix S1: Table S2).
-Hence, some predators encountered prey groups with similar mean speeds, while others encountered prey groups with varying mean speeds throughout the study period.
-The differences in the prey encountered among predators increased only slightly with experience (i.e.
-predator ID (sigma); Figure 2).
+As the predator population gained experience, there was strong evidence that the prey increased their speed, although slightly (Figure 2 and Appendix S1: Table S1).
+The population also encountered groups of prey using different speeds (Appendix S1: Table S1) which did not change with experience (Figure 2).
+At the individual level, all predators encountered prey with similar speeds on average throughout experience (Figure 2 and Appendix S1: Table S2).
+Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix S1: Table S2).
+Thus, some predators encountered similar groups (i.e.
+all groups using similar speeds) while others encountered distinct groups (i.e.
+some slower and some faster).
+These differences among individuals in IIV for prey encounters increased only marginally with experience (Figure 2).
 
-## Relationship between behavioural specialization and prey behaviour
+Similar to the GAMMs, the predator population's mean hunting success increased with experience (Figure 2 and Appendix S1: Table S1), with mean prey consumption revolving around two prey.
+There were also important differences among individuals in mean hunting success (Appendix S1: Table S2), but they remained stable across experience (Figure 2).
 
+## Predator-prey interactions across experience
+
+*je suis rendu ici*
 Predators that were on average faster (mean speed) had a lower intra-individual variability (IIV speed) (Figure 4A-B and Appendix S4: Table S1).
@@
 
-## Hunting success of behavioural specialists vs generalists
+## Comparing the success of flexible and specialist foragers
 
@@
 the number of matches played prior to each observation) is on the x axis.
-Panels A and C show among individual differences in the development of expertise, while panels B and D show the development of expertise for the average individual.
+Panels A and C show the development of expertise for the average individual with the vertical dashed lines representing the lowest and highest predicted values respectively.
+In contrast, panels B and D show among individual differences in the development of expertise, with each curve representing an individual predator.
 (A-B) GAMM where we control for the prey rank (C-D) GAMM where we control for the prey rank and the speed of the prey group.
+
+**Figure 2.** Median posterior differences and HPD intervals comparing predator foraging behaviour at the population and individual level across experience stages.
+The behavioural parameter predicted by the MDHGLM being compared is on the y axis, and the difference in parameter values between two experience stages is on the x axis.
+The pairwise comparisons between experience stages are displayed across the three panels A, B, and C.
+We compare the mean speed of the predator population, the speed of the prey it encountered, and its hunting success across experience (population mean).
+We also compare the population's foraging specialization and variation in speed of the prey it encountered across experience (population variance).
+At the individual level, we compare among individual differences in speed, the speed of the prey encountered, and hunting success (individual variation mean).
+Lastly, we compare individual variation in IIV across experience, indicating whether individual differences in foraging specialization and in the variation of the groups of prey encountered changed with experience (individual variation IIV).
 

### 2023-06-03 code/04_code_figures/figure1.R

@@ -277,7 +277,7 @@
    geom_text(
      aes(label = paste("y =", format(round(max(tabA2_b$estimate__ / 4), digits = 2), nsmall = 2)),
          y = max(tabA2_b$estimate__ / 4) + 0.10,
-         x = tabA2_b[which.max(estimate__), Zcumul_xp] + 0.35),
+         x = tabA2_b[which.max(estimate__), Zcumul_xp] + 0.55),
      color = "#440154",
      size = 5
    ) +
@@ -323,7 +323,7 @@
    geom_text(
      aes(label = paste("y =", format(round(max(tabA2_prey_b$estimate__ / 4), digits = 2), nsmall = 2)),
          y = max(tabA2_prey_b$estimate__ / 4) + 0.10,
-         x = tabA2_prey_b[which.max(estimate__), Zcumul_xp] + 0.35),
+         x = tabA2_prey_b[which.max(estimate__), Zcumul_xp] + 0.3),
      color = "#440154",
      size = 5
    ) +

### 2023-06-05 manuscript/Chapter2-manuscript.Rmd
updte first two parts of the discuss. not knitted

@@
 The second component, estimated on the dispersion part of the model by modeling the residuals, is among individual variation in intra-individual variation (IIV).
-This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization .
+This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization.
+A general intercept is also fitted on both the mean and dispersion part of the model, providing population-level estimates of the aforementioned parameters.
 The third component consists of pairwise comparisons between the individual identity standard deviations on the mean and dispersion part of the model among traits, among experience, and across traits and experience.
@@
 
-The relationship between hunting success and cumulative experience differed among predators (Figure 1B and D).
+The relationship between hunting success and cumulative experience differed among predators (Figure 1B-D).
 Only `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` of the population had an increase in success from the first match to the last in the model where we did not account for the prey's speed and rank (Appendix S1: Figure S1A).
@@
 The prey speed alone also mediated individual differences in the relationship between success and experience.
-The standard deviation of the individual slopes component of the model accounting only for prey rank was equal to 9.72 ($95\%\ CI$: 9.30, 10.15), while the one for the model accounting for prey rank and speed was equal to 3.36 ($95\%\ CI$: 3.04, 3.71), indicating that individual differences in the development of expertise decreased when accounting for prey speed.
+The standard deviation of the individual slopes component of the model accounting only for prey rank was equal to 9.72 (9.30, 10.15 $95\%\ CI$), while the one for the model accounting for prey rank and speed was equal to 3.36 (3.04, 3.71 $95\%\ CI$), indicating that individual differences in the development of expertise decreased when accounting for prey speed.
 
@@
 
-*je suis rendu ici*
-Predators that were on average faster (mean speed) had a lower intra-individual variability (IIV speed) (Figure 4A-B and Appendix S4: Table S1).
-Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement through time.
-As predators gained experience, these strategies were increasingly defined as there was a 0.16 unit increase in the correlation at the advanced stage (Figure 4C).
-Predators that were on average faster (mean speed) also encountered groups of prey that were on average faster (mean prey speed) and more similar (IIV prey speed) (Figure 4A-B and Appendix S4: Table S1).
-There was however only weak to no evidence that these correlations increased with experience (Figure 4C)
+Predators that were on average faster had lower IIV in speed (Figure 4A-B and Appendix S4: Table S1).
+Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement.
+As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 4C).
+Predators that were on average faster also encountered groups of prey that were on average faster and more similar (Figure 4A-B and Appendix S4: Table S1).
+There was however no evidence that these correlations increased with experience (Figure 4C)
 
-There was almost no correlation between mean prey speed and IIV in predator speed when predators were novice (Figure 4A).
-There was however a 0.17 unit increase in this correlation at the advanced stage, such that advanced hunters that encountered faster prey tended to be more specialized (Figure 4C).
-The predator IIV in speed and IIV in prey speed were moderately positively correlated (Figure 4A-B and Appendix S4: Table S1).
+There was no correlation (-0.01 (-0.17, 0.09 $95\%\ CI$)) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.33, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 4C).
+The predators' IIV in speed and IIV in prey speed were weakly positively correlated (Figure 4A-B and Appendix S4: Table S1).
 Hence, predators that encountered groups of prey with similar speeds were more specialized in their tactic while those that encountered groups of prey with varying speeds were more flexible.
@@
 
-## Comparing the success of flexible and specialist foragers
+## Success along the flexible-specialist forager continuum
 
-The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were both equally successful.
+The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were overall both equally successful.
 This is further supported in the scatterplot showing no apparent relationship between success and IIV in speed (Appendix S1: Figure S2).
-However, there was strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
+There was however a slight increase in the correlation between the predator's IIV in speed and success (Figure 4C), suggesting that flexible foragers at the advanced stage were marginally less successful.
+There was strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
 Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B and Appendix S4: Table S1).
-Both relationships remained structurally stable across experience (Figure 4-C)
+Both relationships remained structurally stable across experience (Figure 4C).
 
@@
 
-Learning from experience is predicted to increase foraging specialization when predators encounter prey behaving predictably through time [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
-However, if predators encounter prey behaving unpredictably through time, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-Our results show that predators substantially increased their hunting success with experience.
-While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, we found that individual predators developed their own expertise and behavioural trajectories over successive encounters with the prey.
-This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy.
+Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, and movement is predictable through time [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
+However, if predators encounter varying prey with a greater behavioural range through time, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
+Our results show that predators in *DBD* increased their hunting success with experience substantially, suggesting that learning through repeated interactions played a role in the development of predator expertise.
+While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, we found that individual predators developed their own behavioural trajectories over successive encounters with the prey.
+This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience.
+The behavioural strategies of predators and prey were matched across experience, as both were probably adjusting to each other with specialized cursorial hunters encountering similar groups of prey while slower and flexible hunters encountered varying groups of prey.
+Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.
 
-*parler directement du succès des tactiques ici?*
+## The development of expertise with experience
 
-*ici parler de la covariance qui suggère un ajustement par les deux. Peut être dire que c'était fortement corrélé, mais que ça changeait pas tant avec l'expérience*
-Specialized cursorial hunters encountered similar groups of prey while slower and flexible hunters encountered varying groups of prey, with both achieving similar success over the study period.
+The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @Dukas2019].
+The prey's speed was important in mediating this pattern as well as the differences in expertise acquisition found among individual predators.
+Our results suggest that this was in due to the prey increasing their speed as predators gained experience, which may have made hunting more difficult for less skilled hunters.
+In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
+Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why such prey are more difficult to capture.
+Thus, predators that ellicited faster speeds on their prey probably struggled more to develop their expertise if they couldn't properly hunt at high speeds.
 
-*ici, changer la phrase pour parler que l"interaction a changé, comme ça c'est aveugle au feedback*
-With experience, predators increasingly matched their foraging specialization to the speed of the prey that they encountered,
-
-but they did not achieve greater success, probably because the prey were also matching their speed to the predator.
-Our observations suggest that predators in *DBD* learn to adjust their foraging specialization, not to the variance, but to the mean behaviour of the prey that they encounter throughout their lifetime in the game.
-
-## The development of expertise with hunting experience
-
-Empirical research shows that task proficiency often increases nonlinearly with experience and stabilizes at an expert level [reviewed in @Dukas2019].
-Our analyses revealed a similar trend, with a 13% population increase in success when predators became advanced hunters.
-However, because the game pairs players with similar skill, the increase in expertise could have potentially been greater if predators and prey were paired randomly.
-Individual predators in *DBD* also displayed distinct patterns of expertise acquisition.
-We predicted that this would occur if, by chance, predators differed in the prey that they encountered, because some may be easier and others more difficult to capture.
-In nature, prey can use a variety of defenses such as physical armaments, toxins, camouflage, or antipredator behaviours to escape predation [@BrodieIII.BrodieJr.1999;@Bowen.etal2002;@brodieCoEvolutionPredatorsPrey2010;@Nomura.etal2011;@Carey.Wahl2011].
-In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-Our results confirm that prey speed influenced expertise acquisition at the individual level to some extent.
-This is not surprising because capturing faster prey requires costly and specialized cognitive abilities and coordination [@Kelley.Magurran2011].
-
-However, there were still important differences in expertise acquisition, which suggests that other antipredator tactics may also be involved.
-For example, a well known antipredator tactic associated with speed that confuses human and non-human predators during the attack sequence is unpredictable escapes [@Jones.etal2011;@Herbert-Read.etal2017;@Moore.etal2017;@Richardson.etal2018].
-This tactic compromises the predator's ability to anticipate prey escape routes, but they can adjust to it by using slower approaches before attacking [@Szopa-Comley.Ioannou2022].
-Yet, because unpredictability exploits the predator's cognition, slow learners could struggle to optimize their success if they often encounter prey using this tactic which is also extensively used in *DBD* (personal observation).
-
-Alternatively, it is possible that individual variation in learning rates due to time delays between hunting events drove the observed differences in expertise acquisition.
-For example, in *DBD*, a predator that played 300 matches in the span of six months might forget more critical information (e.g.
-prey escape patterns or muscle memory) than one that played 300 matches in the span of 6 days.
+However, even after we took prey speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved.
+For example, the prey could use camouflage or hiding to avoid detection by the predator [Bowen.etal2002;@Carey.Wahl2011;@Nomura.etal2011].
+This could result in predators varying in their expertise if they do not learn equally how to exploit the visual cues that facilitate cryptic prey detection such as habitat characteristics [@Ehlinger1989;@Hughes.etal1992;@Warburton2003] or prey colour patterns [@Szopa-Comley.etal2020].
+Another important component of predator expertise and learning is the time delay between hunting events.
+In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape pattern anticipation than one that played 300 matches in the span of 6 days.
 While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
-Moreover, the predators could have differed in their ability to detect prey.
-For instance, nonhuman predators can learn visual cues such as coloration to recognize and avoid unpalatable prey [@Skelhorn.etal2016;@Ward-Fear.etal2020;@McLellan.etal2021], or habitat characteristics to locate food patches [@Ehlinger1989;@Hughes.etal1992;@Warburton2003].
-@Szopa-Comley.etal2020 also found consistent among individual variation in the capacity to detect cryptic and conspicuous prey in three-spined sticklebacks (*Gasterosteus aculeatus*).
-Thus, predators could differ in their expertise if they do not learn equally how to exploit the visual cues that facilitate prey detection.
+There are thus interesting avenues for research on the relationship between learning, forgetting, and skill acquisition throughout an individual's experience to better understand predator foraging and predict its consequences.
 
 ## Changes in individual hunting specialization with experience and consequences for predator-prey interactions
-
+*je suis rendu ici*
 There were only weak differences among predators in tactic use (i.e.

### 2023-06-07 manuscript/Chapter2-manuscript.Rmd
updated discussion

@@
 ---
-title: "Hunting experience shapes individual foraging specialization and predator-prey interactions in an online videogame"
+title: "Predator-prey interactions remain stable across a predator's experience in an online videogame"
 output: 
@@
 
-\newpage
 # ABSTRACT {.unnumbered}
@@
 There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging strategies [@Phillips.etal2017].
-This is reflected in the literature showing contrasting results in the links between specialization and fitness at the individual level.
-Some studies have found greater success for individuals that use specialized foraging tactics [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others found that individuals using flexible foraging tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021].
-This disrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility.
-However, many studies have found that both type of foragers can also attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018].
+Some studies have found greater success for individuals specializing on a foraging tactic [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others have found that individuals using flexible foraging tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021].
+This discrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility.
+However, many studies also show that both type of foragers can attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018].
 It is hypothesized that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
 In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty [@dall2010].
-While it is clear that predators can match their hunting behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how?
+While it is clear that predators can match their hunting behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how.
 Given the dynamic nature of predator-prey interactions, it is unlikely that evolution alone could explain such behavioural adjustments by predators, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].
-Thus, uncovering the role of learning during direct predator-prey interactions would help to predict the behavioural decisions and the success of predators when they are hunting.
+Uncovering the role of experience in shaping direct predator-prey interactions would help to predict the behavioural decisions and the success of predators when they are hunting.
 
@@
 If experience reduces the costs of switching between low and high speeds as predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds.
-If experience increases a tactic's efficiency for specific types of prey assuming that all individuals encounter similar groups of prey, then they may instead specialize in their speed.
+However, if individuals encounter similar groups of prey, then the efficiency of a specific tactic should increase with experience and everyone should instead specialize in their speed.
 In both scenarios, among individual variation in IIV (i.e.
-individual differences in specialization) should be low across experience because everyone is either a flexible or a specialist forager, but the population variance would either increase (flexibility) or decrease (specialization).
-Alternatively, both processes may operate at the same time if behavioural interactions with the prey vary among predators, such that among individual variation in IIV should increase.
+individual differences in specialization) would be low across experience, whereas the population variance would either increase (flexibility) or decrease (specialization).
+Alternatively, both processes may operate at the same time if behavioural interactions with the prey vary among predators, such that among individual variation in IIV would increase.
 In this case, we expect predators that experienced more predictable encounters with their prey (i.e.
@@
 We tested whether foraging behaviour changed with experience, and compared the success of predators along the flexible-specialist hunter continuum, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
-We fitted the model on both the predator ($Y_{1}$) and prey ($Y_{2}$) speeds using a Gaussian error distribution, and on the predator's hunting success ($Y_{3}$) using a beta-binomial error distribution.
+For each experience level, we fitted the model on three traits: the predator's speed ($Y_{1}$) and the prey's speed ($Y_{2}$) using a Gaussian error distribution, and the predator's hunting success ($Y_{3}$) using a beta-binomial error distribution.
+Fixed and random effect structure were trait-specific and the same for all experience levels.
+The predator and the prey speed included a mean and a dispersion part.
+For both traits, we controlled for the standardized prey rank on both the mean and the dispersion parts of the model.
+We included game environment, predator avatar, and individual predator identity random effects on the mean part of the model.
+The dispersion part included individual predator identity random effects exclusively.
+For hunting success, we modeled the mean part only and controlled for the standardized prey rank and game duration, and included an individual identity random effect.
 
-The model simultaneously estimated three distinct individual components for each trait across experience levels.
+The model simultaneously estimated three individual components for each trait across experience levels.
 The first component, estimated on the mean part of the model, is among individual variation in mean speed and success.
@@
 This results in a 15x15 (co)variance matrix, allowing to describe the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.
-
-For the predator and the prey speed, we controlled for the standardized prey rank on both the mean and the dispersion parts of the model.
-We included game environment, predator avatar, and individual predator identity random effects on the mean part of the model.
-The dispersion part included individual predator identity random effects exclusively.
-For hunting success, we modeled the mean part only and controlled for the standardized prey rank and game duration, and included an individual identity random effect.
 
@@
 At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix S1: Table S2).
-However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in IIV from novice to advanced (Figure 2).
+However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in among individual differences in IIV from novice to advanced (Figure 2).
 `r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e.
@@
 In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` almost no change with experience (i.e.
+>0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e.
 <0.05 change in standard deviation).
@@
 However, if predators encounter varying prey with a greater behavioural range through time, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-Our results show that predators in *DBD* increased their hunting success with experience substantially, suggesting that learning through repeated interactions played a role in the development of predator expertise.
-While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, we found that individual predators developed their own behavioural trajectories over successive encounters with the prey.
+We found that predators in *DBD* increased their hunting success with experience substantially, suggesting that learning through repeated interactions played a role in the development of predator expertise.
+While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
 This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience.
@@
 
+Our results suggest that expertise is honed through extensive practice, but also depends on an individual's capacity to adjust to difficulty.
 The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @Dukas2019].
-The prey's speed was important in mediating this pattern as well as the differences in expertise acquisition found among individual predators.
-Our results suggest that this was in due to the prey increasing their speed as predators gained experience, which may have made hunting more difficult for less skilled hunters.
-In *DBD* we previously showed that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why such prey are more difficult to capture.
-Thus, predators that ellicited faster speeds on their prey probably struggled more to develop their expertise if they couldn't properly hunt at high speeds.
+The prey's speed was important in mediating this pattern as well as the observed differences in expertise acquisition among predators, probably because the prey increased their speed as predators gained experience.
+We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
+Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why they are more difficult to capture.
+Thus, predators that couldn't properly hunt at high speeds or develop counterstrategies for faster prey were at a disadvantage.
 
 However, even after we took prey speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved.
-For example, the prey could use camouflage or hiding to avoid detection by the predator [Bowen.etal2002;@Carey.Wahl2011;@Nomura.etal2011].
-This could result in predators varying in their expertise if they do not learn equally how to exploit the visual cues that facilitate cryptic prey detection such as habitat characteristics [@Ehlinger1989;@Hughes.etal1992;@Warburton2003] or prey colour patterns [@Szopa-Comley.etal2020].
-Another important component of predator expertise and learning is the time delay between hunting events.
-In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape pattern anticipation than one that played 300 matches in the span of 6 days.
-While this has not been formally tested, a greater delay between exposure events is hypothesized to attenuate or even negate the relationship between success and experience [@Endler1991;@Wright.etal2022].
-There are thus interesting avenues for research on the relationship between learning, forgetting, and skill acquisition throughout an individual's experience to better understand predator foraging and predict its consequences.
+For example, if the prey used camouflage or hiding to avoid being detected by the predator [Bowen.etal2002;@Carey.Wahl2011;@Nomura.etal2011], then predators may only find them if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@Ehlinger1989;@Hughes.etal1992;@Warburton2003;@Szopa-Comley.etal2020].
+In addition, longer time delays between hunting events may exacerbate slower learning or even forgetting [@Endler1991;@Wright.etal2022].
+In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape patterns than one that played 300 matches in the span of six days.
 
-## Changes in individual hunting specialization with experience and consequences for predator-prey interactions
-*je suis rendu ici*
-There were only weak differences among predators in tactic use (i.e.
-mean speed), but differences in specialization were important and related to how different were the groups of prey that they encountered.
-Predators that encountered groups of prey with similar speeds across matches specialized in hunting at high speeds, while those that encountered varying groups of prey adopted a slower and flexible strategy.
-Fast-paced hunting is indeed a highly specialized tactic suited for prey that use rapid escapes [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when hunting prey that use unpredictable escapes [@Szopa-Comley.Ioannou2022].
-However, it remains uncertain whether this phenotypic matching enables predators with different degrees of specialization to achieve equal success within populations [@Woo.etal2008].
-Here, we found that all hunters along the flexible-specialist continuum achieved similar success throughout the study period (Appendix S1: Figure S2).
-Thus, our results provide direct evidence that predators matching their tactic to their prey may be key in maintaining behavioural diversification in predator-prey systems.
+## Predator-prey interactions across experience
 
-Surprisingly, the effect of experience on foraging behaviour was much more subtle than we expected.
-For instance, the predator population maintained their speed and degree of specialization throughout the study period, and individual differences in mean speed did not change with experience.
-However, differences among predators in foraging specialization did increase slightly with experience, with some individuals becoming increasingly flexible.
-Interestingly, the behavioural response (i.e.
-specialization) to experience by individual predators differed.
-For instance, 44% of the population did not alter their degree of specialization with experience (i.e.
-remaining either faster and more specialized, or slower and more flexible), while 56% of the population displayed a switch from a specialized to a flexible tactic or vice-versa with experience.
-These changes were accompanied by predators increasingly matching their specialization to the mean speed of the prey groups across experience, instead of the variability between encounters.
-This suggests that it may be easier for predators to specialize on their prey by relying on mean cues (i.e.
-mean behaviour) instead of relying solely on resource heterogeneity [@Weimerskirch.etal2005;@Weimerskirch2007;@Woo.etal2008;@Phillips.etal2017].
+The predator population maintained their speed and degree of specialization throughout the study period, and all individuals used a similar tactic (i.e.
+mean speed).
+However, differences in specialization were important and increased slightly with experience.
+Predators that specialized in hunting at high speeds encountered groups of prey with similar speeds across matches, while those that adopted a slower and flexible strategy encountered varying groups of prey.
+This pattern might arise because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@Szopa-Comley.Ioannou2022].
+However, it is more plausible that this reflects reciprocal adjustments in speed by predators and prey as they interacted [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a], because prey can also learn how to avoid predation [REFS].
 
-*expliquer pourquoi les généralistes ont moins bien performé ici*
+Surprisingly, although predators changed their specialization across experience, the behavioural interactions between the predator and the prey remained generally stable.
+This may in part be due to almost half (44%) of the population showing close to no change in specialization with experience.
+If these predators were already successful as novices, then there would be no point to change their tactic with experience.
+However, 66% of the predator population did alter their behaviour with experience to different degrees.
+Thus, if the prey also learned through repeated interactions with the predators, then it is possible that it also contributed in stabilizing the system, similar to Red Queen dynamics [@brockhurst2014].
 
-It is likely that predators were also driving changes in prey behaviour because most predator-prey behavioural relationships remained stable even though half of the population switched from a specialist to a flexible strategy and vice-versa across experience.
-This implies that the prey were probably also learning how to avoid predation through repeated interactions.
-Our results concord with what @Mougi.etal2011 define as a matching response relationship, because faster-specialist and slower-flexible hunters preyed upon different prey, but they both achieved equal success.
+The coupling of blabla...pour commencer le paragraphe (moins mettre l'accent sur le changement mais sur le type de relation et ce qui la drive)
+
+When predators were novices, our results align with a matching-response relationship [@Mougi.Kishida2009], because faster-specialist and slower-flexible hunters preyed upon different prey, but they both overall achieved similar success.
+As predators became advanced, slower-flexible hunters became marginally less successfull, suggesting that faster-specialist hunters were probably learning better how to hunt since faster prey were also more difficult to capture.
+*ici ajouter que le long term de ça n'est pas certain.
+il faut que je lise de la littérature explicant pourquoi ça peut être moins bon d'être généraliste*
+
 These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a], but their broader consequences remain unclear.
-Assuming that prey also learned during the interaction, which has been shown across many taxa [refs], we can deduce that learning from reciprocal interactions may contribute in stabilizing predator-prey systems, similar to Red Queen dynamics [@brockhurst2014].
 
-While experience did not alter most of the interaction, predators still managed to increase foraging specialization with increasing prey speed across experience, while individual differences in hunting success simultaneously decreased.
+flexible hunters were slightly less successful than specialists. *expliquer pourquoi les généralistes ont moins bien performé ici*
+*Modifier cette phrase pour appuyer que les généralistes étaient moins bons à long terme: It remains uncertain whether this phenotypic matching enables predators with different degrees of specialization to achieve equal success within populations [@Woo.etal2008].*
+
+*Moreover, even though the relationship was weak, there was an important change in the correlation between the predator's IIV and the mean speed of the prey they encountered.* *pas sûr que je vais ajouter ça*
+
+*ici c'est mon bout sur le matching response je crois...*
 When prey express defensive phenotypes such as high speeds, selection on predators should be strong because of the consequences of repeated failures.
@@
 
-Trait-mediated interactions that affect prey capture are the most important processes driving predator-prey dynamics [@abramsEvolutionPredatorPreyInteractions2000].
-While most studies assume that predators maximize success by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators displayed large differences in the development of their expertise.
+A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
+By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found *support of our prediction that...*
+
+*Thus, our results provide direct evidence that predators matching their tactic to their prey may be key in maintaining behavioural diversification in predator-prey systems.*
+
+that individual predators displayed large differences in the development of their expertise.
 With experience, the population became increasingly distinct along a flexible-specialist continuum, while interactions remained largely stable.
 Overall, all hunters achieved similar hunting success.
-Our results have potential applications for predator-prey models of trait-matching.
-For instance, simulation studies could incorporate individual variation in experience or learning to better predict under which ecological/evolutionary contexts specialization should be favoured over flexibility.
-Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
+
+Virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
 We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.

### 2023-06-14 manuscript/Chapter2-appendix1.Rmd
all manuscript files up to date to the most recent versions

@@
 title: |
-     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame: \
+     Experience shapes individual foraging specialization and success in a virtual predator-prey system: \
      Appendix 1
@@
     fig_caption: yes
-bibliography: references.bib
 csl: ecology.csl

### 2023-06-14 manuscript/Chapter2-appendix2.Rmd
all manuscript files up to date to the most recent versions

@@
 title: |
-     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame: \
+     Experience shapes individual foraging specialization and success in a virtual predator-prey system: \
      Appendix 2
@@
     fig_caption: yes
-bibliography: references2.bib
 csl: ecology.csl

### 2023-06-14 manuscript/Chapter2-appendix3.Rmd
all manuscript files up to date to the most recent versions

@@
 title: |
-     Hunting experience shapes individual foraging specialisation and predator-prey interactions in an online videogame: \
+     Experience shapes individual foraging specialization and success in a virtual predator-prey system: \
      Appendix 3

### 2023-06-14 manuscript/Chapter2-manuscript.Rmd
all manuscript files up to date to the most recent versions

@@
 ---
-title: "Predator-prey interactions remain stable across a predator's experience in an online videogame"
+title: "Experience shapes individual foraging specialization and success in a virtual predator-prey system"
 output: 
@@
     fig_caption: yes
-bibliography: references.bib
+bibliography: 
+  - references1.bib
+  - references2.bib
 csl: ecology.csl
@@
 
-Many predator-prey systems are driven by reciprocal interactions where one responds to changes in the behaviour of the other.
-However, the mechanisms driving these individual responses are only beginning to be explored, in part because of the challenges associated with monitoring direct predator-prey interactions.
+The capacity of predators to match their tactic to the behaviour of their prey is expected to drive the outcome of predator-prey interactions.
+To do so, predators need to practice their tactics extensively to develop the skills and expertise to successfully hunt their prey, which may result in individual foraging specialization.
+Yet, there are very limited empirical assessments showing links between experience, foraging specialization, and performance at the individual level, due to the numerous challenges of monitoring direct interactions in the wild.
 In this study, we used a virtual predator-prey system (the online game *Dead by Daylight*) to investigate if and how hunting experience shapes individual foraging specialization and success in predators across repeated interactions with their prey.
-
-*à modifier pour parler plutôt de l'interaction qui devient fine tuned (i.e. predators and prey)*
-We found that with increasing experience, predators fine-tuned their tactics to the behaviour of their prey.
-Individuals that adopted a flexible tactic (i.e.
-generalists) encountered groups of prey with varying speeds, and those that adopted a cursorial and specialized tactic (i.e.
-specialists) encountered groups of prey with similar speeds throughout the study period.
-
-Our results suggest that experience enables predators to learn how to optimize their tactics to the type of prey that they encounter (i.e.
-fast or slow), which may act as a stabilizing mechanism promoting behavioural diversification in predator-prey systems.
+Our results show that predators optimized prey consumption as they gained experience.
+Prey behaviour was an important mediator of this relationship, which also drove individual differences in the development of expertise.
+With experience, differences among individuals in foraging specialization increased, as individual predators became either specialist or flexible foragers.
+Yet, many individuals remained specialists throughout the study period.
+Moreover, the matching between the predator's strategies (i.e.
+flexible or specialized foraging) and the prey was not strong, suggesting that part of the population did not match their tactic to the prey.
+This individual heterogeneity coincided with differences among individuals in success through time.
+While flexible foragers performed slightly less than specialist foragers, both achieved similar success overall.
+Our observations suggest that individual differences in behavioural change with experience may drive among individual differences in hunting tactics, which may act as a stabilizing mechanism promoting behavioural diversification in predator-prey systems.
 
@@
 In the model where we additionally included the prey's speed, the effect of experience on hunting success for the average individual followed a diminishing returns curve, with predators optimizing their success after playing ~300 matches (Figure 1C).
-The curve shows there was a 39% increase in the probability of consuming all prey for the average individual between the first and the 400$^{th}$ match which has the highest predicted success (Figure 1C).
+The curve shows there was a 38% increase in the probability of consuming all prey for the average individual between the first and the ~330$^{th}$ match where success reached a plateau (Figure 1C).
 
@@
 As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 4C).
-Predators that were on average faster also encountered groups of prey that were on average faster and more similar (Figure 4A-B and Appendix S4: Table S1).
+Predators that were on average faster also tended to encounter groups of prey that were on average faster and more similar (Figure 4A-B and Appendix S4: Table S1).
 There was however no evidence that these correlations increased with experience (Figure 4C)
@@
 The predators' IIV in speed and IIV in prey speed were weakly positively correlated (Figure 4A-B and Appendix S4: Table S1).
-Hence, predators that encountered groups of prey with similar speeds were more specialized in their tactic while those that encountered groups of prey with varying speeds were more flexible.
-We did not however find evidence that this correlation increased with experience (Figure 4C).
+Hence, predators that encountered groups of prey with similar speeds tended to be more specialized in their tactic, while those that encountered groups of prey with varying speeds tended to be more flexible.
+We did not find evidence that this correlation increased with experience (Figure 4C).
 
-## Success along the flexible-specialist forager continuum
+## Success along the foraging continuum
 
@@
 However, if predators encounter varying prey with a greater behavioural range through time, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-We found that predators in *DBD* increased their hunting success with experience substantially, suggesting that learning through repeated interactions played a role in the development of predator expertise.
+We found that predators in *DBD* increased their hunting success with experience, suggesting that the development of predator expertise was honed through extensive practice.
 While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
 This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience.
-The behavioural strategies of predators and prey were matched across experience, as both were probably adjusting to each other with specialized cursorial hunters encountering similar groups of prey while slower and flexible hunters encountered varying groups of prey.
+The behavioural strategies of predators and prey tended to match across experience, suggesting that both were probably adjusting to each other.
+Specialized cursorial hunters tended to encounter similar groups of prey, while slower and flexible hunters tended to encounter varying groups of prey.
+Yet, an important part of the population did not change its behaviour with experience, which probably contributed to an imperfect matching between predator and prey behaviour, resulting in among individual differences in hunting success.
 Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.
 
-## The development of expertise with experience
+## The development of expertise
 
-Our results suggest that expertise is honed through extensive practice, but also depends on an individual's capacity to adjust to difficulty.
+Our results suggest that predator expertise is honed through extensive practice.
 The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @Dukas2019].
-The prey's speed was important in mediating this pattern as well as the observed differences in expertise acquisition among predators, probably because the prey increased their speed as predators gained experience.
+The prey were important in mediating this pattern, probably because they increased their speed as predators gained experience.
 We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why they are more difficult to capture.
-Thus, predators that couldn't properly hunt at high speeds or develop counterstrategies for faster prey were at a disadvantage.
+This resulted in discernable differences in the relationship between success and experience among predators, implying that the development of expertise depends on an individual's capacity to adjust to difficulty.
+Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why such prey were more difficult to capture.
+Thus, predators that couldn't properly hunt at high speeds or develop counterstrategies for faster prey were likely at a disadvantage.
 
-However, even after we took prey speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved.
-For example, if the prey used camouflage or hiding to avoid being detected by the predator [Bowen.etal2002;@Carey.Wahl2011;@Nomura.etal2011], then predators may only find them if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@Ehlinger1989;@Hughes.etal1992;@Warburton2003;@Szopa-Comley.etal2020].
-In addition, longer time delays between hunting events may exacerbate slower learning or even forgetting [@Endler1991;@Wright.etal2022].
+However, even after we took the prey's speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved.
+For example, if the prey used camouflage or hiding to avoid being detected [@Bowen.etal2002;@Carey.Wahl2011;@Nomura.etal2011], then predators may have found them only if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@Ehlinger1989;@Hughes.etal1992;@Warburton2003;@Szopa-Comley.etal2020].
+In addition, longer time intervals between hunting events may delay or even impede learning due to forgetting important information [@Endler1991;@Wright.etal2022].
 In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape patterns than one that played 300 matches in the span of six days.
+Accounting for such time lags may reveal important insights on the outcome of predator-prey interactions.
 
@@
 
-The predator population maintained their speed and degree of specialization throughout the study period, and all individuals used a similar tactic (i.e.
-mean speed).
-However, differences in specialization were important and increased slightly with experience.
-Predators that specialized in hunting at high speeds encountered groups of prey with similar speeds across matches, while those that adopted a slower and flexible strategy encountered varying groups of prey.
-This pattern might arise because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@Szopa-Comley.Ioannou2022].
-However, it is more plausible that this reflects reciprocal adjustments in speed by predators and prey as they interacted [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a], because prey can also learn how to avoid predation [REFS].
+The predator population maintained its speed and degree of specialization throughout the study period, and individuals differed only slightly in their average speeds.
+However, differences in specialization among individuals were important and increased slightly with experience.
+Predators hunting at higher speeds specialized in this tactic and tended to encounter groups of prey with similar speeds, while those hunting at slower speeds were flexible and tended to encounter varying groups of prey.
+On one hand, this pattern could arise if some predators adjusted their strategy to their prey, because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@Szopa-Comley.Ioannou2022].
+However, we observed that 44% of the predator population showed close to no change in specialization with experience.
+Since these individuals were already specialized as novices (MFF personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they more often encountered faster prey.
+This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
+Yet, because prey can also learn how to avoid predation [REFS], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a].
+Indeed, 44% of the predator population altered its behaviour with experience to different degrees, and 12% even switched between flexibility and specialization.
+Hence, if the prey also learned through repeated interactions with the predators, it is possible that experience contributed in stabilizing the system as both were adusting to each other, similar to Red Queen dynamics [@brockhurst2014].
+Our results appear to support this since many individuals were shifting their behavioural niche while the population niche remained stable across experience.
 
-Surprisingly, although predators changed their specialization across experience, the behavioural interactions between the predator and the prey remained generally stable.
-This may in part be due to almost half (44%) of the population showing close to no change in specialization with experience.
-If these predators were already successful as novices, then there would be no point to change their tactic with experience.
-However, 66% of the predator population did alter their behaviour with experience to different degrees.
-Thus, if the prey also learned through repeated interactions with the predators, then it is possible that it also contributed in stabilizing the system, similar to Red Queen dynamics [@brockhurst2014].
-
-The coupling of blabla...pour commencer le paragraphe (moins mettre l'accent sur le changement mais sur le type de relation et ce qui la drive)
-
-When predators were novices, our results align with a matching-response relationship [@Mougi.Kishida2009], because faster-specialist and slower-flexible hunters preyed upon different prey, but they both overall achieved similar success.
-As predators became advanced, slower-flexible hunters became marginally less successfull, suggesting that faster-specialist hunters were probably learning better how to hunt since faster prey were also more difficult to capture.
-*ici ajouter que le long term de ça n'est pas certain.
-il faut que je lise de la littérature explicant pourquoi ça peut être moins bon d'être généraliste*
-
-These types of reciprocal responses to interactions have been observed in other predator-prey systems [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a], but their broader consequences remain unclear.
-
-flexible hunters were slightly less successful than specialists. *expliquer pourquoi les généralistes ont moins bien performé ici*
-*Modifier cette phrase pour appuyer que les généralistes étaient moins bons à long terme: It remains uncertain whether this phenotypic matching enables predators with different degrees of specialization to achieve equal success within populations [@Woo.etal2008].*
-
-*Moreover, even though the relationship was weak, there was an important change in the correlation between the predator's IIV and the mean speed of the prey they encountered.* *pas sûr que je vais ajouter ça*
-
-*ici c'est mon bout sur le matching response je crois...*
-When prey express defensive phenotypes such as high speeds, selection on predators should be strong because of the consequences of repeated failures.
-If predators improve their exploitative ability, then the consequences of hunting these prey should decrease [@BrodieIII.BrodieJr.1999].
-Similarly, theoretical studies predict that learning may attenuate selection [@Anderson1995;@Ancel1999;@Borenstein.etal2006;@Paenke.etal2007], but failing to account for reciprocal interactions may mask more complex outcomes.
-Here, learning appears to have reduced differences in success among predators, but success remained lower when predators hunted faster prey.
-Again, if prey learned how to avoid the predators, then this would explain why advanced hunters still struggled to achieve similar success against faster prey compared to slower prey.
-Thus, disentanling the consequences of learning from reciprocal interactions may reveal important insights on predator-prey interactions.
+Classical theory predicts that individual foraging specialization should maximize prey consumption by optimizing foraging efficiency [@stephens1986], but other work suggests that flexibility and specialization could both be adaptive as resources fluctuate [@Woo.etal2008;@Phillips.etal2017].
+Our results support empirical findings indicating that flexible and specialist foragers obtained similar success [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018], although flexible foragers were slightly less successful.
+Both strategies appeared to emerge in part from individuals learning how to hunt their prey, resulting in a general increase in success in the population.
+However, there were still considerable differences in success among individuals through time, suggesting that some predators were limited in their capacity to match their tactic to their prey or to increase their success.
+Specialist foragers were faster, and thus, probably better equipped to hunt the more difficult faster prey in *DBD*.
+However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for the predator, thereby nullyfing the benefits of using this tactic (Figure 4).
+Thus, specializing probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
+On the other hand, flexible foragers encountered variable prey with slower speeds.
+Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for flexible hunters may have come at the cost of not being adept at capturing faster prey [@Pintor.etal2014].
+Such trade-offs may reflect limitations in learning all the skills required to successfully hunt all types of prey [@healy1992;@belisle1997;@Dukas2019], particularly if the skills required to hunt slower prey are nontransferable to faster prey.
+As the benefits of each hunting style changed under different scenarios, the combination of predatory styles in our virtual system reflects how resource fluctuations can maintain fitness equilibrium within populations, resulting in behavioural diversity in predator-prey systems [@Tinker.etal2008;@Woo.etal2008;@Mougi.Kishida2009].
 
@@
 A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found *support of our prediction that...*
-
-*Thus, our results provide direct evidence that predators matching their tactic to their prey may be key in maintaining behavioural diversification in predator-prey systems.*
-
-that individual predators displayed large differences in the development of their expertise.
-With experience, the population became increasingly distinct along a flexible-specialist continuum, while interactions remained largely stable.
-Overall, all hunters achieved similar hunting success.
-
-Virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
+By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found support of our prediction that prey were driving individual differences in expertise in a predator population.
+We also confirmed that experience and predator-prey encounters drove the patterns of individual foraging specialization and flexibility.
+Our results suggest that predators learned with experience, as their success increased and their speed remained matched the speed of their prey.
+Even though individuals were not all equally successful, both specialized and flexible tactics achieved similar hunting success.
+One limitation of our study was that we couldn't monitor all the matches of the prey, which prevented us from assessing their responses to the predator.
+Hence, future studies should aim at monitoring reciprocal behavioural dynamics through time, which may reveal important insights on the mechanisms driving stable equilibria in predator-prey systems.
+Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
 We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
@@
 the number of matches played prior to each observation) is on the x axis.
-Panels A and C show the development of expertise for the average individual with the vertical dashed lines representing the lowest and highest predicted values respectively.
-In contrast, panels B and D show among individual differences in the development of expertise, with each curve representing an individual predator.
+Panels A and C show the development of expertise for the average individual with the vertical dashed lines on the left representing the lowest predicted values.
+For panel A, the right-side vertical dashed lines shows the highest predicted success.
+For panel C, the right-side dashed line represents the point on the curve where success was optimized, which we calculated using the finite differences method to obtain the first derivative of the predicted values.
+Panels B and D show among individual differences in the development of expertise, with each curve representing an individual predator.
 (A-B) GAMM where we control for the prey rank (C-D) GAMM where we control for the prey rank and the speed of the prey group.

### 2023-06-14 manuscript/Chapter2-manuscript.Rmd
MS and refs up to date.

@@
 This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
-Yet, because prey can also learn how to avoid predation [REFS], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a].
+Yet, because prey can also learn how to avoid predation [@kelley2003;@turner2006;@mccomb2011], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a].
 Indeed, 44% of the predator population altered its behaviour with experience to different degrees, and 12% even switched between flexibility and specialization.
@@
 Specialist foragers were faster, and thus, probably better equipped to hunt the more difficult faster prey in *DBD*.
-However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for the predator, thereby nullyfing the benefits of using this tactic (Figure 4).
+However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for the predator, thereby nullifying the benefits of using this tactic (Figure 4).
 Thus, specializing probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
@@
 Hence, future studies should aim at monitoring reciprocal behavioural dynamics through time, which may reveal important insights on the mechanisms driving stable equilibria in predator-prey systems.
-Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022], but also in other fields such as citizen science and conservation [@Sandbrook.etal2015;@Redpath.etal2018;@Duthie.etal2021].
+Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022].
 We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.

### 2023-06-15 manuscript/Chapter2-manuscript.Rmd
corrected model equation

@@
 
+#eqs <- c(
+#  "Y_{1}(T_{j}) = T^2_{j}(X_{1}\\ b_{1}) + T^2_{j}(M_{1}\\ en_{1}) + T^2_{j}(N_{1}\\ av_{1}) + T^2_{j}(Z_{1}\\ id_{1}) + e_{1}(T_{j})",
+#  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = T^2_{j}(X_{d1}\\ b_{d1}) + T^2_{j}(Z_{d1}\\ id_{d1})",
+#  "Y_{2}(T_{j}) = T^2_{j}(X_{2}\\ b_{2}) + T^2_{j}(M_{2}\\ en_{2}) + T^2_{j}(N_{2}\\ av_{2}) + T^2_{j}(Z_{2}\\ id_{2}) + e_{2}(T_{j})",
+#  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = T^2_{j}(X_{d2}\\ b_{d2}) + T^2_{j}(Z_{d2}\\ id_{d2})",
+#  "Y_{3}(T_{j}) = T^2_{j}(X_{3}\\ b_{3}) + T^2_{j}(Z_{3}\\ id_{3}) + e_{3}(T_{j})"
+#)
+
 eqs <- c(
-  "Y_{1}(T_{j}) = T^2_{j}(X_{1}\\ b_{1}) + T^2_{j}(M_{1}\\ en_{1}) + T^2_{j}(N_{1}\\ av_{1}) + T^2_{j}(Z_{1}\\ id_{1}) + e_{1}(T_{j})",
-  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = T^2_{j}(X_{d1}\\ b_{d1}) + T^2_{j}(Z_{d1}\\ id_{d1})",
-  "Y_{2}(T_{j}) = T^2_{j}(X_{2}\\ b_{2}) + T^2_{j}(M_{2}\\ en_{2}) + T^2_{j}(N_{2}\\ av_{2}) + T^2_{j}(Z_{2}\\ id_{2}) + e_{2}(T_{j})",
-  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = T^2_{j}(X_{d2}\\ b_{d2}) + T^2_{j}(Z_{d2}\\ id_{d2})",
-  "Y_{3}(T_{j}) = T^2_{j}(X_{3}\\ b_{3}) + T^2_{j}(Z_{3}\\ id_{3}) + e_{3}(T_{j})"
+  "Y_{1j} = X_{1j}\\ b_{1j} + M_{1j}\\ en_{1j} + N_{1j}\\ av_{1j} + Z_{1j}\\ id_{1j} + e_{1j}",
+  "log(\\sigma_{e_{Y_{1j}}}) = X_{d1j}\\ b_{d1j} + Z_{d1j}\\ id_{d1j}",
+  "Y_{2j} = X_{2j}\\ b_{2j} + M_{2j}\\ en_{2j} + N_{2j}\\ av_{2j} + Z_{2j}\\ id_{2j} + e_{2j}",
+  "log(\\sigma_{e_{Y_{2j}}}) = X_{d2j}\\ b_{d2j} + Z_{d2j}\\ id_{d2j}",
+  "Y_{3j} = X_{3j}\\ b_{3j} + Z_{3j}\\ id_{3j} + e_{3j}"
 )
@@
 
-where $j$ is the index of the experience levels.
-The model is fitted on the three experience levels denoted by $T_{j}$, where $j$ ranges from 1 to 3 (i.e.
+where $j$ is the index of the three experience levels (i.e.
 novice, intermediate, advanced).
@@
 The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their design matrices $M$, $N$, and $Z$.
-For all experience levels of the predator and prey speed, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en \sim N(0,\ I\ \sigma_{en})$ and $av \sim N(0,\ I\ \sigma_{av})$).
+For all experience levels of $Y_{1}$ and $Y_{2}$, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en_{12j} \sim N(0,\ I\ \sigma_{en_{12j}})$ and $av_{12j} \sim N(0,\ I\ \sigma_{av_{12j}})$).
 $I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
-All the individual identity random effects (mean and dispersion) across all response variables and experience levels are indexed in vector $u$.
-The $u$ vector follows a multivariate Gaussian distribution $u \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of the individual identity standard deviations $\sigma_{id_i}$ across all experience levels and response variables.
+In addition, we assumed that the residuals follow a Gaussian distribution with observation-specific standard deviations $e_{12j} \sim N(0,\ Diag\{\sigma_{e_{12j}}\})$.
+All the individual identity random effects (mean and dispersion) across all response variables and experience levels are indexed in vector $\alpha$.
+The $\alpha$ vector follows a multivariate Gaussian distribution $\alpha \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of the individual identity standard deviations $\sigma_{id_{ij}}$ across all response variables and experience levels.
 

### 2023-06-19 code/04_code_figures/figure4-c.R
increase y axis label size fig4

@@ -149,7 +149,7 @@ custom_theme <- theme(
       face = "plain", size = 11,
       color = "black"),
     axis.text.y = element_text(
-      face = "plain", size = 12,
+      face = "plain", size = 13,
       color = "black"),
     axis.title = element_text(size = 15, face = "plain", color = "black"),
     panel.grid = element_blank(),

### 2023-06-19 manuscript/Chapter2-manuscript.Rmd
minor edits to the MS .rmd suggested by Clint

@@
 While it is clear that predators can match their hunting behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how.
-Given the dynamic nature of predator-prey interactions, it is unlikely that evolution alone could explain such behavioural adjustments by predators, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].
+Given the dynamic nature of predator-prey interactions, it is likely that ontogenic behavioural changes in predators play an important role, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].
 Uncovering the role of experience in shaping direct predator-prey interactions would help to predict the behavioural decisions and the success of predators when they are hunting.
@@
 Predators should thus benefit from learning how the prey behave to be successful.
-Other virtual predator-prey studies show that predation regimes drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al.
-in prep).
+Other virtual predator-prey studies show that predation regimes drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al., public communications and unpublished manuscript).
 These examples outline how virtual systems could be useful in identifying general ecological patterns, which in turn might help to advance predator-prey research.
@@
 If experience reduces the costs of switching between low and high speeds as predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds.
-However, if individuals encounter similar groups of prey, then the efficiency of a specific tactic should increase with experience and everyone should instead specialize in their speed.
+However, if individuals encounter similar groups of prey, then the efficiency of a specific tactic should increase with experience and everyone should instead specialize in similar speeds.
 In both scenarios, among individual variation in IIV (i.e.
@@
 In this case, we expect predators that experienced more predictable encounters with their prey (i.e.
-similar groups across matches) to specialize in their speed, while predators that experienced unpredictable encounters with their prey (i.e.
+similar groups across matches) to specialize in similar speeds, while predators that experienced unpredictable encounters with their prey (i.e.
 heterogeneous groups across matches) should adopt flexible movement speeds.
@@
 However, we observed that 44% of the predator population showed close to no change in specialization with experience.
-Since these individuals were already specialized as novices (MFF personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they more often encountered faster prey.
+Since these individuals were already specialized as novices (Fraser Franco, personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they more often encountered faster prey.
 This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
@@
 We also confirmed that experience and predator-prey encounters drove the patterns of individual foraging specialization and flexibility.
-Our results suggest that predators learned with experience, as their success increased and their speed remained matched the speed of their prey.
-Even though individuals were not all equally successful, both specialized and flexible tactics achieved similar hunting success.
+Our results suggest that predators learned with experience, as their success increased and their speed remained matched to the speed of their prey.
+Even though individuals were not all equally successful, both specialized and flexible hunters achieved similar success.
 One limitation of our study was that we couldn't monitor all the matches of the prey, which prevented us from assessing their responses to the predator.
@@
 for our collaboration which helps in advancing predator-prey science.
-We thank Julien Céré who managed the communication between us and the company, and Marine Dupuy who helped us prepare the data used in this study.
+We thank Julien Céré who managed the communication between us and Behaviour Interactive Inc., and Marine Dupuy who helped us prepare the data used in this study.
 We thank Alastair J.

### 2023-06-20 manuscript/Chapter2-manuscript.Rmd
minor updates to answer JM comments .rmd

@@
 All models were fitted under a Bayesian framework in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
-The models were compiled on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
+The models were run on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
 Each required 64GB of RAM with 48 cores to compile within 5 days.
@@
 This model assumes that predators do not share a common relationship between success and experience.
-The fourth and fifth models were a reproduction of the second and third models respectively, where we included the prey speed to assess its effect on the relationship between success and experience.
+The fourth and fifth models were reproductions of the second and third models respectively, where we included the prey speed to assess its effect on the relationship between success and experience.
 We included the standardized match duration and prey rank as covariates in all five models.
@@
 Fixed and random effect structure were trait-specific and the same for all experience levels.
-The predator and the prey speed included a mean and a dispersion part.
+The predator and the prey speed included a mean and a dispersion part (eqn 1.1, 1.2 and 2.1, 2.2).
 For both traits, we controlled for the standardized prey rank on both the mean and the dispersion parts of the model.
@@
 The dispersion part included individual predator identity random effects exclusively.
-For hunting success, we modeled the mean part only and controlled for the standardized prey rank and game duration, and included an individual identity random effect.
+For hunting success, we modeled the mean part only (eqn 3) and controlled for the standardized prey rank and game duration, and included an individual identity random effect.
 
-The model simultaneously estimated three individual components for each trait across experience levels.
-The first component, estimated on the mean part of the model, is among individual variation in mean speed and success.
+The model simultaneously estimated five among-individual variance components with their covariances for each experience level, resulting in a 15x15 (co)variance matrix.
+For each experience level, the model estimated among individual variance in mean predator speed, mean prey speed, and mean hunting success.
 This allows to test for individual differences in tactic use (i.e.
 along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption.
-The second component, estimated on the dispersion part of the model by modeling the residuals, is among individual variation in intra-individual variation (IIV).
+The model also estimated among individual variance in intra-individual variation (IIV) for both prey and predator speed.
 This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization.
-A general intercept is also fitted on both the mean and dispersion part of the model, providing population-level estimates of the aforementioned parameters.
-The third component consists of pairwise comparisons between the individual identity standard deviations on the mean and dispersion part of the model among traits, among experience, and across traits and experience.
-This results in a 15x15 (co)variance matrix, allowing to describe the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.
+Finally, the model estimated all pairwise covariances at the individual level among traits, among experience, and across traits and experience.
+The resulting 15x15 (co)variance matrix thus provides the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.
 
@@
 The $d$ subscript indicates that a term is from the dispersion part of the model.
-The $b$ terms are vectors of fixed effects with their design matrices $X$.
-The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their design matrices $M$, $N$, and $Z$.
-For all experience levels of $Y_{1}$ and $Y_{2}$, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en_{12j} \sim N(0,\ I\ \sigma_{en_{12j}})$ and $av_{12j} \sim N(0,\ I\ \sigma_{av_{12j}})$).
-$I$ is the identity matrix, with $I\sigma$ indicating that the random effects are independently and identically distributed.
-In addition, we assumed that the residuals follow a Gaussian distribution with observation-specific standard deviations $e_{12j} \sim N(0,\ Diag\{\sigma_{e_{12j}}\})$.
-All the individual identity random effects (mean and dispersion) across all response variables and experience levels are indexed in vector $\alpha$.
-The $\alpha$ vector follows a multivariate Gaussian distribution $\alpha \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of the individual identity standard deviations $\sigma_{id_{ij}}$ across all response variables and experience levels.
+The $b$ terms are vectors of fixed effects with their design matrices $X$ specific to each trait and experience level.
+The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their design matrices $M$, $N$, and $Z$ specific to each trait and experience level.
+For all experience levels of $Y_{1}$ and $Y_{2}$, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en_{12j} \sim N(0,\ I\ \sigma_{en_{12j}}^{2})$ and $av_{12j} \sim N(0,\ I\ \sigma_{av_{12j}}^{2})$).
+$I$ is the identity matrix, with $I\sigma^{2}$ indicating that the random effects are independently and identically distributed.
+In addition, we assumed that the residuals follow a Gaussian distribution with observation-specific variance $e_{12j} \sim N(0,\ Diag\{\sigma_{e_{12j}}^{2}\})$.
+The 15 individual identity random effects $id_{ij}$ across all response variables and experience levels (five for each of the three experience levels) are indexed in vector $\alpha$.
+The $\alpha$ vector follows a multivariate Gaussian distribution $\alpha \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of among individual variation across all response variables and experience levels, with $\sigma_{id_{ij}}^{2}$ on the diagonal and covariances off-diagonal.
 
-We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1)$: eqn.
-1.1 to 2.2) and game duration ($N(0.5,\ 0.5)$: eqn.
+We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1^{2})$: eqn.
+1.1 to 2.2) and game duration ($N(0.5,\ 0.5^{2})$: eqn.
 3).
-Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3,\ 0.5)$: eqn.
+Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3,\ 0.5^{2})$: eqn.
 1.1 and 2.1).
-Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,\ 1)$: eqn 1.2 and 2.2).
-For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1)$: eqn.
-3) and a negative Gaussian prior ($N(-4,\ 1)$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration.
-For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1)$) on the random effects for the mean part and the dispersion part of the model.
+Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,\ 1^{2})$: eqn 1.2 and 2.2).
+For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1^{2})$: eqn.
+3) and a negative Gaussian prior ($N(-4,\ 1^{2})$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration.
+For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1^{2})$) on the random effects for the mean part and the dispersion part of the model.
 We used a regularizing $LKJ(2)$ prior on the correlation matrix.
@@
 Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why such prey were more difficult to capture.
-Thus, predators that couldn't properly hunt at high speeds or develop counterstrategies for faster prey were likely at a disadvantage.
+Thus, predators that couldn't properly hunt at high speeds or develop counter-strategies for faster prey were likely at a disadvantage.
 
@@
 In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape patterns than one that played 300 matches in the span of six days.
-Accounting for such time lags may reveal important insights on the outcome of predator-prey interactions.
+Investigating the impact of such time lags in future analyses may reveal important insights on the outcome of predator-prey interactions.
 
@@
 Yet, because prey can also learn how to avoid predation [@kelley2003;@turner2006;@mccomb2011], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a].
-Indeed, 44% of the predator population altered its behaviour with experience to different degrees, and 12% even switched between flexibility and specialization.
-Hence, if the prey also learned through repeated interactions with the predators, it is possible that experience contributed in stabilizing the system as both were adusting to each other, similar to Red Queen dynamics [@brockhurst2014].
+Indeed, 56% of the predator population altered its behaviour with experience to different degrees, including 12% that even switched between flexibility and specialization.
+Hence, if the prey also learned through repeated interactions with the predators, it is possible that experience contributed in stabilizing the system as both were adjusting to each other, similar to Red Queen dynamics [@brockhurst2014].
 Our results appear to support this since many individuals were shifting their behavioural niche while the population niche remained stable across experience.
@@
 Specialist foragers were faster, and thus, probably better equipped to hunt the more difficult faster prey in *DBD*.
-However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for the predator, thereby nullifying the benefits of using this tactic (Figure 4).
+However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for the predator, thereby decreasing the benefits of using this tactic (Figure 4).
 Thus, specializing probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
@@
 Wilson for insightful comments on the results.
-We also thank all members of Pierre-Olivier Montiglio's laboratory who provided useful feedback on earlier versions on this work.
+We also thank all members of Pierre-Olivier Montiglio's laboratory who provided useful feedback on earlier versions of this work.
 This work was supported by an NSERC postgraduate doctoral scholarship (569716-2022).
@@
 
-The authors declare no conflict of interest
+The authors declare no conflict of interest.
 
@@
 Panels A and C show the development of expertise for the average individual with the vertical dashed lines on the left representing the lowest predicted values.
-For panel A, the right-side vertical dashed lines shows the highest predicted success.
+For panel A, the right-side vertical dashed line shows the highest predicted success.
 For panel C, the right-side dashed line represents the point on the curve where success was optimized, which we calculated using the finite differences method to obtain the first derivative of the predicted values.
@@
 We built the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selected those with the greatest difference using the 25% and 75% quantiles.
-Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal or greater than 0.2 standard deviations.
+Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal to or greater than 0.2 standard deviations.
 
@@
 C) Posterior median differences and HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels.
-The difference is displayed on the y axis and the correlated traits being compared are displayed on the x axis.Positive values indicate an increase in correlation strength from novice to the advanced stage, while negative values indicate stronger correlations when predators were novice.
+The difference is displayed on the y axis and the correlated traits being compared are displayed on the x axis.
+Positive values indicate an increase in correlation strength from novice to the advanced stage, while negative values indicate stronger correlations when predators were novice.
 

### 2023-06-20 manuscript/Chapter2-manuscript.Rmd
version for submission ready

@@
 We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
-We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id})$).
-We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5)$) and the global trend of cumulative experience ($N(0,\ 2)$).
-Following @FraserFranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5)$), a positive Gaussian prior ($N(1,\ 0.5)$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5)$) because encountering faster prey is associated with lower success in this system.
-We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0,\ 0.5)$).
+We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id}^{2})$).
+We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5^{2})$) and the global trend of cumulative experience ($N(0,\ 2^{2}))$).
+Following @FraserFranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5^{2})$), a positive Gaussian prior ($N(1,\ 0.5^{2}))$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5^{2})$) because encountering faster prey is associated with lower success in this system.
+We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0,\ 0.5^{2})$).
 We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].

### 2023-10-17 manuscript/Chapter2-manuscript.Rmd
updt 1st paragraph of intro for 3rd submission

@@
 Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals specializing on different foraging tactics, with consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
-Despite clear evidence that individual specialization is important in predator-prey interactions, its underlying mechanisms remain surprisingly unclear.
-One hypothesis suggests that reciprocal interactions between predators and prey could drive individual foraging specialization [@Araujo.etal2011;@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022].
-For instance, predators often hunt using techniques that are fine-tuned to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Courbin.etal2018], and their refinement is crucial for young predators to reach adulthood and survive [@Phillips.etal2017;@Heithaus.etal2018].
-Thus, the capacity of predators to effectively use hunting tactics should be contingent on periods of extensive practice (i.e.
-experience), which may result in different foraging specializations.
+Indeed, predator populations often comprise assemblages of individuals using different foraging tactics to hunt their prey, with consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
+Theory suggests that foraging tactics are learned through repeated interactions with prey, and the capacity of predators to effectively use them should be contingent on periods of extensive practice, i.e., experience [@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022;@Tinker.etal2009;@Dukas2019].
+Empirical studies show that predators often hunt using techniques that are fine-tuned to the type of prey that they encounter, and their refinement is crucial for young predators to reach adulthood and survive [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Heithaus.etal2018;@Courbin.etal2018].
+However, the underlying mechanisms shaping these processes remain unclear, which hinders our ability to predict the behavioural decisions and the success of predators when they are hunting.
 
@@
 Given the dynamic nature of predator-prey interactions, it is likely that ontogenic behavioural changes in predators play an important role, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].
-Uncovering the role of experience in shaping direct predator-prey interactions would help to predict the behavioural decisions and the success of predators when they are hunting.
 

### 2023-10-17 manuscript/Chapter2-manuscript.Rmd
updated second paragraph. left notes

@@
 Theory suggests that foraging tactics are learned through repeated interactions with prey, and the capacity of predators to effectively use them should be contingent on periods of extensive practice, i.e., experience [@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022;@Tinker.etal2009;@Dukas2019].
-Empirical studies show that predators often hunt using techniques that are fine-tuned to the type of prey that they encounter, and their refinement is crucial for young predators to reach adulthood and survive [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Heithaus.etal2018;@Courbin.etal2018].
-However, the underlying mechanisms shaping these processes remain unclear, which hinders our ability to predict the behavioural decisions and the success of predators when they are hunting.
+Predators often hunt using techniques that are fine-tuned to the type of prey that they encounter, and their refinement is crucial for young predators to reach adulthood and survive [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Heithaus.etal2018;@Courbin.etal2018].
+For example, predatory blue acaras (*Andinoacara pulcher*) adjust their maximum approach speed through repeated exposures to prey with different escape patterns [@Szopa-Comley.Ioannou2022].
+However, the mechanisms underlying how individuals respond to experience, as well as their consequences, remain unclear, hindering our ability to predict the behavioural decisions and the success of predators when they are hunting.
 
-Theory predicts that foraging specialization may emerge via learning and expertise acquisition [@Tinker.etal2009;@Dukas2019].
-@Dukas2019 defines expertise as the characteristics, skills, and knowledge that allow individuals with extensive experience to outperform novices on complex tasks.
-It is described as the relationship between success and experience, where extensive practice optimizes success when individuals reach an advanced level of experience.
-Empirical studies on human and non-human hunters show that experience optimizes foraging efficiency (e.g.
-search and handling times, return rates) potentially via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
-This body of work suggests that such optimization may thus promote individual foraging specialization (e.g.
-repeatedly using fast attacks) if the success of a tactic is constant through time.
-It may also be costly to test different tactics by trial and error when prey are scarce or unpredictable.
-Alternatively, the costs/risks faced by hunters when switching tactics may be offset through extensive practice, as individuals gain experience and information on their prey, leading to increased individual foraging flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
+Empirical studies on human and non-human hunters show that individuals optimize foraging efficiency (e.g.
+search and handling times, return rates) via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
+Through this process, predators with extensive practice acquire expertise (e.g.
+skills, knowledge) that allows them to outperform novice hunters [@Dukas2019].
+In light of this work, it has been suggested that experience may lead to individual foraging specialization (e.g.
+repeatedly using fast attacks) if a predator consistently increases its prey capture by using the same tactic through time [@Tinker.etal2009;@Dukas2019].
+Yet, an alternative view is that learning operates as a mechanism driving behavioural flexibility.
+For instance, predators gain experience and information on their prey as they hunt in varying habitats, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
+
+**Parler des risques pour la transition et les couts/bénéfices qui varient selon le contexte**
+(ici, je dois toutefois faire ressortir qu'il est dangeureux d'être spécialiste si les ressources fluctuent beaucoup.)
+Moreover, individual specialists may avoid the risks of loosing a meal by testing other tactics through trial and error, which can be highly costly if prey are scarce.
+
+Alternatively,  the costs/risks faced by hunters when switching tactics may be offset through extensive practice,
+
 However, predators can differ in the challenges that they face during their lifetime, which could result in both processes (i.e.
@@
 If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success probably because they learned from experience how to adjust their hunting style to their prey.
+
+It is described as the relationship between success and experience, where extensive practice optimizes success when individuals reach an advanced level of experience.
+(ceci devrait aller dans les hypothèses)
 

### 2023-10-17 manuscript/Chapter2-manuscript.Rmd
added notes for par 2 and 3

@@
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
+The importance of context in defining how individual predators learn to hunt makes it difficult to predict whether they should specialize or not in their foraging behaviour with experience.
 
@@
 For example, some individuals may hunt in habitats where prey are faster, which are often proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-Thus, it should be essential for predators to learn how to adjust their tactic to their prey to optimize their success.
+
+Deux idées pour le paragraphe suivant :
+1.
+Focus sur les contextes qui génèrent des différences, et qui devraient donc aussi mener à des différences de fitness (moins mettre l'accent sur le manque de consensus et plutôt focus sur les contextes, pour ensuite expliquer que donc ça devrait être mieux dans un que l'autre)
+2. soit focus sur le fait qu'il y a des différences d'aptitude
 
@@
 This discrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility.
-However, many studies also show that both type of foragers can attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018].
+However,
+(*pourrait retirer en haut et commencer ici*)
+many studies also show that both type of foragers can attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018].
 It is hypothesized that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.

### 2023-10-17 manuscript/Chapter2-manuscript.Rmd
added more notes to par 2 and 3

@@
 To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
-The importance of context in defining how individual predators learn to hunt makes it difficult to predict whether they should specialize or not in their foraging behaviour with experience.
+Context-dependence has proven to be key in defining how individual predators learn to hunt, making it challenging to predict under which circumstances they should specialize in their foraging with experience.
 
@@
 Focus sur les contextes qui génèrent des différences, et qui devraient donc aussi mener à des différences de fitness (moins mettre l'accent sur le manque de consensus et plutôt focus sur les contextes, pour ensuite expliquer que donc ça devrait être mieux dans un que l'autre)
-2. soit focus sur le fait qu'il y a des différences d'aptitude
+2. Je pourrais aussi commencer avec l'exemple indiquant que le foraging behaviour est lié aux proies rencontrées ou capturées
 

### 2023-10-19 manuscript/Chapter2-manuscript.Rmd
update bib et intro par1 et 2

@@
 
-Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [@Griffen.etal2012;@Michalko.Pekar2016;@Moran.etal2017;@Michalko.etal2021].
-Indeed, predator populations often comprise assemblages of individuals using different foraging tactics to hunt their prey, with consequences for habitat use, functional responses, prey choice, and foraging rate [@Kobler.etal2009;@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@Matsumura.Miyatake2022a].
-Theory suggests that foraging tactics are learned through repeated interactions with prey, and the capacity of predators to effectively use them should be contingent on periods of extensive practice, i.e., experience [@toscanoPersonalityForagingBehavior2016;@DeLisle.etal2022;@Tinker.etal2009;@Dukas2019].
-Predators often hunt using techniques that are fine-tuned to the type of prey that they encounter, and their refinement is crucial for young predators to reach adulthood and survive [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Heithaus.etal2018;@Courbin.etal2018].
-For example, predatory blue acaras (*Andinoacara pulcher*) adjust their maximum approach speed through repeated exposures to prey with different escape patterns [@Szopa-Comley.Ioannou2022].
-However, the mechanisms underlying how individuals respond to experience, as well as their consequences, remain unclear, hindering our ability to predict the behavioural decisions and the success of predators when they are hunting.
+Predator express a diverse array of hunting tactics to capture their prey.
+In natural populations, individual differences in tactics such as slow and fast movement speeds or high attack frequencies are associated with differences in prey choice and prey consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
+Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
+Such antipredator tactics often result in reciprocal interactions where predators fine-tune their tactics to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Heithaus.etal2018;@Courbin.etal2018].
+This has prompted ecologists to hypothesize that individual predators develop their hunting tactics by learning through repeated interactions with their prey.
+Thus, predators may only be successful if they learn how to hunt their prey by refining their hunting tactics, which should require periods of extensive practice, i.e., experience [@DeLisle.etal2022;@Tinker.etal2009;@Dukas2019].
 
@@
 search and handling times, return rates) via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
-Through this process, predators with extensive practice acquire expertise (e.g.
+As predators practice and refine their tactics, they acquire expertise (e.g.
 skills, knowledge) that allows them to outperform novice hunters [@Dukas2019].
-In light of this work, it has been suggested that experience may lead to individual foraging specialization (e.g.
-repeatedly using fast attacks) if a predator consistently increases its prey capture by using the same tactic through time [@Tinker.etal2009;@Dukas2019].
-Yet, an alternative view is that learning operates as a mechanism driving behavioural flexibility.
-For instance, predators gain experience and information on their prey as they hunt in varying habitats, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
-To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013].
-Context-dependence has proven to be key in defining how individual predators learn to hunt, making it challenging to predict under which circumstances they should specialize in their foraging with experience.
+Through this process, it is hypothesized that individuals may specialize in a hunting tactic (e.g.
+always moving fast) if it allows them to maintain successful prey captures at each atempt [@Tinker.etal2009;@Dukas2019].
+An alternative view is that learning operates as a mechanism driving behavioural flexibility.
+For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
+
+Ecological interactions when individuals are novice can also shape learning and behavioural trajectories [@vilapouca2021;@beyts2023], making it challenging to predict under which circumstances individuals should specialize in their foraging with experience (REFS).
 
@@
 
+To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013]
+
 However, predators can differ in the challenges that they face during their lifetime, which could result in both processes (i.e.
@@
 For example, some individuals may hunt in habitats where prey are faster, which are often proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
+
+*dans mcghee :*
+*The coexistence of a range of consistent behavioral types within prey (or predator) populations (Sih et al.
+2004a, 2004c) creates a situation where individual prey (or predators) are not equivalent to one another in terms of predation risk (or threat).*
 
@@
 
-There is currently a lack of consensus on the fitness advantages of specialized vs flexible foraging strategies [@Phillips.etal2017].
-Some studies have found greater success for individuals specializing on a foraging tactic [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others have found that individuals using flexible foraging tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021].
+There is currently a lack of consensus on the fitness advantages of specialized vs flexible hunting strategies [@Phillips.etal2017].
+Some studies have found greater success for individuals specializing on a hunting tactic [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others have found that individuals using flexible hunting tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021].
 This discrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility.
 However,
+
 (*pourrait retirer en haut et commencer ici*)
@@
 Second, we test the hypothesis that experience will shape individual foraging specialization.
-We define foraging tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e.
+We define hunting tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e.
 IIV) in movement speed across matches, where low IIV translates to individual specialization (e.g.

### 2023-10-20 manuscript/Chapter2-manuscript.Rmd
updated refs and intro. getting there

@@
 Predator express a diverse array of hunting tactics to capture their prey.
-In natural populations, individual differences in tactics such as slow and fast movement speeds or high attack frequencies are associated with differences in prey choice and prey consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
-Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-Such antipredator tactics often result in reciprocal interactions where predators fine-tune their tactics to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Heithaus.etal2018;@Courbin.etal2018].
-This has prompted ecologists to hypothesize that individual predators develop their hunting tactics by learning through repeated interactions with their prey.
-Thus, predators may only be successful if they learn how to hunt their prey by refining their hunting tactics, which should require periods of extensive practice, i.e., experience [@DeLisle.etal2022;@Tinker.etal2009;@Dukas2019].
+In natural populations, differences among individuals in tactics such as slow and fast movement speeds or high attack frequencies are associated with differences in prey choice and prey consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
+Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@Walker.etal2005;@Kelley.Magurran2011;@Herbert-Read.etal2017].
+Such antipredator tactics result in reciprocal interactions where predators fine-tune hunting style to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Courbin.etal2018].
+Winning the interaction would require that predators refine their tactics through periods of extensive practice [@DeLisle.etal2022;@Tinker.etal2009;@Dukas2019], suggesting that predators may learn through repeated interactions with their prey.
+This implies that a predator's prior experience and skills is an essential component that mediates hunting behaviour and the outcome of predator-prey interactions, with potential implications for community dynamics [@wooster2023].
 
@@
 For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
+However, theoretical and empirical evidence suggests that ecological interactions in early developmental stages can define how learning shapes the behaviour of individuals at later stages [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023], making it challenging to predict under which circumstances individuals should specialize in their foraging with experience.
 
-Ecological interactions when individuals are novice can also shape learning and behavioural trajectories [@vilapouca2021;@beyts2023], making it challenging to predict under which circumstances individuals should specialize in their foraging with experience (REFS).
+When predators learn to hunt in environments where resources are predictable (or stable), individuals should specialize in their foraging behaviour through time because they need less energy and time to search for and handle prey [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015].
+In contrast, while there are risks to attempt novel tactics by trial and error, predators can reduce the consequences of uncertainty when hunting in environments with fluctuating resources by learning to switch hunting tactics [@dall2010;@Szopa-Comley.Ioannou2022].
+(*pourrait donner les exemples direct, et ensuite expliquer que cest toutefois tough d'établir les liens entre tout ça.
+Ultimement, la fitness doit appraitre quelque part.*)
 
-**Parler des risques pour la transition et les couts/bénéfices qui varient selon le contexte**
-(ici, je dois toutefois faire ressortir qu'il est dangeureux d'être spécialiste si les ressources fluctuent beaucoup.)
-Moreover, individual specialists may avoid the risks of loosing a meal by testing other tactics through trial and error, which can be highly costly if prey are scarce.
+Such contexts are important in defining which strategy (i.e. specialized vs flexible foraging)
 
-Alternatively,  the costs/risks faced by hunters when switching tactics may be offset through extensive practice,
-
-To develop proper responses to fluctuating resources, individuals would need to sample their environment broadly during an extensive period, leading to greater performance at later stages of development [reviewed in @Snell-Rood2013]
-
-However, predators can differ in the challenges that they face during their lifetime, which could result in both processes (i.e.
-specialization and flexibility) operating at the same time within a predator population.
-For example, some individuals may hunt in habitats where prey are faster, which are often proven to be more difficult to hunt [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-
-*dans mcghee :*
-*The coexistence of a range of consistent behavioral types within prey (or predator) populations (Sih et al.
-2004a, 2004c) creates a situation where individual prey (or predators) are not equivalent to one another in terms of predation risk (or threat).*
+il est toutefois difficile d'établir le niveau de fluctuation des resources lié à l'apprentissage et la stratégie de chasse.
 
@@
 Focus sur les contextes qui génèrent des différences, et qui devraient donc aussi mener à des différences de fitness (moins mettre l'accent sur le manque de consensus et plutôt focus sur les contextes, pour ensuite expliquer que donc ça devrait être mieux dans un que l'autre)
-2. Je pourrais aussi commencer avec l'exemple indiquant que le foraging behaviour est lié aux proies rencontrées ou capturées
 
@@
 Some studies have found greater success for individuals specializing on a hunting tactic [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others have found that individuals using flexible hunting tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021].
-This discrepancy may in part be due to the limited information we have on the ecological contexts favoring individual specialization over flexibility.
-However,
 
@@
 many studies also show that both type of foragers can attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018].
-It is hypothesized that when resources are predictable (or stable), individual specialists should have higher capture rates by reducing the energy and time required to search for and handle prey.
-In contrast, individual generalists should benefit from adjusting to fluctuating resources by reducing the consequences of uncertainty [@dall2010].
-While it is clear that predators can match their hunting behaviour and locomotion to their prey [@McGhee.etal2013a;@Bro-Jorgensen2013;@Chang.etal2017;@Szopa-Comley.Ioannou2022], the important question remaining is how.
-Given the dynamic nature of predator-prey interactions, it is likely that ontogenic behavioural changes in predators play an important role, because complex hunting strategies require practice to be effective [@Kelley.Magurran2011].
+
+finir le troisième paragraphe en disant que ultimement, si les individus vivent des degrés de fluctuations différentes, ils devraient pouvoir coexister dans la même population.
 

### 2023-10-23 manuscript/Chapter2-manuscript.Rmd
updated 3rd intro paragraph. add notes for par4.

@@
 Predator express a diverse array of hunting tactics to capture their prey.
-In natural populations, differences among individuals in tactics such as slow and fast movement speeds or high attack frequencies are associated with differences in prey choice and prey consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
+In natural populations, differences among individuals in tactics such as slow and fast movement speeds or high attack frequencies are associated with differences in prey choice and consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
 Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@Walker.etal2005;@Kelley.Magurran2011;@Herbert-Read.etal2017].
-Such antipredator tactics result in reciprocal interactions where predators fine-tune hunting style to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Courbin.etal2018].
-Winning the interaction would require that predators refine their tactics through periods of extensive practice [@DeLisle.etal2022;@Tinker.etal2009;@Dukas2019], suggesting that predators may learn through repeated interactions with their prey.
+This results in reciprocal interactions where predators fine-tune their hunting style to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Courbin.etal2018].
+Such prey specific tactics should require periods of extensive practice to be effective [@DeLisle.etal2022;@Tinker.etal2009;@Dukas2019], suggesting that predators must learn through repeated interactions with their prey.
 This implies that a predator's prior experience and skills is an essential component that mediates hunting behaviour and the outcome of predator-prey interactions, with potential implications for community dynamics [@wooster2023].
@@
 For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
-However, theoretical and empirical evidence suggests that ecological interactions in early developmental stages can define how learning shapes the behaviour of individuals at later stages [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023], making it challenging to predict under which circumstances individuals should specialize in their foraging with experience.
+However, ecological interactions and conditions during early development can define how learning shapes the behaviour of individuals through time [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023], making it challenging to predict under which circumstances individuals should specialize in their foraging with experience.
 
-When predators learn to hunt in environments where resources are predictable (or stable), individuals should specialize in their foraging behaviour through time because they need less energy and time to search for and handle prey [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015].
-In contrast, while there are risks to attempt novel tactics by trial and error, predators can reduce the consequences of uncertainty when hunting in environments with fluctuating resources by learning to switch hunting tactics [@dall2010;@Szopa-Comley.Ioannou2022].
-(*pourrait donner les exemples direct, et ensuite expliquer que cest toutefois tough d'établir les liens entre tout ça.
-Ultimement, la fitness doit appraitre quelque part.*)
-
-Such contexts are important in defining which strategy (i.e. specialized vs flexible foraging)
-
-il est toutefois difficile d'établir le niveau de fluctuation des resources lié à l'apprentissage et la stratégie de chasse.
-
-Deux idées pour le paragraphe suivant :
-1.
-Focus sur les contextes qui génèrent des différences, et qui devraient donc aussi mener à des différences de fitness (moins mettre l'accent sur le manque de consensus et plutôt focus sur les contextes, pour ensuite expliquer que donc ça devrait être mieux dans un que l'autre)
-
-There is currently a lack of consensus on the fitness advantages of specialized vs flexible hunting strategies [@Phillips.etal2017].
-Some studies have found greater success for individuals specializing on a hunting tactic [@Pintor.etal2014;@Patrick.Weimerskirch2014a;@vandenBosch.etal2019] while others have found that individuals using flexible hunting tactics have greater success [@Paull.etal2012;@Santoro.etal2019;@Manlick.etal2021].
-
-(*pourrait retirer en haut et commencer ici*)
-many studies also show that both type of foragers can attain equal success depending on timescales, and suggest that fluctuating resources throughout a predator's lifetime may be key in shaping individual foraging specialization [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018].
-
-finir le troisième paragraphe en disant que ultimement, si les individus vivent des degrés de fluctuations différentes, ils devraient pouvoir coexister dans la même population.
+There is increasing evidence suggesting that the fitness consequences of specialization are context-dependent [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019;@Santoro.etal2019;@Manlick.etal2021].
+When predators learn to hunt in environments where resources are predictable (or stable), they should gradually specialize in their foraging tactics because they require less energy and time to search for and handle prey [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015].
+In contrast, while there are risks to attempt novel tactics by trial and error, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010].
+For example, @Szopa-Comley.Ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be equally successful to those exposed to predictable prey.
+Therefore, if specialist and generalist predators can attain equal success by fine-tuning their tactics to their prey [reviewed in @Phillips.etal2017], then empiricists should investigate the link between foraging specialization and success across time and contexts.
 
 A recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and the prey.
+(*DESCRIPTION DES JEUX VIDÉO ET LEURS AVANTAGES/DÉSAVANTAGES, JE POURRAIS DIRE QU'UN APPROCHE EST D'UTILISER DES SIMULATIONS ET DIRE RAPIDEMENT SES INCONVÉNIENTS, MAIS QU'UN MONDE VIRTUEL EST ENCORE MIEUX CAR ON GARDE L'ASPECT SIMULATION TOUT EN INJECTANT LA VARIATION COMPORTEMENTALE.
+POUR LES SIMULATIONS, JE PEUX DIRE QU'ON A UN GRAND CONTRÔLE SUR LE SYSTÈME, MAIS QU'ON A DES PATRONS ÉMERGENTS QUI SONT PARFOIS COMPLÈTEMENT IRRÉALISTES, COMME AVEC DES MÉSOCOSMES*)
+
+*AJOUTER LYMBERY AUX RÉFÉRENCES*
+
 We recently showed, using an online predator-prey videogame called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge [@FraserFranco.etal2022].
@@
 Predators should thus benefit from learning how the prey behave to be successful.
+Of course, the life of neither the predator nor the prey players are at stake, such that emerging patterns are only driven by their motivation to win and not "true" survival.
+Yet, an increasing number of ecological studies show that player behaviour in virtual systems
+
 Other virtual predator-prey studies show that predation regimes drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al., public communications and unpublished manuscript).
 These examples outline how virtual systems could be useful in identifying general ecological patterns, which in turn might help to advance predator-prey research.
-They also generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological scenarios.
+They also generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological contexts.
 Hence, virtual systems, including *DBD*, offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
 
-In this study, we evaluated how hunting experience shapes predator foraging specialization and success using data from players in the online videogame *Dead by Daylight*.
-First, we investigate how predators develop their individual hunting expertise.
+In this study, we assess how hunting experience shapes predator foraging specialization and success using data from players in the online videogame *Dead by Daylight*.
+First, we investigate how individual capture success changes with experience (i.e.
+how individuals develop their hunting expertise).
 We hypothesize that predators should differ in the development of their expertise if they encountered varying levels of difficulty with the prey that they pursued.

### 2023-10-24 manuscript/Chapter2-manuscript.Rmd
updated par1-2 again. create short par3. updt bib

@@
 Predator express a diverse array of hunting tactics to capture their prey.
-In natural populations, differences among individuals in tactics such as slow and fast movement speeds or high attack frequencies are associated with differences in prey choice and consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
+In natural populations, differences among individuals in tactics such as slow and fast movement speeds or high attack frequencies are associated with differences in prey consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
 Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@Walker.etal2005;@Kelley.Magurran2011;@Herbert-Read.etal2017].
-This results in reciprocal interactions where predators fine-tune their hunting style to the type of prey that they encounter [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017;@Courbin.etal2018].
-Such prey specific tactics should require periods of extensive practice to be effective [@DeLisle.etal2022;@Tinker.etal2009;@Dukas2019], suggesting that predators must learn through repeated interactions with their prey.
-This implies that a predator's prior experience and skills is an essential component that mediates hunting behaviour and the outcome of predator-prey interactions, with potential implications for community dynamics [@wooster2023].
+This results in reciprocal interactions where predators fine-tune their tactics to their prey, suggesting that they learn and become efficient hunters through repeated encounters [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017].
+Ultimately, the consequences of experience on the outcome of predator-prey interactions could have larger implications for ecosystem dynamics [@Tinker.etal2009;@Dukas2019;@wooster2023].
 
 Empirical studies on human and non-human hunters show that individuals optimize foraging efficiency (e.g.
-search and handling times, return rates) via associative images or reliance on prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
+search and handling times, return rates) by learning associative images or prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
 As predators practice and refine their tactics, they acquire expertise (e.g.
-skills, knowledge) that allows them to outperform novice hunters [@Dukas2019].
-Through this process, it is hypothesized that individuals may specialize in a hunting tactic (e.g.
+skills, knowledge) that allows them to outperform novice hunters [@Dukas2019;@wooster2023].
+Through this process, it is hypothesized that individuals will specialize in a hunting tactic (e.g.
 always moving fast) if it allows them to maintain successful prey captures at each atempt [@Tinker.etal2009;@Dukas2019].
-An alternative view is that learning operates as a mechanism driving behavioural flexibility.
-For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may thus hunt optimally by adjusting their behaviour to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Kelley.Magurran2011;@Snell-Rood2013].
-However, ecological interactions and conditions during early development can define how learning shapes the behaviour of individuals through time [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023], making it challenging to predict under which circumstances individuals should specialize in their foraging with experience.
+When predators learn to hunt in environments where resources are predictable (or stable), they should gradually specialize in their foraging tactics because they require less energy and time to search for and handle prey [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015].
+These conditions favor specialist hunters because there would be higher costs to switch tactics for the same type of prey.
+An alternative view is that learning is a mechanism driving behavioural flexibility.
+For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may hunt optimally by learning to adjust their tactic to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Kelley.Magurran2011].
+While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010].
+Yet, the feedbacks between ecological interactions and learning makes it challenging to predict under which circumstances predators should specialize with experience [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023].
 
-There is increasing evidence suggesting that the fitness consequences of specialization are context-dependent [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019;@Santoro.etal2019;@Manlick.etal2021].
-When predators learn to hunt in environments where resources are predictable (or stable), they should gradually specialize in their foraging tactics because they require less energy and time to search for and handle prey [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015].
-In contrast, while there are risks to attempt novel tactics by trial and error, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010].
+There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences is driven by resource fluctuation [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019;@Santoro.etal2019;@Manlick.etal2021].
+If predators in different environments adjust their hunting to local prey fluctuations, specialist and flexible hunters can both attain similar hunting success and coexist.
 For example, @Szopa-Comley.Ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be equally successful to those exposed to predictable prey.
@@
 A recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and the prey.
-(*DESCRIPTION DES JEUX VIDÉO ET LEURS AVANTAGES/DÉSAVANTAGES, JE POURRAIS DIRE QU'UN APPROCHE EST D'UTILISER DES SIMULATIONS ET DIRE RAPIDEMENT SES INCONVÉNIENTS, MAIS QU'UN MONDE VIRTUEL EST ENCORE MIEUX CAR ON GARDE L'ASPECT SIMULATION TOUT EN INJECTANT LA VARIATION COMPORTEMENTALE.
-POUR LES SIMULATIONS, JE PEUX DIRE QU'ON A UN GRAND CONTRÔLE SUR LE SYSTÈME, MAIS QU'ON A DES PATRONS ÉMERGENTS QUI SONT PARFOIS COMPLÈTEMENT IRRÉALISTES, COMME AVEC DES MÉSOCOSMES*)
-
-*AJOUTER LYMBERY AUX RÉFÉRENCES*
-
-We recently showed, using an online predator-prey videogame called *Dead by Daylight* (*DBD*), that virtual systems can overcome this challenge [@FraserFranco.etal2022].
-In this dynamic virtual system, four prey players need to forage for resources while avoiding predation by a fifth player.
-The prey can contribute to the group's success by healing or helping others escape from the predator, or be selfish and attempt to escape by themselves [@Cere.etal2021].
-The predators' hunting tactics and success are driven by the movement of the prey [@FraserFranco.etal2022].
+Simulations such as individual-based models can mitigate some of these challenges and have contributed in stirring testable ideas for empiricists [Refs].
+Yet, while providing maximum control over environmental parameters, they can suffer from emerging behaviours that are unrealistic for animals in nature [refs].
+Videogames offer an interesting alternative to agent-based simulations, providing structured and controled virtual environments where real players can interact.
+For example, in the online predator-prey videogame *Dead by Daylight* (*DBD*), four prey players need to forage for resources while avoiding predation by a fifth player.
+In this virtual system, the predators' hunting tactics and success are driven by the movement of the prey, and the prey can increase their chances of survival by cooperating and moving fast when they forage [@Cere.etal2021;@FraserFranco.etal2022, Santostefano et al.
+in press].
 Predators should thus benefit from learning how the prey behave to be successful.
-Of course, the life of neither the predator nor the prey players are at stake, such that emerging patterns are only driven by their motivation to win and not "true" survival.
-Yet, an increasing number of ecological studies show that player behaviour in virtual systems
-
-Other virtual predator-prey studies show that predation regimes drive individual variation in risk perception [@Beauchamp2020], that familiarity between prey has a positive indirect effect on survival [@Cere.etal2021], and that prey face contrasting natural and social selection regimes (Santostefano et al., public communications and unpublished manuscript).
-These examples outline how virtual systems could be useful in identifying general ecological patterns, which in turn might help to advance predator-prey research.
-They also generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological contexts.
-Hence, virtual systems, including *DBD*, offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
+Of course, the life of neither the predator nor the prey players are at stake, such that emerging patterns could be driven by their motivation to win and not "true" survival.
+Yet, the game often ellicits natural reactions in players such as fear from predation (personal observations), which corroborates with another virtual ecological study showing that predation drives individual variation in risk perception [@Beauchamp2020].
+Using simulations in the game Age of Empire II, @lymberyetal.2023 also showed that complex environments favor strong soldiers over large armies in the game as well as in the laboratory with two ant species.
+These examples outline how general ecological patterns can emerge from interactions in virtual systems with fixed rules, which in turn might help to advance predator-prey research.
+Videogames generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological contexts.
+Hence, they offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
 
 In this study, we assess how hunting experience shapes predator foraging specialization and success using data from players in the online videogame *Dead by Daylight*.
-First, we investigate how individual capture success changes with experience (i.e.
+First, we investigate how individual hunting success changes with experience (i.e.
 how individuals develop their hunting expertise).
@@
 For example, a predator may face greater difficulty than other individuals if it encountered elusive groups of prey more often.
+
 Second, we test the hypothesis that experience will shape individual foraging specialization.

### 2023-10-24 manuscript/Chapter2-manuscript.Rmd
update intro hypotheses

@@
 always moving fast) if it allows them to maintain successful prey captures at each atempt [@Tinker.etal2009;@Dukas2019].
-When predators learn to hunt in environments where resources are predictable (or stable), they should gradually specialize in their foraging tactics because they require less energy and time to search for and handle prey [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015].
+When predators learn to hunt in environments where resources are predictable (or stable), they should gradually specialize in their hunting tactics with experience because individuals require less energy and time to search for, capture, and handle prey [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015].
 These conditions favor specialist hunters because there would be higher costs to switch tactics for the same type of prey.
-An alternative view is that learning is a mechanism driving behavioural flexibility.
+An alternative hypothesis is that learning is a mechanism driving behavioural flexibility.
 For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may hunt optimally by learning to adjust their tactic to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Kelley.Magurran2011].
 While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010].
-Yet, the feedbacks between ecological interactions and learning makes it challenging to predict under which circumstances predators should specialize with experience [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023].
+Such feedbacks between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize with experience [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023].
 
 There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences is driven by resource fluctuation [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019;@Santoro.etal2019;@Manlick.etal2021].
-If predators in different environments adjust their hunting to local prey fluctuations, specialist and flexible hunters can both attain similar hunting success and coexist.
-For example, @Szopa-Comley.Ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be equally successful to those exposed to predictable prey.
-Therefore, if specialist and generalist predators can attain equal success by fine-tuning their tactics to their prey [reviewed in @Phillips.etal2017], then empiricists should investigate the link between foraging specialization and success across time and contexts.
+If predators in different environments adjust their hunting to local prey fluctuations, specialist and flexible hunters can both attain similar hunting success and coexist [@Phillips.etal2017].
+For example, @Szopa-Comley.Ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
+Therefore, if specialist and flexible hunters can attain equal success by learning through repeated interactions with their prey, then empiricists should investigate the link between foraging specialization and success across time and contexts.
 
 A recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and the prey.
-Simulations such as individual-based models can mitigate some of these challenges and have contributed in stirring testable ideas for empiricists [Refs].
+Individual-based models can mitigate some of these challenges and have contributed in stirring solid testable ideas for empiricists [Refs].
 Yet, while providing maximum control over environmental parameters, they can suffer from emerging behaviours that are unrealistic for animals in nature [refs].
-Videogames offer an interesting alternative to agent-based simulations, providing structured and controled virtual environments where real players can interact.
-For example, in the online predator-prey videogame *Dead by Daylight* (*DBD*), four prey players need to forage for resources while avoiding predation by a fifth player.
+Videogames offer an interesting alternative to agent-based simulations, providing controled virtual environments where real players can interact.
+For example, in the predator-prey videogame *Dead by Daylight*, four prey players need to forage for resources while avoiding predation by a fifth player.
 In this virtual system, the predators' hunting tactics and success are driven by the movement of the prey, and the prey can increase their chances of survival by cooperating and moving fast when they forage [@Cere.etal2021;@FraserFranco.etal2022, Santostefano et al.
@@
 Yet, the game often ellicits natural reactions in players such as fear from predation (personal observations), which corroborates with another virtual ecological study showing that predation drives individual variation in risk perception [@Beauchamp2020].
-Using simulations in the game Age of Empire II, @lymberyetal.2023 also showed that complex environments favor strong soldiers over large armies in the game as well as in the laboratory with two ant species.
+In the game Age of Empire II, @lymberyetal.2023 also showed that complex environments favor strong soldiers over large armies in the game as well as in the laboratory with two ant species.
 These examples outline how general ecological patterns can emerge from interactions in virtual systems with fixed rules, which in turn might help to advance predator-prey research.
@@
 
-In this study, we assess how hunting experience shapes predator foraging specialization and success using data from players in the online videogame *Dead by Daylight*.
+In this study, we assess how repeated experience shapes predator hunting specialization and success using data from players in *Dead by Daylight*.
 First, we investigate how individual hunting success changes with experience (i.e.
 how individuals develop their hunting expertise).
-We hypothesize that predators should differ in the development of their expertise if they encountered varying levels of difficulty with the prey that they pursued.
+We hypothesize that the predators' success will increase with experience up to a certain level where it will stagnate.
+We expect this pattern to vary among individuals due to differences in prey encounters.
 For example, a predator may face greater difficulty than other individuals if it encountered elusive groups of prey more often.
+Second, we assess how foraging specialization emerges with experience.
 
-Second, we test the hypothesis that experience will shape individual foraging specialization.
 We define hunting tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e.
@@
 always using a fast tactic).
+
 If experience reduces the costs of switching between low and high speeds as predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds.
@@
 If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success probably because they learned from experience how to adjust their hunting style to their prey.
-
-It is described as the relationship between success and experience, where extensive practice optimizes success when individuals reach an advanced level of experience.
-(ceci devrait aller dans les hypothèses)
 

### 2023-10-25 manuscript/Chapter2-manuscript.Rmd
arranged spacing in doc
update intro and knit

@@
 To do so, predators need to practice their tactics extensively to develop the skills and expertise to successfully hunt their prey, which may result in individual foraging specialization.
-Yet, there are very limited empirical assessments showing links between experience, foraging specialization, and performance at the individual level, due to the numerous challenges of monitoring direct interactions in the wild.
+Yet, there are very limited empirical assessments showing links between experience, foraging specialization, and hunting success at the individual level, due to the numerous challenges of monitoring direct interactions in the wild.
 In this study, we used a virtual predator-prey system (the online game *Dead by Daylight*) to investigate if and how hunting experience shapes individual foraging specialization and success in predators across repeated interactions with their prey.
 Our results show that predators optimized prey consumption as they gained experience.
-Prey behaviour was an important mediator of this relationship, which also drove individual differences in the development of expertise.
-With experience, differences among individuals in foraging specialization increased, as individual predators became either specialist or flexible foragers.
-Yet, many individuals remained specialists throughout the study period.
-Moreover, the matching between the predator's strategies (i.e.
-flexible or specialized foraging) and the prey was not strong, suggesting that part of the population did not match their tactic to the prey.
-This individual heterogeneity coincided with differences among individuals in success through time.
-While flexible foragers performed slightly less than specialist foragers, both achieved similar success overall.
-Our observations suggest that individual differences in behavioural change with experience may drive among individual differences in hunting tactics, which may act as a stabilizing mechanism promoting behavioural diversification in predator-prey systems.
+Prey behaviour was an important mediator of this relationship, resulting in differences among predators in the development of expertise.
+Throughout experience, 68% of predators became either increasingly specialized by always moving at a fast pace, or flexible by swithing between slow and fast speeds.
+The remaining 32% of predators used a specialized tactic of fast movement throughout the study period.
+Contrary to our predictions, the predator's strategies (i.e.
+flexible or specialized foraging) was not strongly matched to the preys' speed, suggesting that changes in hunting behaviour were driven more by repeated experience than the prey's speed.
+Ultimately, flexible foragers were only slightly less successful than specialist foragers, such that both achieved similar success overall.
+Our observations suggest that experience drives among individual differences in hunting tactics, which may act as a stabilizing mechanism promoting behavioural diversification in predator-prey systems.
 
@@
 Predator express a diverse array of hunting tactics to capture their prey.
-In natural populations, differences among individuals in tactics such as slow and fast movement speeds or high attack frequencies are associated with differences in prey consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
+In natural populations, differences among individuals in tactics such as ambushing, fast movement speeds, or high attack frequencies are associated with differences in prey consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
 Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@Walker.etal2005;@Kelley.Magurran2011;@Herbert-Read.etal2017].
 This results in reciprocal interactions where predators fine-tune their tactics to their prey, suggesting that they learn and become efficient hunters through repeated encounters [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017].
-Ultimately, the consequences of experience on the outcome of predator-prey interactions could have larger implications for ecosystem dynamics [@Tinker.etal2009;@Dukas2019;@wooster2023].
+These behavioural adjustments with experience can shape the outcome of predator-prey interactions, which may result in larger implications for community and ecosystem dynamics [@wooster2023].
 
@@
 For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may hunt optimally by learning to adjust their tactic to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Kelley.Magurran2011].
-While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010].
+While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010;@mathotAdaptiveStrategiesManaging2012].
 Such feedbacks between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize with experience [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023].
 
-There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences is driven by resource fluctuation [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019;@Santoro.etal2019;@Manlick.etal2021].
-If predators in different environments adjust their hunting to local prey fluctuations, specialist and flexible hunters can both attain similar hunting success and coexist [@Phillips.etal2017].
+There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences is driven by resource fluctuations [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019;@Santoro.etal2019;@Manlick.etal2021].
+If predators that hunt in different environments adjust their tactics to local prey fluctuations, then specialist and flexible hunters can both attain similar hunting success and coexist [@Phillips.etal2017].
 For example, @Szopa-Comley.Ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
@@
 
-A recurring challenge impeding research on predator-prey behavioural interactions, at the individual level, is the need to collect data simultaneously on both the predator and the prey.
-Individual-based models can mitigate some of these challenges and have contributed in stirring solid testable ideas for empiricists [Refs].
+A recurring challenge impeding research on predator-prey behavioural interactions is the need to collect data simultaneously on both the predator and the prey.
+Individual-based models can mitigate some of these challenges and have contributed in stirring testable ideas for empiricists [Refs].
 Yet, while providing maximum control over environmental parameters, they can suffer from emerging behaviours that are unrealistic for animals in nature [refs].
-Videogames offer an interesting alternative to agent-based simulations, providing controled virtual environments where real players can interact.
+Videogames offer an interesting alternative to agent-based simulations, providing controled virtual environments where real players interact.
 For example, in the predator-prey videogame *Dead by Daylight*, four prey players need to forage for resources while avoiding predation by a fifth player.
-In this virtual system, the predators' hunting tactics and success are driven by the movement of the prey, and the prey can increase their chances of survival by cooperating and moving fast when they forage [@Cere.etal2021;@FraserFranco.etal2022, Santostefano et al.
+In this virtual system, the predator population is composed of individuals that either ambush or hunt at high speeds (i.e.
+mean movement speed along a slow-fast continuum), and their success is driven by the movement of the prey [@FraserFranco.etal2022].
+We found that prey can increase their chances of survival by cooperating and moving fast when they forage [@Cere.etal2021;@, Santostefano et al.
 in press].
-Predators should thus benefit from learning how the prey behave to be successful.
 Of course, the life of neither the predator nor the prey players are at stake, such that emerging patterns could be driven by their motivation to win and not "true" survival.
-Yet, the game often ellicits natural reactions in players such as fear from predation (personal observations), which corroborates with another virtual ecological study showing that predation drives individual variation in risk perception [@Beauchamp2020].
-In the game Age of Empire II, @lymberyetal.2023 also showed that complex environments favor strong soldiers over large armies in the game as well as in the laboratory with two ant species.
-These examples outline how general ecological patterns can emerge from interactions in virtual systems with fixed rules, which in turn might help to advance predator-prey research.
-Videogames generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological contexts.
-Hence, they offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
+Yet, the game ellicits natural reactions in players such as fear from predation (personal observations), which corroborates with another virtual ecological study showing that predation drives individual variation in risk perception [@Beauchamp2020].
+In a different system, @lymberyetal.2023 showed that complex environments favor strong soldiers over large armies in a virtual game as well as in the laboratory with two ant species.
+These observations outline how ecological patterns can emerge from interactions in virtual systems with fixed rules.
+Videogames also generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological scenarios.
+Hence, virtual systems such as *Dead by Daylight* offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
 
@@
 Second, we assess how foraging specialization emerges with experience.
-
-We define hunting tactics as the mean movement speed of the predator along a slow-fast continuum, and the level of individual foraging specialization as the intra-individual variance (i.e.
-IIV) in movement speed across matches, where low IIV translates to individual specialization (e.g.
-always using a fast tactic).
-
-If experience reduces the costs of switching between low and high speeds as predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds.
-However, if individuals encounter similar groups of prey, then the efficiency of a specific tactic should increase with experience and everyone should instead specialize in similar speeds.
+We define the level of individual foraging specialization as the intra-individual variance (i.e.
+IIV) in movement speed across matches, where low IIV translates to individual specialization (i.e.
+always using a cursorial tactic).
+If all predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds.
+However, if individuals encounter similar groups of prey, then everyone should instead specialize in similar speeds.
 In both scenarios, among individual variation in IIV (i.e.
-individual differences in specialization) would be low across experience, whereas the population variance would either increase (flexibility) or decrease (specialization).
-Alternatively, both processes may operate at the same time if behavioural interactions with the prey vary among predators, such that among individual variation in IIV would increase.
+individual differences in specialization) should be low across experience, whereas the population variance would either increase (flexibility) or decrease (specialization).
+Alternatively, individual specialization and flexibility may emerge if individuals experience different interactions with their prey, such that among individual variation in IIV would increase.
 In this case, we expect predators that experienced more predictable encounters with their prey (i.e.
@@
 heterogeneous groups across matches) should adopt flexible movement speeds.
-If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success probably because they learned from experience how to adjust their hunting style to their prey.
+If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success if they learned from experience how to adjust their hunting style to their prey.
 

### 2023-10-25 manuscript/Authors.Rmd
remove author info from MS

--- 2023-10-25 manuscript/Chapter2-manuscript.Rmd
@@
     reference_docx: Chapter2-styles.docx
-    fig_caption: yes
-bibliography: 
-  - references1.bib
-  - references2.bib
-csl: ecology.csl
 ---
-
-```{r setup, include = FALSE}
-
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
-
-library(data.table)
-library(brms)
-library(flextable)
-library(officer)
-library(dplyr)
-
-```
-
-```{r}
-
-path <- file.path(here::here(), "data")
-
-dat <- fread(
-  file.path(path, "FraserFrancoetal2023-data.csv"),
-  select = c("timestamp", "match_id", "realm_id",
-             "environment_id", "avatar_id", "predator_id",
-             "game_duration", "total_xp_pred", "cumul_xp_pred",
-             "hunting_success", "pred_speed", "prey_avg_speed"))
-
-dat[, c(2:6) := lapply(.SD, function(x) as.factor(x)), .SDcols = c(2:6)]
-
-# To have a date column
-dat[, date := as.POSIXct(sub(" .*", "", timestamp))]
-
-```
-
-Journal name : Ecology
-
-Manuscript type : article
 
@@
 Keywords: foraging behaviour, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology, Dead by Daylight
-
-# ABSTRACT {.unnumbered}
-
-The capacity of predators to match their tactic to the behaviour of their prey is expected to drive the outcome of predator-prey interactions.
-To do so, predators need to practice their tactics extensively to develop the skills and expertise to successfully hunt their prey, which may result in individual foraging specialization.
-Yet, there are very limited empirical assessments showing links between experience, foraging specialization, and hunting success at the individual level, due to the numerous challenges of monitoring direct interactions in the wild.
-In this study, we used a virtual predator-prey system (the online game *Dead by Daylight*) to investigate if and how hunting experience shapes individual foraging specialization and success in predators across repeated interactions with their prey.
-Our results show that predators optimized prey consumption as they gained experience.
-Prey behaviour was an important mediator of this relationship, resulting in differences among predators in the development of expertise.
-Throughout experience, 68% of predators became either increasingly specialized by always moving at a fast pace, or flexible by swithing between slow and fast speeds.
-The remaining 32% of predators used a specialized tactic of fast movement throughout the study period.
-Contrary to our predictions, the predator's strategies (i.e.
-flexible or specialized foraging) was not strongly matched to the preys' speed, suggesting that changes in hunting behaviour were driven more by repeated experience than the prey's speed.
-Ultimately, flexible foragers were only slightly less successful than specialist foragers, such that both achieved similar success overall.
-Our observations suggest that experience drives among individual differences in hunting tactics, which may act as a stabilizing mechanism promoting behavioural diversification in predator-prey systems.
-
-\newpage
-# INTRODUCTION {.unnumbered}
-
-Predator express a diverse array of hunting tactics to capture their prey.
-In natural populations, differences among individuals in tactics such as ambushing, fast movement speeds, or high attack frequencies are associated with differences in prey consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
-Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@Walker.etal2005;@Kelley.Magurran2011;@Herbert-Read.etal2017].
-This results in reciprocal interactions where predators fine-tune their tactics to their prey, suggesting that they learn and become efficient hunters through repeated encounters [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017].
-These behavioural adjustments with experience can shape the outcome of predator-prey interactions, which may result in larger implications for community and ecosystem dynamics [@wooster2023].
-
-Empirical studies on human and non-human hunters show that individuals optimize foraging efficiency (e.g.
-search and handling times, return rates) by learning associative images or prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
-As predators practice and refine their tactics, they acquire expertise (e.g.
-skills, knowledge) that allows them to outperform novice hunters [@Dukas2019;@wooster2023].
-Through this process, it is hypothesized that individuals will specialize in a hunting tactic (e.g.
-always moving fast) if it allows them to maintain successful prey captures at each atempt [@Tinker.etal2009;@Dukas2019].
-When predators learn to hunt in environments where resources are predictable (or stable), they should gradually specialize in their hunting tactics with experience because individuals require less energy and time to search for, capture, and handle prey [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015].
-These conditions favor specialist hunters because there would be higher costs to switch tactics for the same type of prey.
-An alternative hypothesis is that learning is a mechanism driving behavioural flexibility.
-For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may hunt optimally by learning to adjust their tactic to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Kelley.Magurran2011].
-While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010;@mathotAdaptiveStrategiesManaging2012].
-Such feedbacks between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize with experience [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023].
-
-There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences is driven by resource fluctuations [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019;@Santoro.etal2019;@Manlick.etal2021].
-If predators that hunt in different environments adjust their tactics to local prey fluctuations, then specialist and flexible hunters can both attain similar hunting success and coexist [@Phillips.etal2017].
-For example, @Szopa-Comley.Ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
-Therefore, if specialist and flexible hunters can attain equal success by learning through repeated interactions with their prey, then empiricists should investigate the link between foraging specialization and success across time and contexts.
-
-A recurring challenge impeding research on predator-prey behavioural interactions is the need to collect data simultaneously on both the predator and the prey.
-Individual-based models can mitigate some of these challenges and have contributed in stirring testable ideas for empiricists [Refs].
-Yet, while providing maximum control over environmental parameters, they can suffer from emerging behaviours that are unrealistic for animals in nature [refs].
-Videogames offer an interesting alternative to agent-based simulations, providing controled virtual environments where real players interact.
-For example, in the predator-prey videogame *Dead by Daylight*, four prey players need to forage for resources while avoiding predation by a fifth player.
-In this virtual system, the predator population is composed of individuals that either ambush or hunt at high speeds (i.e.
-mean movement speed along a slow-fast continuum), and their success is driven by the movement of the prey [@FraserFranco.etal2022].
-We found that prey can increase their chances of survival by cooperating and moving fast when they forage [@Cere.etal2021;@, Santostefano et al.
-in press].
-Of course, the life of neither the predator nor the prey players are at stake, such that emerging patterns could be driven by their motivation to win and not "true" survival.
-Yet, the game ellicits natural reactions in players such as fear from predation (personal observations), which corroborates with another virtual ecological study showing that predation drives individual variation in risk perception [@Beauchamp2020].
-In a different system, @lymberyetal.2023 showed that complex environments favor strong soldiers over large armies in a virtual game as well as in the laboratory with two ant species.
-These observations outline how ecological patterns can emerge from interactions in virtual systems with fixed rules.
-Videogames also generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological scenarios.
-Hence, virtual systems such as *Dead by Daylight* offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
-
-In this study, we assess how repeated experience shapes predator hunting specialization and success using data from players in *Dead by Daylight*.
-First, we investigate how individual hunting success changes with experience (i.e.
-how individuals develop their hunting expertise).
-We hypothesize that the predators' success will increase with experience up to a certain level where it will stagnate.
-We expect this pattern to vary among individuals due to differences in prey encounters.
-For example, a predator may face greater difficulty than other individuals if it encountered elusive groups of prey more often.
-Second, we assess how foraging specialization emerges with experience.
-We define the level of individual foraging specialization as the intra-individual variance (i.e.
-IIV) in movement speed across matches, where low IIV translates to individual specialization (i.e.
-always using a cursorial tactic).
-If all predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds.
-However, if individuals encounter similar groups of prey, then everyone should instead specialize in similar speeds.
-In both scenarios, among individual variation in IIV (i.e.
-individual differences in specialization) should be low across experience, whereas the population variance would either increase (flexibility) or decrease (specialization).
-Alternatively, individual specialization and flexibility may emerge if individuals experience different interactions with their prey, such that among individual variation in IIV would increase.
-In this case, we expect predators that experienced more predictable encounters with their prey (i.e.
-similar groups across matches) to specialize in similar speeds, while predators that experienced unpredictable encounters with their prey (i.e.
-heterogeneous groups across matches) should adopt flexible movement speeds.
-If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success if they learned from experience how to adjust their hunting style to their prey.
-
-# MATERIALS AND METHODS {.unnumbered}
-
-## Study system
-
-*DBD* is a survival asymmetric multiplayer online game (i.e.
-a game where the gameplay mechanics differ between two groups) developed by Behaviour Interactive Inc, in which players can play either as a predator or a prey.
-Every match includes only one predator and four prey.
-The objective of the predator is to hunt and capture the prey, and the objective of the prey is to search for resources while avoiding the predator.
-The resources are in the form of power generators that, once all activated, will enable the prey to escape through one of two exit doors.
-The composition of the predator and prey group in a match is determined by a skill-based matchmaking algorithm.
-A match ends when the predator kills all the prey available (i.e.
-that have not escaped), or when the last remaining prey escapes the virtual environment.
-Each player, predator or prey, can choose an avatar with abilities that encourage specific play styles (e.g.
-bold vs cautious prey, or ambush vs roaming predator).
-During our study period, the game offered `r toString(format(length(unique(dat$avatar_id))))` predator avatars.
-The virtual environments are composed of fixed and procedurally generated habitat components, such as vegetation, mazes, and buildings.
-Some of these environments are larger than others, with varying structural complexity.
-However, predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling them to have visual cues of the generators [@FraserFranco.etal2022].
-There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during the study period.
-
-## Data collection
-
-The videogame company provided data that spanned a period of 6 months of gameplay recorded for every player from `r toString(format(min(dat$date)))` to `r toString(format(max(dat$date)))`.
-We only analyzed matches where players did not know each other (i.e.
-"Online" mode).
-We filtered any matches where players were inactive, such as when mean distances traveled per second (i.e.
-speed) were equal to, or very close to, zero.
-Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game as intended.
-We then sampled players that played 300 matches or more, and monitored all their matches from the first to a maximum of 500 matches.
-
-Our population consists of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(formatC(length(unique(dat$match_id)), big.mark = " "))` matches.
-The predator-players' experience varied between `r toString(format(min(dat$total_xp_pred)))` and `r toString(format(max(dat$total_xp_pred)))` matches played.
-These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)` min (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)` min).
-The following information is collected and reported for every match : the player's anonymous ID, its avatar (i.e.
-the predator character chosen with its specific skill-gameplay mechanics), the game environment, the predator-player's experience along with its speed, the mean speed of the groups of prey the player encountered, and their mean rank (a proxy for prey skill).
-The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank), and failing to account for it would prevent us from detecting a change in the predator's foraging success with experience.
-
-We analyzed the predator's mean speed and the mean speed of the prey group encountered by the predator.
-The predator's mean speed is measured as the mean distance traveled per second during a match (mean= `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
-We measured the preys' speed as the mean travel speed of the four individual prey in a match (mean = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
-We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
-Lastly, we defined the predator's cumulative experience as the number of matches played prior to the match being monitored.
-For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.
-We also categorized predators for each match based on their cumulated experience.
-We labeled predators as novices for matches where they had cumulated less than 100 matches, intermediate for matches where they had cumulated between 100 and 299 matches, and advanced for matches where they had cumulated more than 299 matches (max 499).
-Since our goal was to monitor predator players throughout their experience and that they all played at least 300 matches, they all appeared in each of the three experience categories.
-
-We recognize that we could have biased our analyses by retaining only individuals who played for at least 300 matches.
-For example, these individuals might be experienced videogame players and could thus already be playing like experts in their first matches in *DBD*.
-To verify that our sample was not biased, we compared a random sample of players that played either 20 to 50 matches, 51 to 100 matches, or 101 to 300 matches during the same timeframe as our sampled population.
-We then took the first 20 matches played by these players, including those from our sampled population, and compared their mean speed using a Bayesian hierarchical linear model.
-We found that all four groups had similar mean speeds as predators (Appendix 2: Table S1-S2), which indicates an absence of bias due to data sampling.
-
-## Statistical analyses
-
-### Software and computer specifications
-
-All models were fitted under a Bayesian framework in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
-The models were run on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
-Each required 64GB of RAM with 48 cores to compile within 5 days.
-
-### Development of expertise
-
-We tested how prey influenced the development of predator expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e.
-number of prey consumed) and the predators' cumulative experience (i.e.
-number of matches played before the current match).
-We parametrized the models following the method of @Pedersen.etal2019.
-The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID.
-In this model, we assume that predators have the same development of expertise, with the model estimating a trend for the average individual (i.e.
-global smoother).
-For the second model, we included varying individual smoothers for the predator ID.
-Here, we assume that individual predators share a similar relationship between success and experience, but that this relationship can vary among them (e.g.
-predator 1 has a steeper curve than predator 2).
-This enabled us to test whether predators differed in the development of their expertise.
-In the third model, we kept the individual smoothers for the predators, but removed the global smoother.
-This model assumes that predators do not share a common relationship between success and experience.
-The fourth and fifth models were reproductions of the second and third models respectively, where we included the prey speed to assess its effect on the relationship between success and experience.
-We included the standardized match duration and prey rank as covariates in all five models.
-
-We computed the five models using a modified version of the beta-binomial distribution implemented in "brms".
-Hunting success was estimated as the probability of consuming the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
-We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link.
-We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
-We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id}^{2})$).
-We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5^{2})$) and the global trend of cumulative experience ($N(0,\ 2^{2}))$).
-Following @FraserFranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5^{2})$), a positive Gaussian prior ($N(1,\ 0.5^{2}))$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5^{2})$) because encountering faster prey is associated with lower success in this system.
-We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0,\ 0.5^{2})$).
-We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
-
-### Foraging behaviour and predator-prey interactions across experience
-
-We tested whether foraging behaviour changed with experience, and compared the success of predators along the flexible-specialist hunter continuum, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
-For each experience level, we fitted the model on three traits: the predator's speed ($Y_{1}$) and the prey's speed ($Y_{2}$) using a Gaussian error distribution, and the predator's hunting success ($Y_{3}$) using a beta-binomial error distribution.
-Fixed and random effect structure were trait-specific and the same for all experience levels.
-The predator and the prey speed included a mean and a dispersion part (eqn 1.1, 1.2 and 2.1, 2.2).
-For both traits, we controlled for the standardized prey rank on both the mean and the dispersion parts of the model.
-We included game environment, predator avatar, and individual predator identity random effects on the mean part of the model.
-The dispersion part included individual predator identity random effects exclusively.
-For hunting success, we modeled the mean part only (eqn 3) and controlled for the standardized prey rank and game duration, and included an individual identity random effect.
-
-The model simultaneously estimated five among-individual variance components with their covariances for each experience level, resulting in a 15x15 (co)variance matrix.
-For each experience level, the model estimated among individual variance in mean predator speed, mean prey speed, and mean hunting success.
-This allows to test for individual differences in tactic use (i.e.
-along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption.
-The model also estimated among individual variance in intra-individual variation (IIV) for both prey and predator speed.
-This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization.
-Finally, the model estimated all pairwise covariances at the individual level among traits, among experience, and across traits and experience.
-The resulting 15x15 (co)variance matrix thus provides the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.
-
-The model can be written as:
-
-```{r model_equations, ft.align = "left"}
-
-# Prepare equations
-#eqs <- c(
-#  "Y_{1}(T_{j}) = X_{1}(T_{j})\\ b_{1}(T_{j}) + M_{1}(T_{j})\\ en_{1}(T_{j}) + N_{1}(T_{j})\\ av_{1}(T_{j}) + Z_{1}(T_{j})\\ #id_{1}(T_{j}) + e_{1}(T_{j})",
-#  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = X_{d1}(T_{j})\\ b_{d1}(T_{j}) + Z_{d1}(T_{j})\\ id_{d1}(T_{j})",
-#  "Y_{2}(T_{j}) = X_{2}(T_{j})\\ b_{2}(T_{j}) + M_{2}(T_{j})\\ en_{2}(T_{j}) + N_{2}(T_{j})\\ av_{2}(T_{j}) + Z_{2}(T_{j})\\ #id_{2}(T_{j}) + e_{2}(T_{j})",
-#  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = X_{d2}(T_{j})\\ b_{d2}(T_{j}) + Z_{d2}(T_{j})\\ id_{d2}(T_{j})",
-#  "Y_{3}(T_{j}) = X_{3}(T_{j})\\ b_{3}(T_{j}) + Z_{3}(T_{j})\\ id_{3}(T_{j}) + e_{3}(T_{j})"
-#)
-
-#eqs <- c(
-#  "Y_{1}(T_{j}) = T^2_{j}(X_{1}\\ b_{1}) + T^2_{j}(M_{1}\\ en_{1}) + T^2_{j}(N_{1}\\ av_{1}) + T^2_{j}(Z_{1}\\ id_{1}) + e_{1}(T_{j})",
-#  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = T^2_{j}(X_{d1}\\ b_{d1}) + T^2_{j}(Z_{d1}\\ id_{d1})",
-#  "Y_{2}(T_{j}) = T^2_{j}(X_{2}\\ b_{2}) + T^2_{j}(M_{2}\\ en_{2}) + T^2_{j}(N_{2}\\ av_{2}) + T^2_{j}(Z_{2}\\ id_{2}) + e_{2}(T_{j})",
-#  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = T^2_{j}(X_{d2}\\ b_{d2}) + T^2_{j}(Z_{d2}\\ id_{d2})",
-#  "Y_{3}(T_{j}) = T^2_{j}(X_{3}\\ b_{3}) + T^2_{j}(Z_{3}\\ id_{3}) + e_{3}(T_{j})"
-#)
-
-eqs <- c(
-  "Y_{1j} = X_{1j}\\ b_{1j} + M_{1j}\\ en_{1j} + N_{1j}\\ av_{1j} + Z_{1j}\\ id_{1j} + e_{1j}",
-  "log(\\sigma_{e_{Y_{1j}}}) = X_{d1j}\\ b_{d1j} + Z_{d1j}\\ id_{d1j}",
-  "Y_{2j} = X_{2j}\\ b_{2j} + M_{2j}\\ en_{2j} + N_{2j}\\ av_{2j} + Z_{2j}\\ id_{2j} + e_{2j}",
-  "log(\\sigma_{e_{Y_{2j}}}) = X_{d2j}\\ b_{d2j} + Z_{d2j}\\ id_{d2j}",
-  "Y_{3j} = X_{3j}\\ b_{3j} + Z_{3j}\\ id_{3j} + e_{3j}"
-)
-
-eqs_num <- c(
-    "(eqn. 1.1)",
-    "(eqn. 1.2)",
-    "(eqn. 2.1)",
-    "(eqn. 2.2)",
-    "(eqn. 3)"
-)
-
-# Combine into a dataframe
-df <- data.frame(
-    formula = eqs,
-    number = eqs_num
-)
-
-# Create a table to display on Word
-ft <- flextable(df)
-
-# Transform values as a mathematical formula
-ft <- compose(
-  x = ft, j = 1,
-  value = as_paragraph(
-    as_equation(formula, height = .5)
-  )
-)
-
-# Customize table
-my_theme <- function(x, ...) {
-  x <- colformat_double(x, big.mark = " ",
-                        decimal.mark = ".",
-                        digits = 2)
-  x <- border_remove(x)
-  x <- delete_part(x, part = "header")
-  x <- align(x, j = 1, align = "left", part = "body")
-  x <- align(x, j = 2, align = "right", part = "body")
-  x <- font(x, fontname = "Times New Roman", part = "body")
-  x <- fontsize(x, size = 12, part = "body")
-  x <- width(x, j = 1, width = 13, unit = "cm")
-  x <- width(x, j = 2, width = 2.26, unit = "cm")
-}
-
-# Apply theme and print
-ft <- my_theme(x = ft)
-ft
-
-```
-
-where $j$ is the index of the three experience levels (i.e.
-novice, intermediate, advanced).
-The $d$ subscript indicates that a term is from the dispersion part of the model.
-The $b$ terms are vectors of fixed effects with their design matrices $X$ specific to each trait and experience level.
-The terms $en$, $av$, and $id$ are the vectors of random environment, random avatar, and random individual identity effects associated with their design matrices $M$, $N$, and $Z$ specific to each trait and experience level.
-For all experience levels of $Y_{1}$ and $Y_{2}$, we assumed that the game environment and avatar random effects followed a Gaussian distribution with estimated standard deviation ($en_{12j} \sim N(0,\ I\ \sigma_{en_{12j}}^{2})$ and $av_{12j} \sim N(0,\ I\ \sigma_{av_{12j}}^{2})$).
-$I$ is the identity matrix, with $I\sigma^{2}$ indicating that the random effects are independently and identically distributed.
-In addition, we assumed that the residuals follow a Gaussian distribution with observation-specific variance $e_{12j} \sim N(0,\ Diag\{\sigma_{e_{12j}}^{2}\})$.
-The 15 individual identity random effects $id_{ij}$ across all response variables and experience levels (five for each of the three experience levels) are indexed in vector $\alpha$.
-The $\alpha$ vector follows a multivariate Gaussian distribution $\alpha \sim MVN(0,\ \Sigma)$ where $\Sigma$ is a 15x15 (co)variance matrix of among individual variation across all response variables and experience levels, with $\sigma_{id_{ij}}^{2}$ on the diagonal and covariances off-diagonal.
-
-We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1^{2})$: eqn.
-1.1 to 2.2) and game duration ($N(0.5,\ 0.5^{2})$: eqn.
-3).
-Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3,\ 0.5^{2})$: eqn.
-1.1 and 2.1).
-Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,\ 1^{2})$: eqn 1.2 and 2.2).
-For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1^{2})$: eqn.
-3) and a negative Gaussian prior ($N(-4,\ 1^{2})$: eqn 3) on the intercept because hunting success should be close to 0 at the lowest game duration.
-For every predicted variable, we applied a weakly informative half-Gaussian prior ($N(0,\ 1^{2})$) on the random effects for the mean part and the dispersion part of the model.
-We used a regularizing $LKJ(2)$ prior on the correlation matrix.
-
-After inspection of the results, we found that key parameter values for our hypotheses were in the direction of our predictions, but they were largely driven by the very slow speed of one predator.
-Removing this individual reduced the estimates by a significant margin.
-To remain conservative, we thus present the results of the model without this individual in the main text, and provide the results of the model including it in the Appendix S3.
-
-### Markov Chain Monte Carlo settings
-
-We parametrized the GAMMs and the MDHGLM to run four MCMC chains with 1000 posterior samples for each parameter.
-We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table 1), and 1500 iterations with a thinning set to four for the other additive models.
-We set the first 500 iterations in each model as warm ups.
-We parametrized the MDHGLM to run 2500 iterations with a thinning set to eight, with the first 500 iterations used as warm ups.
-We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@Vehtari.etal2021a].
-We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
-We report all the posterior parameter estimates using the median of the posterior distribution with the highest posterior density (HPD) intervals at 50%, 80%, and 95%.
-
-# RESULTS {.unnumbered}
-
-## Development of expertise
-
-```{r}
-
-# Open percentages table
-path <- file.path(here::here("outputs", "03_outputs_model-processing"))
-percent_tab1 <- data.table(readRDS(file.path(path, "GAMM_percentages.rds")))
-percent_tab2 <- data.table(readRDS(file.path(path, "DHMLM_percentages.rds")))
-
-#fit1 <- readRDS(here::here("outputs", "01_outputs_models", "A2_GAMM-rank.rds"))
-#fit2 <- readRDS(here::here("outputs", "01_outputs_models", "A2_GAMM-speed-rank.rds"))
-#
-#fit1
-#fit2
-```
-
-Out of all five GAMM models, two predicted the data the best and achieved similar expected log pointwise densities (elpd).
-Both models accounted for the prey group's rank and speed (Table 1).
-Models in which these effects were not accounted for resulted in no change in hunting success with experience (i.e.
-expertise) for the average individual (results not shown).
-Accounting for the prey rank resulted in a concave-shaped relationship, with the highest success ranging between 100 and 400 matches (Figure 1A).
-In the model where we additionally included the prey's speed, the effect of experience on hunting success for the average individual followed a diminishing returns curve, with predators optimizing their success after playing ~300 matches (Figure 1C).
-The curve shows there was a 38% increase in the probability of consuming all prey for the average individual between the first and the ~330$^{th}$ match where success reached a plateau (Figure 1C).
-
-The relationship between hunting success and cumulative experience differed among predators (Figure 1B-D).
-Only `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` of the population had an increase in success from the first match to the last in the model where we did not account for the prey's speed and rank (Appendix S1: Figure S1A).
-In contrast, accounting for both effects resulted in `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` of the population increasing its success with experience from the first match to the last.
-The prey speed alone also mediated individual differences in the relationship between success and experience.
-The standard deviation of the individual slopes component of the model accounting only for prey rank was equal to 9.72 (9.30, 10.15 $95\%\ CI$), while the one for the model accounting for prey rank and speed was equal to 3.36 (3.04, 3.71 $95\%\ CI$), indicating that individual differences in the development of expertise decreased when accounting for prey speed.
-
-## Changes in foraging behaviour, prey behaviour, and hunting success
-
-The mean speed of the predator population remained stable with experience (Figure 2 and Appendix S1: Table S1).
-Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix S1: Table S1).
-At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix S1: Table S2).
-However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in among individual differences in IIV from novice to advanced (Figure 2).
-`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e.
->0.2 change in standard deviation; Figure 3).
-In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e.
-<0.05 change in standard deviation).
-
-As the predator population gained experience, there was strong evidence that the prey increased their speed, although slightly (Figure 2 and Appendix S1: Table S1).
-The population also encountered groups of prey using different speeds (Appendix S1: Table S1) which did not change with experience (Figure 2).
-At the individual level, all predators encountered prey with similar speeds on average throughout experience (Figure 2 and Appendix S1: Table S2).
-Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix S1: Table S2).
-Thus, some predators encountered similar groups (i.e.
-all groups using similar speeds) while others encountered distinct groups (i.e.
-some slower and some faster).
-These differences among individuals in IIV for prey encounters increased only marginally with experience (Figure 2).
-
-Similar to the GAMMs, the predator population's mean hunting success increased with experience (Figure 2 and Appendix S1: Table S1), with mean prey consumption revolving around two prey.
-There were also important differences among individuals in mean hunting success (Appendix S1: Table S2), but they remained stable across experience (Figure 2).
-
-## Predator-prey interactions across experience
-
-Predators that were on average faster had lower IIV in speed (Figure 4A-B and Appendix S4: Table S1).
-Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement.
-As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 4C).
-Predators that were on average faster also tended to encounter groups of prey that were on average faster and more similar (Figure 4A-B and Appendix S4: Table S1).
-There was however no evidence that these correlations increased with experience (Figure 4C)
-
-There was no correlation (-0.01 (-0.17, 0.09 $95\%\ CI$)) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.33, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 4C).
-The predators' IIV in speed and IIV in prey speed were weakly positively correlated (Figure 4A-B and Appendix S4: Table S1).
-Hence, predators that encountered groups of prey with similar speeds tended to be more specialized in their tactic, while those that encountered groups of prey with varying speeds tended to be more flexible.
-We did not find evidence that this correlation increased with experience (Figure 4C).
-
-## Success along the foraging continuum
-
-The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were overall both equally successful.
-This is further supported in the scatterplot showing no apparent relationship between success and IIV in speed (Appendix S1: Figure S2).
-There was however a slight increase in the correlation between the predator's IIV in speed and success (Figure 4C), suggesting that flexible foragers at the advanced stage were marginally less successful.
-There was strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
-Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B and Appendix S4: Table S1).
-Both relationships remained structurally stable across experience (Figure 4C).
-
-# DISCUSSION
-
-Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, and movement is predictable through time [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
-However, if predators encounter varying prey with a greater behavioural range through time, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-We found that predators in *DBD* increased their hunting success with experience, suggesting that the development of predator expertise was honed through extensive practice.
-While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
-This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience.
-The behavioural strategies of predators and prey tended to match across experience, suggesting that both were probably adjusting to each other.
-Specialized cursorial hunters tended to encounter similar groups of prey, while slower and flexible hunters tended to encounter varying groups of prey.
-Yet, an important part of the population did not change its behaviour with experience, which probably contributed to an imperfect matching between predator and prey behaviour, resulting in among individual differences in hunting success.
-Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.
-
-## The development of expertise
-
-Our results suggest that predator expertise is honed through extensive practice.
-The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @Dukas2019].
-The prey were important in mediating this pattern, probably because they increased their speed as predators gained experience.
-We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
-This resulted in discernable differences in the relationship between success and experience among predators, implying that the development of expertise depends on an individual's capacity to adjust to difficulty.
-Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why such prey were more difficult to capture.
-Thus, predators that couldn't properly hunt at high speeds or develop counter-strategies for faster prey were likely at a disadvantage.
-
-However, even after we took the prey's speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved.
-For example, if the prey used camouflage or hiding to avoid being detected [@Bowen.etal2002;@Carey.Wahl2011;@Nomura.etal2011], then predators may have found them only if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@Ehlinger1989;@Hughes.etal1992;@Warburton2003;@Szopa-Comley.etal2020].
-In addition, longer time intervals between hunting events may delay or even impede learning due to forgetting important information [@Endler1991;@Wright.etal2022].
-In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape patterns than one that played 300 matches in the span of six days.
-Investigating the impact of such time lags in future analyses may reveal important insights on the outcome of predator-prey interactions.
-
-## Predator-prey interactions across experience
-
-The predator population maintained its speed and degree of specialization throughout the study period, and individuals differed only slightly in their average speeds.
-However, differences in specialization among individuals were important and increased slightly with experience.
-Predators hunting at higher speeds specialized in this tactic and tended to encounter groups of prey with similar speeds, while those hunting at slower speeds were flexible and tended to encounter varying groups of prey.
-On one hand, this pattern could arise if some predators adjusted their strategy to their prey, because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@Szopa-Comley.Ioannou2022].
-However, we observed that 44% of the predator population showed close to no change in specialization with experience.
-Since these individuals were already specialized as novices (Fraser Franco, personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they more often encountered faster prey.
-This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
-Yet, because prey can also learn how to avoid predation [@kelley2003;@turner2006;@mccomb2011], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a].
-Indeed, 56% of the predator population altered its behaviour with experience to different degrees, including 12% that even switched between flexibility and specialization.
-Hence, if the prey also learned through repeated interactions with the predators, it is possible that experience contributed in stabilizing the system as both were adjusting to each other, similar to Red Queen dynamics [@brockhurst2014].
-Our results appear to support this since many individuals were shifting their behavioural niche while the population niche remained stable across experience.
-
-Classical theory predicts that individual foraging specialization should maximize prey consumption by optimizing foraging efficiency [@stephens1986], but other work suggests that flexibility and specialization could both be adaptive as resources fluctuate [@Woo.etal2008;@Phillips.etal2017].
-Our results support empirical findings indicating that flexible and specialist foragers obtained similar success [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018], although flexible foragers were slightly less successful.
-Both strategies appeared to emerge in part from individuals learning how to hunt their prey, resulting in a general increase in success in the population.
-However, there were still considerable differences in success among individuals through time, suggesting that some predators were limited in their capacity to match their tactic to their prey or to increase their success.
-Specialist foragers were faster, and thus, probably better equipped to hunt the more difficult faster prey in *DBD*.
-However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for the predator, thereby decreasing the benefits of using this tactic (Figure 4).
-Thus, specializing probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
-On the other hand, flexible foragers encountered variable prey with slower speeds.
-Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for flexible hunters may have come at the cost of not being adept at capturing faster prey [@Pintor.etal2014].
-Such trade-offs may reflect limitations in learning all the skills required to successfully hunt all types of prey [@healy1992;@belisle1997;@Dukas2019], particularly if the skills required to hunt slower prey are nontransferable to faster prey.
-As the benefits of each hunting style changed under different scenarios, the combination of predatory styles in our virtual system reflects how resource fluctuations can maintain fitness equilibrium within populations, resulting in behavioural diversity in predator-prey systems [@Tinker.etal2008;@Woo.etal2008;@Mougi.Kishida2009].
-
-## Conclusions
-
-A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found support of our prediction that prey were driving individual differences in expertise in a predator population.
-We also confirmed that experience and predator-prey encounters drove the patterns of individual foraging specialization and flexibility.
-Our results suggest that predators learned with experience, as their success increased and their speed remained matched to the speed of their prey.
-Even though individuals were not all equally successful, both specialized and flexible hunters achieved similar success.
-One limitation of our study was that we couldn't monitor all the matches of the prey, which prevented us from assessing their responses to the predator.
-Hence, future studies should aim at monitoring reciprocal behavioural dynamics through time, which may reveal important insights on the mechanisms driving stable equilibria in predator-prey systems.
-Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022].
-We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
-
-# ACKNOWLEDGEMENTS
-
-We warmly thank Behaviour Interactive Inc.
-for our collaboration which helps in advancing predator-prey science.
-We thank Julien Céré who managed the communication between us and Behaviour Interactive Inc., and Marine Dupuy who helped us prepare the data used in this study.
-We thank Alastair J.
-Wilson for insightful comments on the results.
-We also thank all members of Pierre-Olivier Montiglio's laboratory who provided useful feedback on earlier versions of this work.
-This work was supported by an NSERC postgraduate doctoral scholarship (569716-2022).
-
-# CONFLICT OF INTEREST STATEMENT
-
-The authors declare no conflict of interest.
-
-# REFERENCES {.unnumbered}
-
-<div id="refs"></div>
-
-\newpage
-
-# TABLES
-
-```{r table1, ft.align = "left"}
-
-# ===========================================================================
-# 1. Import the model fit
-# ===========================================================================
-
-# Open the loo table
-path <- file.path(here::here("outputs", "02_outputs_model-validation"))
-loo_tab <- data.table(readRDS(file.path(path, "GAMM_loo-cv-table.rds")))
-
-# Add model column
-loo_tab[
-  , model := c(
-    "predator xp + ID smoothers + prey rank + prey speed",
-    "ID smoothers + prey rank + prey speed",
-    "ID smoothers + prey rank",
-    "predator xp + ID smoothers + prey rank",
-    "predator xp + prey rank"
-    )
- ]
-
-# Reorder columns
-loo_tab <- loo_tab[, c(9, 1:8)]
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 2. Compute the table using flextable
-# ===========================================================================
-
-# Prepare the table parameters ----------------------------------------------
-
-# Custom header
-my_header <- data.frame(
-   col_keys = c("model",
-                "elpd_diff",
-                "se_diff",
-                "elpd_loo",
-                "se_elpd_loo"),
-   line1 = c("model",
-             "elpd \ndifference",
-             "sd \ndifference",
-             "elpd loo \nvalue",
-             "elpd loo \nstandard error"),
-   stringsAsFactors = FALSE
-)
-
-# Custom theme
-my_theme <- function(x, ...) {
-   x <- colformat_double(x, big.mark = " ",
-                         decimal.mark = ".",
-                         digits = 2)
-   x <- set_table_properties(x, layout = "autofit")
-   x <- border_remove(x)
-   std_border <- fp_border(width = 1, color = "black")
-   x <- hline_top(x, part = "all", border = std_border)
-   x <- hline_bottom(x, part = "all", border = std_border)
-}
-
-# Create the table ----------------------------------------------------------
-
-tab1 <- loo_tab %>%
-  select(model, elpd_diff, se_diff, elpd_loo, se_elpd_loo) %>%
-  flextable(col_keys = my_header$col_keys) %>%
-  set_header_df(mapping = my_header, key = "col_keys") %>%
-  my_theme() %>%
-  align(align = "left", part = "all", j = 1) %>%
-  align(align = "center", part = "all", j = 2) %>%
-  align(align = "center", part = "all", j = 3) %>%
-  align(align = "center", part = "all", j = 4) %>%
-  align(align = "center", part = "all", j = 5) %>%
-  footnote(
-    i = 1, j = 1,
-    part = "header",
-    value = as_paragraph(
-      as_sup("a "),
-      "'elpd' refers to the expected log pointwise density and is the value chosen to select the best model.",
-      as_sup("\nb "),
-      "'xp' is an acronym for experience"),
-    ref_symbols = " "
-  ) %>%
-
-  # Table caption
-  set_caption(
-    caption = "Table 1. Leave-one-out cross-validation table of the five GAMMs relating hunting success to predator experience.",
-    style = "Table Caption"
-  ) %>%
-
-  # Font options
-  font(fontname = "Times New Roman", part = "all") %>%
-  fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer")
-
-tab1
-# ===========================================================================
-# ===========================================================================
-
-```
-
-\newpage
-
-# FIGURE CAPTIONS
-
-**Figure 1.** Median posterior predictions of the development of predator hunting expertise.
-The predators' hunting success (i.e.
-the probability of consuming the four prey) is on the y axis, and the predators' cumulative experience (i.e.
-the number of matches played prior to each observation) is on the x axis.
-Panels A and C show the development of expertise for the average individual with the vertical dashed lines on the left representing the lowest predicted values.
-For panel A, the right-side vertical dashed line shows the highest predicted success.
-For panel C, the right-side dashed line represents the point on the curve where success was optimized, which we calculated using the finite differences method to obtain the first derivative of the predicted values.
-Panels B and D show among individual differences in the development of expertise, with each curve representing an individual predator.
-(A-B) GAMM where we control for the prey rank (C-D) GAMM where we control for the prey rank and the speed of the prey group.
-
-**Figure 2.** Median posterior differences and HPD intervals comparing predator foraging behaviour at the population and individual level across experience stages.
-The behavioural parameter predicted by the MDHGLM being compared is on the y axis, and the difference in parameter values between two experience stages is on the x axis.
-The pairwise comparisons between experience stages are displayed across the three panels A, B, and C.
-We compare the mean speed of the predator population, the speed of the prey it encountered, and its hunting success across experience (population mean).
-We also compare the population's foraging specialization and variation in speed of the prey it encountered across experience (population variance).
-At the individual level, we compare among individual differences in speed, the speed of the prey encountered, and hunting success (individual variation mean).
-Lastly, we compare individual variation in IIV across experience, indicating whether individual differences in foraging specialization and in the variation of the groups of prey encountered changed with experience (individual variation IIV).
-
-**Figure 3.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
-The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
-Both figure panels are ordered by ascending degree of increase in either specialization or flexibility.
-We built the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selected those with the greatest difference using the 25% and 75% quantiles.
-Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal to or greater than 0.2 standard deviations.
-
-**Figure 4.** Correlation matrices of the MDHGLM relating the mean and IIV in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
-Larger dark blue circles indicate stronger positive correlations (positive values on the colour legend), while larger dark red circles indicate stronger negative correlations (negative values on the colour legend).
-A) Correlations when predators were novice hunters.
-B) Correlations when predators were advanced hunters.
-C) Posterior median differences and HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels.
-The difference is displayed on the y axis and the correlated traits being compared are displayed on the x axis.
-Positive values indicate an increase in correlation strength from novice to the advanced stage, while negative values indicate stronger correlations when predators were novice.
-
-\newpage
-
-# FIGURES
-
-```{r fig1, out.width = "100%", fig.cap = "**Figure 1**"}
-
-knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure1.png")
-)
-
-```
-
-\newpage
-
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2**"}
-
-knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure2.png")
-)
-
-```
-
-\newpage
-
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3**"}
-
-knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure3.png")
-)
-
-```
-
-\newpage
-
-```{r fig4, out.width = "100%", fig.cap = "**Figure 4**"}
-
-knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure4.png")
-)
-
-```

### 2023-10-25 manuscript/Chapter2-manuscript.Rmd
remove author info from MS

@@
 ```
-
-Journal name : Ecology
-
-Manuscript type : article
-
-Authors : Maxime Fraser Franco^1^, Francesca Santostefano^1,2^, Julien G. A. Martin^3^, Clint D. Kelly^1^, Pierre-Olivier Montiglio^1^
-
-Affiliations : ^1^ Département des Sciences Biologiques, Université du Québec à Montréal, Montréal, QC, Canada.
-^2^ Centre for Ecology and Conservation, Penryn Campus, University of Exeter, Cornwall, United Kingdom.
-^3^ Department of Biology, University of Ottawa, Ottawa, ON, Canada.
-
-Corresponding author : fraser_franco.maxime@courrier.uqam.ca
-
-Authorship statement : With MFF as the leader, all authors participated in conceiving the ideas behind the study.
-MFF prepared the data, conducted the analyses, and wrote the manuscript with input from all coauthors.
-All authors reviewed and accepted the final version of the manuscript.
-
-Open research statement : The data and code used to produce the results in this manuscript are freely available on GitHub https://github.com/quantitative-ecologist/experience-hunting-tactics
-
-Keywords: foraging behaviour, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology, Dead by Daylight
 

### 2023-10-25 manuscript/manuscript.Rmd
renamed files to remove chapter2 in title

--- 2023-10-25 manuscript/Chapter2-manuscript.Rmd
@@
   word_document:
-    reference_docx: Chapter2-styles.docx
+    reference_docx: manuscript-styles.docx
     fig_caption: yes
@@
 
-\newpage
 # INTRODUCTION {.unnumbered}

### 2023-10-25 manuscript/manuscript.Rmd
update discussion a bit

@@
 Contrary to our predictions, the predator's strategies (i.e.
-flexible or specialized foraging) was not strongly matched to the preys' speed, suggesting that changes in hunting behaviour were driven more by repeated experience than the prey's speed.
+flexible or specialized foraging) was matched only weakly to the preys' speed, suggesting that changes in hunting behaviour were driven more by repeated experience than the prey's speed.
 Ultimately, flexible foragers were only slightly less successful than specialist foragers, such that both achieved similar success overall.
@@
 A recurring challenge impeding research on predator-prey behavioural interactions is the need to collect data simultaneously on both the predator and the prey.
-Individual-based models can mitigate some of these challenges and have contributed in stirring testable ideas for empiricists [Refs].
-Yet, while providing maximum control over environmental parameters, they can suffer from emerging behaviours that are unrealistic for animals in nature [refs].
+Individual-based models can mitigate some of these challenges and have contributed in stirring testable ideas for empiricists [cornell2019].
+Yet, while providing maximum control over environmental parameters, they can suffer from emerging behaviours that are too complex to analyze mathematically [cornell2019].
 Videogames offer an interesting alternative to agent-based simulations, providing controled virtual environments where real players interact.
@@
 
-Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, and movement is predictable through time [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
-However, if predators encounter varying prey with a greater behavioural range through time, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010;@Mery.Burns2010;@Snell-Rood2013;@Wright.etal2022].
-We found that predators in *DBD* increased their hunting success with experience, suggesting that the development of predator expertise was honed through extensive practice.
+Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, or movement is predictable through time [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
+However, if predators experience unpredictable encounters with their prey, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010].
+We found that predators in *Dead by Daylight* increased their hunting success with experience, suggesting that predator expertise was honed through extensive practice.
 While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
 This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience.
-The behavioural strategies of predators and prey tended to match across experience, suggesting that both were probably adjusting to each other.
-Specialized cursorial hunters tended to encounter similar groups of prey, while slower and flexible hunters tended to encounter varying groups of prey.
-Yet, an important part of the population did not change its behaviour with experience, which probably contributed to an imperfect matching between predator and prey behaviour, resulting in among individual differences in hunting success.
+The behavioural strategies of predators and prey tended to match across experience, suggesting that both were adjusting to each other.
+Specialized cursorial hunters encountered similar groups of prey, while slower and flexible hunters encountered varying groups of prey.
 Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.
@@
 Predators hunting at higher speeds specialized in this tactic and tended to encounter groups of prey with similar speeds, while those hunting at slower speeds were flexible and tended to encounter varying groups of prey.
-On one hand, this pattern could arise if some predators adjusted their strategy to their prey, because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018], while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@Szopa-Comley.Ioannou2022].
+On one hand, this pattern could arise if some predators adjusted their strategy to their prey, because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements, while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022].
 However, we observed that 44% of the predator population showed close to no change in specialization with experience.

### 2023-10-26 manuscript/manuscript.Rmd
updated refs to have one file. updated in MS too

@@
     fig_caption: yes
-bibliography: 
-  - references1.bib
-  - references2.bib
+bibliography: references.bib
 csl: ecology.csl
@@
 Predator express a diverse array of hunting tactics to capture their prey.
-In natural populations, differences among individuals in tactics such as ambushing, fast movement speeds, or high attack frequencies are associated with differences in prey consumption [@toscanoTraitmediatedFunctionalResponses2014;@Patrick.Weimerskirch2014;@toscanoPersonalityForagingBehavior2016].
-Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@Walker.etal2005;@Kelley.Magurran2011;@Herbert-Read.etal2017].
-This results in reciprocal interactions where predators fine-tune their tactics to their prey, suggesting that they learn and become efficient hunters through repeated encounters [@Estes.etal2003;@Woo.etal2008;@Phillips.etal2017].
-These behavioural adjustments with experience can shape the outcome of predator-prey interactions, which may result in larger implications for community and ecosystem dynamics [@wooster2023].
+In natural populations, differences among individuals in tactics such as ambushing, fast movement speeds, or high attack frequencies are associated with differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
+Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@walker.etal2005;@kelley.magurran2011;@herbert-read.etal2017].
+This results in reciprocal interactions where predators fine-tune their tactics to their prey, suggesting that they learn and become efficient hunters through repeated encounters [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
+These behavioural adjustments with experience can shape the outcome of predator-prey interactions, which may result in larger implications for community and ecosystem dynamics [@wooster.etal2023].
 
 Empirical studies on human and non-human hunters show that individuals optimize foraging efficiency (e.g.
-search and handling times, return rates) by learning associative images or prey and environmental cues [@Edwards.Jackson1994;@Morse2000;@MacDonald2007;@Reid.etal2010;@Wilson-Rankin2015].
+search and handling times, return rates) by learning associative images or prey and environmental cues [@edwards.jackson1994;@morse2000;@macdonald2007;@reid.etal2010;@wilson-rankin2015].
 As predators practice and refine their tactics, they acquire expertise (e.g.
-skills, knowledge) that allows them to outperform novice hunters [@Dukas2019;@wooster2023].
+skills, knowledge) that allows them to outperform novice hunters [@dukas2019;@wooster.etal2023].
 Through this process, it is hypothesized that individuals will specialize in a hunting tactic (e.g.
-always moving fast) if it allows them to maintain successful prey captures at each atempt [@Tinker.etal2009;@Dukas2019].
-When predators learn to hunt in environments where resources are predictable (or stable), they should gradually specialize in their hunting tactics with experience because individuals require less energy and time to search for, capture, and handle prey [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015].
+always moving fast) if it allows them to maintain successful prey captures at each atempt [@tinker.etal2009;@dukas2019].
+When predators learn to hunt in environments where resources are predictable (or stable), they should gradually specialize in their hunting tactics with experience because individuals require less energy and time to search for, capture, and handle prey [@weimerskirch2007;@woo.etal2008;@potier.etal2015].
 These conditions favor specialist hunters because there would be higher costs to switch tactics for the same type of prey.
 An alternative hypothesis is that learning is a mechanism driving behavioural flexibility.
-For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may hunt optimally by learning to adjust their tactic to the type of prey that they encounter [@Stephens1993;@Ishii.Shimada2010;@Kelley.Magurran2011].
-While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010;@mathotAdaptiveStrategiesManaging2012].
-Such feedbacks between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize with experience [@Stephens1993;@Ishii.Shimada2010;@vilapouca2021;@beyts2023].
+For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may hunt optimally by learning to adjust their tactic to the type of prey that they encounter [@stephens1993;@ishii.shimada2010;@kelley.magurran2011].
+While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010;@mathot.etal2012].
+Such feedbacks between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize with experience [@stephens1993;@ishii.shimada2010;@vilapouca2021;@beyts2023].
 
-There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences is driven by resource fluctuations [@Patrick.Weimerskirch2014a;@vandenBosch.etal2019;@Santoro.etal2019;@Manlick.etal2021].
-If predators that hunt in different environments adjust their tactics to local prey fluctuations, then specialist and flexible hunters can both attain similar hunting success and coexist [@Phillips.etal2017].
-For example, @Szopa-Comley.Ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
+There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences is driven by resource fluctuations [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
+If predators that hunt in different environments adjust their tactics to local prey fluctuations, then specialist and flexible hunters can both attain similar hunting success and coexist [@phillips.etal2017].
+For example, @szopa-comley.ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
 Therefore, if specialist and flexible hunters can attain equal success by learning through repeated interactions with their prey, then empiricists should investigate the link between foraging specialization and success across time and contexts.
@@
 A recurring challenge impeding research on predator-prey behavioural interactions is the need to collect data simultaneously on both the predator and the prey.
-Individual-based models can mitigate some of these challenges and have contributed in stirring testable ideas for empiricists [cornell2019].
-Yet, while providing maximum control over environmental parameters, they can suffer from emerging behaviours that are too complex to analyze mathematically [cornell2019].
+Individual-based models can mitigate some of these challenges and have contributed in stirring testable ideas for empiricists [@cornell2019].
+Yet, while providing maximum control over environmental parameters, they can suffer from emerging behaviours that are too complex to analyze mathematically [@cornell2019].
 Videogames offer an interesting alternative to agent-based simulations, providing controled virtual environments where real players interact.
@@
 In this virtual system, the predator population is composed of individuals that either ambush or hunt at high speeds (i.e.
-mean movement speed along a slow-fast continuum), and their success is driven by the movement of the prey [@FraserFranco.etal2022].
-We found that prey can increase their chances of survival by cooperating and moving fast when they forage [@Cere.etal2021;@, Santostefano et al.
+mean movement speed along a slow-fast continuum), and their success is driven by the movement of the prey [@fraserfranco.etal2022].
+We found that prey can increase their chances of survival by cooperating and moving fast when they forage [@cere.etal2021;@, Santostefano et al.
 in press].
 Of course, the life of neither the predator nor the prey players are at stake, such that emerging patterns could be driven by their motivation to win and not "true" survival.
-Yet, the game ellicits natural reactions in players such as fear from predation (personal observations), which corroborates with another virtual ecological study showing that predation drives individual variation in risk perception [@Beauchamp2020].
-In a different system, @lymberyetal.2023 showed that complex environments favor strong soldiers over large armies in a virtual game as well as in the laboratory with two ant species.
+Yet, the game ellicits natural reactions in players such as fear from predation (personal observations), which corroborates with another virtual ecological study showing that predation drives individual variation in risk perception [@beauchamp2020].
+In a different system, @lymbery.etal2023 showed that complex environments favor strong soldiers over large armies in a virtual game as well as in the laboratory with two ant species.
 These observations outline how ecological patterns can emerge from interactions in virtual systems with fixed rules.
@@
 Some of these environments are larger than others, with varying structural complexity.
-However, predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling them to have visual cues of the generators [@FraserFranco.etal2022].
+However, predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling them to have visual cues of the generators [@fraserfranco.etal2022].
 There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during the study period.
@@
 
-All models were fitted under a Bayesian framework in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@Burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@Gabry.Cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
+All models were fitted under a Bayesian framework in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@gabry.cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
 The models were run on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
@@
 number of matches played before the current match).
-We parametrized the models following the method of @Pedersen.etal2019.
+We parametrized the models following the method of @pedersen.etal2019.
 The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID.
@@
 We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5^{2})$) and the global trend of cumulative experience ($N(0,\ 2^{2}))$).
-Following @FraserFranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5^{2})$), a positive Gaussian prior ($N(1,\ 0.5^{2}))$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5^{2})$) because encountering faster prey is associated with lower success in this system.
+Following @fraserfranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5^{2})$), a positive Gaussian prior ($N(1,\ 0.5^{2}))$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5^{2})$) because encountering faster prey is associated with lower success in this system.
 We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0,\ 0.5^{2})$).
-We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@Vehtari.etal2017;@Piironen.Vehtari2017;@Vehtari.etal2022].
+We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@vehtari.etal2017;@piironen.vehtari2017;@vehtari.etal2022].
 
@@
 
-We tested whether foraging behaviour changed with experience, and compared the success of predators along the flexible-specialist hunter continuum, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@Lee.Nelder2006;@Cleasby.etal2015;@Mitchell.etal2016a].
+We tested whether foraging behaviour changed with experience, and compared the success of predators along the flexible-specialist hunter continuum, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@lee.nelder2006;@cleasby.etal2015;@mitchell.etal2016].
 For each experience level, we fitted the model on three traits: the predator's speed ($Y_{1}$) and the prey's speed ($Y_{2}$) using a Gaussian error distribution, and the predator's hunting success ($Y_{3}$) using a beta-binomial error distribution.
@@
 3).
-Based on previous results showing that the mean predator speed revolves around 3 m/s [@FraserFranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3,\ 0.5^{2})$: eqn.
+Based on previous results showing that the mean predator speed revolves around 3 m/s [@fraserfranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3,\ 0.5^{2})$: eqn.
 1.1 and 2.1).
@@
 We parametrized the MDHGLM to run 2500 iterations with a thinning set to eight, with the first 500 iterations used as warm ups.
-We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@Vehtari.etal2021a].
+We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@vehtari.etal2021].
 We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
@@
 
-Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, or movement is predictable through time [@Estes.etal2003;@Tinker.etal2008;@Tinker.etal2009].
-However, if predators experience unpredictable encounters with their prey, then learning should increase behavioural flexibility [@Stephens1993;@Ishii.Shimada2010].
+Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, or movement is predictable through time [@estes.etal2003;@tinker.etal2008;@tinker.etal2009].
+However, if predators experience unpredictable encounters with their prey, then learning should increase behavioural flexibility [@stephens1993;@ishii.shimada2010].
 We found that predators in *Dead by Daylight* increased their hunting success with experience, suggesting that predator expertise was honed through extensive practice.
@@
 Our results suggest that predator expertise is honed through extensive practice.
-The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @Dukas2019].
+The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @dukas2019].
 The prey were important in mediating this pattern, probably because they increased their speed as predators gained experience.
-We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@FraserFranco.etal2022], and other studies have found that as well [@Walker.etal2005;@Kelley.Magurran2011;@Martin.etal2022].
+We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@fraserfranco.etal2022], and other studies have found that as well [@walker.etal2005;@kelley.magurran2011;@martin.etal2022].
 This resulted in discernable differences in the relationship between success and experience among predators, implying that the development of expertise depends on an individual's capacity to adjust to difficulty.
-Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@Kelley.Magurran2011], and that could explain why such prey were more difficult to capture.
+Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@kelley.magurran2011], and that could explain why such prey were more difficult to capture.
 Thus, predators that couldn't properly hunt at high speeds or develop counter-strategies for faster prey were likely at a disadvantage.
@@
 However, even after we took the prey's speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved.
-For example, if the prey used camouflage or hiding to avoid being detected [@Bowen.etal2002;@Carey.Wahl2011;@Nomura.etal2011], then predators may have found them only if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@Ehlinger1989;@Hughes.etal1992;@Warburton2003;@Szopa-Comley.etal2020].
-In addition, longer time intervals between hunting events may delay or even impede learning due to forgetting important information [@Endler1991;@Wright.etal2022].
+For example, if the prey used camouflage or hiding to avoid being detected, then predators may have found them only if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@ehlinger1989;@hughes.etal1992;@warburton2003;@szopa-comley.etal2020].
+In addition, longer time intervals between hunting events may delay or even impede learning due to forgetting important information [@endler1991;@wright.etal2022].
 In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape patterns than one that played 300 matches in the span of six days.
@@
 Predators hunting at higher speeds specialized in this tactic and tended to encounter groups of prey with similar speeds, while those hunting at slower speeds were flexible and tended to encounter varying groups of prey.
-On one hand, this pattern could arise if some predators adjusted their strategy to their prey, because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements, while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@Endler1991;@Bro-Jorgensen2013;@Wilson.etal2018;@Szopa-Comley.Ioannou2022].
+On one hand, this pattern could arise if some predators adjusted their strategy to their prey, because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements, while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@endler1991;@bro-jorgensen2013;@wilson.etal2018;@szopa-comley.ioannou2022].
 However, we observed that 44% of the predator population showed close to no change in specialization with experience.
@@
 This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
-Yet, because prey can also learn how to avoid predation [@kelley2003;@turner2006;@mccomb2011], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@Kishida.etal2006;@Kishida.etal2009;@Edgell.Rochette2009a;@McGhee.etal2013a].
+Yet, because prey can also learn how to avoid predation [@kelley2003;@turner2006;@mccomb2011], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@kishida.etal2006;@kishida.etal2009;@edgell.rochette2009;@mcghee.etal2013].
 Indeed, 56% of the predator population altered its behaviour with experience to different degrees, including 12% that even switched between flexibility and specialization.
@@
 
-Classical theory predicts that individual foraging specialization should maximize prey consumption by optimizing foraging efficiency [@stephens1986], but other work suggests that flexibility and specialization could both be adaptive as resources fluctuate [@Woo.etal2008;@Phillips.etal2017].
-Our results support empirical findings indicating that flexible and specialist foragers obtained similar success [@Weimerskirch2007;@Woo.etal2008;@Potier.etal2015;@Phillips.etal2017;@Courbin.etal2018], although flexible foragers were slightly less successful.
+Classical theory predicts that individual foraging specialization should maximize prey consumption by optimizing foraging efficiency [@stephens1986], but other work suggests that flexibility and specialization could both be adaptive as resources fluctuate [@woo.etal2008;@phillips.etal2017].
+Our results support empirical findings indicating that flexible and specialist foragers obtained similar success [@weimerskirch2007;@woo.etal2008;@potier.etal2015;@phillips.etal2017;@courbin.etal2018], although flexible foragers were slightly less successful.
 Both strategies appeared to emerge in part from individuals learning how to hunt their prey, resulting in a general increase in success in the population.
@@
 On the other hand, flexible foragers encountered variable prey with slower speeds.
-Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for flexible hunters may have come at the cost of not being adept at capturing faster prey [@Pintor.etal2014].
-Such trade-offs may reflect limitations in learning all the skills required to successfully hunt all types of prey [@healy1992;@belisle1997;@Dukas2019], particularly if the skills required to hunt slower prey are nontransferable to faster prey.
-As the benefits of each hunting style changed under different scenarios, the combination of predatory styles in our virtual system reflects how resource fluctuations can maintain fitness equilibrium within populations, resulting in behavioural diversity in predator-prey systems [@Tinker.etal2008;@Woo.etal2008;@Mougi.Kishida2009].
+Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for flexible hunters may have come at the cost of not being adept at capturing faster prey [@pintor.etal2014].
+Such trade-offs may reflect limitations in learning all the skills required to successfully hunt all types of prey [@healy1992;@belisle1997;@dukas2019], particularly if the skills required to hunt slower prey are nontransferable to faster prey.
+As the benefits of each hunting style changed under different scenarios, the combination of predatory styles in our virtual system reflects how resource fluctuations can maintain fitness equilibrium within populations, resulting in behavioural diversity in predator-prey systems [@tinker.etal2008;@woo.etal2008;@mougi.kishida2009].
 
@@
 
-A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abramsEvolutionPredatorPreyInteractions2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
+A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abrams2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
 By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found support of our prediction that prey were driving individual differences in expertise in a predator population.
@@
 Hence, future studies should aim at monitoring reciprocal behavioural dynamics through time, which may reveal important insights on the mechanisms driving stable equilibria in predator-prey systems.
-Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@Barbe.etal2020;@Beauchamp2020;@Cere.etal2021;@FraserFranco.etal2022].
+Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@beauchamp2020;@cere.etal2021;@fraserfranco.etal2022;@lymbery.etal2023].
 We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.

### 2023-10-26 manuscript/manuscript.Rmd
minor updates to methods and last par in intro

@@
 Predator express a diverse array of hunting tactics to capture their prey.
-In natural populations, differences among individuals in tactics such as ambushing, fast movement speeds, or high attack frequencies are associated with differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
+In natural populations, differences among individuals in tactics such as ambushing and fast movement speeds are associated with differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
 Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@walker.etal2005;@kelley.magurran2011;@herbert-read.etal2017].
@@
 mean movement speed along a slow-fast continuum), and their success is driven by the movement of the prey [@fraserfranco.etal2022].
-We found that prey can increase their chances of survival by cooperating and moving fast when they forage [@cere.etal2021;@, Santostefano et al.
+We found that prey can increase their chances of survival by cooperating and moving fast when they forage [@cere.etal2021;@fraserfranco.etal2022, Santostefano et al.
 in press].
@@
 In this study, we assess how repeated experience shapes predator hunting specialization and success using data from players in *Dead by Daylight*.
+Following @fraserfranco.etal2022 we use the predators' mean movement speed along a slow-fast continuum as a proxy for the hunting tactic (ambush-cursorial), and define the level of individual hunting specialization as the intra-individual variance (i.e.
+IIV) in movement speed across matches, where low IIV translates to individual specialization (i.e.
+always using a cursorial tactic).
 First, we investigate how individual hunting success changes with experience (i.e.
@@
 We expect this pattern to vary among individuals due to differences in prey encounters.
-For example, a predator may face greater difficulty than other individuals if it encountered elusive groups of prey more often.
 Second, we assess how foraging specialization emerges with experience.
-We define the level of individual foraging specialization as the intra-individual variance (i.e.
-IIV) in movement speed across matches, where low IIV translates to individual specialization (i.e.
-always using a cursorial tactic).
 If all predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds.
@@
 We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
-Lastly, we defined the predator's cumulative experience as the number of matches played prior to the match being monitored.
+Lastly, we defined the predator's cumulative experience as the number of matches played as the predator prior to the match being monitored.
 For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.
+We did not account for matches where predators played as the prey.
 We also categorized predators for each match based on their cumulated experience.
@@
 Hence, if the prey also learned through repeated interactions with the predators, it is possible that experience contributed in stabilizing the system as both were adjusting to each other, similar to Red Queen dynamics [@brockhurst2014].
-Our results appear to support this since many individuals were shifting their behavioural niche while the population niche remained stable across experience.
 
@@
 
-A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abrams2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey, in part because of the challenges of investigating direct interactions in the wild.
+A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abrams2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey in part because of the challenges of investigating direct interactions in the wild.
 By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found support of our prediction that prey were driving individual differences in expertise in a predator population.

### 2023-10-30 manuscript/manuscript.Rmd
some minor clarifications to the text

@@
 Prey behaviour was an important mediator of this relationship, resulting in differences among predators in the development of expertise.
-Throughout experience, 68% of predators became either increasingly specialized by always moving at a fast pace, or flexible by swithing between slow and fast speeds.
+Throughout experience, 68% of predators became either increasingly specialized by always moving at a fast pace, or flexible by switching between slow and fast speeds.
 The remaining 32% of predators used a specialized tactic of fast movement throughout the study period.
@@
 
+*check phrase du abstract être sûr que ça match avec discussion?*
+
 # INTRODUCTION {.unnumbered}
 
-Predator express a diverse array of hunting tactics to capture their prey.
+Predator express a diverse array of foraging tactics to capture their prey.
 In natural populations, differences among individuals in tactics such as ambushing and fast movement speeds are associated with differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
@@
 This results in reciprocal interactions where predators fine-tune their tactics to their prey, suggesting that they learn and become efficient hunters through repeated encounters [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
-These behavioural adjustments with experience can shape the outcome of predator-prey interactions, which may result in larger implications for community and ecosystem dynamics [@wooster.etal2023].
+These behavioural adjustments with experience can shape the outcome of predator-prey interactions, and may have larger implications for community and ecosystem dynamics [@wooster.etal2023].
 
@@
 skills, knowledge) that allows them to outperform novice hunters [@dukas2019;@wooster.etal2023].
-Through this process, it is hypothesized that individuals will specialize in a hunting tactic (e.g.
-always moving fast) if it allows them to maintain successful prey captures at each atempt [@tinker.etal2009;@dukas2019].
-When predators learn to hunt in environments where resources are predictable (or stable), they should gradually specialize in their hunting tactics with experience because individuals require less energy and time to search for, capture, and handle prey [@weimerskirch2007;@woo.etal2008;@potier.etal2015].
-These conditions favor specialist hunters because there would be higher costs to switch tactics for the same type of prey.
+Through this process, it is hypothesized that individuals will gradually specialize in a foraging tactic (e.g.
+always moving fast) if it allows them to maintain successful prey captures at each attempt [@tinker.etal2009;@dukas2019].
+This should occur when predators learn to hunt in environments where resources are predictable (or stable) because they require less energy and time to search for, capture, and handle prey [@weimerskirch2007;@woo.etal2008;@potier.etal2015].
+Such conditions favor specialist hunters because there would be higher costs to switch tactics for the same type of prey.
 An alternative hypothesis is that learning is a mechanism driving behavioural flexibility.
@@
 While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010;@mathot.etal2012].
-Such feedbacks between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize with experience [@stephens1993;@ishii.shimada2010;@vilapouca2021;@beyts2023].
+Nonetheless, the complex feedbacks between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize in their foraging with experience [@stephens1993;@ishii.shimada2010;@vilapouca2021;@beyts2023].
 
 There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences is driven by resource fluctuations [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
+For example, @szopa-comley.ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
+Prey that use fast escapes are also proven to be more difficult to hunt [@walker.etal2005;@kelley.magurran2011;@martin.etal2022], and predators that exclusively encounter such prey should benefit from learning to specialize in fast pursuits.
 If predators that hunt in different environments adjust their tactics to local prey fluctuations, then specialist and flexible hunters can both attain similar hunting success and coexist [@phillips.etal2017].
-For example, @szopa-comley.ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
-Therefore, if specialist and flexible hunters can attain equal success by learning through repeated interactions with their prey, then empiricists should investigate the link between foraging specialization and success across time and contexts.
+Therefore, empiricists should investigate the link between foraging specialization and success across time and contexts.
 
 A recurring challenge impeding research on predator-prey behavioural interactions is the need to collect data simultaneously on both the predator and the prey.
-Individual-based models can mitigate some of these challenges and have contributed in stirring testable ideas for empiricists [@cornell2019].
-Yet, while providing maximum control over environmental parameters, they can suffer from emerging behaviours that are too complex to analyze mathematically [@cornell2019].
-Videogames offer an interesting alternative to agent-based simulations, providing controled virtual environments where real players interact.
+Similar to agent-based simulations, online videogames can be useful systems to mitigate these challenges and test specific ecological hypotheses.
+They provide controlled virtual environments with the advantage of having real players that interact in the virtual space.
 For example, in the predator-prey videogame *Dead by Daylight*, four prey players need to forage for resources while avoiding predation by a fifth player.
@@
 
-In this study, we assess how repeated experience shapes predator hunting specialization and success using data from players in *Dead by Daylight*.
-Following @fraserfranco.etal2022 we use the predators' mean movement speed along a slow-fast continuum as a proxy for the hunting tactic (ambush-cursorial), and define the level of individual hunting specialization as the intra-individual variance (i.e.
-IIV) in movement speed across matches, where low IIV translates to individual specialization (i.e.
+In this study, we assess how repeated experience shapes predator foraging specialization and success using data from players in *Dead by Daylight*.
+Following @fraserfranco.etal2022 we use the predators' mean movement speed along a slow-fast continuum as a proxy for the foraging tactic (ambush-cursorial), and define the level of individual foraging specialization as the intra-individual variance (i.e.
+IIV) in movement speed across matches, where low IIV translates to individual foraging specialization (i.e.
 always using a cursorial tactic).
@@
 individual differences in specialization) should be low across experience, whereas the population variance would either increase (flexibility) or decrease (specialization).
-Alternatively, individual specialization and flexibility may emerge if individuals experience different interactions with their prey, such that among individual variation in IIV would increase.
+Alternatively, individual specialization and flexibility may emerge if individuals experience different interactions with their prey.
 In this case, we expect predators that experienced more predictable encounters with their prey (i.e.
 similar groups across matches) to specialize in similar speeds, while predators that experienced unpredictable encounters with their prey (i.e.
-heterogeneous groups across matches) should adopt flexible movement speeds.
+heterogeneous groups across matches) should adopt flexible movement speeds, resulting in an increase in among individual variation in IIV with experience.
 If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success if they learned from experience how to adjust their hunting style to their prey.
@@
 As the predator population gained experience, there was strong evidence that the prey increased their speed, although slightly (Figure 2 and Appendix S1: Table S1).
-The population also encountered groups of prey using different speeds (Appendix S1: Table S1) which did not change with experience (Figure 2).
-At the individual level, all predators encountered prey with similar speeds on average throughout experience (Figure 2 and Appendix S1: Table S2).
+The population also encountered groups of prey using different speeds through time (Figure 2 and Appendix S1: Table S1).
+At the individual level, all predators encountered prey with similar average speeds throughout experience (Figure 2 and Appendix S1: Table S2).
 Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix S1: Table S2).
@@
 The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were overall both equally successful.
-This is further supported in the scatterplot showing no apparent relationship between success and IIV in speed (Appendix S1: Figure S2).
-There was however a slight increase in the correlation between the predator's IIV in speed and success (Figure 4C), suggesting that flexible foragers at the advanced stage were marginally less successful.
-There was strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
+There was however a slight increase in the correlation between the predator's IIV in speed and success (Figure 4C), suggesting that flexible foragers at the advanced stage were marginally less successful (Appendix S1: Figure S2).
+We also found strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
 Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B and Appendix S4: Table S1).

### 2023-10-30 manuscript/manuscript.Rmd
final update on MS

@@
 The remaining 32% of predators used a specialized tactic of fast movement throughout the study period.
-Contrary to our predictions, the predator's strategies (i.e.
-flexible or specialized foraging) was matched only weakly to the preys' speed, suggesting that changes in hunting behaviour were driven more by repeated experience than the prey's speed.
+The predators' strategies (i.e.
+flexible or specialized foraging) were partially matched to the preys' speed, suggesting that changes in hunting behaviour were driven by repeated encounters with prey.
 Ultimately, flexible foragers were only slightly less successful than specialist foragers, such that both achieved similar success overall.
-Our observations suggest that experience drives among individual differences in hunting tactics, which may act as a stabilizing mechanism promoting behavioural diversification in predator-prey systems.
-
-*check phrase du abstract être sûr que ça match avec discussion?*
+Our observations suggest that experience drives among individual differences in foraging tactics, which may act as a stabilizing mechanism promoting behavioural diversification in predator-prey systems.
 
@@
 Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement.
-As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 4C).
+As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 units, from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 4C).
 Predators that were on average faster also tended to encounter groups of prey that were on average faster and more similar (Figure 4A-B and Appendix S4: Table S1).
@@
 
-## Success along the foraging continuum
+## Success along the foraging specialization continuum
 
@@
 Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, or movement is predictable through time [@estes.etal2003;@tinker.etal2008;@tinker.etal2009].
-However, if predators experience unpredictable encounters with their prey, then learning should increase behavioural flexibility [@stephens1993;@ishii.shimada2010].
+However, if predators experience unpredictable encounters with their prey, then learning should favour behavioural flexibility [@stephens1993;@ishii.shimada2010].
 We found that predators in *Dead by Daylight* increased their hunting success with experience, suggesting that predator expertise was honed through extensive practice.
@@
 This resulted in discernable differences in the relationship between success and experience among predators, implying that the development of expertise depends on an individual's capacity to adjust to difficulty.
-Hunting faster prey requires costly and specialized cognitive abilities and coordination in predators [@kelley.magurran2011], and that could explain why such prey were more difficult to capture.
+Hunting faster prey requires costly and specialized cognitive abilities and coordination [@kelley.magurran2011], and that could explain why such prey were more difficult to capture.
 Thus, predators that couldn't properly hunt at high speeds or develop counter-strategies for faster prey were likely at a disadvantage.
@@
 Specialist foragers were faster, and thus, probably better equipped to hunt the more difficult faster prey in *DBD*.
-However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for the predator, thereby decreasing the benefits of using this tactic (Figure 4).
+However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for these predators, thereby decreasing the benefits of using this tactic (Figure 4).
 Thus, specializing probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
@@
 Such trade-offs may reflect limitations in learning all the skills required to successfully hunt all types of prey [@healy1992;@belisle1997;@dukas2019], particularly if the skills required to hunt slower prey are nontransferable to faster prey.
-As the benefits of each hunting style changed under different scenarios, the combination of predatory styles in our virtual system reflects how resource fluctuations can maintain fitness equilibrium within populations, resulting in behavioural diversity in predator-prey systems [@tinker.etal2008;@woo.etal2008;@mougi.kishida2009].
+As the benefits of each hunting style changed under different scenarios, the combination of predatory styles in this virtual system reflects how resource fluctuations can maintain fitness equilibrium within populations, resulting in behavioural diversity in predator-prey systems [@tinker.etal2008;@woo.etal2008;@mougi.kishida2009].
 
@@
 By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found support of our prediction that prey were driving individual differences in expertise in a predator population.
-We also confirmed that experience and predator-prey encounters drove the patterns of individual foraging specialization and flexibility.
+We also confirmed that experience and predator-prey encounters drove the patterns of individual foraging specialization.
 Our results suggest that predators learned with experience, as their success increased and their speed remained matched to the speed of their prey.
 Even though individuals were not all equally successful, both specialized and flexible hunters achieved similar success.
-One limitation of our study was that we couldn't monitor all the matches of the prey, which prevented us from assessing their responses to the predator.
+One limitation of our study was that we couldn't monitor all the matches of the prey, which prevented us from assessing their responses to the predator through their experience.
 Hence, future studies should aim at monitoring reciprocal behavioural dynamics through time, which may reveal important insights on the mechanisms driving stable equilibria in predator-prey systems.
-Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on consumer-resource interactions [@beauchamp2020;@cere.etal2021;@fraserfranco.etal2022;@lymbery.etal2023].
+Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on ecological interactions [@beauchamp2020;@cere.etal2021;@fraserfranco.etal2022;@lymbery.etal2023].
 We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.

### 2023-10-30 manuscript/Authors.Rmd
moved acknowledgements to authors file for anonymity

@@
   word_document:
-    reference_docx: Chapter2-styles.docx
+    reference_docx: appendix-styles.docx
 ---
@@
 Keywords: foraging behaviour, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology, Dead by Daylight
+
+Acknowledgements : We warmly thank Behaviour Interactive Inc.
+for our collaboration which helps in advancing predator-prey science.
+We thank Julien Céré who managed the communication between us and Behaviour Interactive Inc., and Marine Dupuy who helped us prepare the data used in this study.
+We thank Alastair J.
+Wilson for insightful comments on the results.
+We also thank all members of Pierre-Olivier Montiglio's laboratory who provided useful feedback on earlier versions of this work.
+This work was supported by an NSERC postgraduate doctoral scholarship (569716-2022).

### 2023-10-30 manuscript/manuscript.Rmd
moved acknowledgements to authors file for anonymity

@@
 
-# ACKNOWLEDGEMENTS
-
-We warmly thank Behaviour Interactive Inc.
-for our collaboration which helps in advancing predator-prey science.
-We thank Julien Céré who managed the communication between us and Behaviour Interactive Inc., and Marine Dupuy who helped us prepare the data used in this study.
-We thank Alastair J.
-Wilson for insightful comments on the results.
-We also thank all members of Pierre-Olivier Montiglio's laboratory who provided useful feedback on earlier versions of this work.
-This work was supported by an NSERC postgraduate doctoral scholarship (569716-2022).
-
 # CONFLICT OF INTEREST STATEMENT

### 2023-11-07 manuscript/manuscript.Rmd
simplified intro-hyp. added caveats and limits in conclusion

@@
 
-Predator express a diverse array of foraging tactics to capture their prey.
+Predators express a diverse array of foraging tactics to capture their prey.
 In natural populations, differences among individuals in tactics such as ambushing and fast movement speeds are associated with differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
@@
 While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010;@mathot.etal2012].
-Nonetheless, the complex feedbacks between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize in their foraging with experience [@stephens1993;@ishii.shimada2010;@vilapouca2021;@beyts2023].
+Nonetheless, complex feedback between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize with experience [@stephens1993;@ishii.shimada2010;@vilapouca2021;@beyts2023].
 
-There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences is driven by resource fluctuations [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
+There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences are driven by resource fluctuations [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
 For example, @szopa-comley.ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
@@
 Second, we assess how foraging specialization emerges with experience.
-If all predators encounter varying groups of prey, we predict that individuals (and thus the population) should all converge towards flexible speeds.
-However, if individuals encounter similar groups of prey, then everyone should instead specialize in similar speeds.
-In both scenarios, among individual variation in IIV (i.e.
-individual differences in specialization) should be low across experience, whereas the population variance would either increase (flexibility) or decrease (specialization).
-Alternatively, individual specialization and flexibility may emerge if individuals experience different interactions with their prey.
-In this case, we expect predators that experienced more predictable encounters with their prey (i.e.
-similar groups across matches) to specialize in similar speeds, while predators that experienced unpredictable encounters with their prey (i.e.
-heterogeneous groups across matches) should adopt flexible movement speeds, resulting in an increase in among individual variation in IIV with experience.
-If we detect such prey-dependent fine-tuning, then all hunters along the flexible-specialist continuum should attain equal success if they learned from experience how to adjust their hunting style to their prey.
+If all predators encounter similar groups of prey, we predict that individuals (and thus the population) should all specialize in similar speeds.
+In contrast, if all predators encounter varying groups of prey, then they should all converge towards flexible speeds.
+In both scenarios, differences among individuals in IIV across experience should be low (i.e.
+similar individual foraging specialization), whereas the population variance would either decrease (specialization) or increase (flexibility).
+Alternatively, differences among individuals in foraging specialization may emerge if they experience different interactions with their prey.
+In this case, we expect predators that encountered similar groups of prey across experience to specialize in similar speeds, while predators that encountered heterogeneous groups across matches should adopt flexible movement speeds, resulting in an increase in among individual differences in IIV with experience.
+If we detect such prey-dependent fine-tuning with experience, then all hunters along the flexible-specialist continuum should attain equal success.
 
@@
 
-Learning from experience is predicted to increase individual predator foraging specialization when prey distribution, behaviour, or movement is predictable through time [@estes.etal2003;@tinker.etal2008;@tinker.etal2009].
-However, if predators experience unpredictable encounters with their prey, then learning should favour behavioural flexibility [@stephens1993;@ishii.shimada2010].
-We found that predators in *Dead by Daylight* increased their hunting success with experience, suggesting that predator expertise was honed through extensive practice.
+A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abrams2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey in part because of the challenges of investigating direct interactions in the wild.
+By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that predators in *Dead by Daylight* increased their hunting success with experience, suggesting that predator expertise was honed through extensive practice.
 While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
@@
 Both strategies appeared to emerge in part from individuals learning how to hunt their prey, resulting in a general increase in success in the population.
-However, there were still considerable differences in success among individuals through time, suggesting that some predators were limited in their capacity to match their tactic to their prey or to increase their success.
+However, there were still considerable differences in success among individuals through time, suggesting that some predators were limited in their capacity to match their tactic to their prey or to increase their success through other means.
 Specialist foragers were faster, and thus, probably better equipped to hunt the more difficult faster prey in *DBD*.
@@
 
-A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abrams2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found support of our prediction that prey were driving individual differences in expertise in a predator population.
+We found support of our prediction that prey were driving individual differences in expertise in a predator population.
 We also confirmed that experience and predator-prey encounters drove the patterns of individual foraging specialization.
@@
 Even though individuals were not all equally successful, both specialized and flexible hunters achieved similar success.
+A potential caveat is that the more flexible hunters might have experimented with various tactics out of boredom, which could impede ecologically realistic interpretations of our data.
+However, the consistent association between this tactic and heterogeneous prey groups gives us confidence that it emerged from their interactions.
 One limitation of our study was that we couldn't monitor all the matches of the prey, which prevented us from assessing their responses to the predator through their experience.

### 2023-11-07 manuscript/manuscript.Rmd
figs embedded in text

@@
 
-The relationship between hunting success and cumulative experience differed among predators (Figure 1B-D).
-Only `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` of the population had an increase in success from the first match to the last in the model where we did not account for the prey's speed and rank (Appendix S1: Figure S1A).
-In contrast, accounting for both effects resulted in `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` of the population increasing its success with experience from the first match to the last.
-The prey speed alone also mediated individual differences in the relationship between success and experience.
-The standard deviation of the individual slopes component of the model accounting only for prey rank was equal to 9.72 (9.30, 10.15 $95\%\ CI$), while the one for the model accounting for prey rank and speed was equal to 3.36 (3.04, 3.71 $95\%\ CI$), indicating that individual differences in the development of expertise decreased when accounting for prey speed.
-
-## Changes in foraging behaviour, prey behaviour, and hunting success
-
-The mean speed of the predator population remained stable with experience (Figure 2 and Appendix S1: Table S1).
-Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix S1: Table S1).
-At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix S1: Table S2).
-However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in among individual differences in IIV from novice to advanced (Figure 2).
-`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e.
->0.2 change in standard deviation; Figure 3).
-In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e.
-<0.05 change in standard deviation).
-
-As the predator population gained experience, there was strong evidence that the prey increased their speed, although slightly (Figure 2 and Appendix S1: Table S1).
-The population also encountered groups of prey using different speeds through time (Figure 2 and Appendix S1: Table S1).
-At the individual level, all predators encountered prey with similar average speeds throughout experience (Figure 2 and Appendix S1: Table S2).
-Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix S1: Table S2).
-Thus, some predators encountered similar groups (i.e.
-all groups using similar speeds) while others encountered distinct groups (i.e.
-some slower and some faster).
-These differences among individuals in IIV for prey encounters increased only marginally with experience (Figure 2).
-
-Similar to the GAMMs, the predator population's mean hunting success increased with experience (Figure 2 and Appendix S1: Table S1), with mean prey consumption revolving around two prey.
-There were also important differences among individuals in mean hunting success (Appendix S1: Table S2), but they remained stable across experience (Figure 2).
-
-## Predator-prey interactions across experience
-
-Predators that were on average faster had lower IIV in speed (Figure 4A-B and Appendix S4: Table S1).
-Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement.
-As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 units, from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 4C).
-Predators that were on average faster also tended to encounter groups of prey that were on average faster and more similar (Figure 4A-B and Appendix S4: Table S1).
-There was however no evidence that these correlations increased with experience (Figure 4C)
-
-There was no correlation (-0.01 (-0.17, 0.09 $95\%\ CI$)) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.33, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 4C).
-The predators' IIV in speed and IIV in prey speed were weakly positively correlated (Figure 4A-B and Appendix S4: Table S1).
-Hence, predators that encountered groups of prey with similar speeds tended to be more specialized in their tactic, while those that encountered groups of prey with varying speeds tended to be more flexible.
-We did not find evidence that this correlation increased with experience (Figure 4C).
-
-## Success along the foraging specialization continuum
-
-The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were overall both equally successful.
-There was however a slight increase in the correlation between the predator's IIV in speed and success (Figure 4C), suggesting that flexible foragers at the advanced stage were marginally less successful (Appendix S1: Figure S2).
-We also found strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
-Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B and Appendix S4: Table S1).
-Both relationships remained structurally stable across experience (Figure 4C).
-
-# DISCUSSION
-
-A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abrams2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that predators in *Dead by Daylight* increased their hunting success with experience, suggesting that predator expertise was honed through extensive practice.
-While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
-This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience.
-The behavioural strategies of predators and prey tended to match across experience, suggesting that both were adjusting to each other.
-Specialized cursorial hunters encountered similar groups of prey, while slower and flexible hunters encountered varying groups of prey.
-Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.
-
-## The development of expertise
-
-Our results suggest that predator expertise is honed through extensive practice.
-The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @dukas2019].
-The prey were important in mediating this pattern, probably because they increased their speed as predators gained experience.
-We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@fraserfranco.etal2022], and other studies have found that as well [@walker.etal2005;@kelley.magurran2011;@martin.etal2022].
-This resulted in discernable differences in the relationship between success and experience among predators, implying that the development of expertise depends on an individual's capacity to adjust to difficulty.
-Hunting faster prey requires costly and specialized cognitive abilities and coordination [@kelley.magurran2011], and that could explain why such prey were more difficult to capture.
-Thus, predators that couldn't properly hunt at high speeds or develop counter-strategies for faster prey were likely at a disadvantage.
-
-However, even after we took the prey's speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved.
-For example, if the prey used camouflage or hiding to avoid being detected, then predators may have found them only if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@ehlinger1989;@hughes.etal1992;@warburton2003;@szopa-comley.etal2020].
-In addition, longer time intervals between hunting events may delay or even impede learning due to forgetting important information [@endler1991;@wright.etal2022].
-In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape patterns than one that played 300 matches in the span of six days.
-Investigating the impact of such time lags in future analyses may reveal important insights on the outcome of predator-prey interactions.
-
-## Predator-prey interactions across experience
-
-The predator population maintained its speed and degree of specialization throughout the study period, and individuals differed only slightly in their average speeds.
-However, differences in specialization among individuals were important and increased slightly with experience.
-Predators hunting at higher speeds specialized in this tactic and tended to encounter groups of prey with similar speeds, while those hunting at slower speeds were flexible and tended to encounter varying groups of prey.
-On one hand, this pattern could arise if some predators adjusted their strategy to their prey, because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements, while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@endler1991;@bro-jorgensen2013;@wilson.etal2018;@szopa-comley.ioannou2022].
-However, we observed that 44% of the predator population showed close to no change in specialization with experience.
-Since these individuals were already specialized as novices (Fraser Franco, personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they more often encountered faster prey.
-This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
-Yet, because prey can also learn how to avoid predation [@kelley2003;@turner2006;@mccomb2011], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@kishida.etal2006;@kishida.etal2009;@edgell.rochette2009;@mcghee.etal2013].
-Indeed, 56% of the predator population altered its behaviour with experience to different degrees, including 12% that even switched between flexibility and specialization.
-Hence, if the prey also learned through repeated interactions with the predators, it is possible that experience contributed in stabilizing the system as both were adjusting to each other, similar to Red Queen dynamics [@brockhurst2014].
-
-Classical theory predicts that individual foraging specialization should maximize prey consumption by optimizing foraging efficiency [@stephens1986], but other work suggests that flexibility and specialization could both be adaptive as resources fluctuate [@woo.etal2008;@phillips.etal2017].
-Our results support empirical findings indicating that flexible and specialist foragers obtained similar success [@weimerskirch2007;@woo.etal2008;@potier.etal2015;@phillips.etal2017;@courbin.etal2018], although flexible foragers were slightly less successful.
-Both strategies appeared to emerge in part from individuals learning how to hunt their prey, resulting in a general increase in success in the population.
-However, there were still considerable differences in success among individuals through time, suggesting that some predators were limited in their capacity to match their tactic to their prey or to increase their success through other means.
-Specialist foragers were faster, and thus, probably better equipped to hunt the more difficult faster prey in *DBD*.
-However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for these predators, thereby decreasing the benefits of using this tactic (Figure 4).
-Thus, specializing probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
-On the other hand, flexible foragers encountered variable prey with slower speeds.
-Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for flexible hunters may have come at the cost of not being adept at capturing faster prey [@pintor.etal2014].
-Such trade-offs may reflect limitations in learning all the skills required to successfully hunt all types of prey [@healy1992;@belisle1997;@dukas2019], particularly if the skills required to hunt slower prey are nontransferable to faster prey.
-As the benefits of each hunting style changed under different scenarios, the combination of predatory styles in this virtual system reflects how resource fluctuations can maintain fitness equilibrium within populations, resulting in behavioural diversity in predator-prey systems [@tinker.etal2008;@woo.etal2008;@mougi.kishida2009].
-
-## Conclusions
-
-We found support of our prediction that prey were driving individual differences in expertise in a predator population.
-We also confirmed that experience and predator-prey encounters drove the patterns of individual foraging specialization.
-Our results suggest that predators learned with experience, as their success increased and their speed remained matched to the speed of their prey.
-Even though individuals were not all equally successful, both specialized and flexible hunters achieved similar success.
-A potential caveat is that the more flexible hunters might have experimented with various tactics out of boredom, which could impede ecologically realistic interpretations of our data.
-However, the consistent association between this tactic and heterogeneous prey groups gives us confidence that it emerged from their interactions.
-One limitation of our study was that we couldn't monitor all the matches of the prey, which prevented us from assessing their responses to the predator through their experience.
-Hence, future studies should aim at monitoring reciprocal behavioural dynamics through time, which may reveal important insights on the mechanisms driving stable equilibria in predator-prey systems.
-Lastly, virtual systems are increasingly recognized among ecologists as being useful to test hypotheses on ecological interactions [@beauchamp2020;@cere.etal2021;@fraserfranco.etal2022;@lymbery.etal2023].
-We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
-
-# CONFLICT OF INTEREST STATEMENT
-
-The authors declare no conflict of interest.
-
-# REFERENCES {.unnumbered}
-
-<div id="refs"></div>
-
-\newpage
-
-# TABLES
-
 ```{r table1, ft.align = "left"}
@@
 
-\newpage
+The relationship between hunting success and cumulative experience differed among predators (Figure 1B-D).
+Only `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` of the population had an increase in success from the first match to the last in the model where we did not account for the prey's speed and rank (Appendix S1: Figure S1A).
+In contrast, accounting for both effects resulted in `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` of the population increasing its success with experience from the first match to the last.
+The prey speed alone also mediated individual differences in the relationship between success and experience.
+The standard deviation of the individual slopes component of the model accounting only for prey rank was equal to 9.72 (9.30, 10.15 $95\%\ CI$), while the one for the model accounting for prey rank and speed was equal to 3.36 (3.04, 3.71 $95\%\ CI$), indicating that individual differences in the development of expertise decreased when accounting for prey speed.
 
-# FIGURE CAPTIONS
-
-**Figure 1.** Median posterior predictions of the development of predator hunting expertise.
+```{r fig1, out.width = "100%", fig.cap = "**Figure 1**.
+Median posterior predictions of the development of predator hunting expertise.
 The predators' hunting success (i.e.
@@
 Panels B and D show among individual differences in the development of expertise, with each curve representing an individual predator.
-(A-B) GAMM where we control for the prey rank (C-D) GAMM where we control for the prey rank and the speed of the prey group.
-
-**Figure 2.** Median posterior differences and HPD intervals comparing predator foraging behaviour at the population and individual level across experience stages.
-The behavioural parameter predicted by the MDHGLM being compared is on the y axis, and the difference in parameter values between two experience stages is on the x axis.
-The pairwise comparisons between experience stages are displayed across the three panels A, B, and C.
-We compare the mean speed of the predator population, the speed of the prey it encountered, and its hunting success across experience (population mean).
-We also compare the population's foraging specialization and variation in speed of the prey it encountered across experience (population variance).
-At the individual level, we compare among individual differences in speed, the speed of the prey encountered, and hunting success (individual variation mean).
-Lastly, we compare individual variation in IIV across experience, indicating whether individual differences in foraging specialization and in the variation of the groups of prey encountered changed with experience (individual variation IIV).
-
-**Figure 3.** Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
-The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
-Both figure panels are ordered by ascending degree of increase in either specialization or flexibility.
-We built the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selected those with the greatest difference using the 25% and 75% quantiles.
-Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal to or greater than 0.2 standard deviations.
-
-**Figure 4.** Correlation matrices of the MDHGLM relating the mean and IIV in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
-Larger dark blue circles indicate stronger positive correlations (positive values on the colour legend), while larger dark red circles indicate stronger negative correlations (negative values on the colour legend).
-A) Correlations when predators were novice hunters.
-B) Correlations when predators were advanced hunters.
-C) Posterior median differences and HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels.
-The difference is displayed on the y axis and the correlated traits being compared are displayed on the x axis.
-Positive values indicate an increase in correlation strength from novice to the advanced stage, while negative values indicate stronger correlations when predators were novice.
-
-\newpage
-
-# FIGURES
-
-```{r fig1, out.width = "100%", fig.cap = "**Figure 1**"}
+(A-B) GAMM where we control for the prey rank (C-D) GAMM where we control for the prey rank and the speed of the prey group."}
 
@@
 
-\newpage
+## Changes in foraging behaviour, prey behaviour, and hunting success
 
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2**"}
+The mean speed of the predator population remained stable with experience (Figure 2 and Appendix S1: Table S1).
+Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix S1: Table S1).
+At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix S1: Table S2).
+However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in among individual differences in IIV from novice to advanced (Figure 2).
+`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e.
+>0.2 change in standard deviation; Figure 3).
+In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e.
+>0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e.
+<0.05 change in standard deviation).
+
+```{r fig2, out.width = "100%", fig.cap = "**Figure 2**.
+Median posterior differences and HPD intervals comparing predator foraging behaviour at the population and individual level across experience stages.
+The behavioural parameter predicted by the MDHGLM being compared is on the y axis, and the difference in parameter values between two experience stages is on the x axis.
+The pairwise comparisons between experience stages are displayed across the three panels A, B, and C.
+We compare the mean speed of the predator population, the speed of the prey it encountered, and its hunting success across experience (population mean).
+We also compare the population's foraging specialization and variation in speed of the prey it encountered across experience (population variance).
+At the individual level, we compare among individual differences in speed, the speed of the prey encountered, and hunting success (individual variation mean).
+Lastly, we compare individual variation in IIV across experience, indicating whether individual differences in foraging specialization and in the variation of the groups of prey encountered changed with experience (individual variation IIV)."}
 
@@
 
-\newpage
+As the predator population gained experience, there was strong evidence that the prey increased their speed, although slightly (Figure 2 and Appendix S1: Table S1).
+The population also encountered groups of prey using different speeds through time (Figure 2 and Appendix S1: Table S1).
+At the individual level, all predators encountered prey with similar average speeds throughout experience (Figure 2 and Appendix S1: Table S2).
+Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix S1: Table S2).
+Thus, some predators encountered similar groups (i.e.
+all groups using similar speeds) while others encountered distinct groups (i.e.
+some slower and some faster).
+These differences among individuals in IIV for prey encounters increased only marginally with experience (Figure 2).
 
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3**"}
+Similar to the GAMMs, the predator population's mean hunting success increased with experience (Figure 2 and Appendix S1: Table S1), with mean prey consumption revolving around two prey.
+There were also important differences among individuals in mean hunting success (Appendix S1: Table S2), but they remained stable across experience (Figure 2).
+
+```{r fig3, out.width = "100%", fig.cap = "**Figure 3**.
+Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
+The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
+Both figure panels are ordered by ascending degree of increase in either specialization or flexibility.
+We built the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selected those with the greatest difference using the 25% and 75% quantiles.
+Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal to or greater than 0.2 standard deviations."}
 
@@
 
-\newpage
+## Predator-prey interactions across experience
 
-```{r fig4, out.width = "100%", fig.cap = "**Figure 4**"}
+Predators that were on average faster had lower IIV in speed (Figure 4A-B and Appendix S4: Table S1).
+Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement.
+As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 units, from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 4C).
+Predators that were on average faster also tended to encounter groups of prey that were on average faster and more similar (Figure 4A-B and Appendix S4: Table S1).
+There was however no evidence that these correlations increased with experience (Figure 4C)
+
+There was no correlation (-0.01 (-0.17, 0.09 $95\%\ CI$)) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.33, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 4C).
+The predators' IIV in speed and IIV in prey speed were weakly positively correlated (Figure 4A-B and Appendix S4: Table S1).
+Hence, predators that encountered groups of prey with similar speeds tended to be more specialized in their tactic, while those that encountered groups of prey with varying speeds tended to be more flexible.
+We did not find evidence that this correlation increased with experience (Figure 4C).
+
+```{r fig4, out.width = "100%", fig.cap = "**Figure 4**.
+Correlation matrices of the MDHGLM relating the mean and IIV in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
+Larger dark blue circles indicate stronger positive correlations (positive values on the colour legend), while larger dark red circles indicate stronger negative correlations (negative values on the colour legend).
+A) Correlations when predators were novice hunters.
+B) Correlations when predators were advanced hunters.
+C) Posterior median differences and HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels.
+The difference is displayed on the y axis and the correlated traits being compared are displayed on the x axis.
+Positive values indicate an increase in correlation strength from novice to the advanced stage, while negative values indicate stronger correlations when predators were novice."}
 
@@
 ```
+
+## Success along the foraging specialization continuum
+
+The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were overall both equally successful.
+There was however a slight increase in the correlation between the predator's IIV in speed and success (Figure 4C), suggesting that flexible foragers at the advanced stage were marginally less successful (Appendix S1: Figure S2).
+We also found strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
+Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B and Appendix S4: Table S1).
+Both relationships remained structurally stable across experience (Figure 4C).
+
+# DISCUSSION
+
+A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abrams2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey in part because of the challenges of investigating direct interactions in the wild.
+By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that predators in *Dead by Daylight* increased their hunting success with experience, suggesting that predator expertise was honed through extensive practice.
+While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
+This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience.
+The behavioural strategies of predators and prey tended to match across experience, suggesting that both were adjusting to each other.
+Specialized cursorial hunters encountered similar groups of prey, while slower and flexible hunters encountered varying groups of prey.
+Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.
+
+## The development of expertise
+
+Our results suggest that predator expertise is honed through extensive practice.
+The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @dukas2019].
+The prey were important in mediating this pattern, probably because they increased their speed as predators gained experience.
+We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@fraserfranco.etal2022], and other studies have found that as well [@walker.etal2005;@kelley.magurran2011;@martin.etal2022].
+This resulted in discernable differences in the relationship between success and experience among predators, implying that the development of expertise depends on an individual's capacity to adjust to difficulty.
+Hunting faster prey requires costly and specialized cognitive abilities and coordination [@kelley.magurran2011], and that could explain why such prey were more difficult to capture.
+Thus, predators that couldn't properly hunt at high speeds or develop counter-strategies for faster prey were likely at a disadvantage.
+
+However, even after we took the prey's speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved.
+For example, if the prey used camouflage or hiding to avoid being detected, then predators may have found them only if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@ehlinger1989;@hughes.etal1992;@warburton2003;@szopa-comley.etal2020].
+In addition, longer time intervals between hunting events may delay or even impede learning due to forgetting important information [@endler1991;@wright.etal2022].
+In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape patterns than one that played 300 matches in the span of six days.
+Investigating the impact of such time lags in future analyses may reveal important insights on the outcome of predator-prey interactions.
+
+## Predator-prey interactions across experience
+
+The predator population maintained its speed and degree of specialization throughout the study period, and individuals differed only slightly in their average speeds.
+However, differences in specialization among individuals were important and increased slightly with experience.
+Predators hunting at higher speeds specialized in this tactic and tended to encounter groups of prey with similar speeds, while those hunting at slower speeds were flexible and tended to encounter varying groups of prey.
+On one hand, this pattern could arise if some predators adjusted their strategy to their prey, because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements, while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@endler1991;@bro-jorgensen2013;@wilson.etal2018;@szopa-comley.ioannou2022].
+However, we observed that 44% of the predator population showed close to no change in specialization with experience.
+Since these individuals were already specialized as novices (Fraser Franco, personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they more often encountered faster prey.
+This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
+Yet, because prey can also learn how to avoid predation [@kelley2003;@turner2006;@mccomb2011], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@kishida.etal2006;@kishida.etal2009;@edgell.rochette2009;@mcghee.etal2013].
+Indeed, 56% of the predator population altered its behaviour with experience to different degrees, including 12% that even switched between flexibility and specialization.
+Hence, if the prey also learned through repeated interactions with the predators, it is possible that experience contributed in stabilizing the system as both were adjusting to each other, similar to Red Queen dynamics [@brockhurst2014].
+
+Classical theory predicts that individual foraging specialization should maximize prey consumption by optimizing foraging efficiency [@stephens1986], but other work suggests that flexibility and specialization could both be adaptive as resources fluctuate [@woo.etal2008;@phillips.etal2017].
+Our results support empirical findings indicating that flexible and specialist foragers obtained similar success [@weimerskirch2007;@woo.etal2008;@potier.etal2015;@phillips.etal2017;@courbin.etal2018], although flexible foragers were slightly less successful.
+Both strategies appeared to emerge in part from individuals learning how to hunt their prey, resulting in a general increase in success in the population.
+However, there were still considerable differences in success among individuals through time, suggesting that some predators were limited in their capacity to match their tactic to their prey or to increase their success through other means.
+Specialist foragers were faster, and thus, probably better equipped to hunt the more difficult faster prey in *DBD*.
+However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for these predators, thereby decreasing the benefits of using this tactic (Figure 4).
+Thus, specializing probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
+On the other hand, flexible foragers encountered variable prey with slower speeds.
+Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for flexible hunters may have come at the cost of not being adept at capturing faster prey [@pintor.etal2014].
+Such trade-offs may reflect limitations in learning all the skills required to successfully hunt all types of prey [@healy1992;@belisle1997;@dukas2019], particularly if the skills required to hunt slower prey are nontransferable to faster prey.
+As the benefits of each hunting style changed under different scenarios, the combination of predatory styles in this virtual system reflects how resource fluctuations can maintain fitness equilibrium within populations, resulting in behavioural diversity in predator-prey systems [@tinker.etal2008;@woo.etal2008;@mougi.kishida2009].
+
+## Conclusions
+
+We found support of our prediction that prey were driving individual differences in expertise in a predator population.
+We also confirmed that experience and predator-prey encounters drove the patterns of individual foraging specialization.
+Our results suggest that predators learned with experience, as their success increased and their speed remained matched to the speed of their prey.
+Even though individuals were not all equally successful, both specialized and flexible hunters achieved similar success.
+A potential caveat is that the more flexible hunters might have experimented with various tactics out of boredom, which could impede ecologically realistic interpretations of our data.
+However, the consistent association between this tactic and heterogeneous prey groups gives us confidence that it emerged from their interactions.
+One limitation of our study was that we couldn't monitor all the matches of the prey, which prevented us from assessing their responses to the predator through their experience.
+Hence, future studies should aim at monitoring reciprocal behavioural dynamics through time, which may reveal important insights on the mechanisms driving stable equilibria in predator-prey systems.
+Lastly, virtual systems are increasingly recognized as being useful to test hypotheses on ecological interactions [@beauchamp2020;@cere.etal2021;@fraserfranco.etal2022;@lymbery.etal2023].
+We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
+
+# CONFLICT OF INTEREST STATEMENT
+
+The authors declare no conflict of interest.
+
+# REFERENCES {.unnumbered}
+
+<div id="refs"></div>

### 2023-12-15 manuscript/manuscript.Rmd
added keywords to main text
minor edits to words in text. edit refs style and bib.

@@
 bibliography: references.bib
-csl: ecology.csl
+csl: chicago-author-date.csl
 ---
@@
 
+Keywords: foraging behaviour, reciprocal behavioural plasticity, learning, antipredator behaviour, virtual ecology, Dead by Daylight
+
 # INTRODUCTION {.unnumbered}
@@
 Following @fraserfranco.etal2022 we use the predators' mean movement speed along a slow-fast continuum as a proxy for the foraging tactic (ambush-cursorial), and define the level of individual foraging specialization as the intra-individual variance (i.e.
-IIV) in movement speed across matches, where low IIV translates to individual foraging specialization (i.e.
+IIV) in movement speed across matches, where low IIV translates to individual foraging specialization (e.g.
 always using a cursorial tactic).
@@
 For each experience level, the model estimated among individual variance in mean predator speed, mean prey speed, and mean hunting success.
-This allows to test for individual differences in tactic use (i.e.
+This allows us to test for individual differences in tactic use (i.e.
 along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption.
 The model also estimated among individual variance in intra-individual variation (IIV) for both prey and predator speed.
-This allows to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization.
+This allows us to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization.
 Finally, the model estimated all pairwise covariances at the individual level among traits, among experience, and across traits and experience.
@@
 
-# CONFLICT OF INTEREST STATEMENT
-
-The authors declare no conflict of interest.
-
 # REFERENCES {.unnumbered}

### 2024-09-06 code/01_code_models/A1_GAMM-rank.R
split paper - removed gamm outputs and files

@@ -1,178 +1,0 @@
-# ==========================================================================
-
-#            GAMM model G - single common smoother - Hunting success
-
-# ==========================================================================
-
-
-
-
-
-# ==========================================================================
-# 1. Prepare the data
-# ==========================================================================
-
-
-
-# Load packages ------------------------------------------------------------
-
-# Detect cores
-options(mc.cores = parallel::detectCores())
-
-# Load libraries
-library(data.table)
-library(brms)
-library(parallel)
-
-
-
-# Load data ----------------------------------------------------------------
-
-# Folder path Compute Canada
-folder <- file.path("/home", "maxime11", "projects", "def-monti", 
-                    "maxime11", "phd_project", "data")
-
-# Load data on compute canada
-data <- fread(
-  file.path(folder, "FraserFrancoetalXXXX-data.csv"),
-  select = c("predator_id",
-             "hunting_success",
-             "prey_avg_speed",
-             "game_duration",
-             "cumul_xp_pred",
-             "prey_avg_rank")
-)
-
-# Predator id as factor
-data[, predator_id := as.factor(predator_id)]
-
-# Remove any NAs
-data <- data[complete.cases(data)]
-
-
-
-# Standardise the variables (Z-scores) -------------------------------------
-
-standardize <- function(x) {
-  (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
-}
-
-data[, c(
-    "Zprey_speed",
-    "Zgame_duration",
-    "Zcumul_xp",
-    "Zprey_avg_rank"
-    ) := lapply(.SD, standardize),
-       .SDcols = c(3:6)]
-
-# ==========================================================================
-# ==========================================================================
-
-
-
-
-
-# ==========================================================================
-# 2. Parametrize the model
-# ==========================================================================
-
-
-
-# Compute the custom family ------------------------------------------------
-
-beta_binomial2 <- custom_family(
-  "beta_binomial2", dpars = c("mu", "phi"),
-  links = c("logit", "log"), lb = c(NA, 0),
-  type = "int", vars = "vint1[n]"
-)
-
-
-
-# Function -----------------------------------------------------------------
-
-stan_funs <- "
-  real beta_binomial2_lpmf(int y, real mu, real phi, int T) {
-    return beta_binomial_lpmf(y | T, mu * phi, (1 - mu) * phi);
-  }
[…]

### 2024-09-06 code/01_code_models/A2_GAMM-rank.R

@@ -1,178 +1,0 @@
-# ==========================================================================
-
-#           GAMM model GS - group-level smoother - hunting success
-
-# ==========================================================================
-
-
-
-
-
-# ==========================================================================
-# 1. Prepare the data
-# ==========================================================================
-
-
-
-# Load packages ------------------------------------------------------------
-
-# Detect cores
-options(mc.cores = parallel::detectCores())
-
-# Load libraries
-library(data.table)
-library(brms)
-library(parallel)
-
-
-
-# Load data ----------------------------------------------------------------
-
-# Folder path Compute Canada
-folder <- file.path("/home", "maxime11", "projects", "def-monti", 
-                    "maxime11", "phd_project", "data")
-
-# Load data
-data <- fread(
-  file.path(folder, "FraserFrancoetalXXXX-data.csv"),
-  select = c("predator_id",
-             "hunting_success",
-             "prey_avg_speed",
-             "game_duration",
-             "cumul_xp_pred",
-             "prey_avg_rank")
-)
-
-# Predator id as factor
-data[, predator_id := as.factor(predator_id)]
-
-# Remove any NAs
-data <- data[complete.cases(data)]
-
-
-
-# Standardise the variables (Z-scores) -------------------------------------
-
-standardize <- function(x) {
-  (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
-}
-
-data[, c(
-    "Zprey_speed",
-    "Zgame_duration",
-    "Zcumul_xp",
-    "Zprey_avg_rank"
-    ) := lapply(.SD, standardize),
-       .SDcols = c(3:6)]
-
-
-# ==========================================================================
-# ==========================================================================
-
-
-
-
-
-# ==========================================================================
-# 2. Parametrize the model
-# ==========================================================================
-
-
-
-# Compute the custom family ------------------------------------------------
-
-beta_binomial2 <- custom_family(
-  "beta_binomial2", dpars = c("mu", "phi"),
-  links = c("logit", "log"), lb = c(NA, 0),
-  type = "int", vars = "vint1[n]"
-)
-
-
-
-# Function -----------------------------------------------------------------
-
-stan_funs <- "
-  real beta_binomial2_lpmf(int y, real mu, real phi, int T) {
-    return beta_binomial_lpmf(y | T, mu * phi, (1 - mu) * phi);
-  }
[…]

### 2024-09-06 code/01_code_models/A3_GAMM-rank.R

@@ -1,173 +1,0 @@
-# ==========================================================================
-
-#         GAMM model S - individual curves without common smoother
-#                              hunting success
-
-# ==========================================================================
-
-
-
-
-
-# ==========================================================================
-# 1. Prepare the data
-# ==========================================================================
-
-
-
-# Load packages ------------------------------------------------------------
-
-# Detect cores
-options(mc.cores = parallel::detectCores())
-
-# Load libraries
-library(data.table)
-library(brms)
-library(parallel)
-
-
-
-# Load data ----------------------------------------------------------------
-
-# Folder path Compute Canada
-folder <- file.path("/home", "maxime11", "projects", "def-monti", 
-                    "maxime11", "phd_project", "data")
-
-# Load data
-data <- fread(
-  file.path(folder, "FraserFrancoetalXXXX-data.csv"),
-  select = c("predator_id",
-             "hunting_success",
-             "prey_avg_speed",
-             "game_duration",
-             "cumul_xp_pred",
-             "prey_avg_rank")
-)
-
-# Predator id as factor
-data[, predator_id := as.factor(predator_id)]
-
-# Remove any NAs
-data <- data[complete.cases(data)]
-
-
-
-# Standardise the variables (Z-scores) -------------------------------------
-
-standardize <- function(x) {
-  (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
-}
-
-data[, c(
-    "Zprey_speed",
-    "Zgame_duration",
-    "Zcumul_xp",
-    "Zprey_avg_rank"
-    ) := lapply(.SD, standardize),
-       .SDcols = c(3:6)]
-
-# ==========================================================================
-# ==========================================================================
-
-
-
-
-
-# ==========================================================================
-# 2. Parametrize the model
-# ==========================================================================
-
-
-
-# Compute the custom family ------------------------------------------------
-
-beta_binomial2 <- custom_family(
-  "beta_binomial2", dpars = c("mu", "phi"),
-  links = c("logit", "log"), lb = c(NA, 0),
-  type = "int", vars = "vint1[n]"
-)
-
-
-
-# Function -----------------------------------------------------------------
-
-stan_funs <- "
-  real beta_binomial2_lpmf(int y, real mu, real phi, int T) {
-    return beta_binomial_lpmf(y | T, mu * phi, (1 - mu) * phi);
-  }
[…]

### 2024-09-06 code/01_code_models/A3_GAMM-speed-rank.R

@@ -1,177 +1,0 @@
-# ==========================================================================
-
-#         GAMM model S - individual curves without common smoother
-#                              hunting success
-
-# ==========================================================================
-
-
-
-
-
-# ==========================================================================
-# 1. Prepare the data
-# ==========================================================================
-
-
-
-# Load packages ------------------------------------------------------------
-
-# Detect cores
-options(mc.cores = parallel::detectCores())
-
-# Load libraries
-library(data.table)
-library(brms)
-library(parallel)
-
-
-
-# Load data ----------------------------------------------------------------
-
-# Folder path Compute Canada
-folder <- file.path("/home", "maxime11", "projects", "def-monti", 
-                    "maxime11", "phd_project", "data")
-
-# Load data
-data <- fread(
-  file.path(folder, "FraserFrancoetalXXXX-data.csv"),
-  select = c("predator_id",
-             "hunting_success",
-             "prey_avg_speed",
-             "game_duration",
-             "cumul_xp_pred",
-             "prey_avg_rank")
-)
-
-# Predator id as factor
-data[, predator_id := as.factor(predator_id)]
-
-# Remove any NAs
-data <- data[complete.cases(data)]
-
-
-
-# Standardise the variables (Z-scores) -------------------------------------
-
-standardize <- function(x) {
-  (x - mean(x, na.rm = TRUE)) / sd(x, na.rm = TRUE)
-}
-
-data[, c(
-    "Zprey_speed",
-    "Zgame_duration",
-    "Zcumul_xp",
-    "Zprey_avg_rank"
-    ) := lapply(.SD, standardize),
-       .SDcols = c(3:6)]
-
-# ==========================================================================
-# ==========================================================================
-
-
-
-
-
-# ==========================================================================
-# 2. Parametrize the model
-# ==========================================================================
-
-
-
-# Compute the custom family ------------------------------------------------
-
-beta_binomial2 <- custom_family(
-  "beta_binomial2", dpars = c("mu", "phi"),
-  links = c("logit", "log"), lb = c(NA, 0),
-  type = "int", vars = "vint1[n]"
-)
-
-
-
-# Function -----------------------------------------------------------------
-
-stan_funs <- "
-  real beta_binomial2_lpmf(int y, real mu, real phi, int T) {
-    return beta_binomial_lpmf(y | T, mu * phi, (1 - mu) * phi);
-  }
-  int beta_binomial2_rng(real mu, real phi, int T) {
[…]

### 2024-09-06 code/02_code_model-validation/GAMM-diagnostics.R

@@ -1,221 +1,0 @@
-# =======================================================================
-
-#                       GAMM model diagnostics                          #
-
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 1. Load libraries, datasets, and models
-# =======================================================================
-
-
-
-# Librairies ------------------------------------------------------------
-
- # Detect cores
- options(mc.cores = parallel::detectCores())
-
- library(data.table)
- library(brms)
- library(parallel)
- library(ggpubr)
-
-
-
-# Import the model ------------------------------------------------------
-
- path <- file.path(getwd(), "outputs", "01_outputs_models")
- #path <- getwd()
-
- # Load models
- mod1 <- readRDS(file.path(path, "A1_GAMM-rank.rds"))
- mod2 <- readRDS(file.path(path, "A2_GAMM-rank.rds"))
- mod3 <- readRDS(file.path(path, "A3_GAMM-rank.rds"))
- mod4 <- readRDS(file.path(path, "A2_GAMM-speed-rank.rds"))
- mod5 <- readRDS(file.path(path, "A3_GAMM-speed-rank.rds"))
-
- # Check object size
- #print(object.size(mod1), units = "MB")
- #print(object.size(mod2), units = "MB")
- #print(object.size(mod3), units = "MB")
- #print(object.size(mod4), units = "MB")
- #print(object.size(mod5), units = "MB")
-
-# =======================================================================
-# =======================================================================
-
-
-
-
-# =======================================================================
-# 2. Prepare functions for post-processing (beta-binom custom family)
-# =======================================================================
-
- # Expose functions
- expose_functions(mod1, vectorize = TRUE)
-
- # Define the log likelihood function
- log_lik_beta_binomial2 <- function(i, prep) {
-   mu <- brms::get_dpar(prep, "mu", i = i)
-   phi <- brms::get_dpar(prep, "phi", i = i)
-   trials <- prep$data$vint1[i]
[…]

### 2024-09-06 code/02_code_model-validation/GAMM_models-draws.R

@@ -1,263 +1,0 @@
-# =============================================================================
-
-#                       Inspect prior and posterior draws
-#                               from GAMM-GLMM models
-
-# =============================================================================
-
-
-
-
-
-# =============================================================================
-# Prepare session
-# =============================================================================
-
-
-# Load libraries --------------------------------------------------------------
-
- library(brms)
- library(ggplot2)
-
-
-
-# Prepare model draws ---------------------------------------------------------
-
- path <- file.path(getwd(), "outputs", "01_outputs_models")
-
- # Import model in R session
- mod1 <- readRDS(file.path(path, "A1_GAMM-rank.rds"))
- mod2 <- readRDS(file.path(path, "A2_GAMM-rank.rds"))
- mod3 <- readRDS(file.path(path, "A3_GAMM-rank.rds"))
- mod2p <- readRDS(file.path(path, "A2_GAMM-speed-rank.rds"))
- mod3p <- readRDS(file.path(path, "A3_GAMM-speed-rank.rds"))
-
-
- # Extract posterior draws
- posterior_fit1 <- as_draws_df(mod1)
- posterior_fit2 <- as_draws_df(mod2)
- posterior_fit3 <- as_draws_df(mod3)
- posterior_fit4 <- as_draws_df(mod2p)
- posterior_fit5 <- as_draws_df(mod3p)
-
-# =============================================================================
-# =============================================================================
-
-
-
-
-
-# =============================================================================
-# 1. Model 1
-# =============================================================================
-
-
-
-# Plot prior and posterior draws ----------------------------------------------
-
- # Intercept
- ggplot(posterior_fit1) +
-   geom_density(aes(prior_Intercept),
-                fill = "steelblue",
-                color = "black",
-                alpha = 0.6) +
-   geom_density(aes(Intercept),
-                fill = "#FC4E07",
-                color = "black",
-                alpha = 0.6) + 
-   theme_classic()
-
-
- # Game duration
- ggplot(posterior_fit1) +
-   geom_density(aes(prior_b_Zgame_duration),
-                fill = "steelblue",
-                color = "black",
-                alpha = 0.6) +
-   geom_density(aes(b_Zgame_duration),
-                fill = "#FC4E07",
-                color = "black",
-                alpha = 0.6) +
-   theme_classic()
-
- # slope term of cumul xp
- ggplot(posterior_fit1) +
-   geom_density(aes(prior_bs_sZcumul_xp_1),
-                fill = "steelblue",
[…]

### 2024-09-06 code/04_code_figures/figure1.R

@@ -1,413 +1,0 @@
-# ==========================================================================
-
-#                           Plot GAMM models
-
-# ==========================================================================
-
-
-
-# ==========================================================================
-# 1. Prepare script
-# ==========================================================================
-
-
-
-# Load libraries and model -------------------------------------------------
-
- options(mc.cores = parallel::detectCores()) 
-
- library(parallel)
- library(brms)
- library(data.table)
- library(ggplot2)
- library(ggpubr)
- library(viridis)
-
- path <- file.path(getwd(), "outputs", "01_outputs_models")
-
- modA2 <- readRDS(file.path(path, "A2_GAMM-rank.rds"))
- modA2_prey <- readRDS(file.path(path, "A2_GAMM-speed-rank.rds"))
-
-
-
-# Load the data ------------------------------------------------------------
-
- data <- fread("./data/FraserFrancoetal2023-data.csv",
-               select = c("predator_id",
-                          "game_duration",
-                          "pred_speed",
-                          "prey_avg_speed",
-                          "prey_avg_rank",
-                          "cumul_xp_pred",
-                          "total_xp_pred",
-                          "hunting_success"))
-
- data[, predator_id := as.factor(predator_id)]
-
-
-
-# Post processing preparations for custom family ---------------------------
-
- expose_functions(modA2, vectorize = TRUE)
-
- # Define the log likelihood function
- log_lik_beta_binomial2 <- function(i, prep) {
-   mu <- brms::get_dpar(prep, "mu", i = i)
-   phi <- brms::get_dpar(prep, "phi", i = i)
-   trials <- prep$data$vint1[i]
-   y <- prep$data$Y[i]
-   beta_binomial2_lpmf(y, mu, phi, trials)
- }
-
- # Define function for posterior_predict
- posterior_predict_beta_binomial2 <- function(i, prep, ...) {
-   mu <- brms::get_dpar(prep, "mu", i = i)
-   phi <- brms::get_dpar(prep, "phi", i = i)
-   trials <- prep$data$vint1[i]
-   beta_binomial2_rng(mu, phi, trials)
- }
-
- # Define function for posterior_epred
- posterior_epred_beta_binomial2 <- function(prep) {
-   mu <- brms::get_dpar(prep, "mu")
-   trials <- prep$data$vint1
[…]

### 2024-09-06 jobs_slurm/A1_GAMM.sh
delete old GAMM job files

@@ -1,16 +1,0 @@
-#!/bin/bash
-#SBATCH --account=def-monti
-#SBATCH --nodes=1
-#SBATCH --cpus-per-task=48
-#SBATCH --mem=32000M
-#SBATCH --time=00-08:30
-#SBATCH --mail-user=fraser_franco.maxime@courrier.uqam.ca
-#SBATCH --mail-type=ALL
-
-module load StdEnv/2020
-module load gcc/9.3.0
-module load r-bundle-bioconductor/3.14
-module load r/4.1.2
-
-#export R_LIBS=~/.local/R/$EBVERSIONR/
-Rscript A1_GAMM.R

### 2024-09-06 jobs_slurm/A2_GAMM-rank.sh

@@ -1,16 +1,0 @@
-#!/bin/bash
-#SBATCH --account=def-monti
-#SBATCH --nodes=1
-#SBATCH --cpus-per-task=48
-#SBATCH --mem=64000M
-#SBATCH --time=5-00:00
-#SBATCH --mail-user=fraser_franco.maxime@courrier.uqam.ca
-#SBATCH --mail-type=ALL
-
-module load StdEnv/2020
-module load gcc/9.3.0
-module load r-bundle-bioconductor/3.14
-module load r/4.1.2
-
-#export R_LIBS=~/.local/R/$EBVERSIONR/
-Rscript A2_GAMM-rank.R

### 2024-09-06 jobs_slurm/A2_GAMM-speed-rank.sh

@@ -1,16 +1,0 @@
-#!/bin/bash
-#SBATCH --account=def-monti
-#SBATCH --nodes=1
-#SBATCH --cpus-per-task=48
-#SBATCH --mem=64000M
-#SBATCH --time=5-20:00
-#SBATCH --mail-user=fraser_franco.maxime@courrier.uqam.ca
-#SBATCH --mail-type=ALL
-
-module load StdEnv/2020
-module load gcc/9.3.0
-module load r-bundle-bioconductor/3.14
-module load r/4.1.2
-
-#export R_LIBS=~/.local/R/$EBVERSIONR/
-Rscript A2_GAMM-speed-rank.R

### 2024-09-06 jobs_slurm/A3_GAMM-rank.sh

@@ -1,16 +1,0 @@
-#!/bin/bash
-#SBATCH --account=def-monti
-#SBATCH --nodes=1
-#SBATCH --cpus-per-task=48
-#SBATCH --mem=64000M
-#SBATCH --time=2-15:00
-#SBATCH --mail-user=fraser_franco.maxime@courrier.uqam.ca
-#SBATCH --mail-type=ALL
-
-module load StdEnv/2020
-module load gcc/9.3.0
-module load r-bundle-bioconductor/3.14
-module load r/4.1.2
-
-#export R_LIBS=~/.local/R/$EBVERSIONR/
-Rscript A3_GAMM-rank.R

### 2024-09-06 jobs_slurm/A3_GAMM-speed-rank.sh

@@ -1,16 +1,0 @@
-#!/bin/bash
-#SBATCH --account=def-monti
-#SBATCH --nodes=1
-#SBATCH --cpus-per-task=48
-#SBATCH --mem=64000M
-#SBATCH --time=3-00:00
-#SBATCH --mail-user=fraser_franco.maxime@courrier.uqam.ca
-#SBATCH --mail-type=ALL
-
-module load StdEnv/2020
-module load gcc/9.3.0
-module load r-bundle-bioconductor/3.14
-module load r/4.1.2
-
-#export R_LIBS=~/.local/R/$EBVERSIONR/
-Rscript A3_GAMM-speed-rank.R

### 2024-09-06 jobs_slurm/GAMM-diagnostics.sh

@@ -1,16 +1,0 @@
-#!/bin/bash
-#SBATCH --account=def-monti
-#SBATCH --nodes=1
-#SBATCH --cpus-per-task=48
-#SBATCH --mem=32000M
-#SBATCH --time=00-5:00
-#SBATCH --mail-user=fraser_franco.maxime@courrier.uqam.ca
-#SBATCH --mail-type=ALL
-
-module load StdEnv/2020
-module load gcc/9.3.0
-module load r-bundle-bioconductor/3.14
-module load r/4.1.2
-
-#export R_LIBS=~/.local/R/$EBVERSIONR/
-Rscript GAMM-diagnostics.R

### 2024-09-06 manuscript/manuscript.Rmd
files up to date

@@
 
-The capacity of predators to match their tactic to the behaviour of their prey is expected to drive the outcome of predator-prey interactions.
-To do so, predators need to practice their tactics extensively to develop the skills and expertise to successfully hunt their prey, which may result in individual foraging specialization.
-Yet, there are very limited empirical assessments showing links between experience, foraging specialization, and hunting success at the individual level, due to the numerous challenges of monitoring direct interactions in the wild.
-In this study, we used a virtual predator-prey system (the online game *Dead by Daylight*) to investigate if and how hunting experience shapes individual foraging specialization and success in predators across repeated interactions with their prey.
-Our results show that predators optimized prey consumption as they gained experience.
-Prey behaviour was an important mediator of this relationship, resulting in differences among predators in the development of expertise.
+The capacity of predators to match their tactic to their prey is expected to drive the outcome of predator-prey interactions.
+To do so, predators need to practice their tactics extensively to develop the skills to be successful hunters, which may result in individual foraging specialization.
+Yet, there are limited empirical assessments showing links between experience, foraging specialization, and hunting success at the individual level, due to the challenges of monitoring direct interactions in the wild.
+Here, we used a virtual predator-prey system (the game *Dead by Daylight*) to investigate how experience shapes individual foraging specialization and success in predators across repeated interactions with their prey.
+We show that predators optimized prey consumption as they gained experience.
+Prey speed was an important mediator of this relationship, resulting in differences among predators in the development of expertise.
 Throughout experience, 68% of predators became either increasingly specialized by always moving at a fast pace, or flexible by switching between slow and fast speeds.
-The remaining 32% of predators used a specialized tactic of fast movement throughout the study period.
-The predators' strategies (i.e.
-flexible or specialized foraging) were partially matched to the preys' speed, suggesting that changes in hunting behaviour were driven by repeated encounters with prey.
-Ultimately, flexible foragers were only slightly less successful than specialist foragers, such that both achieved similar success overall.
-Our observations suggest that experience drives among individual differences in foraging tactics, which may act as a stabilizing mechanism promoting behavioural diversification in predator-prey systems.
+The predators’ strategies were partially matched to the preys’ speed, suggesting that changes in hunting behaviour were driven by repeated encounters with prey.
+Flexible and specialist foragers achieved similar success overall.
+Our findings suggest that experience may be mechanism promoting behavioural diversification in predator-prey systems.
 

### 2024-09-07 manuscript/appendix1.Rmd
files up to date
arranged appendix1

--- 2023-06-14 manuscript/Chapter2-appendix1.Rmd
@@
   word_document:
-    reference_docx: Chapter2-styles-appendix.docx
+    reference_docx: appendix-styles.docx
     fig_caption: yes
@@
 ```{r setup, include = FALSE}
-
 knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
@@
 library(dplyr)
-
 ```
-
-Journal name : Ecology
-
-Authors : Maxime Fraser Franco, Francesca Santostefano, Julien G. A. Martin, Clint D. Kelly, Pierre-Olivier Montiglio
 
@@
 
-```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Among individual differences in the development of hunting expertise in the model where we do not account for prey speed and average rank.
-The predators' hunting success (i.e.
-the probability of capturing the four prey) is on the y axis, and the predators' cumulative experience (i.e.
-the number of matches played prior to each observation) is on the x axis.
-Each fitted curve represents an individual predator.
-The individual curves are separated by differences between their first and last predicted value, and displayed as such in three distinct panels.
-(A) Individuals with a >0.5 unit increase in hunting success with experience (B) Individuals with a <-0.5 unit decrease in hunting success with experience.
-(C) Individuals that maintained a stable hunting success (between -0.5 and 0.5 unit change in hunting success)"}
-
-knitr::include_graphics(
-  here::here(
-    "outputs", "04_outputs_figures",
-    "appendix1_figureS1.png"
-  )
-)
-
-```
-
-```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Correlations between the predators' mean hunting success (y axis) and intra individual variance in speed (x axis) to test for differences in success between individuals along the flexible-specialist hunter continuum.
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Correlations between the predators' mean hunting success (y axis) and intra individual variance in speed (x axis) to test for differences in success between individuals along the flexible-specialist hunter continuum.
 Each point represents the posterior median predicted value of an individual predator along with its 95% HPD interval.

### 2024-11-26 manuscript/appendix2.Rmd
renamed files to remove chapter2 in title
files up to date
arranged appendix2 rmd
update all appendix files

--- 2023-06-14 manuscript/Chapter2-appendix2.Rmd
@@
 title: |
-     Experience shapes individual foraging specialization and success in a virtual predator-prey system: \
-     Appendix 2
+     Individual foraging specialization and success change across experience in a virtual predator-prey system: \
+     Appendix 3
 
@@
 
-Journal name : Ecology
-
-Authors : Maxime Fraser Franco, Francesca Santostefano, Julien G. A. Martin, Clint D. Kelly, Pierre-Olivier Montiglio
-
 \newpage
 
-```{r tableprep, include = FALSE}
+```{r tableS1, ft.align = "left"}
 
 # ===========================================================================
-# 1. Extract the fixed effects from the MV model
+# 1. Import the model fit
 # ===========================================================================
 
-# Prepare the table ---------------------------------------------------------
+# path
+path <- file.path(here::here("outputs"))
 
-# Model fit
+# Import the model
 fit <- readRDS(
-  here::here("outputs", "01_outputs_models", "B2_DHMLM.rds")
+  file.path(path, "01_outputs_models", "B1_DHMLM.rds")
 )
-
-# Fixed effects table
-results <- data.table(
-  round(summary(fit)$fixed, digits = 2)[, 1:4],
-  keep.rownames = TRUE
-)
-
-setnames(results, "rn", "parameter")
-
-results[parameter %like% "predspeed", trait := "predator speed"][
-  parameter %like% "preyavgspeed", trait := "prey speed"][
-    parameter %like% "success", trait := "hunting success"
-  ]
-
-# mu parameters table
-tabs1 <- results[
-    !(parameter %like% "sigma"),
-    c(6, 1, 2, 4, 5)
-]
-
-# sigma parameters table
-tabs2 <- results[
-    parameter %like% "sigma",
-    c(6, 1, 2, 4, 5)
-]
-
-# Rename parameter values ---------------------------------------------------
-
-# Rename
-tabs1[,
-  parameter := c(
-    rep(
-      c("prey rank",
-        "cumulative experience",
-        "group 1",
-        "group 4",
-        "group 2",
-        "group 3"),
-      2
-    ),
-      c("game duration",
-        "cumulative experience",
-        "group 1",
-        "group 4",
-        "group 2",
-        "group 3")
-  )
-]
-# Reorder rows
-tabs1 <- tabs1[
-  c(1:3, 5, 6, 4,
-    7:9, 11, 12, 10,
-    13:15, 17, 18, 16)
-]
-
-# Rename
-tabs2[,
-  parameter := rep(
-    c("prey rank",
-      "cumulative experience",
-      "group 1",
-      "group 4",
-      "group 2",
-      "group 3"),
-    2
-  )
-]
-
-# Reorder
-tabs2 <- tabs2[
-  c(1:3, 5, 6, 4,
-    7:9, 11, 12, 10)
-]
 
@@
 # ===========================================================================
-# 2. Compute the table using flextable
+# 2. Fixed effects table
+# ===========================================================================
+
+# Prepare the table ---------------------------------------------------------
+
+# Extract the fixed effects posterior samples
+b_draws <- data.table(
+  as_draws_df(
+    fit, variable = "^b_", regex = TRUE
+  )
+)
+
+b_draws[, c(34:36) := NULL]
+
+# Back-transform the parameters ----------------------------------------------
+
+# Take the exponent of sigma parameters
+b_draws[
+  , c("b_sigma_speednovice_Intercept",
+      "b_sigma_speedinterm_Intercept",
+      "b_sigma_speedadvanced_Intercept",
+      "b_sigma_preyspeednovice_Intercept",
+      "b_sigma_preyspeedinterm_Intercept",
+      "b_sigma_preyspeedadvanced_Intercept",
+      "b_sigma_speednovice_Zprey_avg_rank",
+      "b_sigma_speedinterm_Zprey_avg_rank",
+      "b_sigma_speedadvanced_Zprey_avg_rank",
+      "b_sigma_preyspeednovice_Zprey_avg_rank",
+      "b_sigma_preyspeedinterm_Zprey_avg_rank",
+      "b_sigma_preyspeedadvanced_Zprey_avg_rank"
+  )
+  := lapply(.SD, function(x) {exp(x)}),
+  .SDcols = c(
+    "b_sigma_speednovice_Intercept",
+    "b_sigma_speedinterm_Intercept",
+    "b_sigma_speedadvanced_Intercept",
+    "b_sigma_preyspeednovice_Intercept",
+    "b_sigma_preyspeedinterm_Intercept",
+    "b_sigma_preyspeedadvanced_Intercept",
+    "b_sigma_speednovice_Zprey_avg_rank",
+    "b_sigma_speedinterm_Zprey_avg_rank",
+    "b_sigma_speedadvanced_Zprey_avg_rank",
+    "b_sigma_preyspeednovice_Zprey_avg_rank",
+    "b_sigma_preyspeedinterm_Zprey_avg_rank",
+    "b_sigma_preyspeedadvanced_Zprey_avg_rank"
+  )
+]
+
+# plogis for the success parameters
+b_draws[
+  , c("b_successnovice_Intercept",
+      "b_successinterm_Intercept",
+      "b_successadvanced_Intercept",
+      "b_successnovice_Zgame_duration",
+      "b_successinterm_Zgame_duration",
+      "b_successadvanced_Zgame_duration",
+      "b_successnovice_Zprey_avg_rank",
+      "b_successinterm_Zprey_avg_rank",
+      "b_successadvanced_Zprey_avg_rank"
+  )
+  := lapply(.SD, function(x) {plogis(x)}),
+  .SDcols = c(
+    "b_successnovice_Intercept",
+    "b_successinterm_Intercept",
+    "b_successadvanced_Intercept",
+    "b_successnovice_Zgame_duration",
+    "b_successinterm_Zgame_duration",
+    "b_successadvanced_Zgame_duration",
+    "b_successnovice_Zprey_avg_rank",
+    "b_successinterm_Zprey_avg_rank",
+    "b_successadvanced_Zprey_avg_rank"
+  )
+]
+
+# Reshape the table -----------------------------------------------------------
+
+fixef_tab <- melt(
+  b_draws,
+  variable.name = "parameter"
+)
+
+# Summarize the values (medians + 95% CI) -------------------------------------
+
+# Intervals
+lower_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[1]
+}
+upper_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+# Summarize values
+fixef_tab[, ":=" (median = median(value),
+                  lower_ci = lower_interval(value),
+                  upper_ci = upper_interval(value)),
+          by = .(parameter)]
+
+fixef_tab <- unique(fixef_tab[, .(parameter, median, lower_ci, upper_ci)])
+fixef_tab[, c(2:4) := round(fixef_tab[, c(2:4)], digits = 2)]
+
+# Rearrange the table --------------------------------------------------------
+
+# Add a column that specifies the experience level
+fixef_tab[parameter %like% "novice", xp_level := "novice"]
+fixef_tab[parameter %like% "interm", xp_level := "intermediate"]
+fixef_tab[parameter %like% "advanced", xp_level := "advanced"]
+
+# Paste upper and lower ci with estimate
+fixef_tab[, estimate := paste(format(median, digits = 2), "(")]
+fixef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
+fixef_tab[, estimate := paste(estimate, ",", sep = "")]
+fixef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
+fixef_tab[, estimate := paste(estimate, ")", sep = "")]
+fixef_tab[, c("median", "lower_ci", "upper_ci") := NULL]
+
+# reorder columns, and then rows based on xp level
+setorder(
+  fixef_tab,
+  cols = -"xp_level"
+)
+
+# Create trait column
+fixef_tab[, trait := ""][
+  parameter %like% "success", trait := "hunting success"][
+    parameter %like% "speed", trait := "predator speed"][
+      parameter %like% "preyspeed", trait := "prey speed"
+      ]
+
+# Rename parameter column
+fixef_tab[
+  , parameter := rep(
+    c(
+      rep(c("intercept (mean)", "intercept (sigma)"), 2),
+      "intercept (mean)",
+      rep(c("prey rank (mean)", "prey rank (sigma)"), 2),
+      "match duration (mean)", "prey rank (mean)"
+    ),
+    3
+  )
+]
+
+# Reshape
+fixef_tab <- dcast(
+  fixef_tab,
+  trait + parameter ~ xp_level,
+  value.var = "estimate"
+)
+
+# Reorder columns and rows
+fixef_tab <- fixef_tab[, c(1, 2, 5, 4, 3)]
+table <- fixef_tab[c(4, 6, 5, 7, 8, 10, 9, 11, 1, 2, 3)]
+
+# Because I can't align the rows properly
+# in the flextable object
+table[c(2:4, 6:8, 10, 11), 1] <- " "
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 3. Create the table using flextable
 # ===========================================================================
@@
   x <- hline_bottom(x, part = "all", border = std_border)
-   autofit(x)
+  x <- width(x, j = 1, width = 2.84, unit = "cm")
+  x <- width(x, j = 2, width = 3.78, unit = "cm")
+  x <- width(x, j = c(3:5), width = 3.3, unit = "cm")
 }
 
-```
-
-```{r tableS1, ft.align = "left"}
 # Create the table ----------------------------------------------------------
 
-tabs1f <- tabs1 %>%
+tab1 <-
+
+  # table structure
+  table %>%
+  select(trait, parameter,
+         novice, intermediate, advanced) %>%
   flextable(col_keys = my_header$col_keys) %>%
@@
   my_theme() %>%
-  merge_v(j = 1) %>%
+
+  # Align repeated rows on column 1
+  #merge_v(j = 1) %>%
   valign(j = 1, valign = "top", part = "body") %>%
-  align(align = "left", part = "all", j = c(1, 2)) %>%
+
+  # Align text
+  align(align = "left", part = "all", j = 1) %>%
+  align(align = "left", part = "all", j = 2) %>%
   align(align = "center", part = "all", j = 3) %>%
@@
   ) %>%
+
+  # Table caption
   set_caption(
-    tabs1,
-    caption = "Table S1. Fixed effects table on the mean part of the DHMLM comparing random groups of players with different matches played to the group presented in the main text.",
+    caption = "Table S1.
+Posterior medians and 95% HPD intervals of the fixed effects estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
+The coefficients are from the model that includes the outlier.",
     style = "Table Caption"
   ) %>%
+
+  # Font options
+  font(fontname = "Times New Roman", part = "all") %>%
   fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer") %>%
-  font(fontname = "Times New Roman", part = "all")
+  fontsize(size = 12, part = "footer")
 
-tabs1f
+tab1
 
@@
 
-tabs2f <- tabs2 %>%
+# ===========================================================================
+# 1. Import the model fit
+# ===========================================================================
+
+# path
+path <- file.path(here::here("outputs"))
+
+# Import the model
+fit <- readRDS(
+  file.path(path, "01_outputs_models", "B1_DHMLM.rds")
+)
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 2. Random effects table
+# ===========================================================================
+
+# Prepare data --------------------------------------------------------------
+
+# Extract the random effect variances
+sd_draws <- data.table(
+   as_draws_df(
+      fit, variable = "^sd_", regex = TRUE
+   )
+)
+
+sd_draws[, c(28:30) := NULL]
+
+# Calculate parameters -------------------------------------------------------
+
+# Take the exponent of sigma parameters
+sd_draws[
+   , c("sd_predator_id__sigma_speednovice_Intercept",
+       "sd_predator_id__sigma_speedinterm_Intercept",
+       "sd_predator_id__sigma_speedadvanced_Intercept",
+       "sd_predator_id__sigma_preyspeednovice_Intercept",
+       "sd_predator_id__sigma_preyspeedinterm_Intercept",
+       "sd_predator_id__sigma_preyspeedadvanced_Intercept"
+   )
+   := lapply(.SD, function(x) {exp(x)}),
+   .SDcols = c(
+      "sd_predator_id__sigma_speednovice_Intercept",
+      "sd_predator_id__sigma_speedinterm_Intercept",
+      "sd_predator_id__sigma_speedadvanced_Intercept",
+      "sd_predator_id__sigma_preyspeednovice_Intercept",
+      "sd_predator_id__sigma_preyspeedinterm_Intercept",
+      "sd_predator_id__sigma_preyspeedadvanced_Intercept"
+   )
+]
+
+# Reshape the table -----------------------------------------------------------
+
+ranef_tab <- melt(
+   sd_draws,
+   variable.name = "parameter"
+)
+
+# Summarize the values (means + 95% CI) --------------------------------------
+
+# Intervals
+lower_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[1]
+}
+upper_interval <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+# Summarize values
+ranef_tab[, ":=" (median = median(value),
+                  lower_ci = lower_interval(value),
+                  upper_ci = upper_interval(value)),
+          by = .(parameter)]
+
+ranef_tab <- unique(ranef_tab[, .(parameter, median, lower_ci, upper_ci)])
+ranef_tab[, c(2:4) := round(ranef_tab[, c(2:4)], digits = 2)]
+
+# Rearrange the table --------------------------------------------------------
+
+# Add a column that specifies the experience level
+ranef_tab[parameter %like% "novice", xp_level := "novice"]
+ranef_tab[parameter %like% "interm", xp_level := "intermediate"]
+ranef_tab[parameter %like% "advanced", xp_level := "advanced"]
+
+# Paste upper and lower ci with estimate
+ranef_tab[, estimate := paste(format(median, digits = 2), "(")]
+ranef_tab[, estimate := paste(estimate, format(lower_ci, digits = 2), sep = "")]
+ranef_tab[, estimate := paste(estimate, ",", sep = "")]
+ranef_tab[, estimate := paste(estimate, format(upper_ci, digits = 2), sep = " ")]
+ranef_tab[, estimate := paste(estimate, ")", sep = "")]
+ranef_tab[, c("median", "lower_ci", "upper_ci") := NULL]
+
+# Parameter column
+ranef_tab[
+   , parameter1 := ifelse(
+       parameter %like% "predator_id__sigma",
+       "predator ID (sigma)",
+       "predator ID (mean)"
+   )
+]
+ranef_tab[parameter %like% "avatar", parameter1 := "avatar (mean)"]
+ranef_tab[parameter %like% "env", parameter1 := "environment (mean)"]
+
+# Trait column
+ranef_tab[
+   , trait := ifelse(
+       parameter %like% "preyspeed",
+       "prey speed",
+       "predator speed"
+   )
+]
+ranef_tab[parameter %like% "success", trait := "hunting success"]
+
+# Remove old parameter column and replace by new
+ranef_tab[, parameter := NULL]
+setnames(ranef_tab, "parameter1", "parameter")
+
+# Reshape
+ranef_tab <- dcast(
+   ranef_tab,
+   trait + parameter ~ xp_level,
+   value.var = "estimate"
+)
+
+# Reorder columns
+ranef_tab <- ranef_tab[, c(1, 2, 5, 4, 3)]
+
+# Reorder rows
+table <- ranef_tab[c(2:9, 1)]
+
+# ===========================================================================
+# ===========================================================================
+
+# ===========================================================================
+# 3. Create the table using flextable
+# ===========================================================================
+
+# Prepare the table parameters ----------------------------------------------
+
+# Custom header
+my_header <- data.frame(
+  col_keys = c("trait", "parameter",
+               "novice", "intermediate", "advanced"),
+  line1 = c("Trait",
+            "Parameter",
+            "Novice",
+            "Intermediate",
+            "Advanced"),
+  stringsAsFactors = FALSE
+)
+
+# Custom theme
+my_theme <- function(x, ...) {
+  x <- colformat_double(x, big.mark = " ",
+                        decimal.mark = ".",
+                        digits = 2)
+  x <- set_table_properties(x, layout = "autofit")
+  x <- border_remove(x)
+  std_border <- fp_border(width = 1, color = "black")
+  x <- hline_top(x, part = "all", border = std_border)
+  x <- hline_bottom(x, part = "all", border = std_border)
+}
+
+# Create the table ----------------------------------------------------------
+
+tab2 <-
+
+  # table structure
+  table %>%
+  select(trait, parameter,
+         novice, intermediate, advanced) %>%
   flextable(col_keys = my_header$col_keys) %>%
@@
       as_sup("a "),
-      "Group 1: <50 matches, Group 2: between 50 and 99 matches, Group 3: between 100 and 299 matches, Group 4: > 299 (i.e. group in the main text)"
+      "We exponentiated the dispersion parameters (i.e. sigma) which are estimated on a log scale.",
+      as_sup("\nb "),
+      "The standard deviation values on the mean part of the equation indicate, for all traits, among individual differences in mean behaviour, prey encountered, and success.",
+      as_sup("\nc "),
+      "The standard deviation values on the dispersion part of the equation (i.e.
+sigma) for predator speed indicate among individual differences in behavioural specialization.
+For prey speed, they indicate among individual differences in the variability of prey encounters."
     ),
@@
   ) %>%
+
+  # Add table caption
   set_caption(
-    tabs2,
-    caption = "Table S2. Fixed effects table on the dispersion part of the DHMLM comparing random groups of players with different matches played to the group presented in the main text.",
+    caption = "Table S2.
+Posterior medians and 95% HPD intervals of the random effect standard deviations estimated by the MDHGLM of predator speed, prey speed, and predator hunting success.
+The coefficients are from the model that includes the outlier.",
     style = "Table Caption"
   ) %>%
+
+  # Font options
+  font(fontname = "Times New Roman", part = "all") %>%
   fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer") %>%
-  font(fontname = "Times New Roman", part = "all")
+  fontsize(size = 12, part = "footer")
 
-tabs2f
+tab2
+
+# ===========================================================================
+# ===========================================================================
 
 ```
+
+\newpage
+
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and HPD intervals comparing the parameter values predicted by the MDHGLM among all predator experience levels.
+The parameter being compared is on the y axis, and the difference in parameter values between two experience levels is displayed on the x axis.
+The pairwise comparisons between experience levels are displayed across the three panels A, B, and C.
+The results are from the model that includes the outlier."}
+
+knitr::include_graphics(
+    here::here(
+        "outputs", "04_outputs_figures",
+        "appendix2_figureS1.png"
+    )
+)
+
+```
+
+\newpage
+
+```{r figS2, out.width = "100%", fig.cap = "**Figure S2.** Posterior median differences and HPD intervals comparing the trait correlations predicted by the MDHGLM between the advanced and novice levels.
+The difference is displayed on the y axis and the correlated parameters are displayed on the x axis.
+Positive values indicate that the correlation was greater when predators where advanced, while negative values indicate that the correlation was greater when predators where novices.
+The results are from the MDHGLM that includes the outlier."}
+
+knitr::include_graphics(
+  here::here(
+    "outputs", "04_outputs_figures",
+    "appendix2_figureS2.png"
+  )
+)
+
+```

### 2024-11-26 code/04_code_figures/appendix2_figureS1.R

@@ -1,6 +1,6 @@
 # =======================================================================
 
-#                       Code to produce Figure S3                       #
+#                 Code to produce Appendix 2: Figure S3                 #
 
 # =======================================================================
 
@@ -349,7 +349,7 @@ path <- file.path(getwd(), "outputs", "04_outputs_figures")
 
 # Export
 ggsave(
-  filename = file.path(path, "appendix3_figureS1.png"),
+  filename = file.path(path, "appendix2_figureS1.png"),
   plot = fig,
   width = 32, height = 14, # 32 14
   units = "cm",

### 2024-11-26 code/04_code_figures/appendix2_figureS2.R

@@ -1,0 +1,222 @@
+# =======================================================================
+
+#               Code to produce Appendix 2: Figure S2                   #
+
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 1. Load libraries and import model
+# =======================================================================
+
+# Load libraries
+library(brms)
+library(ggplot2)
+library(data.table)
+
+path <- file.path(getwd(), "outputs", "01_outputs_models")
+fit <- readRDS(file.path(path, "B1_DHMLM.rds"))
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 2. Estimate differences between novices and advanced levels
+# =======================================================================
+
+# Prepare the draws -----------------------------------------------------
+
+cors <- as_draws_df(fit, variable = "cor", regex = TRUE)
+cors <- data.table(cors)
+cors <- cors[, !c(".chain", ".iteration", ".draw")]
+
+cors <- melt(cors)
+cors <- cors[!(variable %like% "prior")]
+
+cors1 <- cors[!(variable %like% "interm")]
+cors1 <- cors1[!(variable %like% "novice")]
+cors2 <- cors[!(variable %like% "interm")]
+cors2 <- cors2[!(variable %like% "advanced")]
+
+setnames(cors1, c("variable", "value"), c("variable_adv", "value_adv"))
+setnames(cors2, c("variable", "value"), c("variable_nov", "value_nov"))
+
+
+
+# Compute the differences -----------------------------------------------
+
+# Compute the difference in absolute values
+# since the signs of the correlations do not change
+tab <- cbind(cors1, cors2)
+tab[, difference_cor := abs(value_adv) - abs(value_nov)]
+
+
+# Intervals
+lower_95 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[1]
+}
+upper_95 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
+
+lower_80 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.80)[1]
+}
+upper_80 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.80)[2]
+}
+
[…]

### 2024-11-26 code/04_code_tables/appendix4_tableS1.R

@@ -1,319 +1,0 @@
-# ===========================================================================
-
-#                        Code to produce Table S1                           #
-
-# ===========================================================================
-
-
-
-
-
-# ===========================================================================
-# 1. Load libraries and import the model fit
-# ===========================================================================
-
- # Load libraries
- library(data.table)
- library(flextable)
- library(officer)
- library(dplyr)
- library(brms)
-
- # path
- path <- file.path(getwd(), "outputs")
-
- # Import the model
- fit <- readRDS(
-   file.path(path, "01_outputs_models", "B1_DHMLM-no-outlier.rds")
- )
-# ===========================================================================
-# ===========================================================================
-
-
-
-
-
-# ===========================================================================
-# 2. Create correlation matrix
-# ===========================================================================
-
-
-# Extract the posterior correlations ----------------------------------------
-
- # Taken from fit
- corrs <- data.table(
-   as_draws_df(fit, variable = "^cor_", regex = TRUE)
- )
- # Remove MCMC columns
- corrs[, c(".chain", ".iteration", ".draw") := NULL]
- # Table to long format
- corrs1 <- melt(corrs)
-
-
-
-# Summarize posterior correlations --------------------------------------
-
- # HPD intervals functions
- lower_95 <- function(x) {
-   coda::HPDinterval(as.mcmc(x), 0.95)[1]
- }
- upper_95 <- function(x) {
-   coda::HPDinterval(as.mcmc(x), 0.95)[2]
- }
-
- # Summary of posterior
- corrs1[
-   , ":=" (
-     median_cor = median(value),
-     lower_95 = lower_95(value),
-     upper_95 = upper_95(value)
-   ),
-   by = variable
- ]
-
- # Round the values to 2 digits
- corrs1[
-   , c(3:5) := lapply(.SD, function(x) round(x, digits = 2)),
-   .SDcols = c(3:5)
- ]
-
- # Keep unique values
- cor_tab <- unique(corrs1[, c(1, 3:5)])
-
- # Paste estimate with lower and upper ci into a single column
[…]

### 2024-11-26 code/04_code_figures/figure1.R
update all plot files

@@ -1,0 +1,359 @@
+# =======================================================================
+
+#                       Code to produce Figure 1                        #
+
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 1. Load libraries and import model
+# =======================================================================
+
+# Load libraries
+library(brms)
+library(ggplot2)
+library(viridis)
+library(data.table)
+
+path <- file.path(getwd(), "outputs", "01_outputs_models")
+fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
+
+# =======================================================================
+# =======================================================================
+
+
+
+
+
+# =======================================================================
+# 2. Estimate differences between experience levels
+# =======================================================================
+
+# a -> Compare novices vs intermediate
+# b -> Compare intermediate with advanced
+# c-> Compare novices with advanced
+
+
+# Extract the posterior samples -----------------------------------------
+
+dt <- data.table(
+  as_draws_df(
+    fit,
+    variable = c("b_", "sd"),
+    regex = TRUE
+  )
+)
+dt <- dt[, c(1:15, 54:68)]
+
+
+
+# Back-transform values -------------------------------------------------
+
+# Take the exponent of sigma parameters
+dt[
+  , c("b_sigma_speednovice_Intercept",
+      "b_sigma_speedinterm_Intercept",
+      "b_sigma_speedadvanced_Intercept",
+      "b_sigma_preyspeednovice_Intercept",
+      "b_sigma_preyspeedinterm_Intercept",
+      "b_sigma_preyspeedadvanced_Intercept",
+      "sd_predator_id__sigma_speednovice_Intercept",
+      "sd_predator_id__sigma_speedinterm_Intercept",
+      "sd_predator_id__sigma_speedadvanced_Intercept",
+      "sd_predator_id__sigma_preyspeednovice_Intercept",
+      "sd_predator_id__sigma_preyspeedinterm_Intercept",
+      "sd_predator_id__sigma_preyspeedadvanced_Intercept"
+  )
+  := lapply(.SD, function(x) {exp(x)}),
[…]

### 2024-11-26 code/04_code_figures/figure2.R

@@ -1,6 +1,8 @@
 # =======================================================================
 
+
 #                       Code to produce Figure 2                        #
+#          Plot distribution of players from novice to advanced         #
 
 # =======================================================================
 
@@ -9,18 +11,36 @@
 
 
 # =======================================================================
-# 1. Load libraries and import model
+# 1. Prepare the script
 # =======================================================================
 
-# Load libraries
+
+# Load libraries and model ----------------------------------------------
+
+# Libraries
 library(brms)
-library(ggplot2)
-library(viridis)
 library(data.table)
+library(ggplot2)
+library(ggpubr)
+library(ggridges)
 
+# import model
 path <- file.path(getwd(), "outputs", "01_outputs_models")
 fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
 
+
+
+# Load data ------------------------------------------------------------
+
+# Data
+data <- fread("./data/FraserFrancoetal2023-data.csv",
+              select = c("predator_id",
+                         "cumul_xp_pred",
+                         "pred_speed"))
+
+# Predator id as factor
+data[, predator_id := as.factor(predator_id)]
+
 # =======================================================================
 # =======================================================================
 
@@ -29,330 +49,337 @@ fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
 
 
 # =======================================================================
-# 2. Estimate differences between experience levels
+# 2. Extract posterior draws for predator speed
 # =======================================================================
 
-# a -> Compare novices vs intermediate
-# b -> Compare intermediate with advanced
-# c-> Compare novices with advanced
+# Extract values --------------------------------------------------------
 
-
-# Extract the posterior samples -----------------------------------------
-
-dt <- data.table(
+# individual means
+draws <- data.table(
   as_draws_df(
     fit,
-    variable = c("b_", "sd"),
-    regex = TRUE
-  )
+    variable = c(
+      "r_predator_id__sigma_speed",
[…]

### 2024-11-26 code/04_code_figures/figure3-c.R

@@ -1,6 +1,6 @@
 # =======================================================================
 
-#               Code to produce Appendix 3 : Figure S2                  #
+#                       Code to produce Figure 3 C                      #
 
 # =======================================================================
 
@@ -18,7 +18,7 @@ library(ggplot2)
 library(data.table)
 
 path <- file.path(getwd(), "outputs", "01_outputs_models")
-fit <- readRDS(file.path(path, "B1_DHMLM.rds"))
+fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
 
 # =======================================================================
 # =======================================================================
@@ -105,6 +105,7 @@ tab <- unique(
 
 tab[, c(2:8) := round(tab[, c(2:8)], digits = 2)]
 
+
 names <- c(
   "mean speed\n IIV speed", "mean speed\n mean prey speed",
   "IIV speed\n mean prey speed", "mean speed\n IIV prey speed",
@@ -114,12 +115,14 @@ names <- c(
 )
 tab[, variable_adv := names]
 
+
 # One of the correlations' sign has reversed.
 # Need to update to have absolute difference
-tab[7, c(2:8) := tab[7, c(2:8)] - 0.18]
+tab[7, c(2:8) := tab[7, c(2:8)] - 0.10]
 
 # =======================================================================
 # =======================================================================
+
 
 
 
@@ -139,6 +142,22 @@ colors <- c(
 )
 
 scaleFUN <- function(x) sprintf("%.2f", x)
+
+custom_theme <- theme(
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(
+      face = "plain", size = 11,
+      color = "black"),
+    axis.text.y = element_text(
+      face = "plain", size = 13,
+      color = "black"),
+    axis.title = element_text(size = 15, face = "plain", color = "black"),
+    panel.grid = element_blank(),
+    legend.position = "bottom",
+    legend.key = element_rect(fill = "transparent"),
+    legend.title = element_text(size = 15),
+    legend.text = element_text(size = 13)
+  )
 
 fig <- ggplot(
   tab,
@@ -184,22 +203,7 @@ fig <- ggplot(
     values = colors
   ) +
   theme_bw() +
-  theme(
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(
-      face = "plain", size = 11,
-      color = "black"),
-    axis.text.y = element_text(
[…]

### 2024-11-26 code/04_code_figures/figure3.R

@@ -1,384 +1,0 @@
-# =======================================================================
-
-#          Plot distribution of players from novice to advanced         #
-
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 1. Prepare the script
-# =======================================================================
-
-
-# Load libraries and model ----------------------------------------------
-
-# Libraries
-library(brms)
-library(data.table)
-library(ggplot2)
-library(ggpubr)
-library(ggridges)
-
-# import model
-path <- file.path(getwd(), "outputs", "01_outputs_models")
-fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
-
-
-
-# Load data ------------------------------------------------------------
-
-# Data
-data <- fread("./data/FraserFrancoetal2023-data.csv",
-              select = c("predator_id",
-                         "cumul_xp_pred",
-                         "pred_speed"))
-
-# Predator id as factor
-data[, predator_id := as.factor(predator_id)]
-
-# =======================================================================
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 2. Extract posterior draws for predator speed
-# =======================================================================
-
-# Extract values --------------------------------------------------------
-
-# individual means
-draws <- data.table(
-  as_draws_df(
-    fit,
-    variable = c(
-      "r_predator_id__sigma_speed",
-      "r_predator_id__speed"
-    ),
-    regex = TRUE)
-)
-
-# Remove columns that are not needed
-draws <- draws[, .SD, .SDcols = ! names(draws) %like% "cor"]
-draws <- draws[, .SD, .SDcols = ! names(draws) %like% "interm"]
-draws <- draws[, .SD, .SDcols = ! names(draws) %like% "prey"]
-
-# =======================================================================
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 3. Prepare the draws table
-# =======================================================================
-
-
-# Reshape ---------------------------------------------------------------
-
-# Long format
-draws <- melt(draws,
[…]

### 2024-11-26 code/04_code_figures/figure4-c.R

@@ -1,226 +1,0 @@
-# =======================================================================
-
-#                       Code to produce Figure 4 C                      #
-
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 1. Load libraries and import model
-# =======================================================================
-
-# Load libraries
-library(brms)
-library(ggplot2)
-library(data.table)
-
-path <- file.path(getwd(), "outputs", "01_outputs_models")
-fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
-
-# =======================================================================
-# =======================================================================
-
-
-
-
-
-# =======================================================================
-# 2. Estimate differences between novices and advanced levels
-# =======================================================================
-
-# Prepare the draws -----------------------------------------------------
-
-cors <- as_draws_df(fit, variable = "cor", regex = TRUE)
-cors <- data.table(cors)
-cors <- cors[, !c(".chain", ".iteration", ".draw")]
-
-cors <- melt(cors)
-cors <- cors[!(variable %like% "prior")]
-
-cors1 <- cors[!(variable %like% "interm")]
-cors1 <- cors1[!(variable %like% "novice")]
-cors2 <- cors[!(variable %like% "interm")]
-cors2 <- cors2[!(variable %like% "advanced")]
-
-setnames(cors1, c("variable", "value"), c("variable_adv", "value_adv"))
-setnames(cors2, c("variable", "value"), c("variable_nov", "value_nov"))
-
-
-
-# Compute the differences -----------------------------------------------
-
-# Compute the difference in absolute values
-# since the signs of the correlations do not change
-tab <- cbind(cors1, cors2)
-tab[, difference_cor := abs(value_adv) - abs(value_nov)]
-
-
-# Intervals
-lower_95 <- function(x) {
-  coda::HPDinterval(as.mcmc(x), 0.95)[1]
-}
-upper_95 <- function(x) {
-  coda::HPDinterval(as.mcmc(x), 0.95)[2]
-}
-
-lower_80 <- function(x) {
-  coda::HPDinterval(as.mcmc(x), 0.80)[1]
-}
-upper_80 <- function(x) {
-  coda::HPDinterval(as.mcmc(x), 0.80)[2]
[…]

### 2024-11-26 manuscript/manuscript.Rmd
update manuscript

@@
 ---
-title: "Experience shapes individual foraging specialization and success in a virtual predator-prey system"
+title: "Individual foraging specialization and success change across experience in a virtual predator-prey system"
 output: 
@@
 
-The capacity of predators to match their tactic to their prey is expected to drive the outcome of predator-prey interactions.
-To do so, predators need to practice their tactics extensively to develop the skills to be successful hunters, which may result in individual foraging specialization.
-Yet, there are limited empirical assessments showing links between experience, foraging specialization, and hunting success at the individual level, due to the challenges of monitoring direct interactions in the wild.
-Here, we used a virtual predator-prey system (the game *Dead by Daylight*) to investigate how experience shapes individual foraging specialization and success in predators across repeated interactions with their prey.
-We show that predators optimized prey consumption as they gained experience.
-Prey speed was an important mediator of this relationship, resulting in differences among predators in the development of expertise.
-Throughout experience, 68% of predators became either increasingly specialized by always moving at a fast pace, or flexible by switching between slow and fast speeds.
-The predators’ strategies were partially matched to the preys’ speed, suggesting that changes in hunting behaviour were driven by repeated encounters with prey.
+The capacity of predators to match their tactic to their prey and to optimize their skills at implementing a given tactic are expected to drive the outcome of predator-prey interactions.
+Hence, successive interactions of predators with their prey may result in increased flexibility in tactic use or in individual foraging specialization.
+Yet, there are limited empirical assessments showing links between past experience, foraging specialization, and hunting success at the individual level, due to the challenges of monitoring direct interactions in the wild.
+Here, we used a virtual predator-prey system (the game *Dead by Daylight*) to investigate how individual predator foraging specialization and success developed across repeated interactions with their prey.
+We found that 68% of predators became either increasingly specialized by always moving at a fast pace, or flexible by transitioning between slow and fast speeds.
+The predators' strategies were partially matched to their prey's speed, suggesting that changes in hunting behaviour were driven by repeated encounters with their prey.
 Flexible and specialist foragers achieved similar success overall.
-Our findings suggest that experience may be mechanism promoting behavioural diversification in predator-prey systems.
+Hence, our findings suggest that experience may promote behavioural diversification in predator-prey systems.
 
@@
 This results in reciprocal interactions where predators fine-tune their tactics to their prey, suggesting that they learn and become efficient hunters through repeated encounters [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
-These behavioural adjustments with experience can shape the outcome of predator-prey interactions, and may have larger implications for community and ecosystem dynamics [@wooster.etal2023].
+These behavioural adjustments with experience can shape the outcome of predator-prey interactions and may have larger implications for community and ecosystem dynamics [@wooster.etal2023].
 
-Empirical studies on human and non-human hunters show that individuals optimize foraging efficiency (e.g.
-search and handling times, return rates) by learning associative images or prey and environmental cues [@edwards.jackson1994;@morse2000;@macdonald2007;@reid.etal2010;@wilson-rankin2015].
-As predators practice and refine their tactics, they acquire expertise (e.g.
-skills, knowledge) that allows them to outperform novice hunters [@dukas2019;@wooster.etal2023].
-Through this process, it is hypothesized that individuals will gradually specialize in a foraging tactic (e.g.
+As predators acquire experience, theory suggests that individuals should gradually specialize in a foraging tactic (e.g.
 always moving fast) if it allows them to maintain successful prey captures at each attempt [@tinker.etal2009;@dukas2019].
@@
 Such conditions favor specialist hunters because there would be higher costs to switch tactics for the same type of prey.
-An alternative hypothesis is that learning is a mechanism driving behavioural flexibility.
-For instance, predators can gain expertise and information on their prey through repeated hunting atempts, and may hunt optimally by learning to adjust their tactic to the type of prey that they encounter [@stephens1993;@ishii.shimada2010;@kelley.magurran2011].
-While there are costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010;@mathot.etal2012].
+An alternative hypothesis is that learning could increase behavioural flexibility.
+For instance, predators can gain expertise and information on their prey through repeated hunting attempts, and may hunt optimally by learning to adjust their tactic to the type of prey that they encounter [@stephens1993;@ishii.shimada2010;@kelley.magurran2011].
+While there can be costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010;@mathot.etal2012].
 Nonetheless, complex feedback between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize with experience [@stephens1993;@ishii.shimada2010;@vilapouca2021;@beyts2023].
@@
 For example, @szopa-comley.ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
-Prey that use fast escapes are also proven to be more difficult to hunt [@walker.etal2005;@kelley.magurran2011;@martin.etal2022], and predators that exclusively encounter such prey should benefit from learning to specialize in fast pursuits.
-If predators that hunt in different environments adjust their tactics to local prey fluctuations, then specialist and flexible hunters can both attain similar hunting success and coexist [@phillips.etal2017].
-Therefore, empiricists should investigate the link between foraging specialization and success across time and contexts.
+Prey using fast escapes are also more difficult to hunt [@walker.etal2005;@kelley.magurran2011;@martin.etal2022], and predators that encounter such prey more often should benefit from specializing in fast pursuits.
+Therefore, if predators hunting in different environments adjust their tactics to local prey fluctuations, then specialist and flexible hunters can both achieve similar hunting success and coexist [@phillips.etal2017].
+Empiricists should thus investigate the link between foraging specialization and success across time and contexts.
 
-A recurring challenge impeding research on predator-prey behavioural interactions is the need to collect data simultaneously on both the predator and the prey.
-Similar to agent-based simulations, online videogames can be useful systems to mitigate these challenges and test specific ecological hypotheses.
-They provide controlled virtual environments with the advantage of having real players that interact in the virtual space.
-For example, in the predator-prey videogame *Dead by Daylight*, four prey players need to forage for resources while avoiding predation by a fifth player.
-In this virtual system, the predator population is composed of individuals that either ambush or hunt at high speeds (i.e.
-mean movement speed along a slow-fast continuum), and their success is driven by the movement of the prey [@fraserfranco.etal2022].
-We found that prey can increase their chances of survival by cooperating and moving fast when they forage [@cere.etal2021;@fraserfranco.etal2022, Santostefano et al.
-in press].
-Of course, the life of neither the predator nor the prey players are at stake, such that emerging patterns could be driven by their motivation to win and not "true" survival.
-Yet, the game ellicits natural reactions in players such as fear from predation (personal observations), which corroborates with another virtual ecological study showing that predation drives individual variation in risk perception [@beauchamp2020].
-In a different system, @lymbery.etal2023 showed that complex environments favor strong soldiers over large armies in a virtual game as well as in the laboratory with two ant species.
-These observations outline how ecological patterns can emerge from interactions in virtual systems with fixed rules.
-Videogames also generate large volumes of data on interacting players throughout their lifetime in the game under realistic, controlled, and repeatable ecological scenarios.
-Hence, virtual systems such as *Dead by Daylight* offer the opportunity to tackle fundamental questions about the role of experience on predator-prey interactions.
+In this study, we investigate how repeated experience shapes predator foraging specialization and success using data from players in *Dead by Daylight*.
+In this videogame, four prey players forage for resources while avoiding predation by a fifth player.
+The predator population is composed of individuals that either move at slow speeds and ambush or hunt at high speeds (i.e.
+mean movement speed describes an ambush-cursorial continuum of hunting tactics) [@@fraserfranco.etal2022].
+We also observed that predators acquire expertise through extensive practice, which is driven by the movement of the prey [@fraserfranco.etal2024].
+Indeed, the prey can increase their chances of survival by moving faster in the virtual environment [@fraserfranco.etal2022;@fraserfranco.etal2024].
 
-In this study, we assess how repeated experience shapes predator foraging specialization and success using data from players in *Dead by Daylight*.
-Following @fraserfranco.etal2022 we use the predators' mean movement speed along a slow-fast continuum as a proxy for the foraging tactic (ambush-cursorial), and define the level of individual foraging specialization as the intra-individual variance (i.e.
-IIV) in movement speed across matches, where low IIV translates to individual foraging specialization (e.g.
-always using a cursorial tactic).
-First, we investigate how individual hunting success changes with experience (i.e.
-how individuals develop their hunting expertise).
-We hypothesize that the predators' success will increase with experience up to a certain level where it will stagnate.
-We expect this pattern to vary among individuals due to differences in prey encounters.
-Second, we assess how foraging specialization emerges with experience.
-If all predators encounter similar groups of prey, we predict that individuals (and thus the population) should all specialize in similar speeds.
-In contrast, if all predators encounter varying groups of prey, then they should all converge towards flexible speeds.
+We define the level of individual foraging specialization as the intra-individual variance (i.e.
+IIV) in movement speed across matches.
+Low IIV describes individual foraging specialization (i.e.
+always using an ambush or cursorial tactic), whereas high IIV describes a flexible use of foraging tactics (i.e.
+predators switching between an ambush and cursorial tactic).
+Here, our objective is to assess how foraging specialization emerges throughout experience at the population and individual level.
+If all predators encounter similar groups of prey, we predict that individuals (and thus the population) should all specialize on moving at similar speeds.
+In contrast, if all predators encounter varying groups of prey, then they should converge towards flexible speeds.
 In both scenarios, differences among individuals in IIV across experience should be low (i.e.
@@
 Alternatively, differences among individuals in foraging specialization may emerge if they experience different interactions with their prey.
-In this case, we expect predators that encountered similar groups of prey across experience to specialize in similar speeds, while predators that encountered heterogeneous groups across matches should adopt flexible movement speeds, resulting in an increase in among individual differences in IIV with experience.
+In this case, we expect predators that encountered similar groups of prey across experience to specialize on similar speeds, while predators that encountered heterogeneous groups across matches should adopt flexible movement speeds, resulting in an increase in among individual differences in IIV with experience.
 If we detect such prey-dependent fine-tuning with experience, then all hunters along the flexible-specialist continuum should attain equal success.
@@
 
-*DBD* is a survival asymmetric multiplayer online game (i.e.
-a game where the gameplay mechanics differ between two groups) developed by Behaviour Interactive Inc, in which players can play either as a predator or a prey.
-Every match includes only one predator and four prey.
-The objective of the predator is to hunt and capture the prey, and the objective of the prey is to search for resources while avoiding the predator.
-The resources are in the form of power generators that, once all activated, will enable the prey to escape through one of two exit doors.
-The composition of the predator and prey group in a match is determined by a skill-based matchmaking algorithm.
-A match ends when the predator kills all the prey available (i.e.
-that have not escaped), or when the last remaining prey escapes the virtual environment.
-Each player, predator or prey, can choose an avatar with abilities that encourage specific play styles (e.g.
-bold vs cautious prey, or ambush vs roaming predator).
-During our study period, the game offered `r toString(format(length(unique(dat$avatar_id))))` predator avatars.
-The virtual environments are composed of fixed and procedurally generated habitat components, such as vegetation, mazes, and buildings.
-Some of these environments are larger than others, with varying structural complexity.
-However, predators display only minimal changes in behaviour and hunting success across the environments, probably due to a game feature enabling them to have visual cues of the generators [@fraserfranco.etal2022].
-There were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for play during the study period.
+*DBD* is an asymmetric multiplayer survival game developed by Behaviour Interactive Inc.
+In this game, participants take on roles as either a predator or one of the prey, with each match consisting of one predator and four prey.
+A matchmaking system pairs groups of players with similar skill such that individuals should all have similar experience.
+The predator's primary goal is to hunt and capture the prey, while the prey aim to locate and collect resources in the form of power generators.
+When all generators are activated, the prey can escape through one of two exit gates and win the match.
+A match concludes when the predator eliminates all remaining prey that have not escaped or when the final prey successfully exits the virtual environment.
+Players, whether predator or prey, select avatars with distinct abilities tailored to specific playstyles (e.g.
+stealthy vs evasive prey, or stalking vs patrolling predators).
+During the study period, the game featured `r toString(format(length(unique(dat$avatar_id))))` predator avatars.
+The virtual environments in the game vary in size and structural complexity, combining fixed and procedurally generated elements such as vegetation, buildings, and maze-like structures.
+Troughout the study period, there were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for gameplay.
 
@@
 
-The videogame company provided data that spanned a period of 6 months of gameplay recorded for every player from `r toString(format(min(dat$date)))` to `r toString(format(max(dat$date)))`.
-We only analyzed matches where players did not know each other (i.e.
-"Online" mode).
-We filtered any matches where players were inactive, such as when mean distances traveled per second (i.e.
-speed) were equal to, or very close to, zero.
-Moreover, we used our knowledge of the game to remove any matches where players were potentially hacking, or not playing the game as intended.
-We then sampled players that played 300 matches or more, and monitored all their matches from the first to a maximum of 500 matches.
+The videogame company provided six months of gameplay data, encompassing all player activity from `r toString(format(min(dat$date)))` to `r toString(format(max(dat$date)))`.
+We focused exclusively on matches played in "Online" mode, where players were strangers to one another.
+We excluded matches where players were inactive, as indicated by mean movement speeds that were zero or nearly zero.
+Additionally, matches where players were suspected of hacking or engaging in unintended gameplay behavior were also removed based on our knowledge of the game mechanics.
+We then selected a cohort of players that played 300 matches or more, and monitored all their matches from the first to a maximum of 500 matches.
 
-Our population consists of `r toString(format(length(unique(dat$predator_id))))` predator players with a total record of `r toString(formatC(length(unique(dat$match_id)), big.mark = " "))` matches.
-The predator-players' experience varied between `r toString(format(min(dat$total_xp_pred)))` and `r toString(format(max(dat$total_xp_pred)))` matches played.
-These matches lasted between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)` min (mean = `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)` min).
-The following information is collected and reported for every match : the player's anonymous ID, its avatar (i.e.
-the predator character chosen with its specific skill-gameplay mechanics), the game environment, the predator-player's experience along with its speed, the mean speed of the groups of prey the player encountered, and their mean rank (a proxy for prey skill).
-The ranking system in *DBD* was implemented by the company to pair players in a match based on their skill (https://deadbydaylight.fandom.com/wiki/Rank), and failing to account for it would prevent us from detecting a change in the predator's foraging success with experience.
+Our dataset includes `r toString(format(length(unique(dat$predator_id))))` unique predator players, collectively accounting for `r toString(formatC(length(unique(dat$match_id)), big.mark = " "))` matches.
+The number of matches played by predator players ranged from `r toString(format(min(dat$total_xp_pred)))` to `r toString(format(max(dat$total_xp_pred)))`.
+Match durations varied between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)` minutes, with an average duration of `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)` minutes.
+The following details were recorded for each match: the anonymous player ID, the chosen predator avatar, the game environment, the predator's level of experience, their speed, the average speed of the prey group they encountered, and the average rank of those prey (used as a proxy for prey skill).
+The game's ranking system, designed to match players of similar skill levels (https://deadbydaylight.fandom.com/wiki/Rank), was incorporated into our analysis to detect any relationship between predator experience and foraging success [see @fraserfranco.etal2024].
 
@@
 We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
-Lastly, we defined the predator's cumulative experience as the number of matches played as the predator prior to the match being monitored.
-For example, the first match of a player would have a cumulative experience value of 0, while the tenth match would have a value of 9.
-We did not account for matches where predators played as the prey.
-We also categorized predators for each match based on their cumulated experience.
-We labeled predators as novices for matches where they had cumulated less than 100 matches, intermediate for matches where they had cumulated between 100 and 299 matches, and advanced for matches where they had cumulated more than 299 matches (max 499).
+Lastly, we categorized predators for each match based on their cumulated experience [see @fraserfranco.etal2024].
+We labeled predators as novices for matches where they had cumulated less than 100 matches, intermediate for matches where they had cumulated between 100 and 299 matches, and advanced for matches where they had cumulated more than 299 matches (max 500).
 Since our goal was to monitor predator players throughout their experience and that they all played at least 300 matches, they all appeared in each of the three experience categories.
 
-We recognize that we could have biased our analyses by retaining only individuals who played for at least 300 matches.
-For example, these individuals might be experienced videogame players and could thus already be playing like experts in their first matches in *DBD*.
-To verify that our sample was not biased, we compared a random sample of players that played either 20 to 50 matches, 51 to 100 matches, or 101 to 300 matches during the same timeframe as our sampled population.
-We then took the first 20 matches played by these players, including those from our sampled population, and compared their mean speed using a Bayesian hierarchical linear model.
-We found that all four groups had similar mean speeds as predators (Appendix 2: Table S1-S2), which indicates an absence of bias due to data sampling.
-
 ## Statistical analyses
-
-### Software and computer specifications
-
-All models were fitted under a Bayesian framework in R (version 4.1.2) using Markov chain Monte Carlo (MCMC) sampling with the package "brms" version 2.16.3 [@burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@gabry.cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
-The models were run on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
-Each required 64GB of RAM with 48 cores to compile within 5 days.
-
-### Development of expertise
-
-We tested how prey influenced the development of predator expertise by computing five Bayesian generalized additive mixed models (GAMM) with thin-plate regression splines, all of which estimated the relationship between hunting success (i.e.
-number of prey consumed) and the predators' cumulative experience (i.e.
-number of matches played before the current match).
-We parametrized the models following the method of @pedersen.etal2019.
-The first model was the simplest, with a common global smoothing function and random intercepts for the predator ID.
-In this model, we assume that predators have the same development of expertise, with the model estimating a trend for the average individual (i.e.
-global smoother).
-For the second model, we included varying individual smoothers for the predator ID.
-Here, we assume that individual predators share a similar relationship between success and experience, but that this relationship can vary among them (e.g.
-predator 1 has a steeper curve than predator 2).
-This enabled us to test whether predators differed in the development of their expertise.
-In the third model, we kept the individual smoothers for the predators, but removed the global smoother.
-This model assumes that predators do not share a common relationship between success and experience.
-The fourth and fifth models were reproductions of the second and third models respectively, where we included the prey speed to assess its effect on the relationship between success and experience.
-We included the standardized match duration and prey rank as covariates in all five models.
-
-We computed the five models using a modified version of the beta-binomial distribution implemented in "brms".
-Hunting success was estimated as the probability of consuming the four prey ($\mu_i$), drawn from a Beta distribution ($Beta(\mu_i, \phi)$) with mean ($\mu \in [0,1]$) and precision ($\phi > 0$) parameters.
-We used a logit link function to estimate $\mu_i$ where $\mu_i = \frac{exp(\eta_i)}{exp(\eta_i) + 1}$ and $\eta_i$ is the linear predictor, while the precision parameter ($\phi$) was estimated with an identity link.
-We used the default number of basis functions (K) in "brms" for the models to estimate the relationship between hunting success and experience.
-We assumed that the random intercepts for the predator ID ($id$) followed a Gaussian distribution with estimated standard deviation ($id \sim N(0,\ I\ \sigma_{id}^{2})$).
-We used weakly informative Gaussian priors for the intercept ($N(0,\ 0.5^{2})$) and the global trend of cumulative experience ($N(0,\ 2^{2}))$).
-Following @fraserfranco.etal2022, we defined a positive Gaussian prior on the precision parameter ($N(2,\ 0.5^{2})$), a positive Gaussian prior ($N(1,\ 0.5^{2}))$) on the game duration because longer trials lead to greater success, and a negative Gaussian prior on prey speed ($N(-1,\ 0.5^{2})$) because encountering faster prey is associated with lower success in this system.
-We employed weakly informative half-Gaussian priors on all the standard deviation parameters ($N(0,\ 0.5^{2})$).
-We compared the models' predictive accuracies using approximate leave-one-out cross-validation with Pareto-smoothed importance sampling [@vehtari.etal2017;@piironen.vehtari2017;@vehtari.etal2022].
 
@@
 
+We performed our analyses under a Bayesian framework.
 We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1^{2})$: eqn.
@@
 
-After inspection of the results, we found that key parameter values for our hypotheses were in the direction of our predictions, but they were largely driven by the very slow speed of one predator.
-Removing this individual reduced the estimates by a significant margin.
-To remain conservative, we thus present the results of the model without this individual in the main text, and provide the results of the model including it in the Appendix S3.
+### Model specifications
 
-### Markov Chain Monte Carlo settings
+We fitted the model in R (version 4.1.2) using Hamiltonian Monte Carlo (HMC) sampling with the package "brms" version 2.16.3 [@burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@gabry.cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
+We ran te model on on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
 
-We parametrized the GAMMs and the MDHGLM to run four MCMC chains with 1000 posterior samples for each parameter.
-We ran 2500 iterations with a thinning set to eight for the additive model with a global smoother only (see Table 1), and 1500 iterations with a thinning set to four for the other additive models.
-We set the first 500 iterations in each model as warm ups.
-We parametrized the MDHGLM to run 2500 iterations with a thinning set to eight, with the first 500 iterations used as warm ups.
-We assessed the convergence of the MCMC chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@vehtari.etal2021].
+We parametrized the MDHGLM to run 2500 iterations with a thinning set to eight, with the first 500 used as warm up iterations (yielding 1000 posterior samples for each parameter).
+We assessed the convergence of the chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@vehtari.etal2021].
 We also performed posterior predictive checks which showed an adequate fit of the models (for details, see https://github.com/quantitative-ecologist/experience-hunting-tactics).
@@
 
+After inspection of the results, we found that key parameter values for our hypotheses were in the direction of our predictions, but they were largely driven by the very slow speed of one predator.
+Removing this individual reduced the estimates by a significant margin.
+To remain conservative, we thus present the results of the model without this individual in the main text, and provide the results of the model including it in the Appendix 2.
+
 # RESULTS {.unnumbered}
-
-## Development of expertise
 
@@
 path <- file.path(here::here("outputs", "03_outputs_model-processing"))
-percent_tab1 <- data.table(readRDS(file.path(path, "GAMM_percentages.rds")))
+
 percent_tab2 <- data.table(readRDS(file.path(path, "DHMLM_percentages.rds")))
-
-#fit1 <- readRDS(here::here("outputs", "01_outputs_models", "A2_GAMM-rank.rds"))
-#fit2 <- readRDS(here::here("outputs", "01_outputs_models", "A2_GAMM-speed-rank.rds"))
-#
-#fit1
-#fit2
-```
-
-Out of all five GAMM models, two predicted the data the best and achieved similar expected log pointwise densities (elpd).
-Both models accounted for the prey group's rank and speed (Table 1).
-Models in which these effects were not accounted for resulted in no change in hunting success with experience (i.e.
-expertise) for the average individual (results not shown).
-Accounting for the prey rank resulted in a concave-shaped relationship, with the highest success ranging between 100 and 400 matches (Figure 1A).
-In the model where we additionally included the prey's speed, the effect of experience on hunting success for the average individual followed a diminishing returns curve, with predators optimizing their success after playing ~300 matches (Figure 1C).
-The curve shows there was a 38% increase in the probability of consuming all prey for the average individual between the first and the ~330$^{th}$ match where success reached a plateau (Figure 1C).
-
-```{r table1, ft.align = "left"}
-
-# ===========================================================================
-# 1. Import the model fit
-# ===========================================================================
-
-# Open the loo table
-path <- file.path(here::here("outputs", "02_outputs_model-validation"))
-loo_tab <- data.table(readRDS(file.path(path, "GAMM_loo-cv-table.rds")))
-
-# Add model column
-loo_tab[
-  , model := c(
-    "predator xp + ID smoothers + prey rank + prey speed",
-    "ID smoothers + prey rank + prey speed",
-    "ID smoothers + prey rank",
-    "predator xp + ID smoothers + prey rank",
-    "predator xp + prey rank"
-    )
- ]
-
-# Reorder columns
-loo_tab <- loo_tab[, c(9, 1:8)]
-
-# ===========================================================================
-# ===========================================================================
-
-# ===========================================================================
-# 2. Compute the table using flextable
-# ===========================================================================
-
-# Prepare the table parameters ----------------------------------------------
-
-# Custom header
-my_header <- data.frame(
-   col_keys = c("model",
-                "elpd_diff",
-                "se_diff",
-                "elpd_loo",
-                "se_elpd_loo"),
-   line1 = c("model",
-             "elpd \ndifference",
-             "sd \ndifference",
-             "elpd loo \nvalue",
-             "elpd loo \nstandard error"),
-   stringsAsFactors = FALSE
-)
-
-# Custom theme
-my_theme <- function(x, ...) {
-   x <- colformat_double(x, big.mark = " ",
-                         decimal.mark = ".",
-                         digits = 2)
-   x <- set_table_properties(x, layout = "autofit")
-   x <- border_remove(x)
-   std_border <- fp_border(width = 1, color = "black")
-   x <- hline_top(x, part = "all", border = std_border)
-   x <- hline_bottom(x, part = "all", border = std_border)
-}
-
-# Create the table ----------------------------------------------------------
-
-tab1 <- loo_tab %>%
-  select(model, elpd_diff, se_diff, elpd_loo, se_elpd_loo) %>%
-  flextable(col_keys = my_header$col_keys) %>%
-  set_header_df(mapping = my_header, key = "col_keys") %>%
-  my_theme() %>%
-  align(align = "left", part = "all", j = 1) %>%
-  align(align = "center", part = "all", j = 2) %>%
-  align(align = "center", part = "all", j = 3) %>%
-  align(align = "center", part = "all", j = 4) %>%
-  align(align = "center", part = "all", j = 5) %>%
-  footnote(
-    i = 1, j = 1,
-    part = "header",
-    value = as_paragraph(
-      as_sup("a "),
-      "'elpd' refers to the expected log pointwise density and is the value chosen to select the best model.",
-      as_sup("\nb "),
-      "'xp' is an acronym for experience"),
-    ref_symbols = " "
-  ) %>%
-
-  # Table caption
-  set_caption(
-    caption = "Table 1. Leave-one-out cross-validation table of the five GAMMs relating hunting success to predator experience.",
-    style = "Table Caption"
-  ) %>%
-
-  # Font options
-  font(fontname = "Times New Roman", part = "all") %>%
-  fontsize(size = 10, part = "all") %>%
-  fontsize(size = 12, part = "footer")
-
-tab1
-# ===========================================================================
-# ===========================================================================
-
-```
-
-The relationship between hunting success and cumulative experience differed among predators (Figure 1B-D).
-Only `r toString(scales::percent(percent_tab1[2,]$percentage, accuracy = 0.1))` of the population had an increase in success from the first match to the last in the model where we did not account for the prey's speed and rank (Appendix S1: Figure S1A).
-In contrast, accounting for both effects resulted in `r toString(scales::percent(percent_tab1[5,]$percentage, accuracy = 0.1))` of the population increasing its success with experience from the first match to the last.
-The prey speed alone also mediated individual differences in the relationship between success and experience.
-The standard deviation of the individual slopes component of the model accounting only for prey rank was equal to 9.72 (9.30, 10.15 $95\%\ CI$), while the one for the model accounting for prey rank and speed was equal to 3.36 (3.04, 3.71 $95\%\ CI$), indicating that individual differences in the development of expertise decreased when accounting for prey speed.
-
-```{r fig1, out.width = "100%", fig.cap = "**Figure 1**.
-Median posterior predictions of the development of predator hunting expertise.
-The predators' hunting success (i.e.
-the probability of consuming the four prey) is on the y axis, and the predators' cumulative experience (i.e.
-the number of matches played prior to each observation) is on the x axis.
-Panels A and C show the development of expertise for the average individual with the vertical dashed lines on the left representing the lowest predicted values.
-For panel A, the right-side vertical dashed line shows the highest predicted success.
-For panel C, the right-side dashed line represents the point on the curve where success was optimized, which we calculated using the finite differences method to obtain the first derivative of the predicted values.
-Panels B and D show among individual differences in the development of expertise, with each curve representing an individual predator.
-(A-B) GAMM where we control for the prey rank (C-D) GAMM where we control for the prey rank and the speed of the prey group."}
-
-knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure1.png")
-)
 
@@
 
-The mean speed of the predator population remained stable with experience (Figure 2 and Appendix S1: Table S1).
-Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix S1: Table S1).
-At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix S1: Table S2).
-However, they displayed important differences in foraging specialization (Appendix S1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in among individual differences in IIV from novice to advanced (Figure 2).
+The mean speed of the predator population remained stable with experience (Figure 2 and Appendix 1: Table S1).
+Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix 1: Table S1).
+At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix 1: Table S2).
+However, they displayed important differences in foraging specialization (Appendix 1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in among individual differences in IIV from novice to advanced (Figure 1).
 `r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e.
->0.2 change in standard deviation; Figure 3).
+>0.2 change in standard deviation; Figure 2).
 In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e.
@@
 
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2**.
+```{r fig1, out.width = "100%", fig.cap = "**Figure 1**.
 Median posterior differences and HPD intervals comparing predator foraging behaviour at the population and individual level across experience stages.
@@
 
-As the predator population gained experience, there was strong evidence that the prey increased their speed, although slightly (Figure 2 and Appendix S1: Table S1).
-The population also encountered groups of prey using different speeds through time (Figure 2 and Appendix S1: Table S1).
-At the individual level, all predators encountered prey with similar average speeds throughout experience (Figure 2 and Appendix S1: Table S2).
-Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix S1: Table S2).
+As the predator population gained experience, there was strong evidence that the prey increased their speed, although slightly (Figure 1 and Appendix 1: Table S1).
+The population also encountered groups of prey using different speeds through time (Figure 1 and Appendix 1: Table S1).
+At the individual level, all predators encountered prey with similar average speeds throughout experience (Figure 1 and Appendix 1: Table S2).
+Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix 1: Table S2).
 Thus, some predators encountered similar groups (i.e.
@@
 some slower and some faster).
-These differences among individuals in IIV for prey encounters increased only marginally with experience (Figure 2).
+These differences among individuals in IIV for prey encounters increased only marginally with experience (Figure 1).
 
-Similar to the GAMMs, the predator population's mean hunting success increased with experience (Figure 2 and Appendix S1: Table S1), with mean prey consumption revolving around two prey.
-There were also important differences among individuals in mean hunting success (Appendix S1: Table S2), but they remained stable across experience (Figure 2).
+The predator population's mean hunting success increased with experience (Figure 1 and Appendix 1: Table S1), with mean prey consumption revolving around two prey.
+There were also important differences among individuals in mean hunting success (Appendix 1: Table S2), but they remained stable across experience (Figure 1).
 
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3**.
+```{r fig2, out.width = "100%", fig.cap = "**Figure 2**.
 Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
@@
 
-Predators that were on average faster had lower IIV in speed (Figure 4A-B and Appendix S4: Table S1).
+Predators that were on average faster had lower IIV in speed (Figure 3A-B).
 Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement.
-As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 units, from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 4C).
-Predators that were on average faster also tended to encounter groups of prey that were on average faster and more similar (Figure 4A-B and Appendix S4: Table S1).
-There was however no evidence that these correlations increased with experience (Figure 4C)
+As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 units, from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 3C).
+Predators that were on average faster also tended to encounter groups of prey that were on average faster and more similar (Figure 3A-B).
+There was however no evidence that these correlations increased with experience (Figure 3C)
 
-There was no correlation (-0.01 (-0.17, 0.09 $95\%\ CI$)) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.33, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 4C).
-The predators' IIV in speed and IIV in prey speed were weakly positively correlated (Figure 4A-B and Appendix S4: Table S1).
+There was no correlation (-0.01 (-0.17, 0.09 $95\%\ CI$)) between mean prey speed and IIV in predator speed when predators were novice (Figure 3A), but the correlation increased to -0.16 (-0.33, -0.04 $95\%\ CI$) at the advanced stage (Figure 3B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 3C).
+The predators' IIV in speed and IIV in prey speed were weakly positively correlated (Figure 3A-B).
 Hence, predators that encountered groups of prey with similar speeds tended to be more specialized in their tactic, while those that encountered groups of prey with varying speeds tended to be more flexible.
-We did not find evidence that this correlation increased with experience (Figure 4C).
+We did not find evidence that this correlation increased with experience (Figure 3C).
 
-```{r fig4, out.width = "100%", fig.cap = "**Figure 4**.
+```{r fig3, out.width = "100%", fig.cap = "**Figure 3**.
 Correlation matrices of the MDHGLM relating the mean and IIV in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
@@
 
-The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 4 and Appendix S4: Table S1), suggesting that slower/flexible and faster/specialist predators were overall both equally successful.
-There was however a slight increase in the correlation between the predator's IIV in speed and success (Figure 4C), suggesting that flexible foragers at the advanced stage were marginally less successful (Appendix S1: Figure S2).
-We also found strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 4A-B and Appendix S4: Table S1).
-Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B and Appendix S4: Table S1).
-Both relationships remained structurally stable across experience (Figure 4C).
+The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 3), suggesting that slower/flexible and faster/specialist predators were overall both equally successful.
+There was however a slight increase in the correlation between the predator's IIV in speed and success (Figure 3C), suggesting that flexible foragers at the advanced stage were marginally less successful (Appendix 1: Figure S2).
+We also found strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 3A-B).
+Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B).
+Both relationships remained structurally stable across experience (Figure 3C).
 
@@
 A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abrams2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that predators in *Dead by Daylight* increased their hunting success with experience, suggesting that predator expertise was honed through extensive practice.
-While there was no directional increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
-This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two with experience.
+By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that while predators in *Dead by Daylight* did not show any increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
+This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two across experience.
 The behavioural strategies of predators and prey tended to match across experience, suggesting that both were adjusting to each other.
@@
 Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.
-
-## The development of expertise
-
-Our results suggest that predator expertise is honed through extensive practice.
-The predator population increased and stabilized its success with experience in a diminishing returns fashion as it is typically found in empirical studies of expertise [reviewed in @dukas2019].
-The prey were important in mediating this pattern, probably because they increased their speed as predators gained experience.
-We previously showed in *DBD* that faster movement is an effective strategy used by the prey to avoid predation [@fraserfranco.etal2022], and other studies have found that as well [@walker.etal2005;@kelley.magurran2011;@martin.etal2022].
-This resulted in discernable differences in the relationship between success and experience among predators, implying that the development of expertise depends on an individual's capacity to adjust to difficulty.
-Hunting faster prey requires costly and specialized cognitive abilities and coordination [@kelley.magurran2011], and that could explain why such prey were more difficult to capture.
-Thus, predators that couldn't properly hunt at high speeds or develop counter-strategies for faster prey were likely at a disadvantage.
-
-However, even after we took the prey's speed into account, there were still important differences in expertise acquisition among predators, suggesting that other antipredator tactics were potentially involved.
-For example, if the prey used camouflage or hiding to avoid being detected, then predators may have found them only if they learned how to exploit the visual cues that facilitate cryptic prey detection, such as habitat characteristics or prey colour patterns [@ehlinger1989;@hughes.etal1992;@warburton2003;@szopa-comley.etal2020].
-In addition, longer time intervals between hunting events may delay or even impede learning due to forgetting important information [@endler1991;@wright.etal2022].
-In *DBD*, a predator that played 300 matches in the span of six months might forget more critical information related to prey detection or escape patterns than one that played 300 matches in the span of six days.
-Investigating the impact of such time lags in future analyses may reveal important insights on the outcome of predator-prey interactions.
-
-## Predator-prey interactions across experience
 
@@
 However, we observed that 44% of the predator population showed close to no change in specialization with experience.
-Since these individuals were already specialized as novices (Fraser Franco, personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they more often encountered faster prey.
+Since these individuals were already specialized as novices (Fraser Franco, personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they encountered faster prey more often.
 This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
@@
 However, there were still considerable differences in success among individuals through time, suggesting that some predators were limited in their capacity to match their tactic to their prey or to increase their success through other means.
-Specialist foragers were faster, and thus, probably better equipped to hunt the more difficult faster prey in *DBD*.
-However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in more difficult encounters for these predators, thereby decreasing the benefits of using this tactic (Figure 4).
+
+Specialist foragers were faster and probably better equipped to hunt the faster and more difficult prey in *DBD*.
+However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in challenging encounters for these predators too, thereby decreasing the benefits of using this tactic (Figure 3).
 Thus, specializing probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
-On the other hand, flexible foragers encountered variable prey with slower speeds.
+On the other hand, flexible foragers encountered a larger range of prey moving at slower speeds.
 Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for flexible hunters may have come at the cost of not being adept at capturing faster prey [@pintor.etal2014].
@@
 
-We found support of our prediction that prey were driving individual differences in expertise in a predator population.
-We also confirmed that experience and predator-prey encounters drove the patterns of individual foraging specialization.
+We found support for our prediction that individual foraging specialization changed across experience and predator-prey interactions.
 Our results suggest that predators learned with experience, as their success increased and their speed remained matched to the speed of their prey.
-Even though individuals were not all equally successful, both specialized and flexible hunters achieved similar success.
+Even though individuals were not all equally successful, both specialized and flexible hunters achieved similar success overall.
 A potential caveat is that the more flexible hunters might have experimented with various tactics out of boredom, which could impede ecologically realistic interpretations of our data.
@@
 One limitation of our study was that we couldn't monitor all the matches of the prey, which prevented us from assessing their responses to the predator through their experience.
-Hence, future studies should aim at monitoring reciprocal behavioural dynamics through time, which may reveal important insights on the mechanisms driving stable equilibria in predator-prey systems.
-Lastly, virtual systems are increasingly recognized as being useful to test hypotheses on ecological interactions [@beauchamp2020;@cere.etal2021;@fraserfranco.etal2022;@lymbery.etal2023].
-We therefore hope that our study will inspire more collaborations between scientists and the videogame industry to tackle fundamental questions in ecology.
+Hence, future studies should aim at monitoring reciprocal behavioural dynamics through time, which may reveal important insights on the mechanisms driving predator-prey systems.
 

### 2025-02-21 manuscript/manuscript.Rmd

@@
 The predator population is composed of individuals that either move at slow speeds and ambush or hunt at high speeds (i.e.
-mean movement speed describes an ambush-cursorial continuum of hunting tactics) [@@fraserfranco.etal2022].
+mean movement speed describes an ambush-cursorial continuum of hunting tactics) [@fraserfranco.etal2022].
 We also observed that predators acquire expertise through extensive practice, which is driven by the movement of the prey [@fraserfranco.etal2024].
@@
 knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure2.png")
+  here::here("outputs", "04_outputs_figures", "figure1.png")
 )
@@
 knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure3.png")
+  here::here("outputs", "04_outputs_figures", "figure2.png")
 )
@@
 knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure4.png")
+  here::here("outputs", "04_outputs_figures", "figure3.png")
 )
@@
 We also found strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 3A-B).
-Predators also had greater success across the study when encountering more variable groups of prey (Figure 4A-B).
+Predators also had greater success across the study when encountering more variable groups of prey (Figure 3A-B).
 Both relationships remained structurally stable across experience (Figure 3C).

### 2025-02-21 manuscript/manuscript.Rmd
updated correlation numbers in manuscript

@@
 Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement.
-As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 units, from -0.62 (-0.91, -0.41 $95\%\ CI$) for when predators were novices to -0.78 (-1.00, -0.53 $95\%\ CI$) as they reached the advanced stage (Figure 3C).
+As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 units, from -0.62 (-0.70, -0.55 $95\%\ CI$) for when predators were novices to -0.78 (-0.83, -0.72 $95\%\ CI$) as they reached the advanced stage (Figure 3C).
 Predators that were on average faster also tended to encounter groups of prey that were on average faster and more similar (Figure 3A-B).
@@
 
-There was no correlation (-0.01 (-0.17, 0.09 $95\%\ CI$)) between mean prey speed and IIV in predator speed when predators were novice (Figure 3A), but the correlation increased to -0.16 (-0.33, -0.04 $95\%\ CI$) at the advanced stage (Figure 3B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 3C).
+There was no correlation (-0.02 (-0.14, 0.01 $95\%\ CI$)) between mean prey speed and IIV in predator speed when predators were novice (Figure 3A), but the correlation increased to -0.16 (-0.27, -0.04 $95\%\ CI$) at the advanced stage (Figure 3B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 3C).
 The predators' IIV in speed and IIV in prey speed were weakly positively correlated (Figure 3A-B).

### 2025-02-21 code/04_code_figures/figure3-raw.R
updated correlations figure file

@@ -15,14 +15,15 @@
 
 # Load libraries and model data -----------------------------------------
 
- # Libraries
- library(brms)
- library(corrplot)
- library(export)
+# Libraries
+library(brms)
+library(corrplot)
+library(export)
+library(data.table)
 
- # Model
- path <- file.path(getwd(), "outputs", "01_outputs_models")
- fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
+# Model
+path <- file.path(getwd(), "outputs", "01_outputs_models")
+fit <- readRDS(file.path(path, "B1_DHMLM-no-outlier.rds"))
 
 # =======================================================================
 # =======================================================================
@@ -38,85 +39,85 @@
 
 # Extract the posterior correlations ----------------------------------------
 
- # Taken from fit
- corrs <- data.table(
-   as_draws_df(fit, variable = "^cor_", regex = TRUE)
- )
- # Remove MCMC columns
- corrs[, c(".chain", ".iteration", ".draw") := NULL]
- # Table to long format
- corrs1 <- melt(corrs)
+# Taken from fit
+corrs <- data.table(
+  as_draws_df(fit, variable = "^cor_", regex = TRUE)
+)
+# Remove MCMC columns
+corrs[, c(".chain", ".iteration", ".draw") := NULL]
+# Table to long format
+corrs1 <- melt(corrs)
 
 
 
 # Summarize posterior correlations --------------------------------------
 
- # HPD intervals functions
- lower_95 <- function(x) {
-   coda::HPDinterval(as.mcmc(x), 0.95)[1]
- }
- upper_95 <- function(x) {
-   coda::HPDinterval(as.mcmc(x), 0.95)[2]
- }
+# HPD intervals functions
+lower_95 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[1]
+}
+upper_95 <- function(x) {
+  coda::HPDinterval(as.mcmc(x), 0.95)[2]
+}
 
- # Summary of posterior
- corrs1[
-   , ":=" (
-     median_cor = median(value),
-     lower_95 = lower_95(value),
-     upper_95 = upper_95(value)
-   ),
-   by = variable
- ]
+# Summary of posterior
+corrs1[
+  , ":=" (
+    median_cor = median(value),
[…]

### 2025-03-17 manuscript/manuscript.Rmd
On Windows-->updated introduction. added fig1.

@@
 Predators express a diverse array of foraging tactics to capture their prey.
-In natural populations, differences among individuals in tactics such as ambushing and fast movement speeds are associated with differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
-Prey usually respond to predation cues by reducing their activity, or use rapid or unpredictable movements to successfully escape when they are chased [@walker.etal2005;@kelley.magurran2011;@herbert-read.etal2017].
-This results in reciprocal interactions where predators fine-tune their tactics to their prey, suggesting that they learn and become efficient hunters through repeated encounters [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
-These behavioural adjustments with experience can shape the outcome of predator-prey interactions and may have larger implications for community and ecosystem dynamics [@wooster.etal2023].
+In natural populations, individuals differ in the use of tactics such as ambushing and roaming, often resulting in differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
+This variation in foraging behaviour has been shown to emerge from reciprocal behavioural interactions between predators and their prey.
+For example, prey reduce their activity to avoid predators, while predators match their hunting tactic to their prey based on their profitability **add ref for pred** [@kelley.magurran2011].
+For a long time, these observations have prompted ecologists to hypothesize that predators learn from experience to become efficient hunters through repeated encounters and may unveil links between foraging specialization and prey capture [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
+Hence, while it remains challenging to monitor individual predator experience through time, uncovering how it shapes foraging behaviour is essential to predict hunting success because of its implications for community and ecosystem dynamics [@wooster.etal2023].
 
-As predators acquire experience, theory suggests that individuals should gradually specialize in a foraging tactic (e.g.
-always moving fast) if it allows them to maintain successful prey captures at each attempt [@tinker.etal2009;@dukas2019].
+Recent evidence suggests that resource fluctuations (e.g., temporal changes in prey behaviour) may be a key mechanism underlying the emergence of behavioural specialization with experience and its fitness consequences [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
+Theory suggests two contrasting scenarios with their outcome defined by the degree of resource variability.
+In the first scenario, individuals should gradually specialize in a foraging tactic (e.g., always moving fast) if it allows them to maintain successful prey captures at each attempt [@tinker.etal2009;@dukas2019].
 This should occur when predators learn to hunt in environments where resources are predictable (or stable) because they require less energy and time to search for, capture, and handle prey [@weimerskirch2007;@woo.etal2008;@potier.etal2015].
 Such conditions favor specialist hunters because there would be higher costs to switch tactics for the same type of prey.
-An alternative hypothesis is that learning could increase behavioural flexibility.
-For instance, predators can gain expertise and information on their prey through repeated hunting attempts, and may hunt optimally by learning to adjust their tactic to the type of prey that they encounter [@stephens1993;@ishii.shimada2010;@kelley.magurran2011].
-While there can be costs to attempt novel tactics by trial and error in stable environments, predators that hunt in environments under fluctuating resources can reduce the consequences of uncertainty by learning to switch hunting tactics [@dall2010;@mathot.etal2012].
-Nonetheless, complex feedback between ecological interactions and learning make it challenging to predict under which circumstances predators should specialize with experience [@stephens1993;@ishii.shimada2010;@vilapouca2021;@beyts2023].
+For example, habitat specialization under stable resources is associated with reduced foraging effort and increased offspring growth rates in Herring Gulls (*Larus argentatus*) [@vandenbosch.etal2019].
+In the second scenario, predators are expected to increase behavioural flexibility by using a variety of hunting tactics (i.e.
+generalists) when they hunt in highly variable environments.
+Indeed, while there can be costs to attempt novel tactics by trial and error, predators can reduce the consequences of uncertainty in environments under fluctuating resources by learning to adjust their tactic to the prey that they encounter [@dall2010;@mathot.etal2012;@stephens1993;@ishii.shimada2010;@kelley.magurran2011].
+@szopa-comley.ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
+Given these two scenarios, the relationship between individual foraging specialization and prey capture likely depends on a predator's ability to learn and adapt its hunting tactics to the prey it encounters.
+If predators can adjust their tactics to match the prey fluctuation regime they experience, then both specialist and generalist hunters should achieve similar hunting success and coexist [@phillips.etal2017].
+Empiricists should therefore examine how foraging specialization influences prey capture across time and different ecological scenarios.
 
-There is increasing evidence suggesting that the emergence of behavioural specialization and its fitness consequences are driven by resource fluctuations [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
-For example, @szopa-comley.ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
-Prey using fast escapes are also more difficult to hunt [@walker.etal2005;@kelley.magurran2011;@martin.etal2022], and predators that encounter such prey more often should benefit from specializing in fast pursuits.
-Therefore, if predators hunting in different environments adjust their tactics to local prey fluctuations, then specialist and flexible hunters can both achieve similar hunting success and coexist [@phillips.etal2017].
-Empiricists should thus investigate the link between foraging specialization and success across time and contexts.
+In this study, we use data from players in the online videogame *Dead by Daylight* to investigate 1) how repeated interactions with prey shape predator foraging specialization and 2) how the relationship between specialization and foraging success changes over time.
+*Dead by Daylight* simulates a predator-prey interaction across complex virtual environments, providing a system to test ecological hypotheses on foraging behaviour, group selection, and social interactions [reviewed in @montiglio2025].
+In this game, four prey players forage for resources while avoiding predation by a fifth player.
+The predator population is composed of individuals that vary consistently in their use of hunting tactics along an ambush-cursorial continuum: at one extreme hunters move more slowly and ambush prey; at the other extreme, hunters roam the virtual environment at high velocities [@fraserfranco.etal2022].
+Predators also acquire expertise through extensive practice, and the behaviour of the prey they encounter influences the rate at which they gain expertise [@fraserfranco.etal2024].
+To assess how foraging specialization emerges throughout experience, we define the level of individual foraging specialization as the intra-individual variance (i.e.
+IIV) in movement speed across matches following the definition by @cleasby.etal2015.
+Low IIV describes individual foraging specialization (i.e., always using an ambush or cursorial tactic) whereas high IIV describes a flexible use of foraging tactics (i.e., generalist predators switching between ambush and cursorial tactics).
 
-In this study, we investigate how repeated experience shapes predator foraging specialization and success using data from players in *Dead by Daylight*.
-In this videogame, four prey players forage for resources while avoiding predation by a fifth player.
-The predator population is composed of individuals that either move at slow speeds and ambush or hunt at high speeds (i.e.
-mean movement speed describes an ambush-cursorial continuum of hunting tactics) [@fraserfranco.etal2022].
-We also observed that predators acquire expertise through extensive practice, which is driven by the movement of the prey [@fraserfranco.etal2024].
-Indeed, the prey can increase their chances of survival by moving faster in the virtual environment [@fraserfranco.etal2022;@fraserfranco.etal2024].
+```{r fig1, out.width = "100%", fig.cap = "**Figure 1**.
+Hypothesis describing the outcome of prey-mediated individual foraging specialization.
+Panels A and B display two scenarios with different outcomes at the population level, but similar outcomes at the individual level.
+On panel A, all predators encounter prey with similar attributes (e.g., prey encountered were always fast) through time, such that they all display similar degrees of individual foraging specialization.
+This results in the population being specialized.
+Similarly, on panel B, all individuals encounter varying types of prey (e.g., in some encounters the prey were fast, in others the prey were slower), such that they also display similar degrees of individual foraging specialization.
+In this case, they all become generalist hunters, resulting in the population distribution being wider.
+Panel C shows a different and more plausible scenario, where predators display varying degrees of foraging specialization.
+In this case, some individuals encounter similar prey, and thus specialize, while others encounter varying groups of prey, thus becoming generalists."}
 
-We define the level of individual foraging specialization as the intra-individual variance (i.e.
-IIV) in movement speed across matches.
-Low IIV describes individual foraging specialization (i.e.
-always using an ambush or cursorial tactic), whereas high IIV describes a flexible use of foraging tactics (i.e.
-predators switching between an ambush and cursorial tactic).
-Here, our objective is to assess how foraging specialization emerges throughout experience at the population and individual level.
-If all predators encounter similar groups of prey, we predict that individuals (and thus the population) should all specialize on moving at similar speeds.
-In contrast, if all predators encounter varying groups of prey, then they should converge towards flexible speeds.
-In both scenarios, differences among individuals in IIV across experience should be low (i.e.
-similar individual foraging specialization), whereas the population variance would either decrease (specialization) or increase (flexibility).
+knitr::include_graphics(
+  here::here("outputs", "04_outputs_figures", "figure1.png")
+)
+
+```
+
+To test the hypothesis that repeated interactions with prey shape predator foraging specialization, we analyze the movement behaviour of both predators and their prey using their speed of movement.
+We predict that if all predators consistently encounter prey moving at similar speeds, then the population as a whole (i.e., all individuals) should specialize on moving at similar speeds, resulting in a narrow foraging behavioural niche (Figure 1A).
+In contrast, if all predators encounter groups of prey moving at varying speeds, then they should instead become more flexible in their tactic (i.e., generalists), adjusting their speed to the prey, resulting in a higher population variance in foraging behaviour (Figure 1B).
+In both scenarios, differences among individuals in IIV across experience should be low (i.e., similar individual foraging specialization, Figure 1 A-B).
 Alternatively, differences among individuals in foraging specialization may emerge if they experience different interactions with their prey.
-In this case, we expect predators that encountered similar groups of prey across experience to specialize on similar speeds, while predators that encountered heterogeneous groups across matches should adopt flexible movement speeds, resulting in an increase in among individual differences in IIV with experience.
-If we detect such prey-dependent fine-tuning with experience, then all hunters along the flexible-specialist continuum should attain equal success.
+In this case, predators that encountered similar groups of prey across experience should specialize on moving at a more fixed speed, while predators that encountered heterogeneous groups across matches should adopt a generalist movement strategy, resulting in an increase in among individual differences in IIV with experience (Figure 1C).
+If we detect such prey-dependent fine-tuning with experience, then specialist and generalist hunters should attain equal success, resulting in no apparent relationship between foraging specialization and prey capture.
 
@@
 We excluded matches where players were inactive, as indicated by mean movement speeds that were zero or nearly zero.
-Additionally, matches where players were suspected of hacking or engaging in unintended gameplay behavior were also removed based on our knowledge of the game mechanics.
+Additionally, matches where players were suspected of hacking or engaging in unintended gameplay behaviour were also removed based on our knowledge of the game mechanics.
 We then selected a cohort of players that played 300 matches or more, and monitored all their matches from the first to a maximum of 500 matches.
@@
 
-# Prepare equations
-#eqs <- c(
-#  "Y_{1}(T_{j}) = X_{1}(T_{j})\\ b_{1}(T_{j}) + M_{1}(T_{j})\\ en_{1}(T_{j}) + N_{1}(T_{j})\\ av_{1}(T_{j}) + Z_{1}(T_{j})\\ #id_{1}(T_{j}) + e_{1}(T_{j})",
-#  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = X_{d1}(T_{j})\\ b_{d1}(T_{j}) + Z_{d1}(T_{j})\\ id_{d1}(T_{j})",
-#  "Y_{2}(T_{j}) = X_{2}(T_{j})\\ b_{2}(T_{j}) + M_{2}(T_{j})\\ en_{2}(T_{j}) + N_{2}(T_{j})\\ av_{2}(T_{j}) + Z_{2}(T_{j})\\ #id_{2}(T_{j}) + e_{2}(T_{j})",
-#  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = X_{d2}(T_{j})\\ b_{d2}(T_{j}) + Z_{d2}(T_{j})\\ id_{d2}(T_{j})",
-#  "Y_{3}(T_{j}) = X_{3}(T_{j})\\ b_{3}(T_{j}) + Z_{3}(T_{j})\\ id_{3}(T_{j}) + e_{3}(T_{j})"
-#)
-
-#eqs <- c(
-#  "Y_{1}(T_{j}) = T^2_{j}(X_{1}\\ b_{1}) + T^2_{j}(M_{1}\\ en_{1}) + T^2_{j}(N_{1}\\ av_{1}) + T^2_{j}(Z_{1}\\ id_{1}) + e_{1}(T_{j})",
-#  "log(\\sigma_{e_{Y_{1}(T_{j})}}) = T^2_{j}(X_{d1}\\ b_{d1}) + T^2_{j}(Z_{d1}\\ id_{d1})",
-#  "Y_{2}(T_{j}) = T^2_{j}(X_{2}\\ b_{2}) + T^2_{j}(M_{2}\\ en_{2}) + T^2_{j}(N_{2}\\ av_{2}) + T^2_{j}(Z_{2}\\ id_{2}) + e_{2}(T_{j})",
-#  "log(\\sigma_{e_{Y_{2}(T_{j})}}) = T^2_{j}(X_{d2}\\ b_{d2}) + T^2_{j}(Z_{d2}\\ id_{d2})",
-#  "Y_{3}(T_{j}) = T^2_{j}(X_{3}\\ b_{3}) + T^2_{j}(Z_{3}\\ id_{3}) + e_{3}(T_{j})"
-#)
-
+# Equations
 eqs <- c(
@@
 
-```{r fig1, out.width = "100%", fig.cap = "**Figure 1**.
+```{r fig2, out.width = "100%", fig.cap = "**Figure 2**.
 Median posterior differences and HPD intervals comparing predator foraging behaviour at the population and individual level across experience stages.
@@
 knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure1.png")
+  here::here("outputs", "04_outputs_figures", "figure2.png")
 )
@@
 
-```{r fig2, out.width = "100%", fig.cap = "**Figure 2**.
+```{r fig3, out.width = "100%", fig.cap = "**Figure 3**.
 Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
@@
 knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure2.png")
+  here::here("outputs", "04_outputs_figures", "figure3.png")
 )
@@
 
-```{r fig3, out.width = "100%", fig.cap = "**Figure 3**.
+```{r fig4, out.width = "100%", fig.cap = "**Figure 4**.
 Correlation matrices of the MDHGLM relating the mean and IIV in speed of the predators, the mean and IIV in speed of the prey they encountered, and mean hunting success.
@@
 knitr::include_graphics(
-  here::here("outputs", "04_outputs_figures", "figure3.png")
+  here::here("outputs", "04_outputs_figures", "figure4.png")
 )

### 2025-04-07 manuscript/manuscript.Rmd
On Windows --> intro revamp complete

@@
 
-The capacity of predators to match their tactic to their prey and to optimize their skills at implementing a given tactic are expected to drive the outcome of predator-prey interactions.
-Hence, successive interactions of predators with their prey may result in increased flexibility in tactic use or in individual foraging specialization.
+The capacity of predators to match their hunting tactics to their prey and to optimize their skills at using them over successive encounters is hypothesized to promote individual foraging specialisation.
+Through this process, predators should be able to capture more prey.
 Yet, there are limited empirical assessments showing links between past experience, foraging specialization, and hunting success at the individual level, due to the challenges of monitoring direct interactions in the wild.
-Here, we used a virtual predator-prey system (the game *Dead by Daylight*) to investigate how individual predator foraging specialization and success developed across repeated interactions with their prey.
-We found that 68% of predators became either increasingly specialized by always moving at a fast pace, or flexible by transitioning between slow and fast speeds.
+In this study, we used a virtual predator-prey system (the game *Dead by Daylight*) to investigate how individual predator foraging specialization and success developed across repeated interactions with prey.
+We found that 68% of predators became either increasingly specialized by always moving at a fast pace (specialised cursorial tactic), or flexible by transitioning between slow and fast speeds (generalist ambush tactic).
 The predators' strategies were partially matched to their prey's speed, suggesting that changes in hunting behaviour were driven by repeated encounters with their prey.
@@
 Predators express a diverse array of foraging tactics to capture their prey.
-In natural populations, individuals differ in the use of tactics such as ambushing and roaming, often resulting in differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
-This variation in foraging behaviour has been shown to emerge from reciprocal behavioural interactions between predators and their prey.
-For example, prey reduce their activity to avoid predators, while predators match their hunting tactic to their prey based on their profitability **add ref for pred** [@kelley.magurran2011].
-For a long time, these observations have prompted ecologists to hypothesize that predators learn from experience to become efficient hunters through repeated encounters and may unveil links between foraging specialization and prey capture [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
-Hence, while it remains challenging to monitor individual predator experience through time, uncovering how it shapes foraging behaviour is essential to predict hunting success because of its implications for community and ecosystem dynamics [@wooster.etal2023].
+In natural populations, individuals specialise in the use of tactics such as ambushing and roaming, or switch tactics based on the prey that they encounter, often resulting in differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
+The success of specialist and generalist strategies depend on ecological factors: when resources are abundant, specialist hunters achieve greater success, while generalist hunters prevail under fluctuating conditions [@Terraube2011;@Terraube2014;@phillips.etal2017].
+While evolutionary history can partly explain how specialist and generalist species will fare under given ecological conditions, learning also plays an important part in shaping predator foraging behaviour [@wooster.etal2023].
+This has prompted ecologists to hypothesize that experience may underly associations between foraging specialization and prey capture as predators learn and become efficient hunters through repeated encounters with their prey [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
+Yet, it remains challenging to monitor individual predator experience, limiting our ability to uncover how predator foraging behaviour shapes prey capture over time.
 
-Recent evidence suggests that resource fluctuations (e.g., temporal changes in prey behaviour) may be a key mechanism underlying the emergence of behavioural specialization with experience and its fitness consequences [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
-Theory suggests two contrasting scenarios with their outcome defined by the degree of resource variability.
-In the first scenario, individuals should gradually specialize in a foraging tactic (e.g., always moving fast) if it allows them to maintain successful prey captures at each attempt [@tinker.etal2009;@dukas2019].
-This should occur when predators learn to hunt in environments where resources are predictable (or stable) because they require less energy and time to search for, capture, and handle prey [@weimerskirch2007;@woo.etal2008;@potier.etal2015].
-Such conditions favor specialist hunters because there would be higher costs to switch tactics for the same type of prey.
+Recent evidence suggests that the resource fluctuations predators experience over time (e.g., temporal changes in prey behaviour) may be key in shaping individual behavioural specialization and its fitness consequences [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
+Theory outlines two contrasting scenarios, with outcomes defined by the predator's ability to learn the optimal strategy in response to resource variability.
+In the first scenario, individuals should gradually specialize in a foraging tactic (e.g., always moving fast) if it enables them to consistently achieve successful prey captures while learning to hunt in environments with predictable (or stable) resources [@tinker.etal2009;@dukas2019].
+Such conditions favor specialist hunters, as they require less energy and time to search for, capture, and handle prey [@weimerskirch2007;@woo.etal2008;@potier.etal2015].
 For example, habitat specialization under stable resources is associated with reduced foraging effort and increased offspring growth rates in Herring Gulls (*Larus argentatus*) [@vandenbosch.etal2019].
-In the second scenario, predators are expected to increase behavioural flexibility by using a variety of hunting tactics (i.e.
-generalists) when they hunt in highly variable environments.
+In the second scenario, predators are expected to be more flexible by learning to use a variety of hunting tactics (i.e., generalists) when they hunt in highly variable environments.
 Indeed, while there can be costs to attempt novel tactics by trial and error, predators can reduce the consequences of uncertainty in environments under fluctuating resources by learning to adjust their tactic to the prey that they encounter [@dall2010;@mathot.etal2012;@stephens1993;@ishii.shimada2010;@kelley.magurran2011].
 @szopa-comley.ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
-Given these two scenarios, the relationship between individual foraging specialization and prey capture likely depends on a predator's ability to learn and adapt its hunting tactics to the prey it encounters.
-If predators can adjust their tactics to match the prey fluctuation regime they experience, then both specialist and generalist hunters should achieve similar hunting success and coexist [@phillips.etal2017].
-Empiricists should therefore examine how foraging specialization influences prey capture across time and different ecological scenarios.
+Under these two scenarios, if predators can learn to adjust their tactics to match the prey fluctuation regime they experience, both specialist and generalist hunters should achieve similar hunting success and coexist [@phillips.etal2017].
 
@@
 The predator population is composed of individuals that vary consistently in their use of hunting tactics along an ambush-cursorial continuum: at one extreme hunters move more slowly and ambush prey; at the other extreme, hunters roam the virtual environment at high velocities [@fraserfranco.etal2022].
-Predators also acquire expertise through extensive practice, and the behaviour of the prey they encounter influences the rate at which they gain expertise [@fraserfranco.etal2024].
-To assess how foraging specialization emerges throughout experience, we define the level of individual foraging specialization as the intra-individual variance (i.e.
-IIV) in movement speed across matches following the definition by @cleasby.etal2015.
-Low IIV describes individual foraging specialization (i.e., always using an ambush or cursorial tactic) whereas high IIV describes a flexible use of foraging tactics (i.e., generalist predators switching between ambush and cursorial tactics).
+To assess how foraging specialization emerges throughout experience, we define the level of individual foraging specialization as the intra-individual variance (IIV) in movement speed across matches following the definition by @cleasby.etal2015.
+Low IIV describes individual foraging specialization (i.e., always using an ambush or cursorial tactic) whereas high IIV describes a flexible use of foraging tactics (i.e., generalist predators switching between ambush and cursorial tactics, see Methods for details).
 
 ```{r fig1, out.width = "100%", fig.cap = "**Figure 1**.
-Hypothesis describing the outcome of prey-mediated individual foraging specialization.
+Hypothesis describing how prey-mediated individual foraging specialization emerges over repeated interactions.
 Panels A and B display two scenarios with different outcomes at the population level, but similar outcomes at the individual level.
-On panel A, all predators encounter prey with similar attributes (e.g., prey encountered were always fast) through time, such that they all display similar degrees of individual foraging specialization.
-This results in the population being specialized.
-Similarly, on panel B, all individuals encounter varying types of prey (e.g., in some encounters the prey were fast, in others the prey were slower), such that they also display similar degrees of individual foraging specialization.
-In this case, they all become generalist hunters, resulting in the population distribution being wider.
-Panel C shows a different and more plausible scenario, where predators display varying degrees of foraging specialization.
-In this case, some individuals encounter similar prey, and thus specialize, while others encounter varying groups of prey, thus becoming generalists."}
+On panel A, all predators encounter prey with similar attributes (e.g., some encountered prey that were always fast while others encountered slower prey more often) through time.
+They differ in their mean behaviour (tactic) which is adjusted to the prey that they encountered.
+Because encounters where predictable, they all display similar degrees of individual foraging specialization, resulting in the population being specialized.
+On panel B, all predators encounter varying types of prey (e.g., in some encounters the prey were fast, in others the prey were slower), such that they also display similar degrees of individual foraging specialization as in panel A.
+However, in this case, they all become generalist hunters, resulting in the population distribution being wider.
+Panel C shows a different scenario, where predators display varying degrees of foraging specialization.
+In this case, some individuals consistently encountered similar prey, and thus specialized, while others encountered varying groups of prey, thus becoming generalists.
+Ultimately, those that learn to specialise on the proper tactic given prey encounters have greater success than those that didn't, resulting in no differences between specialists and generalists."}
 
@@
 
-To test the hypothesis that repeated interactions with prey shape predator foraging specialization, we analyze the movement behaviour of both predators and their prey using their speed of movement.
-We predict that if all predators consistently encounter prey moving at similar speeds, then the population as a whole (i.e., all individuals) should specialize on moving at similar speeds, resulting in a narrow foraging behavioural niche (Figure 1A).
-In contrast, if all predators encounter groups of prey moving at varying speeds, then they should instead become more flexible in their tactic (i.e., generalists), adjusting their speed to the prey, resulting in a higher population variance in foraging behaviour (Figure 1B).
-In both scenarios, differences among individuals in IIV across experience should be low (i.e., similar individual foraging specialization, Figure 1 A-B).
+To test the hypothesis that repeated interactions with prey shape predator foraging specialization, we analyze the movement speed of predators and their prey over time.
+We expect predators to differ in the use of their hunting tactic (i.e., mean movement speed) which will be tuned to the mean speed of the prey that they encounter (Figure 1A-B).
+We predict that if all predators consistently encounter prey moving at similar speeds, then the population as a whole (i.e., all individuals) should specialize on moving at similar speeds, resulting in a narrow behavioural niche (Figure 1A).
+In contrast, if all predators encounter groups of prey moving at varying speeds, then they should all become more flexible in their tactic use (i.e., generalists), adjusting their speed to the prey from one encounter to the other, resulting in a higher population variance in foraging behaviour (Figure 1B).
+In both scenarios, differences among individuals in IIV across experience should be low (i.e., similar individual foraging specialization, Figure 1A-B).
 Alternatively, differences among individuals in foraging specialization may emerge if they experience different interactions with their prey.
-In this case, predators that encountered similar groups of prey across experience should specialize on moving at a more fixed speed, while predators that encountered heterogeneous groups across matches should adopt a generalist movement strategy, resulting in an increase in among individual differences in IIV with experience (Figure 1C).
-If we detect such prey-dependent fine-tuning with experience, then specialist and generalist hunters should attain equal success, resulting in no apparent relationship between foraging specialization and prey capture.
+In this case, predators that encountered prey moving at similar speeds across experience should specialize on moving at a more fixed speed, while predators that encountered different prey speeds across matches should adopt a generalist movement strategy, resulting in an increase in among individual differences in IIV (Figure 1C).
+If we detect such prey-dependent fine-tuning with experience, then specialist and generalist hunters should attain equal success, resulting in no apparent relationship between foraging specialization and prey capture (Figure 1C).
 
@@
 For each experience level, the model estimated among individual variance in mean predator speed, mean prey speed, and mean hunting success.
-This allows us to test for individual differences in tactic use (i.e.
-along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption.
+This allows us to test for individual differences in tactic use (i.e., along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption.
 The model also estimated among individual variance in intra-individual variation (IIV) for both prey and predator speed.
@@
 
-where $j$ is the index of the three experience levels (i.e.
+where $j$ is the index of the three experience levels (i.e,.
 novice, intermediate, advanced).
@@
 However, they displayed important differences in foraging specialization (Appendix 1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in among individual differences in IIV from novice to advanced (Figure 1).
-`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e.
->0.2 change in standard deviation; Figure 2).
-In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e.
->0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e.
-<0.05 change in standard deviation).
+`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e., >0.2 change in standard deviation; Figure 2).
+In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e., >0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e., <0.05 change in standard deviation).
 
@@
 Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix 1: Table S2).
-Thus, some predators encountered similar groups (i.e.
-all groups using similar speeds) while others encountered distinct groups (i.e.
-some slower and some faster).
+Thus, some predators encountered similar groups (i.e., all groups using similar speeds) while others encountered distinct groups (i.e., some slower and some faster).
 These differences among individuals in IIV for prey encounters increased only marginally with experience (Figure 1).

### 2025-04-08 manuscript/manuscript.Rmd
on Windows --> updated MS results

@@
 bibliography: references.bib
-csl: chicago-author-date.csl
+csl: ecology.csl
 ---
@@
 library(dplyr)
+library(equatags)
 
@@
 In this study, we used a virtual predator-prey system (the game *Dead by Daylight*) to investigate how individual predator foraging specialization and success developed across repeated interactions with prey.
-We found that 68% of predators became either increasingly specialized by always moving at a fast pace (specialised cursorial tactic), or flexible by transitioning between slow and fast speeds (generalist ambush tactic).
+We found that 68% of predators became either increasingly specialized by always moving at a fast pace (specialised cursorial tactic), or generalists by transitioning between slow and fast speeds (generalist ambush tactic).
 The predators' strategies were partially matched to their prey's speed, suggesting that changes in hunting behaviour were driven by repeated encounters with their prey.
-Flexible and specialist foragers achieved similar success overall.
+Specialist and generalist foragers achieved similar success overall, although specialist hunters had a slight advantage.
 Hence, our findings suggest that experience may promote behavioural diversification in predator-prey systems.
@@
 For example, habitat specialization under stable resources is associated with reduced foraging effort and increased offspring growth rates in Herring Gulls (*Larus argentatus*) [@vandenbosch.etal2019].
-In the second scenario, predators are expected to be more flexible by learning to use a variety of hunting tactics (i.e., generalists) when they hunt in highly variable environments.
+In the second scenario, predators are expected to be more generalist by learning to use a variety of hunting tactics when they hunt in highly variable environments.
 Indeed, while there can be costs to attempt novel tactics by trial and error, predators can reduce the consequences of uncertainty in environments under fluctuating resources by learning to adjust their tactic to the prey that they encounter [@dall2010;@mathot.etal2012;@stephens1993;@ishii.shimada2010;@kelley.magurran2011].
@@
 The predator population is composed of individuals that vary consistently in their use of hunting tactics along an ambush-cursorial continuum: at one extreme hunters move more slowly and ambush prey; at the other extreme, hunters roam the virtual environment at high velocities [@fraserfranco.etal2022].
-To assess how foraging specialization emerges throughout experience, we define the level of individual foraging specialization as the intra-individual variance (IIV) in movement speed across matches following the definition by @cleasby.etal2015.
-Low IIV describes individual foraging specialization (i.e., always using an ambush or cursorial tactic) whereas high IIV describes a flexible use of foraging tactics (i.e., generalist predators switching between ambush and cursorial tactics, see Methods for details).
 
@@
 Panels A and B display two scenarios with different outcomes at the population level, but similar outcomes at the individual level.
-On panel A, all predators encounter prey with similar attributes (e.g., some encountered prey that were always fast while others encountered slower prey more often) through time.
+A) all predators encounter prey with similar attributes (e.g., some encountered prey that were always fast while others encountered slower prey more often) through time.
 They differ in their mean behaviour (tactic) which is adjusted to the prey that they encountered.
 Because encounters where predictable, they all display similar degrees of individual foraging specialization, resulting in the population being specialized.
-On panel B, all predators encounter varying types of prey (e.g., in some encounters the prey were fast, in others the prey were slower), such that they also display similar degrees of individual foraging specialization as in panel A.
+B) all predators encounter varying types of prey (e.g., in some encounters the prey were fast, in others the prey were slower), such that they also display similar degrees of individual foraging specialization as in panel A.
 However, in this case, they all become generalist hunters, resulting in the population distribution being wider.
-Panel C shows a different scenario, where predators display varying degrees of foraging specialization.
+C) A scenario where predators display varying degrees of foraging specialization.
 In this case, some individuals consistently encountered similar prey, and thus specialized, while others encountered varying groups of prey, thus becoming generalists.
@@
 To test the hypothesis that repeated interactions with prey shape predator foraging specialization, we analyze the movement speed of predators and their prey over time.
-We expect predators to differ in the use of their hunting tactic (i.e., mean movement speed) which will be tuned to the mean speed of the prey that they encounter (Figure 1A-B).
-We predict that if all predators consistently encounter prey moving at similar speeds, then the population as a whole (i.e., all individuals) should specialize on moving at similar speeds, resulting in a narrow behavioural niche (Figure 1A).
+To assess how foraging specialization emerges throughout experience, we define the level of individual foraging specialization as the intra-individual variance (IIV) in movement speed across matches following the definition by @cleasby.etal2015.
+Low IIV describes individual foraging specialization (i.e., always using an ambush or cursorial tactic) whereas high IIV describes a flexible use of foraging tactics (i.e., generalist predators switching between ambush and cursorial tactics, see Methods for details).
+First, we expect predators to differ in the use of their hunting tactic (i.e., mean movement speed) which will be tuned to the mean speed of the prey that they encounter (Figure 1A-B).
+Second, we predict that if all predators consistently encounter prey moving at similar speeds, then the population as a whole (i.e., all individuals) should specialize on moving at similar speeds, resulting in a narrow behavioural niche (Figure 1A).
 In contrast, if all predators encounter groups of prey moving at varying speeds, then they should all become more flexible in their tactic use (i.e., generalists), adjusting their speed to the prey from one encounter to the other, resulting in a higher population variance in foraging behaviour (Figure 1B).
@@
 In this case, predators that encountered prey moving at similar speeds across experience should specialize on moving at a more fixed speed, while predators that encountered different prey speeds across matches should adopt a generalist movement strategy, resulting in an increase in among individual differences in IIV (Figure 1C).
-If we detect such prey-dependent fine-tuning with experience, then specialist and generalist hunters should attain equal success, resulting in no apparent relationship between foraging specialization and prey capture (Figure 1C).
+Lastly, if we detect such prey-dependent fine-tuning with experience, then specialist and generalist hunters should attain equal success, resulting in no apparent relationship between foraging specialization and prey capture (Figure 1C).
 
@@
 In this game, participants take on roles as either a predator or one of the prey, with each match consisting of one predator and four prey.
-A matchmaking system pairs groups of players with similar skill such that individuals should all have similar experience.
-The predator's primary goal is to hunt and capture the prey, while the prey aim to locate and collect resources in the form of power generators.
+A matchmaking system pairs groups of players with similar skill levels such that individuals should all have similar profiency.
+The predator's primary goal is to hunt and capture the prey while the prey must locate and collect resources in the form of power generators that must be activated.
 When all generators are activated, the prey can escape through one of two exit gates and win the match.
-A match concludes when the predator eliminates all remaining prey that have not escaped or when the final prey successfully exits the virtual environment.
-Players, whether predator or prey, select avatars with distinct abilities tailored to specific playstyles (e.g.
+A match ends when the predator has eliminated all remaining prey that have not escaped or when the last prey successfully exits the virtual environment.
+Players, whether predator or prey, select avatars with distinct abilities designed for specific playstyles (e.g.
 stealthy vs evasive prey, or stalking vs patrolling predators).
 During the study period, the game featured `r toString(format(length(unique(dat$avatar_id))))` predator avatars.
-The virtual environments in the game vary in size and structural complexity, combining fixed and procedurally generated elements such as vegetation, buildings, and maze-like structures.
+The virtual environments in which matches are played vary in size and structural complexity, combining fixed and procedurally generated elements such as vegetation, buildings, and maze-like structures.
 Troughout the study period, there were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for gameplay.
@@
 
-The videogame company provided six months of gameplay data, encompassing all player activity from `r toString(format(min(dat$date)))` to `r toString(format(max(dat$date)))`.
-We focused exclusively on matches played in "Online" mode, where players were strangers to one another.
-We excluded matches where players were inactive, as indicated by mean movement speeds that were zero or nearly zero.
-Additionally, matches where players were suspected of hacking or engaging in unintended gameplay behaviour were also removed based on our knowledge of the game mechanics.
+The dataset comprised gameplay data from `r toString(format(min(dat$date)))` to `r toString(format(max(dat$date)))`.
+We focused exclusively on matches played in "Online" mode, where players were strangers to one another and paired by a matchmaking algorithm.
+We excluded matches where players were inactive, as indicated by null or nearly null movement speeds, and matches where players were suspected of hacking or engaging in unintended gameplay behaviour based on our knowledge of the game mechanics.
 We then selected a cohort of players that played 300 matches or more, and monitored all their matches from the first to a maximum of 500 matches.
 
-Our dataset includes `r toString(format(length(unique(dat$predator_id))))` unique predator players, collectively accounting for `r toString(formatC(length(unique(dat$match_id)), big.mark = " "))` matches.
+Our dataset includes `r toString(format(length(unique(dat$predator_id))))` unique predator players, collectively contributing to `r toString(formatC(length(unique(dat$match_id)), big.mark = " "))` matches.
 The number of matches played by predator players ranged from `r toString(format(min(dat$total_xp_pred)))` to `r toString(format(max(dat$total_xp_pred)))`.
 Match durations varied between `r toString(format(round(min(dat$game_duration / 60))), digits = 2)` and `r toString(format(round(max(dat$game_duration / 60))), digits = 2)` minutes, with an average duration of `r toString(format(round(mean(dat$game_duration / 60))), digits = 2)` minutes.
-The following details were recorded for each match: the anonymous player ID, the chosen predator avatar, the game environment, the predator's level of experience, their speed, the average speed of the prey group they encountered, and the average rank of those prey (used as a proxy for prey skill).
+The final dataset provided the following variables: the player ID, the chosen predator avatar, the game environment, the predator's level of experience, the mean movement speed of the predator, the mean movement speed of the prey group, and their average rank (used as a proxy for prey skill).
 The game's ranking system, designed to match players of similar skill levels (https://deadbydaylight.fandom.com/wiki/Rank), was incorporated into our analysis to detect any relationship between predator experience and foraging success [see @fraserfranco.etal2024].
@@
 We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
-Lastly, we categorized predators for each match based on their cumulated experience [see @fraserfranco.etal2024].
-We labeled predators as novices for matches where they had cumulated less than 100 matches, intermediate for matches where they had cumulated between 100 and 299 matches, and advanced for matches where they had cumulated more than 299 matches (max 500).
-Since our goal was to monitor predator players throughout their experience and that they all played at least 300 matches, they all appeared in each of the three experience categories.
+Lastly, we categorized predators for each match based on the experience they cumulated [see @fraserfranco.etal2024].
+We labeled predators as novices when they played between 1 and 99 matches, as intermediates between 100 and 299 matches, and as advanced between 300 and 500 matches.
 
@@
 
-We tested whether foraging behaviour changed with experience, and compared the success of predators along the flexible-specialist hunter continuum, using a multivariate double-hierarchical generalized linear model (MDHGLM) [@lee.nelder2006;@cleasby.etal2015;@mitchell.etal2016].
+ We used a multivariate double-hierarchical generalized linear model (MDHGLM) to quantify a) changes in the average foraging tactic (i.e., the mean movement speed) and in the degree of specialization (i.e., IIV in movement speed) over successive matches for each player; and b) the relationship between the average tactic and specialization, and hunting success [@lee.nelder2006;@cleasby.etal2015;@mitchell.etal2016].
 For each experience level, we fitted the model on three traits: the predator's speed ($Y_{1}$) and the prey's speed ($Y_{2}$) using a Gaussian error distribution, and the predator's hunting success ($Y_{3}$) using a beta-binomial error distribution.
-Fixed and random effect structure were trait-specific and the same for all experience levels.
-The predator and the prey speed included a mean and a dispersion part (eqn 1.1, 1.2 and 2.1, 2.2).
-For both traits, we controlled for the standardized prey rank on both the mean and the dispersion parts of the model.
+Fixed and random effect structure was trait-specific and the same for all experience levels.
+For the predator and the prey speed, we modeled the mean and the residual standard deviation (eqn 1.1, 1.2 and 2.1, 2.2).
+For both traits, we controlled for the standardized prey rank on the mean and the residual standard deviation.
 We included game environment, predator avatar, and individual predator identity random effects on the mean part of the model.
-The dispersion part included individual predator identity random effects exclusively.
-For hunting success, we modeled the mean part only (eqn 3) and controlled for the standardized prey rank and game duration, and included an individual identity random effect.
+The residual standard deviation included individual predator identity random effects exclusively.
+For hunting success, we modeled the mean only (eqn 3) and controlled for the standardized prey rank and game duration, and included an individual identity random effect.
 
@@
 For each experience level, the model estimated among individual variance in mean predator speed, mean prey speed, and mean hunting success.
-This allows us to test for individual differences in tactic use (i.e., along the slow-fast continuum), in the mean speed of the prey encountered, and in mean prey consumption.
+This allows us to test for individual differences in tactic use (i.e., along the ambush-cursorial continuum), in the mean speed of the prey encountered, and in mean prey consumption.
 The model also estimated among individual variance in intra-individual variation (IIV) for both prey and predator speed.
@@
 
-We performed our analyses under a Bayesian framework.
+We performed our analyses within a Bayesian framework.
 We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1^{2})$: eqn.
@@
 
-We parametrized the MDHGLM to run 2500 iterations with a thinning set to eight, with the first 500 used as warm up iterations (yielding 1000 posterior samples for each parameter).
+We parametrized the MDHGLM to run 2500 iterations on four chains with a thinning interval set at eight iterations, with the first 500 used as warm up iterations (yielding 1000 posterior samples for each parameter).
 We assessed the convergence of the chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@vehtari.etal2021].
@@
 
-The mean speed of the predator population remained stable with experience (Figure 2 and Appendix 1: Table S1).
-Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2 and Appendix 1: Table S1).
-At the individual level, predators differed slightly in their mean speed across experience levels, indicating marginal differences in hunting tactics (Figure 2 and Appendix 1: Table S2).
-However, they displayed important differences in foraging specialization (Appendix 1: Table S2) which also increased slightly with experience as there was a 0.11 unit increase in among individual differences in IIV from novice to advanced (Figure 1).
-`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialized hunting tactic, and vice-versa, as predators gained experience (i.e., >0.2 change in standard deviation; Figure 2).
+At the population level, the mean predator speed remained stable as predators progressed from novices to advanced hunters (Figure 2A and Appendix 1: Table S1).
+Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2A and Appendix 1: Table S1).
+At the individual level, differences among predators in their mean speed were weak and did not change across experience (Figure 2A and Appendix 1: Table S2).
+However, predators displayed minor differences in foraging specialization as novices, with differences increasing slightly as individuals gained experience (Figure 2A and Appendix 1: Table S2).
+`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a more specialized hunting tactic, and vice-versa, as predators gained experience (i.e., >0.2 change in standard deviation; Figure 3).
 In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e., >0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e., <0.05 change in standard deviation).
@@
 ```{r fig2, out.width = "100%", fig.cap = "**Figure 2**.
-Median posterior differences and HPD intervals comparing predator foraging behaviour at the population and individual level across experience stages.
-The behavioural parameter predicted by the MDHGLM being compared is on the y axis, and the difference in parameter values between two experience stages is on the x axis.
-The pairwise comparisons between experience stages are displayed across the three panels A, B, and C.
-We compare the mean speed of the predator population, the speed of the prey it encountered, and its hunting success across experience (population mean).
-We also compare the population's foraging specialization and variation in speed of the prey it encountered across experience (population variance).
-At the individual level, we compare among individual differences in speed, the speed of the prey encountered, and hunting success (individual variation mean).
-Lastly, we compare individual variation in IIV across experience, indicating whether individual differences in foraging specialization and in the variation of the groups of prey encountered changed with experience (individual variation IIV)."}
+Median posterior differences and HPD intervals comparing predator foraging behaviour, prey behaviour, and predator hunting success at the population and individual level across experience stages.
+The parameters being compared are on the y axis, and the differences in parameter values between two experience stages are on the x axis.
+The pairwise comparisons between experience stages are displayed as different point shapes on each panel.
+A) For the predator speed, we compare the foraging tactic (mean) and specialisation (variance) at the population level and at the individual level between each experience stage.
+B) For the prey speed, we compare the mean and the variance in speed of prey encountered at the population and individual level between each experience stage.
+C) For the predator hunting success, we compare the mean success at the population and individual level between each experience stage."}
 
@@
 
-As the predator population gained experience, there was strong evidence that the prey increased their speed, although slightly (Figure 1 and Appendix 1: Table S1).
-The population also encountered groups of prey using different speeds through time (Figure 1 and Appendix 1: Table S1).
-At the individual level, all predators encountered prey with similar average speeds throughout experience (Figure 1 and Appendix 1: Table S2).
-Yet, even if they experienced similar average prey speeds across all groups encountered, there were important differences among predators in how (dis)similar were the groups they encountered (Appendix 1: Table S2).
-Thus, some predators encountered similar groups (i.e., all groups using similar speeds) while others encountered distinct groups (i.e., some slower and some faster).
-These differences among individuals in IIV for prey encounters increased only marginally with experience (Figure 1).
+At the population level, we found strong evidence that the prey increased their speed slightly as predators gained experience (Figure 2B and Appendix 1: Table S1).
+The predators also encountered a greater variation of prey speeds at later experience stages (Figure 2B and Appendix 1: Table S1).
+At the individual level, predators encountered prey with similar average speeds across experience stages (Figure 2B and Appendix 1: Table S2).
+However, predators differed in the range of prey speeds they encountered and the magnitude of these differences increased as they gained experience (Figure 2B and Appendix 1: Table S2).
+Thus, some predators encountered prey moving at similar speeds from one encounter to the next (i.e., all groups using similar speeds) while others encountered prey moving at different speeds (i.e., some slower and some faster).
 
-The predator population's mean hunting success increased with experience (Figure 1 and Appendix 1: Table S1), with mean prey consumption revolving around two prey.
-There were also important differences among individuals in mean hunting success (Appendix 1: Table S2), but they remained stable across experience (Figure 1).
+The predator population's mean hunting success increased with experience (Figure 2C and Appendix 1: Table S1), with mean prey consumption reaching around two prey.
+We did not find evidence for differences among individuals in mean hunting success at any experience stage, even though differences increased slightly (Figure 2C and Appendix 1: Table S2).
 
 ```{r fig3, out.width = "100%", fig.cap = "**Figure 3**.
-Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase in specialization and (B) the greatest increase in flexibility.
+Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase and (B) the greatest decrease in specialisation.
 The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
-Both figure panels are ordered by ascending degree of increase in either specialization or flexibility.
+Both figure panels are ordered by ascending degree of change in specialization.
 We built the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selected those with the greatest difference using the 25% and 75% quantiles.
@@
 
-Predators that were on average faster had lower IIV in speed (Figure 3A-B).
-Thus, faster predators specialized on fast movement, while slower predators were more flexible in their movement.
-As predators gained experience, these strategies were increasingly defined as the correlation changed by 0.16 units, from -0.62 (-0.70, -0.55 $95\%\ CI$) for when predators were novices to -0.78 (-0.83, -0.72 $95\%\ CI$) as they reached the advanced stage (Figure 3C).
-Predators that were on average faster also tended to encounter groups of prey that were on average faster and more similar (Figure 3A-B).
-There was however no evidence that these correlations increased with experience (Figure 3C)
+Predators that were on average faster had lower IIV in speed (Figure 4A-B).
+Thus, faster predators specialized to a higher degree than slower predators.
+As predators gained experience, these strategies were increasingly defined as the correlation changed from -0.62 (-0.70, -0.55 $95\%\ CI$) among novices to -0.78 (-0.83, -0.72 $95\%\ CI$) among advanced hunters (Figure 4C).
+Faster predators tended to encounter faster prey; they also encountered groups of prey groups of prey that were more similar from match to match (Figure 4A-B), irrespective of their experience (Figure 4C).
 
-There was no correlation (-0.02 (-0.14, 0.01 $95\%\ CI$)) between mean prey speed and IIV in predator speed when predators were novice (Figure 3A), but the correlation increased to -0.16 (-0.27, -0.04 $95\%\ CI$) at the advanced stage (Figure 3B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 3C).
-The predators' IIV in speed and IIV in prey speed were weakly positively correlated (Figure 3A-B).
-Hence, predators that encountered groups of prey with similar speeds tended to be more specialized in their tactic, while those that encountered groups of prey with varying speeds tended to be more flexible.
-We did not find evidence that this correlation increased with experience (Figure 3C).
+There was no correlation (-0.02, -0.14, 0.01 $95\%\ CI$) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.27, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 4C).
+Predators with a larger IIV in speed encountered a greater range of prey speeds, but this effect was weak (Figure 4A-B).
+Hence, predators that encountered groups of prey with similar speeds tended to be more specialized in their tactic, while those that encountered groups of prey with varying speeds were less specialised.
+However, this correlation did not change with experience (Figure 4C).
 
@@
 
-The predator's mean speed and IIV were only weakly negatively correlated with hunting success across experience (Figure 3), suggesting that slower/flexible and faster/specialist predators were overall both equally successful.
-There was however a slight increase in the correlation between the predator's IIV in speed and success (Figure 3C), suggesting that flexible foragers at the advanced stage were marginally less successful (Appendix 1: Figure S2).
-We also found strong evidence that individuals who encountered groups of prey with faster speeds were less successful (Figure 3A-B).
-Predators also had greater success across the study when encountering more variable groups of prey (Figure 3A-B).
-Both relationships remained structurally stable across experience (Figure 3C).
+There were no differences in hunting success among predators in their mean speed (Figure 4).
+More specialised predators achieved a slightly greater foraging success, but this effect was weak (Figure 4).
+This relationship between the predator's IIV in speed and success increased with experience (Figure 4C), suggesting that the success gap between generalists and specialists increased with experience (Appendix 1: Figure S2).
+There was strong evidence that predators that encountered faster prey and prey groups with similar speeds were less successful (Figure 4A-B), irrespective of their experience level (Figure 4C).
 

### 2025-04-09 manuscript/manuscript.Rmd
On Windows --> discussion repassed. fig2 updt

@@
 ---
-title: "Individual foraging specialization and success change across experience in a virtual predator-prey system"
+title: "Individual foraging specialisation and success change across experience in a virtual predator-prey system"
 output: 
@@
 
-The capacity of predators to match their hunting tactics to their prey and to optimize their skills at using them over successive encounters is hypothesized to promote individual foraging specialisation.
+The capacity of predators to match their hunting tactics to their prey and to optimise their skills at using them over successive encounters is hypothesised to promote individual foraging specialisation.
 Through this process, predators should be able to capture more prey.
-Yet, there are limited empirical assessments showing links between past experience, foraging specialization, and hunting success at the individual level, due to the challenges of monitoring direct interactions in the wild.
-In this study, we used a virtual predator-prey system (the game *Dead by Daylight*) to investigate how individual predator foraging specialization and success developed across repeated interactions with prey.
-We found that 68% of predators became either increasingly specialized by always moving at a fast pace (specialised cursorial tactic), or generalists by transitioning between slow and fast speeds (generalist ambush tactic).
+Yet, there are limited empirical assessments showing links between past experience, foraging specialisation, and hunting success at the individual level, due to the challenges of monitoring direct interactions in the wild.
+In this study, we used a virtual predator-prey system (the game *Dead by Daylight*) to investigate how individual predator foraging specialisation and success developed across repeated interactions with prey.
+We found that 68% of predators became either increasingly specialised by always moving at a fast pace (specialised cursorial tactic), or generalists by transitioning between slow and fast speeds (generalist ambush tactic).
 The predators' strategies were partially matched to their prey's speed, suggesting that changes in hunting behaviour were driven by repeated encounters with their prey.
@@
 While evolutionary history can partly explain how specialist and generalist species will fare under given ecological conditions, learning also plays an important part in shaping predator foraging behaviour [@wooster.etal2023].
-This has prompted ecologists to hypothesize that experience may underly associations between foraging specialization and prey capture as predators learn and become efficient hunters through repeated encounters with their prey [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
+This has prompted ecologists to hypothesise that experience may underly associations between foraging specialisation and prey capture as predators learn and become efficient hunters through repeated encounters with their prey [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
 Yet, it remains challenging to monitor individual predator experience, limiting our ability to uncover how predator foraging behaviour shapes prey capture over time.
 
-Recent evidence suggests that the resource fluctuations predators experience over time (e.g., temporal changes in prey behaviour) may be key in shaping individual behavioural specialization and its fitness consequences [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
+Recent evidence suggests that the resource fluctuations predators experience over time (e.g., temporal changes in prey behaviour) may be key in shaping individual behavioural specialisation and its fitness consequences [@patrick.weimerskirch2014b;@vandenbosch.etal2019;@santoro.etal2019;@manlick.etal2021].
 Theory outlines two contrasting scenarios, with outcomes defined by the predator's ability to learn the optimal strategy in response to resource variability.
-In the first scenario, individuals should gradually specialize in a foraging tactic (e.g., always moving fast) if it enables them to consistently achieve successful prey captures while learning to hunt in environments with predictable (or stable) resources [@tinker.etal2009;@dukas2019].
+In the first scenario, individuals should gradually specialise in a foraging tactic (e.g., always moving fast) if it enables them to consistently achieve successful prey captures while learning to hunt in environments with predictable (or stable) resources [@tinker.etal2009;@dukas2019].
 Such conditions favor specialist hunters, as they require less energy and time to search for, capture, and handle prey [@weimerskirch2007;@woo.etal2008;@potier.etal2015].
-For example, habitat specialization under stable resources is associated with reduced foraging effort and increased offspring growth rates in Herring Gulls (*Larus argentatus*) [@vandenbosch.etal2019].
+For example, habitat specialisation under stable resources is associated with reduced foraging effort and increased offspring growth rates in Herring Gulls (*Larus argentatus*) [@vandenbosch.etal2019].
 In the second scenario, predators are expected to be more generalist by learning to use a variety of hunting tactics when they hunt in highly variable environments.
@@
 
-In this study, we use data from players in the online videogame *Dead by Daylight* to investigate 1) how repeated interactions with prey shape predator foraging specialization and 2) how the relationship between specialization and foraging success changes over time.
+In this study, we use data from players in the online videogame *Dead by Daylight* to investigate 1) how repeated interactions with prey shape predator foraging specialisation and 2) how the relationship between specialisation and foraging success changes over time.
 *Dead by Daylight* simulates a predator-prey interaction across complex virtual environments, providing a system to test ecological hypotheses on foraging behaviour, group selection, and social interactions [reviewed in @montiglio2025].
@@
 ```{r fig1, out.width = "100%", fig.cap = "**Figure 1**.
-Hypothesis describing how prey-mediated individual foraging specialization emerges over repeated interactions.
+Hypothesis describing how prey-mediated individual foraging specialisation emerges over repeated interactions.
 Panels A and B display two scenarios with different outcomes at the population level, but similar outcomes at the individual level.
@@
 They differ in their mean behaviour (tactic) which is adjusted to the prey that they encountered.
-Because encounters where predictable, they all display similar degrees of individual foraging specialization, resulting in the population being specialized.
-B) all predators encounter varying types of prey (e.g., in some encounters the prey were fast, in others the prey were slower), such that they also display similar degrees of individual foraging specialization as in panel A.
+Because encounters where predictable, they all display similar degrees of individual foraging specialisation, resulting in the population being specialised.
+B) all predators encounter varying types of prey (e.g., in some encounters the prey were fast, in others the prey were slower), such that they also display similar degrees of individual foraging specialisation as in panel A.
 However, in this case, they all become generalist hunters, resulting in the population distribution being wider.
-C) A scenario where predators display varying degrees of foraging specialization.
-In this case, some individuals consistently encountered similar prey, and thus specialized, while others encountered varying groups of prey, thus becoming generalists.
+C) A scenario where predators display varying degrees of foraging specialisation.
+In this case, some individuals consistently encountered similar prey, and thus specialised, while others encountered varying groups of prey, thus becoming generalists.
 Ultimately, those that learn to specialise on the proper tactic given prey encounters have greater success than those that didn't, resulting in no differences between specialists and generalists."}
@@
 
-To test the hypothesis that repeated interactions with prey shape predator foraging specialization, we analyze the movement speed of predators and their prey over time.
-To assess how foraging specialization emerges throughout experience, we define the level of individual foraging specialization as the intra-individual variance (IIV) in movement speed across matches following the definition by @cleasby.etal2015.
-Low IIV describes individual foraging specialization (i.e., always using an ambush or cursorial tactic) whereas high IIV describes a flexible use of foraging tactics (i.e., generalist predators switching between ambush and cursorial tactics, see Methods for details).
+To test the hypothesis that repeated interactions with prey shape predator foraging specialisation, we analyze the movement speed of predators and their prey over time.
+To assess how foraging specialisation emerges throughout experience, we define the level of individual foraging specialisation as the intra-individual variance (IIV) in movement speed across matches following the definition by @cleasby.etal2015.
+Low IIV describes individual foraging specialisation (i.e., always using an ambush or cursorial tactic) whereas high IIV describes a flexible use of foraging tactics (i.e., generalist predators switching between ambush and cursorial tactics, see Methods for details).
 First, we expect predators to differ in the use of their hunting tactic (i.e., mean movement speed) which will be tuned to the mean speed of the prey that they encounter (Figure 1A-B).
-Second, we predict that if all predators consistently encounter prey moving at similar speeds, then the population as a whole (i.e., all individuals) should specialize on moving at similar speeds, resulting in a narrow behavioural niche (Figure 1A).
+Second, we predict that if all predators consistently encounter prey moving at similar speeds, then the population as a whole (i.e., all individuals) should specialise on moving at similar speeds, resulting in a narrow behavioural niche (Figure 1A).
 In contrast, if all predators encounter groups of prey moving at varying speeds, then they should all become more flexible in their tactic use (i.e., generalists), adjusting their speed to the prey from one encounter to the other, resulting in a higher population variance in foraging behaviour (Figure 1B).
-In both scenarios, differences among individuals in IIV across experience should be low (i.e., similar individual foraging specialization, Figure 1A-B).
-Alternatively, differences among individuals in foraging specialization may emerge if they experience different interactions with their prey.
-In this case, predators that encountered prey moving at similar speeds across experience should specialize on moving at a more fixed speed, while predators that encountered different prey speeds across matches should adopt a generalist movement strategy, resulting in an increase in among individual differences in IIV (Figure 1C).
-Lastly, if we detect such prey-dependent fine-tuning with experience, then specialist and generalist hunters should attain equal success, resulting in no apparent relationship between foraging specialization and prey capture (Figure 1C).
+In both scenarios, differences among individuals in IIV across experience should be low (i.e., similar individual foraging specialisation, Figure 1A-B).
+Alternatively, differences among individuals in foraging specialisation may emerge if they experience different interactions with their prey.
+In this case, predators that encountered prey moving at similar speeds across experience should specialise on moving at a more fixed speed, while predators that encountered different prey speeds across matches should adopt a generalist movement strategy, resulting in an increase in among individual differences in IIV (Figure 1C).
+Lastly, if we detect such prey-dependent fine-tuning with experience, then specialist and generalist hunters should attain equal success, resulting in no apparent relationship between foraging specialisation and prey capture (Figure 1C).
 
@@
 
- We used a multivariate double-hierarchical generalized linear model (MDHGLM) to quantify a) changes in the average foraging tactic (i.e., the mean movement speed) and in the degree of specialization (i.e., IIV in movement speed) over successive matches for each player; and b) the relationship between the average tactic and specialization, and hunting success [@lee.nelder2006;@cleasby.etal2015;@mitchell.etal2016].
+ We used a multivariate double-hierarchical generalized linear model (MDHGLM) to quantify a) changes in the average foraging tactic (i.e., the mean movement speed) and in the degree of specialisation (i.e., IIV in movement speed) over successive matches for each player; and b) the relationship between the average tactic and specialisation, and hunting success [@lee.nelder2006;@cleasby.etal2015;@mitchell.etal2016].
 For each experience level, we fitted the model on three traits: the predator's speed ($Y_{1}$) and the prey's speed ($Y_{2}$) using a Gaussian error distribution, and the predator's hunting success ($Y_{3}$) using a beta-binomial error distribution.
@@
 The model also estimated among individual variance in intra-individual variation (IIV) for both prey and predator speed.
-This allows us to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialization.
+This allows us to test if predators do not experience the same degree of prey heterogeneity and if they differ in individual specialisation.
 Finally, the model estimated all pairwise covariances at the individual level among traits, among experience, and across traits and experience.
-The resulting 15x15 (co)variance matrix thus provides the structure of the predator-prey trait interactions as well as the relationship between specialization and success across experience at the individual-level.
+The resulting 15x15 (co)variance matrix thus provides the structure of the predator-prey trait interactions as well as the relationship between specialisation and success across experience at the individual-level.
 
@@
 At the population level, the mean predator speed remained stable as predators progressed from novices to advanced hunters (Figure 2A and Appendix 1: Table S1).
-Likewise, the variation in speed did not change with experience, indicating that foraging specialization remained stable at the population level (Figure 2A and Appendix 1: Table S1).
+Likewise, the variation in speed did not change with experience, indicating that foraging specialisation remained stable at the population level (Figure 2A and Appendix 1: Table S1).
 At the individual level, differences among predators in their mean speed were weak and did not change across experience (Figure 2A and Appendix 1: Table S2).
-However, predators displayed minor differences in foraging specialization as novices, with differences increasing slightly as individuals gained experience (Figure 2A and Appendix 1: Table S2).
-`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a more specialized hunting tactic, and vice-versa, as predators gained experience (i.e., >0.2 change in standard deviation; Figure 3).
+However, predators displayed minor differences in foraging specialisation as novices, with differences increasing slightly as individuals gained experience (Figure 2A and Appendix 1: Table S2).
+`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a more specialised hunting tactic, and vice-versa, as predators gained experience (i.e., >0.2 change in standard deviation; Figure 3).
 In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e., >0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e., <0.05 change in standard deviation).
@@
 The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
-Both figure panels are ordered by ascending degree of change in specialization.
+Both figure panels are ordered by ascending degree of change in specialisation.
 We built the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selected those with the greatest difference using the 25% and 75% quantiles.
-Individuals on panel A have an increase in specialization equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal to or greater than 0.2 standard deviations."}
+Individuals on panel A have an increase in specialisation equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal to or greater than 0.2 standard deviations."}
 
@@
 Predators that were on average faster had lower IIV in speed (Figure 4A-B).
-Thus, faster predators specialized to a higher degree than slower predators.
+Thus, faster predators specialised to a higher degree than slower predators.
 As predators gained experience, these strategies were increasingly defined as the correlation changed from -0.62 (-0.70, -0.55 $95\%\ CI$) among novices to -0.78 (-0.83, -0.72 $95\%\ CI$) among advanced hunters (Figure 4C).
@@
 
-There was no correlation (-0.02, -0.14, 0.01 $95\%\ CI$) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.27, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialized (Figure 4C).
+There was no correlation (-0.02, -0.14, 0.01 $95\%\ CI$) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.27, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialised (Figure 4C).
 Predators with a larger IIV in speed encountered a greater range of prey speeds, but this effect was weak (Figure 4A-B).
-Hence, predators that encountered groups of prey with similar speeds tended to be more specialized in their tactic, while those that encountered groups of prey with varying speeds were less specialised.
+Hence, predators that encountered groups of prey with similar speeds tended to be more specialised in their tactic, while those that encountered groups of prey with varying speeds were less specialised.
 However, this correlation did not change with experience (Figure 4C).
@@
 
-## Success along the foraging specialization continuum
+## Success along the foraging specialisation continuum
 
@@
 
-A general assumption of predator-prey studies is that predators maximize success by matching their tactic to their prey [@abrams2000], yet, it has remained largely unknown whether this results from predators learning how to hunt their prey in part because of the challenges of investigating direct interactions in the wild.
-By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that while predators in *Dead by Daylight* did not show any increase in either behavioural specialization or flexibility with experience at the population level, individual predators developed their own behavioural trajectories over successive encounters with the prey.
-This was characterized by a continuum of hunting styles ranging from a slower and flexible strategy to a highly specialized fast-paced strategy, with some predators switching between the two across experience.
-The behavioural strategies of predators and prey tended to match across experience, suggesting that both were adjusting to each other.
-Specialized cursorial hunters encountered similar groups of prey, while slower and flexible hunters encountered varying groups of prey.
-Overall, predators along the flexible-specialist continuum achieved similar success, although flexible hunters were slightly less successful as advanced hunters.
+A general assumption in predator-prey studies is that predators maximize their success by matching their tactic to their prey [@abrams2000].
+Yet ecologists have historically struggled to determine whether this results from predators learning how to hunt their prey, in part due to the challenges of studying direct interactions in the wild.
+By capitalizing on a virtual predator-prey system where interactions were directly monitored, we found that individual predators in *Dead by Daylight*  developed behavioural strategies that were associated with prey behaviour over successive encounters.
+The strategies formed a continuum of hunting styles, ranging from a slower, generalist strategy to a highly specialised, fast-paced strategy.
+We also found that some predators switched strategies as they gained experience.
+specialised cursorial hunters encountered groups of prey moving at similar speeds, while the slower and generalist hunters encountered groups of prey with varying speeds.
+Overall, predators along the generalist-specialist continuum achieved similar success, although generalist hunters were slightly less successful at more advanced experience levels.
 
-The predator population maintained its speed and degree of specialization throughout the study period, and individuals differed only slightly in their average speeds.
-However, differences in specialization among individuals were important and increased slightly with experience.
-Predators hunting at higher speeds specialized in this tactic and tended to encounter groups of prey with similar speeds, while those hunting at slower speeds were flexible and tended to encounter varying groups of prey.
-On one hand, this pattern could arise if some predators adjusted their strategy to their prey, because fast-paced hunting is a specialized tactic suited for prey that use rapid evasive movements, while a slower and flexible tactic can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@endler1991;@bro-jorgensen2013;@wilson.etal2018;@szopa-comley.ioannou2022].
-However, we observed that 44% of the predator population showed close to no change in specialization with experience.
-Since these individuals were already specialized as novices (Fraser Franco, personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they encountered faster prey more often.
+The predator population maintained its speed and degree of specialisation throughout the study period, and individuals differed only slightly in their average speeds.
+However, individuals displayed differences in foraging specialisation, and these differences increased slightly as individuals gained experience.
+Predators that hunted at higher speeds specialised in this tactic and tended to encounter groups of prey with similar speeds, while those that hunted at slower speeds were more generalists by switching tactics, and tended to encounter groups of prey moving at different speeds.
+On one hand, this pattern could arise if predators adjusted their strategy to their prey, because fast-paced hunting is a specialised tactic suited for prey that use rapid evasive movements, while a slower and generalist strategy can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@endler1991;@bro-jorgensen2013;@wilson.etal2018;@szopa-comley.ioannou2022].
+However, we observed that 44% of the predator population showed close to no change in specialisation with experience.
+Since these individuals were already specialised as novices (Fraser Franco, personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they encountered faster prey more often.
 This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
 Yet, because prey can also learn how to avoid predation [@kelley2003;@turner2006;@mccomb2011], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@kishida.etal2006;@kishida.etal2009;@edgell.rochette2009;@mcghee.etal2013].
-Indeed, 56% of the predator population altered its behaviour with experience to different degrees, including 12% that even switched between flexibility and specialization.
+Indeed, 56% of the predator population altered its behaviour with experience to different degrees, including 12% that even switched from a specialist to a generalist strategy and vice-versa.
 Hence, if the prey also learned through repeated interactions with the predators, it is possible that experience contributed in stabilizing the system as both were adjusting to each other, similar to Red Queen dynamics [@brockhurst2014].
 
-Classical theory predicts that individual foraging specialization should maximize prey consumption by optimizing foraging efficiency [@stephens1986], but other work suggests that flexibility and specialization could both be adaptive as resources fluctuate [@woo.etal2008;@phillips.etal2017].
-Our results support empirical findings indicating that flexible and specialist foragers obtained similar success [@weimerskirch2007;@woo.etal2008;@potier.etal2015;@phillips.etal2017;@courbin.etal2018], although flexible foragers were slightly less successful.
+Classical theory predicts that individual foraging specialisation should maximise prey consumption by optimising foraging efficiency [@stephens1986], but other work suggests that both generalist and specialist strategies could be adaptive as resources fluctuate [@woo.etal2008;@phillips.etal2017].
+Our results support empirical findings indicating that flexible and specialist foragers obtained similar success given prey behaviour [@weimerskirch2007;@woo.etal2008;@potier.etal2015;@phillips.etal2017;@courbin.etal2018], although generalist hunters were slightly less successful at more advanced stages.
 Both strategies appeared to emerge in part from individuals learning how to hunt their prey, resulting in a general increase in success in the population.
@@
 
-Specialist foragers were faster and probably better equipped to hunt the faster and more difficult prey in *DBD*.
-However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in challenging encounters for these predators too, thereby decreasing the benefits of using this tactic (Figure 3).
-Thus, specializing probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
-On the other hand, flexible foragers encountered a larger range of prey moving at slower speeds.
-Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for flexible hunters may have come at the cost of not being adept at capturing faster prey [@pintor.etal2014].
+Specialist foragers were faster and probably better equipped to hunt the faster and more difficult prey in *DBD* [@fraserfranco.etal2024].
+However, if the prey responded to fast predators by also being faster, then hunting at high speeds resulted in challenging encounters for these predators too, thereby decreasing the benefits of using this tactic (Figure 4).
+Thus, specialising probably compensated for the difficulty of hunting prey at high speeds by helping predators to better predict the location and movement of their prey.
+On the other hand, generalist hunters encountered a larger range of prey moving at slower speeds on average.
+Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for generalist hunters may have come at the cost of not being adept at capturing faster prey [@pintor.etal2014].
 Such trade-offs may reflect limitations in learning all the skills required to successfully hunt all types of prey [@healy1992;@belisle1997;@dukas2019], particularly if the skills required to hunt slower prey are nontransferable to faster prey.
@@
 
-We found support for our prediction that individual foraging specialization changed across experience and predator-prey interactions.
+We found support for our prediction that individual foraging specialisation changed across experience and predator-prey interactions.
 Our results suggest that predators learned with experience, as their success increased and their speed remained matched to the speed of their prey.
-Even though individuals were not all equally successful, both specialized and flexible hunters achieved similar success overall.
-A potential caveat is that the more flexible hunters might have experimented with various tactics out of boredom, which could impede ecologically realistic interpretations of our data.
+Even though individuals were not all equally successful, both specialised and generalist hunters achieved similar success overall.
+A potential caveat is that generalist hunters might have experimented with various tactics out of boredom, which could impede ecologically realistic interpretations of our data.
 However, the consistent association between this tactic and heterogeneous prey groups gives us confidence that it emerged from their interactions.

### 2025-04-09 code/04_code_figures/figure2.R

@@ -261,22 +261,22 @@ custom_theme <- theme(
 
 # y-axis labels
 labels_speed <- c(
-  "id_var" = "Individual foraging specialisation",
-  "id_mean" = "Individual foraging tactic",
-  "pop_var" = "Population foraging specialisation",
-  "pop_mean" = "Population foraging tactic"
+  "id_var" = "Individual foraging\nspecialisation",
+  "id_mean" = "Individual\nforaging tactic",
+  "pop_var" = "Population foraging\nspecialisation",
+  "pop_mean" = "Population\nforaging tactic"
 )
 
 labels_preyspeed <- c(
-  "id_var" = "Variation in prey encountered (id.)",
-  "id_mean" = "Mean prey encountered (id.)",
-  "pop_var" = "Variation in prey encountered (pop.)",
-  "pop_mean" = "Mean prey encountered (pop.)"
+  "id_var" = "Variation in prey\nencountered (id.)",
+  "id_mean" = "Mean prey\nencountered (id.)",
+  "pop_var" = "Variation in prey\nencountered (pop.)",
+  "pop_mean" = "Mean prey\nencountered (pop.)"
 )
 
 labels_success <- c(
-  "id_mean" = "Mean individual success",
-  "pop_mean" = "Mean population success"
+  "id_mean" = "Mean individual\nsuccess",
+  "pop_mean" = "Mean population\nsuccess"
 )
 
 # Set dodge

### 2025-04-09 code/04_code_figures/appendix2_figureS1.R
on Windows --> updt fig2 and fig apdx2 S1

@@ -15,6 +15,7 @@
 # Load libraries
 library(brms)
 library(ggplot2)
+library(ggpubr)
 library(viridis)
 library(data.table)
 
@@ -115,29 +116,29 @@ dt1[
   , parameter := ifelse(
     variable %like% "sd" &
       variable %like% "sigma",
-    "individual variation IIV",
-    "population variation"
+    "id_var",
+    "pop_var"
   )
 ]
 
 dt1[
   !(variable %like% "sigma") &
     variable %like% "sd",
-  parameter := "individual variation mean"
+  parameter := "id_mean"
 ]
 
 dt1[
   variable %like% "Intercept" &
     !(variable %like% "sigma") &
     !(variable %like% "sd"),
-  parameter := "population mean"
+  parameter := "pop_mean"
 ]
 
 
 # Add trait
-dt1[variable %like% "speed", trait := "predator speed"]
-dt1[variable %like% "preyspeed", trait := "prey speed"]
-dt1[variable %like% "success", trait := "success"]
+dt1[variable %like% "speed", trait := "Predator speed"]
+dt1[variable %like% "preyspeed", trait := "Prey speed"]
+dt1[variable %like% "success", trait := "Hunting success"]
 
 dt1[, variable := NULL]
 
@@ -173,13 +174,13 @@ tab3 <- cbind(nov, adv[, 3])
 
 # Calculate difference
 tab1[, diff := value_int - value_nov][
-  , test := "intermediate vs novice"
+  , test := "intermediate - novice"
 ]
 tab2[, diff := value_adv - value_int][
-  , test := "advanced vs intermediate"
+  , test := "advanced - intermediate"
 ]
 tab3[, diff := value_adv - value_nov][
-  , test := "advanced vs novice"
+  , test := "advanced - novice"
 ]
 
 # Combine
@@ -222,7 +223,7 @@ tab[
     upper_95 = upper_95(diff),
     upper_80 = upper_80(diff),
     upper_50 = upper_50(diff)
-    ),
+  ),
   by = .(trait, parameter, test)
 ]
 
@@ -234,111 +235,127 @@ tab[
 
 tab <- unique(tab[, c(1, 2, 4:11)])
 
-# Reorder factor levels
-tab[
-  , parameter := factor(
-      parameter,
-      levels = c(
-        "individual variation IIV",
-        "individual variation mean",
-        "population variation",
-        "population mean"
-      )
-  )
-]
 
 
[…]

### 2025-04-09 code/04_code_figures/figure2.R

@@ -360,7 +360,7 @@ path <- file.path(getwd(), "outputs", "04_outputs_figures")
 ggsave(
   filename = file.path(path, "figure2.png"),
   plot = fig,
-  width = 52, height = 14, # 32 14
+  width = 38, height = 14, # 32 14
   units = "cm",
   dpi = 300, scale = 0.9
 )

### 2025-04-10 manuscript/appendix2.Rmd
update appdx2 and ms with new figures. corrected text on outlier

@@
      Individual foraging specialization and success change across experience in a virtual predator-prey system: \
-     Appendix 3
+     Appendix 2
 
@@
 
-```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Posterior median differences and HPD intervals comparing the parameter values predicted by the MDHGLM among all predator experience levels.
-The parameter being compared is on the y axis, and the difference in parameter values between two experience levels is displayed on the x axis.
-The pairwise comparisons between experience levels are displayed across the three panels A, B, and C.
+```{r figS1, out.width = "100%", fig.cap = "**Figure S1.** Median posterior differences and HPD intervals comparing predator foraging behaviour, prey behaviour, and predator hunting success at the population and individual level across experience stages.
+The parameters being compared are on the y axis, and the differences in parameter values between two experience stages are on the x axis.
+The pairwise comparisons between experience stages are displayed as different point shapes on each panel.
+A) For the predator speed, we compare the foraging tactic (mean) and specialisation (variance) at the population level and at the individual level between each experience stage.
+B) For the prey speed, we compare the mean and the variance in speed of prey encountered at the population and individual level between each experience stage.
+C) For the predator hunting success, we compare the mean success at the population and individual level between each experience stage.
 The results are from the model that includes the outlier."}

### 2025-04-10 manuscript/manuscript.Rmd
update appdx2 and ms with new figures. corrected text on outlier

@@
 
-After inspection of the results, we found that key parameter values for our hypotheses were in the direction of our predictions, but they were largely driven by the very slow speed of one predator.
-Removing this individual reduced the estimates by a significant margin.
+After inspection of the results, we found that key parameter values for our hypotheses were driven by the very slow speed of one predator.
+Although the results are mostly similar, removing this individual reduced the variance estimates at the individual level.
 To remain conservative, we thus present the results of the model without this individual in the main text, and provide the results of the model including it in the Appendix 2.

### 2025-04-11 manuscript/manuscript.Rmd
on Windows --> Integrate CLint's comments

@@
 In natural populations, individuals specialise in the use of tactics such as ambushing and roaming, or switch tactics based on the prey that they encounter, often resulting in differences in prey consumption [@toscano2014;@patrick.weimerskirch2014a;@toscano.etal2016].
-The success of specialist and generalist strategies depend on ecological factors: when resources are abundant, specialist hunters achieve greater success, while generalist hunters prevail under fluctuating conditions [@Terraube2011;@Terraube2014;@phillips.etal2017].
-While evolutionary history can partly explain how specialist and generalist species will fare under given ecological conditions, learning also plays an important part in shaping predator foraging behaviour [@wooster.etal2023].
+The success of specialist and generalist strategies depends on ecological factors: when resources are abundant, specialist hunters achieve greater success, while generalist hunters prevail under fluctuating conditions [@Terraube2011;@Terraube2014;@phillips.etal2017].
+While evolutionary history can partly explain how specialist and generalist species will fare under given ecological conditions, learning also plays an important part in shaping predator-foraging behaviour [@wooster.etal2023].
 This has prompted ecologists to hypothesise that experience may underly associations between foraging specialisation and prey capture as predators learn and become efficient hunters through repeated encounters with their prey [@estes.etal2003;@woo.etal2008;@phillips.etal2017].
@@
 Such conditions favor specialist hunters, as they require less energy and time to search for, capture, and handle prey [@weimerskirch2007;@woo.etal2008;@potier.etal2015].
-For example, habitat specialisation under stable resources is associated with reduced foraging effort and increased offspring growth rates in Herring Gulls (*Larus argentatus*) [@vandenbosch.etal2019].
+For example, habitat specialisation under stable resources is associated with reduced foraging effort and increased offspring growth rates in herring gulls (*Larus argentatus*) [@vandenbosch.etal2019].
 In the second scenario, predators are expected to be more generalist by learning to use a variety of hunting tactics when they hunt in highly variable environments.
-Indeed, while there can be costs to attempt novel tactics by trial and error, predators can reduce the consequences of uncertainty in environments under fluctuating resources by learning to adjust their tactic to the prey that they encounter [@dall2010;@mathot.etal2012;@stephens1993;@ishii.shimada2010;@kelley.magurran2011].
+Indeed, while there can be costs to attempt novel tactics by trial and error, predators can reduce the consequences of uncertainty in environments where resources fluctuate by learning to adjust their tactics to the prey that they encounter [@dall2010;@mathot.etal2012;@stephens1993;@ishii.shimada2010;@kelley.magurran2011].
 @szopa-comley.ioannou2022 showed that predatory blue acaras (*Andinoacara pulcher*) reduce their maximum approach speed when repeatedly exposed to prey that escape unpredictably, enabling them to be as successful as those exposed to predictable prey.
@@
 
-In this study, we use data from players in the online videogame *Dead by Daylight* to investigate 1) how repeated interactions with prey shape predator foraging specialisation and 2) how the relationship between specialisation and foraging success changes over time.
+In this study, we use data from players in the online videogame *Dead by Daylight* to investigate 1) how repeated interactions with prey can shape predator foraging specialisation and 2) how the relationship between specialisation and foraging success changes over time.
 *Dead by Daylight* simulates a predator-prey interaction across complex virtual environments, providing a system to test ecological hypotheses on foraging behaviour, group selection, and social interactions [reviewed in @montiglio2025].
@@
 They differ in their mean behaviour (tactic) which is adjusted to the prey that they encountered.
-Because encounters where predictable, they all display similar degrees of individual foraging specialisation, resulting in the population being specialised.
+Because encounters were predictable, they all display similar degrees of individual foraging specialisation, resulting in the population being specialised.
 B) all predators encounter varying types of prey (e.g., in some encounters the prey were fast, in others the prey were slower), such that they also display similar degrees of individual foraging specialisation as in panel A.
@@
 In this case, some individuals consistently encountered similar prey, and thus specialised, while others encountered varying groups of prey, thus becoming generalists.
-Ultimately, those that learn to specialise on the proper tactic given prey encounters have greater success than those that didn't, resulting in no differences between specialists and generalists."}
+Ultimately, those that learn to specialise on the proper tactic given prey encounters have greater success than those that did not, resulting in no differences between specialists and generalists."}
 
@@
 
-To test the hypothesis that repeated interactions with prey shape predator foraging specialisation, we analyze the movement speed of predators and their prey over time.
+To test the hypothesis that repeated interactions with prey can shape predator foraging specialisation, we analyze the movement speed of predators and their prey over time.
 To assess how foraging specialisation emerges throughout experience, we define the level of individual foraging specialisation as the intra-individual variance (IIV) in movement speed across matches following the definition by @cleasby.etal2015.
-Low IIV describes individual foraging specialisation (i.e., always using an ambush or cursorial tactic) whereas high IIV describes a flexible use of foraging tactics (i.e., generalist predators switching between ambush and cursorial tactics, see Methods for details).
-First, we expect predators to differ in the use of their hunting tactic (i.e., mean movement speed) which will be tuned to the mean speed of the prey that they encounter (Figure 1A-B).
-Second, we predict that if all predators consistently encounter prey moving at similar speeds, then the population as a whole (i.e., all individuals) should specialise on moving at similar speeds, resulting in a narrow behavioural niche (Figure 1A).
+Low IIV describes individual foraging specialisation (i.e., always using an ambush or cursorial tactic) whereas high IIV describes a general and flexible use of foraging tactics (i.e., plastic/generalist predators switching between ambush and cursorial tactics, see Methods for details).
+First, we expect predators to differ in the use of their hunting tactic (i.e., individual-mean movement speed) which will be tuned to the mean speed of the prey that they encounter (Figure 1A-B).
+Second, we predict that if all predators consistently encounter prey moving at similar speeds, then the population as a whole (i.e., all individuals) should specialise in moving at similar speeds, resulting in a narrow behavioural niche (Figure 1A).
 In contrast, if all predators encounter groups of prey moving at varying speeds, then they should all become more flexible in their tactic use (i.e., generalists), adjusting their speed to the prey from one encounter to the other, resulting in a higher population variance in foraging behaviour (Figure 1B).
-In both scenarios, differences among individuals in IIV across experience should be low (i.e., similar individual foraging specialisation, Figure 1A-B).
+In both scenarios, differences among individuals in IIV across experience should be low (i.e., a similar degree of individual foraging specialisation, Figure 1A-B).
 Alternatively, differences among individuals in foraging specialisation may emerge if they experience different interactions with their prey.
-In this case, predators that encountered prey moving at similar speeds across experience should specialise on moving at a more fixed speed, while predators that encountered different prey speeds across matches should adopt a generalist movement strategy, resulting in an increase in among individual differences in IIV (Figure 1C).
-Lastly, if we detect such prey-dependent fine-tuning with experience, then specialist and generalist hunters should attain equal success, resulting in no apparent relationship between foraging specialisation and prey capture (Figure 1C).
+In this case, predators that encountered prey moving at similar speeds across experience should specialise in moving at a fixed speed, while predators that encountered different prey-speeds across matches should adopt a generalist movement strategy, resulting in an increase in among individual differences in IIV (Figure 1C).
+Lastly, if we detect such prey-dependent fine-tuning with experience, then specialist and generalist hunters should achieve equal success, resulting in no apparent relationship between foraging specialisation and prey capture (Figure 1C).
 
@@
 
-*DBD* is an asymmetric multiplayer survival game developed by Behaviour Interactive Inc.
+*DBD* is an asymmetric multiplayer survival game developed by Behaviour Interactive Inc [@cere.etal2021;@fraserfranco.etal2022;@santostefano.etal2024;@cere.etal2024;@montiglio2025].
 In this game, participants take on roles as either a predator or one of the prey, with each match consisting of one predator and four prey.
@@
 The virtual environments in which matches are played vary in size and structural complexity, combining fixed and procedurally generated elements such as vegetation, buildings, and maze-like structures.
-Troughout the study period, there were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for gameplay.
+Throughout the study period, there were `r toString(format(length(unique(dat$environment_id))))` virtual game environments available for gameplay.
 
@@
 We excluded matches where players were inactive, as indicated by null or nearly null movement speeds, and matches where players were suspected of hacking or engaging in unintended gameplay behaviour based on our knowledge of the game mechanics.
-We then selected a cohort of players that played 300 matches or more, and monitored all their matches from the first to a maximum of 500 matches.
+We then selected a cohort of players that played 300 matches or more and monitored all their matches from the first to a maximum of 500 matches.
 
@@
 The predator's mean speed is measured as the mean distance traveled per second during a match (mean= `r toString(format(round(mean(dat$pred_speed), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$pred_speed), digits = 2), nsmall = 2))` m/s).
-We measured the preys' speed as the mean travel speed of the four individual prey in a match (mean = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
+We measured prey speed as the mean travel speed of the four individual prey in a match (mean = `r toString(format(round(mean(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` ± `r toString(format(round(sd(dat$prey_avg_speed, na.rm = T), digits = 2), nsmall = 2))` m/s).
 We defined hunting success as the number of prey consumed during the match (min = `r toString(format(min(dat$hunting_success)))`, max = `r toString(format(max(dat$hunting_success)))`).
-Lastly, we categorized predators for each match based on the experience they cumulated [see @fraserfranco.etal2024].
-We labeled predators as novices when they played between 1 and 99 matches, as intermediates between 100 and 299 matches, and as advanced between 300 and 500 matches.
+Lastly, we categorized predators for each match based on the experience they accumulated [see @fraserfranco.etal2024].
+We labelled predators as novices when they played between 1 and 99 matches, as intermediates between 100 and 299 matches, and as advanced between 300 and 500 matches.
 
@@
 Fixed and random effect structure was trait-specific and the same for all experience levels.
-For the predator and the prey speed, we modeled the mean and the residual standard deviation (eqn 1.1, 1.2 and 2.1, 2.2).
+For the speed of the predator and prey, we modeled the mean and the residual standard deviation (eqn 1.1, 1.2 and 2.1, 2.2).
 For both traits, we controlled for the standardized prey rank on the mean and the residual standard deviation.
@@
 We performed our analyses within a Bayesian framework.
-We used weakly informative Gaussian priors for the prey rank ($N(0,\ 1^{2})$: eqn.
-1.1 to 2.2) and game duration ($N(0.5,\ 0.5^{2})$: eqn.
-3).
-Based on previous results showing that the mean predator speed revolves around 3 m/s [@fraserfranco.etal2022], we applied a weakly informative Gaussian prior on the intercept for predator and prey speed ($N(3,\ 0.5^{2})$: eqn.
-1.1 and 2.1).
-Similarly, we used a weakly informative Gaussian prior on the intercept for the dispersion part ($N(0,\ 1^{2})$: eqn 1.2 and 2.2).
+We used weakly informative Gaussian priors on the slopes of the prey rank ($N(0,\ 1^{2})$: eqn.
+1.1 to 2.2) for both the mean and dispersion.
+We used a weakly informative Gaussian prior on the slope of the game duration ($N(1,\ 0.5^{2})$: eqn.
+3) for the mean hunting success.
+Based on previous results showing that the mean predator speed is approximately three m/s [@fraserfranco.etal2022], we applied a weakly informative Gaussian prior on the intercept of the predator and the prey speed ($N(3,\ 0.5^{2})$: eqn.
+1.1 and 2.1) on the mean part.
+Similarly, we used a weakly informative Gaussian prior on the intercept of the dispersion part ($N(0,\ 1^{2})$: eqn 1.2 and 2.2).
 For hunting success, we applied a positive Gaussian prior on the precision parameter ($N(2,\ 1^{2})$: eqn.
@@
 We fitted the model in R (version 4.1.2) using Hamiltonian Monte Carlo (HMC) sampling with the package "brms" version 2.16.3 [@burkner2017], an R front-end for the STAN software [@StanDevelopmentTeam2023], and "cmdstanr" version 0.4.0 [@gabry.cesnovar2021] as the back-end for estimation (cmdstan installation version 2.28.2).
-We ran te model on on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
+We ran the model on Cedar (Operating system: CentOS Linux 7), a computer cluster maintained by the Digital Research Alliance of Canada (https://docs.alliancecan.ca/wiki/Cedar).
 
-We parametrized the MDHGLM to run 2500 iterations on four chains with a thinning interval set at eight iterations, with the first 500 used as warm up iterations (yielding 1000 posterior samples for each parameter).
+We parametrized the MDHGLM to run 2500 iterations on four chains with a thinning interval set at eight iterations, with the first 500 used as warm-up iterations (yielding 1000 posterior samples for each parameter).
 We assessed the convergence of the chains using trace plots, R-hat diagnostics with a threshold of <1.01, and effective sample sizes (ESS) with a threshold of >100 [@vehtari.etal2021].
@@
 Although the results are mostly similar, removing this individual reduced the variance estimates at the individual level.
-To remain conservative, we thus present the results of the model without this individual in the main text, and provide the results of the model including it in the Appendix 2.
+To remain conservative, we thus present the results of the model without this individual in the main text, and provide the results of the model including it in Appendix 2.
 
@@
 However, predators displayed minor differences in foraging specialisation as novices, with differences increasing slightly as individuals gained experience (Figure 2A and Appendix 1: Table S2).
-`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a more specialised hunting tactic, and vice-versa, as predators gained experience (i.e., >0.2 change in standard deviation; Figure 3).
+`r toString(scales::percent(percent_tab2[1,]$percentage, accuracy = 1))` of the population switched from a flexible to a specialised hunting tactic, and vice-versa, as predators gained experience (i.e., >0.2 change in standard deviation; Figure 3).
 In contrast, `r toString(scales::percent(percent_tab2[2,]$percentage, accuracy = 1))` displayed lower changes (i.e., >0.05 and <0.2 change in standard deviation) and `r toString(scales::percent(percent_tab2[3,]$percentage, accuracy = 1))` showed almost no change with experience (i.e., <0.05 change in standard deviation).
@@
 Median posterior differences and HPD intervals comparing predator foraging behaviour, prey behaviour, and predator hunting success at the population and individual level across experience stages.
-The parameters being compared are on the y axis, and the differences in parameter values between two experience stages are on the x axis.
+The parameters being compared are on the y-axis, and the differences in parameter values between the two experience stages are on the x-axis.
 The pairwise comparisons between experience stages are displayed as different point shapes on each panel.
+The compatibility intervals are of 50%, 80%, and 95%.
 A) For the predator speed, we compare the foraging tactic (mean) and specialisation (variance) at the population level and at the individual level between each experience stage.
@@
 At the population level, we found strong evidence that the prey increased their speed slightly as predators gained experience (Figure 2B and Appendix 1: Table S1).
-The predators also encountered a greater variation of prey speeds at later experience stages (Figure 2B and Appendix 1: Table S1).
+The predators also encountered more variation in prey speeds at later experience stages (Figure 2B and Appendix 1: Table S1).
 At the individual level, predators encountered prey with similar average speeds across experience stages (Figure 2B and Appendix 1: Table S2).
@@
 Individual behavioural distribution of the predators' speed drawn from the MDHGLM estimates for individuals that had (A) the greatest increase and (B) the greatest decrease in specialisation.
-The background (gray) distributions are for when individuals were novice hunters, and the foreground (blue) distributions with solid contour lines are for when they were advanced hunters.
+Distributions represent speed when individuals were either novice (grey) or advanced (blue with solid contour line).
 Both figure panels are ordered by ascending degree of change in specialisation.
-We built the figure by first subtracting the estimated standard deviation of all individuals as novices with their standard deviation as advanced hunters, and then selected those with the greatest difference using the 25% and 75% quantiles.
+We built the figure by first subtracting the estimated standard deviation of all individuals as novices from their standard deviation as advanced hunters and then selected those with the greatest difference using the 25% and 75% quantiles.
 Individuals on panel A have an increase in specialisation equal or greater than 0.2 standard deviations, while those on panel B have an increase in flexibility equal to or greater than 0.2 standard deviations."}
@@
 As predators gained experience, these strategies were increasingly defined as the correlation changed from -0.62 (-0.70, -0.55 $95\%\ CI$) among novices to -0.78 (-0.83, -0.72 $95\%\ CI$) among advanced hunters (Figure 4C).
-Faster predators tended to encounter faster prey; they also encountered groups of prey groups of prey that were more similar from match to match (Figure 4A-B), irrespective of their experience (Figure 4C).
+Faster predators tended to encounter faster prey; they also encountered groups of prey that were more similar from match to match (Figure 4A-B), irrespective of their experience (Figure 4C).
 
-There was no correlation (-0.02, -0.14, 0.01 $95\%\ CI$) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.27, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialised (Figure 4C).
+There was no correlation (-0.02, [-0.14, 0.01] $95\%\ CI$) between mean prey speed and IIV in predator speed when predators were novice (Figure 4A), but the correlation increased to -0.16 (-0.27, -0.04 $95\%\ CI$) at the advanced stage (Figure 4B), such that advanced hunters that encountered faster prey tended to be more specialised (Figure 4C).
 Predators with a larger IIV in speed encountered a greater range of prey speeds, but this effect was weak (Figure 4A-B).
@@
 More specialised predators achieved a slightly greater foraging success, but this effect was weak (Figure 4).
-This relationship between the predator's IIV in speed and success increased with experience (Figure 4C), suggesting that the success gap between generalists and specialists increased with experience (Appendix 1: Figure S2).
+The relationship between the predator's IIV in speed and success increased with experience (Figure 4C), suggesting that the success gap between generalists and specialists increased with experience (Appendix 1: Figure S2).
 There was strong evidence that predators that encountered faster prey and prey groups with similar speeds were less successful (Figure 4A-B), irrespective of their experience level (Figure 4C).
@@
 We also found that some predators switched strategies as they gained experience.
-specialised cursorial hunters encountered groups of prey moving at similar speeds, while the slower and generalist hunters encountered groups of prey with varying speeds.
+Specialised cursorial hunters encountered groups of prey moving at similar speeds, while the slower and generalist hunters encountered groups of prey with varying speeds.
 Overall, predators along the generalist-specialist continuum achieved similar success, although generalist hunters were slightly less successful at more advanced experience levels.
@@
 However, individuals displayed differences in foraging specialisation, and these differences increased slightly as individuals gained experience.
-Predators that hunted at higher speeds specialised in this tactic and tended to encounter groups of prey with similar speeds, while those that hunted at slower speeds were more generalists by switching tactics, and tended to encounter groups of prey moving at different speeds.
+Predators that hunted at higher speeds specialised in this tactic and tended to encounter groups of prey with similar speeds (low variance between encounters), while those that hunted at slower speeds tended to switch tactics and be more generalists because they encountered groups of prey moving at different speeds (high variance betweenn encounters).
 On one hand, this pattern could arise if predators adjusted their strategy to their prey, because fast-paced hunting is a specialised tactic suited for prey that use rapid evasive movements, while a slower and generalist strategy can be useful to minimize the consequences of uncertainty when prey escape unpredictably [@endler1991;@bro-jorgensen2013;@wilson.etal2018;@szopa-comley.ioannou2022].
@@
 Since these individuals were already specialised as novices (Fraser Franco, personal observation), there would be no point in them changing their tactic with experience if they were already successful, or there could have been costs to switch their strategy if they encountered faster prey more often.
-This could explain why the behavioural interactions between the predator and the prey remained stable across the predator's experience.
+This could explain why the behavioural interactions between predator and prey remained stable across the predator's experience.
 Yet, because prey can also learn how to avoid predation [@kelley2003;@turner2006;@mccomb2011], we believe that the predator-prey phenotype matching more likely emerged from reciprocal adjustments in speed by predators and prey as they interacted [@kishida.etal2006;@kishida.etal2009;@edgell.rochette2009;@mcghee.etal2013].
-Indeed, 56% of the predator population altered its behaviour with experience to different degrees, including 12% that even switched from a specialist to a generalist strategy and vice-versa.
-Hence, if the prey also learned through repeated interactions with the predators, it is possible that experience contributed in stabilizing the system as both were adjusting to each other, similar to Red Queen dynamics [@brockhurst2014].
+Indeed, 56% of the predator population altered its behaviour with experience, including 12% that even switched from a specialist to a generalist strategy and vice-versa.
+Hence, if the prey also learned through repeated interactions with the predators, it is possible that reciprocal interactions contributed to stabilizing the system as both were adjusting to each other, similar to Red Queen dynamics [@brockhurst2014].
 
@@
 On the other hand, generalist hunters encountered a larger range of prey moving at slower speeds on average.
-Yet, because the prey increased their speed with experience, the benefits of being able to hunt multiple prey types for generalist hunters may have come at the cost of not being adept at capturing faster prey [@pintor.etal2014].
+Yet, because prey increased their speed with experience, the benefits to generalist predators of hunting multiple prey types may have come at the cost of not being adept at capturing faster prey [@pintor.etal2014].
 Such trade-offs may reflect limitations in learning all the skills required to successfully hunt all types of prey [@healy1992;@belisle1997;@dukas2019], particularly if the skills required to hunt slower prey are nontransferable to faster prey.
